### 2016-07-17 test.tex
.

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{cite}
\usepackage{hyperref}

\begin{document}
\section{Abstract} \label{abstract}
Building on the LIF-SORN-model proposed in \cite{SORN_Paper}, we attempted to replace the intrinsic homeostatic control system used in the original version by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue. The model of diffusive homeostasis was adopted from a paper by Y. Sweeney et al. \cite{Sweeney_Paper} and models the tissue as a surface of square shape and a set of points on this surface, representing the positions of the neurons within the SORN. The group of excitatory neurons then acted as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position. The production and sensing of NO forms the basis of an intrinsic feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate. The control system is then closed by linking the rate of NO-production to the neuron's firing rate.

It should be mentioned that \cite{Sweeney_Paper} included all neurons into the homeostatic control. However, since we excluded inhibitory neurons from the original homeostatic control, we held this decision in the new model.

\section{Methods} \label{methods}
Network dynamics remained the same as in \cite{SORN_Paper}.

The original homeostatic control was described as an operation over discrete time steps $\Delta t$, carried out for each excitatory neuron:

\begin{align}
V_T &\rightarrow V_T + \eta_{IP} (N_{spikes} - h_{IP}) \label{can_hom_1}\\
N_{spikes} &\rightarrow 0 \label{can_hom_2}
\end{align}

where $V_T$ is the firing threshold, $\eta_{IP}$ an adaption rate and $h_{IP}$ the desired number of spikes per time step. $N_{spikes}$ is a variable, counting the number of spikes of a the neuron within each interval. In a continuous, rate-based form, this update rule can be written as:

\begin{equation}
\dot{V}_T = \eta_{IP}(r-r_{IP}) \label{can_hom_rate}
\end{equation}

with $r$ as the neurons momentary firing rate and $r_{IP}=h_{IP}/\Delta t$ the target firing rate.

This feedback control includes no interaction among neurons. The model presented in \cite{Sweeney_Paper} includes spacial interaction through a diffusive term. It is described by the following equations.

\begin{align}
\frac{dCa^{2+}_i}{dt}(t) &= -\frac{Ca^{2+}_i}{\tau_{Ca^{2+}}} + Ca^{2+}_{spike} \sum_{t_{spike}} \delta(t-t_{spike}) \label{Ca_dyn}\\
\frac{dnNOS_i}{dt}(t) &= \frac{1}{\tau_{nNOS}} \left(  \frac{{Ca^{2+}_i}^3}{{Ca^{2+}_i}^3+1} - nNOS_i \right) \label{nNOS_dyn}\\
\frac{dNO}{dt}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{neur,i})\cdot nNOS_i \label{NO_dyn}\\
\frac{d\theta_i}{dt}(t) &= \frac{NO(\mathbf{r}_{neur,i},t)-NO_0}{NO_0\cdot\tau_{\theta}} \label{Theta_dyn}
\end{align}

A depolarization within the cell causes an inflow of $Ca^{2+}$ ions, which is modelled as an instantaneous increase of the $Ca^{2+}$ concentration. Over time, the concentration decays exponentially by a time constant $\tau_{Ca^{2+}}$, see \eqref{Ca_dyn}. Though $Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198-203]{Theor_Neur_Dayan}. It has been experimentally observed that the intracellular $Ca^{2+}$ concentration influences neuronal Nitric oxide synthase \cite{Bredt_Snyder_NO}. This was modelled by Sweeney et al. through \eqref{nNOS_dyn}, using the Hill equation \cite{Hill_Equ} to model a cooperative binding mechanism. The $nNOS$ production is then fed into the "pool" of nitric oxide via point sources located at the neurons' positions \eqref{NO_dyn}. An additional decay term was added to provide a stable $NO$ concentration under constant neuronal activity.

Finally, the dynamics of the firing thresholds $\theta_i$ were modelled such that the rate of change is proportional to the relative deviation of the $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.

Obviously, the appropriate choice of $NO_0$ is crucial for the goal of achieving and maintaining certain level of activity. However, one cannot directly set a parameter of the model to the desired population activity, as it was the case for canonical intrinsic homeostasis. Rather, one needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration. Though it is possible to derive this relation in an analytic fashion, for practical purposes of the simulation, we let the system run with the previous homeostatic mechanism until a steady concentration level was reached. This level was then set to be the target concentration and we switched to diffusive homeostasis.

\section{Results} \label{results}
\subsection{Activity Analysis} \label{activ_analys}
Fig. \ref{full_sim_plots_av} shows the resulting dynamics of the population activity, average $NO$ concentration at the neurons' positions and the average firing threshold. Roughly speaking, both homeostatic mechanisms managed to keep the population activity in the desired range of $3~Hz$. However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Fig. \ref{full_sim_plots_av}, turn out to be very regular oscillations across all three parameters depicted in the closeup. While the oscillation amplitude undergoes a rather unpredictable time course, the frequency remains at a constant level of $\simeq 1Hz$. Although one might argue that regular oscillations of the $NO$ concentration are not of much concern in terms of the network's structure and behaviour, this is not true for the population activity.
\begin{figure}
\includegraphics[width=\textwidth]{../plots/diff_hom/rate_NO_th_compl.eps}
\includegraphics[width=\textwidth]{../plots/diff_hom/rate_NO_th_closeup.eps}
\caption{Population activity, average $NO$ concentration (averaged over readouts at neurons' positions) and average firing threshold. Canonical homeostasis was used for $0-250s$ , diffusive for $250-500s$. Activity target was $3 ~Hz$.}
\label{full_sim_plots_av}
\end{figure}

A first approach in comparing the network activity before and after altering the homeostatic mechanism is by means of the distribution of firing rates within the network. As Sweeney et al. point out, it has been experimentally observed that firing rates are rather heterogeneous, resulting in a broad distribution. In Fig. \ref{firing_rate_dist_comp} we compare our results for the firing distribution to the results by Sweeney et al.. 
\begin{figure}
\includegraphics[width=\textwidth]{../plots/firing_rate_dists/firing_rate_dist_compare.eps}
\caption{Left: Simulation results by Sweeney et al.. Right: Simulation results for the SORN.}
\label{firing_rate_dist_comp}
\end{figure}
We observed a similar tendency of broader firing rate distributions for the diffusive homeostasis, though we did not get as heavy tailed statistics. Sweeney et al. found a reciprocal relation between the broadness of the firing rate distribution and the threshold distribution. The strong oscillations of the threshold make it difficult to estimate the threshold distribution in our case. For the plot in Fig. \ref{thresh_dist_comp}, we calculated each neuron's time average threshold for the case of non-diffusive and diffusive homeostasis and used this as a basis for the distribution. In contrast to Sweeney et al., the statistics did not change significantly.
\begin{figure}
\includegraphics[width=\textwidth]{../plots/diff_hom/threshold_dist_compare.eps}
\caption{Comparison of threshold distributions observed by Sweeney et al. (left) and in the SORN (right).}
\label{thresh_dist_comp}
\end{figure}

Another possibility of characterizing neural activity is to determine the distribution of interspike intervals (ISIs). Using non-diffusive homeostasis, one can observe a Poisson-like spiking behaviour with a stochastic refractory period, which is typically observed in cortical networks (Fig. . This is not what can be observed for the case of diffusive homeostasis: the ISI distribution reveals preference of interspike times in the range of $1s$, whereas interspike times in of $0.1-0.6s$ are less likely than a Poisson process would predict. This deviation matches the frequency of activity oscillations, see Fig. \ref{full_sim_plots_av}.
\begin{figure}
\includegraphics[width=\textwidth]{../plots/Spike_Stats/ISI_compare_SORN.eps}
\caption{Top: log-plot of ISI-distribution of diff. and non-diff. homeostasis in the SORN. Bottom: CV-distribution for diff and non-diff. homeostasis.}
\label{ISI_compare}
\end{figure}

As a whole, the oscillating activity imposes a undesirable regularity onto the network's activity, see also Fig. \ref{spike_sequence}. While this effect might be tolerable without any external input, it is likely that the oscillations will overlay and obscure network responses onto external drive, presumably making it unusable for any computational task.
\begin{figure}
\includegraphics[width=\textwidth]{../plots/Spike_Stats/spike_sequence.eps}
\caption{A spike sequence of 10 randomly picked excitatory neurons of the SORN. At $t=250s$, the homeostatic mechanism is switched to the diffusive variant.}
\label{spike_sequence}
\end{figure}

\subsection{Analysis of sustained Oscillations}\label{theor_osc}

To find an explanation for the described oscillations and a possible way of avoiding them, one has to find the necessary minimal set of mechanisms, required to explain the observed phenomenon, without oversimplifying crucial aspects of the minimal model. In our model, there are two aspects whose simplification is of particular importance: First, it is impossible to analytically predict every single spike within the entire network. Our analytical treatment therefore aims to find analytical expressions for momentary firing rates among the network. Second, one might speculate that the exact solution of the NO diffusion process can be simplified in favour of a model, where one describes the dynamics of the average NO concentration across the nervous tissue. This approach can be justified by the fact that a unified, average NO concentration is effectively equal to a very large diffusion rate.

We took several approaches to find the minimal set of equations that sufficiently reproduces the desired phenomena. Here, we will present the final and most successful version. We derived the equation from the following assumptions and results:

\begin{itemize}
\item Oscillations persisted for very large diffusion constants. Therefore, one may assume that the dynamics of NO solely depend on the decay rate $\lambda$ and can be expressed by a single scalar variable.
\item We observed that even though the overall activity oscillated, the total input for each neuron remained at a relatively steady level, only showing random fluctuations with periodically increasing and decreasing deviations. One can therefore assume that the effect of recurrent, "self-feeding" network dynamics can be neglected.
\item The firing rate distribution has a significant variance.
\item Since we simplified the NO dynamics to a global variable, all thresholds follow the same dynamics (apart from a variance in the initial conditions). We can therefore as well reduce the problem to a single average threshold variable.
\item The phase difference between threshold and activity appears to be practically zero. It is therefore reasonable to assume a direct functional dependence $r_{pop}=r(\theta)_{pop}$.
\item In the regime of the desired population activity of $3~Hz$, nonlinearities within the "$spike \rightarrow Ca^{2+} \rightarrow nNOS$" mechanism can be neglected in favour of a simple relation $nNOS = C\cdot r_{pop}$.  
\end{itemize}

These conclusions can be transferred into the following "simple" dynamical system:
\begin{align}
\dot{NO} &= -\lambda NO + C\cdot r(\theta) + C\cdot \sigma \xi(t) \label{simple_NO_dyn}\\ 
\dot{\theta} &= \frac{NO}{NO_0\cdot \tau_{\theta}} \label{simple_threshold_dyn}
\end{align}
Here, $\xi(t)$ represents standard gaussian noise, accounting for the fact that, apart from the regular oscillation, the population activity features a certain amount of fluctuations. As an additional simplification, the fixed point was set to the origin.

To complete the expression, one has to find an appropriate description of the $r(\theta)$-relation. As a most simple approximation, we applied a linear regression to the data of the average threshold and the corresponding population activity, see Fig. \ref{thresh_r_linfit}. The constant $C$ in equation \eqref{simple_NO_dyn} is then proportional to the slope of the linear fit. In addition, $C$ is proportional to the amount of NO released per spike, proportional to the number of contributing neurons and antiproportional to the total area of the tissue. We can solve and integrate equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} for a single spike, resulting in a total of $\tau_{Ca^{2+}}\cdot ln(1+{Ca^{2+}_{spike}}^3) / 3$. Therefore, $C=N_{neur}\cdot \tau_{Ca^{2+}}\cdot ln(1+{Ca^{2+}_{spike}}^3) / (3\cdot L^2)$ and $C\cdot r(\theta)=\theta \cdot \alpha \cdot N_{neur} \cdot \tau_{Ca^{2+}}\cdot ln(1+{Ca^{2+}_{spike}}^3) / (3\cdot L^2)$, where $\alpha$ is the slope of the linear fit and $L^2$ the area of the tissue.
\begin{figure}
\includegraphics[width=\textwidth]{../plots/diff_hom/thresh_r_linfit.eps}
\caption{Linear fit of the relation between the firing threshold (averaged over population) and the population activity. $R^2=0.99996$.}
\label{thresh_r_linfit}
\end{figure}
\begin{figure}
\includegraphics[width=\textwidth]{../plots/diff_hom/lin_model_osc.eps}
\caption{Simulation results for equations \eqref{simple_NO_dyn} and \eqref{simple_threshold_dyn}.}
\label{lin_mod_osc}
\end{figure}
Fig. \ref{lin_mod_osc} shows the results achieved from the simulation. We observe that noise is capable of maintaining oscillations in an otherwise stable linear system.

Is it possible to get a better understanding of the achieved dynamics? For that purpose, we note that equations \eqref{simple_NO_dyn} and \eqref{simple_threshold_dyn} can be transformed into the following:

\begin{align}
\dot{v} &= -\frac{\lambda}{m} v - \omega_0^2 x + \frac{C\cdot \sigma}{m} \xi (t) \label{langevin_v} \\
\dot{x} &= v \label{langevin_x}
\end{align}
with $x=\theta NO_0 \tau_{\theta}$, $v=NO$, $m=1$ and $\omega_0^2 =-\frac{\alpha C}{NO_0 \tau_{\theta}}$. This set of equations is equal to a Langevin equation, describing a brownian particle in a harmonic potential. By taking the fourier transform of both equations, one can find an analytic expression for the power spectrum of the particle's location:
\begin{equation}
S_x (\omega) = \frac{S_\xi (\omega)}{(\omega_0^2 - \omega^2)^2 + \lambda^2 \omega^2} \label{power_spec_part}
\end{equation}
where, in the case of white gaussian noise, $S_\xi(\omega)=C^2 \cdot \sigma^2$. Substituting the transformations yields
\begin{equation}
S_\theta (\omega) = \left( \frac{C \sigma}{NO_0 \tau_\theta}\right)^2 \frac{1}{(\frac{\alpha C}{NO_0 \tau_\theta} + \omega^2)^2 + \lambda^2 \omega^2} \label{power_spec_thresh}
\end{equation}
By calculating the steady-state solution of equation \eqref{simple_NO_dyn}, one can analytically express the target concentration $NO_0$ as a function of the desired pop. rate $r_g$:
\begin{equation}
NO_0=r_g \frac{N_e \cdot \tau_{Ca^{2+}} \cdot ln(1+{Ca_{Spike}^{2+}}^3)}{3\lambda L^2} = r_g \frac{C}{\lambda}
\label{NO_analytic}
\end{equation} 
Substituting into equ. \eqref{power_spec_thresh} one gets
\begin{equation}
S_\theta (\omega) = \frac{\sigma^2}{(\alpha+\frac{r_g \tau_\theta \omega^2}{\lambda})+\tau_\theta^2 r_g^2 \omega^2}
\label{power_spec_thresh_r_g}
\end{equation}
The maximum of this function then is
\begin{align}
\omega_{max} &= \sqrt{-\lambda(\frac{1}{2}+\frac{\alpha}{\tau_\theta r_g})} \label{max_omega}\\
S_\theta(\omega_{max}) &= \frac{\sigma^2}{\tau _\theta^2 r_g^2 \left(\frac{1}{4}-\frac{\lambda}{2}\right)-\alpha \lambda \tau _\theta r_g} \label{S_max_omega}
\end{align}

Fig. \ref{power_spec_thresh_sim_vs_an} suggests that the theoretical result does not fully cover the dynamics of the simulation, but supports the observation of a sustained oscillation at a preferred frequency.

\begin{figure}
\includegraphics[width=\textwidth]{../plots/power_spec/power_spectrum3}
\caption{Power Spectrum of the firing threshold and analytic result of equation \eqref{power_spec_thresh_r_g}.}
\label{power_spec_thresh_sim_vs_an}
\end{figure}

For the purpose of reducing the oscillations to a negligible amplitude, $\lambda$ and $\tau_\theta$ can be increased. Note however that increasing $\lambda$ will also increase $\omega{max}$, which will presumably result in faster oscillations. $\tau_\theta$ on the other hand leads to a decrease of both, $\omega_{max}$ and $S_\theta(\omega_{max})$.

Since the $S_\theta(\omega)$ represents a spectral density, one should not directly relate $S_\theta(\omega_{max})$ to the actual squared amplitude of the oscillation. However, due to the linearity of the fourier transform, "rescaling" in the frequency spectrum also proportionally alters the amplitude of the signal in the time domain.

\section{The Firing Rate Distribution in the Network}

As shown in Fig. \ref{firing_rate_dist_comp}, the distribution of firing rates within the population of neurons is highly dependent on the diffusion constant $D$, in accordance to the findings by Sweeney et. al. To analyze this dependence, a dynamic mean-field approach was suggested in \cite{Sweeney_Paper}. In short, it consists of set of equations which need to be fulfilled self-consistently.

\begin{align}
\nu &= \langle \phi \rangle = \frac{\sum \phi_i}{N} \label{sweeney_self_consist_rate1} \\
\phi_i &= \phi_i(\mu_i(\nu),\sigma_i(\nu),\theta_i) \label{sweeney_self_consist_rate2} \\
\mu_i &= J_iC_i\nu \tau \label{sweeney_self_consist_rate3} \\
\sigma_i &= J_i\sqrt{C_i\nu  \tau} \label{sweeney_self_consist_rate4}
\end{align}

where $\nu$ is the mean population firing rate, $\phi_i$ the individual firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $\theta_i$ its synaptic input mean and standard deviation and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant. Self consistency is achieved by iterating through equations \eqref{sweeney_self_consist_rate1} and \eqref{sweeney_self_consist_rate2} until the desired precision is reached.

As a simplification, the authors of \ref{firing_rate_dist_comp} proposed to implement diffusive homeostasis in this context by the following equation:

\begin{equation}
\frac{d\theta_i}{dt} = \frac{1}{\tau_{HIP}} \left(  (1-\alpha)\frac{\phi_i-\phi_0}{\phi_i} +\alpha \frac{\langle \phi \rangle-\phi_0}{\langle \phi \rangle} \right) 
\label{diff_hom_simpl_sweeney}
\end{equation}

$\alpha \: \epsilon \: [0,1]$ thereby acts as a parameter that determines the "mixture" between single-neuron-homeostasis ($\alpha=0$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\alpha=1$).

The authors claim that this model reproduces observations in the full network, namely that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or a larger $\alpha$, respectively).

However, in the following, I will argue that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, no matter what $\alpha$ is set to. This can be seen by setting the left hand side of equ. \eqref{diff_hom_simpl_sweeney} to $0$ (which is necessarily the case in the steady state) and rearranging the equation:

\begin{equation}
(\alpha-1)\frac{\phi_i - \phi_0}{\phi_i} = \alpha \frac{\langle \phi \rangle - \phi_0}{\langle \phi \rangle}
\label{diff_hom_simpl_sweeney_3}
\end{equation}

The right term of the equation is the same for all neurons $i$. Since the left term is monotonic as a function of $\phi_i$, only one specific solution $\phi_i = \Phi$ for all $i$ exists that equals the given term on the right. Furthermore, this implies $\langle \phi \rangle = \Phi$. Thus,

\begin{equation}
(\alpha-1)\frac{\Phi - \phi_0}{\Phi} = \alpha \frac{\Phi - \phi_0}{\Phi}
\label{diff_hom_simpl_sweeney_2}
\end{equation}

which is only fulfilled for $\Phi = \phi_0$.

Moreover, one can argue that this result also implies a fixed distribution of thresholds in the steady state, independent of $\alpha$: Given the result above, one finds
\begin{align}
\phi(\mu_i(\nu),\sigma_i(\nu),\theta_i) &= \phi_0 \label{fixed_thresh_dist_argument1} \\
\mu_i &= J_iC_i \phi_0 \tau \label{fixed_thresh_dist_argument2} \\
\sigma_i &= J_i\sqrt{C_i \phi_0  \tau} \label{fixed_thresh_dist_argument3} \\
\rightarrow \theta_i &= {\phi}^{-1}(J_iC_i \phi_0 \tau,J_i\sqrt{C_i \phi_0  \tau},\phi_0) \label{fixed_thresh_dist_argument4}
\end{align}
which implies that $\theta_i$ only depends on the given network topology.

In \cite{Sweeney_Paper}, a non-interacting population of neurons was simulated while inputs where drawn randomly from a gaussian distribution supposed to model the input statistics of the full network.

To verify our remarks concerning the dynamic mean field model, we simulated a similar population, but used an interacting population of neurons of the same size as in the previous simulations (400 excitatory, 80 inhibitory neurons). This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $1500s$ (i.E., the "stable" phase).
Individual values for $\mu_i$ and $\sigma_i$ where then calculated according to \eqref{sweeney_self_consist_rate3} and \eqref{sweeney_self_consist_rate4}. Note however that in this case the mean (input) firing rate $\nu$ also takes different values $\nu_i$ for each neuron.

Instead of directly iterating through equations \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate4} (as done in \cite{Sweeney_Paper}) to fulfil self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation

\begin{equation}
\frac{dr_i}{dt} = \frac{1}{\tau_m} \left( -r_i + \phi_i(\mu_i(\nu),\sigma_i(\nu),\theta_i) \right)
\label{dyn_rate_equation}
\end{equation}

where $\tau_m$ is the membrane time constant.

Of course, equation \eqref{sweeney_self_consist_rate1} has to be rewritten accordingly:

\begin{equation}
\nu_i = {\langle r \rangle}_{presyn.,i} \equiv \frac{\sum_{\exists syn. j\rightarrow i} r_j}{N_{presyn., i}}
\label{sweeney_self_consist_rate1_mod}
\end{equation}

Fig. \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics for $\alpha=0.4$ and $\alpha = 0.8$. Both predictions can be confirmed: All rates approach the same target rate of $3Hz$ and, apparently, thresholds move toward the same state for either choice of $\alpha$. A significant difference only exists within the dynamics leading to the steady state. Roughly, a smaller value of $\alpha$ leads to a faster relaxation. Though, changes in the dynamics appear to be more subtle than a simple rescaling in the time domain.

\begin{figure}
\includegraphics[width=\textwidth]{../plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
\caption{Dynamics of rates and thresholds of excitatory population of 400 Neurons (see equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}). For both values of $\alpha$, rates and thresholds approach the same steady state.}
\label{dynamics_rate_threshold_dyn_mean_field_sweeney}
\end{figure}

\subsection{Equilibrium in the full diffusive Model}

Since the previous section has proven the simplified model in \cite{Sweeney_Paper} to be incapable of maintaining a broad distribution of firing rates, turning to a more general formulation of the problem seems reasonable, especially if it includes the possibility of the "exact" description of the initial model.

Equation \eqref{NO_dyn} describes the full dynamics of the diffusive neurotransmitter. Furthermore, equation \eqref{simple_NO_dyn} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $nNOS_i = C \cdot r_i$, $r_i$ representing a neuron's rate. Here we would like to discuss the implications of an "in-between" simplification, only applying the second one, but retaining the diffusive term:

\begin{equation}
\frac{dNO}{dt}(\mathbf{x},t) =-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot C \cdot r_i
\label{simple_NO_dyn_with_diff}
\end{equation}
As in the previous section, we ask for the steady-state distribution of rates. Thus as a first step, one needs to solve

\begin{equation}
(\lambda - D \nabla^2) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot C \cdot r_i
\label{simple_NO_dyn_with_diff_equil}
\end{equation}
for $\lbrace r_i\rbrace$, such that

\begin{equation}
NO(\mathbf{x}_{neur,i}) = NO_0 \:, \: \forall i
\label{NO_equil_cond}
\end{equation}
Equation \eqref{simple_NO_dyn_with_diff_equil} can be rewritten as

\begin{equation}
\left(\nabla^2 + \left( i\sqrt{\frac{\lambda}{D}}\right)^2\right) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot \frac{- C \cdot r_i}{D}
\label{simple_NO_dyn_with_diff_equil_helmholtz}
\end{equation}
Which is a two-dimensional Helmholtz equation with a superposition of (scaled) Dirac-functions. Thus, the solution of $NO$ is composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left of the equation. For each delta function $\delta^2(\mathbf{x}-\mathbf{x}_i)$, the solution is

\begin{equation}
NO_i(\mathbf{x}) = \frac{r_i C}{2 \pi D} K_0 \left(|\mathbf{x}-\mathbf{x}_{neur,i}|\sqrt{\frac{\lambda}{D}} \right)
\label{solution_diff_equil_bessel}
\end{equation}
where $K_0$ is the zeroth modified Bessel function of the second kind. This solution reveals a fundamental problem of modelling the sources of $NO$-production as point sources: that is to say, the fact that $K_0(x)$ diverges to infinity for $x\rightarrow 0$. It is merely due to the finite density of the numeric grid used for the simulation of the diffusion that allows for a finite target value of concentration. Note that this problem only occurs in the two- or three-dimensional version of the differential equation, whereas in one dimension, the fundamental solution can be expressed as an exponential function with respect to the distance to the origin, resulting in a well-defined finite value at $0$.

Generally speaking, no matter how the actual shape of the numeric solution in the equilibrium at a constant production rate will look like, it is expected to be of the form

\begin{align}
NO_i(\mathbf{x}) &= r_i \cdot \psi (d(\mathbf{x}_{neur,i},\mathbf{x})) \label{general_diff_interaction} \\
d(\mathbf{x},\mathbf{y}) &\equiv |\mathbf{x}-\mathbf{y}| \label{eucl_dist}
\end{align}
The full solution is then
\begin{equation}
NO(\mathbf{x}) = \sum_i NO_i(\mathbf{x})
\label{full_sol_diff_equil}
\end{equation}

If we define
\begin{equation}
\psi_{ij} = \psi_{ij} \equiv \psi (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i}))
\label{interact_matrix_elements}
\end{equation}
we can express the condition \eqref{NO_equil_cond} as
\begin{equation}
\sum_j \psi_{ij}\cdot r_j = NO_0
\label{NO_equil_cond_interact_matrix}
\end{equation}
or, as an operator
\begin{align}
\hat{\psi}\mathbf{r} &= NO_0 \mathbf{n} \label{NO_equil_cond_interact_matrix_operator} \\
\mathbf{n}&\equiv (1,1,...,1)
\end{align}

\bibliography{test_base}
\bibliographystyle{unsrt}
\end{document}

### 2016-07-18 test.tex
.

@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/diff_hom/rate_NO_th_compl.eps}
-\includegraphics[width=\textwidth]{../plots/diff_hom/rate_NO_th_closeup.eps}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/diff_hom/rate_NO_th_compl.eps}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/diff_hom/rate_NO_th_closeup.eps}
 \caption{Population activity, average $NO$ concentration (averaged over readouts at neurons' positions) and average firing threshold.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/firing_rate_dists/firing_rate_dist_compare.eps}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/firing_rate_dists/firing_rate_dist_compare.eps}
 \caption{Left: Simulation results by Sweeney et al.. Right: Simulation results for the SORN.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/diff_hom/threshold_dist_compare.eps}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/diff_hom/threshold_dist_compare.eps}
 \caption{Comparison of threshold distributions observed by Sweeney et al. (left) and in the SORN (right).}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/Spike_Stats/ISI_compare_SORN.eps}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/Spike_Stats/ISI_compare_SORN.eps}
 \caption{Top: log-plot of ISI-distribution of diff. and non-diff. homeostasis in the SORN. Bottom: CV-distribution for diff and non-diff. homeostasis.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/Spike_Stats/spike_sequence.eps}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/Spike_Stats/spike_sequence.eps}
 \caption{A spike sequence of 10 randomly picked excitatory neurons of the SORN. At $t=250s$, the homeostatic mechanism is switched to the diffusive variant.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/diff_hom/thresh_r_linfit.eps}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/diff_hom/thresh_r_linfit.eps}
 \caption{Linear fit of the relation between the firing threshold (averaged over population) and the population activity. $R^2=0.99996$.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/diff_hom/lin_model_osc.eps}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/diff_hom/lin_model_osc.eps}
 \caption{Simulation results for equations \eqref{simple_NO_dyn} and \eqref{simple_threshold_dyn}.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/power_spec/power_spectrum3}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/power_spec/power_spectrum3}
 \caption{Power Spectrum of the firing threshold and analytic result of equation \eqref{power_spec_thresh_r_g}.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
 \caption{Dynamics of rates and thresholds of excitatory population of 400 Neurons (see equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).
@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{/home/fschubert/Master/plots/diff_rate_solve.png}
+\end{figure}
+
 \bibliography{test_base}

### 2016-08-17 draft.tex
.

--- 2016-07-17 test.tex
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/diff_hom/rate_NO_th_compl.eps}
-\includegraphics[width=\textwidth]{../plots/diff_hom/rate_NO_th_closeup.eps}
+\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_compl.eps}
+\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_closeup.eps}
 \caption{Population activity, average $NO$ concentration (averaged over readouts at neurons' positions) and average firing threshold.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/firing_rate_dists/firing_rate_dist_compare.eps}
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/firing_rate_dist_compare.eps}
 \caption{Left: Simulation results by Sweeney et al.. Right: Simulation results for the SORN.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/diff_hom/threshold_dist_compare.eps}
+\includegraphics[width=\textwidth]{../../plots/diff_hom/threshold_dist_compare.eps}
 \caption{Comparison of threshold distributions observed by Sweeney et al. (left) and in the SORN (right).}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/Spike_Stats/ISI_compare_SORN.eps}
+\includegraphics[width=\textwidth]{../../plots/Spike_Stats/ISI_compare_SORN.eps}
 \caption{Top: log-plot of ISI-distribution of diff. and non-diff. homeostasis in the SORN. Bottom: CV-distribution for diff and non-diff. homeostasis.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/Spike_Stats/spike_sequence.eps}
+\includegraphics[width=\textwidth]{../../plots/Spike_Stats/spike_sequence.eps}
 \caption{A spike sequence of 10 randomly picked excitatory neurons of the SORN. At $t=250s$, the homeostatic mechanism is switched to the diffusive variant.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/diff_hom/thresh_r_linfit.eps}
+\includegraphics[width=\textwidth]{../../plots/diff_hom/thresh_r_linfit.eps}
 \caption{Linear fit of the relation between the firing threshold (averaged over population) and the population activity. $R^2=0.99996$.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/diff_hom/lin_model_osc.eps}
+\includegraphics[width=\textwidth]{../../plots/diff_hom/lin_model_osc.eps}
 \caption{Simulation results for equations \eqref{simple_NO_dyn} and \eqref{simple_threshold_dyn}.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/power_spec/power_spectrum3}
+\includegraphics[width=\textwidth]{../../plots/power_spec/power_spectrum3}
 \caption{Power Spectrum of the firing threshold and analytic result of equation \eqref{power_spec_thresh_r_g}.}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
+\includegraphics[width=\textwidth]{../../plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
 \caption{Dynamics of rates and thresholds of excitatory population of 400 Neurons (see equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).
@@
 \end{align}
+The problem of finding the steady-state solution of the homeostatic constraint thus reduces to inverting $\hat{\psi}$:
+\begin{equation}
+\mathbf{r} = NO_0 \hat{\psi}^{-1} \mathbf{n}
+\label{NO_euqil_cond_interact_matrix_operator_solve}
+\end{equation}
+
+An example of a distribution of rates acquired from this method is shown in fig. \ref{rate_dist_interact_matrix}.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/diff_rate_solve.png}
+\caption{Distribution of the solution of \eqref{NO_euqil_cond_interact_matrix_operator_solve} with an exponential distance dependent approximation in 2d (similar to the exact solution in 1d).
+For better statistical significance, calculations where carried out for $1600$ random neurons-positions and $50$ trials in total.}
+\label{rate_dist_interact_matrix}
+\end{figure}
+
+\subsubsection{Results for an Approximation of the Numerical Steady-State Solution}
+
+If one aims for an appropriate expression for the numerical steady-state solution of a single "point"-source with a constant influx, two things should be of importance: first, it should correctly predict the concentration at the location of the source and second, it should be close to the analytic result in regions further away from the source.
+One possibility is to use the following "trick" to overcome the divergence of the analytic solution at the origin:
+
+\begin{equation}
+NO_{approx.}(r) = \frac{1}{\sqrt{\frac{1}{NO_{source,num.}^2} + \frac{1}{NO(r)^2}}}
+\label{Numeric_Solution_Expression_Trick}
+\end{equation}
+
+At the pole $NO(0)$, $NO_{approx.}(0)$ then takes the value $NO_{source,num.}$.
+On the other hand, for larger values of $r$, the term $\frac{1}{NO_{source,num.}^2}$ becomes negligible compared to $ \frac{1}{NO(r)^2}$, thus $NO_{approx.}(r) \rightarrow NO(r)$ for $r \rightarrow \infty$.
+
+To find an approximation for $NO_{source,num.}$, one can interpret this value as a mean of the analytic solution across the square area covered by the corresponding grid cell.
+As an additional simplification, we substitute the necessary integration over the square grid cell by a circular area of equal size around the source.
+This calculation yields
+
+\begin{equation}
+NO_{source,num.} = \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda}
+\end{equation}
+
+\subsubsection{Mean-Field approximation for the Variance of Firing Rates}
+
+Generally, Mean-Field approximations reduce the calculation of a full set of interacting entities (or particles, in the context of physics) to a single instance interacting with an effective mean of the entire field, especially ignoring the influence of the single instance onto the whole set of entities and thus the field itself.
+
+In the system presented here, a single neuron with a firing rate $\nu$ must fulfil the equation
+
+\begin{equation}
+\nu =\frac{NO_0 - \sum \limits_{i} \nu_i \psi(d_i)}{\psi_0}
+\label{sample_neuron_firing_rate}
+\end{equation}
+
+where $i$ indexes over all "remaining" neurons and $d_i$ refers to the euclidean distance of the sample neuron to "field"-neuron $i$.
+$\psi_0$ is the factor that - multiplied with $\nu$ - yields the $NO$-concentration at the origin of the sample neuron.
+
+Depending on the constraints that one imposes onto the system, one might look for different properties to be extracted from this equation.
+Specifically, in the simulation protocol that has been used in all previous simulations, the average firing rate was forced to a certain value by means of adjusting the target concentration $NO_0$.
+A Mean-Field approximation for the average firing rate therefore is of no relevance in this particular case.
+
+However, one might try to give an estimate for the variance of the firing rate distribution in dependence of the diffusion constant $D$.
+Interpreting $\nu$ in \eqref{sample_neuron_firing_rate} as a stochastic variable, one finds
+
+\begin{equation}
+Var[\nu] = \frac{Var[\sum \limits_{i} \nu_i \psi(d_i)]}{\psi_0^2}
+\label{variance_sample_neuron_firing_rate}
+\end{equation}
 

### 2016-09-12 draft.tex
.

@@
 NO_{source,num.} = \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda}
+\label{Numeric_Grid_Bessel_Approx}
 \end{equation}
 
-\subsubsection{Mean-Field approximation for the Variance of Firing Rates}
+\subsubsection{Comparison of the Solution of the Random Matrix Equation and the Simulation of the Spiking Network}
+
+\eqref{Numeric_Solution_Expression_Trick} and \eqref{Numeric_Grid_Bessel_Approx} can be used in \eqref{NO_euqil_cond_interact_matrix_operator_solve} for a more accurate description of the distance-dependent diffusive interaction.
+
+In addition, one needs to account for the boundary conditions used in the network simulation.
+We simulated the network with Von-Neumann boundary conditions (setting the flux through the boundary to zero) as well as periodic boundaries.
+Both types can be modelled by extending the neurons' population through spatially shifted and mirrored versions of the base population:
+
+\begin{itemize}
+\item Periodic boundary conditions are induced by copies of the neurons' positions shifted by $L\cdot (n_x,n_y)$, $n_x,n_y \in \mathbb{Z}$.
+\item Zero flux through the boundaries can be achieved by copied positions being shifted by $L\cdot (n_x,n_y)$, $n_x,n_y \in \mathbb{Z}$ \textit{and} mirrored in $x$($y$)-direction if $n_x$($n_y$) is odd.
+\end{itemize}
+
+\subsubsection{Mean-Field Approximation for the Variance of Firing Rates}
 
@@
 
+As an approximation, one can now replace all $\nu_i$ by the mean activity, which has been forced to a certain value $\nu_0$:
+
+\begin{equation}
+Var[\nu] = \frac{\nu_0^2 \cdot Var[\sum \limits_{i} \psi(d_i)]}{\psi_0^2}
+\label{variance_sample_neuron_firing_rate_mean_act}
+\end{equation}
+
+The random individual neurons' positions are statistically independent, therefore one gets
+
+\begin{equation}
+Var[\nu] = \frac{\nu_0^2 \cdot N \cdot Var[\psi(d)]}{\psi_0^2}
+\label{variance_sample_neuron_firing_rate_mean_act_indep_positions}
+\end{equation}
+where $N$ is the number of neurons.
+One should note however that this expression only applies to the case of open boundaries.
+Furthermore, depending on the position of the "sample neuron" relative to the population, one can achieve different statistics for $\psi(d)$.
+The limit case, in which both remarks are of no relevance, is a population of a certain density spreading across a tissue of infinite size.
+
 \bibliography{test_base}

### 2016-09-12 draft.tex
.

@@
 \begin{equation}
-NO_{approx.}(r) = \frac{1}{\sqrt{\frac{1}{NO_{source,num.}^2} + \frac{1}{NO(r)^2}}}
+NO_{approx.}(d) = \frac{1}{\sqrt{\frac{1}{NO_{source,num.}^2} + \frac{1}{NO(d)^2}}}
 \label{Numeric_Solution_Expression_Trick}
@@
 At the pole $NO(0)$, $NO_{approx.}(0)$ then takes the value $NO_{source,num.}$.
-On the other hand, for larger values of $r$, the term $\frac{1}{NO_{source,num.}^2}$ becomes negligible compared to $ \frac{1}{NO(r)^2}$, thus $NO_{approx.}(r) \rightarrow NO(r)$ for $r \rightarrow \infty$.
+On the other hand, for larger values of $r$, the term $\frac{1}{NO_{source,num.}^2}$ becomes negligible compared to $ \frac{1}{NO(d)^2}$, thus $NO_{approx.}(d) \rightarrow NO(d)$ for $d \rightarrow \infty$.
 
@@
 \begin{equation}
-NO_{source,num.} = \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda}
+NO_{source,num.} =  r \cdot \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda} \equiv r \cdot \psi_{source,num.}
 \label{Numeric_Grid_Bessel_Approx}
+\end{equation}
+with $r$ being the neuron's rate. Equivalently, one can then define
+\begin{equation}
+\psi_{approx.}(d) \equiv \frac{1}{\sqrt{\frac{1}{\psi_{source,num.}^2} + \frac{1}{\psi (d)^2}}}
 \end{equation}
@@
 In addition, one needs to account for the boundary conditions used in the network simulation.
-We simulated the network with Von-Neumann boundary conditions (setting the flux through the boundary to zero) as well as periodic boundaries.
-Both types can be modelled by extending the neurons' population through spatially shifted and mirrored versions of the base population:
+We simulated the network with Neumann boundary conditions (setting the flux through the boundary to zero) as well as periodic boundaries.
+Both types can be modelled by extending the neurons' population through spatially shifted and mirrored versions of the base population (see Figure \ref{Bound_Cond_Patches}):
 
@@
 \end{itemize}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{../../plots/Boundary_Cond_Sketch.png}
+\end{center}
+\caption{Sketch for patches of copied (and mirrored) positions for periodic (A) and Neumann (B) boundary conditions.}
+\label{Bound_Cond_Patches}
+\end{figure}
+
+The entries of the operator for periodic boundary conditions $\hat{\psi}_{per.}$ can now calculated by
+\begin{equation}
+\psi_{ij,per.} = \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i} + L \cdot (n_x,n_y)))
+\label{Psi_entries_periodic_bound}
+\end{equation}
+Note that the shift was applied to the second position.
+Theoretically, $n_x$,$n_y$ is iterated over all integers and in this case it is irrelevant whether to shift the first or the second position.
+For numerical calculations however, the shift was applied to the second position.
+
+For the Neumann boundary condition, one finds
+\begin{align}
+\psi_{ij,neum.} &= \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} \left( d(\mathbf{x}_{neur,i},M(\mathbf{x}_{neur,i}) + L \cdot (n_x,n_y)) \right) \label{Psi_entries_neumann_bound} \\
+M(\mathbf{x}) &\equiv  
+ \begin{pmatrix}
+  (-1)^{n_x} & 0\\
+  0 & (-1)^{n_y}
+ \end{pmatrix}
+\mathbf{x} + L \cdot (mod(\left| n_x\right|,2),mod(\left| n_y\right|,2)) \label{Mirror_Operator}
+\end{align}
+
+We compared the firing rate distributions acquired from the solution of the random matrix system and those of the full simulated network by means of its standard deviation and skewness.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/frequ_moments_compare.png}
+\caption{Standard deviation and skewness of firing rate distributions for the full spiking network (blue) and the solution of the random matrix model (orange) for Neumann (A,B) and periodic (C,D) boundary conditions.}
+\label{frequ_moments_compare}
+\end{figure}
 

### 2016-09-14 draft.tex
.

@@
 We compared the firing rate distributions acquired from the solution of the random matrix system and those of the full simulated network by means of its standard deviation and skewness.
-
 \begin{figure}
@@
 \end{figure}
+While the standard deviation appears to be better fitting the full network in the case of Neumann boundary conditions, the prediction of skewness is more accurate for periodic boundaries.
+In both versions, the standard deviation seems to be underestimated by the solution of the random matrix equation.
+This seems reasonable, considering the fact that a network of irregularly spiking neurons "naturally" provides a certain amount of firing rate variability and that during simulation, all plasticity mechanisms where kept in place (changes of presynaptic weights requires an adjustment of the internal threshold to maintain the desired firing rate).
 
@@
 \end{equation}
-
 where $i$ indexes over all "remaining" neurons and $d_i$ refers to the euclidean distance of the sample neuron to "field"-neuron $i$.

### 2016-10-10 abstract.tex
.

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{cite}
\usepackage{hyperref}
\title{Diffusive Homeostasis in a Recurrent Neural Network \\
\begin{large}
Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity
\end{large}
}

\begin{document}
\maketitle
\section{Abstract} \label{abstract}
Based on the LIF-SORN-model proposed in \cite{SORN_Paper}, we attempt to replace the intrinsic homeostatic control system used in the original version by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue. The model of diffusive homeostasis is adopted from a paper by Y. Sweeney et al. \cite{Sweeney_Paper} and models the tissue as a surface of square shape and a set of points on this surface, representing the positions of the neurons within the SORN. Excitatory neurons then act as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position. The production and sensing of NO forms the basis of a feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate. The control system is then closed by linking the rate of NO-production to the neuron's firing rate.

Key aspects of this thesis include an analysis of the stability of the homeostatic control, followed by a comparison of features of the original LIF-SORN and the diffusive variant. We expect to observe a preservation of non-random structural features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity (as reported by \cite{Sweeney_Paper}) which has previously been suppressed by a rigid single-cell homeostasis. In the face of possible \emph{new} features within the network's structure, we further clarify the - presumably indirect - causal relation between diffusive spatial interaction and synaptic topology.

\bibliography{test_base}
\bibliographystyle{unsrt}
\end{document}

### 2016-10-10 draft.tex
.

@@
 \usepackage{hyperref}
+\usepackage{caption}
+\captionsetup[table]{singlelinecheck=false}
+\title{Diffusive Homeostasis in a Recurrent Neural Network \\
+\begin{large}
+Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity
+\end{large}
+}
 
 \begin{document}
+\maketitle
+
 \section{Abstract} \label{abstract}
-Building on the LIF-SORN-model proposed in \cite{SORN_Paper}, we attempted to replace the intrinsic homeostatic control system used in the original version by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
+Based on the LIF-SORN-model proposed in \cite{SORN_Paper}, we attempted to replace the intrinsic homeostatic control system used in the original version by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
 The model of diffusive homeostasis was adopted from a paper by Y.
 Sweeney et al.
-\cite{Sweeney_Paper} and models the tissue as a surface of square shape and a set of points on this surface, representing the positions of the neurons within the SORN.
+\cite{Sweeney_Paper} and models the tissue as a surface of square shape and a set of points on this surface, representing the neurons' positions within the SORN.
 The group of excitatory neurons then acted as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position.
-The production and sensing of NO forms the basis of an intrinsic feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate.
+The production and sensing of NO forms the basis of a feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate.
 The control system is then closed by linking the rate of NO-production to the neuron's firing rate.
 
-It should be mentioned that \cite{Sweeney_Paper} included all neurons into the homeostatic control.
-However, since we excluded inhibitory neurons from the original homeostatic control, we held this decision in the new model.
+Key aspects of this thesis include an analysis of the stability of the homeostatic control, followed by a comparison of features of the original LIF-SORN and the Diffusive variant.
+We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity (as reported by \cite{Sweeney_Paper}) which has previously been suppressed by a rigid single-cell homeostasis.
+In the face of possible \emph{new} features within the network's structure, one should further clarify the - presumably indirect - causal relation between diffusive spatial interaction and synaptic topology.
 
 \section{Methods} \label{methods}
-Network dynamics remained the same as in \cite{SORN_Paper}.
+\subsection{Network Simulation}
+
+The Neural Network was simulated with the code used in \cite{SORN_Paper}, which makes use of the BRIAN spiking neural network simulator \cite{Briansim}.
+Thus, all following explanations regarding the simulation of neurons and mechanisms of synaptic plasticity are based on the methods described in the aforementioned paper.
+
+Across a square area of 1000 $\times$ 1000 $\mu m$, 400 excitatory LIF neurons and 80 inhibitory LIF neurons where assigned random positions.
+Before the start of the simulation, all but recurrent excitatory synapses where randomly generated until a desired connection fraction was reached.
+The connection probability between two neurons was calculated from a distant dependent Gaussian function with a standard deviation of 200 $\mu m$.
+For exc.
+to inh.
+(EI) and inh.
+to exc.
+(IE) synapses, the connection fraction was set to 0.1, and 0.5 for recurrent inh.
+synapses (II).
+These connections where kept at a fixed connection strength throughout the simulation.
+Furthermore, all synapses where simulated with a fixed (distance independent) conduction delay.
+See table \ref{syn_conn_params} for a summary of parameters.
+
+Recurrent excitatory synapses where subject to a number of plastic mechanisms to be described in the following.
+
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+\textbf{parameter} & \textbf{EE} & \textbf{EI} & \textbf{IE} & \textbf{II} \\ \hline
+connection fraction & $\rightarrow 0.1$ & $0.1$ & $0.1$ & $0.5$ \\ \hline
+initial connection strength & $0.0001 mV$ & $1.5 mV$ & $-1.5 mV$ & $-1.5 mV$ \\ \hline
+conduction delay & $1.5 ms$ & $0.5 ms$ & $1.0 ms$ & $1.0 ms$ \\
+\hline
+\end{tabular}
+\caption{Parameters of synaptic connections.}
+\label{syn_conn_params}
+\end{table}
+
+\subsubsection{Synaptic Plasticity}
+
+\textbf{Synaptic Growth:} At a rate of 1/sec, the random, distance dependent generation of new EE synapses was carried out n times, where n is taken from a normal distribution with mean 920 and standard deviation $\sqrt{920}$.
+This constant growth rate was tuned to achieve the desired target concentration of 0.1 (see \ref{syn_conn_params}).
+
+\textbf{Synaptic Pruning:} At the same rate of 1/sec, EE synapses below a threshold of 0.000001 mV where removed, thus being added again to the set of "potential" connections from which the growth process draws new connections.
+Especially, they were temporarily excluded from STDP (see below).
+
+\textbf{Spike Timing Dependent Plasticity:} An additive STDP rule was used as described e.g.
+in \cite{Zhang_STDP}.
+The change of weight between two neurons due to a pre- and postsynaptic spike (i $\rightarrow$ j) is defined as:
+\begin{align}
+\Delta w_{ji} &= \sum_k \sum_l W(t_j^l - t_i^k) \label{STDP_rule} \\
+W(\Delta t) &= A_{+} exp(-\Delta t / \tau_{+}), & \Delta t > 0 \label{STDP_pos} \\
+W(\Delta t) &= A_{-} exp(\Delta t / \tau_{-}), & \Delta t < 0 \label{STDP_neg}
+\end{align}
+Indexes k and l refer to the kth and lth pre- and postsynaptic spike respectively.
+Parameters where chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
+However, for the sake of reduction of computational effort, we used the "nearest neighbor" approximation, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
+
+\textbf{Synaptic Normalization:} Among other, experiments have suggested rescaling of synapses among individual postsynaptic neurons as a form of activity regulation in the brain: While preserving ratios of weights, the mean incoming connectivity is multiplicatively adjusted.
+While this general mechanism has been confirmed in many experiments, results differ regarding the question whether the target connectivity is dynamically changing in order to preserve a certain postsynaptic firing rate (homeostatic synaptic scaling), or whether it remains constant, effectively enforcing a synaptic normalization.
+Though the latter does not directly enforce a fixed level of activity, one can argue that in a balanced recurrent network, synaptic normalization still reduces the probability of very high or low firing rates caused by an above- or below-average total synaptic input.
+
+We implemented synaptic normalization by calling a function once per sec., updating each $w_{ji}$ from neuron $i$ to neuron $j$ as follows:
+
+\begin{equation}
+w_{ji} \rightarrow w_{ji} \frac{w_{total}}{\sum_i w_{ji}}
+\label{Synnnorm}
+\end{equation}
+
+$w_{total}$ was set to different values for each of the four types of connections between the excitatory and inhibitory pool of neurons.
+Except for the dynamically populated EE-synapses, these values could be directly set in accordance with the previously given parameters of desired mean individual connection strength, size of the presynaptic population and connection fraction, by calculating $w_{total} = w_{mean} \cdot N_{presyn.
+pop}\cdot p_{connect}$.
+This yielded $w_{total,EI} = 60 mV$, $w_{total,IE} = -12 mV$, $w_{total,II} = -60 mV$.
+$w_{total,EE}$ was set to $40mV$,  corresponding to a mean synaptic weight of $1mV$, given a targeted EE-connection fraction of $0.1$ and a population of 400 excitatory neurons.
+
+\textbf{Short Term Plasticity:} As an additional stabilization of network activity, a short term plasticity (STP) mechanism acting on recurrent excitatory connections was implemented as presented in \cite{Markram_STP}.
+It modulates the effective synaptic weights by multiplying the value stored in the weight matrix $w_{ji}$ by two dynamic variables $x$ and $u$, $w^{effective}_{ji} = w_{ji}\cdot x \cdot u$, each synapse owning a pair $(x,u)$.
+The dynamics of these variables are given by:
+
+\begin{equation}
+\dot{x} = \frac{1-x}{\tau_d},\; \dot{u} = \frac{U-u}{\tau_f}
+\label{STP_dynamics1}
+\end{equation}
+Furthermore, each presynaptic spike causes a change of $x$ and $u$ by
+\begin{equation}
+x \rightarrow x - x\cdot u,\; u \rightarrow u + U(1-u)
+\label{STP_dynamics2}
+\end{equation}
+
+If no spikes arrive, the system rests at $x\cdot u = U$.
+Otherwise, depending on the choice of $\tau_d$ and $\tau_f$, one can achieve a weight modulation that is dominated by potentiation ($\tau_f \gg \tau_d$) or depression ($\tau_f \ll \tau_d$).
+As a rough approximation of the values that where experimentally observed \cite{Markram_STP}, we chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$, giving it a tendency towards potentiation.
+However, one should keep in mind that for $U\in [0,1]$, $x\cdot u \in [0,1]$ always holds, thus the factor $x\cdot u$ has a generally diminishing effect.
+E.g., for our choice of variables, a poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim 4.5 Hz$, corresponding to $x\cdot u \approx 0.2$.
+"Potentiation" in this context refers to the fact that stronger input strengthens synaptic transmission \emph{compared} to close to zero incoming spikes.
+
+\subsubsection{Neuron Model}
+
+We used a leaky integrate-and-fire-model for all neurons in the network, whose dynamics are described by a stochastic differential equation:
+\begin{equation}
+dV = -\frac{V-E_l}{\tau_m}dt + \frac{\sigma}{\sqrt{\tau_m}}dW
+\end{equation}
+where $V$ is the membrane potential, $E_l$ is the equilibrium membrane potential, $\tau_m$ is the time constant of the membrane, $\sigma$ is the standard deviation of the noise term and $dW$ is the standard Wiener process.
+A neuron is said to spike when its membrane potential reaches the threshold voltage $V_t$.
+The voltage is then reset to $V_r$.
+A refractory period was not implemented.
+A presynaptic spike causes a simple (delayed, see Table \ref{syn_conn_params}) increment of the membrane potential of the postsynaptic neuron by $w^{effective}_{ji}$.
+Table \ref{LIF_neuron_params} summarizes the aforementioned set of parameters.
+\begin{table}
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{parameter} & \textbf{exc. neur.} & \textbf{inh. neur.}\\ \hline
+$E_l$ & $-60 mV$ & $-60 mV$ \\ \hline
+$\tau_m$ & $20 ms$ & $20 ms$ \\ \hline
+$V_r$ & $-70 mV$ & $-60 mV$ \\ \hline
+$\sigma$ & $\sqrt{5} mV$ & $\sqrt{5} mV$ \\ \hline
+$V_t$ & subject to IP & $-58 mV$ \\ 
+\hline
+\end{tabular}
+\caption{Parameters of LIF neuron}
+\label{LIF_neuron_params}
+\end{table}
+
+\subsubsection{Intrinsic Plasticity}
+
+\subsection{Simulation of Homeostasis}
 

### 2016-10-13 draft.tex
.

@@
 \captionsetup[table]{singlelinecheck=false}
-\title{Diffusive Homeostasis in a Recurrent Neural Network \\
+\captionsetup[figure]{singlelinecheck=false}
+\title{Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\
 \begin{large}
@@
 \textbf{parameter} & \textbf{exc. neur.} & \textbf{inh. neur.}\\ \hline
-$E_l$ & $-60 mV$ & $-60 mV$ \\ \hline
-$\tau_m$ & $20 ms$ & $20 ms$ \\ \hline
-$V_r$ & $-70 mV$ & $-60 mV$ \\ \hline
-$\sigma$ & $\sqrt{5} mV$ & $\sqrt{5} mV$ \\ \hline
-$V_t$ & subject to IP & $-58 mV$ \\ 
+$\mathrm{E_l}$ & $\mathrm{-60\;mV}$ & $\mathrm{-60\;mV}$ \\ \hline
+$\mathrm{\tau_m}$ & $\mathrm{20\;ms}$ & $\mathrm{20\;ms}$ \\ \hline
+$\mathrm{V_r}$ & $\mathrm{-70\;mV}$ & $\mathrm{-60\;mV}$ \\ \hline
+$\mathrm{\sigma}$ & $\mathrm{\sqrt{5}\;mV}$ & $\mathrm{\sqrt{5}\;mV}$ \\ \hline
+$\mathrm{V_t}$ & subject to IP & $\mathrm{-58\;mV}$ \\ 
 \hline
@@
 
-\subsubsection{Intrinsic Plasticity}
+\subsubsection{Intrinsic Plasticity (IP)}
 
-\subsection{Simulation of Homeostasis}
+Apart from dynamic processes within synapses which contribute to a stabilization of the network's activity, neurons possess internal mechanisms capable of maintaining a desired regime of activity.
+Regular-spiking cells are known to down-(up-)regulate their firing rate upon increased (decreased) input on a timescale of tens of milliseconds \cite{Connors_Gutnick_Spike_Patterns,Benda_Herz_Spike_Frequ_Adaption}.
+Since our simulation did not incorporate any rapidly changing external drive, the network itself was not expected to exhibit fast changes of synaptic input, allowing us to neglect this feature.
+On the other hand, a similar form of adaption as a reaction on deprived or enhanced input can be observed on a timescale of hours to days \cite{Desai_IP}.
+In contrast to the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252-256]{Izhikevich_Dynsys}, in the latter case, \cite{Desai_IP} finds evidence that a long-term change in excitability can be attributed to an altered resistance of ionic channels.
 
-The original homeostatic control was described as an operation over discrete time steps $\Delta t$, carried out for each excitatory neuron:
+In the original LIF-SORN, a simple form of low intrinsic homeostasis was implemented by altering the neurons' firing threshold based on the deviation from a target firing rate.
+This thesis implemented a new model of slow intrinsic homeostasis, based on the work in \cite{Sweeney_Paper}.
+The following section describes both models in further detail.
+
+\subsubsection{Modelling of Homeostatic Intrinsic Plasticity}
+
+Our original model of homeostatic control was described as an operation over discrete time steps $\Delta t = 0.1ms$, carried out for each excitatory neuron:
 
 \begin{align}
-V_T &\rightarrow V_T + \eta_{IP} (N_{spikes} - h_{IP}) \label{can_hom_1}\\
+V_t &\rightarrow V_t + \eta_{IP} (N_{spikes} - h_{IP}) \label{can_hom_1}\\
 N_{spikes} &\rightarrow 0 \label{can_hom_2}
 \end{align}
-
-where $V_T$ is the firing threshold, $\eta_{IP}$ an adaption rate and $h_{IP}$ the desired number of spikes per time step.
-$N_{spikes}$ is a variable, counting the number of spikes of a the neuron within each interval.
-In a continuous, rate-based form, this update rule can be written as:
+where $V_t$ is the firing threshold, $\eta_{IP}$ an adaption rate and $h_{IP}$ the desired number of spikes per time step.
+$N_{spikes}$ is a variable, counting the number of spikes of the neuron within each interval.
+In a continuous, rate-based form, this update rule can as well be written as:
 
 \begin{equation}
-\dot{V}_T = \eta_{IP}(r-r_{IP}) \label{can_hom_rate}
+\dot{V}_t = \eta_{IP}(r-r_{IP}) \label{can_hom_rate}
 \end{equation}
+with $r$ as the neuron's firing rate and $r_{IP}=h_{IP}/\Delta t$ the target firing rate.
+This feedback control indirectly drives the firing rate of each neuron towards $r_{IP}$: If $r>(<)r_{IP}$, $V_t$ increases (decreases), reducing (increasing) the probability of a spike to occur.
 
-with $r$ as the neurons momentary firing rate and $r_{IP}=h_{IP}/\Delta t$ the target firing rate.
+The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of nitric oxide (NO).
+Enzymes that are responsible for NO synthase (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS) , the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
+These Enzymes differ in their functionality and dependence on the presence of other molecules.
+In particular, nNOS is sensitive to the concentration of $Ca^{2+}$ ionic Calcium \cite{Knowles_Ca_nNOS}.
 
-This feedback control includes no interaction among neurons.
-The model presented in \cite{Sweeney_Paper} includes spacial interaction through a diffusive term.
-It is described by the following equations.
+Due to a depolarization of the membrane potential in the course of an action potential, voltage dependent $Ca^{2+}$-channels open, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98-100]{Hille_Ion_Channels}.
+A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445-451]{Hille_Ion_Channels}.
+As such, $Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
+
+On the other hand, experimental studies have suggested that NO can act as a diffusive signalling pathway, decreasing intrinsic excitability \cite{Steinert_NO}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
+
+Sweeney et al. combined these empirical findings into a model of \emph{diffusive homeostasis}, which is governed by the following equations:
 
 \begin{align}
-\frac{dCa^{2+}_i}{dt}(t) &= -\frac{Ca^{2+}_i}{\tau_{Ca^{2+}}} + Ca^{2+}_{spike} \sum_{t_{spike}} \delta(t-t_{spike}) \label{Ca_dyn}\\
-\frac{dnNOS_i}{dt}(t) &= \frac{1}{\tau_{nNOS}} \left(  \frac{{Ca^{2+}_i}^3}{{Ca^{2+}_i}^3+1} - nNOS_i \right) \label{nNOS_dyn}\\
-\frac{dNO}{dt}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{neur,i})\cdot nNOS_i \label{NO_dyn}\\
-\frac{d\theta_i}{dt}(t) &= \frac{NO(\mathbf{r}_{neur,i},t)-NO_0}{NO_0\cdot\tau_{\theta}} \label{Theta_dyn}
+\dot{{Ca^{2+}}^i}(t) &= -\frac{{Ca^{2+}}^i}{\tau_{Ca^{2+}}} + Ca^{2+}_{spike} \sum_{j} \delta(t-t^i_{spike,j}) \label{Ca_dyn}\\
+\dot{nNOS^i}(t) &= \frac{1}{\tau_{nNOS}} \left(  \frac{{{Ca^{2+}}^i}^3}{{{Ca^{2+}}^i}^3+1} - nNOS^i \right) \label{nNOS_dyn}\\
+\dot{NO}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{neur}^i)\cdot nNOS^i \label{NO_dyn}\\
+\dot{V_t^i}(t) &= \frac{NO(\mathbf{r}_{neur}^i,t)-NO_0}{NO_0\cdot\tau_{V_t}} \label{Theta_dyn}
 \end{align}
 
-A depolarization within the cell causes an inflow of $Ca^{2+}$ ions, which is modelled as an instantaneous increase of the $Ca^{2+}$ concentration.
+A depolarization within a nerve cell upon a spike-event $t_{spike}$ causes a fixed inflow of ionic current $Ca^{2+}_{spike}$, which is modelled as an instantaneous increase of the $Ca^{2+}$ concentration.
 Over time, the concentration decays exponentially by a time constant $\tau_{Ca^{2+}}$, see \eqref{Ca_dyn}.
 Though $Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198-203]{Theor_Neur_Dayan}.
-It has been experimentally observed that the intracellular $Ca^{2+}$ concentration influences neuronal Nitric oxide synthase \cite{Bredt_Snyder_NO}.
-This was modelled by Sweeney et al.
+The aforementioned influence of $Ca^{2+}$ onto nNOS was modelled by Sweeney et al.
 through \eqref{nNOS_dyn}, using the Hill equation \cite{Hill_Equ} to model a cooperative binding mechanism.
-The $nNOS$ production is then fed into the "pool" of nitric oxide via point sources located at the neurons' positions \eqref{NO_dyn}.
-An additional decay term was added to provide a stable $NO$ concentration under constant neuronal activity.
+The $nNOS$ production is then fed into the "pool" of nitric oxide via point sources located at the neurons' positions.
+Apart from the inflow and the diffusive term $D \nabla^2 NO$, an additional decay term was added to provide a stable finite $NO$ concentration under constant neuronal activity.
 
-Finally, the dynamics of the firing thresholds $\theta_i$ were modelled such that the rate of change is proportional to the relative deviation of the $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
+Finally, the dynamics of the firing thresholds $V_t^i$ were modelled such that the rate of change is proportional to the relative deviation of the $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
 
-Obviously, the appropriate choice of $NO_0$ is crucial for the goal of achieving and maintaining certain level of activity.
+Obviously, the appropriate choice of $NO_0$ is crucial for the goal of achieving and maintaining a certain level of activity.
 However, one cannot directly set a parameter of the model to the desired population activity, as it was the case for canonical intrinsic homeostasis.
 Rather, one needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration.
-Though it is possible to derive this relation in an analytic fashion, for practical purposes of the simulation, we let the system run with the previous homeostatic mechanism until a steady concentration level was reached.
-This level was then set to be the target concentration and we switched to diffusive homeostasis.
+Though it is possible to derive this relation in an analytic fashion, for practical purposes of the simulation, we let the system run with the previous homeostatic mechanism, still solving equation \eqref{Ca_dyn}-\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
+This mean was then set to be the target concentration and we switched to diffusive homeostasis.
+Table \ref{Params_IP} summarizes the choice of parameters that where introduced in this section.
+\begin{table}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{parameter} & \textbf{value} \\
+\hline
+$\mathrm{r_{IP}}$ & $\mathrm{3\;Hz}$ \\
+\hline
+$\mathrm{\eta_{IP}}$ & $\mathrm{0.1\;mV}$ \\
+\hline
+$\mathrm{Ca^{2+}_{spike}}$ & 1 \\ \hline
+$\mathrm{\tau_{Ca^{2+}}}$ &  $\mathrm{10\;ms}$ \\
+\hline
+$\mathrm{\tau_{nNOS}}$ & $\mathrm{100\;ms}$ \\
+\hline
+$\mathrm{D}$ & default: 12500 $\mathrm{\mu m^2 s^{-1}}$ \\
+\hline 
+$\mathrm{\lambda}$ & $\mathrm{0.1\;s^{-1}}$ \\
+\hline
+$\mathrm{\tau_{V_t}}$ & see section ?? \\
+\hline
+\end{tabular}
+\caption{Parameters of homeostatic intrinsic plasticity.}
+\label{Params_IP}
+\end{table}
+
+\subsection{Simulation of Diffusion}
+
+We solved \eqref{NO_dyn} with the finite difference method on a grid with a resolution of $100\times 100$ points.
+Integration over time was carried out by a 4th-order Runge-Kutta method with a time step of $1 ms$.
+On each time step, $\nabla^2 NO(\mathbf{r})$ was approximated by
+\begin{equation}
+\nabla^2 NO(\mathbf{r}_{i,j}) \approx \frac{NO_{i+1,j}+NO_{i-1,j}+NO_{i,j+1}+NO_{i,j-1}-4NO_{i,j}}{h^2}
+\label{Laplace_Numeric}
+\end{equation}
+where $h = L/100$ is the distance between neighboured grid points, determined by the length $L$ of the square sheet and the resolution of the numeric grid.
+We implemented three possible boundary conditions into the simulation:
+
+1.) Periodic boundary conditions:
+\begin{align}
+NO_{i,N+1} &= NO_{i,0} \label{Periodic_Cond_1} \\
+NO_{N+1,i} &= NO_{0,i} \label{Periodic_Cond_2} \\
+NO_{i,-1} &= NO_{i,N} \label{Periodic_Cond_3} \\
+NO_{-1,i} &= NO_{N,i} \label{Periodic_Cond_4}
+\end{align}
+with $N$ being the grid resolution.
+
+2.) Neumann boundary conditions, with $\nabla NO = (0,0)$ at the boundaries:
+\begin{align}
+NO_{i,N+1} &= NO_{i,N-1} \label{Neumann_Cond_1} \\
+NO_{N+1,i} &= NO_{N-1,i} \label{Neumann_Cond_2} \\
+NO_{i,-1} &= NO_{i,1} \label{Neumann_Cond_3} \\
+NO_{-1,i} &= NO_{1,i} \label{Neumann_Cond_4}
+\end{align}
+
+3.) Dirichlet boundary conditions, with $NO = NO_{bound}$ at the boundaries.
+
+If not explicitly marked differently, Neumann boundary conditions where used for most of the simulations.
+This decision relates to the previously described mechanism of synaptic growth: Neurons placed close to the edge of the sheet have a lower connection probability due to the absence of neighbouring neurons in the direction perpendicular to the close-by border.
+It therefore models the synaptic growth within a square "cutout" of neural tissue.
+The Neumann boundary condition fits into this picture, since it allows a zero-flux condition at the borders.
+This is a reasonable assumption, because NO molecules cannot diffuse out of the tissue (unless they were placed in a fluid surrounding).
+
+Equation \eqref{NO_dyn} describes the influx of NO as a sum of scaled and spatially shifted Dirac functions.
+Apart from the question, whether this source term results in a well defined, finite solution at the neurons' positions (see section !!??!!), it can only be modelled to a certain degree of accuracy, depending on the resolution of the numeric grid.
+In practice, we approximated the point sources of NO as an insertions at individual grid cells at a rate of $nNOS^i(t) / h^2$, where the normalizing divisor $h^2$ ensured the desired total influx per neuron.
+This numeric implementation required two additional constraints: First, all random neuron positions were confined to integer multiples of $h$ in x- and y-direction.
+Second, to avoid redundancy and for physiological reasons, each grid cell could only hold one neuron at maximum.
+Both conditions combined led to an iterative generation of positions, where for each neuron a random number generator produced pairs of integers $(n_x,n_y)$, each within $[0,N]$, until an unoccupied pair of integers was found and occupied, moving on to the next neuron.
+Figure \ref{diff_test_plot} shows an example of the resulting NO density.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/density_plots/density_plot.png}
+\end{center}
+\caption{Example of NO-diffusion with 400 point sources of excitatory neurons.}
+\label{diff_test_plot}
+\end{figure}
 
 \section{Results} \label{results}
+
+Since our main goal of the implementation of diffusive homeostasis was to allow the network to develop a broader distribution of firing rates across excitatory neurons compared to the original version of homeostasis, we first present the results of a comparison between features of the network activity in both variants in section \ref{activ_analys}.
+Following this is an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see section \ref{theor_osc}.
+
 \subsection{Activity Analysis} \label{activ_analys}
-Fig.
-\ref{full_sim_plots_av} shows the resulting dynamics of the population activity, average $NO$ concentration at the neurons' positions and the average firing threshold.
-Roughly speaking, both homeostatic mechanisms managed to keep the population activity in the desired range of $3~Hz$.
-However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Fig.
-\ref{full_sim_plots_av}, turn out to be very regular oscillations across all three parameters depicted in the closeup.
+Figure \ref{full_sim_plots_av} shows the resulting dynamics of the population activity, average $NO$ concentration at the neurons' positions and the average firing threshold.
+Both homeostatic mechanisms managed to keep the population activity in the desired range of 3 Hz.
+However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Figure \ref{full_sim_plots_av}, turn out to be very regular oscillations across all three parameters depicted in the closeup.
 While the oscillation amplitude undergoes a rather unpredictable time course, the frequency remains at a constant level of $\simeq 1Hz$.
@@
 point out, it has been experimentally observed that firing rates are rather heterogeneous, resulting in a broad distribution.
-In Fig.
-\ref{firing_rate_dist_comp} we compare our results for the firing distribution to the results by Sweeney et al..
+In Figure \ref{firing_rate_dist_comp} we compare our results for the firing distribution to the results by Sweeney et al..
 \begin{figure}
@@
 The strong oscillations of the threshold make it difficult to estimate the threshold distribution in our case.
-For the plot in Fig.
-\ref{thresh_dist_comp}, we calculated each neuron's time average threshold for the case of non-diffusive and diffusive homeostasis and used this as a basis for the distribution.
+For the plot in Figure \ref{thresh_dist_comp}, we calculated each neuron's time average threshold for the case of non-diffusive and diffusive homeostasis and used this as a basis for the distribution.
 In contrast to Sweeney et al., the statistics did not change significantly.
@@
 Another possibility of characterizing neural activity is to determine the distribution of interspike intervals (ISIs).
-Using non-diffusive homeostasis, one can observe a Poisson-like spiking behaviour with a stochastic refractory period, which is typically observed in cortical networks (Fig.
-.
-This is not what can be observed for the case of diffusive homeostasis: the ISI distribution reveals preference of interspike times in the range of $1s$, whereas interspike times in of $0.1-0.6s$ are less likely than a Poisson process would predict.
-This deviation matches the frequency of activity oscillations, see Fig.
-\ref{full_sim_plots_av}.
+Using non-diffusive homeostasis, one can observe a Poisson-like spiking behaviour with a stochastic refractory period, which is typically observed in cortical networks (This is not what can be observed for the case of diffusive homeostasis: the ISI distribution reveals preference of interspike times in the range of $1s$, whereas interspike times in of $0.1-0.6s$ are less likely than a Poisson process would predict.
+This deviation matches the frequency of activity oscillations, see Figure \ref{full_sim_plots_av}.
 \begin{figure}
@@
 
-As a whole, the oscillating activity imposes a undesirable regularity onto the network's activity, see also Fig.
-\ref{spike_sequence}.
+As a whole, the oscillating activity imposes a undesirable regularity onto the network's activity, see also Figure \ref{spike_sequence}.
 While this effect might be tolerable without any external input, it is likely that the oscillations will overlay and obscure network responses onto external drive, presumably making it unusable for any computational task.
@@
 
-\subsection{Analysis of sustained Oscillations}\label{theor_osc}
+\subsection{Analysis of Sustained Oscillations}\label{theor_osc}
 
@@
 To complete the expression, one has to find an appropriate description of the $r(\theta)$-relation.
-As a most simple approximation, we applied a linear regression to the data of the average threshold and the corresponding population activity, see Fig.
-\ref{thresh_r_linfit}.
+As a most simple approximation, we applied a linear regression to the data of the average threshold and the corresponding population activity, see Figure \ref{thresh_r_linfit}.
 The constant $C$ in equation \eqref{simple_NO_dyn} is then proportional to the slope of the linear fit.
@@
 \end{figure}
-Fig. \ref{lin_mod_osc} shows the results achieved from the simulation. We observe that noise is capable of maintaining oscillations in an otherwise stable linear system.
+Figure \ref{lin_mod_osc} shows the results achieved from the simulation. We observe that noise is capable of maintaining oscillations in an otherwise stable linear system.
 
@@
 
-Fig.
-\ref{power_spec_thresh_sim_vs_an} suggests that the theoretical result does not fully cover the dynamics of the simulation, but supports the observation of a sustained oscillation at a preferred frequency.
+Figure \ref{power_spec_thresh_sim_vs_an} suggests that the theoretical result does not fully cover the dynamics of the simulation, but supports the observation of a sustained oscillation at a preferred frequency.
 
@@
 
-As shown in Fig.
-\ref{firing_rate_dist_comp}, the distribution of firing rates within the population of neurons is highly dependent on the diffusion constant $D$, in accordance to the findings by Sweeney et.
+As shown in Figure \ref{firing_rate_dist_comp}, the distribution of firing rates within the population of neurons is highly dependent on the diffusion constant $D$, in accordance to the findings by Sweeney et.
 al.
@@
 
-Fig.
-\ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics for $\alpha=0.4$ and $\alpha = 0.8$.
+Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics for $\alpha=0.4$ and $\alpha = 0.8$.
 Both predictions can be confirmed: All rates approach the same target rate of $3Hz$ and, apparently, thresholds move toward the same state for either choice of $\alpha$.
@@
 
-An example of a distribution of rates acquired from this method is shown in fig. \ref{rate_dist_interact_matrix}.
+An example of a distribution of rates acquired from this method is shown in Figure \ref{rate_dist_interact_matrix}.
 

### 2016-10-15 draft.tex
.

@@
 \documentclass[10pt,a4paper]{article}
+%\usepackage{layouts}
+\usepackage[a4paper,margin=1.5in]{geometry}
 \usepackage[utf8]{inputenc}
@@
 \maketitle
-
 \section{Abstract} \label{abstract}
@@
 \hline
-$\mathrm{\tau_{V_t}}$ & see section ?? \\
+$\mathrm{\tau_{V_t}}$ & see section \ref{activ_analys} \\
 \hline
@@
 Following this is an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see section \ref{theor_osc}.
+Furthermore, we compare topological features of the network under the influence of diffusive and non-diffusive homeostasis in section ???.
 
 \subsection{Activity Analysis} \label{activ_analys}
-Figure \ref{full_sim_plots_av} shows the resulting dynamics of the population activity, average $NO$ concentration at the neurons' positions and the average firing threshold.
-Both homeostatic mechanisms managed to keep the population activity in the desired range of 3 Hz.
-However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Figure \ref{full_sim_plots_av}, turn out to be very regular oscillations across all three parameters depicted in the closeup.
-While the oscillation amplitude undergoes a rather unpredictable time course, the frequency remains at a constant level of $\simeq 1Hz$.
-Although one might argue that regular oscillations of the $NO$ concentration are not of much concern in terms of the network's structure and behaviour, this is not true for the population activity.
+As a first attempt, we set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$, as given by \cite{Sweeney_Paper}.
+Switching between non-diffusive/diffusive homeostasis after 700 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group, the average $NO$ concentration at the excitatory neurons' positions and the average firing threshold within the exc.
+group (inh.
+threshold was fixed, see table \ref{LIF_neuron_params}).
+Both homeostatic mechanisms managed to keep the excitatory population activity in the desired range of 3 Hz.
+However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Figure \ref{full_sim_osci}, are in fact regular oscillations across all three depicted variables.
+While the oscillation amplitudes undergo a rather unpredictable time course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
+Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further inquiry.
+
 \begin{figure}
-\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_compl.eps}
-\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_closeup.eps}
-\caption{Population activity, average $NO$ concentration (averaged over readouts at neurons' positions) and average firing threshold.
-Canonical homeostasis was used for $0-250s$ , diffusive for $250-500s$.
-Activity target was $3 ~Hz$.}
-\label{full_sim_plots_av}
+\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_compl.png}
+%\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_closeup.png}
+\caption{A/A*: Mean of excitatory (blue) and inhibitory (red) neuronal firing rate.
+B/B*: NO concentration averaged over readouts at exc.
+neurons' positions.
+C/C*: Average exc.
+firing threshold.
+Non-diffusive homeostasis was used for $\mathrm{0-700\, s}$ , diffusive h.
+for $\mathrm{700-1500\, s}$.
+Target activity was $\mathrm{3\, Hz}$.}
+\label{full_sim_osci}
 \end{figure}
+
+Rhythmic patterns of activity are a commonly observed phenomenon within the brain.
+Depending on the rate of oscillations, the location within the brain and the spatial scale over which they are observed, different physiological features are found to be responsible, leading to explanatory models at different levels of abstraction.
+On a microscopic, single-neuron level, a so-called slow after-hyperpolarization conductance explains the appearance of bursting behaviour: A relatively short period of spiking activity is followed by a longer period of silence.
+This phenomenon can be modelled by a $Ca^{2+}$-dependent $K^{+}$-conductance.
+Upon the bursting period, $Ca^{2+}$ concentration rises, prohibiting continuous spiking due to the activation of $K^{+}$  current until the $Ca^{2+}$ concentration has returned to base-level \cite[p.~203-207]{Theor_Neur_Dayan}.
+However, due to the simplicity of our neuron model, this type of oscillating activity can be ruled out as an explanation.
+
+On a larger, rate-based level, dynamical models of interconnected excitatory and inhibitory groups can exhibit sustained oscillations of activity \cite[p.~270]{Theor_Neur_Dayan}.
+As a simplest model, one can describe the dynamics of the exc.
+and inh.
+populations as a 2-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$:
+\begin{align}
+\tau_e \dot{r}_e  &= -r_e + \phi_e(r_e W_{ee} + r_i W_{ie}) \label{2d-exc_inh_rate_1} \\
+\tau_i \dot{r}_i  &= -r_i + \phi_i(r_e W_{ei} + r_i W_{ii}) \label{2d-exc_inh_rate_2}
+\end{align}
+
+where $\tau_e$ and $\tau_i$ represents time constants representing the rapidity of firing rate adaptation, $\phi_e$ and $\phi_i$ the respective transition functions between synaptic input and firing rate and $W_{xy}$ the mean synaptic weight from population x to population y.
+
+As plot A* in Figure \ref{full_sim_osci} indicates, the mean firing rates of both populations are highly correlated in time.
+For the source of oscillating behaviour to be found within the interaction between both populations,
 
@@
 Using non-diffusive homeostasis, one can observe a Poisson-like spiking behaviour with a stochastic refractory period, which is typically observed in cortical networks (This is not what can be observed for the case of diffusive homeostasis: the ISI distribution reveals preference of interspike times in the range of $1s$, whereas interspike times in of $0.1-0.6s$ are less likely than a Poisson process would predict.
-This deviation matches the frequency of activity oscillations, see Figure \ref{full_sim_plots_av}.
+This deviation matches the frequency of activity oscillations, see Figure \ref{full_sim_osci}.
 \begin{figure}

### 2016-10-18 draft.tex
.

@@
 dV = -\frac{V-E_l}{\tau_m}dt + \frac{\sigma}{\sqrt{\tau_m}}dW
+\label{LIF_Dynamics}
 \end{equation}
@@
 where $\tau_e$ and $\tau_i$ represents time constants representing the rapidity of firing rate adaptation, $\phi_e$ and $\phi_i$ the respective transition functions between synaptic input and firing rate and $W_{xy}$ the mean synaptic weight from population x to population y.
+A persistent oscillation then corresponds to a stable limit cycle in the 2-dimensional phase plane.
+According to the Poincaré-Bendixson Theorem, such a limit cycle exists inside a region $R$ if $R$ contains no fixed points and if any trajectory whose starting points lies within $R$ is confined to $R$.
+The second condition is equivalent to the condition that for all points $\mathbf{r}_{edge}$ on the edge of $R$, the vector field $\dot{\mathbf{r}}_{edge}$ is facing "into" $R$, see \cite[p.~248]{Dyn_Sys_Hirsch}.
+This case occurs if the system has a locally unstable fixed point, but a non-linearity that prevents an infinite deviation from the fixed point.
+Coming back to the dynamics in question, one would need to show that the network has a locally unstable fixed point at $\mathrm{(r_e,r_i)\approx (3\, Hz, 13\, Hz)}$, see A* in Figure \ref{full_sim_osci}.
+Several aspects come into play, making it a hard task to fit the full spiking network model onto the simplified equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
+First, the choice of $\tau_e$ and $\tau_i$ in \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2} has significant influence onto the stability of the system.
+However, a straightforward equivalent does not exist in the used spiking neuron model.
+It has been shown that in the case of slowly varying input $\tau_{e/i}$ of equation \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2} are equal to the membrane constant $\tau_m$ of the LIF-neuron used in the network \cite{Gerstner_Pop_Act}, see equation \ref{LIF_Dynamics}.
+A second problem is to choose a good estimate of the activation functions $\phi_{e/i}( \cdot )$.
+In the absence of noise in equation \ref{LIF_Dynamics}, the firing rate for a given constant total input $J$ is
+\begin{equation}
+\phi(J) = \begin{cases}\frac{1}{-\tau_m ln(\frac{V_t -E_l-J\tau_m}{V_r -E_l-J\tau_m})} & \mathrm{for}\; J\tau_m + E_l > V_t\\
+0 & \mathrm{otherwise}
+\end{cases}.
+\label{LIF_Fir_Rate_no_Noise}
+\end{equation}
+If membrane noise is present, according to \cite{Roxin_Firing_Rate_Distribution} one can calculate the \emph{mean} firing rate by
+\begin{equation}
+\phi(J) = 
+\label{LIF_Fir_Rate_with_Noise}
+\end{equation}
 

### 2016-10-24 draft.tex
.

@@
 \begin{equation}
-dV = -\frac{V-E_l}{\tau_m}dt + \frac{\sigma}{\sqrt{\tau_m}}dW
+{\tau_m}dV = -(V-E_l)dt + \sqrt{\tau_m} \sigma dW
 \label{LIF_Dynamics}
@@
 As a first attempt, we set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$, as given by \cite{Sweeney_Paper}.
-Switching between non-diffusive/diffusive homeostasis after 700 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group, the average $NO$ concentration at the excitatory neurons' positions and the average firing threshold within the exc.
+Switching between non-diffusive/diffusive homeostasis after 750 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group, the average $NO$ concentration at the excitatory neurons' positions and the average firing threshold within the exc.
 group (inh.
@@
 While the oscillation amplitudes undergo a rather unpredictable time course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
-Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further inquiry.
-
+Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further enquiry.
 \begin{figure}
@@
 firing threshold.
-Non-diffusive homeostasis was used for $\mathrm{0-700\, s}$ , diffusive h.
-for $\mathrm{700-1500\, s}$.
+Non-diffusive homeostasis was used for $\mathrm{0-750\, s}$ , diffusive h.
+for $\mathrm{750-1500\, s}$.
 Target activity was $\mathrm{3\, Hz}$.}
@@
 \end{equation}
-If membrane noise is present, according to \cite{Roxin_Firing_Rate_Distribution} one can calculate the \emph{mean} firing rate by
+If noise $\sigma$ is present, according to \cite{Roxin_Firing_Rate_Distribution} one can calculate the \emph{mean} firing rate by
+\begin{align}
+\phi(J) &= \left[ \sqrt{\pi}\tau_m \int_{x_-}^{x_+} dx e^{x^2} erfc(-x) \right]^{-1} \label{LIF_Fir_Rate_with_Noise1}\\
+x_- &= (V_r-E_l-J\tau_m)/\sigma \label{LIF_Fir_Rate_with_Noise2}\\
+x_+ &= (V_t-E_l-J\tau_m)/\sigma \label{LIF_Fir_Rate_with_Noise3}
+\end{align}
+where $erfc$ is the complementary error function. Figure \ref{F-I_noise_dep} shows that both predictions are quite accurate in predicting the mean firing rate. 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/F-I_noise_dep.png}
+\end{center}
+\caption{Comparison of mean firing rate of a LIF neuron without noise (squares) and with noise (circles, $\mathrm{\sigma = \sqrt{5}\, mV}$), averaged over $\mathrm{50\, s}$.
+Red and blue curves are the corresponding analytic predictions, see equation \ref{LIF_Fir_Rate_no_Noise} and \ref{LIF_Fir_Rate_with_Noise1}.}
+\label{F-I_noise_dep}
+\end{figure}
+However, one should note that the synaptic input within a spiking network carries an intrinsic randomness: since it is the sum of instantaneous increases in membrane voltage upon arriving spikes, one cannot simply describe it as a mean constant input $J$.
+Rather, if we assume that the arrival of spikes is approximately poisson-distributed and the time constant of the membrane is small compared to the average interspike-interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \cdot \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
+\begin{align}
+\mu_{AB} &= <w_{AB}> \cdot <N_{in,AB}> \cdot <r_A> \label{Noise_Approx_1}\\
+\sigma_{AB} &= \sqrt{\tau_m \cdot <w_{AB}>^2 \cdot <N_{in,AB}> \cdot <r_A>} \label{Noise_Approx_1} \, .
+\end{align}
+$\mathrm{<w_{AB}>,\, <N_{in,AB}>}$ and $\mathrm{<r_A>}$ denote the mean weight of a synapse connection population $\mathrm{A}$ with population $\mathrm{B}$, the mean number of incoming connections at a neuron in population $\mathrm{B}$ and the mean firing rate in population $\mathrm{A}$ (which makes it necessary to assume changes within the firing rate to be slow enough for a quasi-stationary description of the activity).
+Since we can assume intrinsic and input noise to be uncorrelated, the total noise within a neuron of population $\mathrm{B}$ has a standard deviation of 
 \begin{equation}
-\phi(J) = 
-\label{LIF_Fir_Rate_with_Noise}
+\sigma_{tot.} = \sqrt{\sigma_{intr.}^2 + \sum_A \sigma_{AB}^2} \; .
+\label{Total_Noise_Neuron}
 \end{equation}
+
+Apart from the correct description of $\phi_{e/i}$, a third problem is the analytic description of the STP that was present for recurrent excitatory connections in our network.
+In \cite{Markram_STP}, the steady-state value of $\mathrm{x\cdot u}$ for an input of constant rate $\mathrm{r}$ is given by
+\begin{align}
+x_{st.}(r) &= \frac{1-\exp \left(-\frac{1}{r\cdot \tau _d}\right)}{1-\left(1-u_{st.}\left(r\right)\right)\cdot \exp \left(-\frac{1}{r\cdot \tau _d}\right)} \label{STP_steady1} \\
+u_{st.}(r) &= \frac{U}{1-\left(1-U\right)\exp \left(-\frac{1}{r\cdot \tau _f}\right)} \; .\label{STP_steady2}
+\end{align}
+When trying to find the fixed point of equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}, one thus needs to incorporate the factor $\mathrm{x_{st.}\cdot u_{st.}}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise.
+
+All these aspects taken together make it impossible to find an analytic expression for the fixed point of Equation \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
+Running a simulation of \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}, including all aforementioned approximations results in a stable configuration depicted in \ref{Dyn_Rate_Approx}.
+For this simulation, we set the relevant parameters to their predefined values and, in addition, extracted the mean threshold of the excitatory population which was set by the non-diffusive homeostasis, see C/C* in Figure \ref{full_sim_osci}, yielding a threshold of $\mathrm{-56.963\, mV}$.
+The results are depicted in Figure \ref{Dyn_Rate_Approx}.
+The system settled to a fixed point of $\mathrm{(r_{0,e},r_{0,i}) = (2.992\, Hz, 7.144\, Hz)}$, which is quite close to $\mathrm{(3\, Hz, 6.768\, Hz)}$, being the mean excitatory and inhibitory firing rate between 100-750 s of the full simulation (i.e., during non-diffusive homeostasis).
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/approx_rates_EI.png}
+\end{center}
+\caption{Dynamics of equations \ref{2d-exc_inh_rate_1} (blue line) and \ref{2d-exc_inh_rate_2} (red line).
+Dotted lines mark the mean frequencies that where present in the full spiking network.
+Excitatory: 3 Hz, Inhibitory: 6,768 Hz.
+\ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2} converged to 2.992 Hz and 7.144 Hz respectively.}
+\label{Dyn_Rate_Approx}
+\end{figure}
+In principal, one could now further quantify the stability of the found fixed point by calculating the Jacobian matrix at $\mathrm{(r_{0,e},r_{0,i})}$.
+For the sake of the initial question though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: Assuming the validity of the described rate-model, the recurrent network as such (without homeostasis) is stable under the given choice of parameters.
 

### 2016-11-01 draft.tex
.

@@
 
-We solved \eqref{NO_dyn} with the finite difference method on a grid with a resolution of $100\times 100$ points.
+We solved \eqref{NO_dyn} with the finite difference method on a grid $\mathbf{r}_{i,j}$ with a resolution of $100\times 100$ points.
 Integration over time was carried out by a 4th-order Runge-Kutta method with a time step of $1 ms$.
-On each time step, $\nabla^2 NO(\mathbf{r})$ was approximated by
+On each time step, $\nabla^2 NO(\mathbf{r}_{i,j}) = \nabla^2 NO_{i,j}$ was approximated by
 \begin{equation}
-\nabla^2 NO(\mathbf{r}_{i,j}) \approx \frac{NO_{i+1,j}+NO_{i-1,j}+NO_{i,j+1}+NO_{i,j-1}-4NO_{i,j}}{h^2}
+\nabla^2 NO_{i,j} \approx \frac{NO_{i+1,j}+NO_{i-1,j}+NO_{i,j+1}+NO_{i,j-1}-4NO_{i,j}}{h^2}
 \label{Laplace_Numeric}
@@
 In principal, one could now further quantify the stability of the found fixed point by calculating the Jacobian matrix at $\mathrm{(r_{0,e},r_{0,i})}$.
-For the sake of the initial question though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: Assuming the validity of the described rate-model, the recurrent network as such (without homeostasis) is stable under the given choice of parameters.
+For the sake of the initial question though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: Assuming validity of the described rate-model, the recurrent network as such (without homeostasis) is stable under the given choice of parameters.
+Furthermore, on an empirical basis, the occurrence of oscillations appear to be rather dependent on the choice of homeostasis, since apart from the homeostatic mechanism itself, all parameters of the simulation were kept unchanged upon the transition after 750s.
+In consequence, the following section further analyzes the dynamics underlying the diffusive homeostatic feedback.
 
-As plot A* in Figure \ref{full_sim_osci} indicates, the mean firing rates of both populations are highly correlated in time.
-For the source of oscillating behaviour to be found within the interaction between both populations,
+\subsection{Analysis of Oscillations under Dynamic Feedback}\label{theor_osc}
+
+Both forms of homeostasis use the excitatory firing threshold as a means of adjusting the excitatory firing rate.
+Though having a relatively immediate impact on the firing rate of the particular neuron, the network as a whole reacts by means of a local disturbance of activity as well: it settles at a new fixed point of firing rates.
+In the context of feedback dynamics, two questions are of importance.
+First, obviously, how the relation between a local change of threshold and the new fixed point of the network can be described and second, whether the time scale of the network's response is of relevance with respect to other time scales involved in the feedback loop.
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/diff_hom/rate_th_close.png}
+\end{center}
+\label{rate_th_close}
+\end{figure}
+
+!!!!AB HIER NUR UNSAUBER UND UNAUSGEARBEITET!!!!
 

### 2016-11-07 draft.tex
.

@@
 First, obviously, how the relation between a local change of threshold and the new fixed point of the network can be described and second, whether the time scale of the network's response is of relevance with respect to other time scales involved in the feedback loop.
+Regarding the second question, Figure \ref{rate_th_close} suggests that the excitatory population activity follows the mean firing threshold quasi instantaneously, compared with the overall time scale of the oscillating pattern.
 \begin{figure}
@@
 \end{center}
+\caption{Time course of the mean firing rate (blue) and the mean firing threshold within the excitatory pool (red). Bin width for firing rate estimation was 0.1s.}
 \label{rate_th_close}
 \end{figure}
+Thus, in a first attempt of understanding the occurrence of undesired oscillations, we presumed an immediate functional relationship $\mathbf{r}_e (t) = \mathbf{r}_e (\mathbf{V}_{t,e} (t))$, $\mathbf{r}_e$ and $\mathbf{V}_{t,e}$ representing the set of excitatory firing rates and thresholds, respectively.
+
+Describing the neural activity as instantaneous firing rates raises the question how to accurately describe the production of nitric oxide, since the outcome of equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $Ca^{2+}$ concentration caused by spike events.
+Naively, one could replace the sum of dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{spike} r_i(t)$.
+If \eqref{nNOS_dyn} was a linear homogeneous differential equation, this approximation would indeed allow for the correct calculation of a linear relation between mean firing rate and NO production.
+The cubic dependence on $Ca^{2+}$ breaks this simplicity.
 

### 2016-11-15 draft.tex
.

@@
 The cubic dependence on $Ca^{2+}$ breaks this simplicity.
+In order to derive an approximate description, we denote two things: First, the target firing rate of 3 Hz and the corresponding mean interspike interval of 0.33...s is large compared to the decay constant of Calcium, $\tau_{Ca^{2+}} = \mathrm{0.01\,s}$.
+Consequently, it is very unlikely that one spike event will fall into a region where the Calcium concentration, decaying from the instant jump of the previous spike event, is still significantly larger than zero.
+As such, one can justify
+\begin{equation}
+\begin{split}
+{Ca^{2+}}^3(t) &= \left[ Ca^{2+}_{spike} \sum_{i} \theta(t-t^i_{spike,i}) exp(-(t-t^i_{spike,j})/\tau_{Ca^{2+}}) \right]^3 \\
+&\approx {Ca^{2+}_{spike}}^3 \sum_{i} \theta(t-t^i_{spike,i}) exp(-3(t-t^i_{spike,j})/\tau_{Ca^{2+}})
+\end{split} \label{cubic_approx_1}			
+\end{equation}
+with $\theta(x)$ being the Heaviside step function. By the same argument
+\begin{equation}
+\frac{{Ca^{2+}}^3(t)}{{Ca^{2+}}^3(t)+1} \approx \sum_{i} \theta(t-t^i_{spike}) \frac{exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}})}{exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}}  
+\end{equation}
+Therefore, the resulting rate of NO synthesis can be decomposed into a sum of time shifted responses onto a single kernel of Calcium concentration as a result of a spike.
+for a spike at $t_{spike}=0$, the solution of \eqref{nNOS_dyn} can be calculated by
+\begin{equation}
+\begin{split}
+nNOS(t) &= \frac{1}{\tau_{nNOS}}\int_{-\infty}^t dt' exp(-(t-t')/\tau_{nNOS})\cdot \theta(t') \frac{exp(-3t'/\tau_{Ca^{2+}})}{exp(-3t'/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}} \\
+&= \frac{1}{\tau_{nNOS}}\int_{0}^t dt' exp(-(t-t')/\tau_{nNOS})\cdot \frac{exp(-3t'/\tau_{Ca^{2+}})}{exp(-3t'/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}}\;.
+\end{split}\label{nNOS_single_sol}
+\end{equation}
+The exact solution of this integral can be expressed in terms of the hypergeometric function, making it rather impractical for any further analysis.
+Looking for further simplifications, we note that $\tau_{nNOS}$ is chosen ten-fold larger than $\tau_{Ca^{2+}}$.
+This discrepancy in decay times allows for the assumption that the impact of the Calcium kernel onto $nNOS$ is practically instantaneous.
+Consequently, $nNOS(t)$ becomes
+\begin{equation}
+nNOS(t) = \frac{1}{\tau_{nNOS}} \theta(t) exp(-t/\tau_{nNOS}) \int_{0}^\infty dt' \frac{exp(-3t'/\tau_{Ca^{2+}})}{exp(-3t'/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}}\;.
+\label{nNOS_single_sol_approx1}
+\end{equation}
+In this form, the integral has an easy-to-handle solution, which - with all spike events now included - results in
+\begin{equation}
+nNOS(t) = \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3\tau_{nNOS}} \sum_i \theta(t-t^i_{spike}) \exp(-(t-t^i_{spike})/\tau_{nNOS})\;.
+\label{nNOS_single_sol_approx2}
+\end{equation}
+Figure \ref{nNOS_approx_plot} compares the approximation given by \eqref{nNOS_single_sol_approx2} to the full NO production model (equations \eqref{Ca_dyn} and \eqref{nNOS_dyn}).
+Spikes were drawn from a poisson process at a rate of 3 Hz.
+As predicted, the simplified model fits very well for sufficiently isolated spike events.
+For the rare event of two subsequent spikes appearing very close to each other, as seen in Figure \ref{nNOS_approx_plot} at approximately 4 seconds, one can observe a slightly smaller but acceptable agreement.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/nNOS_approx.png}
+\caption{Time course of nNOS(t) with poisson spiking at 3Hz.
+The full simulation (blue, see equations \eqref{Ca_dyn},\eqref{nNOS_dyn}) is well fitted by the simplified model (red, see equation \eqref{nNOS_single_sol_approx2}).
+Top axis is a closeup of the first spike event.}
+\label{nNOS_approx_plot}
+\end{figure}
+
+Returning to the initial question, we note that according to equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$, which makes the mean rate of NO production over time simply $<nNOS> = <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
+More specific, if the average interspike intervals of the underlying spike generation were short compared to the decay constant $\tau_{nNOS}$, one could show that \eqref{nNOS_single_sol_approx2} approaches gaussian noise with the aforementioned mean $\mu_{nNOS}(<r>) =  <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$ and a variance of $\sigma^2_{nNOS}(<r>) = <r> \frac{{Ca^{2+}_{spike}}^6 {\tau_{Ca^{2+}}}^2 ln^2(2)}{18\tau_{nNOS}}$.
+However, for a single cell spiking at a mean firing rate of 3 Hz with approximately poissonian statistics, Figure \ref{nNOS_approx_plot} indicates that this approximation is not valid.
+Furthermore, the condition of interspike intervals to be short compared to the decay constant inherently contradicts the necessary assumptions that were taken for the previous approximations to hold.
+
+To overcome this contradiction, we introduce an idealized picture of diffusive homeostasis, where diffusion across the tissue is instantaneous.
+This simplification results in a single level of NO-concentration for all neurons, only being modified over time by the sum of all neurons' NO-syntheses and the decay term $-\lambda NO$.
+To account for the spread of NO, $nNOS(t)$ must be divided by the area $L^2$ of the tissue.
+The idealized version of \eqref{NO_dyn} then reads
+\begin{equation}
+\dot{NO}(t)=-\lambda NO + \frac{\sum_{i} nNOS^i(t)}{L^2}\;.
+\label{NO_dyn_approx}
+\end{equation}
+In this form, it becomes clear that we can now describe the \emph{total} influx of NO (the sum in \eqref{NO_dyn_approx}) as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective poisson process with a mean rate of $3 Hz \cdot N_{exc.} = \mathrm{1200\,Hz}$, given the assumption that cells are spiking weakly correlated.
+Furthermore, we argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{total} = N_{exc.}\cdot r_{exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
+Thus, equation \eqref{NO_dyn_approx} becomes
+\begin{equation}
+\dot{NO}(t)=-\lambda NO + \frac{\mu_{nNOS}(N_{exc.}r_{exc.pop.}(t)) + \sigma_{nNOS}(N_{exc.}r_{exc.pop.}(t)) \xi (t)}{L^2}\;.
+\label{NO_dyn_approx2}
+\end{equation}
+As a next step, we attempted to simplify the dynamics of threshold adaption and its effect on the population rate.
+Since equation \eqref{NO_dyn_approx2} contains a single variable $r_{exc.pop.}(t)$ for the mean excitatory activity, we attempted to find an appropriate description based solely on
 

### 2016-11-15 draft.tex
.

@@
 As a next step, we attempted to simplify the dynamics of threshold adaption and its effect on the population rate.
-Since equation \eqref{NO_dyn_approx2} contains a single variable $r_{exc.pop.}(t)$ for the mean excitatory activity, we attempted to find an appropriate description based solely on
+Since equation \eqref{NO_dyn_approx2} contains a single variable $r_{exc.pop.}(t)$ for the mean excitatory activity, we wanted to find an appropriate description containing the mean threshold $V_{t,pop.}(t) = <V_t(t)>$.
+As stated earlier, Figure \ref{rate_th_close} suggests an immediate and approximately linear relation between excitatory population rate and the mean of thresholds within the excitatory population.
+Figure \ref{thresh_r_linfit} shows a linear fit (being of the form $\alpha x + \beta$) of these two quantities plotted against each other.
+Apart from rarely appearing high values of $V_{t,pop.}$, we found a good fit to the linear model and concluded $r_{exc.pop.}(t) \approx r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0})$, where $r_{IP}$ is given in table \ref{Params_IP} as the mean excitatory target firing rate and $V_{t,0} \equiv (r_{IP}-\beta)/\alpha$ is the mean threshold corresponding to the target rate.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/Spike_Stats/linfit_th_rate.png}
+\caption{Linear fit of excitatory population activity and mean excitatory threshold.
+Slope $\alpha$ of the fit: $\mathrm{-0.772\, Hz/mV}$.
+Offset $\beta$: $\mathrm{-41.01\, Hz}$.
+Mean squared error: $\mathrm{R^2 = 0.69}$.}
+\label{thresh_r_linfit}
+\end{figure}
+
+Combining these results in a set of equations, we find
+\begin{align}
+\begin{split}
+\dot{NO}(t) &= - \lambda NO + \frac{ N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}[\alpha(V_{t,pop.}(t)-V_{t,0}) + r_{IP}] \\
+&+ \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{\alpha(V_{t,pop.}(t)-V_{t,0}) + r_{IP}}\xi (t)
+\end{split}\label{2d-sys-homeostasis1}\\
+\dot{V_{t,pop.}}(t) &= \frac{NO-NO_0}{NO_0 \tau_{V_t}}\;. \label{2d-sys-homeostasis2}
+\end{align}
+Through the coordinate transformation $n = NO-NO_0 \; , \theta = V_{t,pop.}(t)-V_{t,0}$, we can a simplify the dynamical system:
+\begin{align}
+\begin{split}
+\dot{n} &= -\lambda n + \frac{\alpha N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}\theta \\
+&+ \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{\alpha\theta + r_{IP}}\xi (t)
+\end{split}\label{2d-sys-homeostasis-coord_transf1}\\
+\dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{2d-sys-homeostasis-coord_transf2}
+\end{align}
 
@@
 \caption{Linear fit of the relation between the firing threshold (averaged over population) and the population activity. $R^2=0.99996$.}
-\label{thresh_r_linfit}
+
 \end{figure}

### 2016-11-16 draft.tex
.

@@
 \captionsetup[figure]{singlelinecheck=false}
+
+\usepackage{setspace}
+\makeatletter
+\newcommand{\MSonehalfspacing}{%
+  \setstretch{1.44}%  default
+  \ifcase \@ptsize \relax % 10pt
+    \setstretch {1.448}%
+  \or % 11pt
+    \setstretch {1.399}%
+  \or % 12pt
+    \setstretch {1.433}%
+  \fi
+}
+
+%\makeatother
+%\MSonehalfspacing
+
 \title{Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\
@@
 While the oscillation amplitudes undergo a rather unpredictable time course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
-Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further enquiry.
+This feature is also illustrated by the fact that the power spectra depicted in Figure \ref{Power_Spec_without_Analysis} have a peak at the frequency that appeared to be dominant in Figure \ref{full_sim_osci}.
+The fact that the mean over all power spectra of excitatory thresholds differs from the power spectrum of the mean of these thresholds in its amplitude indicates that not all thresholds oscillate at the same phase.
+Still though, the overall shape of both spectra are equivalent.
 \begin{figure}
@@
 \end{figure}
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/power_spec/power_spectrum_sim_only.png}
+\caption{Blue: Mean of power spectrum over all excitatory thresholds. Red: Power spectrum of mean over all exc. thresholds.}
+\label{Power_Spec_without_Analysis}
+\end{center}
 
+\end{figure}
+Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further enquiry.
 Rhythmic patterns of activity are a commonly observed phenomenon within the brain.
@@
 \subsection{Analysis of Oscillations under Dynamic Feedback}\label{theor_osc}
+In this section, we discuss an analytic treatment of the dynamics underlying the diffusive homeostatic mechanism.
+The goal of this analysis is to predict the shape of the power spectrum shown in Figure \ref{Power_Spec_without_Analysis}.
+This will give insight into the relation between parameters of the model and the resulting preferred frequency and amplitude, allowing us to choose appropriate parameter values in order to reduce frequency and amplitude of the oscillations.
 
@@
 
-Returning to the initial question, we note that according to equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$, which makes the mean rate of NO production over time simply $<nNOS> = <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
+Returning to the question of how to describe NO synthesis in a simplified form, we note that according to equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$, which makes the mean rate of NO production over time simply $<nNOS> = <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
 More specific, if the average interspike intervals of the underlying spike generation were short compared to the decay constant $\tau_{nNOS}$, one could show that \eqref{nNOS_single_sol_approx2} approaches gaussian noise with the aforementioned mean $\mu_{nNOS}(<r>) =  <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$ and a variance of $\sigma^2_{nNOS}(<r>) = <r> \frac{{Ca^{2+}_{spike}}^6 {\tau_{Ca^{2+}}}^2 ln^2(2)}{18\tau_{nNOS}}$.
@@
 \end{align}
-Through the coordinate transformation $n = NO-NO_0 \; , \theta = V_{t,pop.}(t)-V_{t,0}$, we can a simplify the dynamical system:
+Through the coordinate transformation $n = NO-NO_0 \; , \theta = V_{t,pop.}(t)-V_{t,0}$, we can simplify the dynamical system:
 \begin{align}
@@
 \end{align}
+The amplitude of noise in equation \ref{2d-sys-homeostasis-coord_transf1} depends on $\theta$.
+If kept in the equation, this dependence turned out be an insuperable obstacle for our goal of finding an analytic description of the homeostatic oscillations.
+In consequence, we decided to make one further simplification, replacing $\sqrt{\alpha\theta + r_{IP}}$ by a constant factor $\sqrt{r_{IP}}$.
 

### 2016-12-01 draft.tex
.

@@
 \section{Abstract} \label{abstract}
-Based on the LIF-SORN-model proposed in \cite{SORN_Paper}, we attempted to replace the intrinsic homeostatic control system used in the original version by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
+We attempted to replace the intrinsic homeostatic control system used in the original version by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue based on the LIF-SORN-model proposed in \cite{SORN_Paper}.
 The model of diffusive homeostasis was adopted from a paper by Y.
@@
 In this section, we discuss an analytic treatment of the dynamics underlying the diffusive homeostatic mechanism.
-The goal of this analysis is to predict the shape of the power spectrum shown in Figure \ref{Power_Spec_without_Analysis}.
-This will give insight into the relation between parameters of the model and the resulting preferred frequency and amplitude, allowing us to choose appropriate parameter values in order to reduce frequency and amplitude of the oscillations.
-
-Both forms of homeostasis use the excitatory firing threshold as a means of adjusting the excitatory firing rate.
+The goal of this analysis was to predict the shape of the power spectrum shown in Figure \ref{Power_Spec_without_Analysis}.
+This gave insight into the relation between parameters of the model and the resulting preferred frequency and amplitude, allowing us to choose appropriate parameter values in order to reduce frequency and amplitude of the oscillations.
+
+Both forms of homeostasis use excitatory firing thresholds as a means of adjusting the excitatory firing rate.
 Though having a relatively immediate impact on the firing rate of the particular neuron, the network as a whole reacts by means of a local disturbance of activity as well: it settles at a new fixed point of firing rates.
-In the context of feedback dynamics, two questions are of importance.
-First, obviously, how the relation between a local change of threshold and the new fixed point of the network can be described and second, whether the time scale of the network's response is of relevance with respect to other time scales involved in the feedback loop.
-Regarding the second question, Figure \ref{rate_th_close} suggests that the excitatory population activity follows the mean firing threshold quasi instantaneously, compared with the overall time scale of the oscillating pattern.
+Two questions are of importance in the context of feedback dynamics.
+First - obviously - how the relation between a local change of threshold and the new fixed point of the network can be described and second, whether the time scale of the network's response is of relevance with respect to other time scales involved in the feedback loop.
+Regarding the second question, Figure \ref{rate_th_close} suggests that the excitatory population activity follows the mean firing threshold in a quasi instantaneous fashion, at least in comparison with the overall time scale of the oscillating pattern.
 \begin{figure}
@@
 \end{center}
-\caption{Time course of the mean firing rate (blue) and the mean firing threshold within the excitatory pool (red). Bin width for firing rate estimation was 0.1s.}
+\caption{Time course of the mean firing rate (blue) and the mean firing threshold within the excitatory pool (red). Bin width for firing rate estimation was 0.1 s.}
 \label{rate_th_close}
@@
 Figure \ref{thresh_r_linfit} shows a linear fit (being of the form $\alpha x + \beta$) of these two quantities plotted against each other.
-Apart from rarely appearing high values of $V_{t,pop.}$, we found a good fit to the linear model and concluded $r_{exc.pop.}(t) \approx r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0})$, where $r_{IP}$ is given in table \ref{Params_IP} as the mean excitatory target firing rate and $V_{t,0} \equiv (r_{IP}-\beta)/\alpha$ is the mean threshold corresponding to the target rate.
+Apart from rarely appearing high values of $V_{t,pop.}$, we found a good fit to the linear model.
+However, when we color coded the slope of $V_{t,pop.}(t)$, one could see a separation of the rising phase and falling phase within the cloud of data points.
+This indicates a small (due to the "flatness" of the shape) but noticeable delay between threshold and firing rate, the latter following the former.
+We implemented this in a similar way as in Equation \eqref{2d-exc_inh_rate_1}.
+The population rate relaxates towards a value given by the fitted linear dependence on $V_{t,pop.}$ linear fit: $\dot{r_{exc.pop.}}(t) = (-r_{exc.pop.} + r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0}))/\tau_r$, where $r_{IP}$ is given in table \ref{Params_IP} as the mean excitatory target firing rate and $V_{t,0} \equiv (r_{IP}-\beta)/\alpha$ is the mean threshold corresponding to the target rate.
+We expect $\tau_r$ to be in the same order of magnitude as the membrane time constant $\tau_m$.
+However, $r_{exc.pop.}$ represents the whole excitatory population.
+Taking conduction delay and interactions with the inhibitory population into account, $\tau_r$ thus should be slightly larger.
+
 \begin{figure}
@@
 Offset $\beta$: $\mathrm{-41.01\, Hz}$.
-Mean squared error: $\mathrm{R^2 = 0.69}$.}
+Mean squared error: $\mathrm{R^2 = 0.69}$.
+Colors encode the time derivative of $<V_t(t)>$, which indicates an ellipsoid like trajectory in phase space, with the firing rate following the threshold with a short delay.}
 \label{thresh_r_linfit}
@@
 \begin{split}
-\dot{NO}(t) &= - \lambda NO + \frac{ N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}[\alpha(V_{t,pop.}(t)-V_{t,0}) + r_{IP}] \\
-&+ \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{\alpha(V_{t,pop.}(t)-V_{t,0}) + r_{IP}}\xi (t)
+\dot{NO}(t) &= - \lambda NO + \frac{ N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}r_{exc.pop.} \\
+&+ \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{r_{exc.pop.}}\xi (t)
 \end{split}\label{2d-sys-homeostasis1}\\
-\dot{V_{t,pop.}}(t) &= \frac{NO-NO_0}{NO_0 \tau_{V_t}}\;. \label{2d-sys-homeostasis2}
-\end{align}
-Through the coordinate transformation $n = NO-NO_0 \; , \theta = V_{t,pop.}(t)-V_{t,0}$, we can simplify the dynamical system:
+\dot{V_{t,pop.}}(t) &= \frac{NO-NO_0}{NO_0 \tau_{V_t}} \label{2d-sys-homeostasis2} \\
+\dot{r_{exc.pop.}}(t) &= \frac{-r_{exc.pop.}+\alpha(V_{t,pop.}(t)-V_{t,0}) + r_{IP}}{\tau_r}\;. \label{2d-sys-homeostasis3}
+\end{align}
+Through the coordinate transformation $n = NO-NO_0 \; , \theta = V_{t,pop.}(t)-V_{t,0}\; , \nu = r_{exc.pop.} - r_{IP}$ we can simplify the dynamical system:
 \begin{align}
 \begin{split}
-\dot{n} &= -\lambda n + \frac{\alpha N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}\theta \\
-&+ \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{\alpha\theta + r_{IP}}\xi (t)
+\dot{n} &= -\lambda n + \frac{N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}\nu \\
+&+ \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{\nu + r_{IP}}\xi (t)
 \end{split}\label{2d-sys-homeostasis-coord_transf1}\\
-\dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{2d-sys-homeostasis-coord_transf2}
-\end{align}
-The amplitude of noise in equation \ref{2d-sys-homeostasis-coord_transf1} depends on $\theta$.
-If kept in the equation, this dependence turned out be an insuperable obstacle for our goal of finding an analytic description of the homeostatic oscillations.
-In consequence, we decided to make one further simplification, replacing $\sqrt{\alpha\theta + r_{IP}}$ by a constant factor $\sqrt{r_{IP}}$.
+\dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{2d-sys-homeostasis-coord_transf2} \\
+\dot{\nu} &= \frac{-\nu + \alpha \theta}{\tau_r} \label{2d-sys-homeostasis-coord_transf3}
+\end{align}
+where we have used the fact that $NO_0$ can be solved and expressed in terms of $r_{IP}$ by setting $\dot{NO}(t) = 0$.
+The amplitude of noise in equation \ref{2d-sys-homeostasis-coord_transf1} depends on $\nu$.
+Keeping this dependence in the equation turned out be an insuperable obstacle for our goal of finding an analytic description of the power spectrum of homeostatic oscillations.
+In consequence, we decided to take one further step of simplification by replacing $\sqrt{\nu + r_{IP}}$ by a constant factor $\sqrt{r_{IP}}$.
+In the following equation we use the substitutes $A\equiv \frac{N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}$, $B\equiv \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{r_{IP}}$ and $C\equiv \frac{1}{NO_0 \tau_{V_t}}$, resulting in
+\begin{align}
+\dot{n} &= -\lambda n + A \nu + B \xi (t) \label{2d-sys-homeostasis-coord_transf_substitute1} \\
+\dot{\theta} &= Cn \label{2d-sys-homeostasis-coord_transf_substitute2} \\
+\dot{\nu} &= \frac{-\nu + \alpha \theta}{\tau_r} \label{2d-sys-homeostasis-coord_transf_substitute3}
+\end{align}
+As stated in the beginning, we were interested in finding an analytic expression for the power spectrum of the mean excitatory threshold.
+Therefore we took the fourier transform of \eqref{2d-sys-homeostasis-coord_transf_substitute1} and \eqref{2d-sys-homeostasis-coord_transf_substitute2}, yielding
+\begin{align}
+i\omega f_n &= - \lambda f_n + A f_\nu + B f_\xi \label{2d-sys-homeostasis-coord_transf_substitute_ft1}\\
+i\omega f_\theta &= C f_n \label{2d-sys-homeostasis-coord_transf_substitute_ft2} \\
+i\omega f_\nu &= \frac{-f_\nu + \alpha f_\theta}{\tau_r} \label{2d-sys-homeostasis-coord_transf_substitute_ft3}
+\end{align}
+where $f_{(\cdot)}$ denotes the fourier transform. We solved for $f_\theta$ which immediately gave us the power spectrum $P_\theta (\omega) \equiv |f_\theta (\omega)|^2$ of $\theta$:
+\begin{equation}
+P_\theta (\omega) = \frac{B^2 P_\xi (\omega)}{\omega^2 \left( \frac{\lambda}{C} + \frac{A\alpha \tau_r}{1+\omega^2 \tau_r^2}\right)^2  + \left(         \frac{A\alpha}{1+\omega^2\tau_r^2} + \frac{\omega^2}{C}\right)^2}
+\end{equation}
+It was already mentioned that the statistics of $\xi(t)$ are approximately gaussian.
+However, this does not necessarily imply that its power spectrum is white.
+To find the actual power spectrum, we recall that Equation \eqref{nNOS_single_sol_approx2} can be written as a convolution:
+\begin{align}
+nNOS(t) &= \left(f \ast g\right)(t) \label{Noise_Pow_Spec_Conv1_1} \\
+f(t') &= \sum_i \delta(t' - t^i_{spike}) \label{Noise_Pow_Spec_Conv1_2} \\
+g(t') &= \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3\tau_{nNOS}} \theta(t') exp(-t'/\tau_{nNOS}) \label{Noise_Pow_Spec_Conv1_3}
+\end{align}
+Thus $\xi(t)$ is generated in the same way, namely a convolution of an exponential kernel with the same relaxation constant $\tau_{nNOS}$ and a poisson process with a rate of $N_{exc.}\cdot r_{IP}$, since it incorporates spikes from \emph{all} excitatory neurons:
+\begin{align}
+\xi (t) &= \left(f_\xi \ast g_\xi \right)(t) \label{Noise_Pow_Spec_Conv2_1} \\
+f_\xi (t') &= \sum_i \sum_{j=1}^{N_{exc.}} \delta(t' - t^{i,j}_{spike}) \label{Noise_Pow_Spec_Conv2_2} \\
+g_\xi (t') &= \sqrt{\frac{2}{r_{IP}N_{exc.}\tau_{nNOS}}} \theta(t') exp(-t'/\tau_{nNOS}) \label{Noise_Pow_Spec_Conv2_3}
+\end{align}
+where $\sqrt{\frac{2}{r_{IP}N_{exc.}\tau_{nNOS}}}$ accounts for the fact that $\xi(t)$ had a variance of one by definition. We can express the power spectrum as
+\begin{equation}
+P_{\xi} = P_{f_\xi} \cdot P_{g_\xi} \;. \label{Noise_Pow_Spec_Conv2}
+\end{equation}
+Similar to the earlier assumption that the width of the noise term is stationary, we assume that $f_\xi$ is a stationary Poisson Process with an average rate $r_{IP}N_{exc.}$.
+It thus has a power spectrum of (see e.g.
+\cite[p.
+162]{Spiking_Gerstner})
+\begin{equation}
+P_{f_\xi} (\omega) = r_{IP}N_{exc.} + 2\pi (r_{IP}N_{exc.})^2 \delta(\omega) \; . \label{Pow_Spec_Poisson}
+\end{equation}
+for $P_{g_\xi}$, one gets
+\begin{equation}
+\begin{split}
+P_g(\omega) &= \frac{2}{r_{IP}N_{exc.}\tau_{nNOS}}  \left| \int_{-\infty}^{\infty} \theta(t) exp(-t/\tau_{nNOS}) exp(-i\omega t) dt \right|^2\\
+ &= \frac{2}{r_{IP}N_{exc.}\tau_{nNOS}} \frac{1}{\frac{1}{\tau_{nNOS}^2} + \omega^2}
+ \end{split} \;. \label{Pow_Spec_Exponential_Kernel}
+\end{equation}
+Since $\xi(t)$ only accounts for the fluctuations around the mean, we can remove the delta function in $P_{f_\xi}$, and get
+\begin{equation}
+P_{\xi} = \frac{2}{\tau_{nNOS}} \frac{1}{\frac{1}{\tau_{nNOS}^2} + \omega^2}
+\end{equation}
+Substituting all the intermediate results, we get
+\begin{equation}
+\small
+P_\theta(\omega) = \frac{1}{N_{exc.}r_{IP}\tau_{nNOS}^2 \left( \frac{1}{\tau_{nNOS}^2} +\omega^2 \right)\left[ \omega^2 \left( \tau_{V_t} + \frac{\alpha \tau_r}{r_{IP}(1+\omega^2\tau_r^2)}\right)^2 + \left( \omega^2 \frac{\tau_{V_t}}{\lambda} + \frac{\alpha}{r_{IP}(1+\omega^2\tau_r^2)} \right)^2 \right] } \; .\label{Pow_Spec_Theta_Final}
+\normalsize
+\end{equation}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{../../plots/power_spec/power_spectrum_analytic.png}
+\end{center}
+\caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final} for different time constants of spike rate adaption.
+Red curve is a fit by tweaking $\tau_m$,$\alpha$ and the overall amplitude of \eqref{Pow_Spec_Theta_Final}.}
+\label{Pow_Spec_Theta_vs_Analytic}
+\end{figure}
 

### 2016-12-02 draft.tex
.

@@
 \end{equation}
-
+Figure \ref{Pow_Spec_Theta_vs_Analytic} shows the result. Apart from $\mathrm{\tau_r = 20\,ms}$, the prediction underestimates the preferred frequency of oscillations and the overall amplitude.   
 \begin{figure}
@@
 \caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final} for different time constants of spike rate adaption.
-Red curve is a fit by tweaking $\tau_m$,$\alpha$ and the overall amplitude of \eqref{Pow_Spec_Theta_Final}.}
+Red curve is a fit by tweaking $\tau_r$,$\alpha$ and the overall amplitude of \eqref{Pow_Spec_Theta_Final}.
+The fit returned $\mathrm{\tau_r=54\,ms}$, $\mathrm{\alpha=-1.02\,Hz/mV}$ and a correction of amplitude by a factor of $\mathrm{13.1}$.}
 \label{Pow_Spec_Theta_vs_Analytic}
 \end{figure}
+As a reference, we fitted equation \eqref{Pow_Spec_Theta_Final} to the simulation result by means of $\mathrm{\tau_r}$, $\mathrm{\alpha}$ and an additional multiplicative correction of amplitude (dashed line in Figure \ref{Pow_Spec_Theta_vs_Analytic}).
+The result for $\mathrm{\tau_r=54\,ms}$ is in line with our prediction that the firing rate adaption of the entire network should be slower than the membrane constant $\mathrm{\tau_m=20\,ms}$.
+The underestimation of preferred frequency strongly depends on the slope of the linear rate-threshold relation: a steeper slope results in faster oscillations and vice versa.
+While the fit seen in Figure \ref{thresh_r_linfit} resulted in $\mathrm{\alpha=-0.79\,Hz/mV}$, the fit in Figure \ref{Pow_Spec_Theta_vs_Analytic} returned $\mathrm{\alpha=-1.02\,Hz/mV}$.
+This discrepancy can be at least partially explained by the fact that the linear regression overestimates the importance of a number of outliers in the range of $\mathrm{\langle V_t \rangle > 54\,mV}$, resulting in a slightly too shallow negative slope.
+However, excluding these data points from the fit still resulted in a shallower slope of $\mathrm{\alpha=-0.85\,Hz/mV}$.
 

### 2016-12-04 draft.tex
.

@@
 Returning to the question of how to describe NO synthesis in a simplified form, we note that according to equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$, which makes the mean rate of NO production over time simply $<nNOS> = <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
-More specific, if the average interspike intervals of the underlying spike generation were short compared to the decay constant $\tau_{nNOS}$, one could show that \eqref{nNOS_single_sol_approx2} approaches gaussian noise with the aforementioned mean $\mu_{nNOS}(<r>) =  <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$ and a variance of $\sigma^2_{nNOS}(<r>) = <r> \frac{{Ca^{2+}_{spike}}^6 {\tau_{Ca^{2+}}}^2 ln^2(2)}{18\tau_{nNOS}}$.
-However, for a single cell spiking at a mean firing rate of 3 Hz with approximately poissonian statistics, Figure \ref{nNOS_approx_plot} indicates that this approximation is not valid.
-Furthermore, the condition of interspike intervals to be short compared to the decay constant inherently contradicts the necessary assumptions that were taken for the previous approximations to hold.
-
-To overcome this contradiction, we introduce an idealized picture of diffusive homeostasis, where diffusion across the tissue is instantaneous.
-This simplification results in a single level of NO-concentration for all neurons, only being modified over time by the sum of all neurons' NO-syntheses and the decay term $-\lambda NO$.
-To account for the spread of NO, $nNOS(t)$ must be divided by the area $L^2$ of the tissue.
+However, for two reasons it is not sufficient to simply propose $nNOS_i(t) = r_i(t) \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
+First, a single cell fires in the range of $\mathrm{3\,Hz}$, which is - at least on the time scale of the observed oscillations - not enough to assign an "instantaneous" firing rate.
+Second, the exponential kernel of nNOS leads to a certain amount of delay between the spiking activity and the rate of NO synthesis, see Figure \ref{rate_nNOS_lag}.
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/diff_hom/rate_nNOS_close.png}
+\end{center}
+\caption{Average NO synthesis (red) lags behind the mean firing rate of the excitatory population (blue) by $\mathrm{\approx \, 0.1 \,s}$.}
+\label{rate_nNOS_lag}
+\end{figure}
+To deal with this, we introduce an idealized picture of diffusive homeostasis, where diffusion across the tissue is instantaneous.
+This simplification results in a single level of NO-concentration for all neurons, only being modified over time by the sum of all neurons' NO-syntheses $nNOS_{total}(t) \equiv \sum_{i} nNOS^i(t)$ and the decay term $-\lambda NO$.
+To account for the spread of NO, $nNOS_{total}$ must be divided by the area $L^2$ of the tissue.
+Furthermore, we introduce a random fluctuation term $\sigma_{NO} \xi(t)$ that accounts for local, momentary deviations from the mean.
 The idealized version of \eqref{NO_dyn} then reads
 \begin{equation}
-\dot{NO}(t)=-\lambda NO + \frac{\sum_{i} nNOS^i(t)}{L^2}\;.
+\dot{NO}(t)=-\lambda NO + \frac{nNOS_{total}(t)}{L^2} + \sigma_{NO} \xi(t)\;.
 \label{NO_dyn_approx}
 \end{equation}
-In this form, it becomes clear that we can now describe the \emph{total} influx of NO (the sum in \eqref{NO_dyn_approx}) as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective poisson process with a mean rate of $3 Hz \cdot N_{exc.} = \mathrm{1200\,Hz}$, given the assumption that cells are spiking weakly correlated.
+The amount of noise in the system is a hard-to-predict quantity since it depends on the spatial structure on the diffusive lattice, giving neurons that are further separated less impact on each other.
+We tried to estimate the noise level based on the same "instant spread"-simplification made in Equation \eqref{NO_dyn_approx} to describe the overall NO-dynamics.
+In the final result, this led to an underestimation of the total energy within the power spectrum.
+However, as long as we assume the noise in the system to be approximately white, noise level only acts as a global scaling factor of the shape of the power spectrum and was thus left open as a model fitting parameter.
+
+From Equation \eqref{NO_dyn_approx} it is clear why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective poisson process with a mean rate of $3 Hz \cdot N_{exc.} = \mathrm{1200\,Hz}$, given the assumption that cells are spiking weakly correlated.
 Furthermore, we argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{total} = N_{exc.}\cdot r_{exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
-Thus, equation \eqref{NO_dyn_approx} becomes
-\begin{equation}
-\dot{NO}(t)=-\lambda NO + \frac{\mu_{nNOS}(N_{exc.}r_{exc.pop.}(t)) + \sigma_{nNOS}(N_{exc.}r_{exc.pop.}(t)) \xi (t)}{L^2}\;.
-\label{NO_dyn_approx2}
-\end{equation}
+Still though, we need to address the fact that $nNOS_{total}(t)$ lags behind $r_{total}$.
+We do so by a dynamical instead of a purely functional relationship:
+\begin{equation}
+\dot{nNOS_{total}}(t) = \frac{r_{exc.pop.}\cdot N_{exc.}\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3} - nNOS_{total}}{\tau_{nNOS}}
+\label{nNOS_total_dyn}
+\end{equation} 
+where $\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$ is the integral from Equation \eqref{nNOS_single_sol_approx1}.
+
 As a next step, we attempted to simplify the dynamics of threshold adaption and its effect on the population rate.
-Since equation \eqref{NO_dyn_approx2} contains a single variable $r_{exc.pop.}(t)$ for the mean excitatory activity, we wanted to find an appropriate description containing the mean threshold $V_{t,pop.}(t) = <V_t(t)>$.
+Corresponding to the reduction to a single variable $r_{exc.pop.}(t)$ for the mean excitatory activity in equation \eqref{nNOS_total_dyn}, we wanted to find an appropriate description containing only the mean threshold $V_{t,pop.}(t) = <V_t(t)>$.
 As stated earlier, Figure \ref{rate_th_close} suggests an immediate and approximately linear relation between excitatory population rate and the mean of thresholds within the excitatory population.

### 2016-12-04 draft.tex
.

@@
 Apart from rarely appearing high values of $V_{t,pop.}$, we found a good fit to the linear model.
-However, when we color coded the slope of $V_{t,pop.}(t)$, one could see a separation of the rising phase and falling phase within the cloud of data points.
-This indicates a small (due to the "flatness" of the shape) but noticeable delay between threshold and firing rate, the latter following the former.
-We implemented this in a similar way as in Equation \eqref{2d-exc_inh_rate_1}.
-The population rate relaxates towards a value given by the fitted linear dependence on $V_{t,pop.}$ linear fit: $\dot{r_{exc.pop.}}(t) = (-r_{exc.pop.} + r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0}))/\tau_r$, where $r_{IP}$ is given in table \ref{Params_IP} as the mean excitatory target firing rate and $V_{t,0} \equiv (r_{IP}-\beta)/\alpha$ is the mean threshold corresponding to the target rate.
-We expect $\tau_r$ to be in the same order of magnitude as the membrane time constant $\tau_m$.
-However, $r_{exc.pop.}$ represents the whole excitatory population.
-Taking conduction delay and interactions with the inhibitory population into account, $\tau_r$ thus should be slightly larger.
-
+We thus expressed the population rate by $r_{exc.pop.}(t) = r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0})$, where $r_{IP}$ is given in table \ref{Params_IP} as the mean excitatory target firing rate and $V_{t,0} \equiv (r_{IP}-\beta)/\alpha$ is the mean threshold corresponding to the target rate.
 \begin{figure}
@@
 \begin{align}
-\begin{split}
-\dot{NO}(t) &= - \lambda NO + \frac{ N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}r_{exc.pop.} \\
-&+ \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{r_{exc.pop.}}\xi (t)
-\end{split}\label{2d-sys-homeostasis1}\\
+\dot{NO}(t) &= -\lambda NO + \frac{nNOS_{total}(t)}{L^2} + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis1}\\
 \dot{V_{t,pop.}}(t) &= \frac{NO-NO_0}{NO_0 \tau_{V_t}} \label{2d-sys-homeostasis2} \\
-\dot{r_{exc.pop.}}(t) &= \frac{-r_{exc.pop.}+\alpha(V_{t,pop.}(t)-V_{t,0}) + r_{IP}}{\tau_r}\;. \label{2d-sys-homeostasis3}
+\dot{nNOS_{total}}(t) &= \frac{(r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0}))\cdot N_{exc.}\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3} - nNOS_{total}}{\tau_{nNOS}}\;. \label{2d-sys-homeostasis3}
 \end{align}

### 2016-12-05 draft.tex
.

@@
 \caption{Linear fit of excitatory population activity and mean excitatory threshold.
-Slope $\alpha$ of the fit: $\mathrm{-0.772\, Hz/mV}$.
-Offset $\beta$: $\mathrm{-41.01\, Hz}$.
-Mean squared error: $\mathrm{R^2 = 0.69}$.
+Slope $\alpha$ of the fit: $\mathrm{-0.789\, Hz/mV}$.
+Offset $\beta$: $\mathrm{-41.97\, Hz}$.
+Mean squared error: $\mathrm{R^2 = 0.68}$.
 Colors encode the time derivative of $<V_t(t)>$, which indicates an ellipsoid like trajectory in phase space, with the firing rate following the threshold with a short delay.}
@@
 \end{align}
-Through the coordinate transformation $n = NO-NO_0 \; , \theta = V_{t,pop.}(t)-V_{t,0}\; , \nu = r_{exc.pop.} - r_{IP}$ we can simplify the dynamical system:
-\begin{align}
-\begin{split}
-\dot{n} &= -\lambda n + \frac{N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}\nu \\
-&+ \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{\nu + r_{IP}}\xi (t)
-\end{split}\label{2d-sys-homeostasis-coord_transf1}\\
+Through the coordinate transformations
+\begin{align}
+n &\equiv NO-NO_0 \label{simplif_coord_transf1}\\
+\theta &\equiv V_{t,pop.}(t)-V_{t,0} \label{simplif_coord_transf2}\\
+nos &\equiv nNOS_{total} - nNOS_{total,0} \label{simplif_coord_transf3}
+\end{align}
+we can simplify the dynamical system:
+\begin{align}
+\dot{n} &= -\lambda n + \frac{nos}{L^2} + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis-coord_transf1}\\
 \dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{2d-sys-homeostasis-coord_transf2} \\
-\dot{\nu} &= \frac{-\nu + \alpha \theta}{\tau_r} \label{2d-sys-homeostasis-coord_transf3}
-\end{align}
-where we have used the fact that $NO_0$ can be solved and expressed in terms of $r_{IP}$ by setting $\dot{NO}(t) = 0$.
-The amplitude of noise in equation \ref{2d-sys-homeostasis-coord_transf1} depends on $\nu$.
-Keeping this dependence in the equation turned out be an insuperable obstacle for our goal of finding an analytic description of the power spectrum of homeostatic oscillations.
-In consequence, we decided to take one further step of simplification by replacing $\sqrt{\nu + r_{IP}}$ by a constant factor $\sqrt{r_{IP}}$.
-In the following equation we use the substitutes $A\equiv \frac{N_{exc.} {Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3 L^2}$, $B\equiv \frac{{Ca^{2+}_{spike}}^3 {\tau_{Ca^{2+}}} ln(2)}{3L^2}\sqrt{\frac{N_{exc.}}{2 \tau_{nNOS}}}\sqrt{r_{IP}}$ and $C\equiv \frac{1}{NO_0 \tau_{V_t}}$, resulting in
-\begin{align}
-\dot{n} &= -\lambda n + A \nu + B \xi (t) \label{2d-sys-homeostasis-coord_transf_substitute1} \\
-\dot{\theta} &= Cn \label{2d-sys-homeostasis-coord_transf_substitute2} \\
-\dot{\nu} &= \frac{-\nu + \alpha \theta}{\tau_r} \label{2d-sys-homeostasis-coord_transf_substitute3}
+\dot{nos} &= \frac{\alpha \cdot N_{exc} \cdot \gamma \cdot \theta - nos }{\tau_{nNOS}} \label{2d-sys-homeostasis-coord_transf3}
+\end{align}
+where we have additionally used
+\begin{align}
+\gamma &\equiv \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3} \label{2d-sys-fixed-points1}\\
+NO_0 &= \frac{nNOS_{total,0}}{\lambda L^2} \label{2d-sys-fixed-points2}\\
+nNOS_{total,0} &= r_{IP}\cdot N_{exc.} \cdot \gamma \; . \label{2d-sys-fixed-points2}
 \end{align}
 As stated in the beginning, we were interested in finding an analytic expression for the power spectrum of the mean excitatory threshold.
-Therefore we took the fourier transform of \eqref{2d-sys-homeostasis-coord_transf_substitute1} and \eqref{2d-sys-homeostasis-coord_transf_substitute2}, yielding
-\begin{align}
-i\omega f_n &= - \lambda f_n + A f_\nu + B f_\xi \label{2d-sys-homeostasis-coord_transf_substitute_ft1}\\
-i\omega f_\theta &= C f_n \label{2d-sys-homeostasis-coord_transf_substitute_ft2} \\
-i\omega f_\nu &= \frac{-f_\nu + \alpha f_\theta}{\tau_r} \label{2d-sys-homeostasis-coord_transf_substitute_ft3}
+Therefore we took the fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} - \eqref{2d-sys-homeostasis-coord_transf3}, yielding
+\begin{align}
+i\omega f_n &= - \lambda f_n + \frac{f_{nos}}{L^2} + \sigma_{NO} f_{\xi} \label{2d-sys-homeostasis-coord_transf_ft1}\\
+i\omega f_\theta &= \frac{f_n}{NO_0\tau_{V_t}} \label{2d-sys-homeostasis-coord_transf_ft2} \\
+i\omega f_{nos} &= \frac{\alpha \cdot N_{exc.} \cdot \gamma f_\theta - f_{nos}}{\tau_{nNOS}} \label{2d-sys-homeostasis-coord_transf_ft3}
 \end{align}
@@
 \begin{equation}
-P_\theta (\omega) = \frac{B^2 P_\xi (\omega)}{\omega^2 \left( \frac{\lambda}{C} + \frac{A\alpha \tau_r}{1+\omega^2 \tau_r^2}\right)^2  + \left(         \frac{A\alpha}{1+\omega^2\tau_r^2} + \frac{\omega^2}{C}\right)^2}
-\end{equation}
-It was already mentioned that the statistics of $\xi(t)$ are approximately gaussian.
-However, this does not necessarily imply that its power spectrum is white.
-To find the actual power spectrum, we recall that Equation \eqref{nNOS_single_sol_approx2} can be written as a convolution:
-\begin{align}
-nNOS(t) &= \left(f \ast g\right)(t) \label{Noise_Pow_Spec_Conv1_1} \\
-f(t') &= \sum_i \delta(t' - t^i_{spike}) \label{Noise_Pow_Spec_Conv1_2} \\
-g(t') &= \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3\tau_{nNOS}} \theta(t') exp(-t'/\tau_{nNOS}) \label{Noise_Pow_Spec_Conv1_3}
-\end{align}
-Thus $\xi(t)$ is generated in the same way, namely a convolution of an exponential kernel with the same relaxation constant $\tau_{nNOS}$ and a poisson process with a rate of $N_{exc.}\cdot r_{IP}$, since it incorporates spikes from \emph{all} excitatory neurons:
-\begin{align}
-\xi (t) &= \left(f_\xi \ast g_\xi \right)(t) \label{Noise_Pow_Spec_Conv2_1} \\
-f_\xi (t') &= \sum_i \sum_{j=1}^{N_{exc.}} \delta(t' - t^{i,j}_{spike}) \label{Noise_Pow_Spec_Conv2_2} \\
-g_\xi (t') &= \sqrt{\frac{2}{r_{IP}N_{exc.}\tau_{nNOS}}} \theta(t') exp(-t'/\tau_{nNOS}) \label{Noise_Pow_Spec_Conv2_3}
-\end{align}
-where $\sqrt{\frac{2}{r_{IP}N_{exc.}\tau_{nNOS}}}$ accounts for the fact that $\xi(t)$ had a variance of one by definition. We can express the power spectrum as
-\begin{equation}
-P_{\xi} = P_{f_\xi} \cdot P_{g_\xi} \;. \label{Noise_Pow_Spec_Conv2}
-\end{equation}
-Similar to the earlier assumption that the width of the noise term is stationary, we assume that $f_\xi$ is a stationary Poisson Process with an average rate $r_{IP}N_{exc.}$.
-It thus has a power spectrum of (see e.g.
-\cite[p.
-162]{Spiking_Gerstner})
-\begin{equation}
-P_{f_\xi} (\omega) = r_{IP}N_{exc.} + 2\pi (r_{IP}N_{exc.})^2 \delta(\omega) \; . \label{Pow_Spec_Poisson}
-\end{equation}
-for $P_{g_\xi}$, one gets
-\begin{equation}
-\begin{split}
-P_g(\omega) &= \frac{2}{r_{IP}N_{exc.}\tau_{nNOS}}  \left| \int_{-\infty}^{\infty} \theta(t) exp(-t/\tau_{nNOS}) exp(-i\omega t) dt \right|^2\\
- &= \frac{2}{r_{IP}N_{exc.}\tau_{nNOS}} \frac{1}{\frac{1}{\tau_{nNOS}^2} + \omega^2}
- \end{split} \;. \label{Pow_Spec_Exponential_Kernel}
-\end{equation}
-Since $\xi(t)$ only accounts for the fluctuations around the mean, we can remove the delta function in $P_{f_\xi}$, and get
-\begin{equation}
-P_{\xi} = \frac{2}{\tau_{nNOS}} \frac{1}{\frac{1}{\tau_{nNOS}^2} + \omega^2}
-\end{equation}
-Substituting all the intermediate results, we get
-\begin{equation}
-\small
-P_\theta(\omega) = \frac{1}{N_{exc.}r_{IP}\tau_{nNOS}^2 \left( \frac{1}{\tau_{nNOS}^2} +\omega^2 \right)\left[ \omega^2 \left( \tau_{V_t} + \frac{\alpha \tau_r}{r_{IP}(1+\omega^2\tau_r^2)}\right)^2 + \left( \omega^2 \frac{\tau_{V_t}}{\lambda} + \frac{\alpha}{r_{IP}(1+\omega^2\tau_r^2)} \right)^2 \right] } \; .\label{Pow_Spec_Theta_Final}
-\normalsize
-\end{equation}
-Figure \ref{Pow_Spec_Theta_vs_Analytic} shows the result. Apart from $\mathrm{\tau_r = 20\,ms}$, the prediction underestimates the preferred frequency of oscillations and the overall amplitude.   
+P_\theta (\omega) = \frac{\sigma_{NO}^2}{\omega^2 \left( \lambda NO_0 \tau_{V_t} + \frac{\alpha N_{exc.} \gamma \tau_{nNOS}}{L^2(\omega^2\tau_{nNOS}^2 + 1)} \right)^2 + \left( \omega^2 NO_0 \tau_{V_t} + \frac{\alpha N_{exc.} \gamma}{L^2 (\omega^2\tau_{nNOS}^2 + 1)}\right)^2} \label{Pow_Spec_Theta_Final}
+\end{equation}
+Since we assumed the noise term $\xi$ to be approximately white and gaussian noise with unit variance, its power spectrum is $|f_{\xi}|^2 = 1$.
+
+Figure \ref{Pow_Spec_Theta_vs_Analytic} shows the result of \eqref{Pow_Spec_Theta_Final}. 
 \begin{figure}
 \begin{center}
-\includegraphics[width=0.8\textwidth]{../../plots/power_spec/power_spectrum_analytic.png}
+\includegraphics[width=\textwidth]{../../plots/power_spec/power_spectrum_analytic.png}
 \end{center}
-\caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final} for different time constants of spike rate adaption.
-Red curve is a fit by tweaking $\tau_r$,$\alpha$ and the overall amplitude of \eqref{Pow_Spec_Theta_Final}.
-The fit returned $\mathrm{\tau_r=54\,ms}$, $\mathrm{\alpha=-1.02\,Hz/mV}$ and a correction of amplitude by a factor of $\mathrm{13.1}$.}
+\caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final}.
+Red curve was fitted by tweaking only the overall amplitude $\sigma_{NO}$ \eqref{Pow_Spec_Theta_Final} ($\mathrm{\alpha = -0.789 \,Hz/mV}$, as in Figure \ref{thresh_r_linfit}).
+Green curve is a fit achieved by adjusting $\sigma_{NO}$ and $\alpha$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\alpha = -1.114 \,Hz/mV}$).}
 \label{Pow_Spec_Theta_vs_Analytic}
 \end{figure}
-As a reference, we fitted equation \eqref{Pow_Spec_Theta_Final} to the simulation result by means of $\mathrm{\tau_r}$, $\mathrm{\alpha}$ and an additional multiplicative correction of amplitude (dashed line in Figure \ref{Pow_Spec_Theta_vs_Analytic}).
-The result for $\mathrm{\tau_r=54\,ms}$ is in line with our prediction that the firing rate adaption of the entire network should be slower than the membrane constant $\mathrm{\tau_m=20\,ms}$.
-The underestimation of preferred frequency strongly depends on the slope of the linear rate-threshold relation: a steeper slope results in faster oscillations and vice versa.
-While the fit seen in Figure \ref{thresh_r_linfit} resulted in $\mathrm{\alpha=-0.79\,Hz/mV}$, the fit in Figure \ref{Pow_Spec_Theta_vs_Analytic} returned $\mathrm{\alpha=-1.02\,Hz/mV}$.
-This discrepancy can be at least partially explained by the fact that the linear regression overestimates the importance of a number of outliers in the range of $\mathrm{\langle V_t \rangle > 54\,mV}$, resulting in a slightly too shallow negative slope.
-However, excluding these data points from the fit still resulted in a shallower slope of $\mathrm{\alpha=-0.85\,Hz/mV}$.
-
-!!!!AB HIER NUR UNSAUBER UND UNAUSGEARBEITET!!!!
-
-A first approach in comparing the network activity before and after altering the homeostatic mechanism is by means of the distribution of firing rates within the network.
-As Sweeney et al.
-point out, it has been experimentally observed that firing rates are rather heterogeneous, resulting in a broad distribution.
-In Figure \ref{firing_rate_dist_comp} we compare our results for the firing distribution to the results by Sweeney et al..
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/firing_rate_dist_compare.eps}
-\caption{Left: Simulation results by Sweeney et al.. Right: Simulation results for the SORN.}
-\label{firing_rate_dist_comp}
-\end{figure}
-We observed a similar tendency of broader firing rate distributions for the diffusive homeostasis, though we did not get as heavy tailed statistics.
-Sweeney et al.
-found a reciprocal relation between the broadness of the firing rate distribution and the threshold distribution.
-The strong oscillations of the threshold make it difficult to estimate the threshold distribution in our case.
-For the plot in Figure \ref{thresh_dist_comp}, we calculated each neuron's time average threshold for the case of non-diffusive and diffusive homeostasis and used this as a basis for the distribution.
-In contrast to Sweeney et al., the statistics did not change significantly.
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/diff_hom/threshold_dist_compare.eps}
-\caption{Comparison of threshold distributions observed by Sweeney et al. (left) and in the SORN (right).}
-\label{thresh_dist_comp}
-\end{figure}
-
-Another possibility of characterizing neural activity is to determine the distribution of interspike intervals (ISIs).
-Using non-diffusive homeostasis, one can observe a Poisson-like spiking behaviour with a stochastic refractory period, which is typically observed in cortical networks (This is not what can be observed for the case of diffusive homeostasis: the ISI distribution reveals preference of interspike times in the range of $1s$, whereas interspike times in of $0.1-0.6s$ are less likely than a Poisson process would predict.
-This deviation matches the frequency of activity oscillations, see Figure \ref{full_sim_osci}.
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/Spike_Stats/ISI_compare_SORN.eps}
-\caption{Top: log-plot of ISI-distribution of diff. and non-diff. homeostasis in the SORN. Bottom: CV-distribution for diff and non-diff. homeostasis.}
-\label{ISI_compare}
-\end{figure}
-
-As a whole, the oscillating activity imposes a undesirable regularity onto the network's activity, see also Figure \ref{spike_sequence}.
-While this effect might be tolerable without any external input, it is likely that the oscillations will overlay and obscure network responses onto external drive, presumably making it unusable for any computational task.
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/Spike_Stats/spike_sequence.eps}
-\caption{A spike sequence of 10 randomly picked excitatory neurons of the SORN. At $t=250s$, the homeostatic mechanism is switched to the diffusive variant.}
-\label{spike_sequence}
-\end{figure}
-
-\subsection{Analysis of Sustained Oscillations}\label{theor_osc}
-
-To find an explanation for the described oscillations and a possible way of avoiding them, one has to find the necessary minimal set of mechanisms, required to explain the observed phenomenon, without oversimplifying crucial aspects of the minimal model.
-In our model, there are two aspects whose simplification is of particular importance: First, it is impossible to analytically predict every single spike within the entire network.
-Our analytical treatment therefore aims to find analytical expressions for momentary firing rates among the network.
-Second, one might speculate that the exact solution of the NO diffusion process can be simplified in favour of a model, where one describes the dynamics of the average NO concentration across the nervous tissue.
-This approach can be justified by the fact that a unified, average NO concentration is effectively equal to a very large diffusion rate.
-
-We took several approaches to find the minimal set of equations that sufficiently reproduces the desired phenomena.
-Here, we will present the final and most successful version.
-We derived the equation from the following assumptions and results:
-
-\begin{itemize}
-\item Oscillations persisted for very large diffusion constants.
-Therefore, one may assume that the dynamics of NO solely depend on the decay rate $\lambda$ and can be expressed by a single scalar variable.
-\item We observed that even though the overall activity oscillated, the total input for each neuron remained at a relatively steady level, only showing random fluctuations with periodically increasing and decreasing deviations.
-One can therefore assume that the effect of recurrent, "self-feeding" network dynamics can be neglected.
-\item The firing rate distribution has a significant variance.
-\item Since we simplified the NO dynamics to a global variable, all thresholds follow the same dynamics (apart from a variance in the initial conditions).
-We can therefore as well reduce the problem to a single average threshold variable.
-\item The phase difference between threshold and activity appears to be practically zero. It is therefore reasonable to assume a direct functional dependence $r_{pop}=r(\theta)_{pop}$.
-\item In the regime of the desired population activity of $3~Hz$, nonlinearities within the "$spike \rightarrow Ca^{2+} \rightarrow nNOS$" mechanism can be neglected in favour of a simple relation $nNOS = C\cdot r_{pop}$.
-\end{itemize}
-
-These conclusions can be transferred into the following "simple" dynamical system:
-\begin{align}
-\dot{NO} &= -\lambda NO + C\cdot r(\theta) + C\cdot \sigma \xi(t) \label{simple_NO_dyn}\\ 
-\dot{\theta} &= \frac{NO}{NO_0\cdot \tau_{\theta}} \label{simple_threshold_dyn}
-\end{align}
-Here, $\xi(t)$ represents standard gaussian noise, accounting for the fact that, apart from the regular oscillation, the population activity features a certain amount of fluctuations.
-As an additional simplification, the fixed point was set to the origin.
-
-To complete the expression, one has to find an appropriate description of the $r(\theta)$-relation.
-As a most simple approximation, we applied a linear regression to the data of the average threshold and the corresponding population activity, see Figure \ref{thresh_r_linfit}.
-The constant $C$ in equation \eqref{simple_NO_dyn} is then proportional to the slope of the linear fit.
-In addition, $C$ is proportional to the amount of NO released per spike, proportional to the number of contributing neurons and antiproportional to the total area of the tissue.
-We can solve and integrate equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} for a single spike, resulting in a total of $\tau_{Ca^{2+}}\cdot ln(1+{Ca^{2+}_{spike}}^3) / 3$.
-Therefore, $C=N_{neur}\cdot \tau_{Ca^{2+}}\cdot ln(1+{Ca^{2+}_{spike}}^3) / (3\cdot L^2)$ and $C\cdot r(\theta)=\theta \cdot \alpha \cdot N_{neur} \cdot \tau_{Ca^{2+}}\cdot ln(1+{Ca^{2+}_{spike}}^3) / (3\cdot L^2)$, where $\alpha$ is the slope of the linear fit and $L^2$ the area of the tissue.
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/diff_hom/thresh_r_linfit.eps}
-\caption{Linear fit of the relation between the firing threshold (averaged over population) and the population activity. $R^2=0.99996$.}
-
-\end{figure}
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/diff_hom/lin_model_osc.eps}
-\caption{Simulation results for equations \eqref{simple_NO_dyn} and \eqref{simple_threshold_dyn}.}
-\label{lin_mod_osc}
-\end{figure}
-Figure \ref{lin_mod_osc} shows the results achieved from the simulation. We observe that noise is capable of maintaining oscillations in an otherwise stable linear system.
-
-Is it possible to get a better understanding of the achieved dynamics?
-For that purpose, we note that equations \eqref{simple_NO_dyn} and \eqref{simple_threshold_dyn} can be transformed into the following:
-
-\begin{align}
-\dot{v} &= -\frac{\lambda}{m} v - \omega_0^2 x + \frac{C\cdot \sigma}{m} \xi (t) \label{langevin_v} \\
-\dot{x} &= v \label{langevin_x}
-\end{align}
-with $x=\theta NO_0 \tau_{\theta}$, $v=NO$, $m=1$ and $\omega_0^2 =-\frac{\alpha C}{NO_0 \tau_{\theta}}$.
-This set of equations is equal to a Langevin equation, describing a brownian particle in a harmonic potential.
-By taking the fourier transform of both equations, one can find an analytic expression for the power spectrum of the particle's location:
-\begin{equation}
-S_x (\omega) = \frac{S_\xi (\omega)}{(\omega_0^2 - \omega^2)^2 + \lambda^2 \omega^2} \label{power_spec_part}
-\end{equation}
-where, in the case of white gaussian noise, $S_\xi(\omega)=C^2 \cdot \sigma^2$. Substituting the transformations yields
-\begin{equation}
-S_\theta (\omega) = \left( \frac{C \sigma}{NO_0 \tau_\theta}\right)^2 \frac{1}{(\frac{\alpha C}{NO_0 \tau_\theta} + \omega^2)^2 + \lambda^2 \omega^2} \label{power_spec_thresh}
-\end{equation}
-By calculating the steady-state solution of equation \eqref{simple_NO_dyn}, one can analytically express the target concentration $NO_0$ as a function of the desired pop. rate $r_g$:
-\begin{equation}
-NO_0=r_g \frac{N_e \cdot \tau_{Ca^{2+}} \cdot ln(1+{Ca_{Spike}^{2+}}^3)}{3\lambda L^2} = r_g \frac{C}{\lambda}
-\label{NO_analytic}
-\end{equation} 
-Substituting into equ. \eqref{power_spec_thresh} one gets
-\begin{equation}
-S_\theta (\omega) = \frac{\sigma^2}{(\alpha+\frac{r_g \tau_\theta \omega^2}{\lambda})+\tau_\theta^2 r_g^2 \omega^2}
-\label{power_spec_thresh_r_g}
-\end{equation}
-The maximum of this function then is
-\begin{align}
-\omega_{max} &= \sqrt{-\lambda(\frac{1}{2}+\frac{\alpha}{\tau_\theta r_g})} \label{max_omega}\\
-S_\theta(\omega_{max}) &= \frac{\sigma^2}{\tau _\theta^2 r_g^2 \left(\frac{1}{4}-\frac{\lambda}{2}\right)-\alpha \lambda \tau _\theta r_g} \label{S_max_omega}
-\end{align}
-
-Figure \ref{power_spec_thresh_sim_vs_an} suggests that the theoretical result does not fully cover the dynamics of the simulation, but supports the observation of a sustained oscillation at a preferred frequency.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/power_spec/power_spectrum3}
-\caption{Power Spectrum of the firing threshold and analytic result of equation \eqref{power_spec_thresh_r_g}.}
-\label{power_spec_thresh_sim_vs_an}
-\end{figure}
-
-For the purpose of reducing the oscillations to a negligible amplitude, $\lambda$ and $\tau_\theta$ can be increased.
-Note however that increasing $\lambda$ will also increase $\omega{max}$, which will presumably result in faster oscillations.
-$\tau_\theta$ on the other hand leads to a decrease of both, $\omega_{max}$ and $S_\theta(\omega_{max})$.
-
-Since the $S_\theta(\omega)$ represents a spectral density, one should not directly relate $S_\theta(\omega_{max})$ to the actual squared amplitude of the oscillation.
-However, due to the linearity of the fourier transform, "rescaling" in the frequency spectrum also proportionally alters the amplitude of the signal in the time domain.
+Apparently, the value for $\alpha$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency.
+Partially, this can be explained by the fact that the linear regression overestimates the importance of a number of high-threshold-outliers which leads to a shallower slope than what would be appropriate for the "working point" of oscillatory behaviour.
+Another possible explanation is the fact that "instant spread" is only an approximation.
+Rather, one could picture the nitrous oxide just to fill a fraction of the available space on a short time scale by replacing $L^2$ by a smaller area.
+This leads to a stronger local increase of concentration, which eventually leads to faster oscillations.
+Either way, since these parameters always appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}, both explanations have the same effect onto the shape of the power spectrum.
+
+!!! HIER MUSS NOCH EINE ANALYSE HIN, WIE SICH DIE OSCI-AMPLITUDE MIT TAU-TH ÄNDERT !!!
+
+\subsection{Properties of Network Activity}
+
+After the elimination of oscillatory activity in the network, we further investigated the features of spiking behaviour, in particular those of the excitatory population, since these were exposed to homeostasis.
+
+Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behaviour under sparse connectivity with a relatively high per-synapse connection strength, see e.g.
+\cite{Vreeswijk1996} or \cite{Brunel2000}.
+This kind of asynchronous regular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity.
+This feature was shown to be achieved after slowing down the rate of homeostatic adaption.
+On the level of single cells, interspike intervals should be random, approximately following the statistics of a poisson process.
 

### 2016-12-06 draft.tex
.

@@
 This kind of asynchronous regular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity.
-This feature was shown to be achieved after slowing down the rate of homeostatic adaption.
+This feature was shown in the previous section after slowing down the rate of homeostatic adaption.
 On the level of single cells, interspike intervals should be random, approximately following the statistics of a poisson process.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/Spike_Stats/isi_cv_compare.png}
+\caption{A: Distribution of interspike intervals of excitatory neurons for diffusive and non-diffusive homeostasis, measured over $\mathrm{1000\,s}$.
+For diffusive homeostasis, only neurons with a mean firing rate in a certain range (see legend) were included into statistics to prevent overlapping of different firing rates.
+Black lines are fits of exponential functions.
+B: Distribution of coefficients of variation.
+Each sample represents the CV of one excitatory neuron.}
+\label{ISI_CV_compare}
+\end{figure}
+Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficient of variation ($\mathrm{CV\equiv\sigma/\mu}$), both taken over the set of excitatory neurons.
+However, in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case, we restricted the statistics of the latter one to neurons whose mean firing rate fall into a window with a width of 1 Hz.
+Apparently, an approximately exponential distribution of ISIs is preserved for diffusive homeostasis, which is characteristic for poisson processes \cite[p.
+27]{Theor_Neur_Dayan}.
+For perfect poissonian spiking, the CV should give a value of 1.
+CVs that are smaller, as seen in Figure \ref{ISI_CV_compare}, indicate a tendency towards greater regularity.
 

### 2016-12-07 draft.tex
.

--- 2016-12-05 draft.tex
@@
 This kind of asynchronous regular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity.
-This feature was shown to be achieved after slowing down the rate of homeostatic adaption.
+This feature was shown in the previous section after slowing down the rate of homeostatic adaption.
 On the level of single cells, interspike intervals should be random, approximately following the statistics of a poisson process.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/Spike_Stats/isi_cv_compare.png}
+\caption{A/C: Distribution of interspike intervals of excitatory/inhibitory neurons for diffusive and non-diffusive homeostasis, measured over $\mathrm{1000\,s}$.
+Only neurons with a mean firing rate in a certain range (see legend) were included into statistics to prevent overlap of different firing rates (except for non-diff.
+homeostasis and excitatory neurons, all being very close to 3 Hz).
+Black lines are fits of exponential functions.
+B/D: Distribution of coefficients of variation.
+Each sample represents the CV of one excitatory/inhibitory neuron.}
+\label{ISI_CV_compare}
+\end{figure}
+Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficient of variation ($\mathrm{CV\equiv\sigma/\mu}$), taken over the set of excitatory and inhibitory neurons.
+However, in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case, we restricted the statistics of ISIs to neurons whose mean firing rate fall into a window with a width of 1 Hz and a certain mean (see legend in Figure \ref{ISI_CV_compare}).
+Apparently, an approximately exponential distribution of ISIs is preserved for diffusive homeostasis (represented by straight lines in a log-plot), which is characteristic for poisson processes \cite[p.
+27]{Theor_Neur_Dayan}.
+For perfect poissonian spiking, the CV should give a value of 1.
+CVs that are smaller/larger, as seen in Figure \ref{ISI_CV_compare} B/D, indicate a tendency towards greater/less regularity.
+This is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons have an  under-representation of short ISIs, the opposite is the case for inhibitory neurons.
+These types of behaviour of LIF-models have been shown to depend on the CV of input the neuron receives \cite{Ostojic2011}: A smaller signal-to-noise-ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals, see Figure \ref{Ostojic_ISI_plot}.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/external_plots/ostojic_isi.png}
+\caption{Plot was taken from \cite{Ostojic2011}.
+Top row: sample trajectories of the membrane potential of a LIF-neuron (blue curve) and the corresponding probability density (yellow).
+From left to right, the input's CV is successively increased.
+Bottom row: the corresponding ISI distributions and the dominating exponential curve for large ISIs (red).}
+\label{Ostojic_ISI_plot}
+\end{figure}
+This relation fits nicely into our set of network parameters: inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
+This lowers the signal-to-noise ratio for the inputs of inhibitory neurons, leading to the aforementioned statistical differences.
+Still, one can observe a dominant exponential component for both excitatory and inhibitory neurons.
 

### 2016-12-10 draft.tex
.

@@
 
-After the elimination of oscillatory activity in the network, we further investigated the features of spiking behaviour, in particular those of the excitatory population, since these were exposed to homeostasis.
+After the elimination of oscillatory activity in the network, we further investigated the features of neural activity, in particular of the excitatory population, since it was exposed to homeostasis.
 
+\subsubsection{Spike-Train Statistics}
 Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behaviour under sparse connectivity with a relatively high per-synapse connection strength, see e.g.
@@
 This is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons have an  under-representation of short ISIs, the opposite is the case for inhibitory neurons.
-These types of behaviour of LIF-models have been shown to depend on the CV of input the neuron receives \cite{Ostojic2011}: A smaller signal-to-noise-ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals, see Figure \ref{Ostojic_ISI_plot}.
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/external_plots/ostojic_isi.png}
-\caption{Plot was taken from \cite{Ostojic2011}.
-Top row: sample trajectories of the membrane potential of a LIF-neuron (blue curve) and the corresponding probability density (yellow).
-From left to right, the input's CV is successively increased.
-Bottom row: the corresponding ISI distributions and the dominating exponential curve for large ISIs (red).}
-\label{Ostojic_ISI_plot}
-\end{figure}
+These types of behaviour of LIF-models have been shown to depend on the CV of input the neuron receives \cite{Ostojic2011}: A smaller signal-to-noise-ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals.
 This relation fits nicely into our set of network parameters: inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
@@
 Still, one can observe a dominant exponential component for both excitatory and inhibitory neurons.
+
+As an additional possibility of spike-train analysis, we looked at potential correlations across neurons within both populations.
+To do so, we calculated cross-correlations for all possible neuron-pairings within a population, excluding auto-correlations.
+Figure \ref{Pop_Mean_Cross_Corr} shows the mean cross-correlation taken over all these pairs.
+Surprisingly, we found a significant increase in correlation across neurons for diffusive homeostasis.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/Spike_Stats/pop_mean_cross_corr.png}
+\caption{Mean of cross correlation over all pairs of neurons in the respective neuron-group.
+Significantly higher correlation can be found in both groups for diffusive homeostasis.
+Spike data was taken from $\mathrm{1400-1500\,s}$ of the simulation.}
+\label{Pop_Mean_Cross_Corr}
+\end{figure}
+When speculating about the root of this discrepancy one could consider two possibilities: either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network.
+Regarding the first, it is certainly true that some amount of information about the activity of one neuron is transferred to another one in its neighbourhood via diffusion.
+However, due to the time scale of the homeostatic adaption, the response to fluctuations in the diffusive signal is on the order of seconds, while correlations in Figure \ref{Pop_Mean_Cross_Corr} are taking place within milliseconds.
+Thus, we concluded that a \emph{direct} link between homeostatic signalling and increased correlations can be regarded as implausible and that it must be an effect based on topological differences within the network.
+We investigate these in Section (???).
+
+In summary, we found that diffusive homeostasis does not interfere with the poisson-like spiking statistics observed on a single-cell level, but leads to an increased correlation across the neural population.
+
+\subsubsection{Distribution of Firing Rates}
+
+!!!HEAD!!!
 

### 2016-12-12 draft.tex
.

@@
 \hline
-$\mathrm{D}$ & default: 12500 $\mathrm{\mu m^2 s^{-1}}$ \\
+$\mathrm{D}$ & default: 10000 $\mathrm{\mu m^2 s^{-1}}$ \\
 \hline 
@@
 \subsubsection{Distribution of Firing Rates}
+Achieving a broad distribution of firing rates among neurons was the core motivation for the implementation of diffusive homeostasis.
+Figure \ref{Fir_Rate_Dist_Compare} shows a first result, comparing both homeostatic mechanisms.
+As expected, non-diffusive homeostasis leads to a sharp distribution of firing rates at 3 Hz.
+Diffusive homeostasis indeed results in a much broader distribution of mean firing rates.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_compare.png}
+\caption{Histograms of mean firing rates over the excitatory population, regular (A) and logarithmic space (B).
+For diffusive homeostasis ($\mathrm{D=1000\, \mu m^2 s^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
+Mean firing rates where calculated from spikes within $\mathrm{t=1000-1500\,s}$.}
+\label{Fir_Rate_Dist_Compare}
+\end{figure}
 

### 2016-12-14 draft.tex
.

@@
 \hline
-$\mathrm{D}$ & default: 10000 $\mathrm{\mu m^2 s^{-1}}$ \\
+$\mathrm{D}$ & default: 12500 $\mathrm{\mu m^2 s^{-1}}$ \\
 \hline 
@@
 \begin{figure}
+\begin{center}
 \includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_compl.png}
+\end{center}
 %\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_closeup.png}
@@
 firing threshold.
-Non-diffusive homeostasis was used for $\mathrm{0-750\, s}$ , diffusive h.
-for $\mathrm{750-1500\, s}$.
+Non-diffusive homeostasis was used for $\mathrm{0-700\, s}$ , diffusive h.
+for $\mathrm{700-1500\, s}$.
 Target activity was $\mathrm{3\, Hz}$.}
@@
 
-Describing the neural activity as instantaneous firing rates raises the question how to accurately describe the production of nitric oxide, since the outcome of equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $Ca^{2+}$ concentration caused by spike events.
+Describing the neural activity as instantaneous firing rates raises the question how to describe the production of nitric oxide, since the outcome of equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $Ca^{2+}$ concentration caused by spike events.
 Naively, one could replace the sum of dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{spike} r_i(t)$.
@@
 Returning to the question of how to describe NO synthesis in a simplified form, we note that according to equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$, which makes the mean rate of NO production over time simply $<nNOS> = <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
-However, for two reasons it is not sufficient to simply propose $nNOS_i(t) = r_i(t) \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
-First, a single cell fires in the range of $\mathrm{3\,Hz}$, which is - at least on the time scale of the observed oscillations - not enough to assign an "instantaneous" firing rate.
-Second, the exponential kernel of nNOS leads to a certain amount of delay between the spiking activity and the rate of NO synthesis, see Figure \ref{rate_nNOS_lag}.
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.7\textwidth]{../../plots/diff_hom/rate_nNOS_close.png}
-\end{center}
-\caption{Average NO synthesis (red) lags behind the mean firing rate of the excitatory population (blue) by $\mathrm{\approx \, 0.1 \,s}$.}
-\label{rate_nNOS_lag}
-\end{figure}
+However, it is not sufficient to simply propose $nNOS_i(t) = r_i(t) \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
+A single cell fires in the range of $\mathrm{3\,Hz}$, which is - at least on the time scale of the observed oscillations - not enough to assign an "instantaneous" firing rate.
+
 To deal with this, we introduce an idealized picture of diffusive homeostasis, where diffusion across the tissue is instantaneous.
@@
 Furthermore, we argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{total} = N_{exc.}\cdot r_{exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
-Still though, we need to address the fact that $nNOS_{total}(t)$ lags behind $r_{total}$.
-We do so by a dynamical instead of a purely functional relationship:
+We thus propose
 \begin{equation}
-\dot{nNOS_{total}}(t) = \frac{r_{exc.pop.}\cdot N_{exc.}\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3} - nNOS_{total}}{\tau_{nNOS}}
+nNOS_{total}(t) = r_{exc.pop.}\cdot N_{exc.}\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}
 \label{nNOS_total_dyn}
@@
 
-As a next step, we attempted to simplify the dynamics of threshold adaption and its effect on the population rate.
+As a next step, we wanted to simplify the dynamics of threshold adaption and its effect on the population rate.
 Corresponding to the reduction to a single variable $r_{exc.pop.}(t)$ for the mean excitatory activity in equation \eqref{nNOS_total_dyn}, we wanted to find an appropriate description containing only the mean threshold $V_{t,pop.}(t) = <V_t(t)>$.
@@
 Offset $\beta$: $\mathrm{-41.97\, Hz}$.
-Mean squared error: $\mathrm{R^2 = 0.68}$.
-Colors encode the time derivative of $<V_t(t)>$, which indicates an ellipsoid like trajectory in phase space, with the firing rate following the threshold with a short delay.}
+Mean squared error: $\mathrm{R^2 = 0.68}$.}
 \label{thresh_r_linfit}
@@
 \begin{align}
-\dot{NO}(t) &= -\lambda NO + \frac{nNOS_{total}(t)}{L^2} + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis1}\\
-\dot{V_{t,pop.}}(t) &= \frac{NO-NO_0}{NO_0 \tau_{V_t}} \label{2d-sys-homeostasis2} \\
-\dot{nNOS_{total}}(t) &= \frac{(r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0}))\cdot N_{exc.}\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3} - nNOS_{total}}{\tau_{nNOS}}\;. \label{2d-sys-homeostasis3}
+\dot{NO}(t) &= -\lambda NO + \frac{(r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0}))\cdot N_{exc.}\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}}{L^2} + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis1}\\
+\dot{V_{t,pop.}}(t) &= \frac{NO-NO_0}{NO_0 \tau_{V_t}}\;. \label{2d-sys-homeostasis2}
 \end{align}
@@
 \theta &\equiv V_{t,pop.}(t)-V_{t,0} \label{simplif_coord_transf2}\\
-nos &\equiv nNOS_{total} - nNOS_{total,0} \label{simplif_coord_transf3}
 \end{align}
@@
 \begin{align}
-\dot{n} &= -\lambda n + \frac{nos}{L^2} + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis-coord_transf1}\\
-\dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{2d-sys-homeostasis-coord_transf2} \\
-\dot{nos} &= \frac{\alpha \cdot N_{exc} \cdot \gamma \cdot \theta - nos }{\tau_{nNOS}} \label{2d-sys-homeostasis-coord_transf3}
+\dot{n} &= -\lambda n + \frac{\gamma \alpha N_{exc.}}{L^2}\theta + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis-coord_transf1}\\
+\dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{2d-sys-homeostasis-coord_transf2}
 \end{align}
@@
 As stated in the beginning, we were interested in finding an analytic expression for the power spectrum of the mean excitatory threshold.
-Therefore we took the fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} - \eqref{2d-sys-homeostasis-coord_transf3}, yielding
+Therefore we took the fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} and \eqref{2d-sys-homeostasis-coord_transf2}, yielding
 \begin{align}
-i\omega f_n &= - \lambda f_n + \frac{f_{nos}}{L^2} + \sigma_{NO} f_{\xi} \label{2d-sys-homeostasis-coord_transf_ft1}\\
+i\omega f_n &= - \lambda f_n + \frac{\gamma \alpha N_{exc.}}{L^2}f_\theta + \sigma_{NO} f_{\xi} \label{2d-sys-homeostasis-coord_transf_ft1}\\
 i\omega f_\theta &= \frac{f_n}{NO_0\tau_{V_t}} \label{2d-sys-homeostasis-coord_transf_ft2} \\
-i\omega f_{nos} &= \frac{\alpha \cdot N_{exc.} \cdot \gamma f_\theta - f_{nos}}{\tau_{nNOS}} \label{2d-sys-homeostasis-coord_transf_ft3}
 \end{align}
@@
 \begin{equation}
-P_\theta (\omega) = \frac{\sigma_{NO}^2}{\omega^2 \left( \lambda NO_0 \tau_{V_t} + \frac{\alpha N_{exc.} \gamma \tau_{nNOS}}{L^2(\omega^2\tau_{nNOS}^2 + 1)} \right)^2 + \left( \omega^2 NO_0 \tau_{V_t} + \frac{\alpha N_{exc.} \gamma}{L^2 (\omega^2\tau_{nNOS}^2 + 1)}\right)^2} \label{Pow_Spec_Theta_Final}
+P_\theta (\omega) = \frac{\sigma_{NO}^2}{\omega^2 NO_0^2 \tau_{V_t}^2 \lambda^2 + \left( \omega^2 NO_0 \tau_{V_t} + \frac{\gamma \alpha N_{exc.}}{L^2}\right)^2} \label{Pow_Spec_Theta_Final}
 \end{equation}
@@
 Figure \ref{Pow_Spec_Theta_vs_Analytic} shows the result of \eqref{Pow_Spec_Theta_Final}.
+Choosing noise amplitude to be the only free parameter of the model gave a rather unsatisfying result.
+Our approximation underestimated the amount of damping within the system (which controls the "peakiness" of the spectrum), as well as predicting a slightly smaller preferred amplitude.
+While the broadness of the spectrum is mostly controlled by the damping term $-\lambda$, the preferred amplitude is controlled by $\frac{\gamma \alpha N_{exc.}}{L^2}$ and $\frac{1}{NO_0\tau_{V_t}}$.
+Since the latter term was taken unaltered from the original system (apart from a shift in phase space), we added $-\lambda$ and $\alpha$ as free fitting parameters and managed to get a very good fit to the simulation data, see Figure \ref{Pow_Spec_Theta_vs_Analytic}.
 \begin{figure}
@@
 \caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final}.
-Red curve was fitted by tweaking only the overall amplitude $\sigma_{NO}$ \eqref{Pow_Spec_Theta_Final} ($\mathrm{\alpha = -0.789 \,Hz/mV}$, as in Figure \ref{thresh_r_linfit}).
-Green curve is a fit achieved by adjusting $\sigma_{NO}$ and $\alpha$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\alpha = -1.114 \,Hz/mV}$).}
+Red curve was fitted by tweaking only the overall amplitude $\mathrm{\sigma_{NO}}$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\alpha = -0.789 \,Hz/mV}$, as in Figure \ref{thresh_r_linfit}).
+Green curve is a fit achieved by adjusting $\mathrm{\sigma_{NO}}$ and $\mathrm{\lambda}$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\lambda = 0.845 \,s^{-1}}$).
+Black curve was fitted by means of $\mathrm{\sigma_{NO}}$, $\mathrm{\lambda}$ and $\mathrm{\alpha}$ ($\mathrm{\lambda = 0.592 \,s^{-1}}$, $\mathrm{\alpha=-0.989 \,Hz/mV}$).}
 \label{Pow_Spec_Theta_vs_Analytic}
 \end{figure}
-Apparently, the value for $\alpha$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency.
-Partially, this can be explained by the fact that the linear regression overestimates the importance of a number of high-threshold-outliers which leads to a shallower slope than what would be appropriate for the "working point" of oscillatory behaviour.
+The fact that the value for $\mathrm{\alpha}$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency can be partially explained by the fact that the linear regression overestimates the importance of a number of high-threshold-outliers which leads to a shallower slope than what would be appropriate for the "working point" of oscillatory behaviour.
 Another possible explanation is the fact that "instant spread" is only an approximation.
@@
 This leads to a stronger local increase of concentration, which eventually leads to faster oscillations.
-Either way, since these parameters always appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}, both explanations have the same effect onto the shape of the power spectrum.
+In either case, since these parameters appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}, both parameters have the same effect onto the shape of the power spectrum.
 
-!!! HIER MUSS NOCH EINE ANALYSE HIN, WIE SICH DIE OSCI-AMPLITUDE MIT TAU-TH ÄNDERT !!!
+Regarding the damping of the system, we can interpret   !!! SIMULATION STEHT NOCH AUS!!!
+
+In the context of the presented power spectra, reducing oscillations meant to reduce height and frequency of the peak of the spectrum.
+We managed to do so by increasing the time constant $\mathrm{\tau_{V_t}}$, as shown in Figure \ref{Peak_Prop_vs_Theta}.
+Moreover, by choosing $\mathrm{\sigma_{NO}}$, $\mathrm{\lambda}$ and $\mathrm{\alpha}$ in accordance to the fit shown in Figure \ref{Pow_Spec_Theta_vs_Analytic} (black curve), Equation \eqref{Pow_Spec_Theta_Final} provides a good prediction for the position and height of the peak.
+For proper comparison, we smoothed the curve of the simulation data in plot (A) of Figure \ref{Peak_Prop_vs_Theta} by a window of $\mathrm{[-5,5]}$ data points, since the maximum of the power spectrum of simulation data is likely to overshoot the analytic prediction due to random fluctuations.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/diff_hom/osc_ampl_vs_tau_th.png}
+\caption{A: Maximum of the spectrum-peak (see Figure \ref{Pow_Spec_Theta_vs_Analytic}).
+A smoothing window of $\mathrm{[-5,5]}$ data points around the maximum was used to reduce overestimation of the maximum due to random fluctuations.
+Blue line corresponds to Equation \eqref{Pow_Spec_Theta_Final}, fit values taken from black curve in Figure \ref{Pow_Spec_Theta_vs_Analytic}.
+B: Position of the peak on the frequency axis.
+Analytic prediction was acquired according to (A).}
+\label{Peak_Prop_vs_Theta}
+\end{figure} 
+To reduce oscillations as much as possible we eventually settled at a 1000-fold increased time constant, $\mathrm{\tau_{V_t}=2500\,s}$.
+Despite the slowness of threshold adaption, homeostasis still managed to keep excitatory network activity in the desired range, as shown in Figure \ref{full_sim_osci_slow_tau_th}.
+Despite a slight regularity of the NO-concentration, no oscillating activity occurs.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_compl_large_tau.png}
+\caption{A: Excitatory (blue) and and inhibitory (red) population rate, being controlled by diffusive homeostasis over the full simulation time.
+B,C: Mean NO-concentration over excitatory sites and mean excitatory threshold.}
+\label{full_sim_osci_slow_tau_th}
+\end{figure}
+We took this setting as a basis for further analysis of network activity.
 
@@
 After the elimination of oscillatory activity in the network, we further investigated the features of neural activity, in particular of the excitatory population, since it was exposed to homeostasis.
+This includes statistics of spike timing, as well as of heterogeneous firing rates among the network.
 
@@
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_compare.png}
-\caption{Histograms of mean firing rates over the excitatory population, regular (A) and logarithmic space (B).
+\caption{Histograms of mean firing rates over the excitatory population in regular (A) and logarithmic space (B).
 For diffusive homeostasis ($\mathrm{D=1000\, \mu m^2 s^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.

### 2016-12-14 draft.tex
.

@@
 Diffusive homeostasis indeed results in a much broader distribution of mean firing rates.
+A large number of experimental studies have found that distributions of firing rates are not only broadly distributed but well described by a log-normal distribution, which has a non-zero third moment or skewness (\cite{Buzsaki_Fir_Rates_2014}, \cite{Wohrer_Fir_Rates_2012}).
+By definition, the logarithm of the random variable in question is thus again normally distributed.
+To check for this property we plotted the the distribution of decadic logarithms of firing rates in Figure \ref{Fir_Rate_Dist_Compare} (B).
+In (A), we found a skewness of $\mathrm{v_{Diff} = 0.765}$, in (B) $\mathrm{v_{Diff,log} = -0.488}$.
+Though this told us that the distribution is "more symmetric" on a logarithmic scale, it should rather be seen as being neither strictly normally or log-normally distributed.
 \begin{figure}
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_compare.png}
-\caption{Histograms of mean firing rates over the excitatory population in regular (A) and logarithmic space (B).
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_i_compare.png}
+\caption{Histograms of mean firing rates over the excitatory/inhibitory population in regular (A/A*) and logarithmic space (B/B*).
 For diffusive homeostasis ($\mathrm{D=1000\, \mu m^2 s^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
@@
 \end{figure}
-
+In contrast, inhibitory cells showed a much clearer distinction: A skewness of $\mathrm{v_{Diff} = 1.522}$ in regular space and $\mathrm{v_{Diff,log} = -0.147}$ in log-space.
+As a first interpretation, we related this difference to the fact that inhibitory cells are only indirectly affected by diffusive homeostasis in the sense that their distribution of activity is mainly determined by differences withing neural input since inhibitory thresholds are all initialized and kept at the same value.
+
+Despite of fluctuations within the firing rate on small time scales due to the inherent nature of - approximately - random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds.
+This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: if firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates.
 !!!HEAD!!!

### 2016-12-15 draft.tex
.

@@
 \begin{center}
+%%% plot_pow_spec.py
 \includegraphics[width=0.7\textwidth]{../../plots/power_spec/power_spectrum_sim_only.png}
@@
 \end{center}
-
 \end{figure}
@@
 \mu_{AB} &= <w_{AB}> \cdot <N_{in,AB}> \cdot <r_A> \label{Noise_Approx_1}\\
-\sigma_{AB} &= \sqrt{\tau_m \cdot <w_{AB}>^2 \cdot <N_{in,AB}> \cdot <r_A>} \label{Noise_Approx_1} \, .
+\sigma_{AB} &= \sqrt{\tau_m \cdot <w_{AB}>^2 \cdot <N_{in,AB}> \cdot <r_A>} \label{Noise_Approx_2} \, .
 \end{align}
@@
 \begin{figure}
+%%% ca_nnos_test.py
 \includegraphics[width=\textwidth]{../../plots/nNOS_approx.png}
@@
 \begin{figure}
+%%% linfit_th_rate.py
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/linfit_th_rate.png}
@@
 NO_0 &= \frac{nNOS_{total,0}}{\lambda L^2} \label{2d-sys-fixed-points2}\\
-nNOS_{total,0} &= r_{IP}\cdot N_{exc.} \cdot \gamma \; . \label{2d-sys-fixed-points2}
+nNOS_{total,0} &= r_{IP}\cdot N_{exc.} \cdot \gamma \; . \label{2d-sys-fixed-points3}
 \end{align}
@@
 \begin{figure}
+%%% plot_osc_ampl_vs_tau_theta.py
 \includegraphics[width=\textwidth]{../../plots/diff_hom/osc_ampl_vs_tau_th.png}
@@
 \begin{figure}
+%%% oscillating_activity_plot_full_time_only.py
 \includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_compl_large_tau.png}
@@
 \begin{figure}
+%%% isi_plot.py
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/isi_cv_compare.png}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_compare.png}
+%%% plot_frequ_dist_mult_sets.py
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_e_compare.png}
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_i_compare.png}
@@
 This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: if firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates.
-!!!HEAD!!!
+
+A constant "rate" of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous poisson process of the same total mean firing rate.
+As bin sizes increase, possible long-term fluctuations of firing rates can then be identified as deviations from the variance one would expect from a homogeneous process.
+We tested this in Figure \ref{f_Var_vs_n_Bin}.
+(A) was taken from $\mathrm{1000-1500\,s}$, which is well inside the phase of diffusive homeostasis.
+As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{mean}\cdot n_{bins}/T_{total}}$, though slight deviations can be seen as a different factor of proportionality.
+(B) acts as an illustration showing a counterexample: here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis.
+For almost all of the neurons, this will cause a transition of firing rate between 3 Hz and a new rate different from 3 Hz.
+This inhomogeneity is represented by the increasing positive relative deviation from the dashed line for small number of bins (i.e., large bin widths), even increasing again for a very few number of bins.
+\begin{figure}
+%%% plot_spt_var_vs_bin_width.py
+\includegraphics[width=\textwidth]{../../plots/Spike_Stats/sim_f_var_vs_hom_poisson.png}
+\caption{A: Relation between Variance of the frequency signal (acquired by binning spikes) and the number of bins within the given time range of $\mathrm{1000-1500\,s}$, taken from three randomly picked excitatory neurons.
+B: Same procedure as in (A) for a randomly chosen excitatory neuron, but time range was $\mathrm{1000-1500\,s}$, which includes the initial phase of non-diffusive homeostasis.
+In both plots, dashed lines are the expected curve of a homogeneous poisson process of the same mean rate.}
+\label{f_Var_vs_n_Bin}
+\end{figure}
+We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only population-wise but on a single-cell level as well, making Figure \ref In particular, plastic modifications across the network due to STDP and synaptic growth/pruning (which where always acting for all the simulation results presented so far) appeared to be compensated for.
 

### 2016-12-17 draft.tex
.

@@
 
+Sweeney et al.
+found that diffusive homeostasis maintains broadness of firing rates across a wide range of diffusion constants but rapidly approaching zero for small values \cite[p.
+6]{Sweeney_Paper}.
+We were able to reproduce this result, see Figure \ref{Fir_Rate_Dist_Width_vs_D}.
+Homeostasis reaches a point of saturation, where faster diffusion has no effect on the heterogeneity of firing rates.
+\begin{figure}
+%%% freq_dist_width_vs_D.py
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/std_dev_vs_D_neumann.png}
+\caption{Standard deviation of firing rate distribution of excitatory neurons (neumann boundary conditions).}
+\label{Fir_Rate_Dist_Width_vs_D}
+\end{figure}
+To further quantify this dependence, we also investigated the influence of the diffusion constant onto the distribution's skewness, shown in Figure \ref{Fir_Rate_Dist_Skew_vs_D}.
+Compared to the standard deviation, we see a similar but not as clear trend with a drop for very small diffusion constants, even occasionally resulting in a left-skewed distribution (negative D-values).
+\begin{figure}
+%%% freq_dist_skew_vs_D.py
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/skew_vs_D_neumann.png}
+\caption{Skewness of firing rate distribution of excitatory neurons (neumann boundary conditions).}
+\label{Fir_Rate_Dist_Skew_vs_D}
+\end{figure}
+
+!!!HEAD!!!
+
 \section{The Firing Rate Distribution in the Network}

### 2016-12-19 draft.tex
.

@@
 In contrast, inhibitory cells showed a much clearer distinction: A skewness of $\mathrm{v_{Diff} = 1.522}$ in regular space and $\mathrm{v_{Diff,log} = -0.147}$ in log-space.
-As a first interpretation, we related this difference to the fact that inhibitory cells are only indirectly affected by diffusive homeostasis in the sense that their distribution of activity is mainly determined by differences withing neural input since inhibitory thresholds are all initialized and kept at the same value.
+As a first interpretation, we related this difference to the fact that inhibitory cells are only indirectly affected by diffusive homeostasis in the sense that their distribution of activity is mainly determined by differences withing neural input while inhibitory thresholds are all initialized and kept at the same value.
 
@@
 \end{figure}
-We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only population-wise but on a single-cell level as well, making Figure \ref In particular, plastic modifications across the network due to STDP and synaptic growth/pruning (which where always acting for all the simulation results presented so far) appeared to be compensated for.
+We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only population-wise but on a single-cell level as well.
+In particular, plastic modifications across the network due to STDP and synaptic growth/pruning - which where always acting for all the simulation results presented so far - appeared to be compensated for.
 
@@
 \end{figure}
-
-!!!HEAD!!!
+A naturally emerging question when altering the diffusion constant is how the firing rate behaves in the absolute limit of infinitely fast diffusion.
+In fact, simulation-wise this case is quite easy to simulate: one simply has  to feed all NO-sources into a single scalar variable of NO concentration.
+In particular, this will provide the same NO readout for all excitatory neurons, which means that all excitatory thresholds change at the same rate all the time.
+Since we initialized all excitatory neurons at the same threshold, only one global excitatory threshold variable had to be considered in this case.
+Figure \ref{Fir_Rate_Dist_Instant_compare} shows the distribution for this special limiting case.
+The standard deviation for the excitatory was $\mathrm{\sigma_{inst} = 1.41\, Hz}$ and the skewness $\mathrm{v_{inst} = 1.27}$ ($\mathrm{v_{inst,log} = -0.46}$), which makes the asymmetry slightly more pronounced than in Figure \ref{Fir_Rate_Dist_Compare}.
+\begin{figure}
+%%% frequ_dist_instant_diff.py
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/instant_diff_fir_dist_e.png}
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/instant_diff_fir_dist_i.png}
+\caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population. Data was taken from 2 simulations and $\mathrm{t=1000-1500\,s}$.}
+\label{Fir_Rate_Dist_Instant_compare}
+\end{figure}
+
+Summing up the results of this section, we can state that stable network activity can be achieved in the SORN with diffusive homeostasis while producing a broad distribution of firing rates within the excitatory population.
+We found that this ensemble of activity is maintained on a single cell level, each cell spiking with approximately poissonian statistics at a constant mean rate.
+The broadness of distribution could be maintained at a relatively constant level over a wide range of diffusion rates.
+However, we did not find a distribution as right skewed and heavy tailed as reported by Sweeney et al.
+and numerous experimental studies.
+
+\subsection{Network Topology}
+So far, we have only analyzed network activity, whereas in this section we present results that relate to features of synaptic topology.
+Since the SORN we used for all simulations only included plastic mechanisms affecting recurrent excitatory connections, these were the main subject of our investigations.
+Moreover, in contrast to the previous section, we did not explicitly aim for the emergence of an explicitly \emph{new} feature of synaptic topology, but rather sought to recover properties that had been found in earlier versions of the SORN.
 

### 2016-12-19 draft.tex
.

@@
 \section{Methods} \label{methods}
-\subsection{Network Simulation}
+\subsection{Network Simulation} \label{network simulation}
 
@@
 Since the SORN we used for all simulations only included plastic mechanisms affecting recurrent excitatory connections, these were the main subject of our investigations.
-Moreover, in contrast to the previous section, we did not explicitly aim for the emergence of an explicitly \emph{new} feature of synaptic topology, but rather sought to recover properties that had been found in earlier versions of the SORN.
+Moreover, in contrast to the previous section, we did not aim for the emergence of an explicitly \emph{new} feature of synaptic topology, but rather sought to recover properties that had been found in earlier versions of the SORN.
+
+\subsubsection{Excitatory Connection Fraction}
+In the previous version of the SORN, initializing the network with zero recurrent excitatory connections led to a monotonically increasing but saturating excitatory-to-excitatory connection fraction (CF).
+The growth rate was tuned such that the terminal CF settled at $\mathrm{10\%}$, see \cite[p.
+8]{SORN_Paper}.
+Omitting the distance dependence of connection probability for synaptic growth led to a slightly higher connection fraction.
+To compare these previous results to the diffusive case, we ran a full simulation under diffusive homeostasis, including the growth phase by setting the target concentration to an appropriate value that was determined in a previous simulation with non-diffusive homeostasis.
+The resulting time course of CF is depicted in Figure \ref{CF_plot}.
+\begin{figure}
+%%% plot_CF.py
+\includegraphics[width=\textwidth]{../../plots/CF_plot.png}
+\caption{Connection fractions of recurrent excitatory synapses.
+Simulation protocols include all four possible combinations of diffusive/non-diffusive homeostasis and distance-dependent/non-distance-dependent synaptic growth, each variant retained for the entire simulation time.}
+\label{CF_plot}
+\end{figure}
+To our surprise, diffusive homeostasis caused the CF to overshoot its final fraction in the growth phase.
+Eventually however, it settled at a similar equilibrium of $\mathrm{\approx 10\%}$.
+To understand this kind of behaviour, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic growth and pruning.
+The average change of connection fraction is simply proportional to the difference between newly created synapses and those that were removed.
+Though fluctuating, the synaptic growth rate was kept at a constant level of 920 synapses/second.
+In consequence, any differences in Figure \ref{CF_plot} must originate in different pruning rates.
+As explained in section \ref{network simulation}, pruning is performed once per second by collection connections that have fallen under the given weight-threshold.
+Within this second, a synaptic weight can fall below this value for two reasons: either due to multiplicative normalization or additive STDP.
+If the weight of a neuron is already very small, multiplicative changes due to normalization have a minor effect compared to weight fluctuations caused by additive STDP, drawing us to the conclusion that differences within the statistics of STDP are the potential cause for the observed overshooting of the CF.
 

### 2016-12-20 draft.tex
.

@@
 In fact, simulation-wise this case is quite easy to simulate: one simply has  to feed all NO-sources into a single scalar variable of NO concentration.
-In particular, this will provide the same NO readout for all excitatory neurons, which means that all excitatory thresholds change at the same rate all the time.
-Since we initialized all excitatory neurons at the same threshold, only one global excitatory threshold variable had to be considered in this case.
+In particular, this will provide the same NO readout for all excitatory neurons, which means that all excitatory thresholds change at the same rate all the time, only shifting their initial random distribution.
 Figure \ref{Fir_Rate_Dist_Instant_compare} shows the distribution for this special limiting case.
@@
 
-Summing up the results of this section, we can state that stable network activity can be achieved in the SORN with diffusive homeostasis while producing a broad distribution of firing rates within the excitatory population.
+Summing up the results of this section, we can state that stable network activity can be achieved in the LIF-SORN with diffusive homeostasis while producing a broad distribution of firing rates within the excitatory population.
 We found that this ensemble of activity is maintained on a single cell level, each cell spiking with approximately poissonian statistics at a constant mean rate.
@@
 Since the SORN we used for all simulations only included plastic mechanisms affecting recurrent excitatory connections, these were the main subject of our investigations.
-Moreover, in contrast to the previous section, we did not aim for the emergence of an explicitly \emph{new} feature of synaptic topology, but rather sought to recover properties that had been found in earlier versions of the SORN.
+Moreover, in contrast to the previous section, we did not aim for the emergence of an explicitly \emph{new} feature of synaptic topology, but rather sought to recover properties that had been found in earlier versions of the LIF-SORN.
 
@@
 If the weight of a neuron is already very small, multiplicative changes due to normalization have a minor effect compared to weight fluctuations caused by additive STDP, drawing us to the conclusion that differences within the statistics of STDP are the potential cause for the observed overshooting of the CF.
+Figure \ref{STDP_change} shows the mean and standard deviation of weight changes due to STDP between two normalization steps.
+Non-diffusive homeostasis has a higher mean as well as a broader distribution of weight fluctuations throughout the beginning of the simulation.
+However, the difference of mean changes is orders of magnitude smaller than the width of fluctuations.
+Thus, while it might seem counter-intuitive that a higher positive mean weight change comes with a smaller chance of synaptic survival, we attribute the main cause of overshooting in Figure \ref{CF_plot} to the increased fluctuation of weights, since it raises the chance of going below the pruning threshold within a given time interval.
+\begin{figure}
+%%% stdp_change_time.py
+\includegraphics[width=\textwidth]{../../plots/syn_topology/av_stdp_change_time.png}
+\caption{Top: Mean change of synaptic weights (growth and pruning excluded) between two normalization steps.
+Bottom: Standard deviation for the same data.
+Both curves correspond to those in Figure \ref{CF_plot} with the same color.}
+\label{STDP_change}
+\end{figure}
+Apart from reproducing the desired connection fraction, previous versions of the LIF-SORN showed an over-representation of bidirectional connections compared to a random graph with equal connectivity \cite{SORN_Paper}.
+This experimentally observed feature \cite{Markram_Connections_1997,Song_Connectivity_2005} required the presence of a distance dependent connection probability, as described in section \ref{network simulation}.
+The absence of this breaking of spatial homogeneity even led to an under-representation of bidirectional connections, which is known to be an effect of STDP in recurrent networks \cite{Syn_Plast_Abbott}.
+As shown in Figure \ref{RC_CFB_plot}, the separation between simulations with and without a spatial connection profile is retained, but a slight shift towards higher fractions of bidirectional connections is preserved over a long time.
+\begin{figure}
+%%% plot_RC_CFB.py
+\includegraphics[width=\textwidth]{../../plots/syn_topology/RC_CFB_plot.png}
+\caption{Fraction of bidirectional connections normalized over the expected fraction for a random graph with equal total connection fraction.}
+\label{RC_CFB_plot}
+\end{figure}
+\subsubsection{Distribution of Synaptic Weights}
+A very well-studied property of neural networks is the distribution of synaptic weights.
+Experimental studies in hippocampus and cortical regions suggest heavy-tailed log-normal-like distribution of synaptic efficacies \cite{Song_Connectivity_2005,Lisman_Synapses_1993,Yasumatsu_Synapses_2008,Loewenstein_Spine_Sizes}.
+Theoretical models are mainly based on a combination of multiplicative and additive weight dynamics \cite{Loewenstein_Spine_Sizes,Statman_Synapses_2014}, which is in line with our implementation of multiplicative normalization and additive STDP.
+Figure compares the resulting distributions.
+We found that we can retain a log-normal-like distribution in combination with diffusive homeostasis.
+A slightly larger variance can be observed.
+A possible explanation refers back to our observations in Figure \ref{STDP_change}: regarding STDP as a random process, a broader distribution of weights can be explained by a smaller potentiating effect and a decreased variance of STDP-fluctuations, which is both the case for diffusive homeostasis in the beginning of the simulation.
+Still, it seems unlikely that a possible effect of these differences is still present at $\mathrm{t=1500\,s}$.
+\begin{figure}
+%%% plot_weight_dist.py
+\includegraphics[width=\textwidth]{../../plots/syn_topology/syn_weight_dist.png}
+\caption{Distribution of decadic logarithm of excitatory synaptic weights at $\mathrm{t=1500\,s}$ for diffusive and non-diffusive homeostasis (both with distance-dependent connectivity).
+Gaussian fits returned $\mathrm{\mu_{diff}=-0.172\, log_{10}(mV)}$, $\mathrm{\mu_{non-diff}=-0.087\, log_{10}(mV)}$, $\mathrm{\sigma_{diff}=0.643\, log_{10}(mV)}$ and $\mathrm{\sigma_{non-diff}=0.418\, log_{10}(mV)}$.}
+\label{Weight_Dist}
+\end{figure}
+\subsubsection{Synaptic Lifetimes}
+Synaptic lifetimes have been shown to approximately follow a power law distribution in earlier versions of the LIF-SORN and binary SORN \cite{SORN_Paper,Pengsheng_2013}.
 

### 2016-12-22 draft.tex
.

@@
 %%% plot_CF.py
-\includegraphics[width=\textwidth]{../../plots/CF_plot.png}
+\includegraphics[width=\textwidth]{../../plots/syn_topology/CF_plot.png}
 \caption{Connection fractions of recurrent excitatory synapses.
@@
 \end{figure}
-To our surprise, diffusive homeostasis caused the CF to overshoot its final fraction in the growth phase.
-Eventually however, it settled at a similar equilibrium of $\mathrm{\approx 10\%}$.
+Diffusive homeostasis caused the CF to slightly overshoot its final fraction in the growth phase.
 To understand this kind of behaviour, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic growth and pruning.
@@
 In consequence, any differences in Figure \ref{CF_plot} must originate in different pruning rates.
-As explained in section \ref{network simulation}, pruning is performed once per second by collection connections that have fallen under the given weight-threshold.
-Within this second, a synaptic weight can fall below this value for two reasons: either due to multiplicative normalization or additive STDP.
-If the weight of a neuron is already very small, multiplicative changes due to normalization have a minor effect compared to weight fluctuations caused by additive STDP, drawing us to the conclusion that differences within the statistics of STDP are the potential cause for the observed overshooting of the CF.
 Figure \ref{STDP_change} shows the mean and standard deviation of weight changes due to STDP between two normalization steps.
@@
 Synaptic lifetimes have been shown to approximately follow a power law distribution in earlier versions of the LIF-SORN and binary SORN \cite{SORN_Paper,Pengsheng_2013}.
+This feature was preserved under diffusive homeostasis, as shown in Figure \ref{Syn_Lifetimes}.
+The resulting slopes are within previously reported values of $mathrm{\approx - 5/3}$ \cite{SORN_Paper}.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/syn_topology/syn_lifetimes.png}
+\caption{Distribution of recurrent excitatory synaptic lifetimes.
+Linear fits ignoring falloff for large synaptic lifetimes resulted in a slope of $\mathrm{-1.871}$ for diffusive homeostasis and $\mathrm{-1.676}$ for non-diffusive homeostasis.}
+\label{Syn_Lifetimes}
+\end{figure}
+To get an approximative explanation for the observed slope in the region of small lifetimes, we note that short synaptic lifetimes are most likely coming from synapses whose weights did not reach large values compared to the initial weight.
+In this regime of small weights, the effect of multiplicative normalization is small compared to additive STDP.
+Therefore, small weights are determined by additive quasi-random (due to their weak coupling to the postsynaptic neuron) fluctuations, which, as a very simple approximation, can be described as a brownian motion with certain standard deviation $\mathrm{\sigma}$.
+The first hitting time of this brownian motion is described by a Lévy distribution:
+\begin{equation}
+p(t,w_0,w_{prune}) = \frac{|w_0-w_{prune}|}{\sqrt{2\pi \sigma t^3}}exp \left( \frac{(w_0-w_{prune})^2}{2\sigma t}\right)
+\label{Levy_Dist}
+\end{equation}
+For larger $\mathrm{t}$, the dominating term is $\mathrm{t^{-3/2}}$, which roughly resembles the power-law exponents found in Figure \ref{Syn_Lifetimes}.
 

### 2016-12-22 draft.tex
.

@@
 \caption{Connection fractions of recurrent excitatory synapses.
-Simulation protocols include all four possible combinations of diffusive/non-diffusive homeostasis and distance-dependent/non-distance-dependent synaptic growth, each variant retained for the entire simulation time.}
+Simulation protocols include all four possible combinations of diffusive/non-diffusive homeostasis and distance-dependent/non-distance-dependent synaptic growth, each variant retained for the entire simulation time.
+Data from 10 trials, linewidth represents standard error.}
 \label{CF_plot}
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/RC_CFB_plot.png}
-\caption{Fraction of bidirectional connections normalized over the expected fraction for a random graph with equal total connection fraction.}
+\caption{Fraction of bidirectional connections normalized over the expected fraction for a random graph with equal total connection fraction. Data from 10 trials, linewidth represents standard error.}
 \label{RC_CFB_plot}
@@
 \end{figure}
+
 \subsubsection{Synaptic Lifetimes}
@@
 \begin{figure}
+%%% plot_syn_lifetimes.py
 \includegraphics[width=\textwidth]{../../plots/syn_topology/syn_lifetimes.png}
@@
 For larger $\mathrm{t}$, the dominating term is $\mathrm{t^{-3/2}}$, which roughly resembles the power-law exponents found in Figure \ref{Syn_Lifetimes}.
+
+\subsubsection{Mean outgoing Weights}
+Since we only implemented synaptic normalization for the sum of ingoing weights, the total or average strength of outgoing connections may vary from cell to cell.
+In a sense, the strength of outgoing connections per neuron can be regarded as a measure of how "influential" a neuron's activity is with respect to other neurons in the network.
+Effenberger et.
+al.
+have shown in computational studies that these "driver neurons" form highly active and interconnected subnetworks \cite{Effenberger_2015}, an observation that is backed up by experimental studies \cite{Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}.
+Figure \ref{Out_Weight_Mean_Quantile} shows that diffusive homeostasis allows for the emergence of a small group of highly influential neurons, which reproduces the findings in \cite{Effenberger_2015}.
+A comparison of statistics generated with shuffled versions of the weight matrices illustrates that above-chance exceptionally strong outgoing weights were indeed present.
+Furthermore, we noted that the difference between shuffled matrices corresponding to non-diffusive and diffusive homeostasis is in line with our observation from Figure \ref{Weight_Dist}, which indicated a broader distribution of weights for diffusive homeostasis.
+\begin{figure}
+%%% plot_sum_outgoing_weights_dist.py
+\includegraphics[width=\textwidth]{../../plots/syn_topology/outgoing_weights_distribution.png}
+\caption{Mean of outgoing weights of excitatory neurons in order sorted by magnitude.
+Dashed lines are means obtained by randomly shuffling synaptic weights.
+Data was taken from 25 weight matrices per line, representing weights within $\mathrm{t=1000-1500\,s}$.}
+\label{Out_Weight_Mean_Quantile}
+\end{figure}
+
+In contrast to our model, Effenberger et.
+al.
+identified the presence of inhibitory STDP as a necessary mechanism for the development of this feature.
+On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: it weakens inhibitory currents for some neurons, which cause these neurons to have more above-average firing rates.
+In turn, synapses between highly active presynaptic cells and postsynaptic neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
+With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies the same functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity.
+We tested this relationship by plotting mean outgoing weights against the average firing rate
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_weights_vs_rate.png}
+\end{figure}
 

### 2016-12-30 draft.tex
.

@@
 
-\subsubsection{Distribution of Firing Rates}
+\subsubsection{Distribution of Firing Rates}\label{Fir_Dist_Section}
 Achieving a broad distribution of firing rates among neurons was the core motivation for the implementation of diffusive homeostasis.
@@
 The absence of this breaking of spatial homogeneity even led to an under-representation of bidirectional connections, which is known to be an effect of STDP in recurrent networks \cite{Syn_Plast_Abbott}.
-As shown in Figure \ref{RC_CFB_plot}, the separation between simulations with and without a spatial connection profile is retained, but a slight shift towards higher fractions of bidirectional connections is preserved over a long time.
+As shown in Figure \ref{RC_CFB_plot}, the separation between simulations with and without a spatial connection profile is retained.
 \begin{figure}
@@
 With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies the same functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity.
-We tested this relationship by plotting mean outgoing weights against the average firing rate
-\begin{figure}
+We tested this relationship by plotting mean outgoing weights against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
+A strong heterogeneity of firing rates allows for the development of few strong synapses, while the resulting distribution of mean weights of a narrow distribution is limited to a smaller range.
+\begin{figure}
+%%% out_weight_vs_f.py
 \includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_weights_vs_rate.png}
-\end{figure}
-
-\section{The Firing Rate Distribution in the Network}
-
-As shown in Figure \ref{firing_rate_dist_comp}, the distribution of firing rates within the population of neurons is highly dependent on the diffusion constant $D$, in accordance to the findings by Sweeney et.
-al.
-To analyze this dependence, a dynamic mean-field approach was suggested in \cite{Sweeney_Paper}.
-In short, it consists of set of equations which need to be fulfilled self-consistently.
-
+\caption{Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{t=1200-1500\,s}$) in regular (A) and logarithmic space (B).
+Each plot corresponds to a presynaptic excitatory cell.}
+\label{Out_Weight_vs_F}
+\end{figure}
+It is interesting to note that on a logarithmic weight scale, we found a roughly linear relationship.
+Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.
+
+\section{Further Analysis of the Firing Rate Distribution}
+On a preliminary level, the results of section \ref{Fir_Dist_Section} were positive with respect to our goal of achieving a broad and skewed firing rate distribution.
+Following this, we tried to further gain insight to the actual shape of the resulting distribution.
+\subsection{Review of a Dynamic Mean-Field Model}
+Sweeney et al.
+attempted to predict the shape of the firing rate distribution by means of a simplified mean-field approximation of diffusive \cite{Sweeney_Paper}.
+The main simplification within homoestatic feedback is the replacement of Equation \ref{Theta_dyn} by
+\begin{equation}
+\dot{V_t^i}(t) = \frac{1}{\tau_{HIP}} \left( (1-\alpha)\frac{\phi_i-\phi_0}{\phi_i} +\alpha \frac{\langle \phi \rangle-\phi_0}{\langle \phi \rangle} \right)\;. 
+\label{diff_hom_simpl_sweeney}
+\end{equation}
+$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acts as a parameter that determines the "mixture" between single-neuron-homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
+$\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their overall mean.
+
+Furthermore, the spiking recurrent network was replaced by a set of non-interacting non-spiking neurons, whose individual mean firing rates were calculated by
+\begin{align}
+\phi_i(\mu_i,\sigma_i,V_t^i) &= \left[ \sqrt{\pi}\tau_m \int_{x_-}^{x_+} dx e^{x^2} erfc(-x) \right]^{-1} \label{LIF_Fir_Rate_with_Noise1_copy}\\
+x_- &= (V_r-E_l-\mu_i\tau_m)/\sigma_i \label{LIF_Fir_Rate_with_Noise2_copy}\\
+x_+ &= (V_t^i-E_l-\mu_i\tau_m)/\sigma_i \label{LIF_Fir_Rate_with_Noise3_copy}
+\end{align}
+which is the same formula we used in \eqref{LIF_Fir_Rate_with_Noise1}.
+Furthermore, in accordance to \cite{Roxin_Firing_Rate_Distribution}, mean and standard deviation of the inputs were calculated by Sweeney et al.
+as
 \begin{align}
 \nu &= \langle \phi \rangle = \frac{\sum \phi_i}{N} \label{sweeney_self_consist_rate1} \\
-\phi_i &= \phi_i(\mu_i(\nu),\sigma_i(\nu),\theta_i) \label{sweeney_self_consist_rate2} \\
-\mu_i &= J_iC_i\nu \tau \label{sweeney_self_consist_rate3} \\
-\sigma_i &= J_i\sqrt{C_i\nu  \tau} \label{sweeney_self_consist_rate4}
-\end{align}
-
-where $\nu$ is the mean population firing rate, $\phi_i$ the individual firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $\theta_i$ its synaptic input mean and standard deviation and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant.
-Self consistency is achieved by iterating through equations \eqref{sweeney_self_consist_rate1} and \eqref{sweeney_self_consist_rate2} until the desired precision is reached.
-
-As a simplification, the authors of \ref{firing_rate_dist_comp} proposed to implement diffusive homeostasis in this context by the following equation:
-
-\begin{equation}
-\frac{d\theta_i}{dt} = \frac{1}{\tau_{HIP}} \left( (1-\alpha)\frac{\phi_i-\phi_0}{\phi_i} +\alpha \frac{\langle \phi \rangle-\phi_0}{\langle \phi \rangle} \right) 
-\label{diff_hom_simpl_sweeney}
-\end{equation}
-
-$\alpha \: \epsilon \: [0,1]$ thereby acts as a parameter that determines the "mixture" between single-neuron-homeostasis ($\alpha=0$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\alpha=1$).
-
-The authors claim that this model reproduces observations in the full network, namely that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or a larger $\alpha$, respectively).
-
-However, in the following, I will argue that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, no matter what $\alpha$ is set to.
-This can be seen by setting the left hand side of equ.
-\eqref{diff_hom_simpl_sweeney} to $0$ (which is necessarily the case in the steady state) and rearranging the equation:
-
-\begin{equation}
-(\alpha-1)\frac{\phi_i - \phi_0}{\phi_i} = \alpha \frac{\langle \phi \rangle - \phi_0}{\langle \phi \rangle}
-\label{diff_hom_simpl_sweeney_3}
-\end{equation}
-
-The right term of the equation is the same for all neurons $i$.
-Since the left term is monotonic as a function of $\phi_i$, only one specific solution $\phi_i = \Phi$ for all $i$ exists that equals the given term on the right.
-Furthermore, this implies $\langle \phi \rangle = \Phi$.
-Thus,
-
-\begin{equation}
-(\alpha-1)\frac{\Phi - \phi_0}{\Phi} = \alpha \frac{\Phi - \phi_0}{\Phi}
-\label{diff_hom_simpl_sweeney_2}
-\end{equation}
-
-which is only fulfilled for $\Phi = \phi_0$.
-
-Moreover, one can argue that this result also implies a fixed distribution of thresholds in the steady state, independent of $\alpha$: Given the result above, one finds
-\begin{align}
-\phi(\mu_i(\nu),\sigma_i(\nu),\theta_i) &= \phi_0 \label{fixed_thresh_dist_argument1} \\
-\mu_i &= J_iC_i \phi_0 \tau \label{fixed_thresh_dist_argument2} \\
-\sigma_i &= J_i\sqrt{C_i \phi_0  \tau} \label{fixed_thresh_dist_argument3} \\
-\rightarrow \theta_i &= {\phi}^{-1}(J_iC_i \phi_0 \tau,J_i\sqrt{C_i \phi_0  \tau},\phi_0) \label{fixed_thresh_dist_argument4}
-\end{align}
-which implies that $\theta_i$ only depends on the given network topology.
-
-In \cite{Sweeney_Paper}, a non-interacting population of neurons was simulated while inputs where drawn randomly from a gaussian distribution supposed to model the input statistics of the full network.
-
-To verify our remarks concerning the dynamic mean field model, we simulated a similar population, but used an interacting population of neurons of the same size as in the previous simulations (400 excitatory, 80 inhibitory neurons).
+\mu_i &= J_iC_i\nu \tau \label{sweeney_self_consist_rate2} \\
+\sigma_i &= J_i\sqrt{C_i\nu  \tau} \label{sweeney_self_consist_rate3}
+\end{align}
+
+where $\nu$ is the mean population firing rate, $\phi_i$ the individual firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $V_t^i$ its synaptic input mean and standard deviation and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant.
+Synaptic efficacy and number if incoming neurons were drawn randomly to match the statistics of the actual network topology.
+Self consistency was achieved by iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate1} until the desired precision of convergence is reached.
+
+The authors claim that this model reproduces results of the full network, in particular that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or a larger $\alpha$, respectively).
+
+We tested this dynamic mean-field model by simulating a similar population, but used an interacting population of neurons of the same size as in the previous simulations (400 excitatory, 80 inhibitory neurons).
 This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $1500s$ (i.E., the "stable" phase).
-Individual values for $\mu_i$ and $\sigma_i$ where then calculated according to \eqref{sweeney_self_consist_rate3} and \eqref{sweeney_self_consist_rate4}.
+Individual values for $\mu_i$ and $\sigma_i$ where then calculated according to \eqref{sweeney_self_consist_rate2} and \eqref{sweeney_self_consist_rate3}.
 Note however that in this case the mean (input) firing rate $\nu$ also takes different values $\nu_i$ for each neuron.
 
-Instead of directly iterating through equations \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate4} (as done in \cite{Sweeney_Paper}) to fulfil self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
-
+Instead of directly iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate3} - as done in \cite{Sweeney_Paper} - to fulfil self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
 \begin{equation}
@@
 \end{equation}
-
-where $\tau_m$ is the membrane time constant.
-
-Of course, equation \eqref{sweeney_self_consist_rate1} has to be rewritten accordingly:
-
+where $\tau_m$ is the membrane time constant. Equation \eqref{sweeney_self_consist_rate1} has to be rewritten accordingly:
 \begin{equation}
@@
 \end{equation}
-
-Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics for $\alpha=0.4$ and $\alpha = 0.8$.
-Both predictions can be confirmed: All rates approach the same target rate of $3Hz$ and, apparently, thresholds move toward the same state for either choice of $\alpha$.
+In addition, we included the modulation of weights by STP through a rate-dependent prefactor by combining Equation \eqref{STP_dynamics1} and \eqref{STP_dynamics2} into rate-based equations and solving for their steady-state:
+\begin{equation}
+x_{0}\cdot u_{0} = \frac{1+r_{total,i} \tau_f}{1/U + r_{total,i} (\tau_d + \tau_f)+ r_{total,i}^2 \tau_d \tau_f}
+\label{STP_steady}
+\end{equation}
+where $\mathrm{r_{total,i}}$ is the rate of all combined spikes arriving at neuron i.
+
+Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics of excitatory rates and thresholds for $\alpha=0.4$ and $\alpha = 0.8$.
+Apparently, except for the limiting case of $\mathrm{\alpha=1}$, all rates approach the same target rate of $\mathrm{3Hz}$ and thresholds move toward the same configuration for either choice of $\alpha$.
 A significant difference only exists within the dynamics leading to the steady state.
@@
 Though, changes in the dynamics appear to be more subtle than a simple rescaling in the time domain.
-
-\begin{figure}
+\begin{figure}
+%%% plot_sim_mean_field_sweeney.py
 \includegraphics[width=\textwidth]{../../plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
-\caption{Dynamics of rates and thresholds of excitatory population of 400 Neurons (see equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).
-For both values of $\alpha$, rates and thresholds approach the same steady state.}
+\caption{Dynamics of rates (A) and thresholds (B) of excitatory population of 400 Neurons and different values of $\mathrm{\alpha}$ (see equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).}
 \label{dynamics_rate_threshold_dyn_mean_field_sweeney}
 \end{figure}
-
-\subsection{Equilibrium in the full diffusive Model}
-
-Since the previous section has proven the simplified model in \cite{Sweeney_Paper} to be incapable of maintaining a broad distribution of firing rates, turning to a more general formulation of the problem seems reasonable, especially if it includes the possibility of the "exact" description of the initial model.
+These findings led us to the conclusion that, apart from the special case $\mathrm{\alpha=1}$ (which is the equivalent to "instantaneous" diffusion), a mean-field model describing the diffusive signal as a mixture of individual activity and all neurons is not suitable for explaining the existence of stable heterogeneous distributions of rates for a broad range of diffusion constants.
+We did not intent to debase the validity of results of the mean-field model of Sweeney et al.
+However, by analysing Equation \ref{diff_hom_simpl_sweeney}, we could show that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, given any value of $\mathrm{\alpha}$ except $\mathrm{\alpha=1}$.
+This can be seen by setting the left hand side of equ.
+\eqref{diff_hom_simpl_sweeney} to $0$ (which is necessarily the case in the steady state) and rearranging the equation:
+\begin{equation}
+(\alpha-1)\frac{\phi_i - \phi_0}{\phi_i} = \alpha \frac{\langle \phi \rangle - \phi_0}{\langle \phi \rangle}
+\label{diff_hom_simpl_sweeney_2}
+\end{equation}
+The right term of the equation is the same for all neurons $i$.
+Since the left term is monotonically increasing as a function of $\phi_i$ as long as $\mathrm{\alpha<1}$, only one specific solution $\phi_i = \Phi$ for all $i$ exists that equals the given term on the right.
+Furthermore, this implies $\langle \phi \rangle = \Phi$.
+Thus,
+\begin{equation}
+(\alpha-1)\frac{\Phi - \phi_0}{\Phi} = \alpha \frac{\Phi - \phi_0}{\Phi}
+\label{diff_hom_simpl_sweeney_3}
+\end{equation}
+which is only fulfilled for $\Phi = \phi_0$.
+
+Moreover, one can argue that this result also implies a fixed distribution of thresholds in the steady state, independent of $\alpha$: Given the result above, one finds
+\begin{align}
+\phi(\mu_i(\nu),\sigma_i(\nu),V_t^i) &= \phi_0 \label{fixed_thresh_dist_argument1} \\
+\mu_i &= J_iC_i \phi_0 \tau \label{fixed_thresh_dist_argument2} \\
+\sigma_i &= J_i\sqrt{C_i \phi_0  \tau} \label{fixed_thresh_dist_argument3} \\
+\rightarrow V_t^i &= {\phi}^{-1}(J_iC_i \phi_0 \tau,J_i\sqrt{C_i \phi_0  \tau},\phi_0) \label{fixed_thresh_dist_argument4}
+\end{align}
+which implies that the set of $V_t^i$ only depends on the given network topology.
+
+\subsection{Equilibrium in the full Diffusive Model}
+Since the previous section has shown that the simplified model in \cite{Sweeney_Paper} has problems maintaining a broad distribution of firing rates, turning to a more general formulation of the problem seemed reasonable.
 
 Equation \eqref{NO_dyn} describes the full dynamics of the diffusive neurotransmitter.
-Furthermore, equation \eqref{simple_NO_dyn} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $nNOS_i = C \cdot r_i$, $r_i$ representing a neuron's rate.
-Here we would like to discuss the implications of an "in-between" simplification, only applying the second one, but retaining the diffusive term:
-
+Furthermore, equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $nNOS_i = C \cdot r_i$, $r_i$ representing a neuron's rate.
+In this section we discuss the implications of an "in-between" description, only applying the second simplification, but retaining the diffusive term:
 \begin{equation}

### 2017-01-09 draft.tex
.

@@
 This feature was preserved under diffusive homeostasis, as shown in Figure \ref{Syn_Lifetimes}.
-The resulting slopes are within previously reported values of $mathrm{\approx - 5/3}$ \cite{SORN_Paper}.
+The resulting slopes are within previously reported values of $\mathrm{\approx - 5/3}$ \cite{SORN_Paper}.
 \begin{figure}
@@
 
-Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics of excitatory rates and thresholds for $\alpha=0.4$ and $\alpha = 0.8$.
-Apparently, except for the limiting case of $\mathrm{\alpha=1}$, all rates approach the same target rate of $\mathrm{3Hz}$ and thresholds move toward the same configuration for either choice of $\alpha$.
+Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics of excitatory rates and thresholds for $\mathrm{\alpha=\lbrace 0.4,0.8,0.9,1.0\rbrace}$.
+Apparently, except for the limiting case of $\mathrm{\alpha=1}$, all rates approach the same target rate of $\mathrm{3Hz}$ and thresholds move towards the same configuration for either choice of $\mathrm{\alpha}$.
 A significant difference only exists within the dynamics leading to the steady state.
-Roughly, a smaller value of $\alpha$ leads to a faster relaxation.
-Though, changes in the dynamics appear to be more subtle than a simple rescaling in the time domain.
+Roughly, a smaller value of $\mathrm{\alpha}$ leads to a faster relaxation.
 \begin{figure}
@@
 We did not intent to debase the validity of results of the mean-field model of Sweeney et al.
-However, by analysing Equation \ref{diff_hom_simpl_sweeney}, we could show that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, given any value of $\mathrm{\alpha}$ except $\mathrm{\alpha=1}$.
+However, by analyzing Equation \ref{diff_hom_simpl_sweeney}, we could show that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, given any value of $\mathrm{\alpha}$ except $\mathrm{\alpha=1}$.
 This can be seen by setting the left hand side of equ.
@@
 \subsection{Equilibrium in the full Diffusive Model}
-Since the previous section has shown that the simplified model in \cite{Sweeney_Paper} has problems maintaining a broad distribution of firing rates, turning to a more general formulation of the problem seemed reasonable.
+Since the previous section has shown that the simplified model in \cite{Sweeney_Paper} has problems \emph{maintaining} a broad distribution of firing rates, turning to a more general formulation of the problem seemed reasonable.
 
 Equation \eqref{NO_dyn} describes the full dynamics of the diffusive neurotransmitter.
-Furthermore, equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $nNOS_i = C \cdot r_i$, $r_i$ representing a neuron's rate.
+Furthermore, equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma \cdot r_i}$, $\mathrm{r_i}$ representing a neuron's rate and $\mathrm{\gamma}$ being defined by Equation \eqref{2d-sys-fixed-points1}.
 In this section we discuss the implications of an "in-between" description, only applying the second simplification, but retaining the diffusive term:
 \begin{equation}
-\frac{dNO}{dt}(\mathbf{x},t) =-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot C \cdot r_i
+\frac{dNO}{dt}(\mathbf{x},t) =-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot \gamma \cdot r_i
 \label{simple_NO_dyn_with_diff}
@@
 As in the previous section, we ask for the steady-state distribution of rates. Thus as a first step, one needs to solve
-
-\begin{equation}
-(\lambda - D \nabla^2) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot C \cdot r_i
+\begin{equation}
+(\lambda - D \nabla^2) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot \gamma \cdot r_i
 \label{simple_NO_dyn_with_diff_equil}
 \end{equation}
-for $\lbrace r_i\rbrace$, such that
-
+for $\mathrm{\lbrace r_i\rbrace}$, such that
 \begin{equation}
@@
 \end{equation}
+At this point, we were aware of the fact that these equations completely neglect fluctuations of NO-synthesis due to spiking.
+However, given the very slow adaption of thresholds, which are responsible for changes of firing rates, we argued that noise can be neglected in the sense that $\mathrm{\lbrace r_i\rbrace}$ represents the set of mean firing rates whose resulting spike-train-induced NO-synthesis \emph{on average} fulfils \eqref{simple_NO_dyn_with_diff_equil} and \eqref{NO_equil_cond}.
+
 Equation \eqref{simple_NO_dyn_with_diff_equil} can be rewritten as
-
-\begin{equation}
-\left(\nabla^2 + \left( i\sqrt{\frac{\lambda}{D}}\right)^2\right) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot \frac{- C \cdot r_i}{D}
+\begin{equation}
+\left(\nabla^2 + \left( i\sqrt{\frac{\lambda}{D}}\right)^2\right) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot \frac{- \gamma \cdot r_i}{D}
 \label{simple_NO_dyn_with_diff_equil_helmholtz}
 \end{equation}
-Which is a two-dimensional Helmholtz equation with a superposition of (scaled) Dirac-functions.
-Thus, the solution of $NO$ is composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left of the equation.
+which is a two-dimensional Helmholtz equation with a superposition of (scaled) Dirac-functions.
+Thus, the solution of $\mathrm{NO}$ is composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left of the equation.
 For each delta function $\delta^2(\mathbf{x}-\mathbf{x}_i)$, the solution is
-
-\begin{equation}
-NO_i(\mathbf{x}) = \frac{r_i C}{2 \pi D} K_0 \left(|\mathbf{x}-\mathbf{x}_{neur,i}|\sqrt{\frac{\lambda}{D}} \right)
+\begin{equation}
+NO_i(\mathbf{x}) = \frac{r_i \gamma}{2 \pi D} K_0 \left(|\mathbf{x}-\mathbf{x}_{neur,i}|\sqrt{\frac{\lambda}{D}} \right) \equiv r_i \cdot \psi_{point}(|\mathbf{x}-\mathbf{x}_{neur,i}|)
 \label{solution_diff_equil_bessel}
 \end{equation}
-where $K_0$ is the zeroth modified Bessel function of the second kind.
-This solution reveals a fundamental problem of modelling the sources of $NO$-production as point sources: that is to say, the fact that $K_0(x)$ diverges to infinity for $x\rightarrow 0$.
+where $\mathrm{K_0}$ is the zeroth modified Bessel function of the second kind.
+This solution reveals a fundamental problem of modelling the sources of $\mathrm{NO}$-production as point sources: the fact that $\mathrm{K_0(x)}$ diverges to infinity for $\mathrm{x\rightarrow 0}$.
 It is merely due to the finite density of the numeric grid used for the simulation of the diffusion that allows for a finite target value of concentration.
-Note that this problem only occurs in the two- or three-dimensional version of the differential equation, whereas in one dimension, the fundamental solution can be expressed as an exponential function with respect to the distance to the origin, resulting in a well-defined finite value at $0$.
-
-Generally speaking, no matter how the actual shape of the numeric solution in the equilibrium at a constant production rate will look like, it is expected to be of the form
-
+Note that this problem only occurs in the two- or three-dimensional version of the differential equation, whereas in one dimension, the fundamental solution can be expressed as an exponential function with respect to the distance to the origin, resulting in a well-defined finite value at $\mathrm{x=0}$.
+
+Generally speaking, no matter how the actual shape of the numeric solution in the equilibrium at a constant production rate looks like, it is expected to be of the form
 \begin{align}
 NO_i(\mathbf{x}) &= r_i \cdot \psi (d(\mathbf{x}_{neur,i},\mathbf{x})) \label{general_diff_interaction} \\
-d(\mathbf{x},\mathbf{y}) &\equiv |\mathbf{x}-\mathbf{y}| \label{eucl_dist}
+d(\mathbf{x},\mathbf{y}) &\equiv |\mathbf{x}-\mathbf{y}| \; . \label{eucl_dist}
 \end{align}
@@
 \begin{equation}
-NO(\mathbf{x}) = \sum_i NO_i(\mathbf{x})
+NO(\mathbf{x}) = \sum_i NO_i(\mathbf{x})\;.
 \label{full_sol_diff_equil}
 \end{equation}
-
 If we define
 \begin{equation}
-\psi_{ij} = \psi_{ij} \equiv \psi (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i}))
+\psi_{ij} \equiv \psi_{ij} \equiv \psi (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i}))
 \label{interact_matrix_elements}
@@
 \hat{\psi}\mathbf{r} &= NO_0 \mathbf{n} \label{NO_equil_cond_interact_matrix_operator} \\
-\mathbf{n}&\equiv (1,1,...,1)
+\mathbf{n}&\equiv (1,1,...,1) \; .
 \end{align}
@@
 \end{equation}
-
-An example of a distribution of rates acquired from this method is shown in Figure \ref{rate_dist_interact_matrix}.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/diff_rate_solve.png}
-\caption{Distribution of the solution of \eqref{NO_euqil_cond_interact_matrix_operator_solve} with an exponential distance dependent approximation in 2d (similar to the exact solution in 1d).
-For better statistical significance, calculations where carried out for $1600$ random neurons-positions and $50$ trials in total.}
-\label{rate_dist_interact_matrix}
-\end{figure}
-
-\subsubsection{Results for an Approximation of the Numerical Steady-State Solution}
-
-If one aims for an appropriate expression for the numerical steady-state solution of a single "point"-source with a constant influx, two things should be of importance: first, it should correctly predict the concentration at the location of the source and second, it should be close to the analytic result in regions further away from the source.
-One possibility is to use the following "trick" to overcome the divergence of the analytic solution at the origin:
-
-\begin{equation}
-NO_{approx.}(d) = \frac{1}{\sqrt{\frac{1}{NO_{source,num.}^2} + \frac{1}{NO(d)^2}}}
+Still, to acquire any prediction from this model, we had to find a modified, non-diverging version of $\mathrm{\psi (d(\mathbf{x}_{neur,i},\mathbf{x}))}$ that retains the shape given by \eqref{solution_diff_equil_bessel} for larger distances but approaches the correct "numeric error"-value at the origin, determined by the spacing of the numeric grid.
+We "solved" this problem by the following expression:
+\begin{equation}
+\psi_{approx.} \equiv \frac{1}{\left(\frac{1}{\psi_0^\varepsilon} + \frac{1}{\psi_{point}^\varepsilon}\right)^{\frac{1}{\varepsilon}}}
 \label{Numeric_Solution_Expression_Trick}
 \end{equation}
-
-At the pole $NO(0)$, $NO_{approx.}(0)$ then takes the value $NO_{source,num.}$.
-On the other hand, for larger values of $r$, the term $\frac{1}{NO_{source,num.}^2}$ becomes negligible compared to $ \frac{1}{NO(d)^2}$, thus $NO_{approx.}(d) \rightarrow NO(d)$ for $d \rightarrow \infty$.
-
-To find an approximation for $NO_{source,num.}$, one can interpret this value as a mean of the analytic solution across the square area covered by the corresponding grid cell.
+where $\mathrm{\varepsilon}$ determines the "smoothness" of transition between $\mathrm{\psi}$ and the cutoff value $\mathrm{\psi_0}$.
+We chose $\varepsilon=10$ for all further calculations.
+To find an expression for $\mathrm{\psi_0}$, we took the simple approach to interpret this value as a mean of the analytic solution across the square area covered by the corresponding grid cell.
 As an additional simplification, we substitute the necessary integration over the square grid cell by a circular area of equal size around the source.
 This calculation yields
-
-\begin{equation}
-NO_{source,num.} =  r \cdot \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda} \equiv r \cdot \psi_{source,num.}
+\begin{equation}
+\psi_0 = \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda}
 \label{Numeric_Grid_Bessel_Approx}
 \end{equation}
-with $r$ being the neuron's rate. Equivalently, one can then define
-\begin{equation}
-\psi_{approx.}(d) \equiv \frac{1}{\sqrt{\frac{1}{\psi_{source,num.}^2} + \frac{1}{\psi (d)^2}}}
-\end{equation}
-
-\subsubsection{Comparison of the Solution of the Random Matrix Equation and the Simulation of the Spiking Network}
-
-\eqref{Numeric_Solution_Expression_Trick} and \eqref{Numeric_Grid_Bessel_Approx} can be used in \eqref{NO_euqil_cond_interact_matrix_operator_solve} for a more accurate description of the distance-dependent diffusive interaction.
-
-In addition, one needs to account for the boundary conditions used in the network simulation.
-We simulated the network with Neumann boundary conditions (setting the flux through the boundary to zero) as well as periodic boundaries.
+where $\mathrm{h}$ is the spatial resolution of the grid cells.
+Figure \ref{Psi_Approximation_Compare} shows a comparison between the numerically calculated solution and the expression given by \ref{Numeric_Solution_Expression_Trick}.
+As expected, the approximation fits very well for nonzero values.
+The value at the critical point at the origin is slightly underestimated by \eqref{Numeric_Grid_Bessel_Approx}, but nonetheless fits well into the overall shape.
+\begin{figure}
+%% compare_num_diff_steady_vs_analytic.py
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/Psi_Interact_Approximation.png}
+\end{center}
+\caption{Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz} (blue, $\mathrm{h=10\;\mu m}$) and its approximation (dashed) given by \eqref{Numeric_Solution_Expression_Trick}.
+The numerical simulation was carried out on a 2d-grid and the curve represents a cut through the origin in x-direction.}
+\label{Psi_Approximation_Compare}
+\end{figure}
+Thus, we took this approximation as a basis for further calculations of the "interaction" matrix $\mathrm{\hat{\psi}}$.
+
+By simply calculating all matrix elements of $\mathrm{\hat{\psi}}$ by means of Equation \eqref{interact_matrix_elements}, one would neglect the finite boundaries of the system, which would cause neurons close to the edge to "bleed" into empty space.
+This in turn would cause the solution of \eqref{NO_equil_cond_interact_matrix_operator} to contain an over-representation of high firing rates, since close-to-the-edge neurons would need to compensate for their lack of neighbours.
+Thus, we had to account for the boundary conditions used in the network simulation.
+As described in section \ref{methods}, we simulated the network mostly with Neumann boundary conditions as well as periodic boundaries.
 Both types can be modelled by extending the neurons' population through spatially shifted and mirrored versions of the base population (see Figure \ref{Bound_Cond_Patches}):
-
 \begin{itemize}
@@
 \end{itemize}
-
 \begin{figure}
@@
 \end{figure}
-
-The entries of the operator for periodic boundary conditions $\hat{\psi}_{per.}$ can now calculated by
-\begin{equation}
-\psi_{ij,per.} = \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i} + L \cdot (n_x,n_y)))
+Therefore, the entries of the operator for periodic boundary conditions $\hat{\psi}_{per.}$ could be calculated by
+\begin{equation}
+\psi_{ij,per.} = \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i} + L \cdot (n_x,n_y))) \; .
 \label{Psi_entries_periodic_bound}
 \end{equation}
-Note that the shift was applied to the second position.
-Theoretically, $n_x$,$n_y$ is iterated over all integers and in this case it is irrelevant whether to shift the first or the second position.
-For numerical calculations however, the shift was applied to the second position.
-
 For the Neumann boundary condition, one finds
@@
  \end{pmatrix}
-\mathbf{x} + L \cdot (mod(\left| n_x\right|,2),mod(\left| n_y\right|,2)) \label{Mirror_Operator}
-\end{align}
+\mathbf{x} + L \cdot (mod(\left| n_x\right|,2),mod(\left| n_y\right|,2)) \; . \label{Mirror_Operator}
+\end{align}
+Note that the shift was applied to the second position.
+Theoretically, $n_x$,$n_y$ is iterated over all integers and in this case it is irrelevant whether to shift the first or the second position.
+For numerical calculations, we obviously had to limit the amount of elements of the sum such that copies that are shifted further away can be neglected.
+\subsubsection{Comparison of the Solution of the Random Matrix Equation and the Simulation of the Spiking Network}
 

### 2017-01-10 draft.tex
.

@@
 \end{equation}
-where $\mathrm{K_0}$ is the zeroth modified Bessel function of the second kind.
+where $\mathrm{K_0}$ is the zeroth modified Bessel function of the second kind \cite{Helmholtz_Solution_2d}.
 This solution reveals a fundamental problem of modelling the sources of $\mathrm{NO}$-production as point sources: the fact that $\mathrm{K_0(x)}$ diverges to infinity for $\mathrm{x\rightarrow 0}$.
@@
 \begin{equation}
-\psi_0 = \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda}
+\psi_0 = \gamma \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda}
 \label{Numeric_Grid_Bessel_Approx}
@@
 Theoretically, $n_x$,$n_y$ is iterated over all integers and in this case it is irrelevant whether to shift the first or the second position.
-For numerical calculations, we obviously had to limit the amount of elements of the sum such that copies that are shifted further away can be neglected.
+For our calculations, we obviously had to limit the amount of elements of the sum such that copies that are shifted further away can be neglected.
 \subsubsection{Comparison of the Solution of the Random Matrix Equation and the Simulation of the Spiking Network}
+After having worked out the analytical basis, we compared the prediction obtained from numerically solving \eqref{NO_equil_cond_interact_matrix_operator} for certain spatial configurations of neurons to the steady-state firing rates of the full spiking network with the same spatial structure.
+In particular, we were interested in the quality of the predictions in respect to the choice of diffusion constant.
+Figure \ref{Rand_Matrix_Sol_vs_Sim} shows two examples: For $\mathrm{D=10\, \mu m^2 /s}$, the correlation between measured and predicted firing rates is very good.
+In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /s}$.
+Since instant diffusion overrides any spatial inhomogeneities, this represents one limiting case where our analytic model cannot make any predictions.
+The other limit shown in the plot, $\mathrm{D=0}$, is correctly predicted by the analytic model.
+However, because of the singularity of the solution, we could not quantify the correlation.
+Still, both extremes share their property of overriding the effect of spatial heterogeneity onto the firing rates.
+
+\begin{figure}
+%% plot_rand_matrix_sol_vs_sim.py
+\includegraphics[width=\textwidth]{../../plots/rates_matrix_prediction_vs_sim.png}
+\caption{Measured firing rates (t=1200-1500s) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
+For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably "large" diffusion constant of $\mathrm{D=100\, \mu m^2 /s}$.}
+\label{Rand_Matrix_Sol_vs_Sim}
+\end{figure}
 

### 2017-01-11 draft.tex
.

@@
 However, because of the singularity of the solution, we could not quantify the correlation.
-Still, both extremes share their property of overriding the effect of spatial heterogeneity onto the firing rates.
-
+Still, both extremes share their property of overriding the effect of spatial heterogeneity onto firing rates.
 \begin{figure}
@@
 \end{figure}
+Naturally, these observations led us to the question of how the correlation between predicted measured firing rates behaves in between the aforementioned extremes.
+Especially, we were interested in the \emph{range} of the diffusion constant for which our model provides a good description of the full spiking network's activity.
 

### 2017-01-12 draft.tex
.

@@
 \begin{figure}[h!]
+%% density_plot.py
 \begin{center}
@@
 \begin{figure}
+
 \begin{center}
+%% oscillating_activity_plot.py
 \includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_compl.png}
@@
 \begin{figure}
+
 \begin{center}
@@
 \begin{figure}
+%% fixed_point_net.py
 \begin{center}
@@
 \begin{figure}
+%% oscillating_activity_plot_rate_threshold.py
 \begin{center}
@@
 \begin{figure}
+%% plot_pow_spec_analytic.py
 \begin{center}
@@
 Especially, we were interested in the \emph{range} of the diffusion constant for which our model provides a good description of the full spiking network's activity.
-
-We compared the firing rate distributions acquired from the solution of the random matrix system and those of the full simulated network by means of its standard deviation and skewness.
-\begin{figure}
-\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/frequ_moments_compare.png}
-\caption{Standard deviation and skewness of firing rate distributions for the full spiking network (blue) and the solution of the random matrix model (orange) for Neumann (A,B) and periodic (C,D) boundary conditions.}
-\label{frequ_moments_compare}
-\end{figure}
-While the standard deviation appears to be better fitting the full network in the case of Neumann boundary conditions, the prediction of skewness is more accurate for periodic boundaries.
-In both versions, the standard deviation seems to be underestimated by the solution of the random matrix equation.
-This seems reasonable, considering the fact that a network of irregularly spiking neurons "naturally" provides a certain amount of firing rate variability and that during simulation, all plasticity mechanisms where kept in place (changes of presynaptic weights requires an adjustment of the internal threshold to maintain the desired firing rate).
-
-\subsubsection{Mean-Field Approximation for the Variance of Firing Rates}
-
-Generally, Mean-Field approximations reduce the calculation of a full set of interacting entities (or particles, in the context of physics) to a single instance interacting with an effective mean of the entire field, especially ignoring the influence of the single instance onto the whole set of entities and thus the field itself.
-
-In the system presented here, a single neuron with a firing rate $\nu$ must fulfil the equation
-
-\begin{equation}
-\nu =\frac{NO_0 - \sum \limits_{i} \nu_i \psi(d_i)}{\psi_0}
-\label{sample_neuron_firing_rate}
-\end{equation}
-where $i$ indexes over all "remaining" neurons and $d_i$ refers to the euclidean distance of the sample neuron to "field"-neuron $i$.
-$\psi_0$ is the factor that - multiplied with $\nu$ - yields the $NO$-concentration at the origin of the sample neuron.
-
-Depending on the constraints that one imposes onto the system, one might look for different properties to be extracted from this equation.
-Specifically, in the simulation protocol that has been used in all previous simulations, the average firing rate was forced to a certain value by means of adjusting the target concentration $NO_0$.
-A Mean-Field approximation for the average firing rate therefore is of no relevance in this particular case.
-
-However, one might try to give an estimate for the variance of the firing rate distribution in dependence of the diffusion constant $D$.
-Interpreting $\nu$ in \eqref{sample_neuron_firing_rate} as a stochastic variable, one finds
-
-\begin{equation}
-Var[\nu] = \frac{Var[\sum \limits_{i} \nu_i \psi(d_i)]}{\psi_0^2}
-\label{variance_sample_neuron_firing_rate}
-\end{equation}
-
-As an approximation, one can now replace all $\nu_i$ by the mean activity, which has been forced to a certain value $\nu_0$:
-
-\begin{equation}
-Var[\nu] = \frac{\nu_0^2 \cdot Var[\sum \limits_{i} \psi(d_i)]}{\psi_0^2}
-\label{variance_sample_neuron_firing_rate_mean_act}
-\end{equation}
-
-The random individual neurons' positions are statistically independent, therefore one gets
-
-\begin{equation}
-Var[\nu] = \frac{\nu_0^2 \cdot N \cdot Var[\psi(d)]}{\psi_0^2}
-\label{variance_sample_neuron_firing_rate_mean_act_indep_positions}
-\end{equation}
-where $N$ is the number of neurons.
-One should note however that this expression only applies to the case of open boundaries.
-Furthermore, depending on the position of the "sample neuron" relative to the population, one can achieve different statistics for $\psi(d)$.
-The limit case, in which both remarks are of no relevance, is a population of a certain density spreading across a tissue of infinite size.
+Figure \ref{Corr_Coeff_vs_D} depicts the Pearson correlation coefficient of $\mathrm{f_{matrix \\, predict}}$ and $\mathrm{f_{sim}}$ against the diffusion constant used in the simulation.
+A relatively high correlation was obtained for a wide range of diffusion constants.
+However, we could see a general decline of correlation for larger diffusion constants.
+This trend is in line with the aforementioned limit of instant diffusion, resulting in a complete decorrelation between prediction and measurement.
+Furthermore, though being rather small, a slight decorrelation could also be observed for very small diffusion constants.
+
+\begin{figure}
+%% sim_vs_matrix_solve_corr_vs_D.py
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/sim_vs_matrix_solve_corr_vs_D.png}
+\end{center}
+\caption{Pearson correlation coefficient of predicted and measured firing rates (see Figure \ref{Rand_Matrix_Sol_vs_Sim}) versus diffusion constant. Line width depicts standard error.}
+\label{Corr_Coeff_vs_D}
+\end{figure}
+
+\subsubsection{Approximation of analytic Solution by Neuronal Density}
 

### 2017-01-15 draft.tex
.

@@
 6]{Sweeney_Paper}.
-We were able to reproduce this result, see Figure \ref{Fir_Rate_Dist_Width_vs_D}.
+We were able to reproduce this result, see Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} (A).
 Homeostasis reaches a point of saturation, where faster diffusion has no effect on the heterogeneity of firing rates.
 \begin{figure}
+\begin{minipage}{0.5\textwidth}
 %%% freq_dist_width_vs_D.py
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/std_dev_vs_D_neumann.png}
-\caption{Standard deviation of firing rate distribution of excitatory neurons (neumann boundary conditions).}
-\label{Fir_Rate_Dist_Width_vs_D}
-\end{figure}
-To further quantify this dependence, we also investigated the influence of the diffusion constant onto the distribution's skewness, shown in Figure \ref{Fir_Rate_Dist_Skew_vs_D}.
-Compared to the standard deviation, we see a similar but not as clear trend with a drop for very small diffusion constants, even occasionally resulting in a left-skewed distribution (negative D-values).
-\begin{figure}
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
 %%% freq_dist_skew_vs_D.py
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/skew_vs_D_neumann.png}
-\caption{Skewness of firing rate distribution of excitatory neurons (neumann boundary conditions).}
-\label{Fir_Rate_Dist_Skew_vs_D}
-\end{figure}
+\end{minipage}
+\caption{Standard deviation (A) and skewness (B) of firing rate distribution of excitatory neurons (neumann boundary conditions).}
+\label{Fir_Rate_Dist_Width_Skewness_vs_D}
+\end{figure}
+To further quantify this dependence, we also investigated the influence of the diffusion constant onto the distribution's skewness, shown in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} (B).
+Compared to the standard deviation, we see a similar but not as clear trend with a drop for very small diffusion constants, even occasionally resulting in a left-skewed distribution (negative D-values).
+
 A naturally emerging question when altering the diffusion constant is how the firing rate behaves in the absolute limit of infinitely fast diffusion.
@@
 
-\subsubsection{Mean outgoing Weights}
+\subsubsection{Mean outgoing Weights}\label{Section_Mean_outgoing_Weights}
 Since we only implemented synaptic normalization for the sum of ingoing weights, the total or average strength of outgoing connections may vary from cell to cell.
@@
 For our calculations, we obviously had to limit the amount of elements of the sum such that copies that are shifted further away can be neglected.
-\subsubsection{Comparison of the Solution of the Random Matrix Equation and the Simulation of the Spiking Network}
+\subsubsection{Comparison of the Solution of the Random Matrix Equation and the Simulation of the Spiking Network}\label{Section_Rand_Mat_vs_Sim}
 After having worked out the analytical basis, we compared the prediction obtained from numerically solving \eqref{NO_equil_cond_interact_matrix_operator} for certain spatial configurations of neurons to the steady-state firing rates of the full spiking network with the same spatial structure.
 In particular, we were interested in the quality of the predictions in respect to the choice of diffusion constant.
-Figure \ref{Rand_Matrix_Sol_vs_Sim} shows two examples: For $\mathrm{D=10\, \mu m^2 /s}$, the correlation between measured and predicted firing rates is very good.
+Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 /s}$, the correlation between measured and predicted firing rates is very good.
 In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /s}$.
 Since instant diffusion overrides any spatial inhomogeneities, this represents one limiting case where our analytic model cannot make any predictions.
-The other limit shown in the plot, $\mathrm{D=0}$, is correctly predicted by the analytic model.
-However, because of the singularity of the solution, we could not quantify the correlation.
-Still, both extremes share their property of overriding the effect of spatial heterogeneity onto firing rates.
+The outcome of the third case shown in the plot, $\mathrm{D=0}$, is correctly predicted by the analytic model.
+In general, instant diffusion as well as $\mathrm{D=0}$ overrides the effect of spatial heterogeneity onto firing rates.
 \begin{figure}
@@
 \end{figure}
-Naturally, these observations led us to the question of how the correlation between predicted measured firing rates behaves in between the aforementioned extremes.
+As Figure \ref{Fir_Rate_Dist_Sim_vs_Mat} shows, the actual shape of the distribution is well predicted by the solution of the linear system.
+\begin{figure}
+\begin{center}
+%% fir_dist_shape_sim_matrix_compare.py
+\includegraphics[width=0.7\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}
+\end{center}
+\caption{Distribution of firing rates for $\mathrm{D=10\, \mu m^2 / ms}$, full simulation and analytic prediction. Data was taken from 10 simulation runs.}
+\label{Fir_Rate_Dist_Sim_vs_Mat}
+\end{figure}
+Naturally, these observations led us to the question of how the correlation between predicted measured firing rates behaves in between the aforementioned limits.
 Especially, we were interested in the \emph{range} of the diffusion constant for which our model provides a good description of the full spiking network's activity.
@@
 However, we could see a general decline of correlation for larger diffusion constants.
-This trend is in line with the aforementioned limit of instant diffusion, resulting in a complete decorrelation between prediction and measurement.
-Furthermore, though being rather small, a slight decorrelation could also be observed for very small diffusion constants.
-
+This trend is in line with the aforementioned limit of instant diffusion, namely a complete decorrelation between prediction and measurement, as well as the good agreement for $\mathrm{D= 10\, \mu m^2 / ms}$ shown in Figure \ref{Fir_Rate_Dist_Sim_vs_Mat}.
 \begin{figure}
@@
 \end{figure}
-
-\subsubsection{Approximation of analytic Solution by Neuronal Density}
+We characterized the dependence of the shape of the firing rate distribution onto $\mathrm{D}$ by means of its standard deviation and skewness in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.
+To test whether our analytic model predicts this dependence, we generated random ensembles of neuron positions, solved the linear system of rates and extracted the resulting standard deviation and skewness.
+Thereby, we found a good fit of the resulting histogram compared to the simulation data, see Figure \ref{Std_Skew_Dist_vs_Data}.
+\begin{figure}
+\begin{minipage}{0.5\textwidth}
+%% sim_vs_matrix_sol_standard_dev_distribution.py
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_std_dev_dist.png}
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+%% sim_vs_matrix_sol_skew_distribution.py
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_skew_dist.png}
+\end{minipage}
+\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), neumann boundaries.}
+\label{Std_Skew_Dist_vs_Data}
+\end{figure}
+In summary, the shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuation in the spatial distribution of neurons.
+Finally, to further support this result by testing, we arranged excitatory neurons on a regular grid with a nearest-neighbour distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
+By doing so, all neurons were given the same structure of neighbours.
+Due to symmetry, all neurons then should - in theory - exhibit the exact same firing rate.
+Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the result, being a significantly narrower distribution.
+This strongly supports the previous assertion.
+\begin{figure}
+\begin{center}
+%% plot_firing_rate_dist_regular_grid.py
+\includegraphics[width=0.7\textwidth]{../../plots/firing_rate_dists/regular_grid_firing_rate_dist.png}
+\end{center}
+\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and neumann boundary conditions.}
+\label{Fir_Rate_Dist_Reg_Grid}
+\end{figure}
+
+\subsubsection{Low-Density Neighbourhoods correlate with strong outgoing Connections}
+In Section \ref{Section_Mean_outgoing_Weights}, we stated that diffusive homeostasis allowed the network do develop few neurons with exceptionally strong outgoing weights.
+Furthermore, we found this effect to be present in neurons with an highly above-average firing rate.
+Moreover, the outcomes presented in Section \ref{Section_Rand_Mat_vs_Sim} suggest that the steady state of firing rates is strongly influenced by the spatial structure of excitatory neurons.
+Combining these two qualities led us the conclusion that one should be able to observe some relation between spatial structure and the emergence of "driver neurons".
 

### 2017-01-15 draft.tex
.

@@
 
-Across a square area of 1000 $\times$ 1000 $\mu m$, 400 excitatory LIF neurons and 80 inhibitory LIF neurons where assigned random positions.
-Before the start of the simulation, all but recurrent excitatory synapses where randomly generated until a desired connection fraction was reached.
+Across a square area of 1000 $\times$ 1000 $\mu m$, 400 excitatory LIF neurons and 80 inhibitory LIF neurons were assigned random positions.
+Before the start of the simulation, all but recurrent excitatory synapses were randomly generated until a desired connection fraction was reached.
 The connection probability between two neurons was calculated from a distant dependent Gaussian function with a standard deviation of 200 $\mu m$.
@@
 synapses (II).
-These connections where kept at a fixed connection strength throughout the simulation.
-Furthermore, all synapses where simulated with a fixed (distance independent) conduction delay.
+These connections were kept at a fixed connection strength throughout the simulation.
+Furthermore, all synapses were simulated with a fixed (distance independent) conduction delay.
 See table \ref{syn_conn_params} for a summary of parameters.
 
-Recurrent excitatory synapses where subject to a number of plastic mechanisms to be described in the following.
+Recurrent excitatory synapses were subject to a number of plastic mechanisms to be described in the following.
 
@@
 
-\textbf{Synaptic Pruning:} At the same rate of 1/sec, EE synapses below a threshold of 0.000001 mV where removed, thus being added again to the set of "potential" connections from which the growth process draws new connections.
+\textbf{Synaptic Pruning:} At the same rate of 1/sec, EE synapses below a threshold of 0.000001 mV were removed, thus being added again to the set of "potential" connections from which the growth process draws new connections.
 Especially, they were temporarily excluded from STDP (see below).
@@
 Indexes k and l refer to the kth and lth pre- and postsynaptic spike respectively.
-Parameters where chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
+Parameters were chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
 However, for the sake of reduction of computational effort, we used the "nearest neighbor" approximation, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
@@
 Otherwise, depending on the choice of $\tau_d$ and $\tau_f$, one can achieve a weight modulation that is dominated by potentiation ($\tau_f \gg \tau_d$) or depression ($\tau_f \ll \tau_d$).
-As a rough approximation of the values that where experimentally observed \cite{Markram_STP}, we chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$, giving it a tendency towards potentiation.
+As a rough approximation of the values that were experimentally observed \cite{Markram_STP}, we chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$, giving it a tendency towards potentiation.
 However, one should keep in mind that for $U\in [0,1]$, $x\cdot u \in [0,1]$ always holds, thus the factor $x\cdot u$ has a generally diminishing effect.
@@
 This mean was then set to be the target concentration and we switched to diffusive homeostasis.
-Table \ref{Params_IP} summarizes the choice of parameters that where introduced in this section.
+Table \ref{Params_IP} summarizes the choice of parameters that were introduced in this section.
 \begin{table}
@@
 
-If not explicitly marked differently, Neumann boundary conditions where used for most of the simulations.
+If not explicitly marked differently, Neumann boundary conditions were used for most of the simulations.
 This decision relates to the previously described mechanism of synaptic growth: Neurons placed close to the edge of the sheet have a lower connection probability due to the absence of neighbouring neurons in the direction perpendicular to the close-by border.
@@
 \caption{Dynamics of equations \ref{2d-exc_inh_rate_1} (blue line) and \ref{2d-exc_inh_rate_2} (red line).
-Dotted lines mark the mean frequencies that where present in the full spiking network.
+Dotted lines mark the mean frequencies that were present in the full spiking network.
 Excitatory: 3 Hz, Inhibitory: 6,768 Hz.
@@
 For diffusive homeostasis ($\mathrm{D=1000\, \mu m^2 s^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
-Mean firing rates where calculated from spikes within $\mathrm{t=1000-1500\,s}$.}
+Mean firing rates were calculated from spikes within $\mathrm{t=1000-1500\,s}$.}
 \label{Fir_Rate_Dist_Compare}
@@
 We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only population-wise but on a single-cell level as well.
-In particular, plastic modifications across the network due to STDP and synaptic growth/pruning - which where always acting for all the simulation results presented so far - appeared to be compensated for.
+In particular, plastic modifications across the network due to STDP and synaptic growth/pruning - which were always acting for all the simulation results presented so far - appeared to be compensated for.
 
@@
 This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $1500s$ (i.E., the "stable" phase).
-Individual values for $\mu_i$ and $\sigma_i$ where then calculated according to \eqref{sweeney_self_consist_rate2} and \eqref{sweeney_self_consist_rate3}.
+Individual values for $\mu_i$ and $\sigma_i$ were then calculated according to \eqref{sweeney_self_consist_rate2} and \eqref{sweeney_self_consist_rate3}.
 Note however that in this case the mean (input) firing rate $\nu$ also takes different values $\nu_i$ for each neuron.
@@
 \end{center}
-\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and neumann boundary conditions.}
+\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and neumann boundary conditions, $\mathrm{D=10\,\mu m^2/ms}$.}
 \label{Fir_Rate_Dist_Reg_Grid}
@@
 Combining these two qualities led us the conclusion that one should be able to observe some relation between spatial structure and the emergence of "driver neurons".
+More specific, regions of neurons with above average firing rates should develop stronger outgoing connections.
+To get an intuitive understanding of what characterizes regions of above-average firing rates, we interpreted the homeostatic condition in the high-neuron-density limit as an approximation of a continuous integral equation:
+\begin{equation}
+\int d^2 x' \rho(\mathbf{x}') r(\mathbf{x}') \psi(|\mathbf{x}-\mathbf{x}'|) = NO_0 \; , \; \forall \, \mathbf{x}
+\label{Density_Limit_Hom}
+\end{equation}
+where $\mathrm{\rho(\mathbf{x})}$ is the local neuron density and $\mathrm{r(\mathbf{x})}$ the local firing rate.
+Here, we assumed that our tissue is of infinite size and thus the integral is carried out over $\mathbb{R}^2$.
+In this form, the solution for $\mathrm{r(\mathbf{x})}$ is quite trivial:
+\begin{equation}
+r(\mathbf{x}) = \frac{NO_0}{\rho(\mathbf{x}) \int d^2 x' \psi(|\mathbf{x}'|)} \propto \frac{1}{\rho(\mathbf{x})} \; .
+\label{Density_Limit_Hom_Solution}
+\end{equation}
+Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should contain neurons with strong outgoing weights and vice versa.
+To test this hypothesis, we approximated the local neuron density by means of a a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$.
+Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} shows the results.
+Despite a certain amount of randomness, our prediction was verified.
+\begin{figure}
+\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights.png}
+\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
+\caption{(A) and (B): Scatter-plot of inverse of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights.
+Note the spatial correlation in high/low-density regions.
+(C) and (D): Decadic logarithm of outgoing weights correlates with inverse neuron density (corr.
+coeff.
+of 0.513).}
+\label{Inverse_Dens_vs_Sum_Out_Weights}
+\end{figure}
+
+\section{Discussion}
+By implementing diffusive homeostasis into the LIF-SORN model we managed to achieve a broader, skewed firing rate distribution while preserving appreciated features of network topology.
+As an additional effect, we observed the emergence of a small number of highly influential neurons, which is a feature observed in other theoretical and experimental studies.
+Section \ref{theor_osc} discussed the emergence of noise-induced oscillations.
+Suppressing this instability required homeostasis to act on a slow timescale of minutes to hours, which, however, is in accordance with experimentally observed time scales of activity modulation through nitric oxide \cite{Steinert_NO}.
+
+In general, diffusive homeostasis is regarded as a possibility of maintaining an overall level of activity, while allowing single neurons greater variability compared to single-neuron homeostasis, be it a single or individual target rates.
+According to Sweeney et al., this allows for the encoding of heterogeneous input by differences in the resulting excitatory activity.
+For this effect to be persistent, one should be able to alter the homeostatic fixed point by changes in external input.
+Our results did not support this.
+Rather, by analysing network activity and comparing it to our analytic model, we found evidence that the fixed point of network activity is strongly determined and can be well predicted by the spatial configuration of excitatory neurons.
+However, the validity of this prediction declined for larger diffusion constants and completely vanished for instant diffusion.
+In a strict sense, only instant diffusion allows for an infinite number of activity configurations that fulfil the homeostatic condition.
+However, if diffusion in a real biological system happens at a finite but fast speed compared to the adaptation of intrinsic excitability, one could arguably expect it to be equivalent to instant diffusion.
+In our simulation, we explained the fact that we saw a steady decline of correlation in Figure \ref{Corr_Coeff_vs_D} by the decreasing capability of the homeostatic mechanism to quickly enough react to structural synaptic changes that alter the recurrent excitatory inputs and, in consequence, excitatory firing rates.
+
+As an indirect consequence of spatial structure determining activity, we found that neurons with a low-density neighbourhood have a higher chance of developing strong outgoing weights.
+Of course, this raises the question, whether one can expect such an effect to be observable in the nervous system.
 

### 2017-01-16 draft.tex
.

@@
 
+As an additional test, we applied external poisson input for $\mathrm{t\geq 300\, s}$ to two excitatory subgroups to see whether changes in the firing rate of these subgroups is levelled out by homeostasis or retained.
+Members of these subgroups were picked randomly and independent of their position.
+\begin{figure}
+\begin{center}
+%% plot_external_input_switch_activity.py
+\includegraphics[width=0.7\textwidth]{../../plots/external_input_switch.png}
+\end{center}
+\caption{Excitatory population firing rate of subgroups subject to external poisson input for $\mathrm{t\geq 300\, s}$.
+Red and green subgroups consist of 100 randomly picked exc.
+neurons each.
+The remaining 300 neurons (blue) received no external input.}
+\label{Ext_Input_Switch}
+\end{figure}
+
 Sweeney et al.
@@
 \begin{figure}
+%% density_vs_sum_out_weights.py
 \includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights.png}
+%% density_vs_sum_out_weights_points.py
 \includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
@@
 Our results did not support this.
+As shown in Figure \ref{Ext_Input_Switch}, we found that diffusive homeostasis does not maintain separability of external input by the resulting firing rates.
 Rather, by analysing network activity and comparing it to our analytic model, we found evidence that the fixed point of network activity is strongly determined and can be well predicted by the spatial configuration of excitatory neurons.
@@
 In a strict sense, only instant diffusion allows for an infinite number of activity configurations that fulfil the homeostatic condition.
-However, if diffusion in a real biological system happens at a finite but fast speed compared to the adaptation of intrinsic excitability, one could arguably expect it to be equivalent to instant diffusion.
+Presumably however, if diffusion in a real biological system happens at a finite but fast speed compared to the adaptation of intrinsic excitability, one could arguably expect it to be equivalent to instant diffusion.
 In our simulation, we explained the fact that we saw a steady decline of correlation in Figure \ref{Corr_Coeff_vs_D} by the decreasing capability of the homeostatic mechanism to quickly enough react to structural synaptic changes that alter the recurrent excitatory inputs and, in consequence, excitatory firing rates.
@@
 Of course, this raises the question, whether one can expect such an effect to be observable in the nervous system.
+To our knowledge, no experimental study exists that directly relates fluctuations of neuronal densities to the existence of highly influential excitatory neurons.
+Ivenshitz and Segal studied the influence of neuronal density onto neuronal activity in a culture of hippocampal neurons \cite{Ivenshitz_2010}.
+Lower densities resulted in a more irregular activity, with stronger but less frequent bursting events.
+However, since our network was tuned to exhibit non-bursting activity, it is hard to draw any conclusions from this result.
+
+A major problem of the implemented model is the usage of quasi-point sources of nitric oxide, since it leads to a clear single homeostatic fixed point.
+Future modifications of the homeostatic model might integrate a wider-spread kernel of nNOS, allowing for a larger amount of states of activity fulfilling the homeostatic target.
+In fact, experimental and theoretical studies have suggested that NO is synthesized across wider spread cell structures, leading to a more even distribution of NO \cite{Philippides_2005}.
+
+While the implemented mathematical description of diffusion (Equation \eqref{NO_dyn}) is physically based, one can question the validity of the implementation of threshold adaption (Equation \eqref{Theta_dyn}): In principle, it does not impose any bounds onto the threshold value, which, from a biological point of view, seems implausible.
 

### 2017-01-17 draft.tex
.

@@
 Table \ref{Params_IP} summarizes the choice of parameters that were introduced in this section.
+Diffusion parameters roughly match those measured in experiments \cite{Philippides_2000}.
 \begin{table}
@@
 \section{Discussion}
+
+\subsection{Homeostatic Stability}
+Though being unintended in our recurrent network, the occurrence and necessary analysis of persistent oscillations led to a better understanding of their origin and the need for slow timescales of homeostatic adaptation.
+In another theoretical study, Harnack et al.
+treat the necessity of slow homeostatic adaptation in a more general fashion \cite{Stability_Homeostasis_Harnack_2015}.
+Among other results, it is reported that increasing the number of dynamic variables in a feedback system decreases its stability.
+This is in line with the fact that our previously used, single-cell homeostatic control (see Equation \eqref{can_hom_rate}) exhibited no instabilities, since it only incorporated firing thresholds as dynamic variables.
+In contrast, diffusive homeostasis increased the dimensionality of the system by means of its NO-synthesis and diffusion pathway.
+Additionally Harnack et al.
+report a similar effect as seen in our system: Noise can reduce stability in a damped dynamical system by constantly causing deviations from its fixed point.
+
+\subsection{The Firing Rate Distribution}
 By implementing diffusive homeostasis into the LIF-SORN model we managed to achieve a broader, skewed firing rate distribution while preserving appreciated features of network topology.
-As an additional effect, we observed the emergence of a small number of highly influential neurons, which is a feature observed in other theoretical and experimental studies.
-Section \ref{theor_osc} discussed the emergence of noise-induced oscillations.
-Suppressing this instability required homeostasis to act on a slow timescale of minutes to hours, which, however, is in accordance with experimentally observed time scales of activity modulation through nitric oxide \cite{Steinert_NO}.
-
-In general, diffusive homeostasis is regarded as a possibility of maintaining an overall level of activity, while allowing single neurons greater variability compared to single-neuron homeostasis, be it a single or individual target rates.
-According to Sweeney et al., this allows for the encoding of heterogeneous input by differences in the resulting excitatory activity.
-For this effect to be persistent, one should be able to alter the homeostatic fixed point by changes in external input.
-Our results did not support this.
-As shown in Figure \ref{Ext_Input_Switch}, we found that diffusive homeostasis does not maintain separability of external input by the resulting firing rates.
-Rather, by analysing network activity and comparing it to our analytic model, we found evidence that the fixed point of network activity is strongly determined and can be well predicted by the spatial configuration of excitatory neurons.
-However, the validity of this prediction declined for larger diffusion constants and completely vanished for instant diffusion.
-In a strict sense, only instant diffusion allows for an infinite number of activity configurations that fulfil the homeostatic condition.
-Presumably however, if diffusion in a real biological system happens at a finite but fast speed compared to the adaptation of intrinsic excitability, one could arguably expect it to be equivalent to instant diffusion.
-In our simulation, we explained the fact that we saw a steady decline of correlation in Figure \ref{Corr_Coeff_vs_D} by the decreasing capability of the homeostatic mechanism to quickly enough react to structural synaptic changes that alter the recurrent excitatory inputs and, in consequence, excitatory firing rates.
-
-As an indirect consequence of spatial structure determining activity, we found that neurons with a low-density neighbourhood have a higher chance of developing strong outgoing weights.
-Of course, this raises the question, whether one can expect such an effect to be observable in the nervous system.
-To our knowledge, no experimental study exists that directly relates fluctuations of neuronal densities to the existence of highly influential excitatory neurons.
-Ivenshitz and Segal studied the influence of neuronal density onto neuronal activity in a culture of hippocampal neurons \cite{Ivenshitz_2010}.
+Though the distribution did approximately resemble a log-normal-like shape, it did not perfectly match our expectations.
+In order to acquire a deeper understanding of the mechanisms that determine these statistics, we developed analytical expression that allowed us to reliably predict the steady-state of firing rates based on the spatial structure of excitatory neurons.
+We would like to emphasize that this explanation differs from common approaches to understand the emergence of heavy-tailed statistics of firing rates in recurrent networks.
+Theoretical studies on the behaviour of recurrent networks are largely based on the assumption that the excitability of neurons is not individually tuned but rather adjusted globally to achieve a desired mean firing rate.
+Predictions about the resulting activity are then made based on (potentially simplified) statistical features of recurrent connectivity and the specific form of the neuronal transfer function used in the model, see e.g.
+\cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998}.
+Our interpretation of our results leads to the conclusion that this "canonical" approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal much differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behaviour.
+
+Sweeney et al.
+claim that their implementation of diffusive homeostasis enables individual neurons to vary their firing rates more flexible compared to single-neuron homeostatic models, especially allowing for sustained encoding of different levels of external input.
+Interestingly, we could not confirm this, at least within the tests that we performed and the given set of standard parameters.
+Overall, the resulting behaviour of the excitatory population rather appeared to us as a form of single-neuron homeostasis whose individual targets are predetermined by the quenched random spatial structure of the respective cells.
+Of course, this impression only applies to the case where the aforementioned mixture of influence between spatial and synaptic topology is dominated by the former.
+In particular, our result depicted in Figure \ref{Ext_Input_Switch} did not support the notion of separability of inputs.
+Furthermore, by analyzing network activity and comparing it to our analytic model, we found that only one particular homeostatic fixed point of network activity is exists.
+
+For the standard choice of parameters (being roughly based on experimental data), the resulting activity is indeed strongly bound to the spatial structure of the cells.
+Naturally, this raises the question of biological plausibility.
+To our knowledge, no experimental study exists that relates measurements of spontaneous activity to local fluctuations of neuronal density.
+Ivenshitz and Segal studied the influence of (mean) neuronal density onto neuronal activity in a culture of hippocampal neurons \cite{Ivenshitz_2010}.
 Lower densities resulted in a more irregular activity, with stronger but less frequent bursting events.
 However, since our network was tuned to exhibit non-bursting activity, it is hard to draw any conclusions from this result.
+
+From a more general perspective, one could argue that a mechanism binding firing rates to spatial constraints suppresses the ability of the system to adapt to a changing environment since it essentially "freezes" the state of activity.
+However, experiments have shown that neurons' firing rates are indeed correlated under a changing environment/task: Neurons with a certain baseline-firing rate are very likely to have a similar firing rate while performing a task \cite{Buzsaki_Fir_Rates_2014}.
+While homeostatic fixation might not be problematic in the case of transient changes of stimuli, a spatial fixation of firing rates would presumably contradict the fact that long-term learning processes and plasticity lead to persistent changes in activity patterns \cite{Lever_Long_Term_Plast_2002}.
+
+As an indirect consequence of spatial structure determining activity, we found that neurons with a low-density neighbourhood have a higher chance of developing strong outgoing weights.
+Since this effect is directly linked to the low density-high firing rate-relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D).
+
+  If diffusion in a real biological system happens at a finite but fast speed compared to the adaptation of intrinsic excitability, one could arguably expect it to be equivalent to instant diffusion.
+In our simulation, we explained the fact that we saw a steady decline of correlation in Figure \ref{Corr_Coeff_vs_D} by the decreasing capability of the homeostatic mechanism to quickly enough react to structural synaptic changes that alter the recurrent excitatory inputs and, in consequence, excitatory firing rates.
 

### 2017-01-18 draft.tex
.

@@
 Members of these subgroups were picked randomly and independent of their position.
+As shown in Figure \ref{Ext_Input_Switch}, differences in among subgroups caused by different input signal strengths are gradually eliminated by the homeostatic mechanism.
 \begin{figure}
@@
 Figure \ref{Fir_Rate_Dist_Instant_compare} shows the distribution for this special limiting case.
-The standard deviation for the excitatory was $\mathrm{\sigma_{inst} = 1.41\, Hz}$ and the skewness $\mathrm{v_{inst} = 1.27}$ ($\mathrm{v_{inst,log} = -0.46}$), which makes the asymmetry slightly more pronounced than in Figure \ref{Fir_Rate_Dist_Compare}.
+The standard deviation for the excitatory population was $\mathrm{\sigma_{inst} = 1.79\, Hz}$ and the skewness $\mathrm{v_{inst} = 1.51}$ ($\mathrm{v_{inst,log} = -0.52}$), which makes the asymmetry slightly more pronounced than in Figure \ref{Fir_Rate_Dist_Compare}.
 \begin{figure}
@@
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/instant_diff_fir_dist_i.png}
-\caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population. Data was taken from 2 simulations and $\mathrm{t=1000-1500\,s}$.}
+\caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population. Data was taken from 10 simulations and $\mathrm{t=1000-1500\,s}$.}
 \label{Fir_Rate_Dist_Instant_compare}
@@
 
+An interesting idea that the aforementioned paper discusses is the possibility that slowness of homeostatic regulation on the timescale of hours might not only be due to functional reasons, such as this rate of adaption being sufficient to compensate for naturally occurring external perturbations.
+Based on their analysis, it might also be a mere issue of stability.
+In the context of this notion, faster homeostatic controls would simply be ruled out because they do not allow the nervous system to stay in a healthy condition.
+Our findings regarding the stability of diffusive homeostasis thus serves as an example supporting this hypothesis.
+
 \subsection{The Firing Rate Distribution}
@@
 In order to acquire a deeper understanding of the mechanisms that determine these statistics, we developed analytical expression that allowed us to reliably predict the steady-state of firing rates based on the spatial structure of excitatory neurons.
-We would like to emphasize that this explanation differs from common approaches to understand the emergence of heavy-tailed statistics of firing rates in recurrent networks.
-Theoretical studies on the behaviour of recurrent networks are largely based on the assumption that the excitability of neurons is not individually tuned but rather adjusted globally to achieve a desired mean firing rate.
+We would like to emphasize that this explanation differs from common approaches of understanding the emergence of heavy-tailed statistics of firing rates in recurrent networks.
+Theoretical studies on the behaviour of recurrent networks are largely based on the assumption that the excitability of neurons is not individually fine-tuned but rather randomly distributed and adjusted globally to achieve a desired mean firing rate.
 Predictions about the resulting activity are then made based on (potentially simplified) statistical features of recurrent connectivity and the specific form of the neuronal transfer function used in the model, see e.g.
 \cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998}.
-Our interpretation of our results leads to the conclusion that this "canonical" approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal much differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behaviour.
+Our interpretation of our results leads to the conclusion that this "canonical" approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behaviour.
 
@@
 Overall, the resulting behaviour of the excitatory population rather appeared to us as a form of single-neuron homeostasis whose individual targets are predetermined by the quenched random spatial structure of the respective cells.
+In particular, our result depicted in Figure \ref{Ext_Input_Switch} did not support the notion of separability of inputs.
 Of course, this impression only applies to the case where the aforementioned mixture of influence between spatial and synaptic topology is dominated by the former.
-In particular, our result depicted in Figure \ref{Ext_Input_Switch} did not support the notion of separability of inputs.
-Furthermore, by analyzing network activity and comparing it to our analytic model, we found that only one particular homeostatic fixed point of network activity is exists.
-
-For the standard choice of parameters (being roughly based on experimental data), the resulting activity is indeed strongly bound to the spatial structure of the cells.
+By analyzing network activity based on our analytic model, we found that for finite diffusion constants in theory, indeed only a single homeostatic fixed point exists.
+On a practical level though, the gradual decorrelation with this theoretical state of activity upon larger values of $\mathrm{D}$ is presumably caused by synaptic turnovers, which change the synaptic input.
+The resulting changes in activity are more slowly and less accurately compensated in the case of larger diffusion constants.
+
+However, for the standard choice of parameters (being roughly based on experimental data), the resulting activity is indeed strongly bound to the spatial structure of excitatory cells.
 Naturally, this raises the question of biological plausibility.
-To our knowledge, no experimental study exists that relates measurements of spontaneous activity to local fluctuations of neuronal density.
+To our knowledge, no experimental study exists that relates measurements of spontaneous activity to local fluctuations of neuronal densities.
 Ivenshitz and Segal studied the influence of (mean) neuronal density onto neuronal activity in a culture of hippocampal neurons \cite{Ivenshitz_2010}.
@@
 As an indirect consequence of spatial structure determining activity, we found that neurons with a low-density neighbourhood have a higher chance of developing strong outgoing weights.
-Since this effect is directly linked to the low density-high firing rate-relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D).
-
-  If diffusion in a real biological system happens at a finite but fast speed compared to the adaptation of intrinsic excitability, one could arguably expect it to be equivalent to instant diffusion.
-In our simulation, we explained the fact that we saw a steady decline of correlation in Figure \ref{Corr_Coeff_vs_D} by the decreasing capability of the homeostatic mechanism to quickly enough react to structural synaptic changes that alter the recurrent excitatory inputs and, in consequence, excitatory firing rates.
-
-A major problem of the implemented model is the usage of quasi-point sources of nitric oxide, since it leads to a clear single homeostatic fixed point.
-Future modifications of the homeostatic model might integrate a wider-spread kernel of nNOS, allowing for a larger amount of states of activity fulfilling the homeostatic target.
-In fact, experimental and theoretical studies have suggested that NO is synthesized across wider spread cell structures, leading to a more even distribution of NO \cite{Philippides_2005}.
-
-While the implemented mathematical description of diffusion (Equation \eqref{NO_dyn}) is physically based, one can question the validity of the implementation of threshold adaption (Equation \eqref{Theta_dyn}): In principle, it does not impose any bounds onto the threshold value, which, from a biological point of view, seems implausible.
+Since this effect is directly linked to the low-density/high-firing rate-relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
+
+\subsubsection{Possible Modifications}
+Since these considerations evoked a rather sceptical view onto the biological plausibility of these results, one should consider possible modifications of the homeostatic model.
+One should note that these are to be evaluated in the context of providing a model of an actual physiological process.
+If the main goal was to simply provide a homeostatic method that retains an overall level of activity without tightly fixing individual rates, we would suggest to use the idealized model of instant diffusion, especially because of its computational simplicity.
+However, as already mentioned, the given experimentally based parameters do not allow to accept this simplification from the standpoint of biological and physical accuracy.
+Two elements of the model should be put into question: First, is it appropriate to assume an approximately point-like source of nitric oxide?
+Second, are the dynamics of threshold adaption (Equation \eqref{Theta_dyn}) an acceptable description of the actual physiological processes?
+
+While Sweeney et al.
+argue that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide), Philippides et al.
+claim that NO is often synthesized in a more delocalized way by means of fine fibres exceeding the soma \cite{Philippides_2005}.
+The diameter of these "production areas" is on the order of $\mathrm{10-100 \mu m}$.
+To incorporate this spread of synthesis in our model of diffusion, one would - for each neuron - need to convolve a suitably shaped and shifted "production"-kernel (scaled to the momentary rate of NO-synthesis) with the field of NO-concentration.
+Intuitively, this would locally "smear" the distinction between neighbouring neurons.
+From a more abstract point of view, this would provide a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfil the homeostatic target.
+
+Judging the plausibility of the used model of threshold adaptation is a rather problematic task.
+Experimental studies have investigated the effect of NO onto the conductance of ionic channels \cite{Steinert_NO,Steinert_NO_2011}.
+Mapping these features onto a simple LIF-model is obviously not easy, and many consequences of NO-modulation onto neural dynamics can certainly not be represented in such a simple model.
+Our criticism is thus rather based on more general arguments.
+
+A major issue of Equation \eqref{Theta_dyn} is the fact that, given a clamped positive or negative difference between the actual NO concentration and the target concentration, the excitability of the neuron would decrease or increase without bounds.
+Because of the limited amount of ion channels that exist in a cell and can be affected by nitric oxide, upper and lower bounds should certainly exist.
+A simple approach to tackle this would be to implement hard bounds into our neuron model, not allowing the threshold to pass an upper and lower value.
+Another possibility could be to implement these bounds by means of the differential equation itself.
+
+In either case, such a modification would break the ability of the network to tune thresholds in such a way that \emph{all} neurons eventually reach target concentration.
 

### 2017-01-19 draft.tex
.

@@
 \end{figure}
-\subsubsection{Distribution of Synaptic Weights}
+\subsubsection{Distribution of Synaptic Weights} \label{Syn_Weight_Dist_Section}
 A very well-studied property of neural networks is the distribution of synaptic weights.
@@
 A strong heterogeneity of firing rates allows for the development of few strong synapses, while the resulting distribution of mean weights of a narrow distribution is limited to a smaller range.
+We also tested the case of instant diffusion.
+Though firing rates span across a similar range, the resulting mean weights do not reach as high values as in the case of diffusion at a finite rate.
 \begin{figure}
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_weights_vs_rate.png}
-\caption{Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{t=1200-1500\,s}$) in regular (A) and logarithmic space (B).
+\caption{Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{t=700-1000\,s}$) in regular (A) and logarithmic space (B).
 Each plot corresponds to a presynaptic excitatory cell.}
@@
 \end{figure}
-It is interesting to note that on a logarithmic weight scale, we found a roughly linear relationship.
+Furthermore, it is interesting to note that on a logarithmic weight scale, we found a roughly linear relationship.
 Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.
@@
 
-\subsection{Equilibrium in the full Diffusive Model}
+\subsection{Equilibrium in the full Diffusive Model} \label{Matrix_Diff_Model_Section}
 Since the previous section has shown that the simplified model in \cite{Sweeney_Paper} has problems \emph{maintaining} a broad distribution of firing rates, turning to a more general formulation of the problem seemed reasonable.
@@
 However, as already mentioned, the given experimentally based parameters do not allow to accept this simplification from the standpoint of biological and physical accuracy.
-Two elements of the model should be put into question: First, is it appropriate to assume an approximately point-like source of nitric oxide?
+Instead, two elements of the model could be put into question: First, is it appropriate to assume an approximately point-like source of nitric oxide?
 Second, are the dynamics of threshold adaption (Equation \eqref{Theta_dyn}) an acceptable description of the actual physiological processes?
@@
 A major issue of Equation \eqref{Theta_dyn} is the fact that, given a clamped positive or negative difference between the actual NO concentration and the target concentration, the excitability of the neuron would decrease or increase without bounds.
-Because of the limited amount of ion channels that exist in a cell and can be affected by nitric oxide, upper and lower bounds should certainly exist.
+Because of the limited amount of ion channels that exist in a cell and that can be affected by nitric oxide, upper and lower bounds should certainly exist.
 A simple approach to tackle this would be to implement hard bounds into our neuron model, not allowing the threshold to pass an upper and lower value.
-Another possibility could be to implement these bounds by means of the differential equation itself.
+Another possibility is the implementation of these bounds by means of the differential equation itself.
 
 In either case, such a modification would break the ability of the network to tune thresholds in such a way that \emph{all} neurons eventually reach target concentration.
+As a consequence, the fixed point of firing rates under diffusive homeostasis would not be exclusively determined by spatial structure, but by a combination of network structure and the neurons' positions.
+As an example, consider a modification of Equation \eqref{Theta_dyn} of the form
+\begin{equation}
+\dot{V_t^i}(t) = \frac{1}{\tau_{V_t}}\left(\frac{NO(\mathbf{r}_{neur}^i,t)-NO_0}{NO_0} + \frac{\alpha}{V_t^i - V_{t,min}} + \frac{\alpha}{V_t^i - V_{t,max}}\right) \; .
+\label{Theta_dyn_with_Bounds}
+\end{equation}
+In this form, $\mathrm{NO(\mathbf{r}_{neur}^i,t) = NO_0}$ does not follow any more as the fixed point solution.
+Rather, one needs to consider the fact that, given the current network topology, the steady state of $\mathrm{NO(\mathbf{r}_{neur}^i)^* = NO(\mathbf{r}_{neur}^i,V_t^1,...,V_t^n)^*}$ in turn depends on the set of thresholds.
+Unfortunately, this increase in complexity would presumably make it impossible to find a general analytic description of the fixed point as introduced and discussed in Section \ref{Matrix_Diff_Model_Section}.
+Moreover, while this modification would incorporate network topology into the steady state of the system for finite diffusion constants, it is not clear whether it would allow perturbations (e.g.
+due to external input) to be sustained longer.
+
+\subsection{Network Topology} 
+Even though our investigations on network topology were rather intended as a form of sanity-check with respect to properties already found in earlier versions, we found some differences compared to non-diffusive homeostasis.
+
+First, in Section \ref{Syn_Weight_Dist_Section}, we presented our results regarding the distribution of weights, which turned out to be broader but still approximately log-normal distributed for diffusive homeostasis.
+As a first interpretation, we hypothesized that this might due to a slightly decreased amount of STDP-induced potentiation (Figure \ref{STDP_change}) in the case of diffusive homeostasis in the first half of the simulation.
+Another explanation one might consider is that the increased firing rate for some neurons in the case of diffusive homeostasis leads to a greater amount of fluctuation because of the increased amount of STDP-events.
+However, since the overall variance of STDP-induced fluctuations is not significantly higher but even slightly lower compared to non-diffusive homeostasis, this explanation seems rather unlikely.
+
+Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist}, we noted that
 

### 2017-01-21 draft.tex
.

@@
 \captionsetup[figure]{singlelinecheck=false}
+\author{Fabian Schubert}
 
@@
 In the face of possible \emph{new} features within the network's structure, one should further clarify the - presumably indirect - causal relation between diffusive spatial interaction and synaptic topology.
+
+\section{Introduction}
+Among many functional properties of the mammalian central nervous system, it is involved in maintaining many physiological properties in a functional regime.
+Some examples regarding the organism as a whole are e.g.
+body temperature and blood pressure, both being controlled by hypothalamus \cite[p.
+484]{Bear_Exploring_the_Brain}.
+The term \textit{homeostasis} entailing these regulatory mechanisms was first introduced by Walter C.
+Cannon in 1932 \cite{Wisdom_of_the_Body_Cannon, Homeostasis_Queenan_2012}.
+In more recent years, experimental studies have found evidence for processes within the brain that do not function as a regulatory control for certain aspects of the body, but as a homeostatic control of neural activity itself \cite{Turrigiano_1994,Burrone_2003}.
+Many processes underlying this self-regulatory behaviour have been found up till now, and many different biophysical interdependencies have shown to play a role.
+This diversity makes comparability of these mechanisms a rather difficult task.
+On a relatively general level though, experiments have revealed two main types of neuronal regulation: synaptic homeostatic plasticity and intrinsic homeostasis \cite{Desai_2003}.
+
+The notion of synaptic homeostatic plasticity subsumes the observation that neurons being more or less active than a certain set point of mean activity are regulated by means of their incoming synaptic weights.
+Theoretical and experimental studies have suggested that this type of regulation is in a multiplicative manner, thereby retaining proportions between individual synaptic strengths \cite{Syn_Plast_Abbott}.
+Furthermore, one can regard this form of plasticity as an antagonist to other aspects of synaptic plasticity that affect synaptic strengths in an activity dependent, hebbian fashion.
+Forms of regulation belonging to intrinsic homeostasis alter the neurons' capability of spiking upon external input by changing "intrinsic" properties of the nerve cell.
+More precisely, a neurons' ability to form an action potential can change by modifying the conductance of ion channels in its cell membrane \cite[p.
+156]{Theor_Neur_Dayan}.
+It is important to note that - depending on the specific mechanisms involved - both concepts of neural homeostasis can occur on a very wide range of different time scales, ranging from milliseconds to hours or days.
+
+Theoretical models of homeostasis are generally based on a form of feedback control.
+As such, it necessarily contains an error estimation.
+This could be based e.g.
+on the neuron's firing rate of the recent past measured in a given window, or, on a physiological level, e.g.
+a concentration of some molecule within some part of the cell structure.
+In any case, the error estimation requires setting some predefined target that the feedback control will attempt to achieve.
+This raises two questions: First, what would be an appropriate choice of homeostatic targets?
+Second, how could a neural system with fixed homeostatic targets encode changes of external stimuli if homeostasis overrides any information about changes in synaptic input?
 
@@
 %% plot_external_input_switch_activity.py
-\includegraphics[width=0.7\textwidth]{../../plots/external_input_switch.png}
+\includegraphics[width=\textwidth]{../../plots/external_input_switch.png}
 \end{center}
@@
 
-\subsection{The Firing Rate Distribution}
+\subsection{The Firing Rate Distribution} \label{Fir_Rate_Dist_Discussion_Section}
 By implementing diffusive homeostasis into the LIF-SORN model we managed to achieve a broader, skewed firing rate distribution while preserving appreciated features of network topology.
@@
 
-As an indirect consequence of spatial structure determining activity, we found that neurons with a low-density neighbourhood have a higher chance of developing strong outgoing weights.
-Since this effect is directly linked to the low-density/high-firing rate-relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
-
 \subsubsection{Possible Modifications}
@@
 
-First, in Section \ref{Syn_Weight_Dist_Section}, we presented our results regarding the distribution of weights, which turned out to be broader but still approximately log-normal distributed for diffusive homeostasis.
+\subsubsection{Distribution of Weights}
+In Section \ref{Syn_Weight_Dist_Section}, we presented our results regarding the distribution of weights, which turned out to be broader but still approximately log-normal distributed for diffusive homeostasis.
 As a first interpretation, we hypothesized that this might due to a slightly decreased amount of STDP-induced potentiation (Figure \ref{STDP_change}) in the case of diffusive homeostasis in the first half of the simulation.
@@
 
-Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist}, we noted that
+Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist}, we noted that the increased width of the distribution is largely due to to an increment on the left half of the curve.
+Since new weights are initialized at $\mathrm{10^{-4}\, mV}$, this might indicate that some weights are drifting much more slowly from their value of initialization compared to other weights.
+These "slow drifters" are presumably connecting neurons both spiking at a below-average firing rate.
+On the other hand, for non-diffusive homeostasis, one can assume that the amount of STDP-fluctuations is approximately equal for all recurrent excitatory weights because of the fixation of firing rates.
+
+\subsubsection{Strong Differences in Outgoing Weights}
+The most prominent significant difference between homeostatic mechanisms we found within network topology was the emergence of significantly above-average mean outgoing weights for a small subset of neurons.
+By comparing the given mean values to statistics acquired by randomly shuffling recurrent excitatory weights (see Figure \ref{Out_Weight_Mean_Quantile}), we found that this effect cannot be explained by the overall increase of weight heterogeneity that we discussed in the previous section.
+Thus, we identify the over-representation of strong outgoing weights as a non-random effect.
+However, we would like to emphasize that diffusive homeostasis is only indirectly responsible in the sense that it allows for a sustained heterogeneity among firing rates.
+
+As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}), we found that neurons with a low-density neighbourhood have a higher chance of developing these strong outgoing weights.
+Since this effect is directly linked to the low-density/high-firing rate-relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons with above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
 

### 2017-01-21 draft.tex
.

@@
 \maketitle
-\section{Abstract} \label{abstract}
-We attempted to replace the intrinsic homeostatic control system used in the original version by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue based on the LIF-SORN-model proposed in \cite{SORN_Paper}.
-The model of diffusive homeostasis was adopted from a paper by Y.
-Sweeney et al.
-\cite{Sweeney_Paper} and models the tissue as a surface of square shape and a set of points on this surface, representing the neurons' positions within the SORN.
-The group of excitatory neurons then acted as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position.
-The production and sensing of NO forms the basis of a feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate.
-The control system is then closed by linking the rate of NO-production to the neuron's firing rate.
-
-Key aspects of this thesis include an analysis of the stability of the homeostatic control, followed by a comparison of features of the original LIF-SORN and the Diffusive variant.
-We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity (as reported by \cite{Sweeney_Paper}) which has previously been suppressed by a rigid single-cell homeostasis.
-In the face of possible \emph{new} features within the network's structure, one should further clarify the - presumably indirect - causal relation between diffusive spatial interaction and synaptic topology.
 
@@
 This raises two questions: First, what would be an appropriate choice of homeostatic targets?
-Second, how could a neural system with fixed homeostatic targets encode changes of external stimuli if homeostasis overrides any information about changes in synaptic input?
+Second, given this set of targets, how could a neural system with fixed homeostatic targets encode changes of external stimuli if homeostasis overrides any information about changes in synaptic input?
+
+A possible way of choosing homeostatic targets could be to randomly draw from a distribution that matches statistics known to be found in the neural tissue that one wishes to model.
+This, however is a highly artificial ad-hoc solution.
+Furthermore, it does not resolve the second issue of encoding of external input.
+
+This thesis is based on earlier versions of a self-organizing recurrent neural network (SORN), in particular an implementation using leaky integrate-and-fire neurons (LIF-SORN) \cite{SORN_Paper}.
+It was developed to model features of activity and topology of cortical networks, in particular L5 of the neocortex.
+In these previous implementations, a slow homeostatic mechanism was implemented among excitatory neurons by an intrinsic adaptation of excitability.
+This led to the aforementioned problems of homeostatic control: Neural activity was tuned to a globally set target, allowing for no variability.
+In contrast, cortical networks are known to exhibit a broad distribution of firing rates, which is well described by a right-skewed, log-normal like shape \cite{Buzsaki_Fir_Rates_2014,Wohrer_Fir_Rates_2012}.
+If the LIF-SORN was meant to provide a good model for cortical structure and activity, it would require a different type of homeostatic model.
+
+In this thesis, we examined \textit{diffusive homeostasis} as a possible candidate to replace the previously used model of intrinsic plasticity.
+The idea and modelling of diffusive homeostasis was adopted from a paper by Y.
+Sweeney et al.
+\cite{Sweeney_Paper}, which models neural tissue as a two-dimensional surface and a set of points representing the neurons' positions.
+The group of excitatory neurons acted as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position.
+The production and sensing of NO forms the basis of a feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate.
+The control system is then closed by linking the rate of NO-production to the neuron's firing rate.
+The results by Sweeney et al.
+suggest that diffusive signalling could resolve the dichotomy between overall stability of firing activity and the need to allow flexibility among individual neurons' activities.
+Intuitively speaking, through the diffusive signal, each neurons receives a "mixture" of its own activity and its neighbouring neurons.
+Thereby individual tuning of firing rates is suppressed while the overall population activity is kept at a constant level.
+
+Key aspects of this thesis include an analysis of the stability of the homeostatic control, followed by a comparison of features of the original LIF-SORN and the diffusive variant.
+We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity which has previously been suppressed by the rigid single-cell homeostasis.
+In the face of possible \emph{new} features within the network's structure, one should further clarify the causal relation between diffusive spatial interaction and synaptic topology.
 
@@
 Following this is an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see section \ref{theor_osc}.
-Furthermore, we compare topological features of the network under the influence of diffusive and non-diffusive homeostasis in section ???.
+Furthermore, we compare topological features of the network under the influence of diffusive and non-diffusive homeostasis in section \ref{Network_Topology_Section}.
 
@@
 Diffusive homeostasis indeed results in a much broader distribution of mean firing rates.
-A large number of experimental studies have found that distributions of firing rates are not only broadly distributed but well described by a log-normal distribution, which has a non-zero third moment or skewness (\cite{Buzsaki_Fir_Rates_2014}, \cite{Wohrer_Fir_Rates_2012}).
+As mentioned in the introduction, a large number of experimental studies have found that distributions of firing rates are not only broadly distributed but well described by a log-normal distribution, which has a non-zero third moment or skewness.
 By definition, the logarithm of the random variable in question is thus again normally distributed.
@@
 
-\subsection{Network Topology}
+\subsection{Network Topology}\label{Network_Topology_Section}
 So far, we have only analyzed network activity, whereas in this section we present results that relate to features of synaptic topology.

### 2017-01-22 draft.tex
.

@@
 In more recent years, experimental studies have found evidence for processes within the brain that do not function as a regulatory control for certain aspects of the body, but as a homeostatic control of neural activity itself \cite{Turrigiano_1994,Burrone_2003}.
-Many processes underlying this self-regulatory behaviour have been found up till now, and many different biophysical interdependencies have shown to play a role.
+Many processes underlying this self-regulatory behavior have been found up till now, and many different biophysical interdependencies have shown to play a role.
 This diversity makes comparability of these mechanisms a rather difficult task.
@@
 In this thesis, we examined \textit{diffusive homeostasis} as a possible candidate to replace the previously used model of intrinsic plasticity.
-The idea and modelling of diffusive homeostasis was adopted from a paper by Y.
+The idea and modeling of diffusive homeostasis was adopted from a paper by Y.
 Sweeney et al.
@@
 The results by Sweeney et al.
-suggest that diffusive signalling could resolve the dichotomy between overall stability of firing activity and the need to allow flexibility among individual neurons' activities.
-Intuitively speaking, through the diffusive signal, each neurons receives a "mixture" of its own activity and its neighbouring neurons.
+suggest that diffusive signaling could resolve the dichotomy between overall stability of firing activity and the need to allow flexibility among individual neurons' activities.
+Intuitively speaking, through the diffusive signal, each neurons receives a "mixture" of its own activity and its neighboring neurons.
 Thereby individual tuning of firing rates is suppressed while the overall population activity is kept at a constant level.
@@
 The connection probability between two neurons was calculated from a distant dependent Gaussian function with a standard deviation of 200 $\mu m$.
-For exc.
-to inh.
-(EI) and inh.
-to exc.
-(IE) synapses, the connection fraction was set to 0.1, and 0.5 for recurrent inh.
-synapses (II).
+For excitatory to inhibitory (EI) and inhibitory to excitatory (IE) synapses, the connection fraction was set to 0.1, and 0.5 for recurrent inhibitory synapses (II).
 These connections were kept at a fixed connection strength throughout the simulation.
@@
 \end{align}
-Indexes k and l refer to the kth and lth pre- and postsynaptic spike respectively.
+Indexes k and l refer to the k-th and l-th pre- and postsynaptic spike respectively.
 Parameters were chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
@@
 However, one should keep in mind that for $U\in [0,1]$, $x\cdot u \in [0,1]$ always holds, thus the factor $x\cdot u$ has a generally diminishing effect.
-E.g., for our choice of variables, a poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim 4.5 Hz$, corresponding to $x\cdot u \approx 0.2$.
+E.g., for our choice of variables, a Poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim 4.5 Hz$, corresponding to $x\cdot u \approx 0.2$.
 "Potentiation" in this context refers to the fact that stronger input strengthens synaptic transmission \emph{compared} to close to zero incoming spikes.
@@
 
-\subsubsection{Modelling of Homeostatic Intrinsic Plasticity}
+\subsubsection{Modeling of Homeostatic Intrinsic Plasticity}
 
@@
 The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of nitric oxide (NO).
-Enzymes that are responsible for NO synthase (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS) , the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
+Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS) , the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
 These Enzymes differ in their functionality and dependence on the presence of other molecules.
@@
 
-On the other hand, experimental studies have suggested that NO can act as a diffusive signalling pathway, decreasing intrinsic excitability \cite{Steinert_NO}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
+On the other hand, experimental studies have suggested that NO can act as a diffusive signaling pathway, decreasing intrinsic excitability \cite{Steinert_NO}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
 
@@
 
-A depolarization within a nerve cell upon a spike-event $t_{spike}$ causes a fixed inflow of ionic current $Ca^{2+}_{spike}$, which is modelled as an instantaneous increase of the $Ca^{2+}$ concentration.
+A depolarization within a nerve cell upon a spike-event $t_{spike}$ causes a fixed inflow of ionic current $Ca^{2+}_{spike}$, which is modeled as an instantaneous increase of the $Ca^{2+}$ concentration.
 Over time, the concentration decays exponentially by a time constant $\tau_{Ca^{2+}}$, see \eqref{Ca_dyn}.
 Though $Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198-203]{Theor_Neur_Dayan}.
-The aforementioned influence of $Ca^{2+}$ onto nNOS was modelled by Sweeney et al.
+The aforementioned influence of $Ca^{2+}$ onto nNOS was modeled by Sweeney et al.
 through \eqref{nNOS_dyn}, using the Hill equation \cite{Hill_Equ} to model a cooperative binding mechanism.
@@
 
-Finally, the dynamics of the firing thresholds $V_t^i$ were modelled such that the rate of change is proportional to the relative deviation of the $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
+Finally, the dynamics of the firing thresholds $V_t^i$ were modeled such that the rate of change is proportional to the relative deviation of the $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
 
@@
 \end{equation}
-where $h = L/100$ is the distance between neighboured grid points, determined by the length $L$ of the square sheet and the resolution of the numeric grid.
+where $h = L/100$ is the distance between neighbored grid points, determined by the length $L$ of the square sheet and the resolution of the numeric grid.
 We implemented three possible boundary conditions into the simulation:
@@
 If not explicitly marked differently, Neumann boundary conditions were used for most of the simulations.
-This decision relates to the previously described mechanism of synaptic growth: Neurons placed close to the edge of the sheet have a lower connection probability due to the absence of neighbouring neurons in the direction perpendicular to the close-by border.
+This decision relates to the previously described mechanism of synaptic growth: Neurons placed close to the edge of the sheet have a lower connection probability due to the absence of neighboring neurons in the direction perpendicular to the close-by border.
 It therefore models the synaptic growth within a square "cutout" of neural tissue.
@@
 Equation \eqref{NO_dyn} describes the influx of NO as a sum of scaled and spatially shifted Dirac functions.
-Apart from the question, whether this source term results in a well defined, finite solution at the neurons' positions (see section !!??!!), it can only be modelled to a certain degree of accuracy, depending on the resolution of the numeric grid.
+Apart from the question, whether this source term results in a well defined, finite solution at the neurons' positions (see section !!??!!), it can only be modeled to a certain degree of accuracy, depending on the resolution of the numeric grid.
 In practice, we approximated the point sources of NO as an insertions at individual grid cells at a rate of $nNOS^i(t) / h^2$, where the normalizing divisor $h^2$ ensured the desired total influx per neuron.
@@
 As a first attempt, we set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$, as given by \cite{Sweeney_Paper}.
-Switching between non-diffusive/diffusive homeostasis after 750 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group, the average $NO$ concentration at the excitatory neurons' positions and the average firing threshold within the exc.
-group (inh.
-threshold was fixed, see table \ref{LIF_neuron_params}).
+Switching between non-diffusive/diffusive homeostasis after 750 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group, the average $NO$ concentration at the excitatory neurons' positions and the average firing threshold within the excitatory group (inhibitory threshold was fixed, see table \ref{LIF_neuron_params}).
 Both homeostatic mechanisms managed to keep the excitatory population activity in the desired range of 3 Hz.
@@
 \caption{A/A*: Mean of excitatory (blue) and inhibitory (red) neuronal firing rate.
-B/B*: NO concentration averaged over readouts at exc.
-neurons' positions.
-C/C*: Average exc.
-firing threshold.
+B/B*: NO concentration averaged over readouts at excitatory neurons' positions.
+C/C*: Average excitatory firing threshold.
 Non-diffusive homeostasis was used for $\mathrm{0-700\, s}$ , diffusive h.
@@
 \includegraphics[width=0.7\textwidth]{../../plots/power_spec/power_spectrum_sim_only.png}
-\caption{Blue: Mean of power spectrum over all excitatory thresholds. Red: Power spectrum of mean over all exc. thresholds.}
+\caption{Blue: Mean of power spectrum over all excitatory thresholds. Red: Power spectrum of mean over all excitatory thresholds.}
 \label{Power_Spec_without_Analysis}
@@
 \end{figure}
-Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further enquiry.
+Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further inquiry.
 Rhythmic patterns of activity are a commonly observed phenomenon within the brain.
 Depending on the rate of oscillations, the location within the brain and the spatial scale over which they are observed, different physiological features are found to be responsible, leading to explanatory models at different levels of abstraction.
-On a microscopic, single-neuron level, a so-called slow after-hyperpolarization conductance explains the appearance of bursting behaviour: A relatively short period of spiking activity is followed by a longer period of silence.
-This phenomenon can be modelled by a $Ca^{2+}$-dependent $K^{+}$-conductance.
+On a microscopic, single-neuron level, a so-called slow after-hyper-polarization conductance explains the appearance of bursting behavior: A relatively short period of spiking activity is followed by a longer period of silence.
+This phenomenon can be modeled by a $Ca^{2+}$-dependent $K^{+}$-conductance.
 Upon the bursting period, $Ca^{2+}$ concentration rises, prohibiting continuous spiking due to the activation of $K^{+}$  current until the $Ca^{2+}$ concentration has returned to base-level \cite[p.~203-207]{Theor_Neur_Dayan}.
@@
 On a larger, rate-based level, dynamical models of interconnected excitatory and inhibitory groups can exhibit sustained oscillations of activity \cite[p.~270]{Theor_Neur_Dayan}.
-As a simplest model, one can describe the dynamics of the exc.
-and inh.
-populations as a 2-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$:
+As a simplest model, one can describe the dynamics of the excitatory and inhibitory populations as a 2-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$:
 \begin{align}
@@
 A persistent oscillation then corresponds to a stable limit cycle in the 2-dimensional phase plane.
-According to the Poincaré-Bendixson Theorem, such a limit cycle exists inside a region $R$ if $R$ contains no fixed points and if any trajectory whose starting points lies within $R$ is confined to $R$.
+According to the Poincaré-Bendixson theorem, such a limit cycle exists inside a region $R$ if $R$ contains no fixed points and if any trajectory whose starting points lies within $R$ is confined to $R$.
 The second condition is equivalent to the condition that for all points $\mathbf{r}_{edge}$ on the edge of $R$, the vector field $\dot{\mathbf{r}}_{edge}$ is facing "into" $R$, see \cite[p.~248]{Dyn_Sys_Hirsch}.
@@
 However, one should note that the synaptic input within a spiking network carries an intrinsic randomness: since it is the sum of instantaneous increases in membrane voltage upon arriving spikes, one cannot simply describe it as a mean constant input $J$.
-Rather, if we assume that the arrival of spikes is approximately poisson-distributed and the time constant of the membrane is small compared to the average interspike-interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \cdot \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
+Rather, if we assume that the arrival of spikes is approximately Poisson-distributed and the time constant of the membrane is small compared to the average interspike-interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \cdot \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
 \begin{align}
@@
 For the sake of the initial question though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: Assuming validity of the described rate-model, the recurrent network as such (without homeostasis) is stable under the given choice of parameters.
-Furthermore, on an empirical basis, the occurrence of oscillations appear to be rather dependent on the choice of homeostasis, since apart from the homeostatic mechanism itself, all parameters of the simulation were kept unchanged upon the transition after 750s.
+Furthermore, on an empirical basis, the occurrence of oscillations appear to be rather dependent on the choice of homeostasis, since apart from the homeostatic mechanism itself, all parameters of the simulation were kept unchanged upon the transition after 750 s.
 In consequence, the following section further analyzes the dynamics underlying the diffusive homeostatic feedback.
@@
 Describing the neural activity as instantaneous firing rates raises the question how to describe the production of nitric oxide, since the outcome of equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $Ca^{2+}$ concentration caused by spike events.
-Naively, one could replace the sum of dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{spike} r_i(t)$.
+Naively, one could replace the sum of Dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{spike} r_i(t)$.
 If \eqref{nNOS_dyn} was a linear homogeneous differential equation, this approximation would indeed allow for the correct calculation of a linear relation between mean firing rate and NO production.
@@
 \end{equation}
-The exact solution of this integral can be expressed in terms of the hypergeometric function, making it rather impractical for any further analysis.
+The exact solution of this integral can be expressed in terms of the hyper-geometric function, making it rather impractical for any further analysis.
 Looking for further simplifications, we note that $\tau_{nNOS}$ is chosen ten-fold larger than $\tau_{Ca^{2+}}$.
@@
 Figure \ref{nNOS_approx_plot} compares the approximation given by \eqref{nNOS_single_sol_approx2} to the full NO production model (equations \eqref{Ca_dyn} and \eqref{nNOS_dyn}).
-Spikes were drawn from a poisson process at a rate of 3 Hz.
+Spikes were drawn from a Poisson process at a rate of 3 Hz.
 As predicted, the simplified model fits very well for sufficiently isolated spike events.
@@
 \includegraphics[width=\textwidth]{../../plots/nNOS_approx.png}
-\caption{Time course of nNOS(t) with poisson spiking at 3Hz.
+\caption{Time course of nNOS(t) with Poisson spiking at 3 Hz.
 The full simulation (blue, see equations \eqref{Ca_dyn},\eqref{nNOS_dyn}) is well fitted by the simplified model (red, see equation \eqref{nNOS_single_sol_approx2}).
@@
 
-From Equation \eqref{NO_dyn_approx} it is clear why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective poisson process with a mean rate of $3 Hz \cdot N_{exc.} = \mathrm{1200\,Hz}$, given the assumption that cells are spiking weakly correlated.
+From Equation \eqref{NO_dyn_approx} it is clear why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $3 Hz \cdot N_{exc.} = \mathrm{1200\,Hz}$, given the assumption that cells are spiking weakly correlated.
 Furthermore, we argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{total} = N_{exc.}\cdot r_{exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
@@
 As stated in the beginning, we were interested in finding an analytic expression for the power spectrum of the mean excitatory threshold.
-Therefore we took the fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} and \eqref{2d-sys-homeostasis-coord_transf2}, yielding
+Therefore we took the Fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} and \eqref{2d-sys-homeostasis-coord_transf2}, yielding
 \begin{align}
@@
 \end{align}
-where $f_{(\cdot)}$ denotes the fourier transform. We solved for $f_\theta$ which immediately gave us the power spectrum $P_\theta (\omega) \equiv |f_\theta (\omega)|^2$ of $\theta$:
+where $f_{(\cdot)}$ denotes the Fourier transform. We solved for $f_\theta$ which immediately gave us the power spectrum $P_\theta (\omega) \equiv |f_\theta (\omega)|^2$ of $\theta$:
 \begin{equation}
@@
 \end{figure}
-The fact that the value for $\mathrm{\alpha}$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency can be partially explained by the fact that the linear regression overestimates the importance of a number of high-threshold-outliers which leads to a shallower slope than what would be appropriate for the "working point" of oscillatory behaviour.
-Another possible explanation is the fact that "instant spread" is only an approximation.
+The fact that the value for $\mathrm{\alpha}$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency can be partially explained by the linear regression, which overestimates the importance of a number of high-threshold-outliers.
+This leads to a shallower slope than what would be appropriate for the "working point" of oscillatory behavior.
+Another possible explanation could be that "instant spread" is only an approximation.
 Rather, one could picture the nitrous oxide just to fill a fraction of the available space on a short time scale by replacing $L^2$ by a smaller area.
@@
 In either case, since these parameters appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}, both parameters have the same effect onto the shape of the power spectrum.
-
-Regarding the damping of the system, we can interpret   !!! SIMULATION STEHT NOCH AUS!!!
 
@@
 \subsubsection{Spike-Train Statistics}
-Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behaviour under sparse connectivity with a relatively high per-synapse connection strength, see e.g.
+Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behavior under sparse connectivity with a relatively high per-synapse connection strength, see e.g.
 \cite{Vreeswijk1996} or \cite{Brunel2000}.
@@
 This feature was shown in the previous section after slowing down the rate of homeostatic adaption.
-On the level of single cells, interspike intervals should be random, approximately following the statistics of a poisson process.
+On the level of single cells, interspike intervals should be random, approximately following the statistics of a Poisson process.
 \begin{figure}
@@
 \caption{A/C: Distribution of interspike intervals of excitatory/inhibitory neurons for diffusive and non-diffusive homeostasis, measured over $\mathrm{1000\,s}$.
-Only neurons with a mean firing rate in a certain range (see legend) were included into statistics to prevent overlap of different firing rates (except for non-diff.
-homeostasis and excitatory neurons, all being very close to 3 Hz).
+Only neurons with a mean firing rate in a certain range (see legend) were included into statistics to prevent overlap of different firing rates (except for non-diffusive homeostasis and excitatory neurons, all being very close to 3 Hz).
 Black lines are fits of exponential functions.
@@
 However, in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case, we restricted the statistics of ISIs to neurons whose mean firing rate fall into a window with a width of 1 Hz and a certain mean (see legend in Figure \ref{ISI_CV_compare}).
-Apparently, an approximately exponential distribution of ISIs is preserved for diffusive homeostasis (represented by straight lines in a log-plot), which is characteristic for poisson processes \cite[p.
+Apparently, an approximately exponential distribution of ISIs is preserved for diffusive homeostasis (represented by straight lines in a log-plot), which is characteristic for Poisson processes \cite[p.
 27]{Theor_Neur_Dayan}.
@@
 This is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons have an  under-representation of short ISIs, the opposite is the case for inhibitory neurons.
-These types of behaviour of LIF-models have been shown to depend on the CV of input the neuron receives \cite{Ostojic2011}: A smaller signal-to-noise-ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals.
+These types of behavior of LIF-models have been shown to depend on the CV of input the neuron receives \cite{Ostojic2011}: A smaller signal-to-noise-ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals.
 This relation fits nicely into our set of network parameters: inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
@@
 When speculating about the root of this discrepancy one could consider two possibilities: either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network.
-Regarding the first, it is certainly true that some amount of information about the activity of one neuron is transferred to another one in its neighbourhood via diffusion.
+Regarding the first, it is certainly true that some amount of information about the activity of one neuron is transferred to another one in its neighborhood via diffusion.
 However, due to the time scale of the homeostatic adaption, the response to fluctuations in the diffusive signal is on the order of seconds, while correlations in Figure \ref{Pop_Mean_Cross_Corr} are taking place within milliseconds.
-Thus, we concluded that a \emph{direct} link between homeostatic signalling and increased correlations can be regarded as implausible and that it must be an effect based on topological differences within the network.
+Thus, we concluded that a \emph{direct} link between homeostatic signaling and increased correlations can be regarded as implausible and that it must be an effect based on topological differences within the network.
 We investigate these in Section (???).
@@
 
-As an additional test, we applied external poisson input for $\mathrm{t\geq 300\, s}$ to two excitatory subgroups to see whether changes in the firing rate of these subgroups is levelled out by homeostasis or retained.
+As an additional test, we applied external poisson input for $\mathrm{t\geq 300\, s}$ to two excitatory subgroups to see whether changes in the firing rate of these subgroups is leveled out by homeostasis or retained.
 Members of these subgroups were picked randomly and independent of their position.
@@
 \caption{Excitatory population firing rate of subgroups subject to external poisson input for $\mathrm{t\geq 300\, s}$.
-Red and green subgroups consist of 100 randomly picked exc.
-neurons each.
+Red and green subgroups consist of 100 randomly picked excitatory neurons each.
 The remaining 300 neurons (blue) received no external input.}
@@
 \end{minipage}
-\caption{Standard deviation (A) and skewness (B) of firing rate distribution of excitatory neurons (neumann boundary conditions).}
+\caption{Standard deviation (A) and skewness (B) of firing rate distribution of excitatory neurons (Neumann boundary conditions).}
 \label{Fir_Rate_Dist_Width_Skewness_vs_D}
@@
 Diffusive homeostasis caused the CF to slightly overshoot its final fraction in the growth phase.
-To understand this kind of behaviour, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic growth and pruning.
+To understand this kind of behavior, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic growth and pruning.
 The average change of connection fraction is simply proportional to the difference between newly created synapses and those that were removed.
@@
 attempted to predict the shape of the firing rate distribution by means of a simplified mean-field approximation of diffusive \cite{Sweeney_Paper}.
-The main simplification within homoestatic feedback is the replacement of Equation \ref{Theta_dyn} by
+The main simplification within homeostatic feedback is the replacement of Equation \ref{Theta_dyn} by
 \begin{equation}
@@
 
-Instead of directly iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate3} - as done in \cite{Sweeney_Paper} - to fulfil self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
+Instead of directly iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate3} - as done in \cite{Sweeney_Paper} - to fulfill self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
 \begin{equation}
@@
 However, by analyzing Equation \ref{diff_hom_simpl_sweeney}, we could show that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, given any value of $\mathrm{\alpha}$ except $\mathrm{\alpha=1}$.
-This can be seen by setting the left hand side of equ.
-\eqref{diff_hom_simpl_sweeney} to $0$ (which is necessarily the case in the steady state) and rearranging the equation:
+This can be seen by setting the left hand side of Equation \eqref{diff_hom_simpl_sweeney} to $0$ (which is necessarily the case in the steady state) and rearranging the equation:
 \begin{equation}
@@
 At this point, we were aware of the fact that these equations completely neglect fluctuations of NO-synthesis due to spiking.
-However, given the very slow adaption of thresholds, which are responsible for changes of firing rates, we argued that noise can be neglected in the sense that $\mathrm{\lbrace r_i\rbrace}$ represents the set of mean firing rates whose resulting spike-train-induced NO-synthesis \emph{on average} fulfils \eqref{simple_NO_dyn_with_diff_equil} and \eqref{NO_equil_cond}.
+However, given the very slow adaption of thresholds, which are responsible for changes of firing rates, we argued that noise can be neglected in the sense that $\mathrm{\lbrace r_i\rbrace}$ represents the set of mean firing rates whose resulting spike-train-induced NO-synthesis \emph{on average} fulfills \eqref{simple_NO_dyn_with_diff_equil} and \eqref{NO_equil_cond}.
 
@@
 where $\mathrm{K_0}$ is the zeroth modified Bessel function of the second kind \cite{Helmholtz_Solution_2d}.
-This solution reveals a fundamental problem of modelling the sources of $\mathrm{NO}$-production as point sources: the fact that $\mathrm{K_0(x)}$ diverges to infinity for $\mathrm{x\rightarrow 0}$.
+This solution reveals a fundamental problem of modeling the sources of $\mathrm{NO}$-production as point sources: the fact that $\mathrm{K_0(x)}$ diverges to infinity for $\mathrm{x\rightarrow 0}$.
 It is merely due to the finite density of the numeric grid used for the simulation of the diffusion that allows for a finite target value of concentration.
@@
 By simply calculating all matrix elements of $\mathrm{\hat{\psi}}$ by means of Equation \eqref{interact_matrix_elements}, one would neglect the finite boundaries of the system, which would cause neurons close to the edge to "bleed" into empty space.
-This in turn would cause the solution of \eqref{NO_equil_cond_interact_matrix_operator} to contain an over-representation of high firing rates, since close-to-the-edge neurons would need to compensate for their lack of neighbours.
+This in turn would cause the solution of \eqref{NO_equil_cond_interact_matrix_operator} to contain an over-representation of high firing rates, since close-to-the-edge neurons would need to compensate for their lack of neighbors.
 Thus, we had to account for the boundary conditions used in the network simulation.
 As described in section \ref{methods}, we simulated the network mostly with Neumann boundary conditions as well as periodic boundaries.
-Both types can be modelled by extending the neurons' population through spatially shifted and mirrored versions of the base population (see Figure \ref{Bound_Cond_Patches}):
+Both types can be modeled by extending the neurons' population through spatially shifted and mirrored versions of the base population (see Figure \ref{Bound_Cond_Patches}):
 \begin{itemize}
@@
 \includegraphics[width=\textwidth]{../../plots/rates_matrix_prediction_vs_sim.png}
-\caption{Measured firing rates (t=1200-1500s) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
+\caption{Measured firing rates (t=1200-1500 s) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
 For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably "large" diffusion constant of $\mathrm{D=100\, \mu m^2 /s}$.}
@@
 \end{minipage}
-\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), neumann boundaries.}
+\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries.}
 \label{Std_Skew_Dist_vs_Data}
@@
 In summary, the shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuation in the spatial distribution of neurons.
-Finally, to further support this result by testing, we arranged excitatory neurons on a regular grid with a nearest-neighbour distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
-By doing so, all neurons were given the same structure of neighbours.
+Finally, to further support this result by testing, we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
+By doing so, all neurons were given the same structure of neighbors.
 Due to symmetry, all neurons then should - in theory - exhibit the exact same firing rate.
@@
 \end{center}
-\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and neumann boundary conditions, $\mathrm{D=10\,\mu m^2/ms}$.}
+\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2/ms}$.}
 \label{Fir_Rate_Dist_Reg_Grid}
@@
 
-\subsubsection{Low-Density Neighbourhoods correlate with strong outgoing Connections}
+\subsubsection{Low-Density Neighborhoods correlate with strong outgoing Connections}
 In Section \ref{Section_Mean_outgoing_Weights}, we stated that diffusive homeostasis allowed the network do develop few neurons with exceptionally strong outgoing weights.
@@
 Note the spatial correlation in high/low-density regions.
-(C) and (D): Decadic logarithm of outgoing weights correlates with inverse neuron density (corr.
+(C) and (D): The decadic logarithm of outgoing weights correlates with inverse neuron density (corr.
 coeff.
@@
 We would like to emphasize that this explanation differs from common approaches of understanding the emergence of heavy-tailed statistics of firing rates in recurrent networks.
-Theoretical studies on the behaviour of recurrent networks are largely based on the assumption that the excitability of neurons is not individually fine-tuned but rather randomly distributed and adjusted globally to achieve a desired mean firing rate.
+Theoretical studies on the behavior of recurrent networks are largely based on the assumption that the excitability of neurons is not individually fine-tuned but rather randomly distributed and adjusted globally to achieve a desired mean firing rate.
 Predictions about the resulting activity are then made based on (potentially simplified) statistical features of recurrent connectivity and the specific form of the neuronal transfer function used in the model, see e.g.
 \cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998}.
-Our interpretation of our results leads to the conclusion that this "canonical" approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behaviour.
+Our interpretation of our results leads to the conclusion that this "canonical" approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behavior.
 
@@
 Interestingly, we could not confirm this, at least within the tests that we performed and the given set of standard parameters.
-Overall, the resulting behaviour of the excitatory population rather appeared to us as a form of single-neuron homeostasis whose individual targets are predetermined by the quenched random spatial structure of the respective cells.
+Overall, the resulting behavior of the excitatory population rather appeared to us as a form of single-neuron homeostasis whose individual targets are predetermined by the quenched random spatial structure of the respective cells.
 In particular, our result depicted in Figure \ref{Ext_Input_Switch} did not support the notion of separability of inputs.
@@
 
-\subsubsection{Possible Modifications}
-Since these considerations evoked a rather sceptical view onto the biological plausibility of these results, one should consider possible modifications of the homeostatic model.
+\subsubsection{Possible Modifications}\label{Possible_Modifications_Section}
+Since these considerations evoked a rather skeptical view onto the biological plausibility of these results, one should consider possible modifications of the homeostatic model.
 One should note that these are to be evaluated in the context of providing a model of an actual physiological process.
@@
 argue that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide), Philippides et al.
-claim that NO is often synthesized in a more delocalized way by means of fine fibres exceeding the soma \cite{Philippides_2005}.
+claim that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}.
 The diameter of these "production areas" is on the order of $\mathrm{10-100 \mu m}$.
 To incorporate this spread of synthesis in our model of diffusion, one would - for each neuron - need to convolve a suitably shaped and shifted "production"-kernel (scaled to the momentary rate of NO-synthesis) with the field of NO-concentration.
-Intuitively, this would locally "smear" the distinction between neighbouring neurons.
-From a more abstract point of view, this would provide a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfil the homeostatic target.
+Intuitively, this would locally "smear" the distinction between neighboring neurons.
+From a more abstract point of view, this would provide a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.
 
@@
 
+\section{Conclusion}\label{Conclusion_Section}
+Drawing a conclusion from our results presents itself as a somewhat ambiguous task.
+On a phenomenological level, our main goal of allowing the LIF-SORN to exhibit a broad, skewed distribution was achieved.
+However, whether the implications of the diffusive model that revealed itself upon deeper investigations are acceptable in terms of biological plausibility is still left open to debate.
+
+Our analysis of the of the feedback control has shown that the dynamics of the system can be approximately described in a linearized way.
+As we have speculated in Section \ref{Possible_Modifications_Section}, a better model of homeostatic feedback might eventually require the introduction of nonlinearity, at the cost of a harder to analyze and predict behavior.
+
+From a topological point of view, the implementation of homeostasis can be regarded as a success: Thanks to the broad range of neural activity it allowed for the emergence of highly influential subgroups of excitatory neurons.
+This - experimentally confirmed - feature was not present in earlier versions of the LIF-SORN.
+It thus can be regarded as another non-random property of cortical structure that was not hard-coded but naturally emerged from the set of basic rules that constitute dynamics and behavior of our network.
+
 \bibliography{test_base}

### 2017-01-23 draft.tex
.

@@
 
-%\makeatother
-%\MSonehalfspacing
-
 \title{Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\
@@
 \begin{document}
-\maketitle
+\begin{titlepage}
+\clearpage
+\thispagestyle{empty}
+\begin{center}
+\LARGE{{\scshape Faculty 13 Physics}\\
+  {\scshape Frankfurt Institute for Advanced Studies}\\
+  \vspace{1cm}
+  Master's Thesis\\}
+  \vspace{1cm}
+  \huge{Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network}\\
+  \vspace{0.5cm}
+  \LARGE{Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity}\\
+  \vspace{2cm}
+  \LARGE{Fabian Schubert\\
+  Matriculation Number: 4282141}\\
+  \vspace{2cm}
+  Thesis Supervisor: Prof. Dr. Jochen Triesch\\
+  \end{center}
+
+\vfill
+
+% Bottom of the page
+\begin{center}
+{\large \today}
+\end{center}
+\end{titlepage}
+
+\clearpage
+\thispagestyle{empty}
+
+\begin{LARGE}
+\noindent\textbf{Statutory Declaration}
+\end{LARGE}
+\vspace{.5cm}\\
+I hereby declare that I authored this thesis independently and that I have
+not used other than the declared sources/resources.
+I explicitly marked all material which has been quoted either literally or by content from the used sources.
+I further declare that neither the thesis, nor any section of it, was used as a study achievement for any other graded or ungraded exam.
+\vspace{2cm}\\
+\rule{\textwidth}{0.4pt}
+
+\clearpage
+\thispagestyle{empty}
+
+\tableofcontents
+\newpage
+\clearpage
+\setcounter{page}{1}
+
+\makeatother
+\MSonehalfspacing
 
 \section{Introduction}
-Among many functional properties of the mammalian central nervous system, it is involved in maintaining many physiological properties in a functional regime.
+Among other functional properties of the mammalian central nervous system, it is involved in maintaining crucial properties of the body in a functional regime.
 Some examples regarding the organism as a whole are e.g.
@@
 The notion of synaptic homeostatic plasticity subsumes the observation that neurons being more or less active than a certain set point of mean activity are regulated by means of their incoming synaptic weights.
-Theoretical and experimental studies have suggested that this type of regulation is in a multiplicative manner, thereby retaining proportions between individual synaptic strengths \cite{Syn_Plast_Abbott}.
+Theoretical and experimental studies have suggested that this type of regulation is taking place in a multiplicative manner, thereby retaining proportions between individual synaptic strengths \cite{Syn_Plast_Abbott}.
 Furthermore, one can regard this form of plasticity as an antagonist to other aspects of synaptic plasticity that affect synaptic strengths in an activity dependent, hebbian fashion.
@@
 We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity which has previously been suppressed by the rigid single-cell homeostasis.
-In the face of possible \emph{new} features within the network's structure, one should further clarify the causal relation between diffusive spatial interaction and synaptic topology.
+In the face of possible \emph{new} features within the network's structure, we will clarify the causal relation between diffusive spatial interaction and synaptic topology.
 
@@
 Equation \eqref{NO_dyn} describes the influx of NO as a sum of scaled and spatially shifted Dirac functions.
-Apart from the question, whether this source term results in a well defined, finite solution at the neurons' positions (see section !!??!!), it can only be modeled to a certain degree of accuracy, depending on the resolution of the numeric grid.
+Apart from the question, whether this source term results in a well defined, finite solution at the neurons' positions (see section \ref{Matrix_Diff_Model_Section}), it can only be modeled to a certain degree of accuracy, depending on the resolution of the numeric grid.
 In practice, we approximated the point sources of NO as an insertions at individual grid cells at a rate of $nNOS^i(t) / h^2$, where the normalizing divisor $h^2$ ensured the desired total influx per neuron.
@@
 Both conditions combined led to an iterative generation of positions, where for each neuron a random number generator produced pairs of integers $(n_x,n_y)$, each within $[0,N]$, until an unoccupied pair of integers was found and occupied, moving on to the next neuron.
-Figure \ref{diff_test_plot} shows an example of the resulting NO density.
+Figure \ref{diff_test_plot} shows an example of the resulting NO density throughout a simulation.
 \begin{figure}[h!]
@@
 Both homeostatic mechanisms managed to keep the excitatory population activity in the desired range of 3 Hz.
-However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Figure \ref{full_sim_osci}, are in fact regular oscillations across all three depicted variables.
-While the oscillation amplitudes undergo a rather unpredictable time course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
+However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Figure \ref{full_sim_osci}, were in fact regular oscillations across all three depicted variables.
+While the oscillation amplitudes undergo a rather unpredictable course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
 This feature is also illustrated by the fact that the power spectra depicted in Figure \ref{Power_Spec_without_Analysis} have a peak at the frequency that appeared to be dominant in Figure \ref{full_sim_osci}.
@@
 \begin{figure}
-
 \begin{center}
@@
 On a larger, rate-based level, dynamical models of interconnected excitatory and inhibitory groups can exhibit sustained oscillations of activity \cite[p.~270]{Theor_Neur_Dayan}.
-As a simplest model, one can describe the dynamics of the excitatory and inhibitory populations as a 2-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$:
+As a simplest model, one can describe the dynamics of the excitatory and inhibitory populations as a two-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$:
 \begin{align}
@@
 
-where $\tau_e$ and $\tau_i$ represents time constants representing the rapidity of firing rate adaptation, $\phi_e$ and $\phi_i$ the respective transition functions between synaptic input and firing rate and $W_{xy}$ the mean synaptic weight from population x to population y.
+where $\tau_e$ and $\tau_i$ are time constants representing the rapidity of firing rate adaptation, $\phi_e$ and $\phi_i$ the respective transition functions between synaptic input and firing rate and $W_{xy}$ the mean synaptic weight from population x to population y.
 A persistent oscillation then corresponds to a stable limit cycle in the 2-dimensional phase plane.
@@
 \end{equation}
-
 Apart from the correct description of $\phi_{e/i}$, a third problem is the analytic description of the STP that was present for recurrent excitatory connections in our network.
@@
 Furthermore, on an empirical basis, the occurrence of oscillations appear to be rather dependent on the choice of homeostasis, since apart from the homeostatic mechanism itself, all parameters of the simulation were kept unchanged upon the transition after 750 s.
-In consequence, the following section further analyzes the dynamics underlying the diffusive homeostatic feedback.
+Therefore, the following section further analyzes the dynamics underlying the diffusive homeostatic feedback.
 
@@
 Both forms of homeostasis use excitatory firing thresholds as a means of adjusting the excitatory firing rate.
-Though having a relatively immediate impact on the firing rate of the particular neuron, the network as a whole reacts by means of a local disturbance of activity as well: it settles at a new fixed point of firing rates.
+Though having a relatively immediate impact on the firing rate of the particular neuron, the network as a whole reacts by means of a local disturbance of activity as well: It settles at a new fixed point of firing rates.
 Two questions are of importance in the context of feedback dynamics.
@@
 The cubic dependence on $Ca^{2+}$ breaks this simplicity.
-In order to derive an approximate description, we denote two things: First, the target firing rate of 3 Hz and the corresponding mean interspike interval of 0.33...s is large compared to the decay constant of Calcium, $\tau_{Ca^{2+}} = \mathrm{0.01\,s}$.
-Consequently, it is very unlikely that one spike event will fall into a region where the Calcium concentration, decaying from the instant jump of the previous spike event, is still significantly larger than zero.
+In order to derive an approximate description, we denote two things: First, the target firing rate of 3 Hz and the corresponding mean interspike interval of 0.33...s is large compared to the decay constant of calcium, $\tau_{Ca^{2+}} = \mathrm{0.01\,s}$.
+Consequently, it is very unlikely that one spike event will fall into a region where the calcium concentration, decaying from the instant jump of the previous spike event, is still significantly larger than zero.
 As such, one can justify
@@
 \end{equation}
-Therefore, the resulting rate of NO synthesis can be decomposed into a sum of time shifted responses onto a single kernel of Calcium concentration as a result of a spike.
+Therefore, the resulting rate of NO synthesis can be decomposed into a sum of time shifted responses onto a single kernel of calcium concentration as a result of a spike.
 for a spike at $t_{spike}=0$, the solution of \eqref{nNOS_dyn} can be calculated by
@@
 The exact solution of this integral can be expressed in terms of the hyper-geometric function, making it rather impractical for any further analysis.
-Looking for further simplifications, we note that $\tau_{nNOS}$ is chosen ten-fold larger than $\tau_{Ca^{2+}}$.
-This discrepancy in decay times allows for the assumption that the impact of the Calcium kernel onto $nNOS$ is practically instantaneous.
+Looking for further simplifications, we noted that $\tau_{nNOS}$ is ten-fold larger than $\tau_{Ca^{2+}}$.
+This discrepancy in decay times allows for the assumption that the impact of the calcium kernel onto $nNOS$ is practically instantaneous.
 Consequently, $nNOS(t)$ becomes
@@
 
-To deal with this, we introduce an idealized picture of diffusive homeostasis, where diffusion across the tissue is instantaneous.
+To deal with this, we introduced an idealized picture of diffusive homeostasis, where diffusion across the tissue is instantaneous.
 This simplification results in a single level of NO-concentration for all neurons, only being modified over time by the sum of all neurons' NO-syntheses $nNOS_{total}(t) \equiv \sum_{i} nNOS^i(t)$ and the decay term $-\lambda NO$.
@@
 \end{equation}
-The amount of noise in the system is a hard-to-predict quantity since it depends on the spatial structure on the diffusive lattice, giving neurons that are further separated less impact on each other.
+The amount of noise in the system is a hard-to-predict quantity since it depends on the spatial structure on the diffusive lattice, giving neurons that are further separated less impact onto each other.
 We tried to estimate the noise level based on the same "instant spread"-simplification made in Equation \eqref{NO_dyn_approx} to describe the overall NO-dynamics.
@@
 To reduce oscillations as much as possible we eventually settled at a 1000-fold increased time constant, $\mathrm{\tau_{V_t}=2500\,s}$.
-Despite the slowness of threshold adaption, homeostasis still managed to keep excitatory network activity in the desired range, as shown in Figure \ref{full_sim_osci_slow_tau_th}.
-Despite a slight regularity of the NO-concentration, no oscillating activity occurs.
+Even given the slowness of threshold adaption, homeostasis still managed to keep excitatory network activity in the desired range, as shown in Figure \ref{full_sim_osci_slow_tau_th}.
+Despite a slight regularity of the time course of NO-concentration, no oscillating activity occurs.
 \begin{figure}
@@
 \subsubsection{Spike-Train Statistics}
-Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behavior under sparse connectivity with a relatively high per-synapse connection strength, see e.g.
-\cite{Vreeswijk1996} or \cite{Brunel2000}.
+Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behavior under sparse connectivity with a relatively high per-synapse connection strength \cite{Vreeswijk1996,Brunel2000}.
 This kind of asynchronous regular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity.
-This feature was shown in the previous section after slowing down the rate of homeostatic adaption.
+This regularity was shown to be achievable in the previous section after slowing down the rate of homeostatic adaption.
 On the level of single cells, interspike intervals should be random, approximately following the statistics of a Poisson process.
@@
 \end{figure}
-Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficient of variation ($\mathrm{CV\equiv\sigma/\mu}$), taken over the set of excitatory and inhibitory neurons.
+Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficients of variation ($\mathrm{CV\equiv\sigma/\mu}$), taken over the set of excitatory and inhibitory neurons, respectively.
 However, in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case, we restricted the statistics of ISIs to neurons whose mean firing rate fall into a window with a width of 1 Hz and a certain mean (see legend in Figure \ref{ISI_CV_compare}).
@@
 For perfect poissonian spiking, the CV should give a value of 1.
-CVs that are smaller/larger, as seen in Figure \ref{ISI_CV_compare} B/D, indicate a tendency towards greater/less regularity.
-This is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons have an  under-representation of short ISIs, the opposite is the case for inhibitory neurons.
-These types of behavior of LIF-models have been shown to depend on the CV of input the neuron receives \cite{Ostojic2011}: A smaller signal-to-noise-ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals.
-This relation fits nicely into our set of network parameters: inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
+CVs that are smaller or larger, as seen in Figure \ref{ISI_CV_compare} B/D, indicate a tendency towards greater regularity or bunching, respectively.
+This observation is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons have an  under-representation of short ISIs, the opposite is the case for inhibitory neurons.
+These types of behavior of LIF-models have been shown to depend on the CV of input the neuron receives: A smaller signal-to-noise-ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals \cite{Ostojic2011}.
+This relation fits nicely into our set of network parameters: Inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
 This lowers the signal-to-noise ratio for the inputs of inhibitory neurons, leading to the aforementioned statistical differences.
@@
 \end{figure}
-When speculating about the root of this discrepancy one could consider two possibilities: either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network.
+When speculating about the root of this discrepancy one could consider two possibilities: Either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network.
 Regarding the first, it is certainly true that some amount of information about the activity of one neuron is transferred to another one in its neighborhood via diffusion.
@@
 Thus, we concluded that a \emph{direct} link between homeostatic signaling and increased correlations can be regarded as implausible and that it must be an effect based on topological differences within the network.
-We investigate these in Section (???).
+We investigate these in Section \ref{Network_Topology_Section}.
 
@@
 In contrast, inhibitory cells showed a much clearer distinction: A skewness of $\mathrm{v_{Diff} = 1.522}$ in regular space and $\mathrm{v_{Diff,log} = -0.147}$ in log-space.
-As a first interpretation, we related this difference to the fact that inhibitory cells are only indirectly affected by diffusive homeostasis in the sense that their distribution of activity is mainly determined by differences withing neural input while inhibitory thresholds are all initialized and kept at the same value.
 
 Despite of fluctuations within the firing rate on small time scales due to the inherent nature of - approximately - random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds.
-This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: if firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates.
+This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates.
 
@@
 As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{mean}\cdot n_{bins}/T_{total}}$, though slight deviations can be seen as a different factor of proportionality.
-(B) acts as an illustration showing a counterexample: here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis.
+(B) acts as an illustration showing a counterexample: Here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis.
 For almost all of the neurons, this will cause a transition of firing rate between 3 Hz and a new rate different from 3 Hz.
@@
 
-As an additional test, we applied external poisson input for $\mathrm{t\geq 300\, s}$ to two excitatory subgroups to see whether changes in the firing rate of these subgroups is leveled out by homeostasis or retained.
+As an additional test, we applied external Poisson input for $\mathrm{t\geq 300\, s}$ to two excitatory subgroups to see whether changes in the firing rate of these subgroups is leveled out by homeostasis or retained.
 Members of these subgroups were picked randomly and independent of their position.
-As shown in Figure \ref{Ext_Input_Switch}, differences in among subgroups caused by different input signal strengths are gradually eliminated by the homeostatic mechanism.
+As shown in Figure \ref{Ext_Input_Switch}, differences among subgroups caused by different input signal strengths are gradually eliminated by the homeostatic mechanism.
 \begin{figure}
@@
 A naturally emerging question when altering the diffusion constant is how the firing rate behaves in the absolute limit of infinitely fast diffusion.
-In fact, simulation-wise this case is quite easy to simulate: one simply has  to feed all NO-sources into a single scalar variable of NO concentration.
+In fact, simulation-wise this case is quite easy to simulate: One simply has  to feed all NO-sources into a single scalar variable of NO concentration.
 In particular, this will provide the same NO readout for all excitatory neurons, which means that all excitatory thresholds change at the same rate all the time, only shifting their initial random distribution.
@@
 So far, we have only analyzed network activity, whereas in this section we present results that relate to features of synaptic topology.
-Since the SORN we used for all simulations only included plastic mechanisms affecting recurrent excitatory connections, these were the main subject of our investigations.
-Moreover, in contrast to the previous section, we did not aim for the emergence of an explicitly \emph{new} feature of synaptic topology, but rather sought to recover properties that had been found in earlier versions of the LIF-SORN.
+Since the SORN we used for all simulations only included plastic mechanisms affecting recurrent excitatory connections, these were the subject of our investigations.
+Moreover, in contrast to the previous section, we did not explicitly aim for the emergence of a \emph{new} feature of synaptic topology, but rather sought to recover properties that had been found in earlier versions of the LIF-SORN.
 
 \subsubsection{Excitatory Connection Fraction}
-In the previous version of the SORN, initializing the network with zero recurrent excitatory connections led to a monotonically increasing but saturating excitatory-to-excitatory connection fraction (CF).
+In the previous version of the LIF-SORN, initializing the network with zero recurrent excitatory connections led to a monotonically increasing but saturating excitatory-to-excitatory connection fraction (CF).
 The growth rate was tuned such that the terminal CF settled at $\mathrm{10\%}$, see \cite[p.
@@
 \subsubsection{Distribution of Synaptic Weights} \label{Syn_Weight_Dist_Section}
-A very well-studied property of neural networks is the distribution of synaptic weights.
+A well-studied property of neural networks is the distribution of synaptic weights.
 Experimental studies in hippocampus and cortical regions suggest heavy-tailed log-normal-like distribution of synaptic efficacies \cite{Song_Connectivity_2005,Lisman_Synapses_1993,Yasumatsu_Synapses_2008,Loewenstein_Spine_Sizes}.
 Theoretical models are mainly based on a combination of multiplicative and additive weight dynamics \cite{Loewenstein_Spine_Sizes,Statman_Synapses_2014}, which is in line with our implementation of multiplicative normalization and additive STDP.
-Figure compares the resulting distributions.
+Figure \ref{Weight_Dist} compares the resulting distributions.
 We found that we can retain a log-normal-like distribution in combination with diffusive homeostasis.
 A slightly larger variance can be observed.
-A possible explanation refers back to our observations in Figure \ref{STDP_change}: regarding STDP as a random process, a broader distribution of weights can be explained by a smaller potentiating effect and a decreased variance of STDP-fluctuations, which is both the case for diffusive homeostasis in the beginning of the simulation.
+A possible explanation refers back to our observations in Figure \ref{STDP_change}: Regarding STDP as a random process, a broader distribution of weights can be explained by a smaller potentiating effect and a decreased variance of STDP-fluctuations, which is both the case for diffusive homeostasis in the beginning of the simulation.
 Still, it seems unlikely that a possible effect of these differences is still present at $\mathrm{t=1500\,s}$.
@@
 \subsubsection{Synaptic Lifetimes}
-Synaptic lifetimes have been shown to approximately follow a power law distribution in earlier versions of the LIF-SORN and binary SORN \cite{SORN_Paper,Pengsheng_2013}.
+Synaptic lifetimes have been shown to approximately follow a power law distribution in earlier versions of LIF-SORN and binary SORN \cite{SORN_Paper,Pengsheng_2013}.
 This feature was preserved under diffusive homeostasis, as shown in Figure \ref{Syn_Lifetimes}.
@@
 In this regime of small weights, the effect of multiplicative normalization is small compared to additive STDP.
-Therefore, small weights are determined by additive quasi-random (due to their weak coupling to the postsynaptic neuron) fluctuations, which, as a very simple approximation, can be described as a brownian motion with certain standard deviation $\mathrm{\sigma}$.
-The first hitting time of this brownian motion is described by a Lévy distribution:
+Therefore, small weights are determined by additive quasi-random (due to their weak coupling to the postsynaptic neuron) fluctuations, which, as a very simple approximation, can be described as a Brownian motion with certain standard deviation $\mathrm{\sigma}$.
+The first hitting time of this Brownian motion is described by a Lévy distribution:
 \begin{equation}
@@
 \subsubsection{Mean outgoing Weights}\label{Section_Mean_outgoing_Weights}
-Since we only implemented synaptic normalization for the sum of ingoing weights, the total or average strength of outgoing connections may vary from cell to cell.
+Since we only implemented synaptic normalization for the sum of \emph{ingoing} weights, the total or average strength of \emph{outgoing} connections may vary from cell to cell.
 In a sense, the strength of outgoing connections per neuron can be regarded as a measure of how "influential" a neuron's activity is with respect to other neurons in the network.
-Effenberger et.
-al.
+Effenberger et al.
 have shown in computational studies that these "driver neurons" form highly active and interconnected subnetworks \cite{Effenberger_2015}, an observation that is backed up by experimental studies \cite{Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}.
@@
 
-In contrast to our model, Effenberger et.
-al.
+In contrast to our model, Effenberger et al.
 identified the presence of inhibitory STDP as a necessary mechanism for the development of this feature.
-On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: it weakens inhibitory currents for some neurons, which cause these neurons to have more above-average firing rates.
+On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: It weakens inhibitory currents for some neurons, which cause these neurons to have more above-average firing rates.
 In turn, synapses between highly active presynaptic cells and postsynaptic neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
 With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies the same functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity.
-We tested this relationship by plotting mean outgoing weights against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
-A strong heterogeneity of firing rates allows for the development of few strong synapses, while the resulting distribution of mean weights of a narrow distribution is limited to a smaller range.
+We tested this relationship by plotting the mean outgoing weights against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
+A strong heterogeneity of firing rates allows for the development of few strong synapses, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range.
 We also tested the case of instant diffusion.
-Though firing rates span across a similar range, the resulting mean weights do not reach as high values as in the case of diffusion at a finite rate.
+Though firing rates span across a similar range, mean weights do not reach as high values as in the case of diffusion at a finite rate.
 \begin{figure}
@@
 On a preliminary level, the results of section \ref{Fir_Dist_Section} were positive with respect to our goal of achieving a broad and skewed firing rate distribution.
-Following this, we tried to further gain insight to the actual shape of the resulting distribution.
+Following this, we tried to further gain insight into the actual shape of the resulting distribution.
 \subsection{Review of a Dynamic Mean-Field Model}
 Sweeney et al.
-attempted to predict the shape of the firing rate distribution by means of a simplified mean-field approximation of diffusive \cite{Sweeney_Paper}.
-The main simplification within homeostatic feedback is the replacement of Equation \ref{Theta_dyn} by
+attempted to predict the shape of the firing rate distribution by means of a simplified mean-field approximation of diffusion \cite{Sweeney_Paper}.
+The main simplification within homeostatic feedback was the replacement of Equation \ref{Theta_dyn} by
 \begin{equation}
@@
 \end{equation}
-$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acts as a parameter that determines the "mixture" between single-neuron-homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
+$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the "mixture" between single-neuron-homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
 $\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their overall mean.
@@
 \end{align}
-
 where $\nu$ is the mean population firing rate, $\phi_i$ the individual firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $V_t^i$ its synaptic input mean and standard deviation and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant.
-Synaptic efficacy and number if incoming neurons were drawn randomly to match the statistics of the actual network topology.
+Synaptic efficacy and number of incoming neurons were drawn randomly to match the statistics of the actual network topology.
 Self consistency was achieved by iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate1} until the desired precision of convergence is reached.
 
-The authors claim that this model reproduces results of the full network, in particular that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or a larger $\alpha$, respectively).
+The authors claimed that this model reproduces results of the full network, in particular that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or a larger $\alpha$, respectively).
 
 We tested this dynamic mean-field model by simulating a similar population, but used an interacting population of neurons of the same size as in the previous simulations (400 excitatory, 80 inhibitory neurons).
-This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $1500s$ (i.E., the "stable" phase).
+This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $\mathrm{1500 \, s}$ (i.E., the "stable" phase).
 Individual values for $\mu_i$ and $\sigma_i$ were then calculated according to \eqref{sweeney_self_consist_rate2} and \eqref{sweeney_self_consist_rate3}.
@@
 \end{equation}
-where $\tau_m$ is the membrane time constant. Equation \eqref{sweeney_self_consist_rate1} has to be rewritten accordingly:
+where $\tau_m$ is the membrane time constant. Equation \eqref{sweeney_self_consist_rate1} had to be rewritten accordingly:
 \begin{equation}
@@
 \end{equation}
-In addition, we included the modulation of weights by STP through a rate-dependent prefactor by combining Equation \eqref{STP_dynamics1} and \eqref{STP_dynamics2} into rate-based equations and solving for their steady-state:
+In addition, we included the modulation of weights by STP through a rate-dependent prefactor by combining Equation \eqref{STP_dynamics1} and \eqref{STP_dynamics2} into rate-based equations and solving for their steady state:
 \begin{equation}
@@
 Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics of excitatory rates and thresholds for $\mathrm{\alpha=\lbrace 0.4,0.8,0.9,1.0\rbrace}$.
-Apparently, except for the limiting case of $\mathrm{\alpha=1}$, all rates approach the same target rate of $\mathrm{3Hz}$ and thresholds move towards the same configuration for either choice of $\mathrm{\alpha}$.
-A significant difference only exists within the dynamics leading to the steady state.
-Roughly, a smaller value of $\mathrm{\alpha}$ leads to a faster relaxation.
+Apparently, except for the limiting case of $\mathrm{\alpha=1}$, all rates approach the same target rate of $\mathrm{3\,Hz}$ and thresholds move towards the same configuration for either choice of $\mathrm{\alpha}$.
+A significant difference only exists within the transient dynamics leading to the steady state.
+Roughly speaking, a smaller value of $\mathrm{\alpha}$ leads to a faster relaxation.
 \begin{figure}
@@
 \end{figure}
-These findings led us to the conclusion that, apart from the special case $\mathrm{\alpha=1}$ (which is the equivalent to "instantaneous" diffusion), a mean-field model describing the diffusive signal as a mixture of individual activity and all neurons is not suitable for explaining the existence of stable heterogeneous distributions of rates for a broad range of diffusion constants.
+These findings led us to the conclusion that, apart from the special case $\mathrm{\alpha=1}$, which is the equivalent to "instantaneous" diffusion, a mean-field model describing the diffusive signal as a mixture of individual activity and all neurons is not suitable for explaining the existence of stable heterogeneous distributions of rates for a broad range of diffusion constants.
 We did not intent to debase the validity of results of the mean-field model of Sweeney et al.
@@
 \end{equation}
-The right term of the equation is the same for all neurons $i$.
+The right term of the equation is the same for all neurons.
 Since the left term is monotonically increasing as a function of $\phi_i$ as long as $\mathrm{\alpha<1}$, only one specific solution $\phi_i = \Phi$ for all $i$ exists that equals the given term on the right.
@@
 \subsection{Equilibrium in the full Diffusive Model} \label{Matrix_Diff_Model_Section}
-Since the previous section has shown that the simplified model in \cite{Sweeney_Paper} has problems \emph{maintaining} a broad distribution of firing rates, turning to a more general formulation of the problem seemed reasonable.
-
-Equation \eqref{NO_dyn} describes the full dynamics of the diffusive neurotransmitter.
+Since the previous section has shown that the simplified model in \cite{Sweeney_Paper} has problems in maintaining a broad distribution of firing rates, turning to a more general formulation of the problem seemed reasonable.
+
+We did so by recalling that Equation \eqref{NO_dyn} describes the full dynamics of the diffusive neurotransmitter.
 Furthermore, equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma \cdot r_i}$, $\mathrm{r_i}$ representing a neuron's rate and $\mathrm{\gamma}$ being defined by Equation \eqref{2d-sys-fixed-points1}.
@@
 \end{equation}
-As in the previous section, we ask for the steady-state distribution of rates. Thus as a first step, one needs to solve
+As in the previous section, we ask for the steady-state distribution of rates. Thus as a first step, we had to solve
 \begin{equation}
@@
 \begin{equation}
-NO(\mathbf{x}_{neur,i}) = NO_0 \:, \: \forall i
+NO(\mathbf{x}_{neur,i}) = NO_0 \:, \: \forall i \; .
 \label{NO_equil_cond}
@@
 \end{equation}
-which is a two-dimensional Helmholtz equation with a superposition of (scaled) Dirac-functions.
-Thus, the solution of $\mathrm{NO}$ is composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left of the equation.
+which is a two-dimensional Helmholtz equation with a superposition of rescaled Dirac functions.
+Thus, the solution of $\mathrm{NO}$ is composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of the equation.
 For each delta function $\delta^2(\mathbf{x}-\mathbf{x}_i)$, the solution is
@@
 where $\mathrm{K_0}$ is the zeroth modified Bessel function of the second kind \cite{Helmholtz_Solution_2d}.
-This solution reveals a fundamental problem of modeling the sources of $\mathrm{NO}$-production as point sources: the fact that $\mathrm{K_0(x)}$ diverges to infinity for $\mathrm{x\rightarrow 0}$.
+This solution reveals a fundamental problem of modeling the sources of NO-production as point sources: the fact that $\mathrm{K_0(x)}$ diverges to infinity for $\mathrm{x\rightarrow 0}$.
 It is merely due to the finite density of the numeric grid used for the simulation of the diffusion that allows for a finite target value of concentration.
@@
 
-Generally speaking, no matter how the actual shape of the numeric solution in the equilibrium at a constant production rate looks like, it is expected to be of the form
+Generally speaking, no matter how the actual shape of the numeric solution in the equilibrium at a constant production rate looks like, it must be of the form
 \begin{align}
@@
 \end{equation}
-If we define
+By defining
 \begin{equation}
@@
 \end{equation}
-we can express the condition \eqref{NO_equil_cond} as
+we could express the condition \eqref{NO_equil_cond} as
 \begin{equation}
@@
 \end{align}
-The problem of finding the steady-state solution of the homeostatic constraint thus reduces to inverting $\hat{\psi}$:
+The problem of finding the steady-state solution of the homeostatic constraint thus reduced to inverting $\hat{\psi}$:
 \begin{equation}
@@
 where $\mathrm{\varepsilon}$ determines the "smoothness" of transition between $\mathrm{\psi}$ and the cutoff value $\mathrm{\psi_0}$.
-We chose $\varepsilon=10$ for all further calculations.
-To find an expression for $\mathrm{\psi_0}$, we took the simple approach to interpret this value as a mean of the analytic solution across the square area covered by the corresponding grid cell.
-As an additional simplification, we substitute the necessary integration over the square grid cell by a circular area of equal size around the source.
-This calculation yields
+We chose $\mathrm{\varepsilon=10}$ for all further calculations.
+To find an expression for $\mathrm{\psi_0}$, we took the simple approach of interpreting this value as a mean of the analytic solution across the area covered by the corresponding grid cell.
+As an additional simplification, we substituted the necessary integration over the square grid cell by a circular area of equal size around the source.
+This calculation yielded
 \begin{equation}
@@
 Figure \ref{Psi_Approximation_Compare} shows a comparison between the numerically calculated solution and the expression given by \ref{Numeric_Solution_Expression_Trick}.
-As expected, the approximation fits very well for nonzero values.
-The value at the critical point at the origin is slightly underestimated by \eqref{Numeric_Grid_Bessel_Approx}, but nonetheless fits well into the overall shape.
+As expected, the approximation fitted very well for nonzero values.
+The value at the critical point in the origin was slightly underestimated by \eqref{Numeric_Grid_Bessel_Approx}, but nonetheless fitted well into the overall shape.
 \begin{figure}
@@
 \end{figure}
-Thus, we took this approximation as a basis for further calculations of the "interaction" matrix $\mathrm{\hat{\psi}}$.
+Thus, we took this approximation as a basis for further calculations of the interaction-matrix $\mathrm{\hat{\psi}}$.
 
@@
 For our calculations, we obviously had to limit the amount of elements of the sum such that copies that are shifted further away can be neglected.
+For the sake of performance, the number of terms in the sum was adjusted to suffice the given diffusion constant.
+
 \subsubsection{Comparison of the Solution of the Random Matrix Equation and the Simulation of the Spiking Network}\label{Section_Rand_Mat_vs_Sim}
 After having worked out the analytical basis, we compared the prediction obtained from numerically solving \eqref{NO_equil_cond_interact_matrix_operator} for certain spatial configurations of neurons to the steady-state firing rates of the full spiking network with the same spatial structure.
-In particular, we were interested in the quality of the predictions in respect to the choice of diffusion constant.
+In particular, we were interested in the quality of the predictions with respect to the choice of diffusion constant.
 Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 /s}$, the correlation between measured and predicted firing rates is very good.
 In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /s}$.
-Since instant diffusion overrides any spatial inhomogeneities, this represents one limiting case where our analytic model cannot make any predictions.
+Since instant diffusion overrides any spatial inhomogeneities, this represented a limiting case where our analytic model could not make any meaningful predictions.
 The outcome of the third case shown in the plot, $\mathrm{D=0}$, is correctly predicted by the analytic model.
-In general, instant diffusion as well as $\mathrm{D=0}$ overrides the effect of spatial heterogeneity onto firing rates.
+In general, instant diffusion as well as $\mathrm{D=0}$ overrode the effect of spatial heterogeneity onto firing rates.
 \begin{figure}
@@
 \end{figure}
-As Figure \ref{Fir_Rate_Dist_Sim_vs_Mat} shows, the actual shape of the distribution is well predicted by the solution of the linear system.
+As Figure \ref{Fir_Rate_Dist_Sim_vs_Mat} shows, the actual shape of the distribution was also well predicted by the solution of the linear system.
 \begin{figure}
@@
 Naturally, these observations led us to the question of how the correlation between predicted measured firing rates behaves in between the aforementioned limits.
-Especially, we were interested in the \emph{range} of the diffusion constant for which our model provides a good description of the full spiking network's activity.
+Especially, we were interested in the range of the diffusion constant for which our model provides a good description of the full spiking network's activity.
 Figure \ref{Corr_Coeff_vs_D} depicts the Pearson correlation coefficient of $\mathrm{f_{matrix \\, predict}}$ and $\mathrm{f_{sim}}$ against the diffusion constant used in the simulation.
@@
 However, we could see a general decline of correlation for larger diffusion constants.
-This trend is in line with the aforementioned limit of instant diffusion, namely a complete decorrelation between prediction and measurement, as well as the good agreement for $\mathrm{D= 10\, \mu m^2 / ms}$ shown in Figure \ref{Fir_Rate_Dist_Sim_vs_Mat}.
+This trend was in line with the aforementioned limit of instant diffusion, namely a complete decorrelation between prediction and measurement, as well as the good agreement for $\mathrm{D= 10\, \mu m^2 / ms}$ shown in Figure \ref{Fir_Rate_Dist_Sim_vs_Mat}.
 \begin{figure}
@@
 \end{figure}
-We characterized the dependence of the shape of the firing rate distribution onto $\mathrm{D}$ by means of its standard deviation and skewness in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.
+We recalled that we characterized the dependence of the shape of the firing rate distribution onto $\mathrm{D}$ by means of its standard deviation and skewness in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.
 To test whether our analytic model predicts this dependence, we generated random ensembles of neuron positions, solved the linear system of rates and extracted the resulting standard deviation and skewness.
@@
 \end{figure}
-In summary, the shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuation in the spatial distribution of neurons.
-Finally, to further support this result by testing, we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
+In summary, shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuation in the spatial distribution of neurons.
+To further back up this result, we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
 By doing so, all neurons were given the same structure of neighbors.
-Due to symmetry, all neurons then should - in theory - exhibit the exact same firing rate.
+Due to symmetry, we expected that all neurons then should - in theory - exhibit the exact same firing rate.
 Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the result, being a significantly narrower distribution.
-This strongly supports the previous assertion.
+This strongly supported the previous assertion.
 \begin{figure}
@@
 \end{equation}
-Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should contain neurons with strong outgoing weights and vice versa.
-To test this hypothesis, we approximated the local neuron density by means of a a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$.
+Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should correlate with strong outgoing weights and vice versa.
+To test this hypothesis, we approximated the local neuron density by means of a a Gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$.
 Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} shows the results.
-Despite a certain amount of randomness, our prediction was verified.
+Despite a certain amount of randomness, our prediction was indeed verified.
 \begin{figure}
@@
 In another theoretical study, Harnack et al.
-treat the necessity of slow homeostatic adaptation in a more general fashion \cite{Stability_Homeostasis_Harnack_2015}.
+treated the necessity of slow homeostatic adaptation in a more general fashion \cite{Stability_Homeostasis_Harnack_2015}.
 Among other results, it is reported that increasing the number of dynamic variables in a feedback system decreases its stability.
@@
 In contrast, diffusive homeostasis increased the dimensionality of the system by means of its NO-synthesis and diffusion pathway.
-Additionally Harnack et al.
+Additionally, Harnack et al.
 report a similar effect as seen in our system: Noise can reduce stability in a damped dynamical system by constantly causing deviations from its fixed point.
@@
 Sweeney et al.
-claim that their implementation of diffusive homeostasis enables individual neurons to vary their firing rates more flexible compared to single-neuron homeostatic models, especially allowing for sustained encoding of different levels of external input.
+claimed that their implementation of diffusive homeostasis enables individual neurons to vary their firing rates more flexible compared to single-neuron homeostatic models, especially allowing for sustained encoding of different levels of external input.
 Interestingly, we could not confirm this, at least within the tests that we performed and the given set of standard parameters.
@@
 Of course, this impression only applies to the case where the aforementioned mixture of influence between spatial and synaptic topology is dominated by the former.
-By analyzing network activity based on our analytic model, we found that for finite diffusion constants in theory, indeed only a single homeostatic fixed point exists.
+By analyzing network activity based on our analytic model, we found that for finite diffusion constants, indeed only a single homeostatic fixed point exists.
 On a practical level though, the gradual decorrelation with this theoretical state of activity upon larger values of $\mathrm{D}$ is presumably caused by synaptic turnovers, which change the synaptic input.
@@
 From a more general perspective, one could argue that a mechanism binding firing rates to spatial constraints suppresses the ability of the system to adapt to a changing environment since it essentially "freezes" the state of activity.
-However, experiments have shown that neurons' firing rates are indeed correlated under a changing environment/task: Neurons with a certain baseline-firing rate are very likely to have a similar firing rate while performing a task \cite{Buzsaki_Fir_Rates_2014}.
+Experiments have shown that neurons' firing rates are indeed correlated under a changing environment/task: Neurons with a certain baseline-firing rate are very likely to have a similar firing rate while performing a task \cite{Buzsaki_Fir_Rates_2014}.
 While homeostatic fixation might not be problematic in the case of transient changes of stimuli, a spatial fixation of firing rates would presumably contradict the fact that long-term learning processes and plasticity lead to persistent changes in activity patterns \cite{Lever_Long_Term_Plast_2002}.
@@
 \subsubsection{Possible Modifications}\label{Possible_Modifications_Section}
-Since these considerations evoked a rather skeptical view onto the biological plausibility of these results, one should consider possible modifications of the homeostatic model.
+Since these considerations evoked a rather skeptical view onto the biological plausibility of these results, we considered possible modifications of the homeostatic model.
 One should note that these are to be evaluated in the context of providing a model of an actual physiological process.
@@
 Instead, two elements of the model could be put into question: First, is it appropriate to assume an approximately point-like source of nitric oxide?
-Second, are the dynamics of threshold adaption (Equation \eqref{Theta_dyn}) an acceptable description of the actual physiological processes?
+And second, are the relatively simple dynamics of threshold adaption (Equation \eqref{Theta_dyn}) an acceptable description of the actual physiological processes involved?
 
 While Sweeney et al.
-argue that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide), Philippides et al.
-claim that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}.
+argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide), Philippides et al.
+reported that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}.
 The diameter of these "production areas" is on the order of $\mathrm{10-100 \mu m}$.
-To incorporate this spread of synthesis in our model of diffusion, one would - for each neuron - need to convolve a suitably shaped and shifted "production"-kernel (scaled to the momentary rate of NO-synthesis) with the field of NO-concentration.
-Intuitively, this would locally "smear" the distinction between neighboring neurons.
-From a more abstract point of view, this would provide a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.
-
-Judging the plausibility of the used model of threshold adaptation is a rather problematic task.
+To incorporate this spread of synthesis in our model of diffusion, one would - for each neuron - need to convolve a suitably shaped and shifted "production"-kernel (scaled according to the momentary rate of NO-synthesis) with the field of NO-concentration.
+Intuitively, this would locally smear the distinction between neighboring neurons.
+From a more abstract point of view, it would provide a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.
+
+Regarding the second remark, judging the plausibility of the used model of threshold adaptation is a rather problematic task.
 Experimental studies have investigated the effect of NO onto the conductance of ionic channels \cite{Steinert_NO,Steinert_NO_2011}.
@@
 A major issue of Equation \eqref{Theta_dyn} is the fact that, given a clamped positive or negative difference between the actual NO concentration and the target concentration, the excitability of the neuron would decrease or increase without bounds.
-Because of the limited amount of ion channels that exist in a cell and that can be affected by nitric oxide, upper and lower bounds should certainly exist.
+Because of the limited amount of ion channels that exist in a cell and can be affected by nitric oxide, upper and lower bounds should certainly be present.
 A simple approach to tackle this would be to implement hard bounds into our neuron model, not allowing the threshold to pass an upper and lower value.
@@
 
-In either case, such a modification would break the ability of the network to tune thresholds in such a way that \emph{all} neurons eventually reach target concentration.
-As a consequence, the fixed point of firing rates under diffusive homeostasis would not be exclusively determined by spatial structure, but by a combination of network structure and the neurons' positions.
+In either case, such a modification would break the ability of the network to tune thresholds in such a way that necessarily \emph{all} neurons eventually reach target concentration.
+As a consequence, the fixed point of firing rates under diffusive homeostasis would not be strictly determined by spatial structure, but by a combination of network structure and the neurons' positions.
 As an example, consider a modification of Equation \eqref{Theta_dyn} of the form
@@
 In this form, $\mathrm{NO(\mathbf{r}_{neur}^i,t) = NO_0}$ does not follow any more as the fixed point solution.
-Rather, one needs to consider the fact that, given the current network topology, the steady state of $\mathrm{NO(\mathbf{r}_{neur}^i)^* = NO(\mathbf{r}_{neur}^i,V_t^1,...,V_t^n)^*}$ in turn depends on the set of thresholds.
-Unfortunately, this increase in complexity would presumably make it impossible to find a general analytic description of the fixed point as introduced and discussed in Section \ref{Matrix_Diff_Model_Section}.
-Moreover, while this modification would incorporate network topology into the steady state of the system for finite diffusion constants, it is not clear whether it would allow perturbations (e.g.
-due to external input) to be sustained longer.
+Rather, one needs to consider the fact that, given the recurrent network topology, the steady state of $\mathrm{NO(\mathbf{r}_{neur}^i)^* = NO(\mathbf{r}_{neur}^i,V_t^1,...,V_t^n)^*}$ in turn depends on the set of thresholds.
+Unfortunately, this increase in complexity would presumably make it impossible to find a general analytic description of the fixed point similar to the one introduced and discussed in Section \ref{Matrix_Diff_Model_Section}.
+Moreover, while this modification would provide a way to incorporate network topology into the theoretical steady state of the system for finite diffusion constants, it is not clear whether it would allow perturbations (e.g.
+due to external input) to be actually sustained longer.
 
@@
 As a first interpretation, we hypothesized that this might due to a slightly decreased amount of STDP-induced potentiation (Figure \ref{STDP_change}) in the case of diffusive homeostasis in the first half of the simulation.
-Another explanation one might consider is that the increased firing rate for some neurons in the case of diffusive homeostasis leads to a greater amount of fluctuation because of the increased amount of STDP-events.
-However, since the overall variance of STDP-induced fluctuations is not significantly higher but even slightly lower compared to non-diffusive homeostasis, this explanation seems rather unlikely.
+Another explanation one might consider is that the increased firing rate for some neurons in the case of diffusive homeostasis lead to a greater amount of fluctuation because of the increased amount of STDP-events.
+However, since the overall variance of STDP-induced fluctuations was not significantly higher but even slightly lower compared to non-diffusive homeostasis, this explanation seems rather unlikely.
 
@@
 These "slow drifters" are presumably connecting neurons both spiking at a below-average firing rate.
+This provides an explanation why this effect is more present in the case of diffusive homeostasis since it causes a portion of neurons to have rather low firing rates.
 On the other hand, for non-diffusive homeostasis, one can assume that the amount of STDP-fluctuations is approximately equal for all recurrent excitatory weights because of the fixation of firing rates.
@@
 \subsubsection{Strong Differences in Outgoing Weights}
-The most prominent significant difference between homeostatic mechanisms we found within network topology was the emergence of significantly above-average mean outgoing weights for a small subset of neurons.
+The most prominent difference between homeostatic mechanisms we found within network topology was the emergence of significantly above-average mean outgoing weights for a small subset of neurons.
 By comparing the given mean values to statistics acquired by randomly shuffling recurrent excitatory weights (see Figure \ref{Out_Weight_Mean_Quantile}), we found that this effect cannot be explained by the overall increase of weight heterogeneity that we discussed in the previous section.
@@
 
-As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}), we found that neurons with a low-density neighbourhood have a higher chance of developing these strong outgoing weights.
+Referring back to Figure \ref{Pop_Mean_Cross_Corr}, we can now relate the increment of correlation among the excitatory population in the case of diffusive homeostasis to the results discussed in this section: The emergence of very strong outgoing connections increases the probability of neurons being postynaptically connected to such highly influential neurons to fire shortly after the presynaptic neuron.
+In the light of the notion of "rich get richer" or "rich stay rich" weight-dynamics that were reported for earlier versions of SORN and LIF-SORN, one can argue that this increment in correlation even further stabilizes these strong excitatory weights \cite{Pengsheng_2013,SORN_Paper}.
+
+As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}), we found that neurons with a low-density neighborhood have a higher chance of developing these strong outgoing weights.
 Since this effect is directly linked to the low-density/high-firing rate-relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons with above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
@@
 
+\clearpage
 \bibliography{test_base}

### 2017-01-24 draft.tex
.

@@
 \section{Introduction}
+\subsection{Homeostasis in the Nervous System}
 Among other functional properties of the mammalian central nervous system, it is involved in maintaining crucial properties of the body in a functional regime.
@@
 
-This thesis is based on earlier versions of a self-organizing recurrent neural network (SORN), in particular an implementation using leaky integrate-and-fire neurons (LIF-SORN) \cite{SORN_Paper}.
-It was developed to model features of activity and topology of cortical networks, in particular L5 of the neocortex.
-In these previous implementations, a slow homeostatic mechanism was implemented among excitatory neurons by an intrinsic adaptation of excitability.
-This led to the aforementioned problems of homeostatic control: Neural activity was tuned to a globally set target, allowing for no variability.
-In contrast, cortical networks are known to exhibit a broad distribution of firing rates, which is well described by a right-skewed, log-normal like shape \cite{Buzsaki_Fir_Rates_2014,Wohrer_Fir_Rates_2012}.
-If the LIF-SORN was meant to provide a good model for cortical structure and activity, it would require a different type of homeostatic model.
-
+\subsection{Diffusive Homeostasis}
 In this thesis, we examined \textit{diffusive homeostasis} as a possible candidate to replace the previously used model of intrinsic plasticity.
@@
 
+\subsubsection{Nitric Oxide in the Nervous System}\label{NO_Experiments_Section}
+The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of nitric oxide (NO).
+Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS) , the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
+These Enzymes differ in their functionality and dependence on the presence of other molecules.
+In particular, nNOS is sensitive to the concentration of $Ca^{2+}$ ionic Calcium \cite{Knowles_Ca_nNOS,Steinert_NO}.
+Because of its small molecular structure and electrical neutrality, nitric oxide that was synthesized in the nervous system can diffuse freely, which makes it a good candidate to be involved into form of diffusive intracellular communication \cite{Lancaster_1994}.
+
+Due to a depolarization of the membrane potential in the course of an action potential, voltage dependent $Ca^{2+}$-channels open, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98-100]{Hille_Ion_Channels}.
+A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445-451]{Hille_Ion_Channels}.
+As such, $Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
+
+Experimental studies have also suggested that NO can act as an inhibitory diffusive signaling pathway, decreasing intrinsic excitability \cite{Steinert_NO_2011}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
+In experiments upon neurons in the medial nucleus of the trapezoid body, Steinert et al.
+found that cells that were subject to NO-signaling by an external source exhibited an increment in outward $\mathrm{K^+}$ current, which, due to its hyperpolarizing effect, can be regarded as a form of intrinsic inhibition.
+
+\subsection{Current State of the Network Model}
+This thesis is based on earlier versions of a self-organizing recurrent neural network (SORN), in particular an implementation using leaky integrate-and-fire neurons (LIF-SORN) \cite{SORN_Paper}.
+It was developed to model features of activity and topology of cortical networks, in particular L5 of the neocortex.
+In these previous implementations, a slow homeostatic mechanism was implemented among excitatory neurons by an intrinsic adaptation of excitability.
+This led to the aforementioned problems of homeostatic control: Neural activity was tuned to a globally set target, allowing for no variability.
+In contrast, cortical networks are known to exhibit a broad distribution of firing rates, which is well described by a right-skewed, log-normal like shape \cite{Buzsaki_Fir_Rates_2014,Wohrer_Fir_Rates_2012}.
+Thus, if the LIF-SORN was meant to provide a good model for cortical structure \emph{and} activity, it would require a different type of homeostatic model.
+
+\subsection{Thesis Outline}
 Key aspects of this thesis include an analysis of the stability of the homeostatic control, followed by a comparison of features of the original LIF-SORN and the diffusive variant.
@@
 Our original model of homeostatic control was described as an operation over discrete time steps $\Delta t = 0.1ms$, carried out for each excitatory neuron:
-
 \begin{align}
@@
 In a continuous, rate-based form, this update rule can as well be written as:
-
 \begin{equation}
@@
 
-The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of nitric oxide (NO).
-Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS) , the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
-These Enzymes differ in their functionality and dependence on the presence of other molecules.
-In particular, nNOS is sensitive to the concentration of $Ca^{2+}$ ionic Calcium \cite{Knowles_Ca_nNOS}.
-
-Due to a depolarization of the membrane potential in the course of an action potential, voltage dependent $Ca^{2+}$-channels open, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98-100]{Hille_Ion_Channels}.
-A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445-451]{Hille_Ion_Channels}.
-As such, $Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
-
-On the other hand, experimental studies have suggested that NO can act as a diffusive signaling pathway, decreasing intrinsic excitability \cite{Steinert_NO}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
-
-Sweeney et al. combined these empirical findings into a model of \emph{diffusive homeostasis}, which is governed by the following equations:
-
+The new diffusive homeostatic model by Sweeney et al. combined the empirical findings discussed in Section \ref{NO_Experiments_Section} into a set of differential equations:   
 \begin{align}
@@
 Though $Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198-203]{Theor_Neur_Dayan}.
-The aforementioned influence of $Ca^{2+}$ onto nNOS was modeled by Sweeney et al.
+The influence of $Ca^{2+}$ onto nNOS was modeled by Sweeney et al.
 through \eqref{nNOS_dyn}, using the Hill equation \cite{Hill_Equ} to model a cooperative binding mechanism.
@@
 Following this, we tried to further gain insight into the actual shape of the resulting distribution.
-\subsection{Review of a Dynamic Mean-Field Model}
+\subsection{Review of a Dynamic Mean-Field Model}\label{Mean_Field_Review_Section}
 Sweeney et al.
@@
 
+\subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}
+Since our analytic results revealed that a strong correlation between spatial structure and result firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors, we considered the possibility that a wider spread of each individual NO-source could locally decrease distinguishability between neurons.
+Thereby, it might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values.
+The biological plausibility of this idea is discussed in Section \ref{Possible_Modifications_Section}.
+
+To test our hypothesis, we modified our model such that each neuron released nitric oxide evenly into a circular area with a radius of $\mathrm{50 \, \mu m}$, centered around the neuron's position.
+The homeostatic readout was still taken solely from the centering point.
+Thereafter, we ran the same simulation as for Figure \ref{Ext_Input_Switch}.
+Comparing both plots, we saw a much greater persistence of distinction between excitatory subgroups.
+The time course of activity suggests that this distinction might even be permanent and steady instead of a very slow but transient state.
+\begin{figure}
+%% spread_source_illustration.py
+\includegraphics[width=\textwidth]{../../plots/spread_source_illustration.png}
+%% plot_external_input_switch_activity_spread_source.py
+\includegraphics[width=\textwidth]{../../plots/external_input_switch_spread_source.png}
+\caption{A/B: Illustration of circular kernels used for NO-insertion, overlay of all 400 neurons (left) and a single example (right).
+C: Resulting activity for excitatory subgroups.
+All settings were kept the same as for Figure \ref{Ext_Input_Switch}.}
+\label{External_Input_Switch_Spread_Source}
+\end{figure}
+
 \section{Discussion}
@@
 
-\subsubsection{Possible Modifications}\label{Possible_Modifications_Section}
+\subsubsection{Modifications of the Homeostatic Model}\label{Possible_Modifications_Section}
 Since these considerations evoked a rather skeptical view onto the biological plausibility of these results, we considered possible modifications of the homeostatic model.
@@
 However, as already mentioned, the given experimentally based parameters do not allow to accept this simplification from the standpoint of biological and physical accuracy.
-Instead, two elements of the model could be put into question: First, is it appropriate to assume an approximately point-like source of nitric oxide?
-And second, are the relatively simple dynamics of threshold adaption (Equation \eqref{Theta_dyn}) an acceptable description of the actual physiological processes involved?
-
+
+Instead, we hypothesized that by spatially increasing the spread of NO-insertion, we might be able to uncouple activity from spatial structure without tweaking the diffusion process.
 While Sweeney et al.
@@
 The diameter of these "production areas" is on the order of $\mathrm{10-100 \mu m}$.
-To incorporate this spread of synthesis in our model of diffusion, one would - for each neuron - need to convolve a suitably shaped and shifted "production"-kernel (scaled according to the momentary rate of NO-synthesis) with the field of NO-concentration.
-Intuitively, this would locally smear the distinction between neighboring neurons.
-From a more abstract point of view, it would provide a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.
-
-Regarding the second remark, judging the plausibility of the used model of threshold adaptation is a rather problematic task.
+To incorporate this spread of synthesis in our model of diffusion, we convolved a circular shaped and shifted "production"-kernel (scaled according to the momentary rate of NO-synthesis) with the field of NO-concentration.
+Intuitively, this locally smeared the distinction between neighboring neurons.
+From a more abstract point of view, it provided a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.
+As Figure \ref{External_Input_Switch_Spread_Source} suggests, this indeed improved flexibility of individual activity while retaining an overall constant firing rate.
+By adjusting the area of NO insertion we thereby gained further control over the strictness of the homeostatic mechanism.
+
+Another point of criticism that might justify future changes of the homeostatic model is the plausibility of the used model of threshold adaptation.
 Experimental studies have investigated the effect of NO onto the conductance of ionic channels \cite{Steinert_NO,Steinert_NO_2011}.
@@
 
-In either case, such a modification would break the ability of the network to tune thresholds in such a way that necessarily \emph{all} neurons eventually reach target concentration.
+In either case, such a modification could break the ability of the network to tune thresholds in such a way that necessarily \emph{all} neurons eventually reach target concentration.
 As a consequence, the fixed point of firing rates under diffusive homeostasis would not be strictly determined by spatial structure, but by a combination of network structure and the neurons' positions.
@@
 
-\section{Conclusion}\label{Conclusion_Section}
+\section{Conclusion and Outlook}\label{Conclusion_Section}
 Drawing a conclusion from our results presents itself as a somewhat ambiguous task.
@@
 It thus can be regarded as another non-random property of cortical structure that was not hard-coded but naturally emerged from the set of basic rules that constitute dynamics and behavior of our network.
+
+With regard to the future use and implementation of diffusive homeostasis, it could be desirable to cover the essential effects in a more simple and abstract formalism.
+As shown in Section \ref{Mean_Field_Review_Section}, a simple mean field model as presented by Sweeney et al.
+still carries problems similar to those of single-neuron homeostasis.
+However, modifications of this model that incorporates our remarks in Section \ref{Possible_Modifications_Section} might be able to recover properties of the full diffusive homeostatic feedback while being more computationally efficient.
 

### 2017-01-27 draft.tex
.

@@
 \subsection{Homeostasis in the Nervous System}
-Among other functional properties of the mammalian central nervous system, it is involved in maintaining crucial properties of the body in a functional regime.
+Among other functional roles of the mammalian central nervous system, it is involved in maintaining crucial properties of the body in a functional regime.
 Some examples regarding the organism as a whole are e.g.
@@
 Theoretical models of homeostasis are generally based on a form of feedback control.
-As such, it necessarily contains an error estimation.
+As such, they necessarily contain an error estimation.
 This could be based e.g.
@@
 In any case, the error estimation requires setting some predefined target that the feedback control will attempt to achieve.
-This raises two questions: First, what would be an appropriate choice of homeostatic targets?
-Second, given this set of targets, how could a neural system with fixed homeostatic targets encode changes of external stimuli if homeostasis overrides any information about changes in synaptic input?
-
-A possible way of choosing homeostatic targets could be to randomly draw from a distribution that matches statistics known to be found in the neural tissue that one wishes to model.
-This, however is a highly artificial ad-hoc solution.
-Furthermore, it does not resolve the second issue of encoding of external input.
+This, of course, raises the question of what would be an appropriate choice of homeostatic targets.
+
+Experimental studies have found that neuronal populations exhibit a strong heterogeneity within their individual activity.
+In particular, many statistical analyses found evidence for a log-normal like distribution of firing rates \cite{Buzsaki_Fir_Rates_2014,Wohrer_Fir_Rates_2012}.
+Following these results, one approach of modeling this feature would be to randomly distribute individual targets according to the aforementioned statistics.
+A problem of this procedure is the absence of any particular deeper physiological motivation or causation.
+In the light of this conceptual problem, one could, due to a lack of better knowledge, simply define a single global target of activity.
+However, it has been shown that heterogeneity of neural response onto external input within a population is crucial for efficient stimulus encoding \cite{Marsat_2010}.
+Allowing for a broad distribution of activity thus has to be regarded an important compartment of models of cortical activity and structure.
+
+\subsection{Earlier Research on the Network Model}
+This thesis is based on earlier versions of a self-organizing recurrent neural network (SORN), in particular an implementation using leaky integrate-and-fire neurons (LIF-SORN) \cite{SORN_Paper}.
+It was developed to model features of activity and topology of cortical networks, in particular L5 of the neocortex.
+In these previous implementations, a slow homeostatic mechanism was implemented among excitatory neurons by an intrinsic adaptation of excitability.
+This led to the aforementioned problems of homeostatic control: Neural activity was tuned to a globally set target, allowing for no variability.
+Despite this limitation, the model has proven to be capable of showing a number of experimentally confirmed features.
+Zheng et al.
+have shown that distribution and dynamics of synaptic efficacies measured in rat hippocampus can be reproduced by a binary SORN using a discretized version of spike-timing-dependent plasticity and presynaptic normalization \cite{Pengsheng_2013}.
+Based on this model, Miner et al.
+designed the LIF-SORN.
+This network reproduced the results of the binary SORN regarding self-organizing synaptic dynamics.
+Furthermore, it was able to explain the experimentally observed overrepresentation of bidirectional connections (see \cite{Markram_Connections_1997,Song_Connectivity_2005}) by means of a distance-dependent implementation of synaptic growth.
 
@@
 found that cells that were subject to NO-signaling by an external source exhibited an increment in outward $\mathrm{K^+}$ current, which, due to its hyperpolarizing effect, can be regarded as a form of intrinsic inhibition.
-
-\subsection{Current State of the Network Model}
-This thesis is based on earlier versions of a self-organizing recurrent neural network (SORN), in particular an implementation using leaky integrate-and-fire neurons (LIF-SORN) \cite{SORN_Paper}.
-It was developed to model features of activity and topology of cortical networks, in particular L5 of the neocortex.
-In these previous implementations, a slow homeostatic mechanism was implemented among excitatory neurons by an intrinsic adaptation of excitability.
-This led to the aforementioned problems of homeostatic control: Neural activity was tuned to a globally set target, allowing for no variability.
-In contrast, cortical networks are known to exhibit a broad distribution of firing rates, which is well described by a right-skewed, log-normal like shape \cite{Buzsaki_Fir_Rates_2014,Wohrer_Fir_Rates_2012}.
-Thus, if the LIF-SORN was meant to provide a good model for cortical structure \emph{and} activity, it would require a different type of homeostatic model.
 
@@
 Apart from reproducing the desired connection fraction, previous versions of the LIF-SORN showed an over-representation of bidirectional connections compared to a random graph with equal connectivity \cite{SORN_Paper}.
-This experimentally observed feature \cite{Markram_Connections_1997,Song_Connectivity_2005} required the presence of a distance dependent connection probability, as described in section \ref{network simulation}.
+This experimentally observed feature required the presence of a distance dependent connection probability, as described in section \ref{network simulation}.
 The absence of this breaking of spatial homogeneity even led to an under-representation of bidirectional connections, which is known to be an effect of STDP in recurrent networks \cite{Syn_Plast_Abbott}.

### 2017-01-29 draft.tex
.

@@
 156]{Theor_Neur_Dayan}.
-It is important to note that - depending on the specific mechanisms involved - both concepts of neural homeostasis can occur on a very wide range of different time scales, ranging from milliseconds to hours or days.
 
@@
 
-\subsection{Earlier Research on the Network Model}
+A conceptual problem that one might consider is the fact that temporal fluctuations of activity are believed to be a major part of information transmission and processing within the brain \cite[p.
+123-150]{Theor_Neur_Dayan}.
+Homeostasis as described above could potentially override information by eliminating these fluctuations of activity.
+However, it is argued that homeostatic mechanisms act on time scales of hours to days and thus do not interfere with changes in activity taking place on the order of seconds or below \cite{Turrigiano_2011}.
+
+Returning to the previous question, though the slowness of homeostatic adaptation might allow for temporal fluctuations of activity, it does not overcome the conceptual dichotomy between single cell homeostasis and persistent variability in spontaneous activity.
+Marder and Goaillard speculated that instead of a mechanism controlling activity on a single-cell level, one might consider the possibility of a "global sensor
+of network performance to provide error signals for tuning of the network" \cite{Marder_2006}.
+This concept was used by Sweeney et al.
+as the basic idea for the introduction of a diffusive, intercellular homeostatic mechanism, which will be introduced in the next section.
+
+\subsection{Diffusive Homeostasis}
+In this thesis, we examined \textit{diffusive homeostasis} as a possible candidate to replace the previously used model of intrinsic plasticity.
+The idea and modeling of diffusive homeostasis was adopted from a paper by Sweeney et al.
+\cite{Sweeney_Paper}, which models neural tissue as a two-dimensional surface and a set of points representing the neurons' positions.
+The group of excitatory neurons acted as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position.
+The production and sensing of NO forms the basis of a feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate.
+The control system is then closed by linking the rate of NO-production to the neuron's firing rate.
+The results by Sweeney et al.
+suggest that diffusive signaling could resolve the dichotomy between overall stability of firing activity and the need to allow flexibility among individual neurons' activities.
+Intuitively speaking, through the diffusive signal, each neurons receives a "mixture" of its own activity and its neighboring neurons.
+Thereby individual tuning of firing rates is suppressed while the overall population activity is kept at a constant level.
+
+\subsubsection{Nitric Oxide in the Nervous System}\label{NO_Experiments_Section}
+The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of nitric oxide (NO).
+Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS) , the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
+These Enzymes differ in their functionality and dependence on the presence of other molecules.
+In particular, nNOS is sensitive to the concentration of $Ca^{2+}$ ionic Calcium \cite{Knowles_Ca_nNOS,Steinert_NO}.
+Because of its small molecular structure and electrical neutrality, nitric oxide that was synthesized in the nervous system can diffuse freely, which makes it a good candidate to be involved into form of diffusive intracellular communication \cite{Lancaster_1994}.
+
+Due to a depolarization of the membrane potential in the course of an action potential, voltage dependent $Ca^{2+}$-channels open, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98-100]{Hille_Ion_Channels}.
+A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445-451]{Hille_Ion_Channels}.
+As such, $Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
+
+Experimental studies have also suggested that NO can act as an inhibitory diffusive signaling pathway, decreasing intrinsic excitability \cite{Steinert_NO_2011}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
+In experiments upon neurons in the medial nucleus of the trapezoid body, Steinert et al.
+found that cells that were subject to NO-signaling by an external source exhibited an increment in outward $\mathrm{K^+}$ current, which, due to its hyperpolarizing effect, can be regarded as a form of intrinsic inhibition.
+
+\subsection{Previous Research on the used Network Model}
 This thesis is based on earlier versions of a self-organizing recurrent neural network (SORN), in particular an implementation using leaky integrate-and-fire neurons (LIF-SORN) \cite{SORN_Paper}.
 It was developed to model features of activity and topology of cortical networks, in particular L5 of the neocortex.
-In these previous implementations, a slow homeostatic mechanism was implemented among excitatory neurons by an intrinsic adaptation of excitability.
+In these previous implementations, a slow homeostatic mechanism was set up among excitatory neurons through an intrinsic adaptation of excitability.
 This led to the aforementioned problems of homeostatic control: Neural activity was tuned to a globally set target, allowing for no variability.
@@
 Furthermore, it was able to explain the experimentally observed overrepresentation of bidirectional connections (see \cite{Markram_Connections_1997,Song_Connectivity_2005}) by means of a distance-dependent implementation of synaptic growth.
-
-\subsection{Diffusive Homeostasis}
-In this thesis, we examined \textit{diffusive homeostasis} as a possible candidate to replace the previously used model of intrinsic plasticity.
-The idea and modeling of diffusive homeostasis was adopted from a paper by Y.
-Sweeney et al.
-\cite{Sweeney_Paper}, which models neural tissue as a two-dimensional surface and a set of points representing the neurons' positions.
-The group of excitatory neurons acted as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position.
-The production and sensing of NO forms the basis of a feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate.
-The control system is then closed by linking the rate of NO-production to the neuron's firing rate.
-The results by Sweeney et al.
-suggest that diffusive signaling could resolve the dichotomy between overall stability of firing activity and the need to allow flexibility among individual neurons' activities.
-Intuitively speaking, through the diffusive signal, each neurons receives a "mixture" of its own activity and its neighboring neurons.
-Thereby individual tuning of firing rates is suppressed while the overall population activity is kept at a constant level.
-
-\subsubsection{Nitric Oxide in the Nervous System}\label{NO_Experiments_Section}
-The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of nitric oxide (NO).
-Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS) , the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
-These Enzymes differ in their functionality and dependence on the presence of other molecules.
-In particular, nNOS is sensitive to the concentration of $Ca^{2+}$ ionic Calcium \cite{Knowles_Ca_nNOS,Steinert_NO}.
-Because of its small molecular structure and electrical neutrality, nitric oxide that was synthesized in the nervous system can diffuse freely, which makes it a good candidate to be involved into form of diffusive intracellular communication \cite{Lancaster_1994}.
-
-Due to a depolarization of the membrane potential in the course of an action potential, voltage dependent $Ca^{2+}$-channels open, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98-100]{Hille_Ion_Channels}.
-A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445-451]{Hille_Ion_Channels}.
-As such, $Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
-
-Experimental studies have also suggested that NO can act as an inhibitory diffusive signaling pathway, decreasing intrinsic excitability \cite{Steinert_NO_2011}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
-In experiments upon neurons in the medial nucleus of the trapezoid body, Steinert et al.
-found that cells that were subject to NO-signaling by an external source exhibited an increment in outward $\mathrm{K^+}$ current, which, due to its hyperpolarizing effect, can be regarded as a form of intrinsic inhibition.
 

### 2017-01-30 draft.tex
.

@@
 Theoretical models of homeostasis are generally based on a form of feedback control.
-As such, they necessarily contain an error estimation.
+In control theory, this is also known as a \textit{closed loop control}.
+All these systems include a number of necessary functional compartments, which will be briefly introduced in the following.
+Concepts and terms were taken from \cite[p.
+59-64]{Cybernetik_Systems_Cruse_2006}.
+\newpage
+\subsubsection{Theory of Control Systems} \label{Control_Sys_Theo_Section}
+Generally, a closed loop control must contain some \emph{process} that is to be regulated.
+Despite its potential internal complexity, its functional role in the context of a feedback system is to simply generate a time-dependent output based on the history of a time-dependent input.
+This output is what one wishes to control and regulate by means of the feedback loop and thus represents the signal that is further processed.
+However, it might not be possible to directly quantify this desired output in terms of some internal state of the process.
+For example, the firing rate of a neuron is an abstract quantity, which can not be \emph{directly} related to some neuronal state variable.
+Consequently, it might be necessary to transform the actual output of the process into a different signal by a \textit{feedback transducer}.
+As a necessary next step, the (potentially transformed) output is fed into a \textit{comparator}, which, unsurprisingly, compares the given output of the process to some given target or \textit{reference}, typically by subtraction.
+Note that this reference can but does note have to be a time-dependent signal.
+However, the term \textit{homeostasis} generally refers to a fixed reference, while implementations with a time dependent reference can be regarded as a form of \textit{servomechanism}.
+The difference between reference and the feedback transducer's signal is known as the \textit{error} signal.
+This error signal is given to a \textit{controller}, which transforms this error signal into an appropriate input signal for the initially introduced process.
+Additionally, this is also the point in the control loop, where \textit{external disturbances} come into play by being added to the input generated by the controller.
+We illustrated the described flow of feedback control in Figure \ref{Closed_Loop_Control_Illustration}.
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{../../plots/illustrations/closed_loop_control.eps}
+\end{center}
+\caption{Schematic illustration of a closed loop control as described in Section \ref{Control_Sys_Theo_Section}}
+\label{Closed_Loop_Control_Illustration}
+\end{figure}
+Based on the way the controller generates input for the dynamic process based on the error signal, one can classify control loops by three types:
+\newpage
+\begin{itemize}
+\item A \textit{proportional controller} generates a signal that is proportional to the error signal it receives.
+The most important property of a proportional controller is that the stationary state of the control loop generally does not imply an error signal equal to zero.
+\item An \textit{integrator controller} uses an integration over the past of the error signal to obtain its output. The stationary solution necessarily implies that the error signal is zero.
+\item A \textit{differential controller} generates its output by means of the time derivative of the error signal.
+This type of controller can quickly react to momentary changes but does not compensate for sustained deviations of the error signal from zero.
+\end{itemize}
+It should be pointed out that these types of control mechanisms can be simultaneously used in a control system, e.g. through a linear combination.
+
+\subsubsection{Error Signals and Controllers of Neuronal Homeostasis}
+When analyzing or modeling a biological system, a key step characterizing a control loop should be to identify the previously described compartments.
+While the functional separation illustrated in Figure \ref{Closed_Loop_Control_Illustration} might seem intuitive and "straight forward", it is not obvious which physiological element should be attributed to a certain abstract element.
+As a start, we state that the process and its output controlled by homeostasis is the generation of action potentials and the resulting firing rate.
+As stated earlier, "firing rate" is an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a "sensible" quantity.
+In a nerve cell, this could be represented by e.g.
+the relation between the firing of action potentials and the temporary rise in $\mathrm{Ca^{2+}}$ concentration.
+An example for a homeostatic model making use of intracellular calcium concentration as a measure of spiking activity is the LeMasson-Abbott model \cite{LeMasson_1993}.
+More complex chains of activity encoding are of course possible, and we will introduce a recent model making additional use of the concentration of nitric oxide in Section \ref{DIff_Hom_Intro_Section} and \ref{NO_Experiments_Section}.
+Given a representation of activity has been detected, its deviation from a reference value will cause other physiological compartments to affect the neuron's ability to generate action potentials.
+
+  , they necessarily contain an error estimation.
 This could be based e.g.
@@
 Returning to the previous question, though the slowness of homeostatic adaptation might allow for temporal fluctuations of activity, it does not overcome the conceptual dichotomy between single cell homeostasis and persistent variability in spontaneous activity.
-Marder and Goaillard speculated that instead of a mechanism controlling activity on a single-cell level, one might consider the possibility of a "global sensor
-of network performance to provide error signals for tuning of the network" \cite{Marder_2006}.
+Marder and Goaillard speculated that instead of a mechanism controlling activity on a single-cell level, one might consider the possibility of a "global sensor of network performance to provide error signals for tuning of the network" \cite{Marder_2006}.
 This concept was used by Sweeney et al.
@@
 
-\subsection{Diffusive Homeostasis}
+\subsection{Diffusive Homeostasis}\label{DIff_Hom_Intro_Section}
 In this thesis, we examined \textit{diffusive homeostasis} as a possible candidate to replace the previously used model of intrinsic plasticity.
@@
 Furthermore, it was able to explain the experimentally observed overrepresentation of bidirectional connections (see \cite{Markram_Connections_1997,Song_Connectivity_2005}) by means of a distance-dependent implementation of synaptic growth.
+
+Generally, it has been argued that the set of rules used in these recurrent networks represent a realization of a minimum ensemble of functional compartments that are required in order to give rise to the desired capabilities.
+The network's ability of self-organization has not only been investigated in terms of network structure itself.
+It also successfully performed in unsupervised sequence-learning tasks, suggesting that the SORN can acquire and maintain associative memory \cite{Hartmann_2016}.
 

### 2017-01-31 draft.tex
.

@@
 \usepackage{caption}
+
+\usepackage{float}
+
 \captionsetup[table]{singlelinecheck=false}
@@
 \end{itemize}
-It should be pointed out that these types of control mechanisms can be simultaneously used in a control system, e.g. through a linear combination.
+It should be pointed out that these types of control mechanisms can be simultaneously used in a control system, e.g.
+through a linear combination.
+Furthermore, the presented terms refer to concepts of linear control theory.
+Thus, in the study of nonlinear feedback systems they only apply in a limited regime where a first order approximation of the system is sufficiently exact.
 
@@
 More complex chains of activity encoding are of course possible, and we will introduce a recent model making additional use of the concentration of nitric oxide in Section \ref{DIff_Hom_Intro_Section} and \ref{NO_Experiments_Section}.
-Given a representation of activity has been detected, its deviation from a reference value will cause other physiological compartments to affect the neuron's ability to generate action potentials.
-
-  , they necessarily contain an error estimation.
-This could be based e.g.
-on the neuron's firing rate of the recent past measured in a given window, or, on a physiological level, e.g.
-a concentration of some molecule within some part of the cell structure.
-In any case, the error estimation requires setting some predefined target that the feedback control will attempt to achieve.
-This, of course, raises the question of what would be an appropriate choice of homeostatic targets.
-
+Given a representation of activity, its deviation from a reference value will cause other physiological compartments to affect the neuron's ability to generate action potentials.
+Referring to the concepts introduced in the previous section, one could then ask what type of control best resembles the actual neuronal control.
+The fact that neurons, whose firing rate was artificially increased or suppressed over a long time, can reliably tune their activity back to the initial state (see e.g.
+\cite{Burrone_2002}) rules out a purely differential type of control.
+The return to baseline under different disturbances seems to point towards an integral-like control.
+However, it is clear that a the ability of a biological system to encode the accumulation of an error signal is limited by the finite amount of available resources.
+For example, the conductance of an ion channel has natural upper and lower bounds that it can not surpass.
+We will pick up this issue in Section \ref{Possible_Modifications_Section}.
+
+In any case, modeling homeostasis includes an error estimation, which requires setting some predefined target that the feedback control will attempt to achieve.
+This, of course, raises the question of how to choose these homeostatic targets.
 Experimental studies have found that neuronal populations exhibit a strong heterogeneity within their individual activity.
@@
 Key aspects of this thesis include an analysis of the stability of the homeostatic control, followed by a comparison of features of the original LIF-SORN and the diffusive variant.
-We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity which has previously been suppressed by the rigid single-cell homeostasis.
-In the face of possible \emph{new} features within the network's structure, we will clarify the causal relation between diffusive spatial interaction and synaptic topology.
+We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity which has previously been suppressed by single-cell homeostasis.
+By an analytic approach we predict activity within the network, thereby gaining an understanding of the relation between spatial structure and firing rates.
+In the face of possible new features within the network's structure, we clarify the causal relation between diffusive spatial interaction and synaptic topology.
 
@@
 
+\newpage
 \subsubsection{Neuron Model}
-
 We used a leaky integrate-and-fire-model for all neurons in the network, whose dynamics are described by a stochastic differential equation:
@@
 Table \ref{LIF_neuron_params} summarizes the aforementioned set of parameters.
-\begin{table}
+\begin{table}[H]
 \begin{tabular}{|l|l|l|}
@@
 In contrast to the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252-256]{Izhikevich_Dynsys}, in the latter case, \cite{Desai_IP} finds evidence that a long-term change in excitability can be attributed to an altered resistance of ionic channels.
-
 In the original LIF-SORN, a simple form of low intrinsic homeostasis was implemented by altering the neurons' firing threshold based on the deviation from a target firing rate.
@@
 The following section describes both models in further detail.
-
 \subsubsection{Modeling of Homeostatic Intrinsic Plasticity}
@@
 
+\newpage
 \section{Results} \label{results}
@@
 \end{align}
-
 where $\tau_e$ and $\tau_i$ are time constants representing the rapidity of firing rate adaptation, $\phi_e$ and $\phi_i$ the respective transition functions between synaptic input and firing rate and $W_{xy}$ the mean synaptic weight from population x to population y.

### 2017-02-03 draft.tex
.

@@
 \caption{A: Relation between Variance of the frequency signal (acquired by binning spikes) and the number of bins within the given time range of $\mathrm{1000-1500\,s}$, taken from three randomly picked excitatory neurons.
-B: Same procedure as in (A) for a randomly chosen excitatory neuron, but time range was $\mathrm{1000-1500\,s}$, which includes the initial phase of non-diffusive homeostasis.
+B: Same procedure as in (A) for a randomly chosen excitatory neuron, but time range was $\mathrm{0-1500\,s}$, which includes the initial phase of non-diffusive homeostasis.
 In both plots, dashed lines are the expected curve of a homogeneous poisson process of the same mean rate.}
@@
 In particular, we were interested in the quality of the predictions with respect to the choice of diffusion constant.
-Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 /s}$, the correlation between measured and predicted firing rates is very good.
-In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /s}$.
+Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 /ms}$, the correlation between measured and predicted firing rates is very good.
+In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /ms}$.
 Since instant diffusion overrides any spatial inhomogeneities, this represented a limiting case where our analytic model could not make any meaningful predictions.

### 2017-02-06 draft.tex
.

@@
 \begin{figure}
+
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/pop_mean_cross_corr.png}
@@
 This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates.
-
 A constant "rate" of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous poisson process of the same total mean firing rate.
@@
 Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.
-
+\newpage
 \section{Further Analysis of the Firing Rate Distribution}
@@
 %% fir_dist_shape_sim_matrix_compare.py
-\includegraphics[width=0.7\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}
 \end{center}
@@
 
+\newpage
 \subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}
@@
 The resulting changes in activity are more slowly and less accurately compensated in the case of larger diffusion constants.
-
 However, for the standard choice of parameters (being roughly based on experimental data), the resulting activity is indeed strongly bound to the spatial structure of excitatory cells.
@@
 Another possibility is the implementation of these bounds by means of the differential equation itself.
-
 In either case, such a modification could break the ability of the network to tune thresholds in such a way that necessarily \emph{all} neurons eventually reach target concentration.
@@
 
+\newpage
 \section{Conclusion and Outlook}\label{Conclusion_Section}
@@
 
-With regard to the future use and implementation of diffusive homeostasis, it could be desirable to cover the essential effects in a more simple and abstract formalism.
+With respect to future use and implementation of diffusive homeostasis, one might desire to cover the essential effects in a more simple and abstract formalism.
 As shown in Section \ref{Mean_Field_Review_Section}, a simple mean field model as presented by Sweeney et al.

### 2017-02-07 draft.tex
.

@@
 
-The notion of synaptic homeostatic plasticity subsumes the observation that neurons being more or less active than a certain set point of mean activity are regulated by means of their incoming synaptic weights.
+The notion of synaptic homeostatic plasticity subsumes the observation that neurons - being more or less active than a certain set point of mean activity - are regulated by means of their incoming synaptic weights.
 Theoretical and experimental studies have suggested that this type of regulation is taking place in a multiplicative manner, thereby retaining proportions between individual synaptic strengths \cite{Syn_Plast_Abbott}.
@@
 As a start, we state that the process and its output controlled by homeostasis is the generation of action potentials and the resulting firing rate.
-As stated earlier, "firing rate" is an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a "sensible" quantity.
-In a nerve cell, this could be represented by e.g.
+As stated earlier, firing rate is an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a "sensible" quantity.
+In a nerve cell this could be represented by e.g.
 the relation between the firing of action potentials and the temporary rise in $\mathrm{Ca^{2+}}$ concentration.
@@
 The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of nitric oxide (NO).
-Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS) , the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
+Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS), the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
 These Enzymes differ in their functionality and dependence on the presence of other molecules.
@@
 The fact that the mean over all power spectra of excitatory thresholds differs from the power spectrum of the mean of these thresholds in its amplitude indicates that not all thresholds oscillate at the same phase.
-Still though, the overall shape of both spectra are equivalent.
+Still though, the overall shapes of both spectra are equivalent.
 \begin{figure}
@@
 \end{figure}
+
 Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further inquiry.
@@
 On a larger, rate-based level, dynamical models of interconnected excitatory and inhibitory groups can exhibit sustained oscillations of activity \cite[p.~270]{Theor_Neur_Dayan}.
-As a simplest model, one can describe the dynamics of the excitatory and inhibitory populations as a two-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$:
+As a simplest model, one can describe the dynamics of the excitatory and inhibitory populations as a two-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$
 \begin{align}
@@
 This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates.
-A constant "rate" of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous poisson process of the same total mean firing rate.
+A constant rate of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous poisson process of the same total mean firing rate.
 As bin sizes increase, possible long-term fluctuations of firing rates can then be identified as deviations from the variance one would expect from a homogeneous process.
@@
 \subsection{Network Topology}\label{Network_Topology_Section}
-So far, we have only analyzed network activity, whereas in this section we present results that relate to features of synaptic topology.
+We have only analyzed network activity so far.
+In this section we present results that relate to features of synaptic topology.
 Since the SORN we used for all simulations only included plastic mechanisms affecting recurrent excitatory connections, these were the subject of our investigations.
@@
 \end{equation}
-$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the "mixture" between single-neuron-homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
+$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the "mixture" between single-neuron homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
 $\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their overall mean.

### 2017-02-08 draft.tex
.

@@
 \subsection{Homeostasis in the Nervous System}
-Among other functional roles of the mammalian central nervous system, it is involved in maintaining crucial properties of the body in a functional regime.
+Among other functional roles of the mammalian central nervous system it is involved in maintaining crucial properties of the body in a functional regime.
 Some examples regarding the organism as a whole are e.g.
@@
 Cannon in 1932 \cite{Wisdom_of_the_Body_Cannon, Homeostasis_Queenan_2012}.
-In more recent years, experimental studies have found evidence for processes within the brain that do not function as a regulatory control for certain aspects of the body, but as a homeostatic control of neural activity itself \cite{Turrigiano_1994,Burrone_2003}.
-Many processes underlying this self-regulatory behavior have been found up till now, and many different biophysical interdependencies have shown to play a role.
+Experimental studies have found evidence for processes within the brain that do not function as a regulatory control for certain aspects of the body, but as a homeostatic control of neural activity itself \cite{Turrigiano_1994,Burrone_2003}in more recent years.
+Many processes underlying this self-regulatory behavior have been found up till now and many different biophysical interdependencies have shown to play a role.
 This diversity makes comparability of these mechanisms a rather difficult task.
-On a relatively general level though, experiments have revealed two main types of neuronal regulation: synaptic homeostatic plasticity and intrinsic homeostasis \cite{Desai_2003}.
+Though, on a relatively general level experiments have revealed two main types of neuronal regulation: synaptic homeostatic plasticity and intrinsic homeostasis \cite{Desai_2003}.
 
@@
 Theoretical and experimental studies have suggested that this type of regulation is taking place in a multiplicative manner, thereby retaining proportions between individual synaptic strengths \cite{Syn_Plast_Abbott}.
-Furthermore, one can regard this form of plasticity as an antagonist to other aspects of synaptic plasticity that affect synaptic strengths in an activity dependent, hebbian fashion.
+One can regard this form of plasticity as an antagonist to other aspects of synaptic plasticity that affect synaptic strengths in an activity dependent, hebbian fashion.
 Forms of regulation belonging to intrinsic homeostasis alter the neurons' capability of spiking upon external input by changing "intrinsic" properties of the nerve cell.
@@
 
-Theoretical models of homeostasis are generally based on a form of feedback control.
-In control theory, this is also known as a \textit{closed loop control}.
+Theoretical models of homeostasis are generally based on a form of feedback control.This is also known as a \textit{closed loop control} in control theory.
 All these systems include a number of necessary functional compartments, which will be briefly introduced in the following.
@@
 \subsubsection{Theory of Control Systems} \label{Control_Sys_Theo_Section}
-Generally, a closed loop control must contain some \emph{process} that is to be regulated.
+A closed loop control generally must contain some \emph{process} that is to be regulated.
 Despite its potential internal complexity, its functional role in the context of a feedback system is to simply generate a time-dependent output based on the history of a time-dependent input.
@@
 However, it might not be possible to directly quantify this desired output in terms of some internal state of the process.
-For example, the firing rate of a neuron is an abstract quantity, which can not be \emph{directly} related to some neuronal state variable.
-Consequently, it might be necessary to transform the actual output of the process into a different signal by a \textit{feedback transducer}.
-As a necessary next step, the (potentially transformed) output is fed into a \textit{comparator}, which, unsurprisingly, compares the given output of the process to some given target or \textit{reference}, typically by subtraction.
+The firing rate of a neuron for example is an abstract quantity, which can not be \emph{directly} related to some neuronal state variable.
+Consequently, it might be necessary to transform the actual output of the process into a different signal by a \textit{feedback transducer}.The (potentially transformed) output is fed into a \textit{comparator} in the next step, which - unsurprisingly - compares the given output of the process to some given target or \textit{reference}, typically by subtraction.
 Note that this reference can but does note have to be a time-dependent signal.
-However, the term \textit{homeostasis} generally refers to a fixed reference, while implementations with a time dependent reference can be regarded as a form of \textit{servomechanism}.
+The term \textit{homeostasis} however generally refers to a fixed reference, while implementations with a time dependent reference can be regarded as a form of \textit{servomechanism}.
 The difference between reference and the feedback transducer's signal is known as the \textit{error} signal.
 This error signal is given to a \textit{controller}, which transforms this error signal into an appropriate input signal for the initially introduced process.
-Additionally, this is also the point in the control loop, where \textit{external disturbances} come into play by being added to the input generated by the controller.
+This is also the point in the control loop where \textit{external disturbances} come into play by being added to the input generated by the controller.
 We illustrated the described flow of feedback control in Figure \ref{Closed_Loop_Control_Illustration}.
@@
 Furthermore, the presented terms refer to concepts of linear control theory.
-Thus, in the study of nonlinear feedback systems they only apply in a limited regime where a first order approximation of the system is sufficiently exact.
+In the study of nonlinear feedback systems they thus only apply in a limited regime where a first order approximation of the system is sufficiently exact.
 
 \subsubsection{Error Signals and Controllers of Neuronal Homeostasis}
-When analyzing or modeling a biological system, a key step characterizing a control loop should be to identify the previously described compartments.
+A key step in characterizing a control loop in the context of biological systems should be to identify the previously described compartments.
 While the functional separation illustrated in Figure \ref{Closed_Loop_Control_Illustration} might seem intuitive and "straight forward", it is not obvious which physiological element should be attributed to a certain abstract element.
 As a start, we state that the process and its output controlled by homeostasis is the generation of action potentials and the resulting firing rate.
-As stated earlier, firing rate is an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a "sensible" quantity.
+Firing rate is - as stated earlier - an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a "sensible" quantity.
 In a nerve cell this could be represented by e.g.
@@
 An example for a homeostatic model making use of intracellular calcium concentration as a measure of spiking activity is the LeMasson-Abbott model \cite{LeMasson_1993}.
-More complex chains of activity encoding are of course possible, and we will introduce a recent model making additional use of the concentration of nitric oxide in Section \ref{DIff_Hom_Intro_Section} and \ref{NO_Experiments_Section}.
+More complex chains of activity encoding are of course possible and we will introduce a recent model making additional use of the concentration of nitric oxide in Section \ref{DIff_Hom_Intro_Section} and \ref{NO_Experiments_Section}.
 Given a representation of activity, its deviation from a reference value will cause other physiological compartments to affect the neuron's ability to generate action potentials.
-Referring to the concepts introduced in the previous section, one could then ask what type of control best resembles the actual neuronal control.
+Referring to the concepts introduced in the previous section one could then ask what type of control best resembles the actual neuronal control.
 The fact that neurons, whose firing rate was artificially increased or suppressed over a long time, can reliably tune their activity back to the initial state (see e.g.
@@
 The return to baseline under different disturbances seems to point towards an integral-like control.
-However, it is clear that a the ability of a biological system to encode the accumulation of an error signal is limited by the finite amount of available resources.
+It is clear however that a the ability of a biological system to encode the accumulation of an error signal is limited by the finite amount of available resources.
 For example, the conductance of an ion channel has natural upper and lower bounds that it can not surpass.
@@
 In any case, modeling homeostasis includes an error estimation, which requires setting some predefined target that the feedback control will attempt to achieve.
-This, of course, raises the question of how to choose these homeostatic targets.
+Of course this raises the question of how to choose these homeostatic targets.
 Experimental studies have found that neuronal populations exhibit a strong heterogeneity within their individual activity.

### 2017-02-09 draft.tex
.

@@
 }
+
+\clubpenalty = 1000 % schliesst Schusterjungen aus
+\widowpenalty = 1000 \displaywidowpenalty = 1000% schliesst Hurenkinder aus
 
@@
 This diversity makes comparability of these mechanisms a rather difficult task.
-Though, on a relatively general level experiments have revealed two main types of neuronal regulation: synaptic homeostatic plasticity and intrinsic homeostasis \cite{Desai_2003}.
+On a relatively general level though experiments have revealed two main types of neuronal regulation: synaptic homeostatic plasticity and intrinsic homeostasis \cite{Desai_2003}.
 
@@
 One can regard this form of plasticity as an antagonist to other aspects of synaptic plasticity that affect synaptic strengths in an activity dependent, hebbian fashion.
-Forms of regulation belonging to intrinsic homeostasis alter the neurons' capability of spiking upon external input by changing "intrinsic" properties of the nerve cell.
+Forms of regulation belonging to intrinsic homeostasis alter the neurons' capability of spiking upon external input by changing intrinsic properties of the nerve cell.
 More precisely, a neurons' ability to form an action potential can change by modifying the conductance of ion channels in its cell membrane \cite[p.
@@
 This output is what one wishes to control and regulate by means of the feedback loop and thus represents the signal that is further processed.
-However, it might not be possible to directly quantify this desired output in terms of some internal state of the process.
+It might not be possible however to directly quantify this desired output in terms of some internal state of the process.
 The firing rate of a neuron for example is an abstract quantity, which can not be \emph{directly} related to some neuronal state variable.
@@
 \end{figure}
-Based on the way the controller generates input for the dynamic process based on the error signal, one can classify control loops by three types:
+Based on the way the controller generates input for the dynamic process based on the error signal one can classify control loops by three types:
 \newpage
@@
 It is clear however that a the ability of a biological system to encode the accumulation of an error signal is limited by the finite amount of available resources.
-For example, the conductance of an ion channel has natural upper and lower bounds that it can not surpass.
+The conductance of an ion channel for example has natural upper and lower bounds that it can not surpass.
 We will pick up this issue in Section \ref{Possible_Modifications_Section}.
@@
 Experimental studies have found that neuronal populations exhibit a strong heterogeneity within their individual activity.
-In particular, many statistical analyses found evidence for a log-normal like distribution of firing rates \cite{Buzsaki_Fir_Rates_2014,Wohrer_Fir_Rates_2012}.
+Many statistical analyses found particular evidence for a log-normal like distribution of firing rates \cite{Buzsaki_Fir_Rates_2014,Wohrer_Fir_Rates_2012}.
 Following these results, one approach of modeling this feature would be to randomly distribute individual targets according to the aforementioned statistics.
@@
 In the light of this conceptual problem, one could, due to a lack of better knowledge, simply define a single global target of activity.
-However, it has been shown that heterogeneity of neural response onto external input within a population is crucial for efficient stimulus encoding \cite{Marsat_2010}.
+It has been shown however that heterogeneity of neural response onto external input within a population is crucial for efficient stimulus encoding \cite{Marsat_2010}.
 Allowing for a broad distribution of activity thus has to be regarded an important compartment of models of cortical activity and structure.
@@
 \subsection{Diffusive Homeostasis}\label{DIff_Hom_Intro_Section}
-In this thesis, we examined \textit{diffusive homeostasis} as a possible candidate to replace the previously used model of intrinsic plasticity.
+In this thesis we examined \textit{diffusive homeostasis} as a possible candidate to replace a previously used model of single-cell intrinsic plasticity.
 The idea and modeling of diffusive homeostasis was adopted from a paper by Sweeney et al.
 \cite{Sweeney_Paper}, which models neural tissue as a two-dimensional surface and a set of points representing the neurons' positions.
-The group of excitatory neurons acted as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position.
+The group of excitatory neurons acted as a point-source of nitric oxide (NO) as well as as a sensor for the NO-concentration at each individual position.
 The production and sensing of NO forms the basis of a feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate.
@@
 suggest that diffusive signaling could resolve the dichotomy between overall stability of firing activity and the need to allow flexibility among individual neurons' activities.
-Intuitively speaking, through the diffusive signal, each neurons receives a "mixture" of its own activity and its neighboring neurons.
+Through the diffusive signal, each neurons receives - intuitively speaking - a mixture of its own activity and its neighboring neurons.
 Thereby individual tuning of firing rates is suppressed while the overall population activity is kept at a constant level.
@@
 In particular, nNOS is sensitive to the concentration of $Ca^{2+}$ ionic Calcium \cite{Knowles_Ca_nNOS,Steinert_NO}.
-Because of its small molecular structure and electrical neutrality, nitric oxide that was synthesized in the nervous system can diffuse freely, which makes it a good candidate to be involved into form of diffusive intracellular communication \cite{Lancaster_1994}.
-
-Due to a depolarization of the membrane potential in the course of an action potential, voltage dependent $Ca^{2+}$-channels open, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98-100]{Hille_Ion_Channels}.
+Nitric oxide that was synthesized in the nervous system can diffuse freely because of its small molecular structure and electrical neutrality, which makes it a good candidate to be involved into a form of diffusive intracellular communication \cite{Lancaster_1994}.
+
+Voltage dependent $Ca^{2+}$-channels open due to a depolarization of the membrane potential in the course of an action potential, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98-100]{Hille_Ion_Channels}.
 A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445-451]{Hille_Ion_Channels}.
 As such, $Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
-
 Experimental studies have also suggested that NO can act as an inhibitory diffusive signaling pathway, decreasing intrinsic excitability \cite{Steinert_NO_2011}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
-In experiments upon neurons in the medial nucleus of the trapezoid body, Steinert et al.
+In experiments upon neurons in the medial nucleus of the trapezoid body Steinert et al.
 found that cells that were subject to NO-signaling by an external source exhibited an increment in outward $\mathrm{K^+}$ current, which, due to its hyperpolarizing effect, can be regarded as a form of intrinsic inhibition.
@@
 It was developed to model features of activity and topology of cortical networks, in particular L5 of the neocortex.
-In these previous implementations, a slow homeostatic mechanism was set up among excitatory neurons through an intrinsic adaptation of excitability.
+A slow homeostatic mechanism was set up among excitatory neurons through an intrinsic adaptation of excitability in these previous implementations.
 This led to the aforementioned problems of homeostatic control: Neural activity was tuned to a globally set target, allowing for no variability.
@@
 have shown that distribution and dynamics of synaptic efficacies measured in rat hippocampus can be reproduced by a binary SORN using a discretized version of spike-timing-dependent plasticity and presynaptic normalization \cite{Pengsheng_2013}.
-Based on this model, Miner et al.
-designed the LIF-SORN.
+Miner et al.
+designed the LIF-SORN based on this model.
 This network reproduced the results of the binary SORN regarding self-organizing synaptic dynamics.
@@
 
-Generally, it has been argued that the set of rules used in these recurrent networks represent a realization of a minimum ensemble of functional compartments that are required in order to give rise to the desired capabilities.
+It has been generally argued that the set of rules used in these recurrent networks represent a realization of a minimum ensemble of functional compartments required in order to give rise to the desired capabilities.
 The network's ability of self-organization has not only been investigated in terms of network structure itself.
@@
 We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity which has previously been suppressed by single-cell homeostasis.
-By an analytic approach we predict activity within the network, thereby gaining an understanding of the relation between spatial structure and firing rates.
+We predict activity within the network by an analytic approach, thereby gaining an understanding of the relation between spatial structure and firing rates.
 In the face of possible new features within the network's structure, we clarify the causal relation between diffusive spatial interaction and synaptic topology.
@@
 The Neural Network was simulated with the code used in \cite{SORN_Paper}, which makes use of the BRIAN spiking neural network simulator \cite{Briansim}.
-Thus, all following explanations regarding the simulation of neurons and mechanisms of synaptic plasticity are based on the methods described in the aforementioned paper.
-
-Across a square area of 1000 $\times$ 1000 $\mu m$, 400 excitatory LIF neurons and 80 inhibitory LIF neurons were assigned random positions.
-Before the start of the simulation, all but recurrent excitatory synapses were randomly generated until a desired connection fraction was reached.
+All following explanations regarding the simulation of neurons and mechanisms of synaptic plasticity are thus based on the methods described in the aforementioned paper.
+
+400 excitatory LIF neurons and 80 inhibitory LIF neurons were assigned random positions across a square area of 1000 $\times$ 1000 $\mu m$.
+All but recurrent excitatory synapses were randomly generated before the start of the simulation until a desired connection fraction was reached.
 The connection probability between two neurons was calculated from a distant dependent Gaussian function with a standard deviation of 200 $\mu m$.
@@
 \end{table}
-
+\newpage
 \subsubsection{Synaptic Plasticity}
-
-\textbf{Synaptic Growth:} At a rate of 1/sec, the random, distance dependent generation of new EE synapses was carried out n times, where n is taken from a normal distribution with mean 920 and standard deviation $\sqrt{920}$.
+\textbf{Synaptic Growth:} The random, distance dependent generation of new EE synapses was carried out n times once per second, where n is taken from a normal distribution with mean 920 and standard deviation $\sqrt{920}$.
 This constant growth rate was tuned to achieve the desired target concentration of 0.1 (see \ref{syn_conn_params}).
@@
 Parameters were chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
-However, for the sake of reduction of computational effort, we used the "nearest neighbor" approximation, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
-
-\textbf{Synaptic Normalization:} Among other, experiments have suggested rescaling of synapses among individual postsynaptic neurons as a form of activity regulation in the brain: While preserving ratios of weights, the mean incoming connectivity is multiplicatively adjusted.
+However, we used the "nearest neighbor" approximation for the sake of reduction of computational effort, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
+
+\textbf{Synaptic Normalization:} Experiments have suggested rescaling of synapses among individual postsynaptic neurons as a form of activity regulation in the brain: The mean incoming connectivity is multiplicatively adjusted, preserving ratios of weights.
 While this general mechanism has been confirmed in many experiments, results differ regarding the question whether the target connectivity is dynamically changing in order to preserve a certain postsynaptic firing rate (homeostatic synaptic scaling), or whether it remains constant, effectively enforcing a synaptic normalization.
-Though the latter does not directly enforce a fixed level of activity, one can argue that in a balanced recurrent network, synaptic normalization still reduces the probability of very high or low firing rates caused by an above- or below-average total synaptic input.
-
+Though the latter does not directly enforce a fixed level of activity, one can argue that in a balanced recurrent network synaptic normalization still reduces the probability of very high or low firing rates caused by an above- or below-average total synaptic input.
 We implemented synaptic normalization by calling a function once per sec., updating each $w_{ji}$ from neuron $i$ to neuron $j$ as follows:
@@
 \end{equation}
-
 $w_{total}$ was set to different values for each of the four types of connections between the excitatory and inhibitory pool of neurons.
-Except for the dynamically populated EE-synapses, these values could be directly set in accordance with the previously given parameters of desired mean individual connection strength, size of the presynaptic population and connection fraction, by calculating $w_{total} = w_{mean} \cdot N_{presyn.
+Except for the dynamically populated EE-synapses these values could be directly set in accordance with the previously given parameters of desired mean individual connection strength, size of the presynaptic population and connection fraction, by calculating $w_{total} = w_{mean} \cdot N_{presyn.
 pop}\cdot p_{connect}$.
@@
 
-\textbf{Short Term Plasticity:} As an additional stabilization of network activity, a short term plasticity (STP) mechanism acting on recurrent excitatory connections was implemented as presented in \cite{Markram_STP}.
+\textbf{Short Term Plasticity:} A short term plasticity (STP) mechanism acting on recurrent excitatory connections was implemented as presented in \cite{Markram_STP} as an additional stabilization of network activity.
 It modulates the effective synaptic weights by multiplying the value stored in the weight matrix $w_{ji}$ by two dynamic variables $x$ and $u$, $w^{effective}_{ji} = w_{ji}\cdot x \cdot u$, each synapse owning a pair $(x,u)$.
@@
 \end{equation}
-Furthermore, each presynaptic spike causes a change of $x$ and $u$ by
+Each presynaptic spike furthermore causes a change of $x$ and $u$ by
 \begin{equation}
@@
 \end{equation}
-
-If no spikes arrive, the system rests at $x\cdot u = U$.
+If no spikes arrive the system rests at $x\cdot u = U$.
 Otherwise, depending on the choice of $\tau_d$ and $\tau_f$, one can achieve a weight modulation that is dominated by potentiation ($\tau_f \gg \tau_d$) or depression ($\tau_f \ll \tau_d$).
-As a rough approximation of the values that were experimentally observed \cite{Markram_STP}, we chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$, giving it a tendency towards potentiation.
+We chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$ as a rough approximation of the values that were experimentally observed \cite{Markram_STP}, giving it a tendency towards potentiation.
 However, one should keep in mind that for $U\in [0,1]$, $x\cdot u \in [0,1]$ always holds, thus the factor $x\cdot u$ has a generally diminishing effect.
-E.g., for our choice of variables, a Poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim 4.5 Hz$, corresponding to $x\cdot u \approx 0.2$.
-"Potentiation" in this context refers to the fact that stronger input strengthens synaptic transmission \emph{compared} to close to zero incoming spikes.
+For our choice of variables for example, a Poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim 4.5 Hz$, corresponding to $x\cdot u \approx 0.2$.
+\textit{Potentiation} in this context refers to the fact that stronger input strengthens synaptic transmission \emph{compared} to close to zero incoming spikes.
 
@@
 Regular-spiking cells are known to down-(up-)regulate their firing rate upon increased (decreased) input on a timescale of tens of milliseconds \cite{Connors_Gutnick_Spike_Patterns,Benda_Herz_Spike_Frequ_Adaption}.
-Since our simulation did not incorporate any rapidly changing external drive, the network itself was not expected to exhibit fast changes of synaptic input, allowing us to neglect this feature.
+The network itself was not expected to exhibit fast changes of synaptic input since our simulation did not incorporate any rapidly changing external drive, which allowed us to neglect this feature.
 On the other hand, a similar form of adaption as a reaction on deprived or enhanced input can be observed on a timescale of hours to days \cite{Desai_IP}.
-In contrast to the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252-256]{Izhikevich_Dynsys}, in the latter case, \cite{Desai_IP} finds evidence that a long-term change in excitability can be attributed to an altered resistance of ionic channels.
-In the original LIF-SORN, a simple form of low intrinsic homeostasis was implemented by altering the neurons' firing threshold based on the deviation from a target firing rate.
-This thesis implemented a new model of slow intrinsic homeostasis, based on the work in \cite{Sweeney_Paper}.
+In the latter case, \cite{Desai_IP} finds evidence that a long-term change in excitability can be attributed to an altered resistance of ionic channels.
+This contrasts the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252-256]{Izhikevich_Dynsys}.
+A simple form of low intrinsic homeostasis was implemented in the original LIF-SORN by altering the neurons' firing threshold based on the deviation from a target firing rate.
+During the research reported by this thesis we implemented a new model of slow intrinsic homeostasis, based on the work in \cite{Sweeney_Paper}.
 The following section describes both models in further detail.
 \subsubsection{Modeling of Homeostatic Intrinsic Plasticity}
-
 Our original model of homeostatic control was described as an operation over discrete time steps $\Delta t = 0.1ms$, carried out for each excitatory neuron:
@@
 \begin{align}
-\dot{{Ca^{2+}}^i}(t) &= -\frac{{Ca^{2+}}^i}{\tau_{Ca^{2+}}} + Ca^{2+}_{spike} \sum_{j} \delta(t-t^i_{spike,j}) \label{Ca_dyn}\\
-\dot{nNOS^i}(t) &= \frac{1}{\tau_{nNOS}} \left(  \frac{{{Ca^{2+}}^i}^3}{{{Ca^{2+}}^i}^3+1} - nNOS^i \right) \label{nNOS_dyn}\\
-\dot{NO}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{neur}^i)\cdot nNOS^i \label{NO_dyn}\\
-\dot{V_t^i}(t) &= \frac{NO(\mathbf{r}_{neur}^i,t)-NO_0}{NO_0\cdot\tau_{V_t}} \label{Theta_dyn}
+\dot{{Ca^{2+}}_i}(t) &= -\frac{{Ca^{2+}}_i}{\tau_{Ca^{2+}}} + Ca^{2+}_{spike} \sum_{j} \delta(t-t_{spike,i,j}) \label{Ca_dyn}\\
+\dot{nNOS_i}(t) &= \frac{1}{\tau_{nNOS}} \left(\frac{{{Ca^{2+}}_i}^3}{{{Ca^{2+}}_i}^3+1} - nNOS_i \right) \label{nNOS_dyn}\\
+\dot{NO}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{neur,i})\cdot nNOS^i \label{NO_dyn}\\
+\dot{V_{t,i}}(t) &= \frac{NO(\mathbf{r}_{neur,i},t)-NO_0}{NO_0\cdot\tau_{V_t}} \label{Theta_dyn}
 \end{align}
@@
 A depolarization within a nerve cell upon a spike-event $t_{spike}$ causes a fixed inflow of ionic current $Ca^{2+}_{spike}$, which is modeled as an instantaneous increase of the $Ca^{2+}$ concentration.
-Over time, the concentration decays exponentially by a time constant $\tau_{Ca^{2+}}$, see \eqref{Ca_dyn}.
+The concentration decays exponentially by a time constant $\tau_{Ca^{2+}}$, see \eqref{Ca_dyn}.
 Though $Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198-203]{Theor_Neur_Dayan}.
 The influence of $Ca^{2+}$ onto nNOS was modeled by Sweeney et al.
-through \eqref{nNOS_dyn}, using the Hill equation \cite{Hill_Equ} to model a cooperative binding mechanism.
+through \eqref{nNOS_dyn} using the Hill equation \cite{Hill_Equ} to model a cooperative binding mechanism.
 The $nNOS$ production is then fed into the "pool" of nitric oxide via point sources located at the neurons' positions.
-Apart from the inflow and the diffusive term $D \nabla^2 NO$, an additional decay term was added to provide a stable finite $NO$ concentration under constant neuronal activity.
-
-Finally, the dynamics of the firing thresholds $V_t^i$ were modeled such that the rate of change is proportional to the relative deviation of the $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
-
-Obviously, the appropriate choice of $NO_0$ is crucial for the goal of achieving and maintaining a certain level of activity.
-However, one cannot directly set a parameter of the model to the desired population activity, as it was the case for canonical intrinsic homeostasis.
-Rather, one needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration.
-Though it is possible to derive this relation in an analytic fashion, for practical purposes of the simulation, we let the system run with the previous homeostatic mechanism, still solving equation \eqref{Ca_dyn}-\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
+An additional decay term was added apart from the inflow and the diffusive term to provide a stable finite $NO$ concentration under constant neuronal activity.
+
+Finally, the dynamics of the firing thresholds $V_{t,i}$ were modeled such that the rate of change is proportional to the relative deviation of the $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
+
+The appropriate choice of $NO_0$ is obviously crucial for the goal of achieving and maintaining a certain level of activity.
+However, one cannot directly set a parameter of the model to the desired population activity as it was the case for canonical intrinsic homeostasis.
+One rather needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration.
+Though it is possible to derive this relation in an analytic fashion, we let the system run with the previous homeostatic mechanism for practical purposes of the simulation, still solving equation \eqref{Ca_dyn}-\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
 This mean was then set to be the target concentration and we switched to diffusive homeostasis.
@@
 \subsection{Simulation of Diffusion}
-
 We solved \eqref{NO_dyn} with the finite difference method on a grid $\mathbf{r}_{i,j}$ with a resolution of $100\times 100$ points.
 Integration over time was carried out by a 4th-order Runge-Kutta method with a time step of $1 ms$.
-On each time step, $\nabla^2 NO(\mathbf{r}_{i,j}) = \nabla^2 NO_{i,j}$ was approximated by
+$\nabla^2 NO(\mathbf{r}_{i,j}) = \nabla^2 NO_{i,j}$ was approximated by
 \begin{equation}
@@
 \end{equation}
-where $h = L/100$ is the distance between neighbored grid points, determined by the length $L$ of the square sheet and the resolution of the numeric grid.
+on each time step, where $h = L/100$ is the distance between neighbored grid points, determined by the length $L$ of the square sheet and the resolution of the numeric grid.
 We implemented three possible boundary conditions into the simulation:
@@
 
-2.) Neumann boundary conditions, with $\nabla NO = (0,0)$ at the boundaries:
+2.) Neumann boundary conditions with $\nabla NO = (0,0)$ at the boundaries:
 \begin{align}
@@
 
-3.) Dirichlet boundary conditions, with $NO = NO_{bound}$ at the boundaries.
-
-If not explicitly marked differently, Neumann boundary conditions were used for most of the simulations.
+3.) Dirichlet boundary conditions with $NO = NO_{bound}$ at the boundaries.\\
+Neumann boundary conditions were used for most of the simulations if not explicitly marked differently.
 This decision relates to the previously described mechanism of synaptic growth: Neurons placed close to the edge of the sheet have a lower connection probability due to the absence of neighboring neurons in the direction perpendicular to the close-by border.
 It therefore models the synaptic growth within a square "cutout" of neural tissue.
-The Neumann boundary condition fits into this picture, since it allows a zero-flux condition at the borders.
+The Neumann boundary condition fits into this picture since it allows a zero-flux condition at the borders.
 This is a reasonable assumption, because NO molecules cannot diffuse out of the tissue (unless they were placed in a fluid surrounding).
@@
 Equation \eqref{NO_dyn} describes the influx of NO as a sum of scaled and spatially shifted Dirac functions.
-Apart from the question, whether this source term results in a well defined, finite solution at the neurons' positions (see section \ref{Matrix_Diff_Model_Section}), it can only be modeled to a certain degree of accuracy, depending on the resolution of the numeric grid.
-In practice, we approximated the point sources of NO as an insertions at individual grid cells at a rate of $nNOS^i(t) / h^2$, where the normalizing divisor $h^2$ ensured the desired total influx per neuron.
+Apart from the question whether this source term results in a well defined, finite solution at the neurons' positions (see section \ref{Matrix_Diff_Model_Section}), it can only be modeled to a certain degree of accuracy depending on the resolution of the numeric grid.
+In practice, we approximated the point sources of NO as an insertions at individual grid cells at a rate of $nNOS_i(t) / h^2$, where the normalizing divisor $h^2$ ensured the desired total influx per neuron.
 This numeric implementation required two additional constraints: First, all random neuron positions were confined to integer multiples of $h$ in x- and y-direction.
 Second, to avoid redundancy and for physiological reasons, each grid cell could only hold one neuron at maximum.
-Both conditions combined led to an iterative generation of positions, where for each neuron a random number generator produced pairs of integers $(n_x,n_y)$, each within $[0,N]$, until an unoccupied pair of integers was found and occupied, moving on to the next neuron.
+Both conditions combined led to an iterative generation of positions where for each neuron a random number generator produced pairs of integers $(n_x,n_y)$, each within $[0,N]$, until an unoccupied pair of integers was found and occupied, moving on to the next neuron.
 Figure \ref{diff_test_plot} shows an example of the resulting NO density throughout a simulation.
@@
 \section{Results} \label{results}
-
-Since our main goal of the implementation of diffusive homeostasis was to allow the network to develop a broader distribution of firing rates across excitatory neurons compared to the original version of homeostasis, we first present the results of a comparison between features of the network activity in both variants in section \ref{activ_analys}.
-Following this is an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see section \ref{theor_osc}.
+We first present the results of a comparison between features of the network activity in both variants in section \ref{activ_analys} since our main goal of the implementation of diffusive homeostasis was to allow the network to develop a broader distribution of firing rates across excitatory neurons compared to the original version of homeostasis.
+This is followed by an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see section \ref{theor_osc}.
 Furthermore, we compare topological features of the network under the influence of diffusive and non-diffusive homeostasis in section \ref{Network_Topology_Section}.
@@
 \subsection{Activity Analysis} \label{activ_analys}
-As a first attempt, we set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$, as given by \cite{Sweeney_Paper}.
+We set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$ on a first attempt, as given by \cite{Sweeney_Paper}.
 Switching between non-diffusive/diffusive homeostasis after 750 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group, the average $NO$ concentration at the excitatory neurons' positions and the average firing threshold within the excitatory group (inhibitory threshold was fixed, see table \ref{LIF_neuron_params}).
 Both homeostatic mechanisms managed to keep the excitatory population activity in the desired range of 3 Hz.
-However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Figure \ref{full_sim_osci}, were in fact regular oscillations across all three depicted variables.
+However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Figure \ref{full_sim_osci} were in fact regular oscillations across all three depicted variables.
 While the oscillation amplitudes undergo a rather unpredictable course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
@@
 The fact that the mean over all power spectra of excitatory thresholds differs from the power spectrum of the mean of these thresholds in its amplitude indicates that not all thresholds oscillate at the same phase.
-Still though, the overall shapes of both spectra are equivalent.
+The overall shapes of both spectra are though still equivalent.
 \begin{figure}
@@
 Rhythmic patterns of activity are a commonly observed phenomenon within the brain.
-Depending on the rate of oscillations, the location within the brain and the spatial scale over which they are observed, different physiological features are found to be responsible, leading to explanatory models at different levels of abstraction.
+Different physiological features are found to be responsible, depending on the rate of oscillations, the location within the brain and the spatial scale over which they are observed.
+This leads to explanatory models at different levels of abstraction.
 On a microscopic, single-neuron level, a so-called slow after-hyper-polarization conductance explains the appearance of bursting behavior: A relatively short period of spiking activity is followed by a longer period of silence.
 This phenomenon can be modeled by a $Ca^{2+}$-dependent $K^{+}$-conductance.
-Upon the bursting period, $Ca^{2+}$ concentration rises, prohibiting continuous spiking due to the activation of $K^{+}$  current until the $Ca^{2+}$ concentration has returned to base-level \cite[p.~203-207]{Theor_Neur_Dayan}.
-However, due to the simplicity of our neuron model, this type of oscillating activity can be ruled out as an explanation.
-
-On a larger, rate-based level, dynamical models of interconnected excitatory and inhibitory groups can exhibit sustained oscillations of activity \cite[p.~270]{Theor_Neur_Dayan}.
+$Ca^{2+}$ concentration rises upon the bursting period, prohibiting continuous spiking due to the activation of $K^{+}$  current until the $Ca^{2+}$ concentration has returned to base-level \cite[p.~203-207]{Theor_Neur_Dayan}.
+However, this type of oscillating activity can be ruled out as an explanation due to the simplicity of our neuron model.
+
+Dynamical models of interconnected excitatory and inhibitory groups can exhibit sustained oscillations of activity \cite[p.~270]{Theor_Neur_Dayan} on a larger, rate-based level.
 As a simplest model, one can describe the dynamics of the excitatory and inhibitory populations as a two-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$
@@
 A persistent oscillation then corresponds to a stable limit cycle in the 2-dimensional phase plane.
-According to the Poincaré-Bendixson theorem, such a limit cycle exists inside a region $R$ if $R$ contains no fixed points and if any trajectory whose starting points lies within $R$ is confined to $R$.
+Such a limit cycle exists inside a region $R$ if $R$ contains no fixed points and if any trajectory whose starting points lies within $R$ is confined to $R$, according to the Poincaré-Bendixson theorem.
 The second condition is equivalent to the condition that for all points $\mathbf{r}_{edge}$ on the edge of $R$, the vector field $\dot{\mathbf{r}}_{edge}$ is facing "into" $R$, see \cite[p.~248]{Dyn_Sys_Hirsch}.
@@
 \end{figure}
-However, one should note that the synaptic input within a spiking network carries an intrinsic randomness: since it is the sum of instantaneous increases in membrane voltage upon arriving spikes, one cannot simply describe it as a mean constant input $J$.
-Rather, if we assume that the arrival of spikes is approximately Poisson-distributed and the time constant of the membrane is small compared to the average interspike-interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \cdot \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
+One should note however that the synaptic input within a spiking network carries an intrinsic randomness: One cannot simply describe it as a mean constant input $J$, since it is the sum of instantaneous increases in membrane voltage upon arriving spikes.
+Rather, if we assume that the arrival of spikes is approximately Poisson distributed and the time constant of the membrane is small compared to the average interspike-interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \cdot \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
 \begin{align}
@@
 $\mathrm{<w_{AB}>,\, <N_{in,AB}>}$ and $\mathrm{<r_A>}$ denote the mean weight of a synapse connection population $\mathrm{A}$ with population $\mathrm{B}$, the mean number of incoming connections at a neuron in population $\mathrm{B}$ and the mean firing rate in population $\mathrm{A}$ (which makes it necessary to assume changes within the firing rate to be slow enough for a quasi-stationary description of the activity).
-Since we can assume intrinsic and input noise to be uncorrelated, the total noise within a neuron of population $\mathrm{B}$ has a standard deviation of 
+The total noise within a neuron of population $\mathrm{B}$ has a standard deviation of 
 \begin{equation}
@@
 \end{equation}
-Apart from the correct description of $\phi_{e/i}$, a third problem is the analytic description of the STP that was present for recurrent excitatory connections in our network.
-In \cite{Markram_STP}, the steady-state value of $\mathrm{x\cdot u}$ for an input of constant rate $\mathrm{r}$ is given by
+since we can assume intrinsic and input noise to be uncorrelated.
+Apart from the correct description of $\phi_{e/i}$, a third problem is the analytic description of STP that was present for recurrent excitatory connections in our network.
+In \cite{Markram_STP} the steady-state value of $\mathrm{x\cdot u}$ for an input of constant rate $\mathrm{r}$ is given by
 \begin{align}
@@
 \end{align}
-When trying to find the fixed point of equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}, one thus needs to incorporate the factor $\mathrm{x_{st.}\cdot u_{st.}}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise.
+One thus needs to incorporate the factor $\mathrm{x_{st.}\cdot u_{st.}}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise when trying to find the fixed point of equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
 
 All these aspects taken together make it impossible to find an analytic expression for the fixed point of Equation \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
-Running a simulation of \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}, including all aforementioned approximations results in a stable configuration depicted in \ref{Dyn_Rate_Approx}.
-For this simulation, we set the relevant parameters to their predefined values and, in addition, extracted the mean threshold of the excitatory population which was set by the non-diffusive homeostasis, see C/C* in Figure \ref{full_sim_osci}, yielding a threshold of $\mathrm{-56.963\, mV}$.
+Running a simulation of \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}, including all aforementioned approximations results in a stable configuration.
+We set the relevant parameters to their predefined values for this simulation and additionally extracted the mean threshold of the excitatory population which was set by the non-diffusive homeostasis, see C/C* in Figure \ref{full_sim_osci}, yielding a threshold of $\mathrm{-56.963\, mV}$.
 The results are depicted in Figure \ref{Dyn_Rate_Approx}.
-The system settled to a fixed point of $\mathrm{(r_{0,e},r_{0,i}) = (2.992\, Hz, 7.144\, Hz)}$, which is quite close to $\mathrm{(3\, Hz, 6.768\, Hz)}$, being the mean excitatory and inhibitory firing rate between 100-750 s of the full simulation (i.e., during non-diffusive homeostasis).
+The system settled to a fixed point of $\mathrm{(r_{0,e},r_{0,i}) = (2.992\, Hz, 7.144\, Hz)}$, which is quite close to $\mathrm{(3\, Hz, 6.768\, Hz)}$, which is the mean excitatory and inhibitory firing rate between 100-750 s of the full simulation (i.e., during non-diffusive homeostasis).
 \begin{figure}
@@
 \end{figure}
-In principal, one could now further quantify the stability of the found fixed point by calculating the Jacobian matrix at $\mathrm{(r_{0,e},r_{0,i})}$.
-For the sake of the initial question though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: Assuming validity of the described rate-model, the recurrent network as such (without homeostasis) is stable under the given choice of parameters.
-Furthermore, on an empirical basis, the occurrence of oscillations appear to be rather dependent on the choice of homeostasis, since apart from the homeostatic mechanism itself, all parameters of the simulation were kept unchanged upon the transition after 750 s.
-Therefore, the following section further analyzes the dynamics underlying the diffusive homeostatic feedback.
+In principal one could now further quantify the stability of the found fixed point by calculating the Jacobian matrix at $\mathrm{(r_{0,e},r_{0,i})}$.
+For the sake of the initial question though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: The recurrent network as such (without homeostasis) is stable under the given choice of parameters, assuming validity of the described rate model.
+Furthermore, on an empirical basis, the occurrence of oscillations appear to be rather dependent on the choice of homeostasis since all parameters of the simulation were kept unchanged upon the transition after 750 s, apart from the homeostatic mechanism itself.
+Therefore, we present in the following section our further analysis of the dynamics underlying the diffusive homeostatic feedback.
 
@@
 \end{figure}
-Thus, in a first attempt of understanding the occurrence of undesired oscillations, we presumed an immediate functional relationship $\mathbf{r}_e (t) = \mathbf{r}_e (\mathbf{V}_{t,e} (t))$, $\mathbf{r}_e$ and $\mathbf{V}_{t,e}$ representing the set of excitatory firing rates and thresholds, respectively.
+We thus presumed an immediate functional relationship $\mathbf{r}_e (t) = \mathbf{r}_e (\mathbf{V}_{t,e} (t))$ in a first attempt of understanding the occurrence of undesired oscillations, where $\mathbf{r}_e$ and $\mathbf{V}_{t,e}$ represent the set of excitatory firing rates and thresholds, respectively.
 
 Describing the neural activity as instantaneous firing rates raises the question how to describe the production of nitric oxide, since the outcome of equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $Ca^{2+}$ concentration caused by spike events.
-Naively, one could replace the sum of Dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{spike} r_i(t)$.
-If \eqref{nNOS_dyn} was a linear homogeneous differential equation, this approximation would indeed allow for the correct calculation of a linear relation between mean firing rate and NO production.
+One could naively replace the sum of Dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{spike} r_i(t)$.
+This approximation would indeed allow for the correct calculation of a linear relation between mean firing rate and NO production if \eqref{nNOS_dyn} was a linear homogeneous differential equation.
 The cubic dependence on $Ca^{2+}$ breaks this simplicity.
-In order to derive an approximate description, we denote two things: First, the target firing rate of 3 Hz and the corresponding mean interspike interval of 0.33...s is large compared to the decay constant of calcium, $\tau_{Ca^{2+}} = \mathrm{0.01\,s}$.
+We note the following in order to derive an approximate description: The target firing rate of 3 Hz and the corresponding mean interspike interval of 0.33...s is large compared to the decay constant of calcium, $\tau_{Ca^{2+}} = \mathrm{0.01\,s}$.
 Consequently, it is very unlikely that one spike event will fall into a region where the calcium concentration, decaying from the instant jump of the previous spike event, is still significantly larger than zero.
@@
 \begin{equation}
-\frac{{Ca^{2+}}^3(t)}{{Ca^{2+}}^3(t)+1} \approx \sum_{i} \theta(t-t^i_{spike}) \frac{exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}})}{exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}}  
+\frac{{Ca^{2+}}^3(t)}{{Ca^{2+}}^3(t)+1} \approx \sum_{i} \theta(t-t^i_{spike}) \frac{exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}})}{exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}} \; .
 \end{equation}
 Therefore, the resulting rate of NO synthesis can be decomposed into a sum of time shifted responses onto a single kernel of calcium concentration as a result of a spike.
-for a spike at $t_{spike}=0$, the solution of \eqref{nNOS_dyn} can be calculated by
+For a spike at $t_{spike}=0$, the solution of \eqref{nNOS_dyn} can be calculated by
 \begin{equation}
@@
 Spikes were drawn from a Poisson process at a rate of 3 Hz.
-As predicted, the simplified model fits very well for sufficiently isolated spike events.
-For the rare event of two subsequent spikes appearing very close to each other, as seen in Figure \ref{nNOS_approx_plot} at approximately 4 seconds, one can observe a slightly smaller but acceptable agreement.
+The simplified model fits very well for sufficiently isolated spike events, as predicted.
+One can observe a slightly smaller but acceptable agreement for the rare event of two subsequent spikes appearing very close to each other, as seen in Figure \ref{nNOS_approx_plot} at approximately 4 seconds.
 \begin{figure}
@@
 A single cell fires in the range of $\mathrm{3\,Hz}$, which is - at least on the time scale of the observed oscillations - not enough to assign an "instantaneous" firing rate.
-
-To deal with this, we introduced an idealized picture of diffusive homeostasis, where diffusion across the tissue is instantaneous.
+\newpage
+We introduced an idealized picture of diffusive homeostasis to deal with this, where diffusion across the tissue is instantaneous.
 This simplification results in a single level of NO-concentration for all neurons, only being modified over time by the sum of all neurons' NO-syntheses $nNOS_{total}(t) \equiv \sum_{i} nNOS^i(t)$ and the decay term $-\lambda NO$.
-To account for the spread of NO, $nNOS_{total}$ must be divided by the area $L^2$ of the tissue.
+, $nNOS_{total}$ must be divided by the area $L^2$ of the tissue to account for the spread of NO.
 Furthermore, we introduce a random fluctuation term $\sigma_{NO} \xi(t)$ that accounts for local, momentary deviations from the mean.
@@
 The amount of noise in the system is a hard-to-predict quantity since it depends on the spatial structure on the diffusive lattice, giving neurons that are further separated less impact onto each other.
-We tried to estimate the noise level based on the same "instant spread"-simplification made in Equation \eqref{NO_dyn_approx} to describe the overall NO-dynamics.
-In the final result, this led to an underestimation of the total energy within the power spectrum.
-However, as long as we assume the noise in the system to be approximately white, noise level only acts as a global scaling factor of the shape of the power spectrum and was thus left open as a model fitting parameter.
-
-From Equation \eqref{NO_dyn_approx} it is clear why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $3 Hz \cdot N_{exc.} = \mathrm{1200\,Hz}$, given the assumption that cells are spiking weakly correlated.
-Furthermore, we argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{total} = N_{exc.}\cdot r_{exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
+We tried to estimate the noise level based on the same instant-spread-simplification made in Equation \eqref{NO_dyn_approx} to describe the overall NO-dynamics.
+This led to an underestimation of the total energy within the power spectrum in the final result.
+However, noise level only acts as a global scaling factor of the shape of the power spectrum as long as we assume the noise in the system to be approximately white and was thus left open as a model fitting parameter.
+
+It is clear from Equation \eqref{NO_dyn_approx} why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $3 Hz \cdot N_{exc.} = \mathrm{1200\,Hz}$, given the assumption that cells are spiking weakly correlated.
+We furthermore argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{total} = N_{exc.}\cdot r_{exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
 We thus propose
@@
 
-As a next step, we wanted to simplify the dynamics of threshold adaption and its effect on the population rate.
+We wanted to simplify the dynamics of threshold adaption and its effect on the population rate as a next step.
 Corresponding to the reduction to a single variable $r_{exc.pop.}(t)$ for the mean excitatory activity in equation \eqref{nNOS_total_dyn}, we wanted to find an appropriate description containing only the mean threshold $V_{t,pop.}(t) = <V_t(t)>$.
@@
 Figure \ref{thresh_r_linfit} shows a linear fit (being of the form $\alpha x + \beta$) of these two quantities plotted against each other.
-Apart from rarely appearing high values of $V_{t,pop.}$, we found a good fit to the linear model.
+We found a good fit to the linear model apart from rarely appearing high values of $V_{t,pop.}$.
 We thus expressed the population rate by $r_{exc.pop.}(t) = r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0})$, where $r_{IP}$ is given in table \ref{Params_IP} as the mean excitatory target firing rate and $V_{t,0} \equiv (r_{IP}-\beta)/\alpha$ is the mean threshold corresponding to the target rate.
@@
 
-Combining these results in a set of equations, we find
+Combining these results in a set of equations, we found
 \begin{align}
@@
 \end{align}
-we can simplify the dynamical system:
+we could simplify the dynamical system:
 \begin{align}
@@
 As stated in the beginning, we were interested in finding an analytic expression for the power spectrum of the mean excitatory threshold.
-Therefore we took the Fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} and \eqref{2d-sys-homeostasis-coord_transf2}, yielding
+We therefore calculated the Fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} and \eqref{2d-sys-homeostasis-coord_transf2}, yielding
 \begin{align}
@@
 Our approximation underestimated the amount of damping within the system (which controls the "peakiness" of the spectrum), as well as predicting a slightly smaller preferred amplitude.
-While the broadness of the spectrum is mostly controlled by the damping term $-\lambda$, the preferred amplitude is controlled by $\frac{\gamma \alpha N_{exc.}}{L^2}$ and $\frac{1}{NO_0\tau_{V_t}}$.
+The preferred amplitude is controlled by $\frac{\gamma \alpha N_{exc.}}{L^2}$ and $\frac{1}{NO_0\tau_{V_t}}$ while the broadness of the spectrum is mostly controlled by the damping term $-\lambda$.
 Since the latter term was taken unaltered from the original system (apart from a shift in phase space), we added $-\lambda$ and $\alpha$ as free fitting parameters and managed to get a very good fit to the simulation data, see Figure \ref{Pow_Spec_Theta_vs_Analytic}.
@@
 This leads to a stronger local increase of concentration, which eventually leads to faster oscillations.
-In either case, since these parameters appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}, both parameters have the same effect onto the shape of the power spectrum.
-
-In the context of the presented power spectra, reducing oscillations meant to reduce height and frequency of the peak of the spectrum.
+In either case, both parameters have the same effect onto the shape of the power spectrum since these parameters appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}.
+
+Reducing oscillations meant to reduce height and frequency of the peak of the spectrum in the context of the presented power spectra.
 We managed to do so by increasing the time constant $\mathrm{\tau_{V_t}}$, as shown in Figure \ref{Peak_Prop_vs_Theta}.
 Moreover, by choosing $\mathrm{\sigma_{NO}}$, $\mathrm{\lambda}$ and $\mathrm{\alpha}$ in accordance to the fit shown in Figure \ref{Pow_Spec_Theta_vs_Analytic} (black curve), Equation \eqref{Pow_Spec_Theta_Final} provides a good prediction for the position and height of the peak.
-For proper comparison, we smoothed the curve of the simulation data in plot (A) of Figure \ref{Peak_Prop_vs_Theta} by a window of $\mathrm{[-5,5]}$ data points, since the maximum of the power spectrum of simulation data is likely to overshoot the analytic prediction due to random fluctuations.
+We smoothed the curve of the simulation data in plot (A) of Figure \ref{Peak_Prop_vs_Theta} by a window of $\mathrm{[-5,5]}$ data points for proper comparison, since the maximum of the power spectrum of simulation data is likely to overshoot the analytic prediction due to random fluctuations.
 \begin{figure}
@@
 \end{figure} 
-To reduce oscillations as much as possible we eventually settled at a 1000-fold increased time constant, $\mathrm{\tau_{V_t}=2500\,s}$.
-Even given the slowness of threshold adaption, homeostasis still managed to keep excitatory network activity in the desired range, as shown in Figure \ref{full_sim_osci_slow_tau_th}.
-Despite a slight regularity of the time course of NO-concentration, no oscillating activity occurs.
+We eventually settled at a 1000-fold increased time constant to reduce oscillations as much as possible,  $\mathrm{\tau_{V_t}=2500\,s}$.
+Homeostasis still managed to keep excitatory network activity in the desired range, as shown in Figure \ref{full_sim_osci_slow_tau_th}, even given the slowness of threshold adaptation.
+No oscillating activity occurred despite a slight regularity of the time course of NO-concentration.
 \begin{figure}
@@
 
-After the elimination of oscillatory activity in the network, we further investigated the features of neural activity, in particular of the excitatory population, since it was exposed to homeostasis.
+We further investigated the features of neural activity after the elimination of oscillatory activity in the network, in particular those of the excitatory population since it was exposed to homeostasis.
 This includes statistics of spike timing, as well as of heterogeneous firing rates among the network.
@@
 This regularity was shown to be achievable in the previous section after slowing down the rate of homeostatic adaption.
-On the level of single cells, interspike intervals should be random, approximately following the statistics of a Poisson process.
+Interspike intervals should be random on the level of single cells, approximately following the statistics of a Poisson process.
 \begin{figure}
@@
 \end{figure}
-Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficients of variation ($\mathrm{CV\equiv\sigma/\mu}$), taken over the set of excitatory and inhibitory neurons, respectively.
-However, in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case, we restricted the statistics of ISIs to neurons whose mean firing rate fall into a window with a width of 1 Hz and a certain mean (see legend in Figure \ref{ISI_CV_compare}).
-Apparently, an approximately exponential distribution of ISIs is preserved for diffusive homeostasis (represented by straight lines in a log-plot), which is characteristic for Poisson processes \cite[p.
+Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficients of variation ($\mathrm{CV\equiv\sigma/\mu}$) taken over the set of excitatory and inhibitory neurons, respectively.
+However, we restricted the statistics of ISIs to neurons whose mean firing rate fall into a window with a width of 1 Hz and a certain mean in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case (see legend in Figure \ref{ISI_CV_compare}).
+An approximately exponential distribution of ISIs is apparently preserved for diffusive homeostasis (represented by straight lines in a log-plot), which is characteristic for Poisson processes \cite[p.
 27]{Theor_Neur_Dayan}.
@@
 
-As an additional possibility of spike-train analysis, we looked at potential correlations across neurons within both populations.
+We looked at potential correlations across neurons within both populations as an additional possibility of spike-train analysis.
 To do so, we calculated cross-correlations for all possible neuron-pairings within a population, excluding auto-correlations.
@@
 \begin{figure}
-
+%plot_cross_corr.py
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/pop_mean_cross_corr.png}
@@
 \end{figure}
-When speculating about the root of this discrepancy one could consider two possibilities: Either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network.
+One could consider two possibilities when speculating about the root of this discrepancy: Either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network.
 Regarding the first, it is certainly true that some amount of information about the activity of one neuron is transferred to another one in its neighborhood via diffusion.
-However, due to the time scale of the homeostatic adaption, the response to fluctuations in the diffusive signal is on the order of seconds, while correlations in Figure \ref{Pop_Mean_Cross_Corr} are taking place within milliseconds.
+However, the response to fluctuations in the diffusive signal is on the order of seconds due to the time scale of the homeostatic adaption, while correlations in Figure \ref{Pop_Mean_Cross_Corr} are taking place within milliseconds.
 Thus, we concluded that a \emph{direct} link between homeostatic signaling and increased correlations can be regarded as implausible and that it must be an effect based on topological differences within the network.
-We investigate these in Section \ref{Network_Topology_Section}.
+We report our investigation on these in Section \ref{Network_Topology_Section}.
 
@@
 By definition, the logarithm of the random variable in question is thus again normally distributed.
-To check for this property we plotted the the distribution of decadic logarithms of firing rates in Figure \ref{Fir_Rate_Dist_Compare} (B).
+We plotted the the distribution of decadic logarithms of firing rates in Figure \ref{Fir_Rate_Dist_Compare} (B) to check for this property.
 In (A), we found a skewness of $\mathrm{v_{Diff} = 0.765}$, in (B) $\mathrm{v_{Diff,log} = -0.488}$.
@@
 Despite of fluctuations within the firing rate on small time scales due to the inherent nature of - approximately - random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds.
-This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates.
-A constant rate of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous poisson process of the same total mean firing rate.
+This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: The resulting distribution might be narrower than what one could expect from a distribution of momentary rates if firing rates fluctuate too much during the period over which means were calculated.
+A constant rate of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous Poisson process of the same total mean firing rate.
 As bin sizes increase, possible long-term fluctuations of firing rates can then be identified as deviations from the variance one would expect from a homogeneous process.
@@
 (A) was taken from $\mathrm{1000-1500\,s}$, which is well inside the phase of diffusive homeostasis.
-As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{mean}\cdot n_{bins}/T_{total}}$, though slight deviations can be seen as a different factor of proportionality.
+As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous Poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{mean}\cdot n_{bins}/T_{total}}$, though slight deviations can be seen as a different factor of proportionality.
 (B) acts as an illustration showing a counterexample: Here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis.
-For almost all of the neurons, this will cause a transition of firing rate between 3 Hz and a new rate different from 3 Hz.
-This inhomogeneity is represented by the increasing positive relative deviation from the dashed line for small number of bins (i.e., large bin widths), even increasing again for a very few number of bins.
+This will cause a transition of firing rate between 3 Hz and a new rate different from 3 Hz for almost all of the neurons.
+Inhomogeneity is represented by the increasing positive relative deviation from the dashed line for small number of bins (i.e., large bin widths), even increasing again for a very few number of bins.
 \begin{figure}
@@
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/sim_f_var_vs_hom_poisson.png}
-\caption{A: Relation between Variance of the frequency signal (acquired by binning spikes) and the number of bins within the given time range of $\mathrm{1000-1500\,s}$, taken from three randomly picked excitatory neurons.
-B: Same procedure as in (A) for a randomly chosen excitatory neuron, but time range was $\mathrm{0-1500\,s}$, which includes the initial phase of non-diffusive homeostasis.
-In both plots, dashed lines are the expected curve of a homogeneous poisson process of the same mean rate.}
+\caption{A: Relation between variance of the frequency signal (acquired by binning spikes) and the number of bins within the given time range of $\mathrm{1000-1500\,s}$, taken from three randomly picked excitatory neurons.
+B: Same procedure as in (A) for a randomly chosen excitatory neuron, but the time range was $\mathrm{0-1500\,s}$, which includes the initial phase of non-diffusive homeostasis.
+Dashed lines are the expected curve of a homogeneous Poisson process of the same mean rate in both plots.}
 \label{f_Var_vs_n_Bin}
@@
 
-As an additional test, we applied external Poisson input for $\mathrm{t\geq 300\, s}$ to two excitatory subgroups to see whether changes in the firing rate of these subgroups is leveled out by homeostasis or retained.
+We applied external Poisson input for $\mathrm{t\geq 300\, s}$ onto two excitatory subgroups as an additional test to see whether changes in the firing rate of these subgroups are leveled out by homeostasis or retained.
 Members of these subgroups were picked randomly and independent of their position.
@@
 \end{center}
-\caption{Excitatory population firing rate of subgroups subject to external poisson input for $\mathrm{t\geq 300\, s}$.
+\caption{Excitatory population firing rate of subgroups subject to external Poisson input for $\mathrm{t\geq 300\, s}$.
 Red and green subgroups consist of 100 randomly picked excitatory neurons each.
@@
 \end{figure}
-To further quantify this dependence, we also investigated the influence of the diffusion constant onto the distribution's skewness, shown in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} (B).
-Compared to the standard deviation, we see a similar but not as clear trend with a drop for very small diffusion constants, even occasionally resulting in a left-skewed distribution (negative D-values).
+We also investigated the influence of the diffusion constant onto the distribution's skewness, shown in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} (B), to further quantify this dependence.
+Compared to the standard deviation, we saw a similar but not as clear trend with a drop for very small diffusion constants, even occasionally resulting in a left-skewed distribution (negative D-values).
 
 A naturally emerging question when altering the diffusion constant is how the firing rate behaves in the absolute limit of infinitely fast diffusion.
-In fact, simulation-wise this case is quite easy to simulate: One simply has  to feed all NO-sources into a single scalar variable of NO concentration.
-In particular, this will provide the same NO readout for all excitatory neurons, which means that all excitatory thresholds change at the same rate all the time, only shifting their initial random distribution.
+In fact, this case is quite easy to implement simulation-wise: One simply has to feed all NO-sources into a single scalar variable of NO concentration.
+This will provide the same NO readout for all excitatory neurons, which means that all excitatory thresholds change at the same rate all the time, only shifting their initial random distribution.
 Figure \ref{Fir_Rate_Dist_Instant_compare} shows the distribution for this special limiting case.
@@
 \subsection{Network Topology}\label{Network_Topology_Section}
-We have only analyzed network activity so far.
+We have only presented our analysis of network activity so far.
 In this section we present results that relate to features of synaptic topology.
@@
 Omitting the distance dependence of connection probability for synaptic growth led to a slightly higher connection fraction.
-To compare these previous results to the diffusive case, we ran a full simulation under diffusive homeostasis, including the growth phase by setting the target concentration to an appropriate value that was determined in a previous simulation with non-diffusive homeostasis.
+We ran a full simulation under diffusive homeostasis to compare these previous results to the diffusive case, including the growth phase by setting the target concentration to an appropriate value that was determined in a previous simulation with non-diffusive homeostasis.
 The resulting time course of CF is depicted in Figure \ref{CF_plot}.
@@
 Though fluctuating, the synaptic growth rate was kept at a constant level of 920 synapses/second.
-In consequence, any differences in Figure \ref{CF_plot} must originate in different pruning rates.
+Any differences in Figure \ref{CF_plot} must therefore originate in different pruning rates.
 Figure \ref{STDP_change} shows the mean and standard deviation of weight changes due to STDP between two normalization steps.
@@
 However, the difference of mean changes is orders of magnitude smaller than the width of fluctuations.
-Thus, while it might seem counter-intuitive that a higher positive mean weight change comes with a smaller chance of synaptic survival, we attribute the main cause of overshooting in Figure \ref{CF_plot} to the increased fluctuation of weights, since it raises the chance of going below the pruning threshold within a given time interval.
+Thus, while it might seem counter-intuitive that a higher positive mean weight change comes with a smaller chance of synaptic survival, we attribute the main cause of overshooting in Figure \ref{CF_plot} to the increased fluctuation of weights since it raises the chance of going below the pruning threshold within a given time interval.
 \begin{figure}
@@
 The absence of this breaking of spatial homogeneity even led to an under-representation of bidirectional connections, which is known to be an effect of STDP in recurrent networks \cite{Syn_Plast_Abbott}.
-As shown in Figure \ref{RC_CFB_plot}, the separation between simulations with and without a spatial connection profile is retained.
+The separation between simulations with and without a spatial connection profile is retained, as shown in Figure \ref{RC_CFB_plot}.
 \begin{figure}
@@
 To get an approximative explanation for the observed slope in the region of small lifetimes, we note that short synaptic lifetimes are most likely coming from synapses whose weights did not reach large values compared to the initial weight.
-In this regime of small weights, the effect of multiplicative normalization is small compared to additive STDP.
-Therefore, small weights are determined by additive quasi-random (due to their weak coupling to the postsynaptic neuron) fluctuations, which, as a very simple approximation, can be described as a Brownian motion with certain standard deviation $\mathrm{\sigma}$.
+The effect of multiplicative normalization is small compared to additive STDP in this regime of small weights.
+Small weights are therefore determined by additive quasi-random (due to their weak coupling to the postsynaptic neuron) fluctuations, which, as a very simple approximation, can be described as a Brownian motion with a certain standard deviation $\mathrm{\sigma}$.
 The first hitting time of this Brownian motion is described by a Lévy distribution:
@@
 \end{equation}
-For larger $\mathrm{t}$, the dominating term is $\mathrm{t^{-3/2}}$, which roughly resembles the power-law exponents found in Figure \ref{Syn_Lifetimes}.
+The term $\mathrm{t^{-3/2}}$ dominates for larger $\mathrm{t}$, which roughly resembles the power-law exponents found in Figure \ref{Syn_Lifetimes}.
 
@@
 A comparison of statistics generated with shuffled versions of the weight matrices illustrates that above-chance exceptionally strong outgoing weights were indeed present.
-Furthermore, we noted that the difference between shuffled matrices corresponding to non-diffusive and diffusive homeostasis is in line with our observation from Figure \ref{Weight_Dist}, which indicated a broader distribution of weights for diffusive homeostasis.
+We noted further that the difference between shuffled matrices corresponding to non-diffusive and diffusive homeostasis is in line with our observation from Figure \ref{Weight_Dist}, which indicated a broader distribution of weights for diffusive homeostasis.
 \begin{figure}
@@
 
-In contrast to our model, Effenberger et al.
-identified the presence of inhibitory STDP as a necessary mechanism for the development of this feature.
+Effenberger et al.
+identified the presence of inhibitory STDP as a necessary mechanism for the development of this feature, in contrast to our model.
 On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: It weakens inhibitory currents for some neurons, which cause these neurons to have more above-average firing rates.
@@
 \end{figure}
-Furthermore, it is interesting to note that on a logarithmic weight scale, we found a roughly linear relationship.
+Furthermore, it is interesting to note that we found a roughly linear relationship on a logarithmic weight scale.
 Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.
@@
 \section{Further Analysis of the Firing Rate Distribution}
-On a preliminary level, the results of section \ref{Fir_Dist_Section} were positive with respect to our goal of achieving a broad and skewed firing rate distribution.
+The results of section \ref{Fir_Dist_Section} were positive on a preliminary level regarding our goal of achieving a broad and skewed firing rate distribution.
 Following this, we tried to further gain insight into the actual shape of the resulting distribution.
@@
 \begin{equation}
-\dot{V_t^i}(t) = \frac{1}{\tau_{HIP}} \left( (1-\alpha)\frac{\phi_i-\phi_0}{\phi_i} +\alpha \frac{\langle \phi \rangle-\phi_0}{\langle \phi \rangle} \right)\;. 
+\dot{V_{t,i}}(t) = \frac{1}{\tau_{HIP}} \left( (1-\alpha)\frac{\phi_i-\phi_0}{\phi_i} +\alpha \frac{\langle \phi \rangle-\phi_0}{\langle \phi \rangle} \right)\;. 
 \label{diff_hom_simpl_sweeney}
 \end{equation}
-$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the "mixture" between single-neuron homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
+$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the mixture between single-neuron homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
 $\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their overall mean.
 
-Furthermore, the spiking recurrent network was replaced by a set of non-interacting non-spiking neurons, whose individual mean firing rates were calculated by
-\begin{align}
-\phi_i(\mu_i,\sigma_i,V_t^i) &= \left[ \sqrt{\pi}\tau_m \int_{x_-}^{x_+} dx e^{x^2} erfc(-x) \right]^{-1} \label{LIF_Fir_Rate_with_Noise1_copy}\\
+The spiking recurrent network was replaced by a set of non-interacting non-spiking neurons whose individual mean firing rates were calculated by
+\begin{align}
+\phi_i(\mu_i,\sigma_i,V_{t,i}) &= \left[ \sqrt{\pi}\tau_m \int_{x_-}^{x_+} dx e^{x^2} erfc(-x) \right]^{-1} \label{LIF_Fir_Rate_with_Noise1_copy}\\
 x_- &= (V_r-E_l-\mu_i\tau_m)/\sigma_i \label{LIF_Fir_Rate_with_Noise2_copy}\\
-x_+ &= (V_t^i-E_l-\mu_i\tau_m)/\sigma_i \label{LIF_Fir_Rate_with_Noise3_copy}
+x_+ &= (V_{t,i}-E_l-\mu_i\tau_m)/\sigma_i \label{LIF_Fir_Rate_with_Noise3_copy}
 \end{align}
 which is the same formula we used in \eqref{LIF_Fir_Rate_with_Noise1}.
-Furthermore, in accordance to \cite{Roxin_Firing_Rate_Distribution}, mean and standard deviation of the inputs were calculated by Sweeney et al.
+Additionally, in accordance to \cite{Roxin_Firing_Rate_Distribution}, mean and standard deviation of the inputs were calculated by Sweeney et al.
 as
@@
 \end{align}
-where $\nu$ is the mean population firing rate, $\phi_i$ the individual firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $V_t^i$ its synaptic input mean and standard deviation and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant.
+where $\nu$ is the mean population firing rate, $\phi_i$ the individual firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $V_{t,i}$ its synaptic input mean and standard deviation and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant.
 Synaptic efficacy and number of incoming neurons were drawn randomly to match the statistics of the actual network topology.
-Self consistency was achieved by iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate1} until the desired precision of convergence is reached.
-
-The authors claimed that this model reproduces results of the full network, in particular that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or a larger $\alpha$, respectively).
+Self consistency was achieved by iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate1} until the desired precision of convergence was reached.
+
+The authors claimed that this model reproduces results of the full network, in particular that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or a corresponding larger $\alpha$).
 
 We tested this dynamic mean-field model by simulating a similar population, but used an interacting population of neurons of the same size as in the previous simulations (400 excitatory, 80 inhibitory neurons).
-This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $\mathrm{1500 \, s}$ (i.E., the "stable" phase).
+This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $\mathrm{1500 \, s}$ (i.E., the stable phase).
 Individual values for $\mu_i$ and $\sigma_i$ were then calculated according to \eqref{sweeney_self_consist_rate2} and \eqref{sweeney_self_consist_rate3}.
@@
 Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics of excitatory rates and thresholds for $\mathrm{\alpha=\lbrace 0.4,0.8,0.9,1.0\rbrace}$.
-Apparently, except for the limiting case of $\mathrm{\alpha=1}$, all rates approach the same target rate of $\mathrm{3\,Hz}$ and thresholds move towards the same configuration for either choice of $\mathrm{\alpha}$.
+Apparently, all rates approach the same target rate of $\mathrm{3\,Hz}$ and thresholds move towards the same configuration for either choice of $\mathrm{\alpha}$ except for the limiting case of $\mathrm{\alpha=1}$.
 A significant difference only exists within the transient dynamics leading to the steady state.
@@
 \end{figure}
-These findings led us to the conclusion that, apart from the special case $\mathrm{\alpha=1}$, which is the equivalent to "instantaneous" diffusion, a mean-field model describing the diffusive signal as a mixture of individual activity and all neurons is not suitable for explaining the existence of stable heterogeneous distributions of rates for a broad range of diffusion constants.
+These findings led us to the conclusion that - apart from the special case $\mathrm{\alpha=1}$, which is the equivalent to instantaneous diffusion - a mean-field model describing the diffusive signal as a mixture of individual activity and all neurons is not suitable for explaining the existence of stable heterogeneous distributions of rates for a broad range of diffusion constants.
 We did not intent to debase the validity of results of the mean-field model of Sweeney et al.
-However, by analyzing Equation \ref{diff_hom_simpl_sweeney}, we could show that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, given any value of $\mathrm{\alpha}$ except $\mathrm{\alpha=1}$.
+However, we could show that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, given any value of $\mathrm{\alpha}$ except $\mathrm{\alpha=1}$.
 This can be seen by setting the left hand side of Equation \eqref{diff_hom_simpl_sweeney} to $0$ (which is necessarily the case in the steady state) and rearranging the equation:
@@
 Since the left term is monotonically increasing as a function of $\phi_i$ as long as $\mathrm{\alpha<1}$, only one specific solution $\phi_i = \Phi$ for all $i$ exists that equals the given term on the right.
-Furthermore, this implies $\langle \phi \rangle = \Phi$.
+This implies $\langle \phi \rangle = \Phi$.
 Thus,
@@
 \begin{align}
-\phi(\mu_i(\nu),\sigma_i(\nu),V_t^i) &= \phi_0 \label{fixed_thresh_dist_argument1} \\
+\phi(\mu_i(\nu),\sigma_i(\nu),V_{t,i}) &= \phi_0 \label{fixed_thresh_dist_argument1} \\
 \mu_i &= J_iC_i \phi_0 \tau \label{fixed_thresh_dist_argument2} \\
 \sigma_i &= J_i\sqrt{C_i \phi_0  \tau} \label{fixed_thresh_dist_argument3} \\
-\rightarrow V_t^i &= {\phi}^{-1}(J_iC_i \phi_0 \tau,J_i\sqrt{C_i \phi_0  \tau},\phi_0) \label{fixed_thresh_dist_argument4}
-\end{align}
-which implies that the set of $V_t^i$ only depends on the given network topology.
+\rightarrow V_{t,i} &= {\phi}^{-1}(J_iC_i \phi_0 \tau,J_i\sqrt{C_i \phi_0  \tau},\phi_0) \label{fixed_thresh_dist_argument4}
+\end{align}
+which implies that the set of $V_{t,i}$ only depends on the given network topology.
 
@@
 Furthermore, equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma \cdot r_i}$, $\mathrm{r_i}$ representing a neuron's rate and $\mathrm{\gamma}$ being defined by Equation \eqref{2d-sys-fixed-points1}.
-In this section we discuss the implications of an "in-between" description, only applying the second simplification, but retaining the diffusive term:
+In this section we discuss the implications of an in-between description, only applying the second simplification, but retaining the diffusive term:
 \begin{equation}
@@
 \end{equation}
-As in the previous section, we ask for the steady-state distribution of rates. Thus as a first step, we had to solve
+As in the previous section, we ask for the steady-state distribution of rates. Thus, as a first step, we had to solve
 \begin{equation}
@@
 \end{equation}
-At this point, we were aware of the fact that these equations completely neglect fluctuations of NO-synthesis due to spiking.
+We were aware at this point that these equations completely neglect fluctuations of NO-synthesis due to spiking.
 However, given the very slow adaption of thresholds, which are responsible for changes of firing rates, we argued that noise can be neglected in the sense that $\mathrm{\lbrace r_i\rbrace}$ represents the set of mean firing rates whose resulting spike-train-induced NO-synthesis \emph{on average} fulfills \eqref{simple_NO_dyn_with_diff_equil} and \eqref{NO_equil_cond}.
@@
 which is a two-dimensional Helmholtz equation with a superposition of rescaled Dirac functions.
-Thus, the solution of $\mathrm{NO}$ is composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of the equation.
+The solution of $\mathrm{NO}$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of the equation.
 For each delta function $\delta^2(\mathbf{x}-\mathbf{x}_i)$, the solution is
@@
 This solution reveals a fundamental problem of modeling the sources of NO-production as point sources: the fact that $\mathrm{K_0(x)}$ diverges to infinity for $\mathrm{x\rightarrow 0}$.
-It is merely due to the finite density of the numeric grid used for the simulation of the diffusion that allows for a finite target value of concentration.
+It is merely due to the finite density of the numeric grid used for the simulation of diffusion that allows for a finite target value of concentration.
 Note that this problem only occurs in the two- or three-dimensional version of the differential equation, whereas in one dimension, the fundamental solution can be expressed as an exponential function with respect to the distance to the origin, resulting in a well-defined finite value at $\mathrm{x=0}$.
@@
 \end{equation}
-Still, to acquire any prediction from this model, we had to find a modified, non-diverging version of $\mathrm{\psi (d(\mathbf{x}_{neur,i},\mathbf{x}))}$ that retains the shape given by \eqref{solution_diff_equil_bessel} for larger distances but approaches the correct "numeric error"-value at the origin, determined by the spacing of the numeric grid.
-We "solved" this problem by the following expression:
+Still, we had to find a modified, non-diverging version of $\mathrm{\psi (d(\mathbf{x}_{neur,i},\mathbf{x}))}$ to acquire any prediction from this model.
+It had to retain the shape given by \eqref{solution_diff_equil_bessel} for larger distances but approach the correct numeric error value at the origin, determined by the spacing of the numeric grid.
+We solved this problem by the following expression:
 \begin{equation}
@@
 We chose $\mathrm{\varepsilon=10}$ for all further calculations.
-To find an expression for $\mathrm{\psi_0}$, we took the simple approach of interpreting this value as a mean of the analytic solution across the area covered by the corresponding grid cell.
+We took the simple approach of interpreting this value as a mean of the analytic solution across the area covered by the corresponding grid cell to find an expression for $\mathrm{\psi_0}$.
 As an additional simplification, we substituted the necessary integration over the square grid cell by a circular area of equal size around the source.
@@
 Figure \ref{Psi_Approximation_Compare} shows a comparison between the numerically calculated solution and the expression given by \ref{Numeric_Solution_Expression_Trick}.
-As expected, the approximation fitted very well for nonzero values.
+The approximation fitted very well for nonzero values, as expected.
 The value at the critical point in the origin was slightly underestimated by \eqref{Numeric_Grid_Bessel_Approx}, but nonetheless fitted well into the overall shape.
@@
 \end{figure}
-Thus, we took this approximation as a basis for further calculations of the interaction-matrix $\mathrm{\hat{\psi}}$.
+We took this approximation as a basis for further calculations of the interaction-matrix $\mathrm{\hat{\psi}}$.
 
 By simply calculating all matrix elements of $\mathrm{\hat{\psi}}$ by means of Equation \eqref{interact_matrix_elements}, one would neglect the finite boundaries of the system, which would cause neurons close to the edge to "bleed" into empty space.
-This in turn would cause the solution of \eqref{NO_equil_cond_interact_matrix_operator} to contain an over-representation of high firing rates, since close-to-the-edge neurons would need to compensate for their lack of neighbors.
+This in turn would cause the solution of \eqref{NO_equil_cond_interact_matrix_operator} to contain an over-representation of high firing rates since close-to-the-edge neurons would need to compensate for their lack of neighbors.
 Thus, we had to account for the boundary conditions used in the network simulation.
-As described in section \ref{methods}, we simulated the network mostly with Neumann boundary conditions as well as periodic boundaries.
+We simulated the network mostly with Neumann boundary conditions as well as periodic boundaries, as described in section \ref{methods}.
 Both types can be modeled by extending the neurons' population through spatially shifted and mirrored versions of the base population (see Figure \ref{Bound_Cond_Patches}):
@@
 \end{equation}
-For the Neumann boundary condition, one finds
+For the Neumann boundary condition, we found
 \begin{align}
@@
 Note that the shift was applied to the second position.
-Theoretically, $n_x$,$n_y$ is iterated over all integers and in this case it is irrelevant whether to shift the first or the second position.
-For our calculations, we obviously had to limit the amount of elements of the sum such that copies that are shifted further away can be neglected.
-For the sake of performance, the number of terms in the sum was adjusted to suffice the given diffusion constant.
+Theoretically, $n_x$,$n_y$ are to be iterated over all integers and in this case it is irrelevant whether to shift the first or the second position.
+We obviously had to limit the amount of elements of the sum for our calculations, such that copies that are shifted further away can be neglected.
+For the sake of performance the number of terms in the sum was adjusted to suffice the given diffusion constant.
 
@@
 After having worked out the analytical basis, we compared the prediction obtained from numerically solving \eqref{NO_equil_cond_interact_matrix_operator} for certain spatial configurations of neurons to the steady-state firing rates of the full spiking network with the same spatial structure.
-In particular, we were interested in the quality of the predictions with respect to the choice of diffusion constant.
+We were particularly interested in the quality of the predictions with respect to the choice of diffusion constant.
 Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 /ms}$, the correlation between measured and predicted firing rates is very good.
 In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /ms}$.
-Since instant diffusion overrides any spatial inhomogeneities, this represented a limiting case where our analytic model could not make any meaningful predictions.
+This represented a limiting case where our analytic model could not make any meaningful predictions, since instant diffusion overrides any spatial inhomogeneities.
 The outcome of the third case shown in the plot, $\mathrm{D=0}$, is correctly predicted by the analytic model.
-In general, instant diffusion as well as $\mathrm{D=0}$ overrode the effect of spatial heterogeneity onto firing rates.
+In general, instant diffusion as well as $\mathrm{D=0}$ overrode the effects of spatial heterogeneity onto firing rates.
 \begin{figure}
@@
 \caption{Measured firing rates (t=1200-1500 s) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
-For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably "large" diffusion constant of $\mathrm{D=100\, \mu m^2 /s}$.}
+For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably large diffusion constant of $\mathrm{D=100\, \mu m^2 /s}$.}
 \label{Rand_Matrix_Sol_vs_Sim}
@@
 \end{figure}
-Naturally, these observations led us to the question of how the correlation between predicted measured firing rates behaves in between the aforementioned limits.
+These observations naturally led us to the question of how the correlation between predicted measured firing rates behaves in between the aforementioned limits.
 Especially, we were interested in the range of the diffusion constant for which our model provides a good description of the full spiking network's activity.
@@
 We recalled that we characterized the dependence of the shape of the firing rate distribution onto $\mathrm{D}$ by means of its standard deviation and skewness in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.
-To test whether our analytic model predicts this dependence, we generated random ensembles of neuron positions, solved the linear system of rates and extracted the resulting standard deviation and skewness.
-Thereby, we found a good fit of the resulting histogram compared to the simulation data, see Figure \ref{Std_Skew_Dist_vs_Data}.
+To test whether our analytic model predicts this dependence we generated random ensembles of neuron positions, solved the linear system of rates and extracted the resulting standard deviation and skewness.
+We thereby found a good fit of the resulting histogram compared to the simulation data, see Figure \ref{Std_Skew_Dist_vs_Data}.
 \begin{figure}
@@
 In summary, shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuation in the spatial distribution of neurons.
-To further back up this result, we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
-By doing so, all neurons were given the same structure of neighbors.
-Due to symmetry, we expected that all neurons then should - in theory - exhibit the exact same firing rate.
+To further back up this result we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
+By doing so all neurons were given the same structure of neighbors.
+We expected that all neurons then should - in theory - exhibit the exact same firing rate due to symmetry.
 Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the result, being a significantly narrower distribution.
@@
 \subsubsection{Low-Density Neighborhoods correlate with strong outgoing Connections}
-In Section \ref{Section_Mean_outgoing_Weights}, we stated that diffusive homeostasis allowed the network do develop few neurons with exceptionally strong outgoing weights.
+In Section \ref{Section_Mean_outgoing_Weights} we stated that diffusive homeostasis allowed the network do develop few neurons with exceptionally strong outgoing weights.
 Furthermore, we found this effect to be present in neurons with an highly above-average firing rate.
@@
 More specific, regions of neurons with above average firing rates should develop stronger outgoing connections.
-To get an intuitive understanding of what characterizes regions of above-average firing rates, we interpreted the homeostatic condition in the high-neuron-density limit as an approximation of a continuous integral equation:
+To get an intuitive understanding of what characterizes regions of above-average firing rates we interpreted the homeostatic condition in the high-neuron-density limit as an approximation of a continuous integral equation:
 \begin{equation}
@@
 where $\mathrm{\rho(\mathbf{x})}$ is the local neuron density and $\mathrm{r(\mathbf{x})}$ the local firing rate.
-Here, we assumed that our tissue is of infinite size and thus the integral is carried out over $\mathbb{R}^2$.
-In this form, the solution for $\mathrm{r(\mathbf{x})}$ is quite trivial:
+Here we assumed that our tissue is of infinite size and thus the integral is carried out over $\mathbb{R}^2$.
+In this form the solution for $\mathrm{r(\mathbf{x})}$ is quite trivial:
 \begin{equation}
@@
 Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should correlate with strong outgoing weights and vice versa.
-To test this hypothesis, we approximated the local neuron density by means of a a Gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$.
+We approximated the local neuron density by means of a a Gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$ to test this hypothesis.
 Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} shows the results.
@@
 \subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}
-Since our analytic results revealed that a strong correlation between spatial structure and result firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors, we considered the possibility that a wider spread of each individual NO-source could locally decrease distinguishability between neurons.
-Thereby, it might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values.
+We considered the possibility that a wider spread of each individual NO-source could locally decrease distinguishability between neurons since our analytic results revealed that a strong correlation between spatial structure and result firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors.
+Thereby it might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values.
 The biological plausibility of this idea is discussed in Section \ref{Possible_Modifications_Section}.
@@
 Though being unintended in our recurrent network, the occurrence and necessary analysis of persistent oscillations led to a better understanding of their origin and the need for slow timescales of homeostatic adaptation.
-In another theoretical study, Harnack et al.
+In another theoretical study Harnack et al.
 treated the necessity of slow homeostatic adaptation in a more general fashion \cite{Stability_Homeostasis_Harnack_2015}.
-Among other results, it is reported that increasing the number of dynamic variables in a feedback system decreases its stability.
-This is in line with the fact that our previously used, single-cell homeostatic control (see Equation \eqref{can_hom_rate}) exhibited no instabilities, since it only incorporated firing thresholds as dynamic variables.
+Among other results it is reported that increasing the number of dynamic variables in a feedback system decreases its stability.
+This is in line with the fact that our previously used single-cell homeostatic control (see Equation \eqref{can_hom_rate}) exhibited no instabilities since it only incorporated firing thresholds as dynamic variables.
 In contrast, diffusive homeostasis increased the dimensionality of the system by means of its NO-synthesis and diffusion pathway.
-Additionally, Harnack et al.
-report a similar effect as seen in our system: Noise can reduce stability in a damped dynamical system by constantly causing deviations from its fixed point.
+Harnack et al.
+additionally reported a similar effect as seen in our system: Noise can reduce stability in a damped dynamical system by constantly causing deviations from its fixed point.
 
 An interesting idea that the aforementioned paper discusses is the possibility that slowness of homeostatic regulation on the timescale of hours might not only be due to functional reasons, such as this rate of adaption being sufficient to compensate for naturally occurring external perturbations.
-Based on their analysis, it might also be a mere issue of stability.
+Based on their analysis it might also be a mere issue of stability.
 In the context of this notion, faster homeostatic controls would simply be ruled out because they do not allow the nervous system to stay in a healthy condition.
-Our findings regarding the stability of diffusive homeostasis thus serves as an example supporting this hypothesis.
+Our findings regarding the stability of diffusive homeostasis thus serve as an example supporting this hypothesis.
 
@@
 Though the distribution did approximately resemble a log-normal-like shape, it did not perfectly match our expectations.
-In order to acquire a deeper understanding of the mechanisms that determine these statistics, we developed analytical expression that allowed us to reliably predict the steady-state of firing rates based on the spatial structure of excitatory neurons.
+In order to acquire a deeper understanding of the mechanisms that determine these statistics we developed analytical expression that allowed us to reliably predict the steady-state of firing rates based on the spatial structure of excitatory neurons.
 We would like to emphasize that this explanation differs from common approaches of understanding the emergence of heavy-tailed statistics of firing rates in recurrent networks.
@@
 \cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998}.
-Our interpretation of our results leads to the conclusion that this "canonical" approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behavior.
+Our interpretation of our results leads to the conclusion that this canonical approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behavior.
 
@@
 Of course, this impression only applies to the case where the aforementioned mixture of influence between spatial and synaptic topology is dominated by the former.
-By analyzing network activity based on our analytic model, we found that for finite diffusion constants, indeed only a single homeostatic fixed point exists.
-On a practical level though, the gradual decorrelation with this theoretical state of activity upon larger values of $\mathrm{D}$ is presumably caused by synaptic turnovers, which change the synaptic input.
-The resulting changes in activity are more slowly and less accurately compensated in the case of larger diffusion constants.
-However, for the standard choice of parameters (being roughly based on experimental data), the resulting activity is indeed strongly bound to the spatial structure of excitatory cells.
+By analyzing network activity based on our analytic model we found that indeed only a single homeostatic fixed point exists for finite diffusion constants.
+On a practical level though, the gradual decorrelation with this theoretical state of activity upon larger values of $\mathrm{D}$ was presumably caused by synaptic turnovers which change the synaptic input.
+The resulting changes in activity were more slowly and less accurately compensated in the case of larger diffusion constants.
+However, for the standard choice of parameters (being roughly based on experimental data) the resulting activity was indeed strongly bound to the spatial structure of excitatory cells.
 Naturally, this raises the question of biological plausibility.
@@
 Lower densities resulted in a more irregular activity, with stronger but less frequent bursting events.
-However, since our network was tuned to exhibit non-bursting activity, it is hard to draw any conclusions from this result.
-
-From a more general perspective, one could argue that a mechanism binding firing rates to spatial constraints suppresses the ability of the system to adapt to a changing environment since it essentially "freezes" the state of activity.
+However, it is hard to draw any conclusions from this result since our network was tuned to exhibit non-bursting activity.
+
+From a more general perspective one could argue that a mechanism binding firing rates to spatial constraints suppresses the ability of the system to adapt to a changing environment since it essentially "freezes" the state of activity.
 Experiments have shown that neurons' firing rates are indeed correlated under a changing environment/task: Neurons with a certain baseline-firing rate are very likely to have a similar firing rate while performing a task \cite{Buzsaki_Fir_Rates_2014}.
@@
 
-Instead, we hypothesized that by spatially increasing the spread of NO-insertion, we might be able to uncouple activity from spatial structure without tweaking the diffusion process.
+Instead, we hypothesized that we might be able to uncouple activity from spatial structure without tweaking the diffusion process by spatially increasing the spread of NO-insertion.
 While Sweeney et al.
-argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide), Philippides et al.
+argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide) Philippides et al.
 reported that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}.
 The diameter of these "production areas" is on the order of $\mathrm{10-100 \mu m}$.
-To incorporate this spread of synthesis in our model of diffusion, we convolved a circular shaped and shifted "production"-kernel (scaled according to the momentary rate of NO-synthesis) with the field of NO-concentration.
+To incorporate this spread of synthesis in our model of diffusion we convolved a circular shaped and shifted production-kernel (scaled according to the momentary rate of NO-synthesis) with the field of NO-concentration.
 Intuitively, this locally smeared the distinction between neighboring neurons.
@@
 As Figure \ref{External_Input_Switch_Spread_Source} suggests, this indeed improved flexibility of individual activity while retaining an overall constant firing rate.
-By adjusting the area of NO insertion we thereby gained further control over the strictness of the homeostatic mechanism.
+We therefore gained further control over the strictness of the homeostatic mechanism by adjusting the area of NO insertion.
 
@@
 A major issue of Equation \eqref{Theta_dyn} is the fact that, given a clamped positive or negative difference between the actual NO concentration and the target concentration, the excitability of the neuron would decrease or increase without bounds.
-Because of the limited amount of ion channels that exist in a cell and can be affected by nitric oxide, upper and lower bounds should certainly be present.
+Because of the limited amount of ion channels that exist in a cell and can be affected by nitric oxide, upper and lower bounds should however certainly be present.
 A simple approach to tackle this would be to implement hard bounds into our neuron model, not allowing the threshold to pass an upper and lower value.
@@
 \begin{equation}
-\dot{V_t^i}(t) = \frac{1}{\tau_{V_t}}\left(\frac{NO(\mathbf{r}_{neur}^i,t)-NO_0}{NO_0} + \frac{\alpha}{V_t^i - V_{t,min}} + \frac{\alpha}{V_t^i - V_{t,max}}\right) \; .
+\dot{V_{t,i}}(t) = \frac{1}{\tau_{V_t}}\left(\frac{NO(\mathbf{r}_{neur}^i,t)-NO_0}{NO_0} + \frac{\alpha}{V_{t,i} - V_{t,min}} + \frac{\alpha}{V_{t,i} - V_{t,max}}\right) \; .
 \label{Theta_dyn_with_Bounds}
 \end{equation}
-In this form, $\mathrm{NO(\mathbf{r}_{neur}^i,t) = NO_0}$ does not follow any more as the fixed point solution.
-Rather, one needs to consider the fact that, given the recurrent network topology, the steady state of $\mathrm{NO(\mathbf{r}_{neur}^i)^* = NO(\mathbf{r}_{neur}^i,V_t^1,...,V_t^n)^*}$ in turn depends on the set of thresholds.
+In this form $\mathrm{NO(\mathbf{r}_{neur}^i,t) = NO_0}$ does not follow any more as the fixed point solution.
+Rather, one needs to consider the fact that, given the recurrent network topology, the steady state of $\mathrm{NO(\mathbf{r}_{neur}^i)^* = NO(\mathbf{r}_{neur}^i,V_{t,1},...,V_{t,n})^*}$ in turn depends on the set of thresholds.
 Unfortunately, this increase in complexity would presumably make it impossible to find a general analytic description of the fixed point similar to the one introduced and discussed in Section \ref{Matrix_Diff_Model_Section}.
@@
 
-Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist}, we noted that the increased width of the distribution is largely due to to an increment on the left half of the curve.
-Since new weights are initialized at $\mathrm{10^{-4}\, mV}$, this might indicate that some weights are drifting much more slowly from their value of initialization compared to other weights.
+Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist} we noted that the increased width of the distribution is largely due to to an increment on the left half of the curve.
+Since new weights are initialized at $\mathrm{10^{-4}\, mV}$ this might indicate that some weights are drifting much more slowly from their value of initialization compared to other weights.
 These "slow drifters" are presumably connecting neurons both spiking at a below-average firing rate.
@@
 
-As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}), we found that neurons with a low-density neighborhood have a higher chance of developing these strong outgoing weights.
+As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}) we found that neurons with a low-density neighborhood have a higher chance of developing these strong outgoing weights.
 Since this effect is directly linked to the low-density/high-firing rate-relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons with above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
@@
 
-With respect to future use and implementation of diffusive homeostasis, one might desire to cover the essential effects in a more simple and abstract formalism.
+With respect to future use and implementation of diffusive homeostasis one might desire to cover the essential effects in a more simple and abstract formalism.
 As shown in Section \ref{Mean_Field_Review_Section}, a simple mean field model as presented by Sweeney et al.
 still carries problems similar to those of single-neuron homeostasis.
-However, modifications of this model that incorporates our remarks in Section \ref{Possible_Modifications_Section} might be able to recover properties of the full diffusive homeostatic feedback while being more computationally efficient.
+However, modifications of this model that incorporate our remarks in Section \ref{Possible_Modifications_Section} might be able to recover properties of the full diffusive homeostatic feedback while being more computationally efficient.
 

### 2017-02-10 abstract.tex
.

@@
 \maketitle
-\section{Abstract} \label{abstract}
-Based on the LIF-SORN-model proposed in \cite{SORN_Paper}, we attempt to replace the intrinsic homeostatic control system used in the original version by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
-The model of diffusive homeostasis is adopted from a paper by Y.
-Sweeney et al.
-\cite{Sweeney_Paper} and models the tissue as a surface of square shape and a set of points on this surface, representing the positions of the neurons within the SORN.
-Excitatory neurons then act as a point-source of nitric oxide (NO), as well as as a sensor for the NO-concentration at each individual position.
-The production and sensing of NO forms the basis of a feedback loop: The individual NO-readout is fed into a comparator which causes an appropriate change within the internal firing threshold of the neuron, in turn altering the neuron's firing rate.
-The control system is then closed by linking the rate of NO-production to the neuron's firing rate.
+\begin{abstract}
+Building upon on a self-organizing spiking neural network (LIF-SORN) we attempted to replace the intrinsic homeostatic control system used in earlier versions by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
+The model of diffusive homeostasis was adopted from a paper by Sweeney et al.
+\cite{Sweeney_Paper} and models the tissue as a surface of square shape and a set of points on this surface, representing the positions of the neurons within the network.
+Excitatory neurons acted as a source of nitric oxide (NO), as well as as a sensor for the NO concentration at each individual position.
+Production and sensing of NO formed the basis of a feedback loop: Individual NO readouts caused an appropriate change within the internal excitability of the neurons.
+The control system was closed by linking the rate of NO production to the neurons' firing rates.
 
-Key aspects of this thesis include an analysis of the stability of the homeostatic control, followed by a comparison of features of the original LIF-SORN and the diffusive variant.
-We expect to observe a preservation of non-random structural features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity (as reported by \cite{Sweeney_Paper}) which has previously been suppressed by a rigid single-cell homeostasis.
-In the face of possible \emph{new} features within the network's structure, we further clarify the - presumably indirect - causal relation between diffusive spatial interaction and synaptic topology.
+The main goal of this modification was to allow for a broad and heavy tailed distribution of firing rates among the excitatory neural population.
+This feature of cortical activity has been extensively observed and studied experimentally, but could not be achieved by the formerly used single-cell homeostatic mechanism which bound firing rates of all neurons to a fixed target value.
+Indeed, our statistical analysis of spiking activity showed that diffusive homeostasis could significantly broaden the distribution of firing rates.
+
+After having analyzed the stability of the homeostatic control loop and the resulting statistical features of spiking activity, we compared both homeostatic mechanisms with respect to features of synaptic network structures emerging throughout the simulation.
+Apart from the preservation of a number of topological features we found that diffusive homeostasis allowed for the emergence of highly influential neurons with strong outgoing synaptic efficacies.
+By means of an analytic approach to the homeostatic steady state, we could relate this feature of synaptic topology to the imposed spatial structure of the neural population.
+\end{abstract}
 

### 2017-02-10 draft.tex
.

@@
 
+\makeatother
+\MSonehalfspacing
+
+\begin{abstract}
+Building upon on a self-organizing spiking neural network (LIF-SORN) we attempted to replace the intrinsic homeostatic control system used in earlier versions by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
+The model of diffusive homeostasis was adopted from a paper by Sweeney et al.
+and models the tissue as a surface of square shape and a set of points on this surface, representing the positions of the neurons within the network.
+Excitatory neurons acted as a source of nitric oxide (NO), as well as as a sensor for the NO concentration at each individual position.
+Production and sensing of NO formed the basis of a feedback loop: Individual NO readouts caused an appropriate change within the internal excitability of the neurons.
+The control system was closed by linking the rate of NO production to the neurons' firing rates.
+
+The main goal of this modification was to allow for a broad and heavy tailed distribution of firing rates among the excitatory neural population.
+This feature of cortical activity has been extensively observed and studied experimentally, but could not be achieved by the formerly used single-cell homeostatic mechanism which bound firing rates of all neurons to a fixed target value.
+Indeed, our statistical analysis of spiking activity showed that diffusive homeostasis could significantly broaden the distribution of firing rates.
+
+After having analyzed the stability of the homeostatic control loop and the resulting statistical features of spiking activity, we compared both homeostatic mechanisms with respect to features of synaptic network structures emerging throughout the simulation.
+Apart from the preservation of a number of topological features we found that diffusive homeostasis allowed for the emergence of highly influential neurons with strong outgoing synaptic efficacies.
+By means of an analytic approach to the homeostatic steady state, we could relate this feature of synaptic topology to the imposed spatial structure of the neural population.
+\end{abstract}
+
+\clearpage
+
 \tableofcontents
@@
 \setcounter{page}{1}
-
-\makeatother
-\MSonehalfspacing
 
@@
 \textbf{Synaptic Pruning:} At the same rate of 1/sec, EE synapses below a threshold of 0.000001 mV were removed, thus being added again to the set of "potential" connections from which the growth process draws new connections.
-Especially, they were temporarily excluded from STDP (see below).
 

### 2017-02-13 draft.tex
.

@@
 \begin{abstract}
-Building upon on a self-organizing spiking neural network (LIF-SORN) we attempted to replace the intrinsic homeostatic control system used in earlier versions by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
+Building upon on a self-organizing spiking neural network (LIF-SORN), we attempted to replace the intrinsic homeostatic control system used in earlier versions by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
 The model of diffusive homeostasis was adopted from a paper by Sweeney et al.

### 2017-02-15 draft.tex
.

@@
 %\usepackage{layouts}
-\usepackage[a4paper,margin=1.5in]{geometry}
+%\usepackage[a4paper,margin=1.5in]{geometry}
+\usepackage{geometry}
+\geometry{
+a4paper,
+left=2.0in,
+right=1.0in}
 \usepackage[utf8]{inputenc}
@@
 
-In any case, modeling homeostasis includes an error estimation, which requires setting some predefined target that the feedback control will attempt to achieve.
+\subsubsection{The Role of Firing Rate Heterogeneity -  a Dichotomy between Heterogeneity and Control?}
+Modeling homeostasis necessarily includes a form of error estimation, which requires setting some predefined target that the feedback control will attempt to achieve.
 Of course this raises the question of how to choose these homeostatic targets.
@@
 In the light of this conceptual problem, one could, due to a lack of better knowledge, simply define a single global target of activity.
-It has been shown however that heterogeneity of neural response onto external input within a population is crucial for efficient stimulus encoding \cite{Marsat_2010}.
-Allowing for a broad distribution of activity thus has to be regarded an important compartment of models of cortical activity and structure.
-
-A conceptual problem that one might consider is the fact that temporal fluctuations of activity are believed to be a major part of information transmission and processing within the brain \cite[p.
+
+However, numerous experimental and theoretical studies have suggested that the presence of both slow- and fast-firing cells is not to be regarded as a ignorable, mere side effect of brain dynamics.
+It rather seems to be that skewed and heavy-tailed firing rate statistics are necessary with respect to preserving stable synaptic structures of long-term memory against relatively fast synaptic rewiring due to changes in external stimuli.
+For example, experiments by Dragoi et al.
+have found that during remapping of hippocampal place cells, neurons with low firing rates are subject to stronger changes within their field of spatial representation than those with high firing rates.
+In this context Buzsáki and Mizuseki argue that a small subset of highly active neurons may serve to form relatively strongly connected and stable sub-networks that can quickly react to momentary changes in the environment, while fine tuned adaptation over longer time periods involves the slower firing majority of cells \cite{Buzsaki_Fir_Rates_2014}.
+A realistic network model of neural activity and plasticity should therefore allow for a broad distribution of firing rates.
+
+Interestingly, measurements in the barrel cortex and hippocampus have found that firing rates during exploration or task performance are significantly correlated with those found for spontaneous, baseline activity \cite{OConnor_2010,Mizuseki_2013}.
+This suggests that the same set of neurons tend to be relatively active or inactive under different stimuli and changing environments, in line with the idea of modeling homeostasis by means of individual targets of activity, which together form the desired statistical distribution.
+Still, though apparently being a good phenomenological approach, it is unclear what gives rise to these target differences.
+
+Another problem that one might consider is the fact that temporal fluctuations of activity are believed to be a major part of information transmission and processing within the brain \cite[p.
 123-150]{Theor_Neur_Dayan}.
@@
 However, it is argued that homeostatic mechanisms act on time scales of hours to days and thus do not interfere with changes in activity taking place on the order of seconds or below \cite{Turrigiano_2011}.
-
 Returning to the previous question, though the slowness of homeostatic adaptation might allow for temporal fluctuations of activity, it does not overcome the conceptual dichotomy between single cell homeostasis and persistent variability in spontaneous activity.

### 2017-02-16 draft.tex
.

@@
 
-However, numerous experimental and theoretical studies have suggested that the presence of both slow- and fast-firing cells is not to be regarded as a ignorable, mere side effect of brain dynamics.
-It rather seems to be that skewed and heavy-tailed firing rate statistics are necessary with respect to preserving stable synaptic structures of long-term memory against relatively fast synaptic rewiring due to changes in external stimuli.
+However, numerous experimental and theoretical studies have suggested that the presence of both slow- and fast-firing cells is not to be regarded as an ignorable, mere side effect of brain dynamics.
+It rather seems to be that skewed and heavy-tailed firing rate statistics are necessary with respect to the preservation of stable synaptic structures, being related to long-term memory, while still allowing synaptic rewiring in order to adapt to changes in external stimuli.
 For example, experiments by Dragoi et al.
-have found that during remapping of hippocampal place cells, neurons with low firing rates are subject to stronger changes within their field of spatial representation than those with high firing rates.
-In this context Buzsáki and Mizuseki argue that a small subset of highly active neurons may serve to form relatively strongly connected and stable sub-networks that can quickly react to momentary changes in the environment, while fine tuned adaptation over longer time periods involves the slower firing majority of cells \cite{Buzsaki_Fir_Rates_2014}.
-A realistic network model of neural activity and plasticity should therefore allow for a broad distribution of firing rates.
+have found that during remapping of hippocampal place cells, neurons with low firing rates are subject to stronger changes within their field of spatial representation than those with high firing rates \cite{Dragoi_2003}.
+In this context Buzsáki and Mizuseki argue that a small subset of highly active neurons may serve to form relatively strongly connected and stable sub-networks that can quickly react to momentary changes in the environment, while fine tuned adaptation involves the slower firing majority of cells \cite{Buzsaki_Fir_Rates_2014}.
+A realistic network model of neural activity and plasticity should therefore allow for a broad distribution of firing rates to cope with these functional aspects.
 
@@
 Through the diffusive signal, each neurons receives - intuitively speaking - a mixture of its own activity and its neighboring neurons.
-Thereby individual tuning of firing rates is suppressed while the overall population activity is kept at a constant level.
+Individual tuning of firing rates is thereby suppressed while the overall population activity is kept at a constant level.
 
@@
 We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity which has previously been suppressed by single-cell homeostasis.
-We predict activity within the network by an analytic approach, thereby gaining an understanding of the relation between spatial structure and firing rates.
+Furthermore, we predict excitatory activity on the level of individual cells by an analytic approach, thereby gaining an understanding of the relation between spatial structure and firing rates.
 In the face of possible new features within the network's structure, we clarify the causal relation between diffusive spatial interaction and synaptic topology.
@@
 On the other hand, a similar form of adaption as a reaction on deprived or enhanced input can be observed on a timescale of hours to days \cite{Desai_IP}.
-In the latter case, \cite{Desai_IP} finds evidence that a long-term change in excitability can be attributed to an altered resistance of ionic channels.
+In the latter case, a long-term change in excitability can be attributed to an altered resistance of ionic channels.
 This contrasts the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252-256]{Izhikevich_Dynsys}.
@@
 
-Finally, the dynamics of the firing thresholds $V_{t,i}$ were modeled such that the rate of change is proportional to the relative deviation of the $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
+Finally, the dynamics of firing thresholds $V_{t,i}$ were modeled such that the rate of change is proportional to the relative deviation of $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
 
@@
 One rather needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration.
-Though it is possible to derive this relation in an analytic fashion, we let the system run with the previous homeostatic mechanism for practical purposes of the simulation, still solving equation \eqref{Ca_dyn}-\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
+Though it is possible to derive this relation in an analytic fashion, we let the system run with the previous homeostatic mechanism, still solving equation \eqref{Ca_dyn}-\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
 This mean was then set to be the target concentration and we switched to diffusive homeostasis.
@@
 \section{Results} \label{results}
-We first present the results of a comparison between features of the network activity in both variants in section \ref{activ_analys} since our main goal of the implementation of diffusive homeostasis was to allow the network to develop a broader distribution of firing rates across excitatory neurons compared to the original version of homeostasis.
+We first present the results of a comparison between features of the network activity in both variants in section \ref{activ_analys}, since our main goal of the implementation of diffusive homeostasis was to allow the network to develop a broader distribution of firing rates across excitatory neurons compared to the original version of homeostasis.
 This is followed by an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see section \ref{theor_osc}.
@@
 \subsubsection{Distribution of Firing Rates}\label{Fir_Dist_Section}
-Achieving a broad distribution of firing rates among neurons was the core motivation for the implementation of diffusive homeostasis.
+Achieving a broad distribution of firing rates among excitatory neurons was the core motivation for the implementation of diffusive homeostasis.
 Figure \ref{Fir_Rate_Dist_Compare} shows a first result, comparing both homeostatic mechanisms.
@@
 Despite of fluctuations within the firing rate on small time scales due to the inherent nature of - approximately - random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds.
-This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: The resulting distribution might be narrower than what one could expect from a distribution of momentary rates if firing rates fluctuate too much during the period over which means were calculated.
+This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of momentary rates.
 A constant rate of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous Poisson process of the same total mean firing rate.

### 2017-02-17 draft.tex
.

@@
 \hline
-$\mathrm{D}$ & default: 10000 $\mathrm{\mu m^2 s^{-1}}$ \\
+$\mathrm{D}$ & default: 10 $\mathrm{\mu m^2 ms^{-1}}$ \\
 \hline 
@@
 \caption{Histograms of mean firing rates over the excitatory/inhibitory population in regular (A/A*) and logarithmic space (B/B*).
-For diffusive homeostasis ($\mathrm{D=1000\, \mu m^2 s^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
+For diffusive homeostasis ($\mathrm{D=10\, \mu m^2 ms^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
 Mean firing rates were calculated from spikes within $\mathrm{t=1000-1500\,s}$.}
@@
 We were particularly interested in the quality of the predictions with respect to the choice of diffusion constant.
-Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 /ms}$, the correlation between measured and predicted firing rates is very good.
-In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 /ms}$.
+Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 ms^{-1}}$, the correlation between measured and predicted firing rates is very good.
+In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 ms^{-1}}$.
 This represented a limiting case where our analytic model could not make any meaningful predictions, since instant diffusion overrides any spatial inhomogeneities.
@@
 \caption{Measured firing rates (t=1200-1500 s) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
-For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably large diffusion constant of $\mathrm{D=100\, \mu m^2 /s}$.}
+For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably large diffusion constant of $\mathrm{D=100\, \mu m^2 ms^{-1}}$.}
 \label{Rand_Matrix_Sol_vs_Sim}
@@
 \end{center}
-\caption{Distribution of firing rates for $\mathrm{D=10\, \mu m^2 / ms}$, full simulation and analytic prediction. Data was taken from 10 simulation runs.}
+\caption{Distribution of firing rates for $\mathrm{D=10\, \mu m^2 ms^{-1}}$, full simulation and analytic prediction. Data was taken from 10 simulation runs.}
 \label{Fir_Rate_Dist_Sim_vs_Mat}
@@
 However, we could see a general decline of correlation for larger diffusion constants.
-This trend was in line with the aforementioned limit of instant diffusion, namely a complete decorrelation between prediction and measurement, as well as the good agreement for $\mathrm{D= 10\, \mu m^2 / ms}$ shown in Figure \ref{Fir_Rate_Dist_Sim_vs_Mat}.
+This trend was in line with the aforementioned limit of instant diffusion, namely a complete decorrelation between prediction and measurement, as well as the good agreement for $\mathrm{D= 10\, \mu m^2 ms^{-1}}$ shown in Figure \ref{Fir_Rate_Dist_Sim_vs_Mat}.
 \begin{figure}
@@
 \end{center}
-\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2/ms}$.}
+\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2 ms^{-1}}$.}
 \label{Fir_Rate_Dist_Reg_Grid}

### 2017-02-22 draft.tex
.

@@
 %\usepackage{layouts}
-%\usepackage[a4paper,margin=1.5in]{geometry}
-\usepackage{geometry}
-\geometry{
-a4paper,
-left=2.0in,
-right=1.0in}
+\usepackage[a4paper,margin=1.5in]{geometry}
+%\usepackage{geometry}
+%\geometry{
+%a4paper,
+%left=2.0in,
+%right=1.0in}
 \usepackage[utf8]{inputenc}
@@
 have shown in computational studies that these "driver neurons" form highly active and interconnected subnetworks \cite{Effenberger_2015}, an observation that is backed up by experimental studies \cite{Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}.
-Figure \ref{Out_Weight_Mean_Quantile} shows that diffusive homeostasis allows for the emergence of a small group of highly influential neurons, which reproduces the findings in \cite{Effenberger_2015}.
-A comparison of statistics generated with shuffled versions of the weight matrices illustrates that above-chance exceptionally strong outgoing weights were indeed present.
+Figure \ref{Out_Weight_Mean_Quantile} shows that diffusive homeostasis allows for the emergence of a small group of highly influential neurons, which resembles the findings in \cite{Effenberger_2015}.
+A comparison of statistics generated with shuffled versions of the weight matrices illustrates that above-chance exceptionally strong mean outgoing weights were indeed present.
 We noted further that the difference between shuffled matrices corresponding to non-diffusive and diffusive homeostasis is in line with our observation from Figure \ref{Weight_Dist}, which indicated a broader distribution of weights for diffusive homeostasis.
@@
 In turn, synapses between highly active presynaptic cells and postsynaptic neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
-With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies the same functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity.
+With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies a similar functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity.
 We tested this relationship by plotting the mean outgoing weights against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
-A strong heterogeneity of firing rates allows for the development of few strong synapses, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range.
+A strong heterogeneity of firing rates allows for the development of few neurons with comparably strong mean outgoing weights, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range.
 We also tested the case of instant diffusion.
@@
 Generally speaking, no matter how the actual shape of the numeric solution in the equilibrium at a constant production rate looks like, it must be of the form
-\begin{align}
-NO_i(\mathbf{x}) &= r_i \cdot \psi (d(\mathbf{x}_{neur,i},\mathbf{x})) \label{general_diff_interaction} \\
-d(\mathbf{x},\mathbf{y}) &\equiv |\mathbf{x}-\mathbf{y}| \; . \label{eucl_dist}
-\end{align}
+\begin{equation}
+NO_i(\mathbf{x}) = r_i \cdot \psi (|\mathbf{x}_{neur,i}-\mathbf{x}|) \; . \label{general_diff_interaction}
+\end{equation}
 The full solution is then
@@
 \begin{equation}
-\psi_{ij} \equiv \psi_{ij} \equiv \psi (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i}))
+\psi_{ij} \equiv \psi_{ij} \equiv \psi (|\mathbf{x}_{neur,i}-\mathbf{x}_{neur,i}|)
 \label{interact_matrix_elements}
@@
 \end{equation}
-Still, we had to find a modified, non-diverging version of $\mathrm{\psi (d(\mathbf{x}_{neur,i},\mathbf{x}))}$ to acquire any prediction from this model.
+Still, we had to find a modified, non-diverging version of $\mathrm{\psi (|\mathbf{x}_{neur,i}-\mathbf{x}|)}$ to acquire any prediction from this model.
 It had to retain the shape given by \eqref{solution_diff_equil_bessel} for larger distances but approach the correct numeric error value at the origin, determined by the spacing of the numeric grid.
@@
 \begin{equation}
-\psi_{ij,per.} = \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i} + L \cdot (n_x,n_y))) \; .
+\psi_{ij,per.} = \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} (|\mathbf{x}_{neur,i}-\mathbf{x}_{neur,i} - L \cdot (n_x,n_y)|) \; .
 \label{Psi_entries_periodic_bound}
@@
 \begin{align}
-\psi_{ij,neum.} &= \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} \left( d(\mathbf{x}_{neur,i},M(\mathbf{x}_{neur,i}) + L \cdot (n_x,n_y)) \right) \label{Psi_entries_neumann_bound} \\
+\psi_{ij,neum.} &= \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} \left(|\mathbf{x}_{neur,i}-M(\mathbf{x}_{neur,i}) - L \cdot (n_x,n_y)| \right) \label{Psi_entries_neumann_bound} \\
 M(\mathbf{x}) &\equiv  
@@
 In Section \ref{Section_Mean_outgoing_Weights} we stated that diffusive homeostasis allowed the network do develop few neurons with exceptionally strong outgoing weights.
-Furthermore, we found this effect to be present in neurons with an highly above-average firing rate.
+We found this effect to be present in neurons with an highly above-average firing rate.
 Moreover, the outcomes presented in Section \ref{Section_Rand_Mat_vs_Sim} suggest that the steady state of firing rates is strongly influenced by the spatial structure of excitatory neurons.
@@
 Though the distribution did approximately resemble a log-normal-like shape, it did not perfectly match our expectations.
-In order to acquire a deeper understanding of the mechanisms that determine these statistics we developed analytical expression that allowed us to reliably predict the steady-state of firing rates based on the spatial structure of excitatory neurons.
+In order to acquire a deeper understanding of the mechanisms that determine these statistics we developed an analytical expression that allowed us to reliably predict the steady-state of firing rates based on the spatial structure of excitatory neurons.
 We would like to emphasize that this explanation differs from common approaches of understanding the emergence of heavy-tailed statistics of firing rates in recurrent networks.
@@
 On a practical level though, the gradual decorrelation with this theoretical state of activity upon larger values of $\mathrm{D}$ was presumably caused by synaptic turnovers which change the synaptic input.
-The resulting changes in activity were more slowly and less accurately compensated in the case of larger diffusion constants.
+Fluctuations in activity were more slowly and less accurately compensated in the case of larger diffusion constants.
 However, for the standard choice of parameters (being roughly based on experimental data) the resulting activity was indeed strongly bound to the spatial structure of excitatory cells.
@@
 The diameter of these "production areas" is on the order of $\mathrm{10-100 \mu m}$.
-To incorporate this spread of synthesis in our model of diffusion we convolved a circular shaped and shifted production-kernel (scaled according to the momentary rate of NO-synthesis) with the field of NO-concentration.
-Intuitively, this locally smeared the distinction between neighboring neurons.
+To incorporate this spread of synthesis in our model of diffusion we convolved a circular shaped and shifted production-kernel (multiplied by the momentary rate of NO-synthesis) with the field of NO-concentration.
+Intuitively, it locally smeared the distinction between neighboring neurons.
 From a more abstract point of view, it provided a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.

### 2017-02-24 draft.tex
.

@@
 A key step in characterizing a control loop in the context of biological systems should be to identify the previously described compartments.
-While the functional separation illustrated in Figure \ref{Closed_Loop_Control_Illustration} might seem intuitive and "straight forward", it is not obvious which physiological element should be attributed to a certain abstract element.
+While the functional separation illustrated in Figure \ref{Closed_Loop_Control_Illustration} might seem intuitive and ``straight forward", it is not obvious which physiological element should be attributed to a certain abstract element.
 As a start, we state that the process and its output controlled by homeostasis is the generation of action potentials and the resulting firing rate.
-Firing rate is - as stated earlier - an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a "sensible" quantity.
+Firing rate is - as stated earlier - an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a ``sensible" quantity.
 In a nerve cell this could be represented by e.g.
@@
 Returning to the previous question, though the slowness of homeostatic adaptation might allow for temporal fluctuations of activity, it does not overcome the conceptual dichotomy between single cell homeostasis and persistent variability in spontaneous activity.
-Marder and Goaillard speculated that instead of a mechanism controlling activity on a single-cell level, one might consider the possibility of a "global sensor of network performance to provide error signals for tuning of the network" \cite{Marder_2006}.
+Marder and Goaillard speculated that instead of a mechanism controlling activity on a single-cell level, one might consider the possibility of a ``global sensor of network performance to provide error signals for tuning of the network" \cite{Marder_2006}.
 This concept was used by Sweeney et al.
@@
 
-\textbf{Synaptic Pruning:} At the same rate of 1/sec, EE synapses below a threshold of 0.000001 mV were removed, thus being added again to the set of "potential" connections from which the growth process draws new connections.
+\textbf{Synaptic Pruning:} At the same rate of 1/sec, EE synapses below a threshold of 0.000001 mV were removed, thus being added again to the set of ``potential" connections from which the growth process draws new connections.
 
@@
 Parameters were chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
-However, we used the "nearest neighbor" approximation for the sake of reduction of computational effort, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
+However, we used the ``nearest neighbor" approximation for the sake of reduction of computational effort, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
 
@@
 \begin{align}
-\dot{{Ca^{2+}}_i}(t) &= -\frac{{Ca^{2+}}_i}{\tau_{Ca^{2+}}} + Ca^{2+}_{spike} \sum_{j} \delta(t-t_{spike,i,j}) \label{Ca_dyn}\\
+\dot{{Ca^{2+}}_i}(t) &= -\frac{{Ca^{2+}}_i}{\tau_{Ca^{2+}}} + Ca^{2+}_{spike} \sum_{j} \delta(t-t^j_{spike,i}) \label{Ca_dyn}\\
 \dot{nNOS_i}(t) &= \frac{1}{\tau_{nNOS}} \left(\frac{{{Ca^{2+}}_i}^3}{{{Ca^{2+}}_i}^3+1} - nNOS_i \right) \label{nNOS_dyn}\\
@@
 through \eqref{nNOS_dyn} using the Hill equation \cite{Hill_Equ} to model a cooperative binding mechanism.
-The $nNOS$ production is then fed into the "pool" of nitric oxide via point sources located at the neurons' positions.
+The $nNOS$ production is then fed into the pool of nitric oxide via point sources located at the neurons' positions.
 An additional decay term was added apart from the inflow and the diffusive term to provide a stable finite $NO$ concentration under constant neuronal activity.
@@
 \hline
-$\mathrm{\tau_{V_t}}$ & see section \ref{activ_analys} \\
+$\mathrm{\tau_{V_t}}$ & see Section \ref{activ_analys} \\
 \hline
@@
 This decision relates to the previously described mechanism of synaptic growth: Neurons placed close to the edge of the sheet have a lower connection probability due to the absence of neighboring neurons in the direction perpendicular to the close-by border.
-It therefore models the synaptic growth within a square "cutout" of neural tissue.
+It therefore models the synaptic growth within a square ``cutout" of neural tissue.
 The Neumann boundary condition fits into this picture since it allows a zero-flux condition at the borders.
@@
 Equation \eqref{NO_dyn} describes the influx of NO as a sum of scaled and spatially shifted Dirac functions.
-Apart from the question whether this source term results in a well defined, finite solution at the neurons' positions (see section \ref{Matrix_Diff_Model_Section}), it can only be modeled to a certain degree of accuracy depending on the resolution of the numeric grid.
+Apart from the question whether this source term results in a well defined, finite solution at the neurons' positions (see Section \ref{Matrix_Diff_Model_Section}), it can only be modeled to a certain degree of accuracy depending on the resolution of the numeric grid.
 In practice, we approximated the point sources of NO as an insertions at individual grid cells at a rate of $nNOS_i(t) / h^2$, where the normalizing divisor $h^2$ ensured the desired total influx per neuron.
@@
 We first present the results of a comparison between features of the network activity in both variants in section \ref{activ_analys}, since our main goal of the implementation of diffusive homeostasis was to allow the network to develop a broader distribution of firing rates across excitatory neurons compared to the original version of homeostasis.
-This is followed by an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see section \ref{theor_osc}.
+This is followed by an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see Section \ref{theor_osc}.
 Furthermore, we compare topological features of the network under the influence of diffusive and non-diffusive homeostasis in section \ref{Network_Topology_Section}.
@@
 Such a limit cycle exists inside a region $R$ if $R$ contains no fixed points and if any trajectory whose starting points lies within $R$ is confined to $R$, according to the Poincaré-Bendixson theorem.
-The second condition is equivalent to the condition that for all points $\mathbf{r}_{edge}$ on the edge of $R$, the vector field $\dot{\mathbf{r}}_{edge}$ is facing "into" $R$, see \cite[p.~248]{Dyn_Sys_Hirsch}.
+The second condition is equivalent to the condition that for all points $\mathbf{r}_{edge}$ on the edge of $R$, the vector field $\dot{\mathbf{r}}_{edge}$ is facing into $R$, see \cite[p.~248]{Dyn_Sys_Hirsch}.
 This case occurs if the system has a locally unstable fixed point, but a non-linearity that prevents an infinite deviation from the fixed point.
@@
 \begin{split}
-{Ca^{2+}}^3(t) &= \left[ Ca^{2+}_{spike} \sum_{i} \theta(t-t^i_{spike,i}) exp(-(t-t^i_{spike,j})/\tau_{Ca^{2+}}) \right]^3 \\
-&\approx {Ca^{2+}_{spike}}^3 \sum_{i} \theta(t-t^i_{spike,i}) exp(-3(t-t^i_{spike,j})/\tau_{Ca^{2+}})
+{Ca^{2+}}^3(t) &= \left[ Ca^{2+}_{spike} \sum_{i} \theta(t-t^i_{spike}) exp(-(t-t^i_{spike})/\tau_{Ca^{2+}}) \right]^3 \\
+&\approx {Ca^{2+}_{spike}}^3 \sum_{i} \theta(t-t^i_{spike}) exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}})
 \end{split} \label{cubic_approx_1}			
@@
 However, it is not sufficient to simply propose $nNOS_i(t) = r_i(t) \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
-A single cell fires in the range of $\mathrm{3\,Hz}$, which is - at least on the time scale of the observed oscillations - not enough to assign an "instantaneous" firing rate.
+A single cell fires in the range of $\mathrm{3\,Hz}$, which is - at least on the time scale of the observed oscillations - not enough to assign an instantaneous firing rate.
 \newpage
@@
 Choosing noise amplitude to be the only free parameter of the model gave a rather unsatisfying result.
-Our approximation underestimated the amount of damping within the system (which controls the "peakiness" of the spectrum), as well as predicting a slightly smaller preferred amplitude.
+Our approximation underestimated the amount of damping within the system (which controls the ``peakiness" of the spectrum), as well as predicting a slightly smaller preferred amplitude.
 The preferred amplitude is controlled by $\frac{\gamma \alpha N_{exc.}}{L^2}$ and $\frac{1}{NO_0\tau_{V_t}}$ while the broadness of the spectrum is mostly controlled by the damping term $-\lambda$.
@@
 The fact that the value for $\mathrm{\alpha}$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency can be partially explained by the linear regression, which overestimates the importance of a number of high-threshold-outliers.
-This leads to a shallower slope than what would be appropriate for the "working point" of oscillatory behavior.
-Another possible explanation could be that "instant spread" is only an approximation.
+This leads to a shallower slope than what would be appropriate for the working point of oscillatory behavior.
+Another possible explanation could be that ``instant spread" is only an approximation.
 Rather, one could picture the nitrous oxide just to fill a fraction of the available space on a short time scale by replacing $L^2$ by a smaller area.
@@
 In (A), we found a skewness of $\mathrm{v_{Diff} = 0.765}$, in (B) $\mathrm{v_{Diff,log} = -0.488}$.
-Though this told us that the distribution is "more symmetric" on a logarithmic scale, it should rather be seen as being neither strictly normally or log-normally distributed.
+Though this told us that the distribution is ``more symmetric" on a logarithmic scale, it should rather be seen as being neither strictly normally or log-normally distributed.
 \begin{figure}
@@
 Despite of fluctuations within the firing rate on small time scales due to the inherent nature of - approximately - random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds.
-This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of momentary rates.
+This question is not only of relevance with respect to the ``stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of momentary rates.
 A constant rate of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous Poisson process of the same total mean firing rate.
@@
 Since we only implemented synaptic normalization for the sum of \emph{ingoing} weights, the total or average strength of \emph{outgoing} connections may vary from cell to cell.
-In a sense, the strength of outgoing connections per neuron can be regarded as a measure of how "influential" a neuron's activity is with respect to other neurons in the network.
+In a sense, the strength of outgoing connections per neuron can be regarded as a measure of how influential a neuron's activity is with respect to other neurons in the network.
 Effenberger et al.
-have shown in computational studies that these "driver neurons" form highly active and interconnected subnetworks \cite{Effenberger_2015}, an observation that is backed up by experimental studies \cite{Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}.
+have shown in computational studies that these ``driver neurons" form highly active and interconnected subnetworks \cite{Effenberger_2015}, an observation that is backed up by experimental studies \cite{Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}.
 Figure \ref{Out_Weight_Mean_Quantile} shows that diffusive homeostasis allows for the emergence of a small group of highly influential neurons, which resembles the findings in \cite{Effenberger_2015}.
@@
 \end{equation}
-where $\mathrm{\varepsilon}$ determines the "smoothness" of transition between $\mathrm{\psi}$ and the cutoff value $\mathrm{\psi_0}$.
+where $\mathrm{\varepsilon}$ determines the ``smoothness" of transition between $\mathrm{\psi}$ and the cutoff value $\mathrm{\psi_0}$.
 We chose $\mathrm{\varepsilon=10}$ for all further calculations.
@@
 
-By simply calculating all matrix elements of $\mathrm{\hat{\psi}}$ by means of Equation \eqref{interact_matrix_elements}, one would neglect the finite boundaries of the system, which would cause neurons close to the edge to "bleed" into empty space.
+By simply calculating all matrix elements of $\mathrm{\hat{\psi}}$ by means of Equation \eqref{interact_matrix_elements}, one would neglect the finite boundaries of the system, which would cause neurons close to the edge to ``bleed" into empty space.
 This in turn would cause the solution of \eqref{NO_equil_cond_interact_matrix_operator} to contain an over-representation of high firing rates since close-to-the-edge neurons would need to compensate for their lack of neighbors.
@@
 Moreover, the outcomes presented in Section \ref{Section_Rand_Mat_vs_Sim} suggest that the steady state of firing rates is strongly influenced by the spatial structure of excitatory neurons.
-Combining these two qualities led us the conclusion that one should be able to observe some relation between spatial structure and the emergence of "driver neurons".
+Combining these two qualities led us the conclusion that one should be able to observe some relation between spatial structure and the emergence of ``driver neurons".
 More specific, regions of neurons with above average firing rates should develop stronger outgoing connections.
@@
 
-From a more general perspective one could argue that a mechanism binding firing rates to spatial constraints suppresses the ability of the system to adapt to a changing environment since it essentially "freezes" the state of activity.
+From a more general perspective one could argue that a mechanism binding firing rates to spatial constraints suppresses the ability of the system to adapt to a changing environment since it essentially ``freezes" the state of activity.
 Experiments have shown that neurons' firing rates are indeed correlated under a changing environment/task: Neurons with a certain baseline-firing rate are very likely to have a similar firing rate while performing a task \cite{Buzsaki_Fir_Rates_2014}.
@@
 reported that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}.
-The diameter of these "production areas" is on the order of $\mathrm{10-100 \mu m}$.
+The diameter of these ``production areas" is on the order of $\mathrm{10-100 \mu m}$.
 To incorporate this spread of synthesis in our model of diffusion we convolved a circular shaped and shifted production-kernel (multiplied by the momentary rate of NO-synthesis) with the field of NO-concentration.
@@
 Since new weights are initialized at $\mathrm{10^{-4}\, mV}$ this might indicate that some weights are drifting much more slowly from their value of initialization compared to other weights.
-These "slow drifters" are presumably connecting neurons both spiking at a below-average firing rate.
+These ``slow drifters" are presumably connecting neurons both spiking at a below-average firing rate.
 This provides an explanation why this effect is more present in the case of diffusive homeostasis since it causes a portion of neurons to have rather low firing rates.
@@
 Referring back to Figure \ref{Pop_Mean_Cross_Corr}, we can now relate the increment of correlation among the excitatory population in the case of diffusive homeostasis to the results discussed in this section: The emergence of very strong outgoing connections increases the probability of neurons being postynaptically connected to such highly influential neurons to fire shortly after the presynaptic neuron.
-In the light of the notion of "rich get richer" or "rich stay rich" weight-dynamics that were reported for earlier versions of SORN and LIF-SORN, one can argue that this increment in correlation even further stabilizes these strong excitatory weights \cite{Pengsheng_2013,SORN_Paper}.
+In the light of the notion of ``rich get richer" or ``rich stay rich" weight-dynamics that were reported for earlier versions of SORN and LIF-SORN, one can argue that this increment in correlation even further stabilizes these strong excitatory weights \cite{Pengsheng_2013,SORN_Paper}.
 

### 2017-03-01 draft.tex
.

@@
 Excitatory neurons acted as a source of nitric oxide (NO), as well as as a sensor for the NO concentration at each individual position.
-Production and sensing of NO formed the basis of a feedback loop: Individual NO readouts caused an appropriate change within the internal excitability of the neurons.
+Production and sensing of NO formed the basis of a feedback loop: Individual NO readouts caused an appropriate change within the intrinsic excitability of the neurons.
 The control system was closed by linking the rate of NO production to the neurons' firing rates.
 
-The main goal of this modification was to allow for a broad and heavy tailed distribution of firing rates among the excitatory neural population.
+The main goal of the modification of homeostasis was to allow for a broad and heavy tailed distribution of firing rates among the excitatory neural population.
 This feature of cortical activity has been extensively observed and studied experimentally, but could not be achieved by the formerly used single-cell homeostatic mechanism which bound firing rates of all neurons to a fixed target value.
@@
 Cannon in 1932 \cite{Wisdom_of_the_Body_Cannon, Homeostasis_Queenan_2012}.
-Experimental studies have found evidence for processes within the brain that do not function as a regulatory control for certain aspects of the body, but as a homeostatic control of neural activity itself \cite{Turrigiano_1994,Burrone_2003}in more recent years.
-Many processes underlying this self-regulatory behavior have been found up till now and many different biophysical interdependencies have shown to play a role.
+In more recent years, experimental studies have found evidence for processes within the brain that do not function as a regulatory control for certain aspects of the body, but as a homeostatic control of neural activity itself \cite{Turrigiano_1994,Burrone_2003}.
+Many processes underlying this self-regulatory behavior have been found so far and many different biophysical interdependencies have shown to play a role.
 This diversity makes comparability of these mechanisms a rather difficult task.
@@
 Theoretical and experimental studies have suggested that this type of regulation is taking place in a multiplicative manner, thereby retaining proportions between individual synaptic strengths \cite{Syn_Plast_Abbott}.
-One can regard this form of plasticity as an antagonist to other aspects of synaptic plasticity that affect synaptic strengths in an activity dependent, hebbian fashion.
+One can regard this form of plasticity as an antagonist to other aspects of synaptic plasticity that affect synaptic strengths in an activity dependent, Hebbian fashion.
 Forms of regulation belonging to intrinsic homeostasis alter the neurons' capability of spiking upon external input by changing intrinsic properties of the nerve cell.
@@
 
-Theoretical models of homeostasis are generally based on a form of feedback control.This is also known as a \textit{closed loop control} in control theory.
-All these systems include a number of necessary functional compartments, which will be briefly introduced in the following.
+Theoretical models of homeostasis are generally based on a form of feedback control.
+This is also known as a \textit{closed loop control} in control theory.
+All these systems include a number of necessary functional components, which will be briefly introduced in the following.
 Concepts and terms were taken from \cite[p.
@@
 The firing rate of a neuron for example is an abstract quantity, which can not be \emph{directly} related to some neuronal state variable.
-Consequently, it might be necessary to transform the actual output of the process into a different signal by a \textit{feedback transducer}.The (potentially transformed) output is fed into a \textit{comparator} in the next step, which - unsurprisingly - compares the given output of the process to some given target or \textit{reference}, typically by subtraction.
+Consequently, it might be necessary to transform the actual output of the process into a different signal by a \textit{feedback transducer}.
+The (potentially transformed) output is fed into a \textit{comparator} in the next step, which---unsurprisingly---compares the given output of the process to some given target or \textit{reference}, typically by subtraction.
 Note that this reference can but does note have to be a time-dependent signal.
@@
 \subsubsection{Error Signals and Controllers of Neuronal Homeostasis}
-A key step in characterizing a control loop in the context of biological systems should be to identify the previously described compartments.
+A key step in characterizing a control loop in the context of biological systems should be to identify the previously described abstract elements.
 While the functional separation illustrated in Figure \ref{Closed_Loop_Control_Illustration} might seem intuitive and ``straight forward", it is not obvious which physiological element should be attributed to a certain abstract element.
 As a start, we state that the process and its output controlled by homeostasis is the generation of action potentials and the resulting firing rate.
-Firing rate is - as stated earlier - an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a ``sensible" quantity.
+Firing rate is---as stated earlier---an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a ``sensible" quantity.
 In a nerve cell this could be represented by e.g.
@@
 An example for a homeostatic model making use of intracellular calcium concentration as a measure of spiking activity is the LeMasson-Abbott model \cite{LeMasson_1993}.
-More complex chains of activity encoding are of course possible and we will introduce a recent model making additional use of the concentration of nitric oxide in Section \ref{DIff_Hom_Intro_Section} and \ref{NO_Experiments_Section}.
-Given a representation of activity, its deviation from a reference value will cause other physiological compartments to affect the neuron's ability to generate action potentials.
+More complex chains of activity encoding are of course possible and we will introduce a recent model making additional use of the concentration of nitric oxide in Section \ref{DIff_Hom_Intro_Section}.
+Given a representation of activity, its deviation from a reference value will cause other physiological quantities to affect the neuron's ability to generate action potentials.
 Referring to the concepts introduced in the previous section one could then ask what type of control best resembles the actual neuronal control.
 The fact that neurons, whose firing rate was artificially increased or suppressed over a long time, can reliably tune their activity back to the initial state (see e.g.
-\cite{Burrone_2002}) rules out a purely differential type of control.
-The return to baseline under different disturbances seems to point towards an integral-like control.
-It is clear however that a the ability of a biological system to encode the accumulation of an error signal is limited by the finite amount of available resources.
+\cite{Burrone_2002}) rules out a purely differential type of control, and rather points to an integral or proportional control.
+It is clear however that the ability of a biological system to encode the accumulation of an error signal is limited by the finite amount of available resources.
 The conductance of an ion channel for example has natural upper and lower bounds that it can not surpass.
@@
 
-\subsubsection{The Role of Firing Rate Heterogeneity -  a Dichotomy between Heterogeneity and Control?}
+\subsubsection{The Role of Firing Rate Heterogeneity---a Dichotomy between Heterogeneity and Control?}
 Modeling homeostasis necessarily includes a form of error estimation, which requires setting some predefined target that the feedback control will attempt to achieve.
@@
 
-However, numerous experimental and theoretical studies have suggested that the presence of both slow- and fast-firing cells is not to be regarded as an ignorable, mere side effect of brain dynamics.
+However, numerous experimental and theoretical studies have suggested that the presence of both slow- and fast-firing cells is not to be regarded as an ignorable, mere side effect of brain dynamics \cite{Buzsaki_2004,Marsat_2010,Tripathy_2013}.
 It rather seems to be that skewed and heavy-tailed firing rate statistics are necessary with respect to the preservation of stable synaptic structures, being related to long-term memory, while still allowing synaptic rewiring in order to adapt to changes in external stimuli.
@@
 Another problem that one might consider is the fact that temporal fluctuations of activity are believed to be a major part of information transmission and processing within the brain \cite[p.
-123-150]{Theor_Neur_Dayan}.
+123--150]{Theor_Neur_Dayan}.
 Homeostasis as described above could potentially override information by eliminating these fluctuations of activity.
@@
 suggest that diffusive signaling could resolve the dichotomy between overall stability of firing activity and the need to allow flexibility among individual neurons' activities.
-Through the diffusive signal, each neurons receives - intuitively speaking - a mixture of its own activity and its neighboring neurons.
+Through the diffusive signal, each neurons receives---intuitively speaking---a mixture of its own activity and its neighboring neurons.
 Individual tuning of firing rates is thereby suppressed while the overall population activity is kept at a constant level.
@@
 These Enzymes differ in their functionality and dependence on the presence of other molecules.
-In particular, nNOS is sensitive to the concentration of $Ca^{2+}$ ionic Calcium \cite{Knowles_Ca_nNOS,Steinert_NO}.
-Nitric oxide that was synthesized in the nervous system can diffuse freely because of its small molecular structure and electrical neutrality, which makes it a good candidate to be involved into a form of diffusive intracellular communication \cite{Lancaster_1994}.
-
-Voltage dependent $Ca^{2+}$-channels open due to a depolarization of the membrane potential in the course of an action potential, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98-100]{Hille_Ion_Channels}.
-A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445-451]{Hille_Ion_Channels}.
+In particular, nNOS is sensitive to the concentration of $\mathrm{Ca^{2+}}$ ionic Calcium \cite{Knowles_Ca_nNOS,Steinert_NO}.
+Nitric oxide that was synthesized in the nervous system can diffuse freely because of its small molecular structure and electrical neutrality, which makes it a good candidate to be involved into a form of diffusive intercellular communication \cite{Lancaster_1994}.
+
+Voltage dependent $Ca^{2+}$-channels open due to a depolarization of the membrane potential in the course of an action potential, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98--100]{Hille_Ion_Channels}.
+A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445--451]{Hille_Ion_Channels}.
 As such, $Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
 Experimental studies have also suggested that NO can act as an inhibitory diffusive signaling pathway, decreasing intrinsic excitability \cite{Steinert_NO_2011}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
-In experiments upon neurons in the medial nucleus of the trapezoid body Steinert et al.
-found that cells that were subject to NO-signaling by an external source exhibited an increment in outward $\mathrm{K^+}$ current, which, due to its hyperpolarizing effect, can be regarded as a form of intrinsic inhibition.
+In experiments on neurons in the medial nucleus of the trapezoid body Steinert et al.
+found that cells that were subject to NO-signaling by an external source exhibited an increment in outward $\mathrm{K^+}$ current, which, due to its hyperpolarizing effect, can be regarded as a form of intrinsic inhibition \cite{Steinert_NO}.
 
@@
 
-It has been generally argued that the set of rules used in these recurrent networks represent a realization of a minimum ensemble of functional compartments required in order to give rise to the desired capabilities.
+It has been generally argued that the set of rules used in these recurrent networks represents a realization of a minimum ensemble of functional elements required in order to give rise to the desired capabilities.
 The network's ability of self-organization has not only been investigated in terms of network structure itself.
@@
 All but recurrent excitatory synapses were randomly generated before the start of the simulation until a desired connection fraction was reached.
-The connection probability between two neurons was calculated from a distant dependent Gaussian function with a standard deviation of 200 $\mu m$.
+The connection probability between two neurons was calculated from a distance-dependent Gaussian function with a standard deviation of 200 $\mu m$.
 For excitatory to inhibitory (EI) and inhibitory to excitatory (IE) synapses, the connection fraction was set to 0.1, and 0.5 for recurrent inhibitory synapses (II).
@@
 
-Recurrent excitatory synapses were subject to a number of plastic mechanisms to be described in the following.
+Recurrent excitatory synapses were subject to a number of plastic mechanisms to be described in Section \ref{Section_Syn_Plast}.
 
@@
 \newpage
-\subsubsection{Synaptic Plasticity}
-\textbf{Synaptic Growth:} The random, distance dependent generation of new EE synapses was carried out n times once per second, where n is taken from a normal distribution with mean 920 and standard deviation $\sqrt{920}$.
-This constant growth rate was tuned to achieve the desired target concentration of 0.1 (see \ref{syn_conn_params}).
-
-\textbf{Synaptic Pruning:} At the same rate of 1/sec, EE synapses below a threshold of 0.000001 mV were removed, thus being added again to the set of ``potential" connections from which the growth process draws new connections.
-
-\textbf{Spike Timing Dependent Plasticity:} An additive STDP rule was used as described e.g.
-in \cite{Zhang_STDP}.
-The change of weight between two neurons due to a pre- and postsynaptic spike (i $\rightarrow$ j) is defined as:
-\begin{align}
-\Delta w_{ji} &= \sum_k \sum_l W(t_j^l - t_i^k) \label{STDP_rule} \\
-W(\Delta t) &= A_{+} exp(-\Delta t / \tau_{+}), & \Delta t > 0 \label{STDP_pos} \\
-W(\Delta t) &= A_{-} exp(\Delta t / \tau_{-}), & \Delta t < 0 \label{STDP_neg}
-\end{align}
-Indexes k and l refer to the k-th and l-th pre- and postsynaptic spike respectively.
-Parameters were chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
-However, we used the ``nearest neighbor" approximation for the sake of reduction of computational effort, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
-
-\textbf{Synaptic Normalization:} Experiments have suggested rescaling of synapses among individual postsynaptic neurons as a form of activity regulation in the brain: The mean incoming connectivity is multiplicatively adjusted, preserving ratios of weights.
-While this general mechanism has been confirmed in many experiments, results differ regarding the question whether the target connectivity is dynamically changing in order to preserve a certain postsynaptic firing rate (homeostatic synaptic scaling), or whether it remains constant, effectively enforcing a synaptic normalization.
-Though the latter does not directly enforce a fixed level of activity, one can argue that in a balanced recurrent network synaptic normalization still reduces the probability of very high or low firing rates caused by an above- or below-average total synaptic input.
-We implemented synaptic normalization by calling a function once per sec., updating each $w_{ji}$ from neuron $i$ to neuron $j$ as follows:
-
-\begin{equation}
-w_{ji} \rightarrow w_{ji} \frac{w_{total}}{\sum_i w_{ji}}
-\label{Synnnorm}
-\end{equation}
-$w_{total}$ was set to different values for each of the four types of connections between the excitatory and inhibitory pool of neurons.
-Except for the dynamically populated EE-synapses these values could be directly set in accordance with the previously given parameters of desired mean individual connection strength, size of the presynaptic population and connection fraction, by calculating $w_{total} = w_{mean} \cdot N_{presyn.
-pop}\cdot p_{connect}$.
-This yielded $w_{total,EI} = 60 mV$, $w_{total,IE} = -12 mV$, $w_{total,II} = -60 mV$.
-$w_{total,EE}$ was set to $40mV$,  corresponding to a mean synaptic weight of $1mV$, given a targeted EE-connection fraction of $0.1$ and a population of 400 excitatory neurons.
-
-\textbf{Short Term Plasticity:} A short term plasticity (STP) mechanism acting on recurrent excitatory connections was implemented as presented in \cite{Markram_STP} as an additional stabilization of network activity.
-It modulates the effective synaptic weights by multiplying the value stored in the weight matrix $w_{ji}$ by two dynamic variables $x$ and $u$, $w^{effective}_{ji} = w_{ji}\cdot x \cdot u$, each synapse owning a pair $(x,u)$.
-The dynamics of these variables are given by:
-
-\begin{equation}
-\dot{x} = \frac{1-x}{\tau_d},\; \dot{u} = \frac{U-u}{\tau_f}
-\label{STP_dynamics1}
-\end{equation}
-Each presynaptic spike furthermore causes a change of $x$ and $u$ by
-\begin{equation}
-x \rightarrow x - x\cdot u,\; u \rightarrow u + U(1-u)
-\label{STP_dynamics2}
-\end{equation}
-If no spikes arrive the system rests at $x\cdot u = U$.
-Otherwise, depending on the choice of $\tau_d$ and $\tau_f$, one can achieve a weight modulation that is dominated by potentiation ($\tau_f \gg \tau_d$) or depression ($\tau_f \ll \tau_d$).
-We chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$ as a rough approximation of the values that were experimentally observed \cite{Markram_STP}, giving it a tendency towards potentiation.
-However, one should keep in mind that for $U\in [0,1]$, $x\cdot u \in [0,1]$ always holds, thus the factor $x\cdot u$ has a generally diminishing effect.
-For our choice of variables for example, a Poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim 4.5 Hz$, corresponding to $x\cdot u \approx 0.2$.
-\textit{Potentiation} in this context refers to the fact that stronger input strengthens synaptic transmission \emph{compared} to close to zero incoming spikes.
-
-\newpage
+
 \subsubsection{Neuron Model}
-We used a leaky integrate-and-fire-model for all neurons in the network, whose dynamics are described by a stochastic differential equation:
+We used a leaky integrate-and-fire model for all neurons in the network, whose dynamics are described by a stochastic differential equation:
 \begin{equation}
@@
 A refractory period was not implemented.
-A presynaptic spike causes a simple (delayed, see Table \ref{syn_conn_params}) increment of the membrane potential of the postsynaptic neuron by $w^{effective}_{ji}$.
+A presynaptic spike causes a simple (delayed, see Table \ref{syn_conn_params}) increment of the membrane potential of the postsynaptic neuron by $w^{\rm effective}_{ji}$.
 Table \ref{LIF_neuron_params} summarizes the aforementioned set of parameters.
@@
 
+\subsubsection{Synaptic Plasticity}\label{Section_Syn_Plast}
+\textbf{Synaptic Growth:} Once per second, $\mathrm{n}$ new EE synapses were generated, where n is taken from a normal distribution with mean 920 and standard deviation $\sqrt{920}$.
+This constant growth rate was tuned to achieve the desired target concentration of 0.1 (see \ref{syn_conn_params}).
+
+\textbf{Synaptic Pruning:} At the same rate of 1/sec, EE synapses below a threshold of 0.000001 mV were removed, thus being added again to the set of ``potential" connections from which the growth process draws new connections.
+
+\textbf{Spike Timing Dependent Plasticity:} An additive STDP rule was used as described e.g.
+in \cite{Zhang_STDP}.
+The change of weight between two neurons due to a pre- and postsynaptic spike (i $\rightarrow$ j) is defined as:
+\begin{align}
+\Delta w_{ji} &= \sum_k \sum_l W(t_j^l - t_i^k) \label{STDP_rule} \\
+W(\Delta t) &= A_{+} \mathrm{exp}(-\Delta t / \tau_{+}), & \Delta t \geq 0 \label{STDP_pos} \\
+W(\Delta t) &= A_{-} \mathrm{exp}(\Delta t / \tau_{-}), & \Delta t < 0 \label{STDP_neg}
+\end{align}
+Indexes k and l refer to the k-th and l-th pre- and postsynaptic spike respectively.
+Parameters were chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
+However, we used the ``nearest neighbor" approximation for the sake of reduction of computational effort, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
+
+\textbf{Synaptic Normalization:} Experiments have suggested rescaling of synapses among individual postsynaptic neurons as a form of activity regulation in the brain: The mean incoming connectivity is multiplicatively adjusted, preserving ratios of weights.
+While this general mechanism has been confirmed in many experiments, results differ regarding the question whether the target connectivity is dynamically changing in order to preserve a certain postsynaptic firing rate (homeostatic synaptic scaling), or whether it remains constant, effectively enforcing a synaptic normalization.
+Though the latter does not directly enforce a fixed level of activity, one can argue that in a balanced recurrent network synaptic normalization still reduces the probability of very high or low firing rates caused by an above- or below-average total synaptic input.
+We implemented synaptic normalization by calling a function once per sec., updating each $w_{ji}$ from neuron $i$ to neuron $j$ as follows:
+
+\begin{equation}
+w_{ji} \rightarrow w_{ji} \frac{w_{total}}{\sum_i w_{ji}}
+\label{Synnnorm}
+\end{equation}
+$w_{total}$ was set to different values for each of the four types of connections between the excitatory and inhibitory pool of neurons.
+Except for the dynamically populated EE-synapses these values could be directly set in accordance with the previously given parameters of desired mean individual connection strength, size of the presynaptic population and connection fraction, by calculating $w_{total} = w_{mean} \cdot N_{presyn.
+pop}\cdot p_{connect}$.
+This yielded $w_{total,EI} = 60 mV$, $w_{total,IE} = -12 mV$, $w_{total,II} = -60 mV$.
+$w_{total,EE}$ was set to $40mV$,  corresponding to a mean synaptic weight of $1mV$, given a targeted EE-connection fraction of $0.1$ and a population of 400 excitatory neurons.
+
+\textbf{Short Term Plasticity:} A short term plasticity (STP) mechanism acting on recurrent excitatory connections was implemented as presented in \cite{Markram_STP} as an additional stabilization of network activity.
+It modulates the effective synaptic weights by multiplying the value stored in the weight matrix $w_{ji}$ by two dynamic variables $x$ and $u$, $w^{\rm effective}_{ji} = w_{ji}\cdot x \cdot u$, each synapse owning a pair $(x,u)$.
+The dynamics of these variables are given by:
+
+\begin{equation}
+\dot{x} = \frac{1-x}{\tau_d},\; \dot{u} = \frac{U-u}{\tau_f}
+\label{STP_dynamics1}
+\end{equation}
+Each presynaptic spike furthermore causes a change of $x$ and $u$ by
+\begin{equation}
+x \rightarrow x - x\cdot u,\; u \rightarrow u + U(1-u)
+\label{STP_dynamics2}
+\end{equation}
+If no spikes arrive the system rests at $x\cdot u = U$.
+Otherwise, depending on the choice of $\tau_d$ and $\tau_f$, one can achieve a weight modulation that is dominated by potentiation ($\tau_f \gg \tau_d$) or depression ($\tau_f \ll \tau_d$).
+We chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$ as a rough approximation of the values that were experimentally observed \cite{Markram_STP}, giving it a tendency towards potentiation.
+However, one should keep in mind that for $U\in [0,1]$, $x\cdot u \in [0,1]$ always holds, thus the factor $x\cdot u$ has a generally diminishing effect.
+For our choice of variables for example, a Poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim 4.5 Hz$, corresponding to $x\cdot u \approx 0.2$.
+\textit{Potentiation} in this context refers to the fact that stronger input strengthens synaptic transmission \emph{compared} to close to zero incoming spikes.
+
+\newpage
+
 \subsubsection{Intrinsic Plasticity (IP)}
@@
 In the latter case, a long-term change in excitability can be attributed to an altered resistance of ionic channels.
-This contrasts the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252-256]{Izhikevich_Dynsys}.
+This contrasts the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252--256]{Izhikevich_Dynsys}.
 A simple form of low intrinsic homeostasis was implemented in the original LIF-SORN by altering the neurons' firing threshold based on the deviation from a target firing rate.
@@
 \begin{align}
-V_t &\rightarrow V_t + \eta_{IP} (N_{spikes} - h_{IP}) \label{can_hom_1}\\
+V_t &\rightarrow V_t + \eta_{IP} (N_{\rm spikes} - h_{IP}) \label{can_hom_1}\\
 N_{spikes} &\rightarrow 0 \label{can_hom_2}
@@
 with $r$ as the neuron's firing rate and $r_{IP}=h_{IP}/\Delta t$ the target firing rate.
-This feedback control indirectly drives the firing rate of each neuron towards $r_{IP}$: If $r>(<)r_{IP}$, $V_t$ increases (decreases), reducing (increasing) the probability of a spike to occur.
+This feedback control indirectly drives the firing rate of each neuron towards $r_{IP}$: If $r>r_{IP}$($r<r_{IP}$), $V_t$ increases (decreases), reducing (increasing) the probability of a spike to occur.
 
@@
 \begin{align}
-\dot{{Ca^{2+}}_i}(t) &= -\frac{{Ca^{2+}}_i}{\tau_{Ca^{2+}}} + Ca^{2+}_{spike} \sum_{j} \delta(t-t^j_{spike,i}) \label{Ca_dyn}\\
-\dot{nNOS_i}(t) &= \frac{1}{\tau_{nNOS}} \left(\frac{{{Ca^{2+}}_i}^3}{{{Ca^{2+}}_i}^3+1} - nNOS_i \right) \label{nNOS_dyn}\\
-\dot{NO}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{neur,i})\cdot nNOS^i \label{NO_dyn}\\
-\dot{V_{t,i}}(t) &= \frac{NO(\mathbf{r}_{neur,i},t)-NO_0}{NO_0\cdot\tau_{V_t}} \label{Theta_dyn}
+\dot{Ca}_i^{2+}(t) &= -\frac{Ca_i^{2+}}{\tau_{Ca^{2+}}} + Ca^{2+}_{\rm spike} \sum_{j} \delta(t-t^j_{\mathrm{spike},i}) \label{Ca_dyn}\\
+\dot{nNOS_i}(t) &= \frac{1}{\tau_{nNOS}} \left(\frac{{Ca_i^{2+}}^3}{{Ca_i^{2+}}^3+1} - nNOS_i \right) \label{nNOS_dyn}\\
+\dot{NO}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{\mathrm{neur},i})\cdot nNOS^i \label{NO_dyn}\\
+\dot{V}_{t,i}(t) &= \frac{NO(\mathbf{r}_{\mathrm{neur},i},t)-NO_0}{NO_0\cdot\tau_{V_t}} \label{Theta_dyn}
 \end{align}
@@
 A depolarization within a nerve cell upon a spike-event $t_{spike}$ causes a fixed inflow of ionic current $Ca^{2+}_{spike}$, which is modeled as an instantaneous increase of the $Ca^{2+}$ concentration.
-The concentration decays exponentially by a time constant $\tau_{Ca^{2+}}$, see \eqref{Ca_dyn}.
-Though $Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198-203]{Theor_Neur_Dayan}.
+The concentration decays exponentially with a time constant $\tau_{Ca^{2+}}$, see \eqref{Ca_dyn}.
+Though $Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198--203]{Theor_Neur_Dayan}.
 The influence of $Ca^{2+}$ onto nNOS was modeled by Sweeney et al.
@@
 One rather needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration.
-Though it is possible to derive this relation in an analytic fashion, we let the system run with the previous homeostatic mechanism, still solving equation \eqref{Ca_dyn}-\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
+Though it is possible to derive this relation in an analytic fashion, we let the system run with the previous homeostatic mechanism, still solving equation \eqref{Ca_dyn}--\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
 This mean was then set to be the target concentration and we switched to diffusive homeostasis.
@@
 
-Although one might argue that - for the sake of practical purposes - regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further inquiry.
+Although one might argue that---for the sake of practical purposes---regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further inquiry.
 Rhythmic patterns of activity are a commonly observed phenomenon within the brain.
@@
 On a microscopic, single-neuron level, a so-called slow after-hyper-polarization conductance explains the appearance of bursting behavior: A relatively short period of spiking activity is followed by a longer period of silence.
-This phenomenon can be modeled by a $Ca^{2+}$-dependent $K^{+}$-conductance.
-$Ca^{2+}$ concentration rises upon the bursting period, prohibiting continuous spiking due to the activation of $K^{+}$  current until the $Ca^{2+}$ concentration has returned to base-level \cite[p.~203-207]{Theor_Neur_Dayan}.
+This phenomenon can be modeled by a $Ca^{2+}$-dependent $K^{+}$ conductance.
+$Ca^{2+}$ concentration rises upon the bursting period, prohibiting continuous spiking due to the activation of $K^{+}$  current until the $Ca^{2+}$ concentration has returned to base-level \cite[p.~203--207]{Theor_Neur_Dayan}.
 However, this type of oscillating activity can be ruled out as an explanation due to the simplicity of our neuron model.
@@
 where $\tau_e$ and $\tau_i$ are time constants representing the rapidity of firing rate adaptation, $\phi_e$ and $\phi_i$ the respective transition functions between synaptic input and firing rate and $W_{xy}$ the mean synaptic weight from population x to population y.
-A persistent oscillation then corresponds to a stable limit cycle in the 2-dimensional phase plane.
+A persistent oscillation then corresponds to a stable limit cycle in the two-dimensional phase plane.
 Such a limit cycle exists inside a region $R$ if $R$ contains no fixed points and if any trajectory whose starting points lies within $R$ is confined to $R$, according to the Poincaré-Bendixson theorem.
@@
 \begin{equation}
-\phi(J) = \begin{cases}\frac{1}{-\tau_m ln(\frac{V_t -E_l-J\tau_m}{V_r -E_l-J\tau_m})} & \mathrm{for}\; J\tau_m + E_l > V_t\\
+\phi(J) = \begin{cases}\frac{1}{-\tau_m ln \left( \frac{V_t -E_l-J\tau_m}{V_r -E_l-J\tau_m} \right)} & \mathrm{for}\; J\tau_m + E_l > V_t\\
 0 & \mathrm{otherwise}
@@
 \begin{align}
-\phi(J) &= \left[ \sqrt{\pi}\tau_m \int_{x_-}^{x_+} dx e^{x^2} erfc(-x) \right]^{-1} \label{LIF_Fir_Rate_with_Noise1}\\
-x_- &= (V_r-E_l-J\tau_m)/\sigma \label{LIF_Fir_Rate_with_Noise2}\\
-x_+ &= (V_t-E_l-J\tau_m)/\sigma \label{LIF_Fir_Rate_with_Noise3}
-\end{align}
-where $erfc$ is the complementary error function. Figure \ref{F-I_noise_dep} shows that both predictions are quite accurate in predicting the mean firing rate. 
+\phi(J) &= \left[ \sqrt{\pi}\tau_m \int_{x_-}^{x_+} dx e^{x^2} \mathrm{erfc}(-x) \right]^{-1} \label{LIF_Fir_Rate_with_Noise1}\\
+x_- &= \left( V_r-E_l-J\tau_m \right)/\sigma \label{LIF_Fir_Rate_with_Noise2}\\
+x_+ &= \left( V_t-E_l-J\tau_m \right)/\sigma \label{LIF_Fir_Rate_with_Noise3}
+\end{align}
+where $\mathrm{erfc}$ is the complementary error function. Figure \ref{F-I_noise_dep} shows that both predictions are quite accurate in predicting the mean firing rate. 
 \begin{figure}
@@
 One should note however that the synaptic input within a spiking network carries an intrinsic randomness: One cannot simply describe it as a mean constant input $J$, since it is the sum of instantaneous increases in membrane voltage upon arriving spikes.
-Rather, if we assume that the arrival of spikes is approximately Poisson distributed and the time constant of the membrane is small compared to the average interspike-interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \cdot \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
-\begin{align}
-\mu_{AB} &= <w_{AB}> \cdot <N_{in,AB}> \cdot <r_A> \label{Noise_Approx_1}\\
-\sigma_{AB} &= \sqrt{\tau_m \cdot <w_{AB}>^2 \cdot <N_{in,AB}> \cdot <r_A>} \label{Noise_Approx_2} \, .
-\end{align}
-$\mathrm{<w_{AB}>,\, <N_{in,AB}>}$ and $\mathrm{<r_A>}$ denote the mean weight of a synapse connection population $\mathrm{A}$ with population $\mathrm{B}$, the mean number of incoming connections at a neuron in population $\mathrm{B}$ and the mean firing rate in population $\mathrm{A}$ (which makes it necessary to assume changes within the firing rate to be slow enough for a quasi-stationary description of the activity).
+Rather, if we assume that the arrival of spikes is approximately Poisson distributed and the time constant of the membrane is small compared to the average interspike-interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
+\begin{align}
+\mu_{AB} &= \langle w_{AB} \rangle  \langle N_{\mathrm{in},AB} \rangle \cdot \langle r_A \rangle \label{Noise_Approx_1}\\
+\sigma_{AB} &= \sqrt{\tau_m  \langle w_{AB} \rangle ^2  \langle N_{\mathrm{in},AB} \rangle  \langle r_A \rangle} \label{Noise_Approx_2} \, .
+\end{align}
+$\mathrm{\langle w_{AB} \rangle,\, \langle N_{\mathrm{in},AB} \rangle}$ and $\mathrm{\langle r_A \rangle}$ denote the mean weight of a synapse connection population $\mathrm{A}$ with population $\mathrm{B}$, the mean number of incoming connections at a neuron in population $\mathrm{B}$ and the mean firing rate in population $\mathrm{A}$ (which makes it necessary to assume changes within the firing rate to be slow enough for a quasi-stationary description of the activity).
 The total noise within a neuron of population $\mathrm{B}$ has a standard deviation of 
@@
 The results are depicted in Figure \ref{Dyn_Rate_Approx}.
-The system settled to a fixed point of $\mathrm{(r_{0,e},r_{0,i}) = (2.992\, Hz, 7.144\, Hz)}$, which is quite close to $\mathrm{(3\, Hz, 6.768\, Hz)}$, which is the mean excitatory and inhibitory firing rate between 100-750 s of the full simulation (i.e., during non-diffusive homeostasis).
+The system settled to a fixed point of $\mathrm{(r_{0,e},r_{0,i}) = (2.992\, Hz, 7.144\, Hz)}$, which is quite close to $\mathrm{(3\, Hz, 6.768\, Hz)}$, which is the mean excitatory and inhibitory firing rate between $\mathrm{100-750\, s}$ of the full simulation (i.e., during non-diffusive homeostasis).
 \begin{figure}
@@
 Two questions are of importance in the context of feedback dynamics.
-First - obviously - how the relation between a local change of threshold and the new fixed point of the network can be described and second, whether the time scale of the network's response is of relevance with respect to other time scales involved in the feedback loop.
+First---obviously---how the relation between a local change of threshold and the new fixed point of the network can be described and second, whether the time scale of the network's response is of relevance with respect to other time scales involved in the feedback loop.
 Regarding the second question, Figure \ref{rate_th_close} suggests that the excitatory population activity follows the mean firing threshold in a quasi instantaneous fashion, at least in comparison with the overall time scale of the oscillating pattern.
@@
 \end{equation}
-In this form, the integral has an easy-to-handle solution, which - with all spike events now included - results in
+In this form, the integral has an easy-to-handle solution, which---with all spike events now included---results in
 \begin{equation}
@@
 However, it is not sufficient to simply propose $nNOS_i(t) = r_i(t) \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
-A single cell fires in the range of $\mathrm{3\,Hz}$, which is - at least on the time scale of the observed oscillations - not enough to assign an instantaneous firing rate.
+A single cell fires in the range of $\mathrm{3\,Hz}$, which is---at least on the time scale of the observed oscillations---not enough to assign an instantaneous firing rate.
 \newpage
@@
 The amount of noise in the system is a hard-to-predict quantity since it depends on the spatial structure on the diffusive lattice, giving neurons that are further separated less impact onto each other.
-We tried to estimate the noise level based on the same instant-spread-simplification made in Equation \eqref{NO_dyn_approx} to describe the overall NO-dynamics.
+We tried to estimate the noise level based on the same instant-spread simplification made in Equation \eqref{NO_dyn_approx} to describe the overall NO-dynamics.
 This led to an underestimation of the total energy within the power spectrum in the final result.
@@
 \end{figure}
-The fact that the value for $\mathrm{\alpha}$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency can be partially explained by the linear regression, which overestimates the importance of a number of high-threshold-outliers.
+The fact that the value for $\mathrm{\alpha}$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency can be partially explained by the linear regression, which overestimates the importance of a number of high-threshold outliers.
 This leads to a shallower slope than what would be appropriate for the working point of oscillatory behavior.
@@
 \includegraphics[width=\textwidth]{../../plots/diff_hom/osc_ampl_vs_tau_th.png}
-\caption{A: Maximum of the spectrum-peak (see Figure \ref{Pow_Spec_Theta_vs_Analytic}).
+\caption{A: Maximum of the spectrum peak (see Figure \ref{Pow_Spec_Theta_vs_Analytic}).
 A smoothing window of $\mathrm{[-5,5]}$ data points around the maximum was used to reduce overestimation of the maximum due to random fluctuations.
@@
 This observation is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons have an  under-representation of short ISIs, the opposite is the case for inhibitory neurons.
-These types of behavior of LIF-models have been shown to depend on the CV of input the neuron receives: A smaller signal-to-noise-ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals \cite{Ostojic2011}.
+These types of behavior of LIF-models have been shown to depend on the CV of input the neuron receives: A smaller signal-to-noise ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals \cite{Ostojic2011}.
 This relation fits nicely into our set of network parameters: Inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
@@
 We looked at potential correlations across neurons within both populations as an additional possibility of spike-train analysis.
-To do so, we calculated cross-correlations for all possible neuron-pairings within a population, excluding auto-correlations.
+To do so, we calculated cross-correlations for all possible neuron pairings within a population, excluding auto-correlations.
 Figure \ref{Pop_Mean_Cross_Corr} shows the mean cross-correlation taken over all these pairs.
@@
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/pop_mean_cross_corr.png}
-\caption{Mean of cross correlation over all pairs of neurons in the respective neuron-group.
+\caption{Mean of cross correlation over all pairs of neurons in the respective neuron group.
 Significantly higher correlation can be found in both groups for diffusive homeostasis.
@@
 
-Despite of fluctuations within the firing rate on small time scales due to the inherent nature of - approximately - random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds.
+Despite of fluctuations within the firing rate on small time scales due to the inherent nature of---approximately---random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds.
 This question is not only of relevance with respect to the ``stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of momentary rates.
@@
 We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only population-wise but on a single-cell level as well.
-In particular, plastic modifications across the network due to STDP and synaptic growth/pruning - which were always acting for all the simulation results presented so far - appeared to be compensated for.
+In particular, plastic modifications across the network due to STDP and synaptic growth/pruning---which were always acting for all the simulation results presented so far---appeared to be compensated for.
 
@@
 Synaptic efficacy and number of incoming neurons were drawn randomly to match the statistics of the actual network topology.
-Self consistency was achieved by iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate1} until the desired precision of convergence was reached.
+Self consistency was achieved by iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate1} until the desired precision of convergence was reached.
 
@@
 
-Instead of directly iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1} - \eqref{sweeney_self_consist_rate3} - as done in \cite{Sweeney_Paper} - to fulfill self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
+Instead of directly iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate3}---as done in \cite{Sweeney_Paper}---to fulfill self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
 \begin{equation}
@@
 \end{figure}
-These findings led us to the conclusion that - apart from the special case $\mathrm{\alpha=1}$, which is the equivalent to instantaneous diffusion - a mean-field model describing the diffusive signal as a mixture of individual activity and all neurons is not suitable for explaining the existence of stable heterogeneous distributions of rates for a broad range of diffusion constants.
+These findings led us to the conclusion that---apart from the special case $\mathrm{\alpha=1}$, which is the equivalent to instantaneous diffusion---a mean-field model describing the diffusive signal as a mixture of individual activity and all neurons is not suitable for explaining the existence of stable heterogeneous distributions of rates for a broad range of diffusion constants.
 We did not intent to debase the validity of results of the mean-field model of Sweeney et al.
@@
 \caption{Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz} (blue, $\mathrm{h=10\;\mu m}$) and its approximation (dashed) given by \eqref{Numeric_Solution_Expression_Trick}.
-The numerical simulation was carried out on a 2d-grid and the curve represents a cut through the origin in x-direction.}
+The numerical simulation was carried out on a two-dimensional grid and the curve represents a cut through the origin in x-direction.}
 \label{Psi_Approximation_Compare}
 \end{figure}
-We took this approximation as a basis for further calculations of the interaction-matrix $\mathrm{\hat{\psi}}$.
+We took this approximation as a basis for further calculations of the interaction matrix $\mathrm{\hat{\psi}}$.
 
@@
 Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 ms^{-1}}$, the correlation between measured and predicted firing rates is very good.
-In contrast, we included the - obviously unsuccessful - attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 ms^{-1}}$.
+In contrast, we included the---obviously unsuccessful---attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 ms^{-1}}$.
 This represented a limiting case where our analytic model could not make any meaningful predictions, since instant diffusion overrides any spatial inhomogeneities.
@@
 \includegraphics[width=\textwidth]{../../plots/rates_matrix_prediction_vs_sim.png}
-\caption{Measured firing rates (t=1200-1500 s) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
+\caption{Measured firing rates ($\mathrm{1200\,s \leq t \leq 1500\, s}$) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
 For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably large diffusion constant of $\mathrm{D=100\, \mu m^2 ms^{-1}}$.}
@@
 By doing so all neurons were given the same structure of neighbors.
-We expected that all neurons then should - in theory - exhibit the exact same firing rate due to symmetry.
+We expected that all neurons then should---in theory---exhibit the exact same firing rate due to symmetry.
 Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the result, being a significantly narrower distribution.
@@
 \includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
-\caption{(A) and (B): Scatter-plot of inverse of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights.
+\caption{(A) and (B): Scatter plot of inverse of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights.
 Note the spatial correlation in high/low-density regions.
@@
 Though the distribution did approximately resemble a log-normal-like shape, it did not perfectly match our expectations.
-In order to acquire a deeper understanding of the mechanisms that determine these statistics we developed an analytical expression that allowed us to reliably predict the steady-state of firing rates based on the spatial structure of excitatory neurons.
+In order to acquire a deeper understanding of the mechanisms that determine these statistics we developed an analytical expression that allowed us to reliably predict the steady state of firing rates based on the spatial structure of excitatory neurons.
 We would like to emphasize that this explanation differs from common approaches of understanding the emergence of heavy-tailed statistics of firing rates in recurrent networks.
@@
 From a more general perspective one could argue that a mechanism binding firing rates to spatial constraints suppresses the ability of the system to adapt to a changing environment since it essentially ``freezes" the state of activity.
-Experiments have shown that neurons' firing rates are indeed correlated under a changing environment/task: Neurons with a certain baseline-firing rate are very likely to have a similar firing rate while performing a task \cite{Buzsaki_Fir_Rates_2014}.
+Experiments have shown that neurons' firing rates are indeed correlated under a changing environment/task: Neurons with a certain baseline firing rate are very likely to have a similar firing rate while performing a task \cite{Buzsaki_Fir_Rates_2014}.
 While homeostatic fixation might not be problematic in the case of transient changes of stimuli, a spatial fixation of firing rates would presumably contradict the fact that long-term learning processes and plasticity lead to persistent changes in activity patterns \cite{Lever_Long_Term_Plast_2002}.
@@
 \subsection{Network Topology} 
-Even though our investigations on network topology were rather intended as a form of sanity-check with respect to properties already found in earlier versions, we found some differences compared to non-diffusive homeostasis.
+Even though our investigations on network topology were rather intended as a form of sanity check with respect to properties already found in earlier versions, we found some differences compared to non-diffusive homeostasis.
 
@@
 Referring back to Figure \ref{Pop_Mean_Cross_Corr}, we can now relate the increment of correlation among the excitatory population in the case of diffusive homeostasis to the results discussed in this section: The emergence of very strong outgoing connections increases the probability of neurons being postynaptically connected to such highly influential neurons to fire shortly after the presynaptic neuron.
-In the light of the notion of ``rich get richer" or ``rich stay rich" weight-dynamics that were reported for earlier versions of SORN and LIF-SORN, one can argue that this increment in correlation even further stabilizes these strong excitatory weights \cite{Pengsheng_2013,SORN_Paper}.
+In the light of the notion of ``rich get richer" or ``rich stay rich" weight dynamics that were reported for earlier versions of SORN and LIF-SORN, one can argue that this increment in correlation even further stabilizes these strong excitatory weights \cite{Pengsheng_2013,SORN_Paper}.
 
 As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}) we found that neurons with a low-density neighborhood have a higher chance of developing these strong outgoing weights.
-Since this effect is directly linked to the low-density/high-firing rate-relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons with above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
+Since this effect is directly linked to the low-density/high-firing-rate relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons with above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
 
@@
 From a topological point of view, the implementation of homeostasis can be regarded as a success: Thanks to the broad range of neural activity it allowed for the emergence of highly influential subgroups of excitatory neurons.
-This - experimentally confirmed - feature was not present in earlier versions of the LIF-SORN.
+This---experimentally confirmed---feature was not present in earlier versions of the LIF-SORN.
 It thus can be regarded as another non-random property of cortical structure that was not hard-coded but naturally emerged from the set of basic rules that constitute dynamics and behavior of our network.

### 2017-03-01 draft.tex
.

@@
 
-Voltage dependent $Ca^{2+}$-channels open due to a depolarization of the membrane potential in the course of an action potential, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98--100]{Hille_Ion_Channels}.
+Voltage dependent $\rm Ca^{2+}$-channels open due to a depolarization of the membrane potential in the course of an action potential, which causes a significant increase of the intracellular Calcium concentration (relative to the low concentration at rest) \cite[p.~98--100]{Hille_Ion_Channels}.
 A common theoretical description of voltage-dependent ion channels is provided by the Goldman-Hodgkin-Katz equations, see \cite[p.~445--451]{Hille_Ion_Channels}.
-As such, $Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
+As such, $\rm Ca^{2+}$ constitutes a causal link between spiking activity and the production of NO.
 Experimental studies have also suggested that NO can act as an inhibitory diffusive signaling pathway, decreasing intrinsic excitability \cite{Steinert_NO_2011}, or generally suggest a role of NO in maintaining a functional state of activity \cite{Pape_NO}.
@@
 \begin{equation}
-{\tau_m}dV = -(V-E_l)dt + \sqrt{\tau_m} \sigma dW
+{\tau_m}dV_i = -\left( V_i-E_l \right) dt + \sqrt{\tau_m} \sigma dW_i + \tau_m \sum_{j,k} w^{\rm effective}_{ij}\delta \left( t^k_{\mathrm{spike},j} + t_{\rm delay} - t \right)
 \label{LIF_Dynamics}
 \end{equation}
-where $V$ is the membrane potential, $E_l$ is the equilibrium membrane potential, $\tau_m$ is the time constant of the membrane, $\sigma$ is the standard deviation of the noise term and $dW$ is the standard Wiener process.
+where $V_i$ is the membrane potential of neuron $i$, $E_l$ is the equilibrium membrane potential, $\tau_m$ is the time constant of the membrane, $\sigma$ is the standard deviation of the noise term and $dW$ is the standard Wiener process.
 A neuron is said to spike when its membrane potential reaches the threshold voltage $V_t$.
@@
 A refractory period was not implemented.
-A presynaptic spike causes a simple (delayed, see Table \ref{syn_conn_params}) increment of the membrane potential of the postsynaptic neuron by $w^{\rm effective}_{ji}$.
+A presynaptic spike from neuron $j$ causes a simple (delayed, see Table \ref{syn_conn_params}) increment of the membrane potential of the postsynaptic neuron $i$ by $w^{\rm effective}_{ij}$.
 Table \ref{LIF_neuron_params} summarizes the aforementioned set of parameters.
@@
 In the latter case, a long-term change in excitability can be attributed to an altered resistance of ionic channels.
-This contrasts the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252--256]{Izhikevich_Dynsys}.
+This contrasts with the former short-term adaption, which can be explained by a separation of timescales among different ionic currents in the cell \cite[p.~252--256]{Izhikevich_Dynsys}.
 A simple form of low intrinsic homeostasis was implemented in the original LIF-SORN by altering the neurons' firing threshold based on the deviation from a target firing rate.
 During the research reported by this thesis we implemented a new model of slow intrinsic homeostasis, based on the work in \cite{Sweeney_Paper}.
-The following section describes both models in further detail.
+The following section describes both models in detail.
 \subsubsection{Modeling of Homeostatic Intrinsic Plasticity}
@@
 V_t &\rightarrow V_t + \eta_{IP} (N_{\rm spikes} - h_{IP}) \label{can_hom_1}\\
-N_{spikes} &\rightarrow 0 \label{can_hom_2}
+N_{\rm spikes} &\rightarrow 0 \label{can_hom_2}
 \end{align}
@@
 \dot{nNOS_i}(t) &= \frac{1}{\tau_{nNOS}} \left(\frac{{Ca_i^{2+}}^3}{{Ca_i^{2+}}^3+1} - nNOS_i \right) \label{nNOS_dyn}\\
-\dot{NO}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{\mathrm{neur},i})\cdot nNOS^i \label{NO_dyn}\\
+\dot{NO}(\mathbf{r},t)&=-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{r}-\mathbf{r}_{\mathrm{neur},i})\cdot nNOS_i \label{NO_dyn}\\
 \dot{V}_{t,i}(t) &= \frac{NO(\mathbf{r}_{\mathrm{neur},i},t)-NO_0}{NO_0\cdot\tau_{V_t}} \label{Theta_dyn}
@@
 
-A depolarization within a nerve cell upon a spike-event $t_{spike}$ causes a fixed inflow of ionic current $Ca^{2+}_{spike}$, which is modeled as an instantaneous increase of the $Ca^{2+}$ concentration.
+A depolarization within a nerve cell upon a spike-event $t_{spike}$ causes a fixed inflow of ionic current $Ca^{2+}_{spike}$, which is modeled as an instantaneous increase of the $\rm Ca^{2+}$ concentration.
 The concentration decays exponentially with a time constant $\tau_{Ca^{2+}}$, see \eqref{Ca_dyn}.
-Though $Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198--203]{Theor_Neur_Dayan}.
-The influence of $Ca^{2+}$ onto nNOS was modeled by Sweeney et al.
+Though $\rm Ca^{2+}$ currents can be described in a much more detailed fashion, it can be considered as a reasonable approximation \cite[p.~198--203]{Theor_Neur_Dayan}.
+The influence of $\rm Ca^{2+}$ onto nNOS was modeled by Sweeney et al.
 through \eqref{nNOS_dyn} using the Hill equation \cite{Hill_Equ} to model a cooperative binding mechanism.
-The $nNOS$ production is then fed into the pool of nitric oxide via point sources located at the neurons' positions.
-An additional decay term was added apart from the inflow and the diffusive term to provide a stable finite $NO$ concentration under constant neuronal activity.
+The $\rm nNOS$ production is then fed into the pool of nitric oxide via point sources located at the neurons' positions.
+An additional decay term was added apart from the inflow and the diffusive term to provide a stable finite $\rm NO$ concentration under constant neuronal activity.
 
@@
 The appropriate choice of $NO_0$ is obviously crucial for the goal of achieving and maintaining a certain level of activity.
-However, one cannot directly set a parameter of the model to the desired population activity as it was the case for canonical intrinsic homeostasis.
+However, one cannot directly set a parameter of the model to the desired population activity as was the case for canonical intrinsic homeostasis.
 One rather needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration.
@@
 \end{equation}
-on each time step, where $h = L/100$ is the distance between neighbored grid points, determined by the length $L$ of the square sheet and the resolution of the numeric grid.
-We implemented three possible boundary conditions into the simulation:
+on each time step, where $h = L/100$ is the distance between neighboring grid points, determined by the length $L$ of the square sheet and the resolution of the numeric grid.
+We implemented three possible boundary conditions for the simulation:
 
@@
 
-2.) Neumann boundary conditions with $\nabla NO = (0,0)$ at the boundaries:
+2.) Neumann boundary conditions (named after Carl Neumann) with $\nabla NO = (0,0)$ at the boundaries:
 \begin{align}
@@
 Figure \ref{diff_test_plot} shows an example of the resulting NO density throughout a simulation.
+Note that the actual values of concentration do not approximate actual biological values, since Equation \eqref{nNOS_dyn} binds the rate of $\rm NO$ production between $\rm 0$ and $\rm 1$ for simplicity.
 \begin{figure}[h!]
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{../../plots/density_plots/density_plot.png}
+\includegraphics[width=0.8\textwidth]{../../plots/density_plots/density_plot.png}
 \end{center}
@@
 We set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$ on a first attempt, as given by \cite{Sweeney_Paper}.
-Switching between non-diffusive/diffusive homeostasis after 750 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group, the average $NO$ concentration at the excitatory neurons' positions and the average firing threshold within the excitatory group (inhibitory threshold was fixed, see table \ref{LIF_neuron_params}).
+Switching between non-diffusive/diffusive homeostasis after 750 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group (panel A/A*), the average $\rm NO$ concentration at the excitatory neurons' positions (panel B/B*) and the average firing threshold (panel C/C*) within the excitatory group (inhibitory threshold was fixed, see table \ref{LIF_neuron_params}).
 Both homeostatic mechanisms managed to keep the excitatory population activity in the desired range of 3 Hz.
-However, what might appear to be slightly faster and stronger random fluctuations in the upper three plots of Figure \ref{full_sim_osci} were in fact regular oscillations across all three depicted variables.
+However, what might appear to be slightly faster and stronger random fluctuations in panel A-C were in fact regular oscillations across all three depicted variables, as can be seen in panel A*-C*, showing the dynamics in a smaller time window.
 While the oscillation amplitudes undergo a rather unpredictable course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
@@
 The fact that the mean over all power spectra of excitatory thresholds differs from the power spectrum of the mean of these thresholds in its amplitude indicates that not all thresholds oscillate at the same phase.
-The overall shapes of both spectra are though still equivalent.
+The overall shapes of both spectra are still similar, though.
 \begin{figure}
@@
 
-Although one might argue that---for the sake of practical purposes---regular oscillations of the $NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further inquiry.
+Although one might argue that---for the sake of practical purposes---regular oscillations of the $\rm NO$ concentration are not of much concern for the network as such, a periodically fluctuating firing rate is a qualitative feature requiring further inquiry.
 Rhythmic patterns of activity are a commonly observed phenomenon within the brain.
@@
 On a microscopic, single-neuron level, a so-called slow after-hyper-polarization conductance explains the appearance of bursting behavior: A relatively short period of spiking activity is followed by a longer period of silence.
-This phenomenon can be modeled by a $Ca^{2+}$-dependent $K^{+}$ conductance.
-$Ca^{2+}$ concentration rises upon the bursting period, prohibiting continuous spiking due to the activation of $K^{+}$  current until the $Ca^{2+}$ concentration has returned to base-level \cite[p.~203--207]{Theor_Neur_Dayan}.
+This phenomenon can be modeled by a $\rm Ca^{2+}$-dependent $\rm K^{+}$ conductance.
+$\rm Ca^{2+}$ concentration rises upon the bursting period, prohibiting continuous spiking due to the activation of $\rm K^{+}$  current until the $\rm Ca^{2+}$ concentration has returned to base-level \cite[p.~203--207]{Theor_Neur_Dayan}.
 However, this type of oscillating activity can be ruled out as an explanation due to the simplicity of our neuron model.
@@
 \end{align}
-where $\tau_e$ and $\tau_i$ are time constants representing the rapidity of firing rate adaptation, $\phi_e$ and $\phi_i$ the respective transition functions between synaptic input and firing rate and $W_{xy}$ the mean synaptic weight from population x to population y.
+where $\tau_e$ and $\tau_i$ are time constants representing the rapidity of firing rate dynamics, $\phi_e$ and $\phi_i$ the respective transfer functions between synaptic input and firing rate and $W_{xy}$ the mean synaptic weight from population x to population y.
 A persistent oscillation then corresponds to a stable limit cycle in the two-dimensional phase plane.
@@
 Several aspects come into play, making it a hard task to fit the full spiking network model onto the simplified equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
-First, the choice of $\tau_e$ and $\tau_i$ in \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2} has significant influence onto the stability of the system.
+First, the choice of $\tau_e$ and $\tau_i$ in \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2} has significant influence on the stability of the system.
 However, a straightforward equivalent does not exist in the used spiking neuron model.
@@
 \begin{figure}
+%noise_no_noise_rate_compare.py
 \begin{center}
@@
 \begin{align}
-\mu_{AB} &= \langle w_{AB} \rangle  \langle N_{\mathrm{in},AB} \rangle \cdot \langle r_A \rangle \label{Noise_Approx_1}\\
+\mu_{AB} &= \langle w_{AB} \rangle  \langle N_{\mathrm{in},AB} \rangle \langle r_A \rangle \label{Noise_Approx_1}\\
 \sigma_{AB} &= \sqrt{\tau_m  \langle w_{AB} \rangle ^2  \langle N_{\mathrm{in},AB} \rangle  \langle r_A \rangle} \label{Noise_Approx_2} \, .
@@
 \begin{equation}
-\sigma_{tot.} = \sqrt{\sigma_{intr.}^2 + \sum_A \sigma_{AB}^2} \; .
+\sigma_{tot.} = \sqrt{\sigma_{\rm intr.}^2 + \sum_A \sigma_{AB}^2} \; .
 \label{Total_Noise_Neuron}
@@
 \end{figure}
-In principal one could now further quantify the stability of the found fixed point by calculating the Jacobian matrix at $\mathrm{(r_{0,e},r_{0,i})}$.
-For the sake of the initial question though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: The recurrent network as such (without homeostasis) is stable under the given choice of parameters, assuming validity of the described rate model.
-Furthermore, on an empirical basis, the occurrence of oscillations appear to be rather dependent on the choice of homeostasis since all parameters of the simulation were kept unchanged upon the transition after 750 s, apart from the homeostatic mechanism itself.
+In principle, one could now further quantify the stability of the found fixed point by calculating the Jacobian matrix at $\mathrm{(r_{0,e},r_{0,i})}$.
+For the sake of the initial question, though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: The recurrent network as such (without homeostasis) is stable under the given choice of parameters, assuming validity of the described rate model.
+Furthermore, on an empirical basis, the occurrence of oscillations appears to be rather dependent on the choice of homeostasis since all parameters of the simulation were kept unchanged upon the transition after 750 s, apart from the homeostatic mechanism itself.
 Therefore, we present in the following section our further analysis of the dynamics underlying the diffusive homeostatic feedback.
@@
 \end{figure}
-We thus presumed an immediate functional relationship $\mathbf{r}_e (t) = \mathbf{r}_e (\mathbf{V}_{t,e} (t))$ in a first attempt of understanding the occurrence of undesired oscillations, where $\mathbf{r}_e$ and $\mathbf{V}_{t,e}$ represent the set of excitatory firing rates and thresholds, respectively.
+We thus presumed an immediate functional relationship $\mathbf{r}_e (t) = \mathbf{r}_e (\mathbf{V}_{t,e} (t))$ in a first attempt at understanding the occurrence of undesired oscillations, where $\mathbf{r}_e$ and $\mathbf{V}_{t,e}$ represent the set of excitatory firing rates and thresholds, respectively.
 
 Describing the neural activity as instantaneous firing rates raises the question how to describe the production of nitric oxide, since the outcome of equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $Ca^{2+}$ concentration caused by spike events.
-One could naively replace the sum of Dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{spike} r_i(t)$.
+One could naively replace the sum of Dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{\rm spike} r_i(t)$.
 This approximation would indeed allow for the correct calculation of a linear relation between mean firing rate and NO production if \eqref{nNOS_dyn} was a linear homogeneous differential equation.
@@
 Consequently, it is very unlikely that one spike event will fall into a region where the calcium concentration, decaying from the instant jump of the previous spike event, is still significantly larger than zero.
-As such, one can justify
+In fact, calculating the mean concentration of $\rm Ca^{2+}$ before a new spike event over all neurons and all spike events for $\rm 1500\,s$ resulted in a value of $\rm 0.0013$.
+As such, one can justify the approximation of replacing the exact expression of ${Ca^{2+}}^3(t)$, which is a cubed sum of cut-off exponential functions, by a sum of cubed exponentials, because only one term of the sum at a time is significantly larger than zero:
 \begin{equation}
 \begin{split}
-{Ca^{2+}}^3(t) &= \left[ Ca^{2+}_{spike} \sum_{i} \theta(t-t^i_{spike}) exp(-(t-t^i_{spike})/\tau_{Ca^{2+}}) \right]^3 \\
-&\approx {Ca^{2+}_{spike}}^3 \sum_{i} \theta(t-t^i_{spike}) exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}})
+{Ca^{2+}}^3(t) &= \left[ Ca^{2+}_{\rm spike} \sum_{i} \mathrm{\theta} \left( t-t^i_{\rm spike} \right) \mathrm{exp} \left( - \left( t-t^i_{\rm spike} \right) /\tau_{Ca^{2+}} \right) \right]^3 \\
+&\approx {Ca_{\rm spike}^{2+}}^3 \sum_{i} \mathrm{\theta} \left( t-t^i_{\rm spike} \right) \mathrm{exp} \left( -3 \left( t-t^i_{\rm spike} \right) /\tau_{Ca^{2+}} \right) 
 \end{split} \label{cubic_approx_1}			
 \end{equation}
-with $\theta(x)$ being the Heaviside step function. By the same argument
-\begin{equation}
-\frac{{Ca^{2+}}^3(t)}{{Ca^{2+}}^3(t)+1} \approx \sum_{i} \theta(t-t^i_{spike}) \frac{exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}})}{exp(-3(t-t^i_{spike})/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}} \; .
+with $\mathrm{\theta}(x)$ being the Heaviside step function. By the same argument
+\begin{equation}
+\frac{{Ca^{2+}}^3(t)}{{Ca^{2+}}^3(t)+1} \approx \sum_{i} \mathrm{\theta} \left( t-t^i_{\rm spike} \right) \frac{ \mathrm{exp} \left( -3 \left( t-t^i_{\rm spike} \right) /\tau_{Ca^{2+}} \right) }{\mathrm{exp} \left( -3 \left( t-t^i_{spike} \right) /\tau_{Ca^{2+}} \right) + \frac{1}{{Ca_{\rm spike}^{2+}}^3}} \; .
 \end{equation}
 Therefore, the resulting rate of NO synthesis can be decomposed into a sum of time shifted responses onto a single kernel of calcium concentration as a result of a spike.
-For a spike at $t_{spike}=0$, the solution of \eqref{nNOS_dyn} can be calculated by
+For a spike at $t_{\rm spike}=0$, the solution of \eqref{nNOS_dyn} can be calculated by
 \begin{equation}
 \begin{split}
-nNOS(t) &= \frac{1}{\tau_{nNOS}}\int_{-\infty}^t dt' exp(-(t-t')/\tau_{nNOS})\cdot \theta(t') \frac{exp(-3t'/\tau_{Ca^{2+}})}{exp(-3t'/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}} \\
-&= \frac{1}{\tau_{nNOS}}\int_{0}^t dt' exp(-(t-t')/\tau_{nNOS})\cdot \frac{exp(-3t'/\tau_{Ca^{2+}})}{exp(-3t'/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}}\;.
+nNOS(t) &= \frac{1}{\tau_{nNOS}}\int_{-\infty}^t dt' \mathrm{exp} \left( - \left( t-t' \right) /\tau_{nNOS} \right)  \mathrm{\theta} (t') \frac{\mathrm{exp} \left( -3t'/\tau_{Ca^{2+}} \right) }{\mathrm{exp} \left( -3t'/\tau_{Ca^{2+}} \right) + \frac{1}{{Ca^{2+}_{\rm spike}}^3}} \\
+&= \frac{1}{\tau_{nNOS}}\int_{0}^t dt' \mathrm{exp} \left( - \left( t-t' \right) /\tau_{nNOS} \right)  \frac{\mathrm{exp} \left( -3t'/\tau_{Ca^{2+}} \right) }{\mathrm{exp} \left( -3t'/\tau_{Ca^{2+}} \right) + \frac{1}{{Ca^{2+}_{\rm spike}}^3}}\;.
 \end{split}\label{nNOS_single_sol}
@@
 \begin{equation}
-nNOS(t) = \frac{1}{\tau_{nNOS}} \theta(t) exp(-t/\tau_{nNOS}) \int_{0}^\infty dt' \frac{exp(-3t'/\tau_{Ca^{2+}})}{exp(-3t'/\tau_{Ca^{2+}}) + \frac{1}{{Ca^{2+}_{spike}}^3}}\;.
+nNOS(t) = \frac{1}{\tau_{nNOS}} \mathrm{\theta}(t) \mathrm{exp} \left( -t/\tau_{nNOS} \right) \int_{0}^\infty dt' \frac{\mathrm{exp} \left( -3t'/\tau_{Ca^{2+}} \right) }{\mathrm{exp} \left( -3t'/\tau_{Ca^{2+}} \right) + \frac{1}{{Ca^{2+}_{\rm spike}}^3}}\;.
 \label{nNOS_single_sol_approx1}
@@
 \begin{equation}
-nNOS(t) = \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3\tau_{nNOS}} \sum_i \theta(t-t^i_{spike}) \exp(-(t-t^i_{spike})/\tau_{nNOS})\;.
+nNOS(t) = \frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2) }{3\tau_{nNOS}} \sum_i \mathrm{\theta} \left( t-t^i_{\rm spike} \right) \mathrm{exp} \left( - \left( t-t^i_{\rm spike} \right) /\tau_{nNOS} \right) \;.
 \label{nNOS_single_sol_approx2}
@@
 The simplified model fits very well for sufficiently isolated spike events, as predicted.
-One can observe a slightly smaller but acceptable agreement for the rare event of two subsequent spikes appearing very close to each other, as seen in Figure \ref{nNOS_approx_plot} at approximately 4 seconds.
+One can observe a slightly worse but acceptable agreement for the rare event of two subsequent spikes appearing very close to each other, as seen in Figure \ref{nNOS_approx_plot} at approximately $\rm 1.5\, s$.
 \begin{figure}
@@
 The full simulation (blue, see equations \eqref{Ca_dyn},\eqref{nNOS_dyn}) is well fitted by the simplified model (red, see equation \eqref{nNOS_single_sol_approx2}).
-Top axis is a closeup of the first spike event.}
+Top panel is a closeup of the first spike event.
+Dashed lines mark the time span shown in the closeup.}
 \label{nNOS_approx_plot}
@@
 
-Returning to the question of how to describe NO synthesis in a simplified form, we note that according to equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$, which makes the mean rate of NO production over time simply $<nNOS> = <r> \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
-However, it is not sufficient to simply propose $nNOS_i(t) = r_i(t) \cdot \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$.
-A single cell fires in the range of $\mathrm{3\,Hz}$, which is---at least on the time scale of the observed oscillations---not enough to assign an instantaneous firing rate.
+Returning to the question of how to describe NO synthesis in a simplified form, we note that according to equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}}\mathrm{ln}(2)}{3}$, which makes the mean rate of NO production over time simply $\langle nNOS \rangle = \langle r \rangle \frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3}$.
+However, it is not sufficient to simply propose $nNOS_i(t) = r_i(t) \frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3}$.
+A single cell fires in the range of $\mathrm{3\,Hz}$.
+Therefore, the dynamics of $\rm nNOS$ are dominated by single spike events as shown in Figure \ref{nNOS_approx_plot} and it is---at least on the time scale of the observed oscillations---not a proper approximation to describe $\rm nNOS$ in this smooth, rate-based fashion.
 \newpage
 We introduced an idealized picture of diffusive homeostasis to deal with this, where diffusion across the tissue is instantaneous.
-This simplification results in a single level of NO-concentration for all neurons, only being modified over time by the sum of all neurons' NO-syntheses $nNOS_{total}(t) \equiv \sum_{i} nNOS^i(t)$ and the decay term $-\lambda NO$.
-, $nNOS_{total}$ must be divided by the area $L^2$ of the tissue to account for the spread of NO.
+This simplification results in a single level of NO-concentration for all neurons, only being modified over time by the sum of all neurons' NO-syntheses $nNOS_{\rm total}(t) \equiv \sum_{i} nNOS_i(t)$ and the decay term $-\lambda NO$.
+$nNOS_{\rm total}$ must be divided by the area $L^2$ of the tissue to account for the spread of NO.
 Furthermore, we introduce a random fluctuation term $\sigma_{NO} \xi(t)$ that accounts for local, momentary deviations from the mean.
@@
 \begin{equation}
-\dot{NO}(t)=-\lambda NO + \frac{nNOS_{total}(t)}{L^2} + \sigma_{NO} \xi(t)\;.
+\dot{NO}(t)=-\lambda NO + \frac{nNOS_{\rm total}(t)}{L^2} + \sigma_{NO} \xi(t)\;.
 \label{NO_dyn_approx}
@@
 This led to an underestimation of the total energy within the power spectrum in the final result.
-However, noise level only acts as a global scaling factor of the shape of the power spectrum as long as we assume the noise in the system to be approximately white and was thus left open as a model fitting parameter.
-
-It is clear from Equation \eqref{NO_dyn_approx} why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $3 Hz \cdot N_{exc.} = \mathrm{1200\,Hz}$, given the assumption that cells are spiking weakly correlated.
-We furthermore argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{total} = N_{exc.}\cdot r_{exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
+However, the noise level only acts as a global scaling factor of the shape of the power spectrum as long as we assume the noise in the system to be approximately white and was thus left open as a model fitting parameter.
+
+It is clear from Equation \eqref{NO_dyn_approx} why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $3 Hz \cdot N_{\rm exc.} = \mathrm{1200\,Hz}$, given the assumption that cells' spiking is approximately independent.
+We furthermore argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{\rm total} = N_{\rm exc.} r_{\rm exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
 We thus propose
 \begin{equation}
-nNOS_{total}(t) = r_{exc.pop.}\cdot N_{exc.}\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}
+nNOS_{\rm total}(t) = r_{\rm exc.pop.} N_{\rm exc.}\frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3}
 \label{nNOS_total_dyn}
 \end{equation} 
-where $\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}$ is the integral from Equation \eqref{nNOS_single_sol_approx1}.
+where $\frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3}$ is the integral from Equation \eqref{nNOS_single_sol_approx1}.
 
 We wanted to simplify the dynamics of threshold adaption and its effect on the population rate as a next step.
-Corresponding to the reduction to a single variable $r_{exc.pop.}(t)$ for the mean excitatory activity in equation \eqref{nNOS_total_dyn}, we wanted to find an appropriate description containing only the mean threshold $V_{t,pop.}(t) = <V_t(t)>$.
+Corresponding to the reduction to a single variable $r_{\rm exc.pop.}(t)$ for the mean excitatory activity in equation \eqref{nNOS_total_dyn}, we wanted to find an appropriate description containing only the mean threshold $V_{t,\rm pop.}(t) = \langle V_t(t) \rangle$.
 As stated earlier, Figure \ref{rate_th_close} suggests an immediate and approximately linear relation between excitatory population rate and the mean of thresholds within the excitatory population.
 Figure \ref{thresh_r_linfit} shows a linear fit (being of the form $\alpha x + \beta$) of these two quantities plotted against each other.
-We found a good fit to the linear model apart from rarely appearing high values of $V_{t,pop.}$.
-We thus expressed the population rate by $r_{exc.pop.}(t) = r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0})$, where $r_{IP}$ is given in table \ref{Params_IP} as the mean excitatory target firing rate and $V_{t,0} \equiv (r_{IP}-\beta)/\alpha$ is the mean threshold corresponding to the target rate.
+We found a good fit to the linear model apart from rarely appearing high values of $V_{t,\rm pop.}$.
+We thus expressed the population rate by $r_{\rm exc.pop.}(t) = r_{IP} + \alpha(V_{t,\rm pop.}(t)-V_{t,0})$, where $r_{IP}$ is given in Table \ref{Params_IP} as the mean excitatory target firing rate and $V_{t,0} \equiv (r_{IP}-\beta)/\alpha$ is the mean threshold corresponding to the target rate.
 \begin{figure}
@@
 \caption{Linear fit of excitatory population activity and mean excitatory threshold.
-Slope $\alpha$ of the fit: $\mathrm{-0.789\, Hz/mV}$.
+Slope $\alpha$ of the fit: $\mathrm{-0.79\, Hz/mV}$.
 Offset $\beta$: $\mathrm{-41.97\, Hz}$.
@@
 \begin{align}
-\dot{NO}(t) &= -\lambda NO + \frac{(r_{IP} + \alpha(V_{t,pop.}(t)-V_{t,0}))\cdot N_{exc.}\frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3}}{L^2} + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis1}\\
-\dot{V_{t,pop.}}(t) &= \frac{NO-NO_0}{NO_0 \tau_{V_t}}\;. \label{2d-sys-homeostasis2}
+\dot{NO}(t) &= -\lambda NO + \frac{ \left( r_{IP} + \alpha \left( V_{t,\rm pop.}(t)-V_{t,0} \right) \right)  N_{\rm exc.}\frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3}}{L^2} + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis1}\\
+\dot{V}_{t,\rm pop.}(t) &= \frac{NO-NO_0}{NO_0 \tau_{V_t}}\;. \label{2d-sys-homeostasis2}
 \end{align}
@@
 n &\equiv NO-NO_0 \label{simplif_coord_transf1}\\
-\theta &\equiv V_{t,pop.}(t)-V_{t,0} \label{simplif_coord_transf2}\\
+\theta &\equiv V_{t,\rm pop.}(t)-V_{t,0} \label{simplif_coord_transf2}\\
 \end{align}
@@
 \begin{align}
-\dot{n} &= -\lambda n + \frac{\gamma \alpha N_{exc.}}{L^2}\theta + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis-coord_transf1}\\
+\dot{n} &= -\lambda n + \frac{\gamma \alpha N_{\rm exc.}}{L^2}\theta + \sigma_{NO} \xi(t) \label{2d-sys-homeostasis-coord_transf1}\\
 \dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{2d-sys-homeostasis-coord_transf2}
@@
 \begin{align}
-\gamma &\equiv \frac{{Ca^{2+}_{spike}}^3 \tau_{Ca^{2+}}ln(2)}{3} \label{2d-sys-fixed-points1}\\
-NO_0 &= \frac{nNOS_{total,0}}{\lambda L^2} \label{2d-sys-fixed-points2}\\
-nNOS_{total,0} &= r_{IP}\cdot N_{exc.} \cdot \gamma \; . \label{2d-sys-fixed-points3}
+\gamma &\equiv \frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3} \label{2d-sys-fixed-points1}\\
+NO_0 &= \frac{nNOS_{\mathrm{ total},0}}{\lambda L^2} \label{2d-sys-fixed-points2}\\
+nNOS_{\mathrm{ total},0} &= r_{IP} N_{\rm exc.} \cdot \gamma \; . \label{2d-sys-fixed-points3}
 \end{align}
@@
 \begin{align}
-i\omega f_n &= - \lambda f_n + \frac{\gamma \alpha N_{exc.}}{L^2}f_\theta + \sigma_{NO} f_{\xi} \label{2d-sys-homeostasis-coord_transf_ft1}\\
+i\omega f_n &= - \lambda f_n + \frac{\gamma \alpha N_{\rm exc.}}{L^2}f_\theta + \sigma_{NO} f_{\xi} \label{2d-sys-homeostasis-coord_transf_ft1}\\
 i\omega f_\theta &= \frac{f_n}{NO_0\tau_{V_t}} \label{2d-sys-homeostasis-coord_transf_ft2} \\
@@
 \begin{equation}
-P_\theta (\omega) = \frac{\sigma_{NO}^2}{\omega^2 NO_0^2 \tau_{V_t}^2 \lambda^2 + \left( \omega^2 NO_0 \tau_{V_t} + \frac{\gamma \alpha N_{exc.}}{L^2}\right)^2} \label{Pow_Spec_Theta_Final}
+P_\theta (\omega) = \frac{\sigma_{NO}^2}{\omega^2 NO_0^2 \tau_{V_t}^2 \lambda^2 + \left( \omega^2 NO_0 \tau_{V_t} + \frac{\gamma \alpha N_{\rm exc.}}{L^2}\right)^2} \label{Pow_Spec_Theta_Final}
 \end{equation}
@@
 Our approximation underestimated the amount of damping within the system (which controls the ``peakiness" of the spectrum), as well as predicting a slightly smaller preferred amplitude.
-The preferred amplitude is controlled by $\frac{\gamma \alpha N_{exc.}}{L^2}$ and $\frac{1}{NO_0\tau_{V_t}}$ while the broadness of the spectrum is mostly controlled by the damping term $-\lambda$.
+The preferred amplitude is controlled by $\frac{\gamma \alpha N_{\rm exc.}}{L^2}$ and $\frac{1}{NO_0\tau_{V_t}}$ while the broadness of the spectrum is mostly controlled by the damping term $-\lambda$.
 Since the latter term was taken unaltered from the original system (apart from a shift in phase space), we added $-\lambda$ and $\alpha$ as free fitting parameters and managed to get a very good fit to the simulation data, see Figure \ref{Pow_Spec_Theta_vs_Analytic}.
@@
 \caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final}.
-Red curve was fitted by tweaking only the overall amplitude $\mathrm{\sigma_{NO}}$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\alpha = -0.789 \,Hz/mV}$, as in Figure \ref{thresh_r_linfit}).
-Green curve is a fit achieved by adjusting $\mathrm{\sigma_{NO}}$ and $\mathrm{\lambda}$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\lambda = 0.845 \,s^{-1}}$).
-Black curve was fitted by means of $\mathrm{\sigma_{NO}}$, $\mathrm{\lambda}$ and $\mathrm{\alpha}$ ($\mathrm{\lambda = 0.592 \,s^{-1}}$, $\mathrm{\alpha=-0.989 \,Hz/mV}$).}
+Red curve was fitted by varying only the overall amplitude $\mathrm{\sigma_{NO}}$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\alpha = -0.79 \,Hz/mV}$, as in Figure \ref{thresh_r_linfit}).
+Green curve is a fit achieved by adjusting $\mathrm{\sigma_{NO}}$ and $\mathrm{\lambda}$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\lambda = 0.85 \,s^{-1}}$).
+Black curve was fitted by means of $\mathrm{\sigma_{NO}}$, $\mathrm{\lambda}$ and $\mathrm{\alpha}$ ($\mathrm{\lambda = 0.59 \,s^{-1}}$, $\mathrm{\alpha=-0.99 \,Hz/mV}$).}
 \label{Pow_Spec_Theta_vs_Analytic}
@@
 This leads to a stronger local increase of concentration, which eventually leads to faster oscillations.
-In either case, both parameters have the same effect onto the shape of the power spectrum since these parameters appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}.
+In either case, both parameters have the same effect on the shape of the power spectrum since these parameters appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}.
 
@@
 We plotted the the distribution of decadic logarithms of firing rates in Figure \ref{Fir_Rate_Dist_Compare} (B) to check for this property.
-In (A), we found a skewness of $\mathrm{v_{Diff} = 0.765}$, in (B) $\mathrm{v_{Diff,log} = -0.488}$.
+In (A), we found a skewness of $\mathrm{v_{\rm diff.} = 0.77}$, in (B) $\mathrm{v_{\rm diff.,log} = -0.49}$.
 Though this told us that the distribution is ``more symmetric" on a logarithmic scale, it should rather be seen as being neither strictly normally or log-normally distributed.
@@
 For diffusive homeostasis ($\mathrm{D=10\, \mu m^2 ms^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
-Mean firing rates were calculated from spikes within $\mathrm{t=1000-1500\,s}$.}
+Mean firing rates were calculated from spikes within $\mathrm{1000-1500\,s}$.}
 \label{Fir_Rate_Dist_Compare}
 \end{figure}
-In contrast, inhibitory cells showed a much clearer distinction: A skewness of $\mathrm{v_{Diff} = 1.522}$ in regular space and $\mathrm{v_{Diff,log} = -0.147}$ in log-space.
+In contrast, inhibitory cells showed a much clearer distinction: A skewness of $\mathrm{v_{\rm diff.} = 1.52}$ in regular space and $\mathrm{v_{\rm diff.,log} = -0.15}$ in log-space.
 
@@
 (A) was taken from $\mathrm{1000-1500\,s}$, which is well inside the phase of diffusive homeostasis.
-As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous Poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{mean}\cdot n_{bins}/T_{total}}$, though slight deviations can be seen as a different factor of proportionality.
+As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous Poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{\rm mean} n_{\rm bins}/T_{\rm total}}$, though slight deviations can be seen as a different factor of proportionality.
 (B) acts as an illustration showing a counterexample: Here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis.
@@
 Figure \ref{Fir_Rate_Dist_Instant_compare} shows the distribution for this special limiting case.
-The standard deviation for the excitatory population was $\mathrm{\sigma_{inst} = 1.79\, Hz}$ and the skewness $\mathrm{v_{inst} = 1.51}$ ($\mathrm{v_{inst,log} = -0.52}$), which makes the asymmetry slightly more pronounced than in Figure \ref{Fir_Rate_Dist_Compare}.
+The standard deviation for the excitatory population was $\mathrm{\sigma_{\rm inst.} = 1.79\, Hz}$ and the skewness $\mathrm{v_{\rm inst.} = 1.51}$ ($\mathrm{v_{\rm inst.,log} = -0.52}$), which makes the asymmetry slightly more pronounced than in Figure \ref{Fir_Rate_Dist_Compare}.
 \begin{figure}
@@
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/instant_diff_fir_dist_i.png}
-\caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population. Data was taken from 10 simulations and $\mathrm{t=1000-1500\,s}$.}
+\caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population. Data was taken from 10 simulations and $\mathrm{1000-1500\,s}$.}
 \label{Fir_Rate_Dist_Instant_compare}
@@
 \caption{Distribution of decadic logarithm of excitatory synaptic weights at $\mathrm{t=1500\,s}$ for diffusive and non-diffusive homeostasis (both with distance-dependent connectivity).
-Gaussian fits returned $\mathrm{\mu_{diff}=-0.172\, log_{10}(mV)}$, $\mathrm{\mu_{non-diff}=-0.087\, log_{10}(mV)}$, $\mathrm{\sigma_{diff}=0.643\, log_{10}(mV)}$ and $\mathrm{\sigma_{non-diff}=0.418\, log_{10}(mV)}$.}
+Gaussian fits returned $\mathrm{\mu_{\rm diff.}=-0.17\, \mathrm{log}_{10}(mV)}$, $\mathrm{\mu_{\rm non-diff.}=-0.087\, \mathrm{log}_{10}(mV)}$, $\mathrm{\sigma_{\rm diff.}=0.64\, log_{10}(mV)}$ and $\mathrm{\sigma_{non-diff.}=0.42\, log_{10}(mV)}$.}
 \label{Weight_Dist}
@@
 \caption{Distribution of recurrent excitatory synaptic lifetimes.
-Linear fits ignoring falloff for large synaptic lifetimes resulted in a slope of $\mathrm{-1.871}$ for diffusive homeostasis and $\mathrm{-1.676}$ for non-diffusive homeostasis.}
+Linear fits ignoring falloff for large synaptic lifetimes resulted in a slope of $\mathrm{-1.87}$ for diffusive homeostasis and $\mathrm{-1.68}$ for non-diffusive homeostasis.}
 \label{Syn_Lifetimes}
@@
 \begin{equation}
-p(t,w_0,w_{prune}) = \frac{|w_0-w_{prune}|}{\sqrt{2\pi \sigma t^3}}exp \left( \frac{(w_0-w_{prune})^2}{2\sigma t}\right)
+p(t,w_0,w_{\rm prune}) = \frac{ | w_0-w_{\rm prune}|}{\sqrt{2\pi \sigma t^3}} \mathrm{exp} \left( \frac{ \left( w_0-w_{\rm prune} \right) ^2}{2\sigma t}\right)
 \label{Levy_Dist}
@@
 Dashed lines are means obtained by randomly shuffling synaptic weights.
-Data was taken from 25 weight matrices per line, representing weights within $\mathrm{t=1000-1500\,s}$.}
+Data was taken from 25 weight matrices per line, representing weights within $\mathrm{1000-1500\,s}$.}
 \label{Out_Weight_Mean_Quantile}
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_weights_vs_rate.png}
-\caption{Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{t=700-1000\,s}$) in regular (A) and logarithmic space (B).
+\caption{Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{700-1000\,s}$) in regular (A) and logarithmic space (B).
 Each plot corresponds to a presynaptic excitatory cell.}
@@
 \begin{align}
-\phi_i(\mu_i,\sigma_i,V_{t,i}) &= \left[ \sqrt{\pi}\tau_m \int_{x_-}^{x_+} dx e^{x^2} erfc(-x) \right]^{-1} \label{LIF_Fir_Rate_with_Noise1_copy}\\
+\phi_i(\mu_i,\sigma_i,V_{t,i}) &= \left[ \sqrt{\pi}\tau_m \int_{x_-}^{x_+} dx e^{x^2} \mathrm{erfc}(-x) \right]^{-1} \label{LIF_Fir_Rate_with_Noise1_copy}\\
 x_- &= (V_r-E_l-\mu_i\tau_m)/\sigma_i \label{LIF_Fir_Rate_with_Noise2_copy}\\
@@
 We tested this dynamic mean-field model by simulating a similar population, but used an interacting population of neurons of the same size as in the previous simulations (400 excitatory, 80 inhibitory neurons).
-This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $\mathrm{1500 \, s}$ (i.E., the stable phase).
+This allowed us to directly use a weight matrix acquired by means of a simulation of the full plastic network, taken from the network after $\mathrm{1500 \, s}$ (i.e., the stable phase).
 Individual values for $\mu_i$ and $\sigma_i$ were then calculated according to \eqref{sweeney_self_consist_rate2} and \eqref{sweeney_self_consist_rate3}.
@@
 \begin{equation}
-\nu_i = {\langle r \rangle}_{presyn.,i} \equiv \frac{\sum_{\exists syn. j\rightarrow i} r_j}{N_{presyn., i}}
+\nu_i = {\langle r \rangle}_{\mathrm{ presyn.},i} \equiv \frac{\sum_{\mathrm{ \exists syn.} j\rightarrow i} r_j}{N_{\mathrm{ presyn.}, i}}
 \label{sweeney_self_consist_rate1_mod}
@@
 \begin{equation}
-x_{0}\cdot u_{0} = \frac{1+r_{total,i} \tau_f}{1/U + r_{total,i} (\tau_d + \tau_f)+ r_{total,i}^2 \tau_d \tau_f}
+x_{0}\cdot u_{0} = \frac{1+r_{\mathrm{ total},i} \tau_f}{1/U + r_{\mathrm{ total},i} (\tau_d + \tau_f)+ r_{\mathrm{ total},i}^2 \tau_d \tau_f}
 \label{STP_steady}
 \end{equation}
-where $\mathrm{r_{total,i}}$ is the rate of all combined spikes arriving at neuron i.
+where $\mathrm{r_{\mathrm{ total},i}}$ is the rate of all combined spikes arriving at neuron i.
 
@@
 \begin{align}
-\phi(\mu_i(\nu),\sigma_i(\nu),V_{t,i}) &= \phi_0 \label{fixed_thresh_dist_argument1} \\
+\phi \left( \mu_i(\nu),\sigma_i \left( \nu \right) ,V_{t,i} \right) &= \phi_0 \label{fixed_thresh_dist_argument1} \\
 \mu_i &= J_iC_i \phi_0 \tau \label{fixed_thresh_dist_argument2} \\
 \sigma_i &= J_i\sqrt{C_i \phi_0  \tau} \label{fixed_thresh_dist_argument3} \\
-\rightarrow V_{t,i} &= {\phi}^{-1}(J_iC_i \phi_0 \tau,J_i\sqrt{C_i \phi_0  \tau},\phi_0) \label{fixed_thresh_dist_argument4}
+\rightarrow V_{t,i} &= {\phi}^{-1} \left( J_iC_i \phi_0 \tau,J_i\sqrt{C_i \phi_0  \tau},\phi_0 \right) \label{fixed_thresh_dist_argument4}
 \end{align}
@@
 We did so by recalling that Equation \eqref{NO_dyn} describes the full dynamics of the diffusive neurotransmitter.
-Furthermore, equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma \cdot r_i}$, $\mathrm{r_i}$ representing a neuron's rate and $\mathrm{\gamma}$ being defined by Equation \eqref{2d-sys-fixed-points1}.
+Furthermore, equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma  r_i}$, $r_i$ representing a neuron's rate and $\gamma$ being defined by Equation \eqref{2d-sys-fixed-points1}.
 In this section we discuss the implications of an in-between description, only applying the second simplification, but retaining the diffusive term:
 \begin{equation}
-\frac{dNO}{dt}(\mathbf{x},t) =-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot \gamma \cdot r_i
+\frac{dNO}{dt}(\mathbf{x},t) =-\lambda NO + D \nabla^2 NO + \sum_{i} \delta^2 \left( \mathbf{x}-\mathbf{x}_{\mathrm{ neur.},i} \right) \gamma r_i
 \label{simple_NO_dyn_with_diff}
@@
 \begin{equation}
-(\lambda - D \nabla^2) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot \gamma \cdot r_i
+\left( \lambda - D \nabla^2 \right) NO = \sum_{i} \delta^2 \left( \mathbf{x}-\mathbf{x}_{\mathrm{ neur.},i} \right) \gamma  r_i
 \label{simple_NO_dyn_with_diff_equil}
@@
 \begin{equation}
-NO(\mathbf{x}_{neur,i}) = NO_0 \:, \: \forall i \; .
+NO(\mathbf{x}_{\mathrm{ neur.},i}) = NO_0 \:, \: \forall i \; .
 \label{NO_equil_cond}
@@
 \begin{equation}
-\left(\nabla^2 + \left( i\sqrt{\frac{\lambda}{D}}\right)^2\right) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{neur,i})\cdot \frac{- \gamma \cdot r_i}{D}
+\left( \nabla^2 + \left( i\sqrt{\frac{\lambda}{D}}\right)^2\right) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{\mathrm{ neur.},i})\cdot \frac{- \gamma \cdot r_i}{D}
 \label{simple_NO_dyn_with_diff_equil_helmholtz}
@@
 which is a two-dimensional Helmholtz equation with a superposition of rescaled Dirac functions.
-The solution of $\mathrm{NO}$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of the equation.
+The solution of $NO$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of the equation.
 For each delta function $\delta^2(\mathbf{x}-\mathbf{x}_i)$, the solution is
 \begin{equation}
-NO_i(\mathbf{x}) = \frac{r_i \gamma}{2 \pi D} K_0 \left(|\mathbf{x}-\mathbf{x}_{neur,i}|\sqrt{\frac{\lambda}{D}} \right) \equiv r_i \cdot \psi_{point}(|\mathbf{x}-\mathbf{x}_{neur,i}|)
+NO_i(\mathbf{x}) = \frac{r_i \gamma}{2 \pi D} K_0 \left(|\mathbf{x}-\mathbf{x}_{\mathrm{ neur.},i}|\sqrt{\frac{\lambda}{D}} \right) \equiv r_i \psi_{\rm point}(|\mathbf{x}-\mathbf{x}_{\mathrm{ neur.},i}|)
 \label{solution_diff_equil_bessel}
@@
 \begin{equation}
-NO_i(\mathbf{x}) = r_i \cdot \psi (|\mathbf{x}_{neur,i}-\mathbf{x}|) \; . \label{general_diff_interaction}
+NO_i(\mathbf{x}) = r_i \psi (|\mathbf{x}_{\mathrm{ neur.},i}-\mathbf{x}|) \; . \label{general_diff_interaction}
 \end{equation}
@@
 \begin{equation}
-\psi_{ij} \equiv \psi_{ij} \equiv \psi (|\mathbf{x}_{neur,i}-\mathbf{x}_{neur,i}|)
+\psi_{ij} \equiv \psi_{ji} \equiv \psi (|\mathbf{x}_{\mathrm{ neur.},i}-\mathbf{x}_{\mathrm{ neur.},i}|)
 \label{interact_matrix_elements}
@@
 \begin{equation}
-\sum_j \psi_{ij}\cdot r_j = NO_0
+\sum_j \psi_{ij} r_j = NO_0
 \label{NO_equil_cond_interact_matrix}
@@
 \end{equation}
-Still, we had to find a modified, non-diverging version of $\mathrm{\psi (|\mathbf{x}_{neur,i}-\mathbf{x}|)}$ to acquire any prediction from this model.
+Still, we had to find a modified, non-diverging version of $\mathrm{\psi (|\mathbf{x}_{\mathrm{ neur.},i}-\mathbf{x}|)}$ to acquire any prediction from this model.
 It had to retain the shape given by \eqref{solution_diff_equil_bessel} for larger distances but approach the correct numeric error value at the origin, determined by the spacing of the numeric grid.
@@
 \begin{equation}
-\psi_{approx.} \equiv \frac{1}{\left(\frac{1}{\psi_0^\varepsilon} + \frac{1}{\psi_{point}^\varepsilon}\right)^{\frac{1}{\varepsilon}}}
+\psi_{\rm approx.} \equiv \frac{1}{\left(\frac{1}{\psi_0^\varepsilon} + \frac{1}{\psi_{\rm point}^\varepsilon}\right)^{\frac{1}{\varepsilon}}}
 \label{Numeric_Solution_Expression_Trick}
 \end{equation}
-where $\mathrm{\varepsilon}$ determines the ``smoothness" of transition between $\mathrm{\psi}$ and the cutoff value $\mathrm{\psi_0}$.
-We chose $\mathrm{\varepsilon=10}$ for all further calculations.
+where $\varepsilon$ determines the ``smoothness" of transition between $\psi$ and the cutoff value $\psi_0$.
+We chose $\varepsilon=10$ for all further calculations.
 We took the simple approach of interpreting this value as a mean of the analytic solution across the area covered by the corresponding grid cell to find an expression for $\mathrm{\psi_0}$.
@@
 \end{equation}
-where $\mathrm{h}$ is the spatial resolution of the grid cells.
+where $h$ is the spatial resolution of the grid cells.
 Figure \ref{Psi_Approximation_Compare} shows a comparison between the numerically calculated solution and the expression given by \ref{Numeric_Solution_Expression_Trick}.
@@
 \end{center}
-\caption{Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz} (blue, $\mathrm{h=10\;\mu m}$) and its approximation (dashed) given by \eqref{Numeric_Solution_Expression_Trick}.
+\caption{Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz} (blue, $h=10\;\mu m$) and its approximation (dashed) given by \eqref{Numeric_Solution_Expression_Trick}.
 The numerical simulation was carried out on a two-dimensional grid and the curve represents a cut through the origin in x-direction.}
@@
 \end{figure}
-We took this approximation as a basis for further calculations of the interaction matrix $\mathrm{\hat{\psi}}$.
+We took this approximation as a basis for further calculations of the interaction matrix $\hat{\psi}$.
 
@@
 \end{figure}
-Therefore, the entries of the operator for periodic boundary conditions $\hat{\psi}_{per.}$ could be calculated by
-\begin{equation}
-\psi_{ij,per.} = \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} (|\mathbf{x}_{neur,i}-\mathbf{x}_{neur,i} - L \cdot (n_x,n_y)|) \; .
+Therefore, the entries of the operator for periodic boundary conditions $\hat{\psi}_{\rm per.}$ could be calculated by
+\begin{equation}
+\psi_{ij,\rm per.} = \sum_{n_x,n_y \in \mathbb{Z}} \psi_{\rm approx.} (|\mathbf{x}_{\mathrm{ neur.},i}-\mathbf{x}_{\mathrm{ neur.},i} - L \cdot (n_x,n_y)|) \; .
 \label{Psi_entries_periodic_bound}
@@
 \begin{align}
-\psi_{ij,neum.} &= \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} \left(|\mathbf{x}_{neur,i}-M(\mathbf{x}_{neur,i}) - L \cdot (n_x,n_y)| \right) \label{Psi_entries_neumann_bound} \\
+\psi_{ij,\rm neum.} &= \sum_{n_x,n_y \in \mathbb{Z}} \psi_{\rm approx.} \left(|\mathbf{x}_{\mathrm{ neur.},i}-M(\mathbf{x}_{\mathrm{neur.},i}) - L \cdot (n_x,n_y)| \right) \label{Psi_entries_neumann_bound} \\
 M(\mathbf{x}) &\equiv  

### 2017-03-02 draft.tex
.

@@
 A smoothing window of $\mathrm{[-5,5]}$ data points around the maximum was used to reduce overestimation of the maximum due to random fluctuations.
-Blue line corresponds to Equation \eqref{Pow_Spec_Theta_Final}, fit values taken from black curve in Figure \ref{Pow_Spec_Theta_vs_Analytic}.
-B: Position of the peak on the frequency axis.
-Analytic prediction was acquired according to (A).}
+Fit values for analytic prediction were taken from black curve in Figure \ref{Pow_Spec_Theta_vs_Analytic}.
+B: Position of the peak on the frequency axis.}
 \label{Peak_Prop_vs_Theta}
 \end{figure} 
-We eventually settled at a 1000-fold increased time constant to reduce oscillations as much as possible,  $\mathrm{\tau_{V_t}=2500\,s}$.
+We eventually settled at a $\rm 1000$-fold increased time constant to reduce oscillations as much as possible,  $\mathrm{\tau_{V_t}=2500\,s}$.
 Homeostasis still managed to keep excitatory network activity in the desired range, as shown in Figure \ref{full_sim_osci_slow_tau_th}, even given the slowness of threshold adaptation.
@@
 Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behavior under sparse connectivity with a relatively high per-synapse connection strength \cite{Vreeswijk1996,Brunel2000}.
-This kind of asynchronous regular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity.
+This kind of asynchronous irregular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity.
 This regularity was shown to be achievable in the previous section after slowing down the rate of homeostatic adaption.
@@
 Only neurons with a mean firing rate in a certain range (see legend) were included into statistics to prevent overlap of different firing rates (except for non-diffusive homeostasis and excitatory neurons, all being very close to 3 Hz).
-Black lines are fits of exponential functions.
 B/D: Distribution of coefficients of variation.
@@
 \end{figure}
-Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficients of variation ($\mathrm{CV\equiv\sigma/\mu}$) taken over the set of excitatory and inhibitory neurons, respectively.
+Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficients of variation ($\mathrm{CV\equiv\sigma/\mu}$) taken over the set of excitatory and inhibitory neurons.
 However, we restricted the statistics of ISIs to neurons whose mean firing rate fall into a window with a width of 1 Hz and a certain mean in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case (see legend in Figure \ref{ISI_CV_compare}).
@@
 This observation is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons have an  under-representation of short ISIs, the opposite is the case for inhibitory neurons.
-These types of behavior of LIF-models have been shown to depend on the CV of input the neuron receives: A smaller signal-to-noise ratio (larger CV) of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals \cite{Ostojic2011}.
-This relation fits nicely into our set of network parameters: Inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
+These types of behavior of LIF-models have been shown to depend on the amount of fluctuations of the input the neuron receives: A larger CV of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals \cite{Ostojic2011}.
+By the CV of the input we mean the ratio between standard deviation and mean of postsynaptic current due to presynaptic spiking events (under the assumption of a stationary mean and variance).
+This relation between fluctuating input and spiking statistics fits nicely into our set of network parameters: Inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
 This lowers the signal-to-noise ratio for the inputs of inhibitory neurons, leading to the aforementioned statistical differences.
@@
 
-We looked at potential correlations across neurons within both populations as an additional possibility of spike-train analysis.
+We also considered potential correlations across neurons within both populations as an additional possibility of spike-train analysis.
 To do so, we calculated cross-correlations for all possible neuron pairings within a population, excluding auto-correlations.
@@
 This question is not only of relevance with respect to the ``stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of momentary rates.
-A constant rate of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous Poisson process of the same total mean firing rate.
+A constant rate of an approximately randomly spiking neuron means that the dependence of fluctuations of rates on the width of the averaging window should be identical to a homogeneous Poisson process of the same total mean firing rate.
 As bin sizes increase, possible long-term fluctuations of firing rates can then be identified as deviations from the variance one would expect from a homogeneous process.
@@
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/instant_diff_fir_dist_i.png}
-\caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population. Data was taken from 10 simulations and $\mathrm{1000-1500\,s}$.}
+\caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population.
+Data was taken from 10 simulations and $\mathrm{1000\,s \leq t \leq 1500\,s}$.}
 \label{Fir_Rate_Dist_Instant_compare}
@@
 We have only presented our analysis of network activity so far.
-In this section we present results that relate to features of synaptic topology.
+In this section we present results that relate to features of network topology.
 Since the SORN we used for all simulations only included plastic mechanisms affecting recurrent excitatory connections, these were the subject of our investigations.
-Moreover, in contrast to the previous section, we did not explicitly aim for the emergence of a \emph{new} feature of synaptic topology, but rather sought to recover properties that had been found in earlier versions of the LIF-SORN.
+Moreover, in contrast to the previous section, we did not explicitly aim for the emergence of a \emph{new} feature of network topology, but rather sought to recover properties that had been found in earlier versions of the LIF-SORN.
 
 \subsubsection{Excitatory Connection Fraction}
-In the previous version of the LIF-SORN, initializing the network with zero recurrent excitatory connections led to a monotonically increasing but saturating excitatory-to-excitatory connection fraction (CF).
+In the previous version of the LIF-SORN, initializing the network with zero recurrent excitatory connections led to a overall increasing but saturating time course of the excitatory-to-excitatory connection fraction (CF).
 The growth rate was tuned such that the terminal CF settled at $\mathrm{10\%}$, see \cite[p.
@@
 Diffusive homeostasis caused the CF to slightly overshoot its final fraction in the growth phase.
-To understand this kind of behavior, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic growth and pruning.
+To understand this kind of behavior, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic creation and pruning.
 The average change of connection fraction is simply proportional to the difference between newly created synapses and those that were removed.
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/av_stdp_change_time.png}
-\caption{Top: Mean change of synaptic weights (growth and pruning excluded) between two normalization steps.
+\caption{Top: Mean change of synaptic weights (creation and pruning excluded) between two normalization steps.
 Bottom: Standard deviation for the same data.
@@
 \end{figure}
+
 Apart from reproducing the desired connection fraction, previous versions of the LIF-SORN showed an over-representation of bidirectional connections compared to a random graph with equal connectivity \cite{SORN_Paper}.
 This experimentally observed feature required the presence of a distance dependent connection probability, as described in section \ref{network simulation}.
-The absence of this breaking of spatial homogeneity even led to an under-representation of bidirectional connections, which is known to be an effect of STDP in recurrent networks \cite{Syn_Plast_Abbott}.
-The separation between simulations with and without a spatial connection profile is retained, as shown in Figure \ref{RC_CFB_plot}.
+The theoretical background of this effect was laid out by Miner and Triesch \cite{SORN_Paper} and further generalized by Hoffmann and Triesch \cite{Hoffmann_2017}.
+The result of these investigations was that any deviation from a perfectly uniform connection probability that preserves symmetry of these connection probabilities will necessarily lead to an over-representation of bidirectional connections.
+We shall explain this effect in more detail.
+
+First, assume that the connection probability $p_{\rm hom.}$ between every pair of neurons is equal.
+The resulting structure is called an Erd\H{o}s-Renyi graph and the bidirectional connection probability is simply $p_{\rm hom.}^2$.
+Now, we consider the case where each neuron $i$ connects to another neuron $j$ with a certain probability $p_{ij}$ and where neuron $j$ connects with equal probability $p_{ji}=p_{ij}$ to neuron $i$.
+We further assume that all these connection probabilities are drawn from the same distribution.
+The bidirectional connection probability between a random pair of neurons is thus
+\begin{equation}
+p_{\rm bidir.} = \mathrm{E[}p_{ij}p_{ji}\mathrm{]} = \mathrm{E[}p_{ij}^2\mathrm{]}
+\label{bidir_prob}
+\end{equation}
+where $\rm E[\cdot ]$ denotes the expected value.
+The \textit{relative} bidirectional connectivity now compares this value to the expected bidirectional connection probability of an Erd\H{o}s-Renyi graph with the same unidirectional overall connection probability.
+In such a graph, the unidirectional connection probability is $\mathrm{E[}p_{ij}\mathrm{]}$ and thus, the bidirectional connection is
+\begin{equation}
+p_{\rm bidir. rand.} = \mathrm{E[}p_{ij}\mathrm{]}^2 \; .
+\label{bidir_rand_prob}
+\end{equation}
+The ration we would like to calculate thus is
+\begin{equation}
+r_{CFB} = \frac{\mathrm{E[}p_{ij}^2\mathrm{]}}{\mathrm{E[}p_{ij}\mathrm{]}^2} \; .
+\end{equation}
+Using Jensen's inequality and the fact that the squaring function is convex, Hoffmann and Triesch showed that for any distribution of connection probabilities with a non-vanishing variance $\mathrm{Var[}p_{ij}\mathrm{]} > 0$, $r_{CFB}$ will be greater or equal to one.
+This provided an explanation why a non-uniform, distance-dependent connection profile with reciprocally symmetric connection probabilities leads to an over-representation of bidirectional connections.
+
+In the plastic network, the absence of this breaking of spatial homogeneity even led to an under-representation of bidirectional connections, which is known to be an effect of STDP in recurrent networks \cite{Syn_Plast_Abbott}.
+The separation between simulations with and without a spatial connection profile is retained after having implemented diffusive homeostasis, as shown in Figure \ref{RC_CFB_plot}.
 \begin{figure}
@@
 A well-studied property of neural networks is the distribution of synaptic weights.
-Experimental studies in hippocampus and cortical regions suggest heavy-tailed log-normal-like distribution of synaptic efficacies \cite{Song_Connectivity_2005,Lisman_Synapses_1993,Yasumatsu_Synapses_2008,Loewenstein_Spine_Sizes}.
+Experimental studies in hippocampus and cortical regions suggest heavy-tailed log-normal-like distributions of excitatory synaptic efficacies \cite{Song_Connectivity_2005,Lisman_Synapses_1993,Yasumatsu_Synapses_2008,Loewenstein_Spine_Sizes}.
 Theoretical models are mainly based on a combination of multiplicative and additive weight dynamics \cite{Loewenstein_Spine_Sizes,Statman_Synapses_2014}, which is in line with our implementation of multiplicative normalization and additive STDP.
@@
 A slightly larger variance can be observed.
-A possible explanation refers back to our observations in Figure \ref{STDP_change}: Regarding STDP as a random process, a broader distribution of weights can be explained by a smaller potentiating effect and a decreased variance of STDP-fluctuations, which is both the case for diffusive homeostasis in the beginning of the simulation.
+A possible explanation refers back to our observations in Figure \ref{STDP_change}: Regarding STDP as a combination of a multiplicative and an additive random process, a broader distribution of weights can be explained by a smaller potentiating effect, which is the case for diffusive homeostasis in the beginning of the simulation.
 Still, it seems unlikely that a possible effect of these differences is still present at $\mathrm{t=1500\,s}$.
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/syn_lifetimes.png}
-\caption{Distribution of recurrent excitatory synaptic lifetimes.
+\caption{Distribution of lifetimes of recurrent excitatory synaptic connections.
 Linear fits ignoring falloff for large synaptic lifetimes resulted in a slope of $\mathrm{-1.87}$ for diffusive homeostasis and $\mathrm{-1.68}$ for non-diffusive homeostasis.}
@@
 Small weights are therefore determined by additive quasi-random (due to their weak coupling to the postsynaptic neuron) fluctuations, which, as a very simple approximation, can be described as a Brownian motion with a certain standard deviation $\mathrm{\sigma}$.
-The first hitting time of this Brownian motion is described by a Lévy distribution:
+The first-hitting time of this Brownian motion is described by a Lévy distribution \cite{Roy_1968}:
 \begin{equation}
@@
 \end{equation}
-The term $\mathrm{t^{-3/2}}$ dominates for larger $\mathrm{t}$, which roughly resembles the power-law exponents found in Figure \ref{Syn_Lifetimes}.
+The term $\mathrm{t^{-3/2}}$ dominates for larger $\mathrm{t}$, which very roughly resembles the power-law exponents found in Figure \ref{Syn_Lifetimes}.
+Zheng et al.
+found a similar slope in the binary version of the SORN and also argued that this could be referred to random-walk behavior \cite{Pengsheng_2013}.
+Still, understanding the exponent of this distribution is subject to ongoing research and it has been argued that a more precise explanation could be used to relate certain parameters of synaptic plasticity to the value of this exponent, especially regarding the balance between long-term potentiation and depression.
 
 \subsubsection{Mean outgoing Weights}\label{Section_Mean_outgoing_Weights}
-Since we only implemented synaptic normalization for the sum of \emph{ingoing} weights, the total or average strength of \emph{outgoing} connections may vary from cell to cell.
+Since we only implemented synaptic normalization for the sum of \emph{incoming} weights, the total or average strength of \emph{outgoing} connections may vary from cell to cell.
 In a sense, the strength of outgoing connections per neuron can be regarded as a measure of how influential a neuron's activity is with respect to other neurons in the network.
 Effenberger et al.
-have shown in computational studies that these ``driver neurons" form highly active and interconnected subnetworks \cite{Effenberger_2015}, an observation that is backed up by experimental studies \cite{Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}.
+have shown in computational studies that influential ``driver neurons" form highly active and interconnected subnetworks \cite{Effenberger_2015}, an observation that is backed up by experimental studies \cite{Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}.
 Figure \ref{Out_Weight_Mean_Quantile} shows that diffusive homeostasis allows for the emergence of a small group of highly influential neurons, which resembles the findings in \cite{Effenberger_2015}.

### 2017-03-02 draft.tex
.

@@
 have shown in computational studies that influential ``driver neurons" form highly active and interconnected subnetworks \cite{Effenberger_2015}, an observation that is backed up by experimental studies \cite{Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}.
-Figure \ref{Out_Weight_Mean_Quantile} shows that diffusive homeostasis allows for the emergence of a small group of highly influential neurons, which resembles the findings in \cite{Effenberger_2015}.
+Figure \ref{Out_Weight_Mean_Quantile} shows that diffusive homeostasis allows for the emergence of a small group of highly influential neurons, which resembles the findings in \cite{Effenberger_2015}, though the range over which the mean outgoing weights vary is not as prominent.
 A comparison of statistics generated with shuffled versions of the weight matrices illustrates that above-chance exceptionally strong mean outgoing weights were indeed present.
@@
 identified the presence of inhibitory STDP as a necessary mechanism for the development of this feature, in contrast to our model.
-On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: It weakens inhibitory currents for some neurons, which cause these neurons to have more above-average firing rates.
-In turn, synapses between highly active presynaptic cells and postsynaptic neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
+On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: Though it is known that inhibitory STDP can balance network activity \cite{Vogels_2011}, for some excitatory neurons in the network, presynaptic inhibitory neurons can not fully compensate the above-average firing rate of the postsynaptic neuron.
+Furthermore, synapses between highly active excitatory presynaptic cells and postsynaptic excitatory neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
+These two effects combined then give rise to the strong mean outgoing weights of this subgroup of neurons.
 With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies a similar functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity.
 We tested this relationship by plotting the mean outgoing weights against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
-A strong heterogeneity of firing rates allows for the development of few neurons with comparably strong mean outgoing weights, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range.
+We also tested A strong heterogeneity of firing rates allows for the development of few neurons with comparably strong mean outgoing weights, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range.
 We also tested the case of instant diffusion.

### 2017-03-03 draft.tex
.

@@
 \usepackage{caption}
-
+\usepackage{tabu}
 \usepackage{float}
@@
 \begin{document}
+\tabulinesep=1.2mm
+
 \begin{titlepage}
@@
 \begin{table}
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabu}{|l|l|l|l|l|}
 \hline
@@
 \hline
-\end{tabular}
+\end{tabu}
 \caption{Parameters of synaptic connections.}
@@
 \begin{table}[H]
-\begin{tabular}{|l|l|l|}
+\begin{tabu}{|l|l|l|}
 \hline
@@
 \hline
-\end{tabular}
+\end{tabu}
 \caption{Parameters of LIF neuron}
@@
 \begin{table}
-\begin{tabular}{|l|l|}
+\begin{tabu}{|l|l|}
 \hline
@@
 \hline
-\end{tabular}
+\end{tabu}
 \caption{Parameters of homeostatic intrinsic plasticity.}
@@
 
-Describing the neural activity as instantaneous firing rates raises the question how to describe the production of nitric oxide, since the outcome of equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $Ca^{2+}$ concentration caused by spike events.
+Describing the neural activity as instantaneous firing rates raises the question how to describe the production of nitric oxide, since the outcome of Equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $\rm Ca^{2+}$ concentration caused by spike events.
 One could naively replace the sum of Dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{\rm spike} r_i(t)$.
@@
 Homeostasis reaches a point of saturation, where faster diffusion has no effect on the heterogeneity of firing rates.
+Each of the data points in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} (A) and (B) corresponds to a single full simulation, though the same simulation data was used in (A) and (B).
+$\rm 55$ simulations were ran in total.
+We picked the $\rm D$-values by hand to achieve a good representation of the overall trend while limiting the amount of simulations.
+The set of diffusion constants used is given in Table \ref{Diff_Test_Constants_Sim_Number}.
 \begin{figure}
@@
 \end{figure}
+
+\begin{table}
+\begin{tabu}{|l|l|}
+\hline
+\boldmath{$\rm D\;[\mu m^2 ms^{-1}]$} & \textbf{Number of Sim.} \\ \hline
+$\rm 0.0$ & 1 \\ \hline
+$\rm 0.1,0.2,...,0.8,0.9$ & 2 \\ \hline
+$\rm 1.0,2.0,...,5.0,8.0,10.0,15.0,20.0$ & 4 \\ \hline
+\end{tabu}
+\caption{Diffusion constants and number of simulations used in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.}
+\label{Diff_Test_Constants_Sim_Number}
+\end{table}
+
 We also investigated the influence of the diffusion constant onto the distribution's skewness, shown in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} (B), to further quantify this dependence.
@@
 \caption{Distribution of lifetimes of recurrent excitatory synaptic connections.
-Linear fits ignoring falloff for large synaptic lifetimes resulted in a slope of $\mathrm{-1.87}$ for diffusive homeostasis and $\mathrm{-1.68}$ for non-diffusive homeostasis.}
+Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a slope of $\mathrm{-1.87}$ for diffusive homeostasis and $\mathrm{-1.68}$ for non-diffusive homeostasis.}
 \label{Syn_Lifetimes}
@@
 found a similar slope in the binary version of the SORN and also argued that this could be referred to random-walk behavior \cite{Pengsheng_2013}.
-Still, understanding the exponent of this distribution is subject to ongoing research and it has been argued that a more precise explanation could be used to relate certain parameters of synaptic plasticity to the value of this exponent, especially regarding the balance between long-term potentiation and depression.
+Still, understanding the exponent of this distribution is subject to ongoing research and it has been argued that a more precise explanation could be used to relate certain parameters of synaptic plasticity to the value of this exponent.
+Especially, the balance between long-term potentiation and depression is thought to influence this exponent, where potentiation/depression dominated plasticity leads to a smaller/larger absolute value of the exponent of the distribution.
 
@@
 Figure \ref{Out_Weight_Mean_Quantile} shows that diffusive homeostasis allows for the emergence of a small group of highly influential neurons, which resembles the findings in \cite{Effenberger_2015}, though the range over which the mean outgoing weights vary is not as prominent.
+
 A comparison of statistics generated with shuffled versions of the weight matrices illustrates that above-chance exceptionally strong mean outgoing weights were indeed present.
+To check for statistical significance, we performed a two-sample Kolmogorov-Smirnov tests between all datasets depicted in Figure \ref{Out_Weight_Mean_Quantile}.
+This statistical test allows to compare the empirical distribution functions of two sets of random variables by means of .
+More specifically, the null hypothesis states that both sets share the same underlying probability function.
+Thus, in our case, there should be a high statistical significance towards the rejection of this hypothesis.
+Though we did calculate the p-value for all possible pairs of datasets (28 in total), only a number of those were of relevance since we were interested in statistical differences due to diffusive homeostasis.
+These are listed in Table \ref{Kolmogorov_Mean_Out}.
+As the values indicate, the statistical significance is very high.
+Apart from the difference between diffusive and non-diffusive homeostasis, the difference between original and randomly shuffled versions of the weight matrices also appear to be significant.
+
+\begin{table}
+\begin{tabu}{|l|l|}
+\hline
+\textbf{Combination} & \textbf{p-value} \\ \hline
+D,T,NS vs ND,T,NS & $\rm 4.662 \cdot 10^{-35}$ \\ \hline
+D,NT,NS vs ND,NT,NS & $\rm 6.895 \cdot 10^{-77}$ \\ \hline
+D,T,NS vs D,T,S & $\rm 3.344 \cdot 10^{-44}$ \\ \hline
+D,NT,NS vs D,NT,S & $\rm 1.790 \cdot 10^{-61}$ \\ \hline
+\end{tabu}
+\caption{p-values of the Kolmogorov-Smirnov test calculated for a subset of dataset combinations depicted in Figure \ref{Out_Weight_Mean_Quantile}.
+The abbreviations are as follows: D: diffusive, T: topology, S: shuffled weights, N: negotiation.}
+\label{Kolmogorov_Mean_Out}
+\end{table}
+
 We noted further that the difference between shuffled matrices corresponding to non-diffusive and diffusive homeostasis is in line with our observation from Figure \ref{Weight_Dist}, which indicated a broader distribution of weights for diffusive homeostasis.
@@
 Dashed lines are means obtained by randomly shuffling synaptic weights.
-Data was taken from 25 weight matrices per line, representing weights within $\mathrm{1000-1500\,s}$.}
+Data was taken from a single weight matrix each, at $\mathrm{t = 1500\,s}$.}
 \label{Out_Weight_Mean_Quantile}
@@
 On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: Though it is known that inhibitory STDP can balance network activity \cite{Vogels_2011}, for some excitatory neurons in the network, presynaptic inhibitory neurons can not fully compensate the above-average firing rate of the postsynaptic neuron.
-Furthermore, synapses between highly active excitatory presynaptic cells and postsynaptic excitatory neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
+Furthermore, synapses from highly active excitatory presynaptic cells to postsynaptic excitatory neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
 These two effects combined then give rise to the strong mean outgoing weights of this subgroup of neurons.
 With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies a similar functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity.
-We tested this relationship by plotting the mean outgoing weights against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
-We also tested A strong heterogeneity of firing rates allows for the development of few neurons with comparably strong mean outgoing weights, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range.
-We also tested the case of instant diffusion.
-Though firing rates span across a similar range, mean weights do not reach as high values as in the case of diffusion at a finite rate.
+We tested this relationship by plotting the mean of excitatory outgoing weights, sum of outgoing weights and the out degree against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
+A strong heterogeneity of firing rates allows for the development of few neurons with comparably strong mean outgoing weights, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range.
+Interestingly, the heterogeneity of out weights is most prominent when looking at the total sum.
+While this should lead to the conclusion that this is the case because an increased firing rate increases both, mean and number of outgoing weights, the latter can not be strictly verified based on Figure \ref{Out_Weight_vs_F} (D).
+In consequence, we also did not find a strong direct correlation between mean outgoing weights and out degree, as shown in Figure \ref{Mean_Weight_vs_Out_Degree}.
+Still though, it is interesting to note that diffusive homeostasis, in contrast to the other shown variants, diffusive homeostasis at least has a correlation coefficient of $\rho_{\rm Diff.} =  0.4$, especially in contrast to $\rho_{\rm Inst.
+Diff.} =  -0.23$, though instant diffusion leads to similarly spread firing rates.
+
+Furthermore, it is interesting to note that we found a roughly linear relationship between mean outgoing weight and firing rate on a logarithmic weight scale, see Figure \ref{Out_Weight_vs_F} (B).
+Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.
+
 \begin{figure}
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_weights_vs_rate.png}
-\caption{Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{700-1000\,s}$) in regular (A) and logarithmic space (B).
-Each plot corresponds to a presynaptic excitatory cell.}
+\includegraphics[width=\textwidth]{../../plots/syn_topology/sum_out_weights_vs_rate.png}
+\includegraphics[width=\textwidth]{../../plots/syn_topology/out_degree_vs_rate.png}
+\caption{A,B: Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{700-1000\,s}$) in regular and logarithmic space.
+Each point corresponds to a presynaptic excitatory cell.
+C,D: Sum of outgoing excitatory weights, same setting as in (A) and (B).
+E: Out degree of excitatory neurons, same setting as in (A) and (B).
+}
 \label{Out_Weight_vs_F}
 \end{figure}
-Furthermore, it is interesting to note that we found a roughly linear relationship on a logarithmic weight scale.
-Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.
+
+\begin{figure}
+%%% out_weight_vs_out_degree.py
+\includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_vs_out_degree.png}
+\caption{Out degree vs.
+mean outgoing excitatory weights at $\mathrm{t=1500\,s}$, same dataset as in Figure \ref{Out_Weight_vs_F}.
+Pearson correlation coefficients were $\rho_{\rm Diff.} =  0.4$, $\rho_{\rm Inst.
+Diff.} =  -0.23$ and $\rho_{\rm Non-Diff.} =  0.07$.}
+\label{Mean_Weight_vs_Out_Degree}
+\end{figure}
+
 \newpage

### 2017-03-04 draft.tex
.

@@
 In consequence, we also did not find a strong direct correlation between mean outgoing weights and out degree, as shown in Figure \ref{Mean_Weight_vs_Out_Degree}.
-Still though, it is interesting to note that diffusive homeostasis, in contrast to the other shown variants, diffusive homeostasis at least has a correlation coefficient of $\rho_{\rm Diff.} =  0.4$, especially in contrast to $\rho_{\rm Inst.
-Diff.} =  -0.23$, though instant diffusion leads to similarly spread firing rates.
+Still though, it is interesting to note that diffusive homeostasis, in contrast to the other shown variants, at least has a correlation coefficient of $\rho_{\rm Diff.} =  0.4$, especially in contrast to $\rho_{\rm Inst.
+Diff.} =  -0.23$, even though instant diffusion leads to similarly spread firing rates.
 
@@
 $\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the mixture between single-neuron homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
-$\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their overall mean.
-
-The spiking recurrent network was replaced by a set of non-interacting non-spiking neurons whose individual mean firing rates were calculated by
+$\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their population mean.
+
+The spiking recurrent network was replaced by a set of non-interacting non-spiking neurons whose individual firing rates were calculated by
 \begin{align}
@@
 \end{align}
-where $\nu$ is the mean population firing rate, $\phi_i$ the individual firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $V_{t,i}$ its synaptic input mean and standard deviation and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant.
+where $\nu$ is the mean population firing rate, $\phi_i$ the firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $V_{t,i}$ its synaptic input mean and standard deviation over time and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant.
 Synaptic efficacy and number of incoming neurons were drawn randomly to match the statistics of the actual network topology.
-Self consistency was achieved by iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate1} until the desired precision of convergence was reached.
-
-The authors claimed that this model reproduces results of the full network, in particular that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or a corresponding larger $\alpha$).
+Self consistency was achieved by iterating through Equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate3} until the desired precision of convergence was reached.
+
+The authors claimed that this model reproduces results of the full network, in particular that the steady-state firing rate distribution spreads out due to a larger diffusion constant (or corresponding to a larger $\alpha$).
 
@@
 
-Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics of excitatory rates and thresholds for $\mathrm{\alpha=\lbrace 0.4,0.8,0.9,1.0\rbrace}$.
-Apparently, all rates approach the same target rate of $\mathrm{3\,Hz}$ and thresholds move towards the same configuration for either choice of $\mathrm{\alpha}$ except for the limiting case of $\mathrm{\alpha=1}$.
+Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics of excitatory rates and thresholds for $\mathrm{\alpha=\lbrace 0.5,0.9,1.0\rbrace}$.
+We ran simulations with other values of $\rm \alpha$ and found that all rates approach the same target rate of $\mathrm{3\,Hz}$ and thresholds move towards the same configuration for either choice of $\mathrm{\alpha}$ except for the limiting case of $\mathrm{\alpha=1}$.
 A significant difference only exists within the transient dynamics leading to the steady state.
@@
 \begin{equation}
-\left( \nabla^2 + \left( i\sqrt{\frac{\lambda}{D}}\right)^2\right) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{\mathrm{ neur.},i})\cdot \frac{- \gamma \cdot r_i}{D}
+\left( \nabla^2 + \left( i\sqrt{\frac{\lambda}{D}}\right)^2\right) NO = \sum_{i} \delta^2(\mathbf{x}-\mathbf{x}_{\mathrm{ neur.},i}) \frac{- \gamma \cdot r_i}{D}
 \label{simple_NO_dyn_with_diff_equil_helmholtz}
@@
 which is a two-dimensional Helmholtz equation with a superposition of rescaled Dirac functions.
-The solution of $NO$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of the equation.
+The solution of $NO$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of the equation \cite{EncyMath}.
 For each delta function $\delta^2(\mathbf{x}-\mathbf{x}_i)$, the solution is
@@
 We obviously had to limit the amount of elements of the sum for our calculations, such that copies that are shifted further away can be neglected.
-For the sake of performance the number of terms in the sum was adjusted to suffice the given diffusion constant.
+For the sake of performance the number of terms in the sum was adjusted to suffice for the given diffusion constant.
 
@@
 \end{figure}
-These observations naturally led us to the question of how the correlation between predicted measured firing rates behaves in between the aforementioned limits.
+These observations naturally led us to the question of how the correlation between predicted and measured firing rates behaves in between the aforementioned limits.
 Especially, we were interested in the range of the diffusion constant for which our model provides a good description of the full spiking network's activity.

### 2017-03-06 draft.tex
.

@@
 %% sim_vs_matrix_sol_standard_dev_distribution.py
-\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_std_dev_dist.png}
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_std_dev_dist_new.png}
 \end{minipage}
@@
 %% sim_vs_matrix_sol_skew_distribution.py
-\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_skew_dist.png}
+\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_skew_dist_new.png}
 \end{minipage}
-\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries.}
+\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries.
+Same simulation data as in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} was used, each point representing a single simulation.
+The histograms for the analytic solutions were generated for 50 $\rm D$ values, spanning equally between $\rm D=0 mu m^2 /ms$ and $\rm D=20 mu m^2 /ms$.
+Each column is a histogram of $\rm 200$ firing-rate solutions for randomly generated positions, giving a total of $\rm 10000$ matrix solutions.}
 \label{Std_Skew_Dist_vs_Data}
 \end{figure}
-In summary, shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuation in the spatial distribution of neurons.
+In summary, shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuations in the spatial distribution of neurons.
+
 To further back up this result we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
@@
 We expected that all neurons then should---in theory---exhibit the exact same firing rate due to symmetry.
-Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the result, being a significantly narrower distribution.
+Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the simulation result, being a significantly narrower distribution.
+As predicted, the analytic result showed a similarly narrow distribution.
 This strongly supported the previous assertion.
@@
 \end{center}
-\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2 ms^{-1}}$.}
+\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2 ms^{-1}}$, full simulation and analytic prediction.
+1 Simulation run was used, with spikes within $\rm 1200 \leq t \leq 1500$.}
 \label{Fir_Rate_Dist_Reg_Grid}
@@
 \subsubsection{Low-Density Neighborhoods correlate with strong outgoing Connections}
-In Section \ref{Section_Mean_outgoing_Weights} we stated that diffusive homeostasis allowed the network do develop few neurons with exceptionally strong outgoing weights.
-We found this effect to be present in neurons with an highly above-average firing rate.
-Moreover, the outcomes presented in Section \ref{Section_Rand_Mat_vs_Sim} suggest that the steady state of firing rates is strongly influenced by the spatial structure of excitatory neurons.
+In Section \ref{Section_Mean_outgoing_Weights} we stated that diffusive homeostasis allowed the network to develop few neurons with exceptionally strong outgoing weights.
+We found this effect to be present in neurons with an above-average firing rate.
+Moreover, the outcomes presented in Section \ref{Section_Rand_Mat_vs_Sim} suggest that the steady state of firing rates is strongly influenced by the spatial arrangement of excitatory neurons.
 Combining these two qualities led us the conclusion that one should be able to observe some relation between spatial structure and the emergence of ``driver neurons".
-More specific, regions of neurons with above average firing rates should develop stronger outgoing connections.
+More specifically, regions of neurons with above average firing rates should develop stronger outgoing connections.
 To get an intuitive understanding of what characterizes regions of above-average firing rates we interpreted the homeostatic condition in the high-neuron-density limit as an approximation of a continuous integral equation:
@@
 \end{equation}
-Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should correlate with strong outgoing weights and vice versa.
+Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should have strong outgoing weights and vice versa.
 We approximated the local neuron density by means of a a Gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$ to test this hypothesis.
@@
 \includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
-\caption{(A) and (B): Scatter plot of inverse of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights.
+\caption{A and B: Scatter plot of \emph{inverse} of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights.
 Note the spatial correlation in high/low-density regions.
-(C) and (D): The decadic logarithm of outgoing weights correlates with inverse neuron density (corr.
-coeff.
-of 0.513).}
+C: Frequency of excitatory weights (averaged over $\rm 1200\,s \leq t \leq 1500\,s$) versus inverse neural density (same estimation method as in (A)).
+Coefficient of correlation $\rho_{\rm frequ.-dens.} = 0.798$.
+D: Decadic logarithm of mean outgoing excitatory weights versus inverse neural density.
+Coefficient of correlation $\rho_{\rm weight.-dens.} = 0.513$.}
 \label{Inverse_Dens_vs_Sum_Out_Weights}
@@
 \newpage
-\subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}
-We considered the possibility that a wider spread of each individual NO-source could locally decrease distinguishability between neurons since our analytic results revealed that a strong correlation between spatial structure and result firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors.
-Thereby it might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values.
-The biological plausibility of this idea is discussed in Section \ref{Possible_Modifications_Section}.
+\subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}\label{NO_source_spread_section}
+We considered the possibility that a wider spatial spread of each individual NO source---in contrast to the approximate point source used up to this point---could locally decrease distinguishability between neurons since our analytic results revealed that a strong correlation between spatial structure and resulting firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors.
+Referring to the results shown in Figure \ref{Ext_Input_Switch}, this modification with respect to the NO influx might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values.
+More specifically, one could potentially observe the distinction of input groups shown in Figure \ref{Ext_Input_Switch} over a longer time scale.
+While Sweeney et al.
+argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide) Philippides et al.
+reported that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}.
+The diameter of these ``production areas" is on the order of $\mathrm{10-100 \mu m}$.
 
@@
 Thereafter, we ran the same simulation as for Figure \ref{Ext_Input_Switch}.
-Comparing both plots, we saw a much greater persistence of distinction between excitatory subgroups.
+Comparing both plots, we saw a much greater persistence of distinction between excitatory subgroups, see Figure \ref{External_Input_Switch_Spread_Source}.
 The time course of activity suggests that this distinction might even be permanent and steady instead of a very slow but transient state.
@@
 Harnack et al.
-additionally reported a similar effect as seen in our system: Noise can reduce stability in a damped dynamical system by constantly causing deviations from its fixed point.
+additionally reported a similar effect as seen in our system: Noise can induce oscillations in a subscritical dynamical system by constantly causing deviations from its fixed point.
 
@@
 
+Interestingly, Zenke, Hennequin and Gerstner theoretically investigated the interplay between Hebbian plasticity mechanisms and homeostatic processes that prevent runaway of synaptic efficacies and network activity \cite{Zenke_2013,Zenke_2017}.
+They came to the conclusion that regulatory mechanisms actually need to act on a time scale of at least minutes or seconds or faster to avoid dynamic instabilities such as persistent oscillations of activity and/or synaptic weights.
+It should however be noted that their research dealt with models of synaptic homeostasis rather than intrinsic mechanisms.
+Though it might seem so at first glance, we do not regard the findings by Zenke and Gerstner as necessarily contradicting those by Harnack et al., since the arguments brought forward do differ: While Zenke and Gerstner had to introduce a fast compensatory process mainly due to the self-potentiating effect of Hebbian plasticity rules, Harnack et al.
+only considered activity regulation in static networks.
+In a sense, while the former describes Hebbian plasticity as the source of instability that needs to be compensated by a fast homeostatic mechanism, the latter allocates the source of oscillatory instability within the homeostatic mechanism itself.
+This, however, might bring up the question why Zenke et al.
+did not as well observe similar instabilities as described by Harnack et al.
+when using relatively fast homeostasis in their network \cite{Zenke_2013}.
+A possible explanation could be that their feedback loop consists of a rather low-dimensional system that estimates firing rates through an exponential filter, keeping delays due to intermediate dynamic variables---a potential source of instability---small.
+
+Furthermore, there is no reason to assume that fast synaptic homeostatic mechanisms could not act \emph{alongside} other slow activity-regulating processes.
+In fact, our network model also contained a form of fast synaptic homeostasis, though not regulating firing rates in a strict manner: Postsynaptic normalization, which was carried out once per second (see Section \ref{Section_Syn_Plast}) regulates synaptic efficacies on a time scale  that is in accordance to the findings by Zenke and Gerstner.
+
 \subsection{The Firing Rate Distribution} \label{Fir_Rate_Dist_Discussion_Section}
@@
 Though the distribution did approximately resemble a log-normal-like shape, it did not perfectly match our expectations.
-In order to acquire a deeper understanding of the mechanisms that determine these statistics we developed an analytical expression that allowed us to reliably predict the steady state of firing rates based on the spatial structure of excitatory neurons.
+In order to acquire a deeper understanding of the mechanisms that determine these statistics we derived an analytical expression that allowed us to reliably predict the steady state of firing rates based on the spatial structure of excitatory neurons.
 We would like to emphasize that this explanation differs from common approaches of understanding the emergence of heavy-tailed statistics of firing rates in recurrent networks.
@@
 Instead, we hypothesized that we might be able to uncouple activity from spatial structure without tweaking the diffusion process by spatially increasing the spread of NO-insertion.
-While Sweeney et al.
-argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide) Philippides et al.
-reported that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}.
-The diameter of these ``production areas" is on the order of $\mathrm{10-100 \mu m}$.
-To incorporate this spread of synthesis in our model of diffusion we convolved a circular shaped and shifted production-kernel (multiplied by the momentary rate of NO-synthesis) with the field of NO-concentration.
-Intuitively, it locally smeared the distinction between neighboring neurons.
-From a more abstract point of view, it provided a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.
-As Figure \ref{External_Input_Switch_Spread_Source} suggests, this indeed improved flexibility of individual activity while retaining an overall constant firing rate.
-We therefore gained further control over the strictness of the homeostatic mechanism by adjusting the area of NO insertion.
+The result presented in Section \ref{NO_source_spread_section} was positive.
+Intuitively, this modification would allow to locally smear the distinction between neighboring neurons.
+From a more abstract point of view, it provides a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.
+We therefore regard this idea as a potential modification for future use of diffusive homeostasis, gaining further control over the strictness of the homeostatic mechanism by adjusting the area of NO insertion.
 
@@
 
-Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist} we noted that the increased width of the distribution is largely due to to an increment on the left half of the curve.
+Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist} we noted that the increased width of the distribution is largely due to an increment on the left half of the curve.
 Since new weights are initialized at $\mathrm{10^{-4}\, mV}$ this might indicate that some weights are drifting much more slowly from their value of initialization compared to other weights.
@@
 As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}) we found that neurons with a low-density neighborhood have a higher chance of developing these strong outgoing weights.
-Since this effect is directly linked to the low-density/high-firing-rate relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons with above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
+Since this effect is directly linked to the low-density/high-firing-rate relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that synapses with above-average firing presynaptic neurons tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
 

### 2017-03-06 draft.tex
.

@@
 %% fir_dist_shape_sim_matrix_compare.py
-\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}
+\includegraphics[width=0.7\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}
 \end{center}
@@
 Same simulation data as in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} was used, each point representing a single simulation.
-The histograms for the analytic solutions were generated for 50 $\rm D$ values, spanning equally between $\rm D=0 mu m^2 /ms$ and $\rm D=20 mu m^2 /ms$.
+The histograms for the analytic solutions were generated for 50 $\rm D$ values, spanning equally between $\rm D=0 mu m^2 /ms$ and $\rm D=20 \mu m^2 /ms$.
 Each column is a histogram of $\rm 200$ firing-rate solutions for randomly generated positions, giving a total of $\rm 10000$ matrix solutions.}

### 2017-03-06 draft.tex
.

@@
 
-\textbf{Short Term Plasticity:} A short term plasticity (STP) mechanism acting on recurrent excitatory connections was implemented as presented in \cite{Markram_STP} as an additional stabilization of network activity.
+\textbf{Short-Term Plasticity:} A short-term plasticity (STP) mechanism acting on recurrent excitatory connections was implemented as presented in \cite{Markram_STP} as an additional stabilization of network activity.
 It modulates the effective synaptic weights by multiplying the value stored in the weight matrix $w_{ji}$ by two dynamic variables $x$ and $u$, $w^{\rm effective}_{ji} = w_{ji}\cdot x \cdot u$, each synapse owning a pair $(x,u)$.
@@
 \end{equation}
-If no spikes arrive the system rests at $x\cdot u = U$.
-Otherwise, depending on the choice of $\tau_d$ and $\tau_f$, one can achieve a weight modulation that is dominated by potentiation ($\tau_f \gg \tau_d$) or depression ($\tau_f \ll \tau_d$).
+This is a phenomenological model of short-term plasticity that models two aspects of synaptic transmission, namely short-term depression (STD) and short-term facilitation (STF).
+STD is an effect that subsumes different mechanisms involved in the depletion of available neurotransmitters in the presynaptic terminal due to presynaptic action potentials.
+This fraction of depletion is represented by the variable $x$.
+Consequently, it is reduced upon a presynaptic spike.
+STF is based on the fact that a presynaptic action potential causes an increase of neurotransmitters available for release due to the influx of calcium into the presynaptic terminal \cite{Katz_1967,Katz_1968}.
+This effect is modeled by the variable $u$.
+The amount of potentially available neurotransmitters during an ``idle" state, with no presynaptic action potentials arriving, is given by $U$.
+Consequently, the dynamical system given by Equations \eqref{STP_dynamics1} and \eqref{STP_dynamics2} has its fixed point at $(x=1,u=U)$.
+If spikes arrive, depending on the choice of $\tau_d$ and $\tau_f$, one can achieve a weight modulation that is dominated by potentiation ($\tau_f \gg \tau_d$) or depression ($\tau_f \ll \tau_d$).
 We chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$ as a rough approximation of the values that were experimentally observed \cite{Markram_STP}, giving it a tendency towards potentiation.
@@
 \section{Results} \label{results}
-We first present the results of a comparison between features of the network activity in both variants in section \ref{activ_analys}, since our main goal of the implementation of diffusive homeostasis was to allow the network to develop a broader distribution of firing rates across excitatory neurons compared to the original version of homeostasis.
+We first present the results of a comparison between features of the network activity in both homeostatic variants in Section \ref{activ_analys}, since our main goal of the implementation of diffusive homeostasis was to allow the network to develop a broader distribution of firing rates across excitatory neurons compared to the original version of homeostasis.
 This is followed by an analytic discussion of an instability we observed within the diffusive homeostatic feedback loop, see Section \ref{theor_osc}.
@@
 \subsection{Activity Analysis} \label{activ_analys}
+As a first step, we investigated how diffusive homeostasis compares to non-diffusive homeostasis in terms of maintaining a stable level of population activity among excitatory and inhibitory population (though the latter one is only indirectly affected by excitatory synaptic input).
+\subsubsection{Dynamic Behavior of the Population Activity}
 We set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$ on a first attempt, as given by \cite{Sweeney_Paper}.
-Switching between non-diffusive/diffusive homeostasis after 750 seconds, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group (panel A/A*), the average $\rm NO$ concentration at the excitatory neurons' positions (panel B/B*) and the average firing threshold (panel C/C*) within the excitatory group (inhibitory threshold was fixed, see table \ref{LIF_neuron_params}).
+Switching between non-diffusive/diffusive homeostasis after $\rm 750\, s$, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group (panel A/A*), the average $\rm NO$ concentration at the excitatory neurons' positions (panel B/B*) and the average firing threshold (panel C/C*) within the excitatory group (inhibitory threshold was fixed, see table \ref{LIF_neuron_params}).
 Both homeostatic mechanisms managed to keep the excitatory population activity in the desired range of 3 Hz.
@@
 
-Dynamical models of interconnected excitatory and inhibitory groups can exhibit sustained oscillations of activity \cite[p.~270]{Theor_Neur_Dayan} on a larger, rate-based level.
+We thus speculated whether the observed oscillations might be explicable based on the network topology and the dynamic interplay between excitatory and inhibitory population.
+For this purpose, we transferred the structure and dynamics onto a simpler, rate-based model of neural network activity.
+The results are discussed in the following section
+\subsubsection{Predicting Activity in a Simplified Rate-Based Network}
+Dynamical models of interconnected excitatory and inhibitory groups can exhibit sustained oscillations of activity on a larger, rate-based level \cite[p.~270]{Theor_Neur_Dayan}.
+We therefore considered this interplay as a source of the observed oscillations.
+To test this, we mapped the LIF-SORN onto a non-spiking neural network.
+We ignored plastic changes due to STDP, since we assumed these to be irrelevant in the context of the time scale of the observed oscillations.
+
 As a simplest model, one can describe the dynamics of the excitatory and inhibitory populations as a two-dimensional dynamical system, representing the respective population rates $r_e$ and $r_i$
@@
 \end{align}
-$\mathrm{\langle w_{AB} \rangle,\, \langle N_{\mathrm{in},AB} \rangle}$ and $\mathrm{\langle r_A \rangle}$ denote the mean weight of a synapse connection population $\mathrm{A}$ with population $\mathrm{B}$, the mean number of incoming connections at a neuron in population $\mathrm{B}$ and the mean firing rate in population $\mathrm{A}$ (which makes it necessary to assume changes within the firing rate to be slow enough for a quasi-stationary description of the activity).
+$\mathrm{\langle w_{AB} \rangle,\, \langle N_{\mathrm{in},AB} \rangle}$ and $\mathrm{\langle r_A \rangle}$ denote the mean weight of a synapse connecting population $\mathrm{A}$ with population $\mathrm{B}$, the mean number of incoming connections at a neuron in population $\mathrm{B}$ and the mean firing rate in population $\mathrm{A}$ (which makes it necessary to assume changes within the firing rate to be slow enough for a quasi-stationary description of the activity).
 The total noise within a neuron of population $\mathrm{B}$ has a standard deviation of 
@@
 \end{align}
-One thus needs to incorporate the factor $\mathrm{x_{st.}\cdot u_{st.}}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise when trying to find the fixed point of equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
+One thus needs to incorporate the factor $\mathrm{x_{st.}\cdot u_{st.}}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise when trying to find the fixed point of Equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
 
 All these aspects taken together make it impossible to find an analytic expression for the fixed point of Equation \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
-Running a simulation of \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}, including all aforementioned approximations results in a stable configuration.
+Running a simulation of Equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}, including all aforementioned approximations resulted in a stable configuration.
 We set the relevant parameters to their predefined values for this simulation and additionally extracted the mean threshold of the excitatory population which was set by the non-diffusive homeostasis, see C/C* in Figure \ref{full_sim_osci}, yielding a threshold of $\mathrm{-56.963\, mV}$.
 The results are depicted in Figure \ref{Dyn_Rate_Approx}.
-The system settled to a fixed point of $\mathrm{(r_{0,e},r_{0,i}) = (2.992\, Hz, 7.144\, Hz)}$, which is quite close to $\mathrm{(3\, Hz, 6.768\, Hz)}$, which is the mean excitatory and inhibitory firing rate between $\mathrm{100-750\, s}$ of the full simulation (i.e., during non-diffusive homeostasis).
+The system settled to a fixed point of $\mathrm{(r_{0,e},r_{0,i}) = (2.992\, Hz, 7.144\, Hz)}$, which is quite close to $\mathrm{(3\, Hz, 6.768\, Hz)}$, being the mean excitatory and inhibitory firing rate found between $\mathrm{100-750\, s}$ of the full simulation (i.e., during non-diffusive homeostasis).
 \begin{figure}
@@
 \end{equation}
-Figure \ref{nNOS_approx_plot} compares the approximation given by \eqref{nNOS_single_sol_approx2} to the full NO production model (equations \eqref{Ca_dyn} and \eqref{nNOS_dyn}).
+Figure \ref{nNOS_approx_plot} compares the approximation given by \eqref{nNOS_single_sol_approx2} to the full NO production model (Equations \eqref{Ca_dyn} and \eqref{nNOS_dyn}).
 Spikes were drawn from a Poisson process at a rate of 3 Hz.
@@
 \caption{Time course of nNOS(t) with Poisson spiking at 3 Hz.
-The full simulation (blue, see equations \eqref{Ca_dyn},\eqref{nNOS_dyn}) is well fitted by the simplified model (red, see equation \eqref{nNOS_single_sol_approx2}).
+The full simulation (blue, see Equations \eqref{Ca_dyn},\eqref{nNOS_dyn}) is well fitted by the simplified model (red, see Equation \eqref{nNOS_single_sol_approx2}).
 Top panel is a closeup of the first spike event.
@@
 
-Returning to the question of how to describe NO synthesis in a simplified form, we note that according to equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}}\mathrm{ln}(2)}{3}$, which makes the mean rate of NO production over time simply $\langle nNOS \rangle = \langle r \rangle \frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3}$.
+Returning to the question of how to describe NO synthesis in a simplified form, we note that according to Equation \eqref{nNOS_single_sol_approx2}, a single spike causes the release of NO by an amount of $\frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}}\mathrm{ln}(2)}{3}$, which makes the mean rate of NO production over time simply $\langle nNOS \rangle = \langle r \rangle \frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3}$.
 However, it is not sufficient to simply propose $nNOS_i(t) = r_i(t) \frac{{Ca^{2+}_{\rm spike}}^3 \tau_{Ca^{2+}} \mathrm{ln} (2)}{3}$.
@@
 
-It is clear from Equation \eqref{NO_dyn_approx} why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $3 Hz \cdot N_{\rm exc.} = \mathrm{1200\,Hz}$, given the assumption that cells' spiking is approximately independent.
+It is clear from Equation \eqref{NO_dyn_approx} why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify Equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $3 Hz \cdot N_{\rm exc.} = \mathrm{1200\,Hz}$, given the assumption that cells' spiking is approximately independent.
 We furthermore argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{\rm total} = N_{\rm exc.} r_{\rm exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
@@
 We wanted to simplify the dynamics of threshold adaption and its effect on the population rate as a next step.
-Corresponding to the reduction to a single variable $r_{\rm exc.pop.}(t)$ for the mean excitatory activity in equation \eqref{nNOS_total_dyn}, we wanted to find an appropriate description containing only the mean threshold $V_{t,\rm pop.}(t) = \langle V_t(t) \rangle$.
+Corresponding to the reduction to a single variable $r_{\rm exc.pop.}(t)$ for the mean excitatory activity in Equation \eqref{nNOS_total_dyn}, we wanted to find an appropriate description containing only the mean threshold $V_{t,\rm pop.}(t) = \langle V_t(t) \rangle$.
 As stated earlier, Figure \ref{rate_th_close} suggests an immediate and approximately linear relation between excitatory population rate and the mean of thresholds within the excitatory population.
@@
 Figure \ref{Weight_Dist} compares the resulting distributions.
-We found that we can retain a log-normal-like distribution in combination with diffusive homeostasis.
-A slightly larger variance can be observed.
-A possible explanation refers back to our observations in Figure \ref{STDP_change}: Regarding STDP as a combination of a multiplicative and an additive random process, a broader distribution of weights can be explained by a smaller potentiating effect, which is the case for diffusive homeostasis in the beginning of the simulation.
-Still, it seems unlikely that a possible effect of these differences is still present at $\mathrm{t=1500\,s}$.
-\begin{figure}
-%%% plot_weight_dist.py
-\includegraphics[width=\textwidth]{../../plots/syn_topology/syn_weight_dist.png}
+We found that we can retain a log-normal-like distribution in combination with diffusive homeostasis, giving a similar distribution as for non-diffusive homeostasis.
+\begin{figure}
+%%% plot_weight_dist_mult_sets.py
+\includegraphics[width=\textwidth]{../../plots/syn_topology/syn_weight_dist_mult_sets.png}
 \caption{Distribution of decadic logarithm of excitatory synaptic weights at $\mathrm{t=1500\,s}$ for diffusive and non-diffusive homeostasis (both with distance-dependent connectivity).
-Gaussian fits returned $\mathrm{\mu_{\rm diff.}=-0.17\, \mathrm{log}_{10}(mV)}$, $\mathrm{\mu_{\rm non-diff.}=-0.087\, \mathrm{log}_{10}(mV)}$, $\mathrm{\sigma_{\rm diff.}=0.64\, log_{10}(mV)}$ and $\mathrm{\sigma_{non-diff.}=0.42\, log_{10}(mV)}$.}
+Gaussian fits returned $\mathrm{\mu_{\rm diff.}=-0.128\, \mathrm{log}_{10}(mV)}$, $\mathrm{\mu_{\rm non-diff.}=-0.064\, \mathrm{log}_{10}(mV)}$, $\mathrm{\sigma_{\rm diff.}=0.415\, log_{10}(mV)}$ and $\mathrm{\sigma_{non-diff.}=0.395\, log_{10}(mV)}$.
+Weight matrices were taken from 5 simulations, each at $\rm t = 1500\,s$.}
 \label{Weight_Dist}
@@
 
-Instead of directly iterating through equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate3}---as done in \cite{Sweeney_Paper}---to fulfill self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
+Instead of directly iterating through Equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate3}---as done in \cite{Sweeney_Paper}---to fulfill self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
 \begin{equation}
@@
 \includegraphics[width=\textwidth]{../../plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
-\caption{Dynamics of rates (A) and thresholds (B) of excitatory population of 400 Neurons and different values of $\mathrm{\alpha}$ (see equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).}
+\caption{Dynamics of rates (A) and thresholds (B) of excitatory population of 400 Neurons and different values of $\mathrm{\alpha}$ (see Equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).}
 \label{dynamics_rate_threshold_dyn_mean_field_sweeney}
@@
 We did so by recalling that Equation \eqref{NO_dyn} describes the full dynamics of the diffusive neurotransmitter.
-Furthermore, equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma  r_i}$, $r_i$ representing a neuron's rate and $\gamma$ being defined by Equation \eqref{2d-sys-fixed-points1}.
+Furthermore, Equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma  r_i}$, $r_i$ representing a neuron's rate and $\gamma$ being defined by Equation \eqref{2d-sys-fixed-points1}.
 In this section we discuss the implications of an in-between description, only applying the second simplification, but retaining the diffusive term:
@@
 which is a two-dimensional Helmholtz equation with a superposition of rescaled Dirac functions.
-The solution of $NO$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of the equation \cite{EncyMath}.
+The solution of $NO$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of Equation \cite{EncyMath}.
 For each delta function $\delta^2(\mathbf{x}-\mathbf{x}_i)$, the solution is
@@
 \end{center}
-\caption{Pearson correlation coefficient of predicted and measured firing rates (see Figure \ref{Rand_Matrix_Sol_vs_Sim}) versus diffusion constant. Line width depicts standard error.}
+\caption{Pearson correlation coefficient of predicted and measured firing rates (see Figure \ref{Rand_Matrix_Sol_vs_Sim}) versus diffusion constant.
+Line width depicts standard error, 5 simulations were used for each $\rm D$-value.}
 \label{Corr_Coeff_vs_D}

### 2017-03-07 draft.tex
.

@@
 
+\subsubsection{Former Single-Cell Homeostasis as an Integral Control}
+Former versions of the LIF-SORN and SORN used a simple form of integral control to regulate excitatory firing rates.
+Individual firing rates of excitatory cells were estimated by a spike counter over short subsequent time periods and compared to a target value.
+This difference was then fed to a controller which increased or decreased neuronal excitability in an additive way (making it a discrete form of integral control).
+As mentioned before, this type of control allowed to reliably tune each cell to a given target firing rate under changing input.
+A global target firing rate was chosen for all excitatory neurons.
+Consequently, this resulted in a very narrow distribution of excitatory firing rates.
+
 \subsubsection{The Role of Firing Rate Heterogeneity---a Dichotomy between Heterogeneity and Control?}
@@
 Of course this raises the question of how to choose these homeostatic targets.
-Experimental studies have found that neuronal populations exhibit a strong heterogeneity within their individual activity.
+As mentioned in the previous section, former versions of the SORN defined a single global target value.
+However, experimental studies have found that neuronal populations exhibit a strong heterogeneity within their individual activity.
 Many statistical analyses found particular evidence for a log-normal like distribution of firing rates \cite{Buzsaki_Fir_Rates_2014,Wohrer_Fir_Rates_2012}.
@@
 A problem of this procedure is the absence of any particular deeper physiological motivation or causation.
-In the light of this conceptual problem, one could, due to a lack of better knowledge, simply define a single global target of activity.
+In the light of this conceptual problem, one could, due to a lack of better knowledge, claim that it is reasonable to define a single global target of activity.
 
@@
 This suggests that the same set of neurons tend to be relatively active or inactive under different stimuli and changing environments, in line with the idea of modeling homeostasis by means of individual targets of activity, which together form the desired statistical distribution.
-Still, though apparently being a good phenomenological approach, it is unclear what gives rise to these target differences.
-
+Similar findings have recently been reported by Hengen et al.
+\cite{Hengen_2016}.
+They measured firing rates of individual neurons in the primary visual cortex of rats over several days after monocular deprivation.
+Among others, one of the results was that after an initial decline of firing rates due to the continuous lack of visual stimuli, firing rates subsequently returned to pre-deprivation levels on a single-cell level within an accuracy of 15\%, on average.
+However, they also reported that this accommodation took place predominantly during active awake phases, while firing rates remained relatively unchanged during sleep.
+This, however, does not attenuate that their result generally supports the existence of single-cell firing rate targets.
+
+Still, though apparently being a good phenomenological description, it is unclear what gives rise to these target differences.
 Another problem that one might consider is the fact that temporal fluctuations of activity are believed to be a major part of information transmission and processing within the brain \cite[p.
@@
 Synaptic lifetimes have been shown to approximately follow a power law distribution in earlier versions of LIF-SORN and binary SORN \cite{SORN_Paper,Pengsheng_2013}.
+Power law distributions appear in different areas of natural and social sciences \cite{Gabaix_1999,Pascual_2002,Kagan_2010}.
+Some quantity $x$ is said to be power law distributed if its distribution $p(x)$ obeys
+\begin{equation}
+p(x) \propto x^{-\alpha}
+\label{Pow_Law}
+\end{equation}
+with an exponent $\alpha>0$.
+Note that for this distribution to be properly normalized, one needs to set a lower (upper) bound $x_{\rm min.}$($x_{\rm max.}$) if $\alpha \geq 1$ ($\alpha \leq 1$).
+This family of distributions is of particular interest with respect to the fact that the ``long tail" of the distribution contains a significant portion of the total normalized integral of the probability density function.
+In other words, the probability of the appearance of exceptionally large values of $x$ can not be regarded as insignificant.
+Analyses of empirical data that is believed to obey a power-law distribution thus usually focus on the statistics of rare large events.
+
+In our case of synaptic lifetimes, this raises a practical problem: Measuring lifetimes over a finite total simulation time leads to a fallow of probability for larger lifetimes.
+Furthermore, synapses whose lifetimes \emph{could} have been potentially longer but were simply terminated by the end of the simulation will cause a bunching and over-representation of lifetimes within the time range given by the total simulation time.
+There exists no general solution for the first problem other than running longer simulations.
+The second problem could be tackled by only including synapses into the statistics which terminated before the end of the simulation, though this of course reduces the size of the dataset.
+Practically, we accounted for this by only including lifetime periods into the statistics that explicitly contained an ``on-off" transition in the end.
+
+Another question regarding the data
+
+Still, estimating an power-law exponent based on the given data required setting an upper and lower limit over which
+
  This feature was preserved under diffusive homeostasis, as shown in Figure \ref{Syn_Lifetimes}.

### 2017-03-08 draft.tex
.

@@
 
-\subsubsection{Synaptic Lifetimes}
+\subsubsection{Synaptic Lifetimes}\label{Section_Syn_Lifetimes}
 Synaptic lifetimes have been shown to approximately follow a power law distribution in earlier versions of LIF-SORN and binary SORN \cite{SORN_Paper,Pengsheng_2013}.
 Power law distributions appear in different areas of natural and social sciences \cite{Gabaix_1999,Pascual_2002,Kagan_2010}.
-Some quantity $x$ is said to be power law distributed if its distribution $p(x)$ obeys
-\begin{equation}
-p(x) \propto x^{-\alpha}
+Some quantity $x$ is said to be power law distributed if its distribution $\mathrm{p}(x)$ obeys
+\begin{equation}
+\mathrm{p}(x) = C x^{-\alpha}
 \label{Pow_Law}
 \end{equation}
-with an exponent $\alpha>0$.
+with an exponent $\alpha>0$ and $C$ an appropriate normalization.
 Note that for this distribution to be properly normalized, one needs to set a lower (upper) bound $x_{\rm min.}$($x_{\rm max.}$) if $\alpha \geq 1$ ($\alpha \leq 1$).
@@
 
-Another question regarding the data
+Another question we faced was which method of estimating the power-law exponent to use. Since taking the logarithm of Equation \eqref{Pow_Law} yields
+\begin{equation}
+\mathrm{ln}(\mathrm{p}) = \mathrm{ln}(C) - \alpha \mathrm{ln}(x) \; ,
+\label{Pow_Law_Log} 
+\end{equation}
+the most naive approach one could choose is to generate a histogram of the lifetimes, transform it into a log-log space and estimate the exponent via the slope of a straight line acquired via linear regression.
+Though this might seem to be a straight-forward procedure, it has been argued that it can easily lead to wrong estimates due to large systematic errors, and common error estimates of the regression cannot be trivially interpreted \cite{Bauke_2007,Clauset_2009}.
+Clauset et al.
+have shown that the method of maximum likelihood estimation (MLE) provides a better framework for extracting power-law exponents \cite{Clauset_2009}.
+The basic idea of a MLE is to construct a family of probability density functions (PDF) $\rm f \left( \cdot| \left( \theta_0,\theta_1,...
+\right) \right)$ by means of one or more parameters $\theta_i$ one wishes to estimate \cite{EncyMath_Max_Like}.
+In the case of a power law, the family of PDFs would be characterized by the single exponent $\alpha$ and the function given in Equation \eqref{Pow_Law}.
+This parameter is then said to best characterize a given set of data points $(x_0,...,x_n)$ if its value $\alpha_{\rm max.}$ maximizes the joint probability of finding (or measuring) these data points under the assumption that they are independent and identically distributed according to $\rm f(x_i|\alpha)$.
+The expression one needs to maximize with respect to $\alpha$ is thus given by
+\begin{equation}
+\rm p_{\rm joint}(\alpha) = f(x_0|\alpha)f(x_1|\alpha)...f(x_n|\alpha) \; .
+\label{Joint_Prob_Pow_Law}
+\end{equation}
+Ideally, an analytic expression for finding the maximum for the given set of data points exists.
+Otherwise, numerical optimization methods have to be used.
+For a continuous power-law PDF, such an expression indeed exists:\begin{equation}
+\alpha_{\rm max.} = 1 + n \left[ \sum_{i=1}^n \mathrm{ln}\frac{x_i}{x_{\rm min.}} \right]^{-1}
+\end{equation}
+where $n$ is the number of data points and $x_{\rm min.}$ the smallest observed value \cite{Clauset_2009}.
+This equation does not apply for the discrete variant of a power-law distribution, where only integer values can be observed.
+Unfortunately, tracking synaptic connections in our network only allowed us to check the state of the connections once per second.
+Therefore, our dataset indeed only consists of integer multiples of one second.
+Numerical methods thus had to be used for proper estimation of the exponent.
+
+We made use of the \textit{powerlaw python package} for this purpose \cite{Powerlaw_Package,Alstott_2014}.
+It provides a toolset for the analysis of potentially power-law distributed data, applying the maximum likelihood method as described by Clauset et al.
+\cite{Clauset_2009}.
+An additional feature of this package---also originally proposed by Clauset et al.---is the possibility to automatically find a lower bound $x_{\rm min.}$ below which data points are discarded from the analysis, based on the goodness of the estimated power law to the actual data.
+The authors argue that this feature accounts for the possibility that smaller values of a dataset might not as strictly follow a power law as found in the tail of the distribution.
+This optimization is based on the Kolmogorov-Smirnov statistic, which is the maximum absolute distance $d_{\rm max}$ between the empirical cumulative distribution function of the data and the cumulative distribution function of the analytic prediction.
+It can be further used to perform a statistical test, allowing a judgment whether a given dataset of random variables was generated from the given PDF \cite{EncyMath_Kolmogorov_Smirnov}.
+For the sake of finding the optimal value of $x_{\rm min.}$ however, the authors simply minimize $d_{\rm max}$ in order to find the best fitting setting.
 
@@
 %%% plot_syn_lifetimes.py
-\includegraphics[width=\textwidth]{../../plots/syn_topology/syn_lifetimes.png}
+\includegraphics[width=\textwidth]{../../plots/syn_topology/syn_lifetimes_new.png}
 \caption{Distribution of lifetimes of recurrent excitatory synaptic connections.
-Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a slope of $\mathrm{-1.87}$ for diffusive homeostasis and $\mathrm{-1.68}$ for non-diffusive homeostasis.}
+Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a power-law exponent of $\mathrm{\alpha_{\rm Diff.} = -1.455}$ (standard error $\mathrm{\sigma_{\rm Diff.} = 5.52 \cdot 10^{-4}}$) for diffusive homeostasis and $\mathrm{\alpha_{\rm Non-Diff.} = -1.468}$ (standard error $\mathrm{\sigma_{\rm Non-Diff.} = 5.70 \cdot 10^{-4}}$) for non-diffusive homeostasis.}
 \label{Syn_Lifetimes}
@@
 A comparison of statistics generated with shuffled versions of the weight matrices illustrates that above-chance exceptionally strong mean outgoing weights were indeed present.
-To check for statistical significance, we performed a two-sample Kolmogorov-Smirnov tests between all datasets depicted in Figure \ref{Out_Weight_Mean_Quantile}.
-This statistical test allows to compare the empirical distribution functions of two sets of random variables by means of .
-More specifically, the null hypothesis states that both sets share the same underlying probability function.
+To check for statistical significance, we performed a two-sample Kolmogorov-Smirnov test between all datasets depicted in Figure \ref{Out_Weight_Mean_Quantile}.
+It is based on the same principle as the one-sample Kolmogorov-Smirnov test used in Section \ref{Section_Syn_Lifetimes}.
+The only difference is that two empirical cumulative distributions are compared instead of comparing one empirical dataset to a given analytical function.
+The null hypothesis of the test states that both sets share the same underlying probability function.
 Thus, in our case, there should be a high statistical significance towards the rejection of this hypothesis.

### 2017-03-09 draft.tex
.

@@
 
-\subsubsection{Former Single-Cell Homeostasis as an Integral Control}
+\subsubsection{Single-Cell Homeostasis as an Integral Control}
 Former versions of the LIF-SORN and SORN used a simple form of integral control to regulate excitatory firing rates.
@@
 We found that we can retain a log-normal-like distribution in combination with diffusive homeostasis, giving a similar distribution as for non-diffusive homeostasis.
+Both distributions were slightly left-skewed ($\mathrm{v_{\rm diff.} = -1.21}$,$\mathrm{v_{\rm non-diff.} = -1.44}$).
 \begin{figure}
@@
 \caption{Distribution of decadic logarithm of excitatory synaptic weights at $\mathrm{t=1500\,s}$ for diffusive and non-diffusive homeostasis (both with distance-dependent connectivity).
-Gaussian fits returned $\mathrm{\mu_{\rm diff.}=-0.128\, \mathrm{log}_{10}(mV)}$, $\mathrm{\mu_{\rm non-diff.}=-0.064\, \mathrm{log}_{10}(mV)}$, $\mathrm{\sigma_{\rm diff.}=0.415\, log_{10}(mV)}$ and $\mathrm{\sigma_{non-diff.}=0.395\, log_{10}(mV)}$.
+Gaussian fits (non-linear least squares) returned $\mathrm{\mu_{\rm diff.}=-0.128\, \mathrm{log}_{10}(mV)}$, $\mathrm{\mu_{\rm non-diff.}=-0.064\, \mathrm{log}_{10}(mV)}$, $\mathrm{\sigma_{\rm diff.}=0.415\, log_{10}(mV)}$ and $\mathrm{\sigma_{non-diff.}=0.395\, log_{10}(mV)}$.
 Weight matrices were taken from 5 simulations, each at $\rm t = 1500\,s$.}
@@
 The authors argue that this feature accounts for the possibility that smaller values of a dataset might not as strictly follow a power law as found in the tail of the distribution.
-This optimization is based on the Kolmogorov-Smirnov statistic, which is the maximum absolute distance $d_{\rm max}$ between the empirical cumulative distribution function of the data and the cumulative distribution function of the analytic prediction.
+This optimization is based on the Kolmogorov-Smirnov statistic, which is the maximum absolute distance $d_{\rm max.}$ between the empirical cumulative distribution function of the data and the cumulative distribution function of the analytic prediction.
 It can be further used to perform a statistical test, allowing a judgment whether a given dataset of random variables was generated from the given PDF \cite{EncyMath_Kolmogorov_Smirnov}.
-For the sake of finding the optimal value of $x_{\rm min.}$ however, the authors simply minimize $d_{\rm max}$ in order to find the best fitting setting.
-
-Still, estimating an power-law exponent based on the given data required setting an upper and lower limit over which
-
-This feature was preserved under diffusive homeostasis, as shown in Figure \ref{Syn_Lifetimes}.
-The resulting slopes are within previously reported values of $\mathrm{\approx - 5/3}$ \cite{SORN_Paper}.
+For the sake of finding the optimal value of $x_{\rm min.}$ however, the authors simply minimize $d_{\rm max.}$ in order to find the best fitting setting.
+
+Observing the distribution of synaptic lifetimes, we found that fitting a power law to the simulation data would rather require to define an \emph{upper} bound $x_{\rm max.}$ than a lower one, since we observed a falloff from the linear behavior in a log-log plot for large synaptic lifetimes, see Figure \ref{Syn_Lifetimes}.
+The \textit{powerlaw package} allows manually setting an upper bound, but the optimization described before is only available for $x_{\rm min.}$.
+We therefore decided to manually implement the same approach for $x_{\rm max.}$, while keeping the lower bound fixed at $x_{\rm min.} = 1 \, s$.
+We swept through values for $x_{\rm max.}$ within $\mathrm{2\,s} \leq x_{\rm max.} \leq \mathrm{750\,s}$, with $\rm 750 \, s$ being the maximal possible synaptic lifetime to be recorded.
+We estimated the power-law exponent with the aforementioned package for each value of $x_{\rm max.}$ and calculated $d_{\rm max.}$.
+The value of $x_{\rm max.}$ resulting in the smallest $d_{\rm max.}^{min.}$ was then picked for the final estimation of $\alpha$.
+We did expect $d_{\rm max.}$ to go through a minimum for a certain value of $x_{\rm max.}$ and to increase again due to the statistical deviations for long lifetimes.
+We did not observe this behavior, however.
+Instead, $d_{\rm max.}$ was monotonically decreasing but converging.
+Therefore, we actually found its minimal value for $x_{\rm max.} = \rm 750 \, s$ for both diffusive homeostasis and non-diffusive homeostasis ($d_{\rm max.,diff.}^{min.} = 0.30$,$d_{\rm max.,non-diff.}^{min.} = 0.34$).
+We thus accepted the values for $\alpha$ acquired by MLE for both entire datasets as valid, yielding $\mathrm{\alpha_{\rm diff.} = -1.455}$ and $\mathrm{\alpha_{\rm don-diff.} = -1.468}$.
+The resulting exponents are slightly smaller than previously reported values of $\mathrm{\approx - 5/3}$ \cite{SORN_Paper}.
 \begin{figure}
@@
 \caption{Distribution of lifetimes of recurrent excitatory synaptic connections.
-Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a power-law exponent of $\mathrm{\alpha_{\rm Diff.} = -1.455}$ (standard error $\mathrm{\sigma_{\rm Diff.} = 5.52 \cdot 10^{-4}}$) for diffusive homeostasis and $\mathrm{\alpha_{\rm Non-Diff.} = -1.468}$ (standard error $\mathrm{\sigma_{\rm Non-Diff.} = 5.70 \cdot 10^{-4}}$) for non-diffusive homeostasis.}
+Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a power-law exponent of $\mathrm{\alpha_{\rm diff.} = -1.455}$ (standard error $\mathrm{\sigma_{\rm diff.} = 5.52 \cdot 10^{-4}}$) for diffusive homeostasis and $\mathrm{\alpha_{\rm don-diff.} = -1.468}$ (standard error $\mathrm{\sigma_{\rm don-diff.} = 5.70 \cdot 10^{-4}}$) for non-diffusive homeostasis.}
 \label{Syn_Lifetimes}
@@
 \end{equation}
-The term $\mathrm{t^{-3/2}}$ dominates for larger $\mathrm{t}$, which very roughly resembles the power-law exponents found in Figure \ref{Syn_Lifetimes}.
+The term $\mathrm{t^{-3/2}}$ dominates for larger $\mathrm{t}$, which approximately resembles the power-law exponents found in Figure \ref{Syn_Lifetimes}.
 Zheng et al.
@@
 
-We noted further that the difference between shuffled matrices corresponding to non-diffusive and diffusive homeostasis is in line with our observation from Figure \ref{Weight_Dist}, which indicated a broader distribution of weights for diffusive homeostasis.
 \begin{figure}
@@
 Figure \ref{dynamics_rate_threshold_dyn_mean_field_sweeney} depicts the resulting dynamics of excitatory rates and thresholds for $\mathrm{\alpha=\lbrace 0.5,0.9,1.0\rbrace}$.
-We ran simulations with other values of $\rm \alpha$ and found that all rates approach the same target rate of $\mathrm{3\,Hz}$ and thresholds move towards the same configuration for either choice of $\mathrm{\alpha}$ except for the limiting case of $\mathrm{\alpha=1}$.
-A significant difference only exists within the transient dynamics leading to the steady state.
-Roughly speaking, a smaller value of $\mathrm{\alpha}$ leads to a faster relaxation.
+We ran simulations with other values of $\rm \alpha$ and found that all rates approached the same target rate of $\mathrm{3\,Hz}$ and thresholds moved towards the same configuration for either choice of $\mathrm{\alpha}$ except for the limiting case of $\mathrm{\alpha=1}$.
+A significant difference only existed within the transient dynamics leading to the steady state.
+Roughly speaking, a smaller value of $\mathrm{\alpha}$ led to a faster relaxation.
 \begin{figure}
@@
 \section{Discussion}
+The investigations and results presented within this thesis should be contextualized within two topics of research: First, the dynamic properties and mechanisms of neural homeostasis and how concepts of control theory should be applied to properly model activity regulation in the brain.
+And second, if, and if so, how much the particular distribution of firing rates present within a network affects neural plasticity and structure.
+The focus of this thesis was put onto the first topic.
+In the introduction, we laid out the conceptual problems of single-cell homeostasis in the context of linear control theory.
+Though some experimental results suggested that individual homeostatic targets might be a reasonable theoretic approach \cite{OConnor_2010,Mizuseki_2013,Hengen_2016}, we wanted to find a possibility of achieving a broad and heavy-tailed distribution of firing rates and stable network activity without the need to artificially tune individual homeostatic targets to fit the desired distribution.
+By introducing the notion of diffusive homeostasis, Sweeney et al.
+provided a theoretical approach that seemed to fulfill this demand.
+A large part of our research thus focused on the analysis of the dynamics and statistics of network activity that resulted from implementing the mechanism introduced in \cite{Sweeney_Paper}.
+
+The second part of our investigations consisted of checking for possible effects of greater firing-rate heterogeneity onto the network topology, based on findings of earlier research on the SORN.
+It has been claimed that the mechanisms included in the SORN and LIF-SORN constitute a minimal set of rules required for the emergence of non-random topological features and spine-size dynamics resembling experimental data \cite{SORN_Paper,Pengsheng_2013}.
+We thus aimed for preserving these features under diffusive homeostasis.
+
+We shall now discuss the presented results in further detail in the following sections.
 
@@
 Predictions about the resulting activity are then made based on (potentially simplified) statistical features of recurrent connectivity and the specific form of the neuronal transfer function used in the model, see e.g.
-\cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998}.
+\cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998,Koulakov_2009}.
 Our interpretation of our results leads to the conclusion that this canonical approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behavior.
@@
 \subsection{Network Topology}
-Even though our investigations on network topology were rather intended as a form of sanity check with respect to properties already found in earlier versions, we found some differences compared to non-diffusive homeostasis.
-
-\subsubsection{Distribution of Weights}
-In Section \ref{Syn_Weight_Dist_Section}, we presented our results regarding the distribution of weights, which turned out to be broader but still approximately log-normal distributed for diffusive homeostasis.
-As a first interpretation, we hypothesized that this might due to a slightly decreased amount of STDP-induced potentiation (Figure \ref{STDP_change}) in the case of diffusive homeostasis in the first half of the simulation.
-Another explanation one might consider is that the increased firing rate for some neurons in the case of diffusive homeostasis lead to a greater amount of fluctuation because of the increased amount of STDP-events.
-However, since the overall variance of STDP-induced fluctuations was not significantly higher but even slightly lower compared to non-diffusive homeostasis, this explanation seems rather unlikely.
-
-Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist} we noted that the increased width of the distribution is largely due to an increment on the left half of the curve.
-Since new weights are initialized at $\mathrm{10^{-4}\, mV}$ this might indicate that some weights are drifting much more slowly from their value of initialization compared to other weights.
-These ``slow drifters" are presumably connecting neurons both spiking at a below-average firing rate.
-This provides an explanation why this effect is more present in the case of diffusive homeostasis since it causes a portion of neurons to have rather low firing rates.
-On the other hand, for non-diffusive homeostasis, one can assume that the amount of STDP-fluctuations is approximately equal for all recurrent excitatory weights because of the fixation of firing rates.
+
+\subsubsection{Robustness of Synaptic Weight- and Lifetime Statistics}
+The results of section \ref{Syn_Weight_Dist_Section} and \ref{Section_Syn_Lifetimes} have shown that both features, log-normal distribution of synaptic weights and a power-law distribution of synaptic lifetimes, can be reliably reproduced under our new homeostatic model.
+Relating this to the main result of Section \ref{Fir_Dist_Section}, it does not appear to be the case that a greater heterogeneity of firing activity has a significant influence onto the overall statistics of neural connectivity (though on a more detailed level, structural differences could be observed, as discussed in the next Section).
+
+The precise spiking activity of neurons does certainly influence weight dynamics due to STDP and learning processes in the brain depend on this relation between neural activity and synaptic structure.
+However, one might doubt that this non-randomness on a small scale is required to explain overall statistical features of neural connectivity.
+As mentioned in Section \ref{Syn_Weight_Dist_Section}, theoretical models based on stochastic processes were able to give an explanation for the presence of log-normal weight distributions \cite{Loewenstein_Spine_Sizes,Statman_Synapses_2014}.
+Individual spikes in this context rather act as initiators of approximately random additive changes of synaptic efficacy.
+Since diffusive homeostasis kept the population activity at the same value of $\rm 3\, Hz$ as for non-diffusive homeostasis, the amount of additive weight changes due to STDP is the same.
+Treating STDP-events as random, this equality gives an idea of why no significant statistical differences could be observed for weight distributions and synaptic lifetimes.
+
+On the other hand, persistent differences within firing rates did indeed lead to noticeable topological difference that shall be discussed in the following section
 
 \subsubsection{Strong Differences in Outgoing Weights}
-The most prominent difference between homeostatic mechanisms we found within network topology was the emergence of significantly above-average mean outgoing weights for a small subset of neurons.
-By comparing the given mean values to statistics acquired by randomly shuffling recurrent excitatory weights (see Figure \ref{Out_Weight_Mean_Quantile}), we found that this effect cannot be explained by the overall increase of weight heterogeneity that we discussed in the previous section.
+Even though our investigations on network topology were rather intended as a form of sanity check with respect to properties already found in earlier versions, we found a differences compared to non-diffusive homeostasis:
+The emergence of significantly above-average mean outgoing weights for a small subset of neurons, see section \ref{Section_Mean_outgoing_Weights}.
+By comparing the given mean values to statistics acquired by randomly shuffling recurrent excitatory weights and running a statistical test(see Figure \ref{Out_Weight_Mean_Quantile}), we found that this effect is indeed significant compared to chance.
 Thus, we identify the over-representation of strong outgoing weights as a non-random effect.

### 2017-03-10 draft.tex
.

@@
 
+\usepackage[titletoc]{appendix}
+
 \captionsetup[table]{singlelinecheck=false}
@@
 
-\subsubsection{The Role of Firing Rate Heterogeneity---a Dichotomy between Heterogeneity and Control?}
+\subsubsection{The Role of Firing Rate Heterogeneity---a Dichotomy between Heterogeneity and Control?}\label{Section_Role_Fir_Rate_Het}
 Modeling homeostasis necessarily includes a form of error estimation, which requires setting some predefined target that the feedback control will attempt to achieve.
@@
 \end{equation}
-Since we assumed the noise term $\xi$ to be approximately white and gaussian noise with unit variance, its power spectrum is $|f_{\xi}|^2 = 1$.
+Appendix \ref{Appendix_Power_Spectrum} contains the full calculation.
 
@@
 Diffusive homeostasis indeed results in a much broader distribution of mean firing rates.
-As mentioned in the introduction, a large number of experimental studies have found that distributions of firing rates are not only broadly distributed but well described by a log-normal distribution, which has a non-zero third moment or skewness.
+As mentioned in Section \ref{Section_Role_Fir_Rate_Het}, a large number of experimental studies have found that distributions of firing rates are not only broadly distributed but well described by a log-normal distribution, which has a non-zero third moment or skewness.
 By definition, the logarithm of the random variable in question is thus again normally distributed.
 We plotted the the distribution of decadic logarithms of firing rates in Figure \ref{Fir_Rate_Dist_Compare} (B) to check for this property.
-In (A), we found a skewness of $\mathrm{v_{\rm diff.} = 0.77}$, in (B) $\mathrm{v_{\rm diff.,log} = -0.49}$.
-Though this told us that the distribution is ``more symmetric" on a logarithmic scale, it should rather be seen as being neither strictly normally or log-normally distributed.
+A Gaussian fit of the histogram in log-space (B) fitted the data reasonably well, with a mean $\mu_{\rm diff.,exc.} = \rm 0.152 \pm  0.002\, log_{10}(Hz)$ and a standard deviation of $\sigma_{\rm diff.,exc.} = \rm 0.152 \pm  0.002\, log_{10}(Hz)$.
+In (A), we found a skewness of $\mathrm{v_{\rm diff.,exc.,reg.} = 0.77}$, in (B) $\mathrm{v_{\rm diff.,exc.,log.} = -0.49}$.
+Though this told us that the distribution is ``more symmetric" on a logarithmic scale, the fact that we still find a skewness on the same order as in regular space indicated that it should rather be seen as not perfectly log-normal distributed.
 \begin{figure}
@@
 For diffusive homeostasis ($\mathrm{D=10\, \mu m^2 ms^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
+Green curves are non-linear least-squares Gaussian fit onto the distribution resulting from diffusive homeostasis.
 Mean firing rates were calculated from spikes within $\mathrm{1000-1500\,s}$.}
@@
 \end{figure}
-In contrast, inhibitory cells showed a much clearer distinction: A skewness of $\mathrm{v_{\rm diff.} = 1.52}$ in regular space and $\mathrm{v_{\rm diff.,log} = -0.15}$ in log-space.
+In contrast, inhibitory cells showed a much clearer distinction: A skewness of $\mathrm{v_{\rm diff.,inh.,reg.} = 1.52}$ in regular space and $\mathrm{v_{\rm diff.,inh.,log.} = -0.15}$ in log-space.
+Furthermore, the broadness of firing rates was more pronounced, with a Gaussian fit resulting in $\mu_{\rm diff.,inh.} = \rm 0.793 \pm  0.006\, log_{10}(Hz)$ and $\sigma_{\rm diff.,inh.} = \rm 0.190 \pm  0.006\, log_{10}(Hz)$.
 
@@
 Figure \ref{Fir_Rate_Dist_Instant_compare} shows the distribution for this special limiting case.
-The standard deviation for the excitatory population was $\mathrm{\sigma_{\rm inst.} = 1.79\, Hz}$ and the skewness $\mathrm{v_{\rm inst.} = 1.51}$ ($\mathrm{v_{\rm inst.,log} = -0.52}$), which makes the asymmetry slightly more pronounced than in Figure \ref{Fir_Rate_Dist_Compare}.
+The standard deviation for the excitatory population was $\mathrm{\sigma_{\rm inst.,reg.} = 1.79\, Hz}$ ($\mathrm{\sigma_{\rm inst.,log.} = 0.28\, log_{10}(Hz)}$) and the skewness $\mathrm{v_{\rm inst.,reg.} = 1.51}$ ($\mathrm{v_{\rm inst.,log} = -0.52}$), which makes the asymmetry slightly more pronounced than in Figure \ref{Fir_Rate_Dist_Compare}.
 \begin{figure}
@@
 \caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population.
+Red curves are least-squares Gaussian fits ($\mu_{\rm exc.} = \rm 0.420 \pm  0.006\, log_{10}(Hz)$, $\sigma_{\rm exc.} = \rm 0.254 \pm  0.006\, log_{10}(Hz)$, $\mu_{\rm inh.} = \rm 0.761 \pm  0.007\, log_{10}(Hz)$, $\sigma_{\rm inh.} = \rm 0.233 \pm  0.007\, log_{10}(Hz)$).
 Data was taken from 10 simulations and $\mathrm{1000\,s \leq t \leq 1500\,s}$.}
@@
 However, we did not find a distribution as right skewed and heavy tailed as reported by Sweeney et al.
-and numerous experimental studies.
+Though we will argue in Section \ref{Matrix_Diff_Model_Section} that the quenched random structure of the neurons' positions plays an important role in shaping the distribution of firing rates as well, a potential explanation might be the fact that Sweeney et al.
+did not impose postsynaptic normalization onto their (static) recurrent excitatory connections, which were randomly generated.
+A balanced state was achieved by a global scaling factor between excitatory and inhibitory conductances.
+Therefore, some neurons could potentially be driven by significantly more (or less) synaptic input currents than on average, allowing for greater heterogeneity of firing rates.
 
@@
 \end{figure}
+
+Experimental studies have not only considered the presence of neurons with strong influence onto other neurons \cite{Eckmann_Leader_Neurons_2008}, but also found evidence that highly active neurons form subnetworks with an increased connectivity, in the sense that these cells were more likely than average to connect to each other, see \cite{Yassin_Subnetworks_2010}.
+We tested this in our network by evaluating the connection fraction $\rm CF_{diff.,leader}$ among the top 10\% of excitatory neurons with respect to their average firing rate within $\rm 1000\,s < t < 1500\,s$ and comparing it to the rest of the excitatory population and the same calculation for the non-diffusive case.
+This returned $\rm CF_{diff.,leader} = 0.1371 \pm 0.0061$, $\rm CF_{diff.,non-leader} = 0.0982 \pm 0.0013$, $\rm CF_{non-diff.,leader} = 0.0954 \pm 0.0044$ and $\rm CF_{non-diff.,non-leader} = 0.0992 \pm 0.0002$.
+Standard errors were calculated from 5 simulation runs for each homeostatic mechanism, and connectivity matrices were taken from $\rm t = 1500\,s$.
+This showed that connectivity is indeed increased among the fastest-firing neurons 10\% in the case of diffusive homeostasis.
+Effenberger et al.
+reported a similar effect, though differences of connectivity were even more pronounced \cite{Effenberger_2015}.
 
@@
 
-As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}) we found that neurons with a low-density neighborhood have a higher chance of developing these strong outgoing weights.
+Though theoretical and experimental studies have reported similarly about the presence of exceptionally ``ìnfluential" neurons \cite{Effenberger_2015,Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}, a lack of a clear concept of ``leader neurons" makes comparisons difficult and should be made with care.
+On the one hand, one could refer to the finding, that some neurons are more effective in terms of local spike initiation or bursting \cite{Eckmann_Leader_Neurons_2008}.
+The presence of stronger outgoing weights for some excitatory neurons and an increment of pre-post spiketime correlations within the excitatory population generally support this finding.
+On the other hand, another aspect one could conceptually associate to ``driver neurons" is the presence of subnetworks of highly active neurons with stronger connectivity \cite{Yassin_Subnetworks_2010}.
+Though we did find evidence that the connection fraction of a subpopulation of fast-spiking neurons was increased, the meaning and implication of this effect on a functional level needs more investigation.
+As mentioned in Section \ref{Section_Role_Fir_Rate_Het}, it has been argued that the combination of a large group of slowly firing neurons, which subject to stronger neuronal rewiring, and a small group of fast-firing neurons, forming more stable connections, is required to allow the brain to efficiently process and transmit information while being able to undergo longer lasting learning processes, which require plastic changes in the network structure \cite{Dragoi_2003,Buzsaki_2004,Buzsaki_Fir_Rates_2014}.
+Thus, one might consider testing the performance of learning tasks that had previously been investigated using the SORN and LIF-SORN under diffusive homeostasis.
+Potentially, this would allow the network to use the number of available nodes in a more efficient way.
+
+As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}) we found that neurons with a low-density neighborhood have a higher chance of developing strong outgoing weights.
 Since this effect is directly linked to the low-density/high-firing-rate relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that synapses with above-average firing presynaptic neurons tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
@@
 \section{Conclusion and Outlook}\label{Conclusion_Section}
-Drawing a conclusion from our results presents itself as a somewhat ambiguous task.
-On a phenomenological level, our main goal of allowing the LIF-SORN to exhibit a broad, skewed distribution was achieved.
-However, whether the implications of the diffusive model that revealed itself upon deeper investigations are acceptable in terms of biological plausibility is still left open to debate.
-
-Our analysis of the of the feedback control has shown that the dynamics of the system can be approximately described in a linearized way.
-As we have speculated in Section \ref{Possible_Modifications_Section}, a better model of homeostatic feedback might eventually require the introduction of nonlinearity, at the cost of a harder to analyze and predict behavior.
-
-From a topological point of view, the implementation of homeostasis can be regarded as a success: Thanks to the broad range of neural activity it allowed for the emergence of highly influential subgroups of excitatory neurons.
-This---experimentally confirmed---feature was not present in earlier versions of the LIF-SORN.
-It thus can be regarded as another non-random property of cortical structure that was not hard-coded but naturally emerged from the set of basic rules that constitute dynamics and behavior of our network.
-
-With respect to future use and implementation of diffusive homeostasis one might desire to cover the essential effects in a more simple and abstract formalism.
+Our main goal of implementing diffusive homeostasis was to allow a broad distribution of firing rates across the excitatory population of the LIF-SORN, since experimental research has shown this to be a extensively observable phenomenon in the cortex.
+The implementation of diffusive homeostasis can be regarded as a success with respect to this feature.
+Furthermore, we did not observe any breakdown of previously studied desirable features of network topology, emerging from the plasticity mechanisms included.
+
+The fact that unwanted oscillations appeared on the first attempts of running the network with diffusive homeostasis forced us to better understand the dynamics of the feedback control and allowed us to contextualize the results into other theoretical research on the stability of neural homeostasis.
+
+Our theoretical considerations regarding the steady state of firing activity allowed us to further clarify the actual determinants of the resulting firing rate statistics.
+It turned out that, depending on the choice of diffusion parameters, a weighted mixture between the distribution of neural inputs and the spatial configuration determines the resulting statistics of firing rates.
+The former aspect is in line with common theoretical approaches of explaining firing rate distributions.
+The latter aspect can be subsumed by the hypothesis that local fluctuations of neural density can influence firing rates and shape their overall distribution.
+This was a rather unconventional idea, and we had to leave the question of biological plausibility unanswered.
+
+The implementation of diffusive homeostasis led to an interesting observation regarding network structure: Due to the broad range of neural activity it allowed for the emergence of highly influential subgroups of excitatory neurons.
+This feature was not present in earlier versions of the LIF-SORN.
+It can be regarded as another non-random property of cortical structure that was not hard-coded but naturally emerged from the set of basic rules that constitute dynamics and behavior of our network.
+As stated earlier, future research should investigate whether this effect also influences the performance of the SORN in learning tasks.
+
+With respect to future use and implementation of diffusive homeostasis one might also desire to cover the essential effects in a more simple and abstract formalism.
 As shown in Section \ref{Mean_Field_Review_Section}, a simple mean field model as presented by Sweeney et al.
@@
 \clearpage
+
 \bibliography{test_base}
 \bibliographystyle{unsrt}
+
+\clearpage
+
+\begin{appendices}
+
+\section{Full Derivation of the Power Spectrum given in Equation \eqref{Pow_Spec_Theta_Final}}\label{Appendix_Power_Spectrum}
+Starting with the dynamic equations
+\begin{align}
+\dot{n} &= -\lambda n + \frac{\gamma \alpha N_{\rm exc.}}{L^2}\theta + \sigma_{NO} \xi(t) \label{Appendix_Equation_1}\\
+\dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{Appendix_Equation_2}
+\end{align}
+taking the Fourier transform yields
+\begin{align}
+i\omega f_n &= - \lambda f_n + \frac{\gamma \alpha N_{\rm exc.}}{L^2}f_\theta + \sigma_{NO} f_{\xi} \label{Appendix_Equation_3} \\
+i\omega f_\theta &= \frac{f_n}{NO_0\tau_{V_t}}\;. \label{Appendix_Equation_4}\\
+\end{align}
+We solve Equation \eqref{Appendix_Equation_4} for $f_n$:
+\begin{equation}
+f_n = i\omega NO_0 \tau_{V_t} f_\theta \label{Appendix_Equation_5}
+\end{equation}
+Substituting into Equation \eqref{Appendix_Equation_3} gives
+\begin{equation}
+-\omega^2 NO_0 \tau_{V_t} f_\theta = - i\omega NO_0 \tau_{V_t} \lambda f_\theta + \frac{\gamma \alpha N_{\rm exc.}}{L^2}f_\theta + \sigma_{NO} f_{\xi} \; . \label{Appendix_Equation_6}
+\end{equation}
+Solving for $f_\theta$ results in
+\begin{equation}
+f_\theta = \frac{\sigma_{NO} f_{\xi}}{i\omega NO_0 \tau_{V_t} \lambda - \left(\omega^2 NO_0 \tau_{V_t} + \frac{\gamma \alpha N_{\rm exc.}}{L^2} \right)} \; . \label{Appendix_Equation_7}
+\end{equation}
+The squared absolute value of this expression is the power spectrum $P_\theta$:
+\begin{equation}
+P_\theta (\omega) = |f_\theta|^2 = \frac{\sigma_{NO}^2}{\omega^2 NO_0^2 \tau_{V_t}^2 \lambda^2 + \left( \omega^2 NO_0 \tau_{V_t} + \frac{\gamma \alpha N_{\rm exc.}}{L^2}\right)^2} \label{Appendix_Equation_8}
+\end{equation}
+Note that since we assumed the noise term $\xi$ to be approximately white and Gaussian noise with unit variance, its power spectrum is $|f_{\xi}|^2 = 1$
+
+\end{appendices}
+
 \end{document}

### 2017-03-11 draft.tex
.

@@
 \usepackage[titletoc]{appendix}
-
 \captionsetup[table]{singlelinecheck=false}
 \captionsetup[figure]{singlelinecheck=false}
+
 \author{Fabian Schubert}
@@
 \clearpage
+
 \setcounter{page}{1}
+
+\section*{Glossary}
+\bigskip
+\begin{minipage}{0.33\textwidth} 
+$\rm Ca^{2+}$\\
+CDF\\
+CF\\
+CNS\\
+CV\\
+IP\\
+ISI\\
+$\rm K^{+}$\\
+LIF\\
+LTD\\
+LTP\\
+L5\\
+MLE\\
+nNOS\\
+NO\\
+PDF\\
+SORN\\
+STD\\
+STDP\\
+STF\\
+STP
+\end{minipage}
+\hfill
+\begin{minipage}{0.66\textwidth}
+ionic calcium\\
+cumulative distribution function\\
+connection fraction\\
+central nervous system\\
+coefficient of variation\\
+intrinsic plasticity\\
+interspike interval\\
+ionic potassium\\
+leaky-integrate-and-fire\\
+long-term depression\\
+long-term potentiation\\
+layer five of the mammalian neocortex\\
+maximum likelihood estimation\\
+neural nitric oxide synthesis\\
+nitric oxide\\
+probability density function\\
+self-organizing recurrent neural network\\
+short-term depression\\
+spike-timing-dependent plasticity\\
+short-term facilitation\\
+short-term plasticity
+\end{minipage}
+
+\clearpage
+
+\listoffigures
+
+\clearpage
+
+\listoftables
+
+\clearpage
 
@@
 \end{center}
-\caption{Schematic illustration of a closed loop control as described in Section \ref{Control_Sys_Theo_Section}}
+\caption[Schematic illustration of a closed loop control]{Schematic illustration of a closed loop control as described in Section \ref{Control_Sys_Theo_Section}}
 \label{Closed_Loop_Control_Illustration}
@@
 \begin{table}
+\caption{Parameters of synaptic connections.}
 \begin{tabu}{|l|l|l|l|l|}
@@
 \end{tabu}
-\caption{Parameters of synaptic connections.}
 \label{syn_conn_params}
@@
 \begin{table}[H]
+\caption{Parameters of LIF neuron}
 \begin{tabu}{|l|l|l|}
@@
 \end{tabu}
-\caption{Parameters of LIF neuron}
 \label{LIF_neuron_params}
@@
 
-Finally, the dynamics of firing thresholds $V_{t,i}$ were modeled such that the rate of change is proportional to the relative deviation of $NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
+Finally, the dynamics of firing thresholds $V_{t,i}$ were modeled such that the rate of change is proportional to the relative deviation of $\rm NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
 
@@
 \begin{table}
+\caption{Parameters of homeostatic intrinsic plasticity.}
 \begin{tabu}{|l|l|}
@@
 \end{tabu}
-\caption{Parameters of homeostatic intrinsic plasticity.}
 \label{Params_IP}
@@
 
-3.) Dirichlet boundary conditions with $NO = NO_{bound}$ at the boundaries.\\
+3.) Dirichlet boundary conditions with $NO = NO_{\rm bound.}$ at the boundaries.\\
 Neumann boundary conditions were used for most of the simulations if not explicitly marked differently.
@@
 Both homeostatic mechanisms managed to keep the excitatory population activity in the desired range of 3 Hz.
-However, what might appear to be slightly faster and stronger random fluctuations in panel A-C were in fact regular oscillations across all three depicted variables, as can be seen in panel A*-C*, showing the dynamics in a smaller time window.
+However, what might appear to be slightly faster and stronger random fluctuations in panel A--C were in fact regular oscillations across all three depicted variables, as can be seen in panel A*--C*, showing the dynamics in a smaller time window.
 While the oscillation amplitudes undergo a rather unpredictable course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
@@
 %\includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_closeup.png}
-\caption{A/A*: Mean of excitatory (blue) and inhibitory (red) neuronal firing rate.
+\caption[Time course of population firing rates, population mean of NO concentration and of excitatory threshold]{A/A*: Mean of excitatory (blue) and inhibitory (red) neuronal firing rate.
 B/B*: NO concentration averaged over readouts at excitatory neurons' positions.
@@
 \includegraphics[width=0.7\textwidth]{../../plots/power_spec/power_spectrum_sim_only.png}
-\caption{Blue: Mean of power spectrum over all excitatory thresholds. Red: Power spectrum of mean over all excitatory thresholds.}
+\caption[Power spectrum of thresholds of excitatory neurons]{Blue: Mean of power spectrum over all excitatory thresholds. Red: Power spectrum of mean over all excitatory thresholds.}
 \label{Power_Spec_without_Analysis}
@@
 Such a limit cycle exists inside a region $R$ if $R$ contains no fixed points and if any trajectory whose starting points lies within $R$ is confined to $R$, according to the Poincaré-Bendixson theorem.
-The second condition is equivalent to the condition that for all points $\mathbf{r}_{edge}$ on the edge of $R$, the vector field $\dot{\mathbf{r}}_{edge}$ is facing into $R$, see \cite[p.~248]{Dyn_Sys_Hirsch}.
+The second condition is equivalent to the condition that for all points $\mathbf{r}_{\rm edge}$ on the edge of $R$, the vector field $\dot{\mathbf{r}}_{\rm edge}$ is facing into $R$, see \cite[p.~248]{Dyn_Sys_Hirsch}.
 This case occurs if the system has a locally unstable fixed point, but a non-linearity that prevents an infinite deviation from the fixed point.
@@
 \end{center}
-\caption{Comparison of mean firing rate of a LIF neuron without noise (squares) and with noise (circles, $\mathrm{\sigma = \sqrt{5}\, mV}$), averaged over $\mathrm{50\, s}$.
+\caption[Comparison of mean firing rate of a LIF neuron without noise and with noise]{Comparison of mean firing rate of a LIF neuron without noise (squares) and with noise (circles, $\mathrm{\sigma = \sqrt{5}\, mV}$), averaged over $\mathrm{50\, s}$.
 Red and blue curves are the corresponding analytic predictions, see equation \ref{LIF_Fir_Rate_no_Noise} and \ref{LIF_Fir_Rate_with_Noise1}.}
@@
 \begin{equation}
-\sigma_{tot.} = \sqrt{\sigma_{\rm intr.}^2 + \sum_A \sigma_{AB}^2} \; .
+\sigma_{\rm tot.} = \sqrt{\sigma_{\rm intr.}^2 + \sum_A \sigma_{AB}^2} \; .
 \label{Total_Noise_Neuron}
@@
 \begin{align}
-x_{st.}(r) &= \frac{1-\exp \left(-\frac{1}{r\cdot \tau _d}\right)}{1-\left(1-u_{st.}\left(r\right)\right)\cdot \exp \left(-\frac{1}{r\cdot \tau _d}\right)} \label{STP_steady1} \\
-u_{st.}(r) &= \frac{U}{1-\left(1-U\right)\exp \left(-\frac{1}{r\cdot \tau _f}\right)} \; .\label{STP_steady2}
-\end{align}
-One thus needs to incorporate the factor $\mathrm{x_{st.}\cdot u_{st.}}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise when trying to find the fixed point of Equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
+x_{\rm st.}(r) &= \frac{1-\exp \left(-\frac{1}{r\cdot \tau _d}\right)}{1-\left(1-u_{st.}\left(r\right)\right)\cdot \exp \left(-\frac{1}{r\cdot \tau _d}\right)} \label{STP_steady1} \\
+u_{\rm st.}(r) &= \frac{U}{1-\left(1-U\right)\exp \left(-\frac{1}{r\cdot \tau _f}\right)} \; .\label{STP_steady2}
+\end{align}
+One thus needs to incorporate the factor $x_{\rm st.}\cdot u_{\rm st.}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise when trying to find the fixed point of Equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
 
@@
 \end{center}
-\caption{Dynamics of equations \ref{2d-exc_inh_rate_1} (blue line) and \ref{2d-exc_inh_rate_2} (red line).
+\caption[Dynamics of rate-based network model]{Dynamics of equations \ref{2d-exc_inh_rate_1} (blue line) and \ref{2d-exc_inh_rate_2} (red line).
 Dotted lines mark the mean frequencies that were present in the full spiking network.
@@
 \end{figure}
-In principle, one could now further quantify the stability of the found fixed point by calculating the Jacobian matrix at $\mathrm{(r_{0,e},r_{0,i})}$.
+In principle, one could now further quantify the stability of the found fixed point by calculating the Jacobian matrix at $(r_{0,e},r_{0,i})$.
 For the sake of the initial question, though, namely the source of oscillation, it is sufficient at this point to restrict oneself to a preliminary result: The recurrent network as such (without homeostasis) is stable under the given choice of parameters, assuming validity of the described rate model.
@@
 \end{center}
-\caption{Time course of the mean firing rate (blue) and the mean firing threshold within the excitatory pool (red). Bin width for firing rate estimation was 0.1 s.}
+\caption[Time course of the mean firing rate and the mean firing threshold within the excitatory pool]{Time course of the mean firing rate (blue) and the mean firing threshold within the excitatory pool (red).
+Bin width for firing rate estimation was 0.1 s.}
 \label{rate_th_close}
@@
 \includegraphics[width=\textwidth]{../../plots/nNOS_approx.png}
-\caption{Time course of nNOS(t) with Poisson spiking at 3 Hz.
+\caption[Time course of nNOS(t) with Poisson spiking of 3 Hz]{Time course of nNOS(t) with Poisson spiking of 3 Hz.
 The full simulation (blue, see Equations \eqref{Ca_dyn},\eqref{nNOS_dyn}) is well fitted by the simplified model (red, see Equation \eqref{nNOS_single_sol_approx2}).
@@
 A single cell fires in the range of $\mathrm{3\,Hz}$.
-Therefore, the dynamics of $\rm nNOS$ are dominated by single spike events as shown in Figure \ref{nNOS_approx_plot} and it is---at least on the time scale of the observed oscillations---not a proper approximation to describe $\rm nNOS$ in this smooth, rate-based fashion.
+Therefore, the dynamics of $\rm nNOS$ are dominated by single spike events as shown in Figure \ref{nNOS_approx_plot} and it is---at least on the time scale of the observed oscillations---not a proper approximation to describe $nNOS$ in this smooth, rate-based fashion.
 \newpage
@@
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/linfit_th_rate.png}
-\caption{Linear fit of excitatory population activity and mean excitatory threshold.
+\caption[Linear fit of excitatory population activity and mean excitatory threshold]{Linear fit of excitatory population activity and mean excitatory threshold.
 Slope $\alpha$ of the fit: $\mathrm{-0.79\, Hz/mV}$.
@@
 \end{center}
-\caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final}.
+\caption[Power Spectrum of $\mathrm{\langle V_t \rangle}$ and analytic predictions]{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final}.
 Red curve was fitted by varying only the overall amplitude $\mathrm{\sigma_{NO}}$ in \eqref{Pow_Spec_Theta_Final} ($\mathrm{\alpha = -0.79 \,Hz/mV}$, as in Figure \ref{thresh_r_linfit}).
@@
 \includegraphics[width=\textwidth]{../../plots/diff_hom/osc_ampl_vs_tau_th.png}
-\caption{A: Maximum of the spectrum peak (see Figure \ref{Pow_Spec_Theta_vs_Analytic}).
+\caption[Maximal height and corresponding frequency of the threshold power spectrum]{A: Maximum of the spectrum peak shown in Figure \ref{Pow_Spec_Theta_vs_Analytic}.
 A smoothing window of $\mathrm{[-5,5]}$ data points around the maximum was used to reduce overestimation of the maximum due to random fluctuations.
@@
 \includegraphics[width=\textwidth]{../../plots/diff_hom/rate_NO_th_compl_large_tau.png}
-\caption{A: Excitatory (blue) and and inhibitory (red) population rate, being controlled by diffusive homeostasis over the full simulation time.
+\caption[Excitatory and inhibitory population rate controlled by diffusive homeostasis]{A: Excitatory (blue) and and inhibitory (red) population rate, being controlled by diffusive homeostasis over the full simulation time.
 B,C: Mean NO-concentration over excitatory sites and mean excitatory threshold.}
@@
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/isi_cv_compare.png}
-\caption{A/C: Distribution of interspike intervals of excitatory/inhibitory neurons for diffusive and non-diffusive homeostasis, measured over $\mathrm{1000\,s}$.
+\caption[Distribution of interspike intervals and of coefficient of variation]{A/C: Distribution of interspike intervals of excitatory/inhibitory neurons for diffusive and non-diffusive homeostasis, measured over $\mathrm{1000\,s}$.
 Only neurons with a mean firing rate in a certain range (see legend) were included into statistics to prevent overlap of different firing rates (except for non-diffusive homeostasis and excitatory neurons, all being very close to 3 Hz).
@@
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/pop_mean_cross_corr.png}
-\caption{Mean of cross correlation over all pairs of neurons in the respective neuron group.
+\caption[Mean of cross correlation over all pairs of neurons in the respective neuron group]{Mean of cross correlation over all pairs of neurons in the respective neuron group.
 Significantly higher correlation can be found in both groups for diffusive homeostasis.
@@
 By definition, the logarithm of the random variable in question is thus again normally distributed.
-We plotted the the distribution of decadic logarithms of firing rates in Figure \ref{Fir_Rate_Dist_Compare} (B) to check for this property.
+We plotted the the distribution of decadic logarithms of firing rates in Figure \ref{Fir_Rate_Dist_Compare} B to check for this property.
 A Gaussian fit of the histogram in log-space (B) fitted the data reasonably well, with a mean $\mu_{\rm diff.,exc.} = \rm 0.152 \pm  0.002\, log_{10}(Hz)$ and a standard deviation of $\sigma_{\rm diff.,exc.} = \rm 0.152 \pm  0.002\, log_{10}(Hz)$.
-In (A), we found a skewness of $\mathrm{v_{\rm diff.,exc.,reg.} = 0.77}$, in (B) $\mathrm{v_{\rm diff.,exc.,log.} = -0.49}$.
+For the data shown in panel A, we found a skewness of $\mathrm{v_{\rm diff.,exc.,reg.} = 0.77}$, in panel B $\mathrm{v_{\rm diff.,exc.,log.} = -0.49}$.
 Though this told us that the distribution is ``more symmetric" on a logarithmic scale, the fact that we still find a skewness on the same order as in regular space indicated that it should rather be seen as not perfectly log-normal distributed.
@@
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_i_compare.png}
-\caption{Histograms of mean firing rates over the excitatory/inhibitory population in regular (A/A*) and logarithmic space (B/B*).
+\caption[Histograms of mean firing rates over the excitatory/inhibitory population]{Histograms of mean firing rates over the excitatory/inhibitory population in regular (A/A*) and logarithmic space (B/B*).
 For diffusive homeostasis ($\mathrm{D=10\, \mu m^2 ms^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
@@
 We tested this in Figure \ref{f_Var_vs_n_Bin}.
-(A) was taken from $\mathrm{1000-1500\,s}$, which is well inside the phase of diffusive homeostasis.
+Panel A was taken from $\mathrm{1000-1500\,s}$, which is well inside the phase of diffusive homeostasis.
 As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous Poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{\rm mean} n_{\rm bins}/T_{\rm total}}$, though slight deviations can be seen as a different factor of proportionality.
-(B) acts as an illustration showing a counterexample: Here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis.
+Panel B acts as an illustration showing a counterexample: Here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis.
 This will cause a transition of firing rate between 3 Hz and a new rate different from 3 Hz for almost all of the neurons.
@@
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/sim_f_var_vs_hom_poisson.png}
-\caption{A: Relation between variance of the frequency signal (acquired by binning spikes) and the number of bins within the given time range of $\mathrm{1000-1500\,s}$, taken from three randomly picked excitatory neurons.
+\caption[Relation between variance of the frequency signal and the number of bins]{A: Relation between variance of the frequency signal (acquired by binning spikes) and the number of bins within the given time range of $\mathrm{1000-1500\,s}$, taken from three randomly picked excitatory neurons.
 B: Same procedure as in (A) for a randomly chosen excitatory neuron, but the time range was $\mathrm{0-1500\,s}$, which includes the initial phase of non-diffusive homeostasis.
@@
 \end{center}
-\caption{Excitatory population firing rate of subgroups subject to external Poisson input for $\mathrm{t\geq 300\, s}$.
+\caption[Excitatory population firing rate of subgroups subject to external Poisson input]{Excitatory population firing rate of subgroups subject to external Poisson input for $\mathrm{t\geq 300\, s}$.
 Red and green subgroups consist of 100 randomly picked excitatory neurons each.
@@
 6]{Sweeney_Paper}.
-We were able to reproduce this result, see Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} (A).
+We were able to reproduce this result, see Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} A.
 Homeostasis reaches a point of saturation, where faster diffusion has no effect on the heterogeneity of firing rates.
-Each of the data points in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} (A) and (B) corresponds to a single full simulation, though the same simulation data was used in (A) and (B).
+Each of the data points in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} A and B corresponds to a single full simulation, though the same simulation data was used in A and B.
 $\rm 55$ simulations were ran in total.
@@
 \end{minipage}
-\caption{Standard deviation (A) and skewness (B) of firing rate distribution of excitatory neurons (Neumann boundary conditions).}
+\caption[Standard deviation and skewness of firing rate distribution of excitatory neurons]{Standard deviation (A) and skewness (B) of firing rate distribution of excitatory neurons (Neumann boundary conditions).}
 \label{Fir_Rate_Dist_Width_Skewness_vs_D}
@@
 \begin{table}
+\caption{Diffusion constants and number of simulations used in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.}
 \begin{tabu}{|l|l|}
@@
 \end{tabu}
-\caption{Diffusion constants and number of simulations used in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.}
 \label{Diff_Test_Constants_Sim_Number}
@@
 \includegraphics[width=\textwidth]{../../plots/firing_rate_dists/instant_diff_fir_dist_i.png}
-\caption{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population.
+\caption[Distribution of firing rates for instantaneous diffusion]{Distribution of firing rates for instantaneous diffusion for excitatory (A,B) and inhibitory (A*,B*) population.
 Red curves are least-squares Gaussian fits ($\mu_{\rm exc.} = \rm 0.420 \pm  0.006\, log_{10}(Hz)$, $\sigma_{\rm exc.} = \rm 0.254 \pm  0.006\, log_{10}(Hz)$, $\mu_{\rm inh.} = \rm 0.761 \pm  0.007\, log_{10}(Hz)$, $\sigma_{\rm inh.} = \rm 0.233 \pm  0.007\, log_{10}(Hz)$).
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/CF_plot.png}
-\caption{Connection fractions of recurrent excitatory synapses.
+\caption[Connection fractions of recurrent excitatory synapses]{Connection fractions of recurrent excitatory synapses.
 Simulation protocols include all four possible combinations of diffusive/non-diffusive homeostasis and distance-dependent/non-distance-dependent synaptic growth, each variant retained for the entire simulation time.
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/av_stdp_change_time.png}
-\caption{Top: Mean change of synaptic weights (creation and pruning excluded) between two normalization steps.
+\caption[Mean and standard deviation of weight changes between synaptic normalization]{Top: Mean change of synaptic weights (creation and pruning excluded) between two normalization steps.
 Bottom: Standard deviation for the same data.
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/RC_CFB_plot.png}
-\caption{Fraction of bidirectional connections normalized over the expected fraction for a random graph with equal total connection fraction. Data from 10 trials, linewidth represents standard error.}
+\caption[Fraction of bidirectional connections]{Fraction of bidirectional connections normalized over the expected fraction for a random graph with equal total connection fraction.
+Data from 10 trials, linewidth represents standard error.}
 \label{RC_CFB_plot}
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/syn_weight_dist_mult_sets.png}
-\caption{Distribution of decadic logarithm of excitatory synaptic weights at $\mathrm{t=1500\,s}$ for diffusive and non-diffusive homeostasis (both with distance-dependent connectivity).
+\caption[Distribution of decadic logarithm of excitatory synaptic weights]{Distribution of decadic logarithm of excitatory synaptic weights at $\mathrm{t=1500\,s}$ for diffusive and non-diffusive homeostasis (both with distance-dependent connectivity).
 Gaussian fits (non-linear least squares) returned $\mathrm{\mu_{\rm diff.}=-0.128\, \mathrm{log}_{10}(mV)}$, $\mathrm{\mu_{\rm non-diff.}=-0.064\, \mathrm{log}_{10}(mV)}$, $\mathrm{\sigma_{\rm diff.}=0.415\, log_{10}(mV)}$ and $\mathrm{\sigma_{non-diff.}=0.395\, log_{10}(mV)}$.
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/syn_lifetimes_new.png}
-\caption{Distribution of lifetimes of recurrent excitatory synaptic connections.
+\caption[Distribution of lifetimes of recurrent excitatory synaptic connections]{Distribution of lifetimes of recurrent excitatory synaptic connections.
 Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a power-law exponent of $\mathrm{\alpha_{\rm diff.} = -1.455}$ (standard error $\mathrm{\sigma_{\rm diff.} = 5.52 \cdot 10^{-4}}$) for diffusive homeostasis and $\mathrm{\alpha_{\rm don-diff.} = -1.468}$ (standard error $\mathrm{\sigma_{\rm don-diff.} = 5.70 \cdot 10^{-4}}$) for non-diffusive homeostasis.}
@@
 \begin{table}
+\caption[p-values of the Kolmogorov-Smirnov test calculated for a subset of dataset combinations depicted in Figure \ref{Out_Weight_Mean_Quantile}]{p-values of the Kolmogorov-Smirnov test calculated for a subset of dataset combinations depicted in Figure \ref{Out_Weight_Mean_Quantile}.
+The abbreviations are as follows: D: diffusive, T: topology, S: shuffled weights, N: negotiation.}
 \begin{tabu}{|l|l|}
@@
 \end{tabu}
-\caption{p-values of the Kolmogorov-Smirnov test calculated for a subset of dataset combinations depicted in Figure \ref{Out_Weight_Mean_Quantile}.
-The abbreviations are as follows: D: diffusive, T: topology, S: shuffled weights, N: negotiation.}
 \label{Kolmogorov_Mean_Out}
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/outgoing_weights_distribution.png}
-\caption{Mean of outgoing weights of excitatory neurons in order sorted by magnitude.
+\caption[Mean of outgoing weights of excitatory neurons sorted by magnitude]{Mean of outgoing weights of excitatory neurons sorted by magnitude.
 Dashed lines are means obtained by randomly shuffling synaptic weights.
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/out_degree_vs_rate.png}
-\caption{A,B: Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{700-1000\,s}$) in regular and logarithmic space.
+\caption[Mean, sum and out degree of outgoing excitatory weights plotted against mean presynaptic firing rate]{A,B: Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{700-1000\,s}$) in regular and logarithmic space.
 Each point corresponds to a presynaptic excitatory cell.
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_vs_out_degree.png}
-\caption{Out degree vs.
+\caption[Out degree vs.
+mean outgoing excitatory weights]{Out degree vs.
 mean outgoing excitatory weights at $\mathrm{t=1500\,s}$, same dataset as in Figure \ref{Out_Weight_vs_F}.
@@
 \includegraphics[width=\textwidth]{../../plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
-\caption{Dynamics of rates (A) and thresholds (B) of excitatory population of 400 Neurons and different values of $\mathrm{\alpha}$ (see Equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).}
+\caption[Dynamics of rates and thresholds of excitatory population]{Dynamics of rates (A) and thresholds (B) of excitatory population of 400 Neurons and different values of $\mathrm{\alpha}$ (see Equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).}
 \label{dynamics_rate_threshold_dyn_mean_field_sweeney}
@@
 \end{center}
-\caption{Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz} (blue, $h=10\;\mu m$) and its approximation (dashed) given by \eqref{Numeric_Solution_Expression_Trick}.
+\caption[Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz}]{Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz} (blue, $h=10\;\mu m$) and its approximation (dashed) given by \eqref{Numeric_Solution_Expression_Trick}.
 The numerical simulation was carried out on a two-dimensional grid and the curve represents a cut through the origin in x-direction.}
@@
 \end{center}
-\caption{Sketch for patches of copied (and mirrored) positions for periodic (A) and Neumann (B) boundary conditions.}
+\caption[Sketch of patches of copied (and mirrored) neuron positions]{Sketch of patches of copied (and mirrored) neuron positions for periodic (A) and Neumann (B) boundary conditions.}
 \label{Bound_Cond_Patches}
@@
 \includegraphics[width=\textwidth]{../../plots/rates_matrix_prediction_vs_sim.png}
-\caption{Measured firing rates ($\mathrm{1200\,s \leq t \leq 1500\, s}$) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
+\caption[Measured firing rates versus analytically predicted firing rates]{Measured firing rates ($\mathrm{1200\,s \leq t \leq 1500\, s}$) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
 For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably large diffusion constant of $\mathrm{D=100\, \mu m^2 ms^{-1}}$.}
@@
 \end{center}
-\caption{Distribution of firing rates for $\mathrm{D=10\, \mu m^2 ms^{-1}}$, full simulation and analytic prediction. Data was taken from 10 simulation runs.}
+\caption[Distribution of firing rates, full simulation and analytic prediction]{Distribution of firing rates for $\mathrm{D=10\, \mu m^2 ms^{-1}}$, full simulation and analytic prediction.
+Data was taken from 10 simulation runs.}
 \label{Fir_Rate_Dist_Sim_vs_Mat}
@@
 \end{center}
-\caption{Pearson correlation coefficient of predicted and measured firing rates (see Figure \ref{Rand_Matrix_Sol_vs_Sim}) versus diffusion constant.
+\caption[Pearson correlation coefficient of predicted and measured firing rates]{Pearson correlation coefficient of predicted and measured firing rates (see Figure \ref{Rand_Matrix_Sol_vs_Sim}) versus diffusion constant.
 Line width depicts standard error, 5 simulations were used for each $\rm D$-value.}
@@
 \end{minipage}
-\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries.
+\caption[Comparison of distribution of standard deviation and skewness for random-matrix solutions and simulation data]{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries.
 Same simulation data as in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} was used, each point representing a single simulation.
@@
 \end{center}
-\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2 ms^{-1}}$, full simulation and analytic prediction.
+\caption[Distribution of firing rates for a regular square grid]{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2 ms^{-1}}$, full simulation and analytic prediction.
 1 Simulation run was used, with spikes within $\rm 1200 \leq t \leq 1500$.}
@@
 \includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
-\caption{A and B: Scatter plot of \emph{inverse} of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights.
+\caption[A/B: Scatter plot of inverse of local neuron density and decadic logarithm of outgoing excitatory weights.
+C: Frequency of excitatory weights versus inverse neural density.
+D: Decadic logarithm of mean outgoing excitatory weights versus inverse neural density]{A/B: Scatter plot of \emph{inverse} of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights.
 Note the spatial correlation in high/low-density regions.
@@
 \includegraphics[width=\textwidth]{../../plots/external_input_switch_spread_source.png}
-\caption{A/B: Illustration of circular kernels used for NO-insertion, overlay of all 400 neurons (left) and a single example (right).
+\caption[A/B: Illustration of circular kernels used for NO-insertion, overlay of all 400 neurons and a single example.
+C: Resulting activity for excitatory subgroups]{A/B: Illustration of circular kernels used for NO-insertion, overlay of all 400 neurons (left) and a single example (right).
 C: Resulting activity for excitatory subgroups.

### 2017-03-13 draft.tex
.

@@
 
-\clubpenalty = 1000 % schliesst Schusterjungen aus
-\widowpenalty = 1000 \displaywidowpenalty = 1000% schliesst Hurenkinder aus
+\clubpenalty = 10000 % schliesst Schusterjungen aus
+\widowpenalty = 10000 \displaywidowpenalty = 10000% schliesst Hurenkinder aus
 
@@
 \tableofcontents
-\newpage
+
 \clearpage
@@
 59-64]{Cybernetik_Systems_Cruse_2006}.
-\newpage
+
 \subsubsection{Theory of Control Systems} \label{Control_Sys_Theo_Section}
@@
 Based on the way the controller generates input for the dynamic process based on the error signal one can classify control loops by three types:
-\newpage
 \begin{itemize}
@@
 \end{table}
-\newpage
 
@@
 \textit{Potentiation} in this context refers to the fact that stronger input strengthens synaptic transmission \emph{compared} to close to zero incoming spikes.
-
-\newpage
 
@@
 
-\newpage
+\clearpage
+
 \section{Results} \label{results}
@@
 Therefore, the dynamics of $\rm nNOS$ are dominated by single spike events as shown in Figure \ref{nNOS_approx_plot} and it is---at least on the time scale of the observed oscillations---not a proper approximation to describe $nNOS$ in this smooth, rate-based fashion.
-\newpage
+
 We introduced an idealized picture of diffusive homeostasis to deal with this, where diffusion across the tissue is instantaneous.
@@
 We ran a full simulation under diffusive homeostasis to compare these previous results to the diffusive case, including the growth phase by setting the target concentration to an appropriate value that was determined in a previous simulation with non-diffusive homeostasis.
-The resulting time course of CF is depicted in Figure \ref{CF_plot}.
+The resulting time course of CFs is depicted in Figure \ref{CF_plot}.
 \begin{figure}
@@
 Simulation protocols include all four possible combinations of diffusive/non-diffusive homeostasis and distance-dependent/non-distance-dependent synaptic growth, each variant retained for the entire simulation time.
-Data from 10 trials, linewidth represents standard error.}
+Data from 5 trials, linewidth represents standard error.}
 \label{CF_plot}
 \end{figure}
-Diffusive homeostasis caused the CF to slightly overshoot its final fraction in the growth phase.
-To understand this kind of behavior, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic creation and pruning.
+It appeared to be the case that diffusive homeostasis caused the CF to slightly overshoot its non-diffusive counterpart in the growth phase.
+To estimate statistical significance, we performed a \textit{two-sample t-test} for the sample data taken from $\rm t = 300\, s$, which---judging by eye---is the point where the overshoot of CFs resulting from diffusive homeostasis is at its maximum.
+The null hypothesis of the two-sample t-test states that the probability density functions underlying two sets of sample data have the same expected value, under the assumption that both are normally distributed \cite{EncyMath_t_test} and have equal variance.
+Since we could not guarantee the last assumption, we used a generalization by Welch that allows for different variances \cite{Welch_1947}.
+The condition of normality was left as an assumption.
+Comparing diffusive versus non-diffusive data, we found a p-value of $p_{\rm topol.} = \rm 1.25 \cdot 10^{-3}$ for networks with a spatially-dependent connection profile and $p_{\rm no topol.} = \rm 4.00 \cdot 10^{-3}$ for networks with a flat connection profile.
+In terms of usual significance levels (1--10\% \cite{EncyMath_sign_level}), we thus rejected the null hypothesis and concluded that the observed overshoot is statistically significant for both network-growth variants.
+
+To understand this overshoot, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic creation and pruning.
 The average change of connection fraction is simply proportional to the difference between newly created synapses and those that were removed.
@@
 \caption[Fraction of bidirectional connections]{Fraction of bidirectional connections normalized over the expected fraction for a random graph with equal total connection fraction.
-Data from 10 trials, linewidth represents standard error.}
+Data from 5 trials, linewidth represents standard error.}
 \label{RC_CFB_plot}
@@
 \caption[p-values of the Kolmogorov-Smirnov test calculated for a subset of dataset combinations depicted in Figure \ref{Out_Weight_Mean_Quantile}]{p-values of the Kolmogorov-Smirnov test calculated for a subset of dataset combinations depicted in Figure \ref{Out_Weight_Mean_Quantile}.
-The abbreviations are as follows: D: diffusive, T: topology, S: shuffled weights, N: negotiation.}
+Abbreviations are as follows: D: diffusive, T: topology, S: shuffled weights, N: negotiation.}
 \begin{tabu}{|l|l|}
@@
 
-\newpage
+\clearpage
+
 \section{Further Analysis of the Firing Rate Distribution}
@@
 
-\newpage
 \subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}\label{NO_source_spread_section}
@@
 
-\newpage
 \section{Conclusion and Outlook}\label{Conclusion_Section}

### 2017-03-15 draft.tex
.

@@
 \usepackage{float}
-
+\usepackage{upgreek}
 \usepackage[titletoc]{appendix}
@@
 \begin{large}
-Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity
+Spatially Dependent Interaction As a Determinant of Neural Activity and Plasticity
 \end{large}
@@
   \vspace{0.5cm}
-  \LARGE{Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity}\\
+  \LARGE{Spatially Dependent Interaction As a Determinant of Neural Activity and Plasticity}\\
   \vspace{2cm}
@@
 \begin{abstract}
-Building upon on a self-organizing spiking neural network (LIF-SORN), we attempted to replace the intrinsic homeostatic control system used in earlier versions by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
-The model of diffusive homeostasis was adopted from a paper by Sweeney et al.
-and models the tissue as a surface of square shape and a set of points on this surface, representing the positions of the neurons within the network.
-Excitatory neurons acted as a source of nitric oxide (NO), as well as as a sensor for the NO concentration at each individual position.
-Production and sensing of NO formed the basis of a feedback loop: Individual NO readouts caused an appropriate change within the intrinsic excitability of the neurons.
-The control system was closed by linking the rate of NO production to the neurons' firing rates.
-
-The main goal of the modification of homeostasis was to allow for a broad and heavy tailed distribution of firing rates among the excitatory neural population.
+Building on a Self-Organizing Spiking Neural Network (LIF-SORN), we attempted to replace the intrinsic homeostatic control system used in earlier versions by a mechanism based on the diffusion of a neurotransmitter across the nervous tissue.
+The model of diffusive homeostasis was adopted from a study by Sweeney et al.
+\cite{Sweeney_Paper} and models the tissue as a surface of square shape and a set of points on this surface, representing the positions of the neurons within the network.
+Excitatory neurons act as a source of nitric oxide (NO) as well as as a sensor for the NO concentration at each individual position.
+Production and sensing of NO forms the basis of a feedback loop: Individual NO readouts cause an appropriate change within the intrinsic excitability of the neurons.
+The control system is closed by linking the rate of NO production to the neurons' firing rates.
+
+The main goal of the modification of homeostasis was to allow for a broad and heavy tailed distribution of firing rates among the excitatory neuronal population.
 This feature of cortical activity has been extensively observed and studied experimentally, but could not be achieved by the formerly used single-cell homeostatic mechanism which bound firing rates of all neurons to a fixed target value.
@@
 Apart from the preservation of a number of topological features we found that diffusive homeostasis allowed for the emergence of highly influential neurons with strong outgoing synaptic efficacies.
-By means of an analytic approach to the homeostatic steady state, we could relate this feature of synaptic topology to the imposed spatial structure of the neural population.
+By means of an analytic approach to the homeostatic steady state, we could relate this feature of synaptic topology to the imposed spatial structure of the neuronal population.
 \end{abstract}
@@
 probability density function\\
-self-organizing recurrent neural network\\
+Self-Organizing Recurrent Neural Network\\
 short-term depression\\
@@
 484]{Bear_Exploring_the_Brain}.
-The term \textit{homeostasis} entailing these regulatory mechanisms was first introduced by Walter C.
+The term \textit{homeostasis} embracing these regulatory mechanisms was first introduced by Walter C.
 Cannon in 1932 \cite{Wisdom_of_the_Body_Cannon, Homeostasis_Queenan_2012}.
-In more recent years, experimental studies have found evidence for processes within the brain that do not function as a regulatory control for certain aspects of the body, but as a homeostatic control of neural activity itself \cite{Turrigiano_1994,Burrone_2003}.
+In more recent years, experimental studies have found evidence for processes within the brain that do not function as a regulatory control for certain aspects of the body, but for neuronal activity itself \cite{Turrigiano_1994,Burrone_2003}.
 Many processes underlying this self-regulatory behavior have been found so far and many different biophysical interdependencies have shown to play a role.
@@
 The notion of synaptic homeostatic plasticity subsumes the observation that neurons - being more or less active than a certain set point of mean activity - are regulated by means of their incoming synaptic weights.
-Theoretical and experimental studies have suggested that this type of regulation is taking place in a multiplicative manner, thereby retaining proportions between individual synaptic strengths \cite{Syn_Plast_Abbott}.
+Theoretical and experimental studies have suggested that this type of regulation is taking place in a multiplicative manner, thereby preserving proportions between individual synaptic strengths \cite{Syn_Plast_Abbott}.
 One can regard this form of plasticity as an antagonist to other aspects of synaptic plasticity that affect synaptic strengths in an activity dependent, Hebbian fashion.
@@
 This is also known as a \textit{closed loop control} in control theory.
-All these systems include a number of necessary functional components, which will be briefly introduced in the following.
+All these systems include a number of necessary functional components, which will be briefly introduced in the following section.
 Concepts and terms were taken from \cite[p.
@@
 A closed loop control generally must contain some \emph{process} that is to be regulated.
-Despite its potential internal complexity, its functional role in the context of a feedback system is to simply generate a time-dependent output based on the history of a time-dependent input.
-This output is what one wishes to control and regulate by means of the feedback loop and thus represents the signal that is further processed.
+Despite its potential internal complexity, its functional role in the context of a feedback system is simply to generate a time-dependent output based on the history of a time-dependent input.
+This output is what one wishes to regulate by means of the feedback loop and thus represents the signal that is further processed.
 It might not be possible however to directly quantify this desired output in terms of some internal state of the process.
@@
 \end{figure}
-Based on the way the controller generates input for the dynamic process based on the error signal one can classify control loops by three types:
+Based on the way the controller generates input for the dynamic process one can classify control loops by three types:
 \begin{itemize}
@@
 
-\subsubsection{Error Signals and Controllers of Neuronal Homeostasis}
+\subsubsection{Error Signals and Controllers of Neural Homeostasis}
 A key step in characterizing a control loop in the context of biological systems should be to identify the previously described abstract elements.
@@
 As a start, we state that the process and its output controlled by homeostasis is the generation of action potentials and the resulting firing rate.
-Firing rate is---as stated earlier---an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a ``sensible" quantity.
+The latter is---as stated earlier---an abstract quantity, requiring a feedback transducer to translate the neuron's spiking activity into a ``sensible" quantity.
 In a nerve cell this could be represented by e.g.
@@
 Given a representation of activity, its deviation from a reference value will cause other physiological quantities to affect the neuron's ability to generate action potentials.
-Referring to the concepts introduced in the previous section one could then ask what type of control best resembles the actual neuronal control.
+Referring to the concepts introduced in the previous section one could then ask what type of control best resembles the actual neural control.
 The fact that neurons, whose firing rate was artificially increased or suppressed over a long time, can reliably tune their activity back to the initial state (see e.g.
@@
 The conductance of an ion channel for example has natural upper and lower bounds that it can not surpass.
-We will pick up this issue in Section \ref{Possible_Modifications_Section}.
-
-\subsubsection{Single-Cell Homeostasis as an Integral Control}
+We will come back to this issue in Section \ref{Possible_Modifications_Section}.
+
+\subsubsection{Single-Cell Homeostasis As an Integral Control}
 Former versions of the LIF-SORN and SORN used a simple form of integral control to regulate excitatory firing rates.
@@
 
-\subsubsection{The Role of Firing Rate Heterogeneity---a Dichotomy between Heterogeneity and Control?}\label{Section_Role_Fir_Rate_Het}
+\subsubsection{The Role of Firing Rate Heterogeneity---a Dichotomy Between\\ Heterogeneity and Control?}\label{Section_Role_Fir_Rate_Het}
 Modeling homeostasis necessarily includes a form of error estimation, which requires setting some predefined target that the feedback control will attempt to achieve.
@@
 In this context Buzsáki and Mizuseki argue that a small subset of highly active neurons may serve to form relatively strongly connected and stable sub-networks that can quickly react to momentary changes in the environment, while fine tuned adaptation involves the slower firing majority of cells \cite{Buzsaki_Fir_Rates_2014}.
-A realistic network model of neural activity and plasticity should therefore allow for a broad distribution of firing rates to cope with these functional aspects.
+A realistic network model of neuronal activity and plasticity should therefore allow for a broad distribution of firing rates to cope with these functional aspects.
 
@@
 \subsubsection{Nitric Oxide in the Nervous System}\label{NO_Experiments_Section}
-The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of nitric oxide (NO).
-Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS), the immune system (inducible NOS, iNOS) and the CNS (neuronal NOS, nNOS) \cite{NOS_Mammals}.
+The model presented in \cite{Sweeney_Paper} includes spatial interaction across excitatory neurons through the diffusion of NO.
+Enzymes that are responsible for NO synthesis (NOS) are present in different areas of the body, namely being involved in the dilation of blood vessels (endothelial NOS, eNOS), the immune system (inducible NOS, iNOS) and the CNS (neural NOS, nNOS) \cite{NOS_Mammals}.
 These Enzymes differ in their functionality and dependence on the presence of other molecules.
-In particular, nNOS is sensitive to the concentration of $\mathrm{Ca^{2+}}$ ionic Calcium \cite{Knowles_Ca_nNOS,Steinert_NO}.
+In particular, nNOS is sensitive to the concentration of $\mathrm{Ca^{2+}}$ \cite{Knowles_Ca_nNOS,Steinert_NO}.
 Nitric oxide that was synthesized in the nervous system can diffuse freely because of its small molecular structure and electrical neutrality, which makes it a good candidate to be involved into a form of diffusive intercellular communication \cite{Lancaster_1994}.
@@
 
-\subsection{Previous Research on the used Network Model}
-This thesis is based on earlier versions of a self-organizing recurrent neural network (SORN), in particular an implementation using leaky integrate-and-fire neurons (LIF-SORN) \cite{SORN_Paper}.
-It was developed to model features of activity and topology of cortical networks, in particular L5 of the neocortex.
+\subsection{Previous Research on the Used Network Model}
+This thesis is based on earlier versions of a Self-Organizing Recurrent Neural Network (SORN), in particular an implementation using leaky integrate-and-fire neurons (LIF-SORN) \cite{SORN_Paper}.
+It was developed to model features of activity and topology of cortical networks, in particular of L5 of the neocortex.
 A slow homeostatic mechanism was set up among excitatory neurons through an intrinsic adaptation of excitability in these previous implementations.
-This led to the aforementioned problems of homeostatic control: Neural activity was tuned to a globally set target, allowing for no variability.
+This led to the aforementioned problems of homeostatic control: Neuronal activity was tuned to a globally set target, allowing for no variability.
 Despite this limitation, the model has proven to be capable of showing a number of experimentally confirmed features.
 Zheng et al.
-have shown that distribution and dynamics of synaptic efficacies measured in rat hippocampus can be reproduced by a binary SORN using a discretized version of spike-timing-dependent plasticity and presynaptic normalization \cite{Pengsheng_2013}.
+have shown that the distribution and dynamics of synaptic efficacies measured in rat hippocampus can be reproduced by a binary SORN using a discretized version of spike-timing-dependent plasticity and presynaptic normalization \cite{Pengsheng_2013}.
 Miner et al.
@@
 Key aspects of this thesis include an analysis of the stability of the homeostatic control, followed by a comparison of features of the original LIF-SORN and the diffusive variant.
-We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neural activity which has previously been suppressed by single-cell homeostasis.
+We expect to observe a preservation of non-random features that have been found in the original LIF-SORN while incorporating a stronger variance within neuronal activity which has previously been suppressed by single-cell homeostasis.
 Furthermore, we predict excitatory activity on the level of individual cells by an analytic approach, thereby gaining an understanding of the relation between spatial structure and firing rates.
@@
 
-The Neural Network was simulated with the code used in \cite{SORN_Paper}, which makes use of the BRIAN spiking neural network simulator \cite{Briansim}.
+The neural network was simulated with the code used in \cite{SORN_Paper}, which makes use of the BRIAN spiking neural network simulator \cite{Briansim}.
 All following explanations regarding the simulation of neurons and mechanisms of synaptic plasticity are thus based on the methods described in the aforementioned paper.
 
-400 excitatory LIF neurons and 80 inhibitory LIF neurons were assigned random positions across a square area of 1000 $\times$ 1000 $\mu m$.
-All but recurrent excitatory synapses were randomly generated before the start of the simulation until a desired connection fraction was reached.
-The connection probability between two neurons was calculated from a distance-dependent Gaussian function with a standard deviation of 200 $\mu m$.
+400 excitatory LIF neurons and 80 inhibitory LIF neurons were assigned random positions across a square area of 1000 $\times$ 1000 $\rm \upmu m$.
+All except recurrent excitatory synapses were randomly generated before the start of the simulation until a desired connection fraction was reached.
+The connection probability between two neurons was calculated from a distance-dependent Gaussian function with a standard deviation of 200 $\rm \upmu m$.
 For excitatory to inhibitory (EI) and inhibitory to excitatory (IE) synapses, the connection fraction was set to 0.1, and 0.5 for recurrent inhibitory synapses (II).
@@
 \caption{Parameters of synaptic connections.}
+\begin{center}
 \begin{tabu}{|l|l|l|l|l|}
@@
 connection fraction & $\rightarrow 0.1$ & $0.1$ & $0.1$ & $0.5$ \\ \hline
-initial connection strength & $0.0001 mV$ & $1.5 mV$ & $-1.5 mV$ & $-1.5 mV$ \\ \hline
-conduction delay & $1.5 ms$ & $0.5 ms$ & $1.0 ms$ & $1.0 ms$ \\
+initial connection strength & $\rm 0.0001\, mV$ & $\rm 1.5\, mV$ & $\rm -1.5\, mV$ & $\rm -1.5\, mV$ \\ \hline
+conduction delay & $\rm 1.5\, ms$ & $\rm 0.5\, ms$ & $\rm 1.0\, ms$ & $\rm 1.0\, ms$ \\
 \hline
 \end{tabu}
+\end{center}
 \label{syn_conn_params}
@@
 \caption{Parameters of LIF neuron}
+\begin{center}
 \begin{tabu}{|l|l|l|}
@@
 \end{tabu}
+\end{center}
 \label{LIF_neuron_params}
@@
 \subsubsection{Synaptic Plasticity}\label{Section_Syn_Plast}
-\textbf{Synaptic Growth:} Once per second, $\mathrm{n}$ new EE synapses were generated, where n is taken from a normal distribution with mean 920 and standard deviation $\sqrt{920}$.
-This constant growth rate was tuned to achieve the desired target concentration of 0.1 (see \ref{syn_conn_params}).
+
+\textbf{Synaptic Growth:} Once per second, $n$ new EE synapses were generated, where $n$ is taken from a normal distribution with mean 920 and standard deviation $\sqrt{920}$.
+This constant growth rate was tuned to achieve the desired target concentration of 0.1 (see Table \ref{syn_conn_params}).
 
@@
 in \cite{Zhang_STDP}.
-The change of weight between two neurons due to a pre- and postsynaptic spike (i $\rightarrow$ j) is defined as:
+The change of weight between two neurons due to a pre- and postsynaptic spike ($i$ $\rightarrow$ $j$) is defined as:
 \begin{align}
@@
 \end{align}
-Indexes k and l refer to the k-th and l-th pre- and postsynaptic spike respectively.
-Parameters were chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = 15 ms$, $A_{+} = 15 mV$, $\tau_{-} = 30 ms$ and $A_{-} = -7.5 mV$.
+Indices $k$ and $l$ refer to the $k$-th and $l$-th pre- and postsynaptic spike respectively.
+Parameters were chosen to approximate data from \cite{Bi_Poo_STDP} and \cite{Froemke_STDP}, namely $\tau_{+} = \rm 15\, ms$, $A_{+} =\rm 15\, mV$, $\tau_{-} =\rm 30\, ms$ and $A_{-} =\rm -7.5\, mV$.
 However, we used the ``nearest neighbor" approximation for the sake of reduction of computational effort, only calculating the effect of the most recent pre-post pair of spikes for potentiation and post-pre pair for depression, yielding roughly the same value as the full summation due to the fast decay times $\tau_{+}$ and $\tau_{-}$ of the STDP-window.
@@
 Though the latter does not directly enforce a fixed level of activity, one can argue that in a balanced recurrent network synaptic normalization still reduces the probability of very high or low firing rates caused by an above- or below-average total synaptic input.
-We implemented synaptic normalization by calling a function once per sec., updating each $w_{ji}$ from neuron $i$ to neuron $j$ as follows:
-
-\begin{equation}
-w_{ji} \rightarrow w_{ji} \frac{w_{total}}{\sum_i w_{ji}}
+We implemented synaptic normalization by calling a function once per second, updating each $w_{ji}$ from neuron $i$ to neuron $j$ as follows:
+
+\begin{equation}
+w_{ji} \rightarrow w_{ji} \frac{w_{\rm total}}{\sum_i w_{ji}}
 \label{Synnnorm}
 \end{equation}
-$w_{total}$ was set to different values for each of the four types of connections between the excitatory and inhibitory pool of neurons.
-Except for the dynamically populated EE-synapses these values could be directly set in accordance with the previously given parameters of desired mean individual connection strength, size of the presynaptic population and connection fraction, by calculating $w_{total} = w_{mean} \cdot N_{presyn.
-pop}\cdot p_{connect}$.
-This yielded $w_{total,EI} = 60 mV$, $w_{total,IE} = -12 mV$, $w_{total,II} = -60 mV$.
-$w_{total,EE}$ was set to $40mV$,  corresponding to a mean synaptic weight of $1mV$, given a targeted EE-connection fraction of $0.1$ and a population of 400 excitatory neurons.
+$w_{\rm total}$ was set to different values for each of the four types of connections between the excitatory and inhibitory pool of neurons.
+Except for the dynamically populated EE-synapses these values could be directly set in accordance with the previously given parameters of desired mean individual connection strength, size of the presynaptic population and connection fraction, by calculating $w_{\rm total} = w_{\rm mean} N_{\rm presyn.
+pop} p_{\rm connect}$.
+This yielded $w_{\rm total,EI} = \rm 60\, mV$, $w_{\rm total,IE} =\rm -12\, mV$, $w_{\rm total,II} =\rm -60\, mV$.
+$w_{\rm total,EE}$ was set to $\rm 40\, mV$,  corresponding to a mean synaptic weight of $\rm 1\, mV$, given a targeted EE-connection fraction of $0.1$ and a population of 400 excitatory neurons.
 
@@
 \end{equation}
-This is a phenomenological model of short-term plasticity that models two aspects of synaptic transmission, namely short-term depression (STD) and short-term facilitation (STF).
+This is a phenomenological model of short-term plasticity that comprises two aspects of synaptic transmission, namely short-term depression (STD) and short-term facilitation (STF).
 STD is an effect that subsumes different mechanisms involved in the depletion of available neurotransmitters in the presynaptic terminal due to presynaptic action potentials.
@@
 The amount of potentially available neurotransmitters during an ``idle" state, with no presynaptic action potentials arriving, is given by $U$.
-Consequently, the dynamical system given by Equations \eqref{STP_dynamics1} and \eqref{STP_dynamics2} has its fixed point at $(x=1,u=U)$.
+Consequently, the dynamical system given by Equation \eqref{STP_dynamics1} and \eqref{STP_dynamics2} has a fixed point at $(x=1,u=U)$.
 If spikes arrive, depending on the choice of $\tau_d$ and $\tau_f$, one can achieve a weight modulation that is dominated by potentiation ($\tau_f \gg \tau_d$) or depression ($\tau_f \ll \tau_d$).
-We chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$ as a rough approximation of the values that were experimentally observed \cite{Markram_STP}, giving it a tendency towards potentiation.
-However, one should keep in mind that for $U\in [0,1]$, $x\cdot u \in [0,1]$ always holds, thus the factor $x\cdot u$ has a generally diminishing effect.
-For our choice of variables for example, a Poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim 4.5 Hz$, corresponding to $x\cdot u \approx 0.2$.
+We chose $U=0.04$, $\tau_d = 0.5s$ and $\tau_f = 2s$ as a rough approximation of experimentally observed values \cite{Markram_STP}, giving it a tendency towards potentiation.
+However, one should keep in mind that for $U\in [0,1]$, $x\cdot u \in [0,1]$ always holds, hence the factor $x\cdot u$ generally has a diminishing effect.
+For our choice of variables for example, a Poisson input with a constant rate achieves the best synaptic transmission at a rate of $\sim \rm 4.5\, Hz$, corresponding to $x\cdot u \approx 0.2$.
 \textit{Potentiation} in this context refers to the fact that stronger input strengthens synaptic transmission \emph{compared} to close to zero incoming spikes.
 
-\subsubsection{Intrinsic Plasticity (IP)}
+\subsubsection{Intrinsic Plasticity}
 
@@
 
-Finally, the dynamics of firing thresholds $V_{t,i}$ were modeled such that the rate of change is proportional to the relative deviation of $\rm NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
+Finally, the dynamics of the firing thresholds $V_{t,i}$ were modeled such that the rate of change is proportional to the relative deviation of $\rm NO$ concentration at the neurons' locations from a global target concentration $NO_0$.
 
@@
 One rather needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration.
-Though it is possible to derive this relation in an analytic fashion, we let the system run with the previous homeostatic mechanism, still solving equation \eqref{Ca_dyn}--\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
+Though it is possible to derive this relation in an analytic fashion, we let the system run with the previous homeostatic mechanism, still solving Equation \eqref{Ca_dyn}--\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached.
 This mean was then set to be the target concentration and we switched to diffusive homeostasis.
@@
 \caption{Parameters of homeostatic intrinsic plasticity.}
+\begin{center}
 \begin{tabu}{|l|l|}
@@
 \hline
-$\mathrm{D}$ & default: 10 $\mathrm{\mu m^2 ms^{-1}}$ \\
+$\mathrm{D}$ & default: 10 $\mathrm{\upmu m^2 ms^{-1}}$ \\
 \hline 
@@
 \end{tabu}
+\end{center}
 \label{Params_IP}
@@
 3.) Dirichlet boundary conditions with $NO = NO_{\rm bound.}$ at the boundaries.\\
-Neumann boundary conditions were used for most of the simulations if not explicitly marked differently.
+Neumann boundary conditions were used in all simulations unless stated otherwise.
 This decision relates to the previously described mechanism of synaptic growth: Neurons placed close to the edge of the sheet have a lower connection probability due to the absence of neighboring neurons in the direction perpendicular to the close-by border.
@@
 The Neumann boundary condition fits into this picture since it allows a zero-flux condition at the borders.
-This is a reasonable assumption, because NO molecules cannot diffuse out of the tissue (unless they were placed in a fluid surrounding).
+This is a reasonable assumption, because NO molecules cannot diffuse out of the tissue (unless they were placed in a surrounding fluid).
 
@@
 Apart from the question whether this source term results in a well defined, finite solution at the neurons' positions (see Section \ref{Matrix_Diff_Model_Section}), it can only be modeled to a certain degree of accuracy depending on the resolution of the numeric grid.
-In practice, we approximated the point sources of NO as an insertions at individual grid cells at a rate of $nNOS_i(t) / h^2$, where the normalizing divisor $h^2$ ensured the desired total influx per neuron.
+In practice, we approximated the point sources of NO as insertions at individual grid cells at a rate of $nNOS_i(t) / h^2$, where the normalizing divisor $h^2$ ensured the desired total influx per neuron.
 This numeric implementation required two additional constraints: First, all random neuron positions were confined to integer multiples of $h$ in x- and y-direction.
 Second, to avoid redundancy and for physiological reasons, each grid cell could only hold one neuron at maximum.
-Both conditions combined led to an iterative generation of positions where for each neuron a random number generator produced pairs of integers $(n_x,n_y)$, each within $[0,N]$, until an unoccupied pair of integers was found and occupied, moving on to the next neuron.
+Combining both conditions led to an iterative generation of positions where for each neuron a random number generator produced pairs of integers $(n_x,n_y)$, each within $[0,N]$, until an unoccupied pair of integers was found and occupied, moving on to the next neuron.
 Figure \ref{diff_test_plot} shows an example of the resulting NO density throughout a simulation.
-Note that the actual values of concentration do not approximate actual biological values, since Equation \eqref{nNOS_dyn} binds the rate of $\rm NO$ production between $\rm 0$ and $\rm 1$ for simplicity.
+Note that the values of concentration do not approximate actual biological values, since Equation \eqref{nNOS_dyn} binds the rate of $\rm NO$ production between $\rm 0$ and $\rm 1$ for simplicity.
 \begin{figure}[h!]
@@
 \subsubsection{Dynamic Behavior of the Population Activity}
-We set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$ on a first attempt, as given by \cite{Sweeney_Paper}.
+We set the time constant of threshold adaptation in the diffusive homeostasis to $\mathrm{2500\, ms}$ in a first attempt, as given by \cite{Sweeney_Paper}.
 Switching between non-diffusive/diffusive homeostasis after $\rm 750\, s$, Figure \ref{full_sim_osci} shows the resulting dynamics of the population activity of the excitatory and inhibitory group (panel A/A*), the average $\rm NO$ concentration at the excitatory neurons' positions (panel B/B*) and the average firing threshold (panel C/C*) within the excitatory group (inhibitory threshold was fixed, see table \ref{LIF_neuron_params}).
@@
 However, what might appear to be slightly faster and stronger random fluctuations in panel A--C were in fact regular oscillations across all three depicted variables, as can be seen in panel A*--C*, showing the dynamics in a smaller time window.
-While the oscillation amplitudes undergo a rather unpredictable course, the frequency remains at a constant level of $\simeq 0.5\, Hz$.
+While the oscillation amplitudes undergo a rather unpredictable course, the frequency remains at a constant level of $\simeq \rm 0.5\, Hz$.
 This feature is also illustrated by the fact that the power spectra depicted in Figure \ref{Power_Spec_without_Analysis} have a peak at the frequency that appeared to be dominant in Figure \ref{full_sim_osci}.
@@
 This leads to explanatory models at different levels of abstraction.
-On a microscopic, single-neuron level, a so-called slow after-hyper-polarization conductance explains the appearance of bursting behavior: A relatively short period of spiking activity is followed by a longer period of silence.
+On a microscopic, single-neuron level, a so-called \textit{slow after-hyper-polarization conductance} explains the appearance of bursting behavior: A relatively short period of spiking activity is followed by a longer period of silence.
 This phenomenon can be modeled by a $\rm Ca^{2+}$-dependent $\rm K^{+}$ conductance.
-$\rm Ca^{2+}$ concentration rises upon the bursting period, prohibiting continuous spiking due to the activation of $\rm K^{+}$  current until the $\rm Ca^{2+}$ concentration has returned to base-level \cite[p.~203--207]{Theor_Neur_Dayan}.
+$\rm Ca^{2+}$ concentration rises upon the bursting period, prohibiting continuous spiking due to the activation of $\rm K^{+}$  current until the $\rm Ca^{2+}$ concentration has returned to base level \cite[p.~203--207]{Theor_Neur_Dayan}.
 However, this type of oscillating activity can be ruled out as an explanation due to the simplicity of our neuron model.
@@
 For this purpose, we transferred the structure and dynamics onto a simpler, rate-based model of neural network activity.
-The results are discussed in the following section
+The results are discussed in the following section.
+
 \subsubsection{Predicting Activity in a Simplified Rate-Based Network}
@@
 Coming back to the dynamics in question, one would need to show that the network has a locally unstable fixed point at $\mathrm{(r_e,r_i)\approx (3\, Hz, 13\, Hz)}$, see A* in Figure \ref{full_sim_osci}.
-Several aspects come into play, making it a hard task to fit the full spiking network model onto the simplified equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
+Several aspects come into play, making it a hard task to fit the full spiking network model onto the simplified equations \eqref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
 First, the choice of $\tau_e$ and $\tau_i$ in \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2} has significant influence on the stability of the system.
 However, a straightforward equivalent does not exist in the used spiking neuron model.
-It has been shown that in the case of slowly varying input $\tau_{e/i}$ of equation \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2} are equal to the membrane constant $\tau_m$ of the LIF-neuron used in the network \cite{Gerstner_Pop_Act}, see equation \ref{LIF_Dynamics}.
+It has been shown that in the case of slowly varying input $\tau_{e/i}$ of Equation \eqref{2d-exc_inh_rate_1} and \eqref{2d-exc_inh_rate_2} are equal to the membrane constant $\tau_m$ of the LIF-neuron used in the network \cite{Gerstner_Pop_Act}, see Equation \eqref{LIF_Dynamics}.
 A second problem is to choose a good estimate of the activation functions $\phi_{e/i}( \cdot )$.
-In the absence of noise in equation \ref{LIF_Dynamics}, the firing rate for a given constant total input $J$ is
+In the absence of noise in Equation \eqref{LIF_Dynamics}, the firing rate for a given constant total input $J$ is
 \begin{equation}
@@
 \end{equation}
-If noise $\sigma$ is present, according to \cite{Roxin_Firing_Rate_Distribution} one can calculate the \emph{mean} firing rate by
+If noise $\sigma$ is present, one can calculate the \emph{mean} firing rate according to \cite{Roxin_Firing_Rate_Distribution} by
 \begin{align}
@@
 \end{align}
-where $\mathrm{erfc}$ is the complementary error function. Figure \ref{F-I_noise_dep} shows that both predictions are quite accurate in predicting the mean firing rate. 
+where $\mathrm{erfc(\cdot)}$ is the complementary error function. Figure \ref{F-I_noise_dep} shows that both predictions are quite accurate in predicting the mean firing rate. 
 \begin{figure}
@@
 \caption[Comparison of mean firing rate of a LIF neuron without noise and with noise]{Comparison of mean firing rate of a LIF neuron without noise (squares) and with noise (circles, $\mathrm{\sigma = \sqrt{5}\, mV}$), averaged over $\mathrm{50\, s}$.
-Red and blue curves are the corresponding analytic predictions, see equation \ref{LIF_Fir_Rate_no_Noise} and \ref{LIF_Fir_Rate_with_Noise1}.}
+Red and blue curves are the corresponding analytic predictions, see Equation \eqref{LIF_Fir_Rate_no_Noise} and \eqref{LIF_Fir_Rate_with_Noise1}.}
 \label{F-I_noise_dep}
@@
 One should note however that the synaptic input within a spiking network carries an intrinsic randomness: One cannot simply describe it as a mean constant input $J$, since it is the sum of instantaneous increases in membrane voltage upon arriving spikes.
-Rather, if we assume that the arrival of spikes is approximately Poisson distributed and the time constant of the membrane is small compared to the average interspike-interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
+Rather, if we assume that the arrival of spikes is approximately Poisson distributed and the time constant of the membrane is small compared to the average interspike interval, according to \cite{Roxin_Firing_Rate_Distribution}, one can describe the synaptic input from population $\mathrm{A}$ to population $\mathrm{B}$ as $J_{AB}(t) = \mu_{AB} (t) + \sigma_{AB} \zeta(t)$, where $\zeta(t)$ is zero-mean standard gaussian noise and
 \begin{align}
@@
 Apart from the correct description of $\phi_{e/i}$, a third problem is the analytic description of STP that was present for recurrent excitatory connections in our network.
-In \cite{Markram_STP} the steady-state value of $\mathrm{x\cdot u}$ for an input of constant rate $\mathrm{r}$ is given by
+In \cite{Markram_STP}, the steady-state value of $\mathrm{x\cdot u}$ for an input of constant rate $\mathrm{r}$ is given by
 \begin{align}
@@
 \end{align}
-One thus needs to incorporate the factor $x_{\rm st.}\cdot u_{\rm st.}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise when trying to find the fixed point of Equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
-
-All these aspects taken together make it impossible to find an analytic expression for the fixed point of Equation \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}.
-Running a simulation of Equations \ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2}, including all aforementioned approximations resulted in a stable configuration.
+One thus needs to incorporate the factor $x_{\rm st.}\cdot u_{\rm st.}$ by means of the previously described mean input and the contribution to the total variance of the membrane noise when trying to find the fixed point of \eqref{2d-exc_inh_rate_1} and \eqref{2d-exc_inh_rate_2}.
+
+All these aspects taken together make it impossible to find an analytic expression for the fixed point of Equation \eqref{2d-exc_inh_rate_1} and \eqref{2d-exc_inh_rate_2}.
+Running a simulation of \eqref{2d-exc_inh_rate_1} and \eqref{2d-exc_inh_rate_2}, including all aforementioned approximations resulted in a stable configuration.
 We set the relevant parameters to their predefined values for this simulation and additionally extracted the mean threshold of the excitatory population which was set by the non-diffusive homeostasis, see C/C* in Figure \ref{full_sim_osci}, yielding a threshold of $\mathrm{-56.963\, mV}$.
@@
 \end{center}
-\caption[Dynamics of rate-based network model]{Dynamics of equations \ref{2d-exc_inh_rate_1} (blue line) and \ref{2d-exc_inh_rate_2} (red line).
+\caption[Dynamics of rate-based network model]{Dynamics of Equation \eqref{2d-exc_inh_rate_1} (blue line) and \eqref{2d-exc_inh_rate_2} (red line).
 Dotted lines mark the mean frequencies that were present in the full spiking network.
 Excitatory: 3 Hz, Inhibitory: 6,768 Hz.
-\ref{2d-exc_inh_rate_1} and \ref{2d-exc_inh_rate_2} converged to 2.992 Hz and 7.144 Hz respectively.}
+Equation \eqref{2d-exc_inh_rate_1} and \eqref{2d-exc_inh_rate_2} converged to 2.992 Hz and 7.144 Hz respectively.}
 \label{Dyn_Rate_Approx}
@@
 Furthermore, on an empirical basis, the occurrence of oscillations appears to be rather dependent on the choice of homeostasis since all parameters of the simulation were kept unchanged upon the transition after 750 s, apart from the homeostatic mechanism itself.
-Therefore, we present in the following section our further analysis of the dynamics underlying the diffusive homeostatic feedback.
-
-\subsection{Analysis of Oscillations under Dynamic Feedback}\label{theor_osc}
+Therefore, we present our further analysis of the dynamics underlying the diffusive homeostatic feedback in the following section.
+
+\subsection{Analysis of Oscillations Under Dynamic Feedback}\label{theor_osc}
 In this section, we discuss an analytic treatment of the dynamics underlying the diffusive homeostatic mechanism.
@@
 
-Describing the neural activity as instantaneous firing rates raises the question how to describe the production of nitric oxide, since the outcome of Equations \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $\rm Ca^{2+}$ concentration caused by spike events.
+Describing the neuronal activity as instantaneous firing rates raises the question how to describe the production of nitric oxide, since the outcome of \eqref{Ca_dyn} and \eqref{nNOS_dyn} relies on sudden increases of $\rm Ca^{2+}$ concentration caused by spike events.
 One could naively replace the sum of Dirac functions in \eqref{Ca_dyn} by a continuous inflow $Ca^{2+}_{\rm spike} r_i(t)$.
@@
 We note the following in order to derive an approximate description: The target firing rate of 3 Hz and the corresponding mean interspike interval of 0.33...s is large compared to the decay constant of calcium, $\tau_{Ca^{2+}} = \mathrm{0.01\,s}$.
-Consequently, it is very unlikely that one spike event will fall into a region where the calcium concentration, decaying from the instant jump of the previous spike event, is still significantly larger than zero.
+Consequently, it is very unlikely that one spike event will fall into a region where the calcium concentration, decaying from the instantaneous jump of the previous spike event, is still significantly larger than zero.
 In fact, calculating the mean concentration of $\rm Ca^{2+}$ before a new spike event over all neurons and all spike events for $\rm 1500\,s$ resulted in a value of $\rm 0.0013$.
@@
 The exact solution of this integral can be expressed in terms of the hyper-geometric function, making it rather impractical for any further analysis.
-Looking for further simplifications, we noted that $\tau_{nNOS}$ is ten-fold larger than $\tau_{Ca^{2+}}$.
+Looking for more possible simplifications, we noted that $\tau_{nNOS}$ is ten-fold larger than $\tau_{Ca^{2+}}$.
 This discrepancy in decay times allows for the assumption that the impact of the calcium kernel onto $nNOS$ is practically instantaneous.
@@
 \end{equation}
-Figure \ref{nNOS_approx_plot} compares the approximation given by \eqref{nNOS_single_sol_approx2} to the full NO production model (Equations \eqref{Ca_dyn} and \eqref{nNOS_dyn}).
+Figure \ref{nNOS_approx_plot} compares the approximation given by \eqref{nNOS_single_sol_approx2} to the full NO production model (\eqref{Ca_dyn} and \eqref{nNOS_dyn}).
 Spikes were drawn from a Poisson process at a rate of 3 Hz.
@@
 \caption[Time course of nNOS(t) with Poisson spiking of 3 Hz]{Time course of nNOS(t) with Poisson spiking of 3 Hz.
-The full simulation (blue, see Equations \eqref{Ca_dyn},\eqref{nNOS_dyn}) is well fitted by the simplified model (red, see Equation \eqref{nNOS_single_sol_approx2}).
+The full simulation (blue, see Equation \eqref{Ca_dyn}, \eqref{nNOS_dyn}) is well fitted by the simplified model (red, see Equation \eqref{nNOS_single_sol_approx2}).
 Top panel is a closeup of the first spike event.
@@
 We introduced an idealized picture of diffusive homeostasis to deal with this, where diffusion across the tissue is instantaneous.
-This simplification results in a single level of NO-concentration for all neurons, only being modified over time by the sum of all neurons' NO-syntheses $nNOS_{\rm total}(t) \equiv \sum_{i} nNOS_i(t)$ and the decay term $-\lambda NO$.
+This simplification results in a single level of NO concentration for all neurons, only being modified over time by the sum of all neurons' NO syntheses $nNOS_{\rm total}(t) \equiv \sum_{i} nNOS_i(t)$ and the decay term $-\lambda NO$.
 $nNOS_{\rm total}$ must be divided by the area $L^2$ of the tissue to account for the spread of NO.
@@
 \end{equation}
-The amount of noise in the system is a hard-to-predict quantity since it depends on the spatial structure on the diffusive lattice, giving neurons that are further separated less impact onto each other.
-We tried to estimate the noise level based on the same instant-spread simplification made in Equation \eqref{NO_dyn_approx} to describe the overall NO-dynamics.
+The amount of noise in the system is a hard to predict quantity since it depends on the spatial structure on the diffusive lattice, giving further separated neurons less impact onto each other.
+We tried to estimate the noise level based on the same instantaneous-spread simplification made in Equation \eqref{NO_dyn_approx} to describe the overall NO-dynamics.
 This led to an underestimation of the total energy within the power spectrum in the final result.
@@
 
-It is clear from Equation \eqref{NO_dyn_approx} why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify Equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $3 Hz \cdot N_{\rm exc.} = \mathrm{1200\,Hz}$, given the assumption that cells' spiking is approximately independent.
+It is clear from Equation \eqref{NO_dyn_approx} why we can now describe the \emph{total} influx of NO as the sum of a mean and a random fluctuation: While spiking events on individual cells remain sufficiently separated to justify Equation \eqref{nNOS_single_sol_approx2}, the sum of all spike events from the excitatory population results in an effective Poisson process with a mean rate of $\mathrm{3\, Hz} \cdot N_{\rm exc.} = \mathrm{1200\,Hz}$, given the assumption that cells' spiking is approximately independent.
 We furthermore argue that a total rate of $\mathrm{1200\,Hz}$ is sufficiently large to express this rate as a continuous function of time, $r_{\rm total} = N_{\rm exc.} r_{\rm exc.pop.}(t)$, at least on the time scale of the oscillations to be studied (see  Figure \ref{rate_th_close}).
@@
 
-We wanted to simplify the dynamics of threshold adaption and its effect on the population rate as a next step.
+As a next step, we wanted to simplify the dynamics of threshold adaption and its effect on the population rate.
 Corresponding to the reduction to a single variable $r_{\rm exc.pop.}(t)$ for the mean excitatory activity in Equation \eqref{nNOS_total_dyn}, we wanted to find an appropriate description containing only the mean threshold $V_{t,\rm pop.}(t) = \langle V_t(t) \rangle$.
@@
 \end{align}
-Through the coordinate transformations
+By mean of the coordinate transformations
 \begin{align}
 n &\equiv NO-NO_0 \label{simplif_coord_transf1}\\
-\theta &\equiv V_{t,\rm pop.}(t)-V_{t,0} \label{simplif_coord_transf2}\\
+\theta &\equiv V_{t,\rm pop.}(t)-V_{t,0} \label{simplif_coord_transf2}
 \end{align}
@@
 NO_0 &= \frac{nNOS_{\mathrm{ total},0}}{\lambda L^2} \label{2d-sys-fixed-points2}\\
-nNOS_{\mathrm{ total},0} &= r_{IP} N_{\rm exc.} \cdot \gamma \; . \label{2d-sys-fixed-points3}
+nNOS_{\mathrm{ total},0} &= r_{IP} N_{\rm exc.} \gamma \; . \label{2d-sys-fixed-points3}
 \end{align}
 As stated in the beginning, we were interested in finding an analytic expression for the power spectrum of the mean excitatory threshold.
-We therefore calculated the Fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} and \eqref{2d-sys-homeostasis-coord_transf2}, yielding
+We hence calculated the Fourier transform of \eqref{2d-sys-homeostasis-coord_transf1} and \eqref{2d-sys-homeostasis-coord_transf2}, yielding
 \begin{align}
 i\omega f_n &= - \lambda f_n + \frac{\gamma \alpha N_{\rm exc.}}{L^2}f_\theta + \sigma_{NO} f_{\xi} \label{2d-sys-homeostasis-coord_transf_ft1}\\
-i\omega f_\theta &= \frac{f_n}{NO_0\tau_{V_t}} \label{2d-sys-homeostasis-coord_transf_ft2} \\
-\end{align}
-where $f_{(\cdot)}$ denotes the Fourier transform. We solved for $f_\theta$ which immediately gave us the power spectrum $P_\theta (\omega) \equiv |f_\theta (\omega)|^2$ of $\theta$:
+i\omega f_\theta &= \frac{f_n}{NO_0\tau_{V_t}} \label{2d-sys-homeostasis-coord_transf_ft2}
+\end{align}
+where $f_{(\cdot)}$ denotes the Fourier transform. We solved for $f_\theta$, which immediately gave us the power spectrum $P_\theta (\omega) \equiv |f_\theta (\omega)|^2$ of $\theta$:
 \begin{equation}
@@
 Choosing noise amplitude to be the only free parameter of the model gave a rather unsatisfying result.
-Our approximation underestimated the amount of damping within the system (which controls the ``peakiness" of the spectrum), as well as predicting a slightly smaller preferred amplitude.
+Our approximation underestimated the amount of damping within the system (which controls the ``peakiness" of the spectrum) and predicted a slightly smaller preferred amplitude.
 The preferred amplitude is controlled by $\frac{\gamma \alpha N_{\rm exc.}}{L^2}$ and $\frac{1}{NO_0\tau_{V_t}}$ while the broadness of the spectrum is mostly controlled by the damping term $-\lambda$.
@@
 \end{figure}
-The fact that the value for $\mathrm{\alpha}$ that was determined by means of the linear fit in Figure \ref{thresh_r_linfit} leads to an underestimation of the preferred frequency can be partially explained by the linear regression, which overestimates the importance of a number of high-threshold outliers.
+The fact that the value for $\mathrm{\alpha}$, that was determined by means of the linear fit in Figure \ref{thresh_r_linfit}, leads to an underestimation of the preferred frequency can be partially explained by the linear regression, which overestimates the importance of a number of high-threshold outliers.
 This leads to a shallower slope than what would be appropriate for the working point of oscillatory behavior.
-Another possible explanation could be that ``instant spread" is only an approximation.
-Rather, one could picture the nitrous oxide just to fill a fraction of the available space on a short time scale by replacing $L^2$ by a smaller area.
-This leads to a stronger local increase of concentration, which eventually leads to faster oscillations.
-In either case, both parameters have the same effect on the shape of the power spectrum since these parameters appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}.
+Another possible explanation could be that ``instantaneous spread" is only an approximation.
+Rather, one could picture NO just to fill a fraction of the available space on a short time scale by replacing $L^2$ by a smaller area.
+This would lead to a stronger local increase of concentration and eventually to faster oscillations.
+In either case, both parameters have the same effect on the shape of the power spectrum since they appear as a fraction $\alpha/L^2$ in \eqref{Pow_Spec_Theta_Final}.
 
@@
 We managed to do so by increasing the time constant $\mathrm{\tau_{V_t}}$, as shown in Figure \ref{Peak_Prop_vs_Theta}.
-Moreover, by choosing $\mathrm{\sigma_{NO}}$, $\mathrm{\lambda}$ and $\mathrm{\alpha}$ in accordance to the fit shown in Figure \ref{Pow_Spec_Theta_vs_Analytic} (black curve), Equation \eqref{Pow_Spec_Theta_Final} provides a good prediction for the position and height of the peak.
-We smoothed the curve of the simulation data in plot (A) of Figure \ref{Peak_Prop_vs_Theta} by a window of $\mathrm{[-5,5]}$ data points for proper comparison, since the maximum of the power spectrum of simulation data is likely to overshoot the analytic prediction due to random fluctuations.
+Moreover, by choosing $\mathrm{\sigma_{NO}}$, $\mathrm{\lambda}$ and $\mathrm{\alpha}$ in accordance to the fit shown in Figure \ref{Pow_Spec_Theta_vs_Analytic} (black curve), Equation \eqref{Pow_Spec_Theta_Final} provided a good prediction for the position and height of the peak.
+We smoothed the curve of the simulation data in plot A of Figure \ref{Peak_Prop_vs_Theta} by a window of $\mathrm{[-5,5]}$ data points for proper comparison, since the maximum of the power spectrum of simulation data is likely to overshoot the analytic prediction due to random fluctuations.
 \begin{figure}
@@
 
-We further investigated the features of neural activity after the elimination of oscillatory activity in the network, in particular those of the excitatory population since it was exposed to homeostasis.
+We further investigated the features of neuronal activity after the elimination of oscillatory activity in the network, in particular those of the excitatory population since it was exposed to homeostasis.
 This includes statistics of spike timing, as well as of heterogeneous firing rates among the network.
@@
 Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behavior under sparse connectivity with a relatively high per-synapse connection strength \cite{Vreeswijk1996,Brunel2000}.
-This kind of asynchronous irregular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity.
+This kind of asynchronous irregular state is characterized by a population firing rate showing no regularities over time, while maintaining an overall stable level of activity.
 This regularity was shown to be achievable in the previous section after slowing down the rate of homeostatic adaption.
@@
 \includegraphics[width=\textwidth]{../../plots/Spike_Stats/isi_cv_compare.png}
-\caption[Distribution of interspike intervals and of coefficient of variation]{A/C: Distribution of interspike intervals of excitatory/inhibitory neurons for diffusive and non-diffusive homeostasis, measured over $\mathrm{1000\,s}$.
+\caption[Distribution of interspike intervals and of coefficients variation]{A/C: Distribution of interspike intervals of excitatory/inhibitory neurons for diffusive and non-diffusive homeostasis, measured over $\mathrm{1000\,s}$.
 Only neurons with a mean firing rate in a certain range (see legend) were included into statistics to prevent overlap of different firing rates (except for non-diffusive homeostasis and excitatory neurons, all being very close to 3 Hz).
@@
 Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficients of variation ($\mathrm{CV\equiv\sigma/\mu}$) taken over the set of excitatory and inhibitory neurons.
-However, we restricted the statistics of ISIs to neurons whose mean firing rate fall into a window with a width of 1 Hz and a certain mean in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case (see legend in Figure \ref{ISI_CV_compare}).
+However, we restricted the statistics of ISIs to neurons whose mean firing rate fell into a window of a width of $\rm 1\, Hz$ and a certain mean in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case (see legend in Figure \ref{ISI_CV_compare}).
 An approximately exponential distribution of ISIs is apparently preserved for diffusive homeostasis (represented by straight lines in a log-plot), which is characteristic for Poisson processes \cite[p.
 27]{Theor_Neur_Dayan}.
-For perfect poissonian spiking, the CV should give a value of 1.
+For perfect Poisson spiking, the CV should give a value of 1.
 CVs that are smaller or larger, as seen in Figure \ref{ISI_CV_compare} B/D, indicate a tendency towards greater regularity or bunching, respectively.
@@
 These types of behavior of LIF-models have been shown to depend on the amount of fluctuations of the input the neuron receives: A larger CV of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals \cite{Ostojic2011}.
-By the CV of the input we mean the ratio between standard deviation and mean of postsynaptic current due to presynaptic spiking events (under the assumption of a stationary mean and variance).
+By the CV of the \emph{input} we mean the ratio between standard deviation and mean of postsynaptic current due to presynaptic spiking events (under the assumption of a stationary mean and variance).
 This relation between fluctuating input and spiking statistics fits nicely into our set of network parameters: Inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
@@
 We also considered potential correlations across neurons within both populations as an additional possibility of spike-train analysis.
-To do so, we calculated cross-correlations for all possible neuron pairings within a population, excluding auto-correlations.
+To do so, we calculated cross-correlations for all possible neuron pairings within a population, excluding autocorrelations.
 Figure \ref{Pop_Mean_Cross_Corr} shows the mean cross-correlation taken over all these pairs.
@@
 \end{figure}
-One could consider two possibilities when speculating about the root of this discrepancy: Either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network.
+One could consider two possibilities when speculating about the origin of this discrepancy: Either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network.
 Regarding the first, it is certainly true that some amount of information about the activity of one neuron is transferred to another one in its neighborhood via diffusion.
@@
 
-In summary, we found that diffusive homeostasis does not interfere with the poisson-like spiking statistics observed on a single-cell level, but leads to an increased correlation across the neural population.
+In summary, we found that diffusive homeostasis does not interfere with the poisson-like spiking statistics observed on a single-cell level, but leads to an increased correlation across the neuronal population.
 
@@
 \caption[Histograms of mean firing rates over the excitatory/inhibitory population]{Histograms of mean firing rates over the excitatory/inhibitory population in regular (A/A*) and logarithmic space (B/B*).
-For diffusive homeostasis ($\mathrm{D=10\, \mu m^2 ms^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
+For diffusive homeostasis ($\mathrm{D=10\, \upmu m^2 ms^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis.
 Green curves are non-linear least-squares Gaussian fit onto the distribution resulting from diffusive homeostasis.
@@
 This question is not only of relevance with respect to the ``stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of momentary rates.
-A constant rate of an approximately randomly spiking neuron means that the dependence of fluctuations of rates on the width of the averaging window should be identical to a homogeneous Poisson process of the same total mean firing rate.
+A constant rate of an approximately randomly spiking neuron means that the dependence of rate fluctuations on the width of the averaging window should be identical to a homogeneous Poisson process of the same total mean firing rate.
 As bin sizes increase, possible long-term fluctuations of firing rates can then be identified as deviations from the variance one would expect from a homogeneous process.
@@
 \end{figure}
-We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only population-wise but on a single-cell level as well.
+We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only with respect to the population, but on a single-cell level as well.
 In particular, plastic modifications across the network due to STDP and synaptic growth/pruning---which were always acting for all the simulation results presented so far---appeared to be compensated for.
@@
 \caption{Diffusion constants and number of simulations used in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.}
+\begin{center}
 \begin{tabu}{|l|l|}
 \hline
-\boldmath{$\rm D\;[\mu m^2 ms^{-1}]$} & \textbf{Number of Sim.} \\ \hline
+\boldmath{$\rm D\;[\upmu m^2 ms^{-1}]$} & \textbf{Number of Sim.} \\ \hline
 $\rm 0.0$ & 1 \\ \hline
@@
 \end{tabu}
+\end{center}
 \label{Diff_Test_Constants_Sim_Number}
@@
 A naturally emerging question when altering the diffusion constant is how the firing rate behaves in the absolute limit of infinitely fast diffusion.
-In fact, this case is quite easy to implement simulation-wise: One simply has to feed all NO-sources into a single scalar variable of NO concentration.
+In fact, this case is quite easy to implement in the simulation: One simply has to feed all NO-sources into a single scalar variable of NO concentration.
 This will provide the same NO readout for all excitatory neurons, which means that all excitatory thresholds change at the same rate all the time, only shifting their initial random distribution.
@@
 \subsection{Network Topology}\label{Network_Topology_Section}
-We have only presented our analysis of network activity so far.
-In this section we present results that relate to features of network topology.
-Since the SORN we used for all simulations only included plastic mechanisms affecting recurrent excitatory connections, these were the subject of our investigations.
+We have only presented our analysis of network \emph{activity} so far.
+In this section we show results relating to features of network \emph{topology}.
+Since the SORN used for all simulations only included plasticity mechanisms affecting recurrent excitatory connections, these were subject to our investigations.
 Moreover, in contrast to the previous section, we did not explicitly aim for the emergence of a \emph{new} feature of network topology, but rather sought to recover properties that had been found in earlier versions of the LIF-SORN.
@@
 To understand this overshoot, we recalled the two mechanisms that directly determine changes within the connection fraction, namely synaptic creation and pruning.
-The average change of connection fraction is simply proportional to the difference between newly created synapses and those that were removed.
+The average change of the connection fraction is proportional to the difference between newly created synapses and those that were removed.
 Though fluctuating, the synaptic growth rate was kept at a constant level of 920 synapses/second.
@@
 This experimentally observed feature required the presence of a distance dependent connection probability, as described in section \ref{network simulation}.
-The theoretical background of this effect was laid out by Miner and Triesch \cite{SORN_Paper} and further generalized by Hoffmann and Triesch \cite{Hoffmann_2017}.
+The theoretical background of this effect was laid out by Miner and Triesch \cite{SORN_Paper} and generalized by Hoffmann and Triesch \cite{Hoffmann_2017}.
 The result of these investigations was that any deviation from a perfectly uniform connection probability that preserves symmetry of these connection probabilities will necessarily lead to an over-representation of bidirectional connections.
@@
 \end{equation}
-The ration we would like to calculate thus is
+The ratio we would like to calculate thus is
 \begin{equation}
@@
 An additional feature of this package---also originally proposed by Clauset et al.---is the possibility to automatically find a lower bound $x_{\rm min.}$ below which data points are discarded from the analysis, based on the goodness of the estimated power law to the actual data.
-The authors argue that this feature accounts for the possibility that smaller values of a dataset might not as strictly follow a power law as found in the tail of the distribution.
+The authors argue that this feature accounts for the possibility that smaller values of a dataset might not follow a power law as strictly as found in the tail of the distribution.
 This optimization is based on the Kolmogorov-Smirnov statistic, which is the maximum absolute distance $d_{\rm max.}$ between the empirical cumulative distribution function of the data and the cumulative distribution function of the analytic prediction.
 It can be further used to perform a statistical test, allowing a judgment whether a given dataset of random variables was generated from the given PDF \cite{EncyMath_Kolmogorov_Smirnov}.
-For the sake of finding the optimal value of $x_{\rm min.}$ however, the authors simply minimize $d_{\rm max.}$ in order to find the best fitting setting.
-
-Observing the distribution of synaptic lifetimes, we found that fitting a power law to the simulation data would rather require to define an \emph{upper} bound $x_{\rm max.}$ than a lower one, since we observed a falloff from the linear behavior in a log-log plot for large synaptic lifetimes, see Figure \ref{Syn_Lifetimes}.
-The \textit{powerlaw package} allows manually setting an upper bound, but the optimization described before is only available for $x_{\rm min.}$.
+To find the optimal value of $x_{\rm min.}$ however, the authors simply minimize $d_{\rm max.}$.
+
+Observing the distribution of synaptic lifetimes, we found that fitting a power law to the simulation data would rather require to define an \emph{upper} bound $x_{\rm max.}$ than a lower one, since we observed a negative deviation from the linear behavior in a log-log plot for large synaptic lifetimes, see Figure \ref{Syn_Lifetimes}.
+The \textit{powerlaw package} allows for manually setting an upper bound, but the optimization described before is only available for $x_{\rm min.}$.
 We therefore decided to manually implement the same approach for $x_{\rm max.}$, while keeping the lower bound fixed at $x_{\rm min.} = 1 \, s$.
@@
 Instead, $d_{\rm max.}$ was monotonically decreasing but converging.
-Therefore, we actually found its minimal value for $x_{\rm max.} = \rm 750 \, s$ for both diffusive homeostasis and non-diffusive homeostasis ($d_{\rm max.,diff.}^{min.} = 0.30$,$d_{\rm max.,non-diff.}^{min.} = 0.34$).
+Therefore, we actually found its minimal value for $x_{\rm max.} = \rm 750 \, s$ for both diffusive homeostasis and non-diffusive homeostasis ($d_{\rm max.,diff.}^{min.} = 0.30$, $d_{\rm max.,non-diff.}^{min.} = 0.34$).
 We thus accepted the values for $\alpha$ acquired by MLE for both entire datasets as valid, yielding $\mathrm{\alpha_{\rm diff.} = -1.455}$ and $\mathrm{\alpha_{\rm don-diff.} = -1.468}$.
@@
 \end{figure}
-To get an approximative explanation for the observed slope in the region of small lifetimes, we note that short synaptic lifetimes are most likely coming from synapses whose weights did not reach large values compared to the initial weight.
+To get an approximate explanation for the observed slope in the region of small lifetimes, we note that short synaptic lifetimes are most likely coming from synapses whose weights did not reach large values compared to the initial weight.
 The effect of multiplicative normalization is small compared to additive STDP in this regime of small weights.
 Small weights are therefore determined by additive quasi-random (due to their weak coupling to the postsynaptic neuron) fluctuations, which, as a very simple approximation, can be described as a Brownian motion with a certain standard deviation $\mathrm{\sigma}$.
-The first-hitting time of this Brownian motion is described by a Lévy distribution \cite{Roy_1968}:
+The first-passage time of this Brownian motion is described by a Lévy distribution \cite{Roy_1968}:
 \begin{equation}
@@
 Zheng et al.
-found a similar slope in the binary version of the SORN and also argued that this could be referred to random-walk behavior \cite{Pengsheng_2013}.
+found a similar slope in the binary version of the SORN and also argued that this could be related to random-walk behavior \cite{Pengsheng_2013}.
 Still, understanding the exponent of this distribution is subject to ongoing research and it has been argued that a more precise explanation could be used to relate certain parameters of synaptic plasticity to the value of this exponent.
@@
 
-\subsubsection{Mean outgoing Weights}\label{Section_Mean_outgoing_Weights}
+\subsubsection{Mean Outgoing Weights}\label{Section_Mean_outgoing_Weights}
 Since we only implemented synaptic normalization for the sum of \emph{incoming} weights, the total or average strength of \emph{outgoing} connections may vary from cell to cell.
@@
 To check for statistical significance, we performed a two-sample Kolmogorov-Smirnov test between all datasets depicted in Figure \ref{Out_Weight_Mean_Quantile}.
-It is based on the same principle as the one-sample Kolmogorov-Smirnov test used in Section \ref{Section_Syn_Lifetimes}.
-The only difference is that two empirical cumulative distributions are compared instead of comparing one empirical dataset to a given analytical function.
+It is based on the same principle as the one-sample Kolmogorov-Smirnov test used in Section \ref{Section_Syn_Lifetimes}, the only difference being that two empirical cumulative distributions are compared instead of one empirical dataset and a given analytic function.
 The null hypothesis of the test states that both sets share the same underlying probability function.
 Thus, in our case, there should be a high statistical significance towards the rejection of this hypothesis.
-Though we did calculate the p-value for all possible pairs of datasets (28 in total), only a number of those were of relevance since we were interested in statistical differences due to diffusive homeostasis.
+Even though we did calculate the p-value for all possible pairs of datasets (28 in total), only a number of those were of relevance since we were interested in statistical differences due to diffusive homeostasis.
 These are listed in Table \ref{Kolmogorov_Mean_Out}.
 As the values indicate, the statistical significance is very high.
-Apart from the difference between diffusive and non-diffusive homeostasis, the difference between original and randomly shuffled versions of the weight matrices also appear to be significant.
+In addition to the difference between diffusive and non-diffusive homeostasis, the difference between original and randomly shuffled versions of the weight matrices also appear to be significant.
 
@@
 Abbreviations are as follows: D: diffusive, T: topology, S: shuffled weights, N: negotiation.}
+\begin{center}
 \begin{tabu}{|l|l|}
@@
 \textbf{Combination} & \textbf{p-value} \\ \hline
-D,T,NS vs ND,T,NS & $\rm 4.662 \cdot 10^{-35}$ \\ \hline
-D,NT,NS vs ND,NT,NS & $\rm 6.895 \cdot 10^{-77}$ \\ \hline
-D,T,NS vs D,T,S & $\rm 3.344 \cdot 10^{-44}$ \\ \hline
-D,NT,NS vs D,NT,S & $\rm 1.790 \cdot 10^{-61}$ \\ \hline
+D,T,NS vs. ND,T,NS & $\rm 4.662 \cdot 10^{-35}$ \\ \hline
+D,NT,NS vs. ND,NT,NS & $\rm 6.895 \cdot 10^{-77}$ \\ \hline
+D,T,NS vs. D,T,S & $\rm 3.344 \cdot 10^{-44}$ \\ \hline
+D,NT,NS vs. D,NT,S & $\rm 1.790 \cdot 10^{-61}$ \\ \hline
 \end{tabu}
+\end{center}
 \label{Kolmogorov_Mean_Out}
@@
 identified the presence of inhibitory STDP as a necessary mechanism for the development of this feature, in contrast to our model.
-On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: Though it is known that inhibitory STDP can balance network activity \cite{Vogels_2011}, for some excitatory neurons in the network, presynaptic inhibitory neurons can not fully compensate the above-average firing rate of the postsynaptic neuron.
+On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: While it is known that inhibitory STDP can balance network activity \cite{Vogels_2011}, for some excitatory neurons in the network, presynaptic inhibitory neurons can not fully compensate the above-average firing rate of the postsynaptic neuron.
 Furthermore, synapses from highly active excitatory presynaptic cells to postsynaptic excitatory neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
@@
 With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies a similar functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity.
-We tested this relationship by plotting the mean of excitatory outgoing weights, sum of outgoing weights and the out degree against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
+We tested this relationship by plotting the mean of excitatory outgoing weights, sum of outgoing weights and the outdegree against the average firing rate, see Figure \ref{Out_Weight_vs_F}.
 A strong heterogeneity of firing rates allows for the development of few neurons with comparably strong mean outgoing weights, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range.
-Interestingly, the heterogeneity of out weights is most prominent when looking at the total sum.
-While this should lead to the conclusion that this is the case because an increased firing rate increases both, mean and number of outgoing weights, the latter can not be strictly verified based on Figure \ref{Out_Weight_vs_F} (D).
-In consequence, we also did not find a strong direct correlation between mean outgoing weights and out degree, as shown in Figure \ref{Mean_Weight_vs_Out_Degree}.
-Still though, it is interesting to note that diffusive homeostasis, in contrast to the other shown variants, at least has a correlation coefficient of $\rho_{\rm Diff.} =  0.4$, especially in contrast to $\rho_{\rm Inst.
-Diff.} =  -0.23$, even though instant diffusion leads to similarly spread firing rates.
-
-Furthermore, it is interesting to note that we found a roughly linear relationship between mean outgoing weight and firing rate on a logarithmic weight scale, see Figure \ref{Out_Weight_vs_F} (B).
+Interestingly, the heterogeneity of outgoing weights is most prominent when looking at the total sum.
+While this should lead to the conclusion that this arises from an increased firing rate increasing both, mean and number of outgoing weights, the latter can not be strictly verified based on Figure \ref{Out_Weight_vs_F} D.
+Correspondingly, we neither found a strong direct correlation between mean outgoing weights and outdegree, as shown in Figure \ref{Mean_Weight_vs_Out_Degree}.
+Nevertheless, it is interesting to note that diffusive homeostasis, in contrast to the other shown variants, at least has a correlation coefficient of $\rho_{\rm Diff.} =  0.4$, especially in contrast to $\rho_{\rm Inst.
+Diff.} =  -0.23$, even though instantaneous diffusion leads to similarly spread firing rates.
+
+It is also interesting to note that we found a roughly linear relationship between mean outgoing weight and firing rate on a logarithmic weight scale, see Figure \ref{Out_Weight_vs_F} (B).
 Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/out_degree_vs_rate.png}
-\caption[Mean, sum and out degree of outgoing excitatory weights plotted against mean presynaptic firing rate]{A,B: Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{700-1000\,s}$) in regular and logarithmic space.
+\caption[Mean, sum and outdegree of outgoing excitatory weights plotted against mean presynaptic firing rate]{A,B: Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{700-1000\,s}$) in regular and logarithmic space.
 Each point corresponds to a presynaptic excitatory cell.
 C,D: Sum of outgoing excitatory weights, same setting as in (A) and (B).
-E: Out degree of excitatory neurons, same setting as in (A) and (B).
+E: Outdegree of excitatory neurons, same setting as in (A) and (B).
 }
@@
 \includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_vs_out_degree.png}
-\caption[Out degree vs.
-mean outgoing excitatory weights]{Out degree vs.
+\caption[Outdegree vs.
+mean outgoing excitatory weights]{Outdegree vs.
 mean outgoing excitatory weights at $\mathrm{t=1500\,s}$, same dataset as in Figure \ref{Out_Weight_vs_F}.
@@
 Standard errors were calculated from 5 simulation runs for each homeostatic mechanism, and connectivity matrices were taken from $\rm t = 1500\,s$.
-This showed that connectivity is indeed increased among the fastest-firing neurons 10\% in the case of diffusive homeostasis.
+This showed that connectivity is indeed increased among the fastest-firing 10\% of the neurons in the case of diffusive homeostasis.
 Effenberger et al.
-reported a similar effect, though differences of connectivity were even more pronounced \cite{Effenberger_2015}.
+reported a similar effect, in fact with even more pronounced differences of connectivity \cite{Effenberger_2015}.
 
@@
 The results of section \ref{Fir_Dist_Section} were positive on a preliminary level regarding our goal of achieving a broad and skewed firing rate distribution.
-Following this, we tried to further gain insight into the actual shape of the resulting distribution.
+As to this, we tried to further gain insight into its actual shape.
 \subsection{Review of a Dynamic Mean-Field Model}\label{Mean_Field_Review_Section}
@@
 attempted to predict the shape of the firing rate distribution by means of a simplified mean-field approximation of diffusion \cite{Sweeney_Paper}.
-The main simplification within homeostatic feedback was the replacement of Equation \ref{Theta_dyn} by
+The main simplification within homeostatic feedback was the replacement of Equation \eqref{Theta_dyn} by
 \begin{equation}
@@
 \end{equation}
-$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the mixture between single-neuron homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
+$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determined the mixture between single-neuron homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$).
 $\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their population mean.
@@
 where $\nu$ is the mean population firing rate, $\phi_i$ the firing rate of neuron $i$, $\mu_i$, $\sigma_i$ and $V_{t,i}$ its synaptic input mean and standard deviation over time and intrinsic firing threshold respectively and $J_i$, $C_i$ and $\tau$ the neuron's mean synaptic efficacy, number of incoming neurons and the membrane time constant.
-Synaptic efficacy and number of incoming neurons were drawn randomly to match the statistics of the actual network topology.
-Self consistency was achieved by iterating through Equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate3} until the desired precision of convergence was reached.
+The synaptic efficacy and number of incoming neurons were drawn randomly to match the statistics of the actual network topology.
+Self consistency was achieved by iterating through Equation \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate3} until the desired precision of convergence was reached.
 
@@
 Individual values for $\mu_i$ and $\sigma_i$ were then calculated according to \eqref{sweeney_self_consist_rate2} and \eqref{sweeney_self_consist_rate3}.
-Note however that in this case the mean (input) firing rate $\nu$ also takes different values $\nu_i$ for each neuron.
-
-Instead of directly iterating through Equations \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate3}---as done in \cite{Sweeney_Paper}---to fulfill self-consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
+Note, however, that in this case the mean (input) firing rate $\nu$ also takes different values $\nu_i$ for each neuron.
+
+Instead of directly iterating through Equation \eqref{LIF_Fir_Rate_with_Noise1_copy} and \eqref{sweeney_self_consist_rate1}--\eqref{sweeney_self_consist_rate3}---as done in \cite{Sweeney_Paper}---to fulfill self consistency, we described the dynamics of the neurons' rates $r_i$ through a continuous dynamic equation
 \begin{equation}
@@
 \includegraphics[width=\textwidth]{../../plots/rate_threshold_simpl_hip_alpha/rate_threshold_simpl_hip_alpha_comb}
-\caption[Dynamics of rates and thresholds of excitatory population]{Dynamics of rates (A) and thresholds (B) of excitatory population of 400 Neurons and different values of $\mathrm{\alpha}$ (see Equations \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).}
+\caption[Rate and threshold dynamics of excitatory population]{Dynamics of rates (A) and thresholds (B) of 30 randomly picked representative excitatory neurons for different values of $\mathrm{\alpha}$ (see Equation \eqref{dyn_rate_equation} and \eqref{diff_hom_simpl_sweeney}).}
 \label{dynamics_rate_threshold_dyn_mean_field_sweeney}
@@
 These findings led us to the conclusion that---apart from the special case $\mathrm{\alpha=1}$, which is the equivalent to instantaneous diffusion---a mean-field model describing the diffusive signal as a mixture of individual activity and all neurons is not suitable for explaining the existence of stable heterogeneous distributions of rates for a broad range of diffusion constants.
-We did not intent to debase the validity of results of the mean-field model of Sweeney et al.
+We did not intend to debase the validity of results of the mean-field model of Sweeney et al.
 However, we could show that the steady-state solution of this simplified model will result in the same firing rate $\phi_0$ for all neurons, given any value of $\mathrm{\alpha}$ except $\mathrm{\alpha=1}$.
@@
 
-\subsection{Equilibrium in the full Diffusive Model} \label{Matrix_Diff_Model_Section}
+\subsection{Equilibrium in the Full Diffusive Model} \label{Matrix_Diff_Model_Section}
 Since the previous section has shown that the simplified model in \cite{Sweeney_Paper} has problems in maintaining a broad distribution of firing rates, turning to a more general formulation of the problem seemed reasonable.
@@
 We did so by recalling that Equation \eqref{NO_dyn} describes the full dynamics of the diffusive neurotransmitter.
-Furthermore, Equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregard of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma  r_i}$, $r_i$ representing a neuron's rate and $\gamma$ being defined by Equation \eqref{2d-sys-fixed-points1}.
+Furthermore, Equation \eqref{2d-sys-homeostasis1} represents a simplification by means of two assumptions, namely the disregarding of the diffusive term and the simplification of the process of NO-generation to a simple relation $\mathrm{nNOS_i = \gamma  r_i}$, $r_i$ representing a neuron's rate and $\gamma$ being defined by Equation \eqref{2d-sys-fixed-points1}.
 In this section we discuss the implications of an in-between description, only applying the second simplification, but retaining the diffusive term:
@@
 which is a two-dimensional Helmholtz equation with a superposition of rescaled Dirac functions.
-The solution of $NO$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of Equation \cite{EncyMath}.
+The solution of $NO$ is thus composed of a superposition of shifted and scaled versions of the Green's function of the differential operator on the left hand side of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz}, see \cite{EncyMath}.
 For each delta function $\delta^2(\mathbf{x}-\mathbf{x}_i)$, the solution is
@@
 where $\varepsilon$ determines the ``smoothness" of transition between $\psi$ and the cutoff value $\psi_0$.
-We chose $\varepsilon=10$ for all further calculations.
-We took the simple approach of interpreting this value as a mean of the analytic solution across the area covered by the corresponding grid cell to find an expression for $\mathrm{\psi_0}$.
+We chose $\varepsilon=10$ for all further calculations and we took the simple approach of interpreting this value as a mean of the analytic solution across the area covered by the corresponding grid cell to find an expression for $\mathrm{\psi_0}$.
 As an additional simplification, we substituted the necessary integration over the square grid cell by a circular area of equal size around the source.
@@
 \end{center}
-\caption[Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz}]{Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz} (blue, $h=10\;\mu m$) and its approximation (dashed) given by \eqref{Numeric_Solution_Expression_Trick}.
+\caption[Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz}]{Numerical steady-state solution of Equation \eqref{simple_NO_dyn_with_diff_equil_helmholtz} (blue, $h=10\, \upmu m$) and its approximation (dashed) given by \eqref{Numeric_Solution_Expression_Trick}.
 The numerical simulation was carried out on a two-dimensional grid and the curve represents a cut through the origin in x-direction.}
@@
 Note that the shift was applied to the second position.
-Theoretically, $n_x$,$n_y$ are to be iterated over all integers and in this case it is irrelevant whether to shift the first or the second position.
-We obviously had to limit the amount of elements of the sum for our calculations, such that copies that are shifted further away can be neglected.
-For the sake of performance the number of terms in the sum was adjusted to suffice for the given diffusion constant.
+Theoretically, $n_x$,$n_y$ are to be iterated over all integers, making it irrelevant whether to shift the first or the second position.
+We obviously had to limit the number of elements to be summed for our calculations, such that copies that are shifted further away can be neglected.
+For the sake of performance, the number of terms in the sum was adjusted to suffice for the given diffusion constant.
 
@@
 We were particularly interested in the quality of the predictions with respect to the choice of diffusion constant.
-Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \mu m^2 ms^{-1}}$, the correlation between measured and predicted firing rates is very good.
-In contrast, we included the---obviously unsuccessful---attempt to predict firing rates for a simulation with instant diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \mu m^2 ms^{-1}}$.
-This represented a limiting case where our analytic model could not make any meaningful predictions, since instant diffusion overrides any spatial inhomogeneities.
+Figure \ref{Rand_Matrix_Sol_vs_Sim} shows three examples: For $\mathrm{D=10\, \upmu m^2 ms^{-1}}$, the correlation between measured and predicted firing rates is very good.
+In contrast, we included the---obviously unsuccessful---attempt to predict firing rates for a simulation with instantaneous diffusion based on the spatial structure by setting D to a relatively high value of $\mathrm{D=100\, \upmu m^2 ms^{-1}}$.
+This represented a limiting case where our analytic model could not make any meaningful predictions, since instantaneous diffusion overrides any spatial inhomogeneities.
 The outcome of the third case shown in the plot, $\mathrm{D=0}$, is correctly predicted by the analytic model.
-In general, instant diffusion as well as $\mathrm{D=0}$ overrode the effects of spatial heterogeneity onto firing rates.
+In general, instantaneous diffusion as well as $\mathrm{D=0}$ overrode the effects of spatial heterogeneity onto firing rates.
 \begin{figure}
@@
 \caption[Measured firing rates versus analytically predicted firing rates]{Measured firing rates ($\mathrm{1200\,s \leq t \leq 1500\, s}$) versus predicted firing rates based on the solution of Equation \eqref{NO_equil_cond_interact_matrix_operator}.
-For $\mathrm{D=\infty}$ (instant diffusion in the full simulation), the analytic prediction was calculated with a comparably large diffusion constant of $\mathrm{D=100\, \mu m^2 ms^{-1}}$.}
+For $\mathrm{D=\infty}$ (instantaneous diffusion in the full simulation), the analytic prediction was calculated with a comparably large diffusion constant of $\mathrm{D=100\, \upmu m^2 ms^{-1}}$.}
 \label{Rand_Matrix_Sol_vs_Sim}
@@
 \end{center}
-\caption[Distribution of firing rates, full simulation and analytic prediction]{Distribution of firing rates for $\mathrm{D=10\, \mu m^2 ms^{-1}}$, full simulation and analytic prediction.
+\caption[Distribution of firing rates, full simulation and analytic prediction]{Distribution of firing rates for $\mathrm{D=10\, \upmu m^2 ms^{-1}}$, full simulation and analytic prediction.
 Data was taken from 10 simulation runs.}
@@
 However, we could see a general decline of correlation for larger diffusion constants.
-This trend was in line with the aforementioned limit of instant diffusion, namely a complete decorrelation between prediction and measurement, as well as the good agreement for $\mathrm{D= 10\, \mu m^2 ms^{-1}}$ shown in Figure \ref{Fir_Rate_Dist_Sim_vs_Mat}.
+This trend was in line with the aforementioned limit of instantaneous diffusion, namely a complete decorrelation between prediction and measurement, as well as the good agreement for $\mathrm{D= 10\, \upmu m^2 ms^{-1}}$ shown in Figure \ref{Fir_Rate_Dist_Sim_vs_Mat}.
 \begin{figure}
@@
 Same simulation data as in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} was used, each point representing a single simulation.
-The histograms for the analytic solutions were generated for 50 $\rm D$ values, spanning equally between $\rm D=0 mu m^2 /ms$ and $\rm D=20 \mu m^2 /ms$.
+The histograms for the analytic solutions were generated for 50 $\rm D$ values, spanning equally between $\rm D=0 \upmu m^2 /ms$ and $\rm D=20 \upmu m^2 /ms$.
 Each column is a histogram of $\rm 200$ firing-rate solutions for randomly generated positions, giving a total of $\rm 10000$ matrix solutions.}
@@
 
-To further back up this result we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it.
+To further back up this result we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \upmu m}$ and a $\mathrm{25\, \upmu m}$ distance between the border and the neurons closest to it.
 By doing so all neurons were given the same structure of neighbors.
@@
 Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the simulation result, being a significantly narrower distribution.
-As predicted, the analytic result showed a similarly narrow distribution.
-This strongly supported the previous assertion.
+The analytic result showed a similarly narrow distribution, which strongly supported the previous assertion.
 \begin{figure}
@@
 \end{center}
-\caption[Distribution of firing rates for a regular square grid]{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2 ms^{-1}}$, full simulation and analytic prediction.
+\caption[Distribution of firing rates for a regular square grid]{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \upmu m}$ and Neumann boundary conditions, $\mathrm{D=10\, \upmu m^2 ms^{-1}}$, full simulation and analytic prediction.
 1 Simulation run was used, with spikes within $\rm 1200 \leq t \leq 1500$.}
@@
 
-\subsubsection{Low-Density Neighborhoods correlate with strong outgoing Connections}
+\subsubsection{Low-Density Neighborhoods Correlate with Strong Outgoing Connections}
 In Section \ref{Section_Mean_outgoing_Weights} we stated that diffusive homeostasis allowed the network to develop few neurons with exceptionally strong outgoing weights.
@@
 \end{equation}
-Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should have strong outgoing weights and vice versa.
-We approximated the local neuron density by means of a a Gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$ to test this hypothesis.
+Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this made us draw the conclusion that low density regions should have strong outgoing weights and vice versa.
+We approximated the local neuron density by means of a a Gaussian kernel with $\mathrm{\sigma = 50\, \upmu m}$ to test this hypothesis.
 Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} shows the results.
@@
 \includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
-\caption[A/B: Scatter plot of inverse of local neuron density and decadic logarithm of outgoing excitatory weights.
-C: Frequency of excitatory weights versus inverse neural density.
-D: Decadic logarithm of mean outgoing excitatory weights versus inverse neural density]{A/B: Scatter plot of \emph{inverse} of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights.
+\caption[A/B: Scatter plot of reciprocal local neuron density and decadic logarithm of outgoing excitatory weights.
+C: Frequency of excitatory weights versus reciprocal neuronal density.
+D: Decadic logarithm of mean outgoing excitatory weights versus reciprocal neuronal density]{A/B: Scatter plot of \emph{reciprocal} local neuron density (calculated by convolution with a Gaussian kernel with $\mathrm{\sigma = 50\, \upmu m}$) and decadic logarithm of outgoing excitatory weights.
 Note the spatial correlation in high/low-density regions.
-C: Frequency of excitatory weights (averaged over $\rm 1200\,s \leq t \leq 1500\,s$) versus inverse neural density (same estimation method as in (A)).
+C: Frequency of excitatory weights (averaged over $\rm 1200\,s \leq t \leq 1500\,s$) versus reciprocal neuronal density (same estimation method as in (A)).
 Coefficient of correlation $\rho_{\rm frequ.-dens.} = 0.798$.
-D: Decadic logarithm of mean outgoing excitatory weights versus inverse neural density.
+D: Decadic logarithm of mean outgoing excitatory weights versus reciprocal neuronal density.
 Coefficient of correlation $\rho_{\rm weight.-dens.} = 0.513$.}
@@
 
-\subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}\label{NO_source_spread_section}
+\subsection{Spreading of NO Sources Extends Encoding of Input Heterogeneity}\label{NO_source_spread_section}
 We considered the possibility that a wider spatial spread of each individual NO source---in contrast to the approximate point source used up to this point---could locally decrease distinguishability between neurons since our analytic results revealed that a strong correlation between spatial structure and resulting firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors.
@@
 While Sweeney et al.
-argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide) Philippides et al.
-reported that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}.
-The diameter of these ``production areas" is on the order of $\mathrm{10-100 \mu m}$.
-
-To test our hypothesis, we modified our model such that each neuron released nitric oxide evenly into a circular area with a radius of $\mathrm{50 \, \mu m}$, centered around the neuron's position.
+argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide), Philippides et al.
+reported that NO is often synthesized in a more delocalized way by means of fine fibers originating from the soma \cite{Philippides_2005}.
+The diameter of these ``production areas" is on the order of $\mathrm{10-100 \upmu m}$.
+
+To test our hypothesis, we modified our model such that each neuron released nitric oxide evenly into a circular area with a radius of $\mathrm{50 \, \upmu m}$, centered around the neuron's position.
 The homeostatic readout was still taken solely from the centering point.
@@
 
+\clearpage
+
 \section{Discussion}
 The investigations and results presented within this thesis should be contextualized within two topics of research: First, the dynamic properties and mechanisms of neural homeostasis and how concepts of control theory should be applied to properly model activity regulation in the brain.
-And second, if, and if so, how much the particular distribution of firing rates present within a network affects neural plasticity and structure.
+And second, whether the particular distribution of firing rates present within a network affects neural plasticity and structure, and if so, to what extent.
 The focus of this thesis was put onto the first topic.
@@
 \subsection{Homeostatic Stability}
-Though being unintended in our recurrent network, the occurrence and necessary analysis of persistent oscillations led to a better understanding of their origin and the need for slow timescales of homeostatic adaptation.
+Though being unintended in our recurrent network, the occurrence and necessary analysis of persistent oscillations led to a better understanding of their origin and the need for slow timescales of homeostatic adaption.
 In another theoretical study Harnack et al.
@@
 \cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998,Koulakov_2009}.
-Our interpretation of our results leads to the conclusion that this canonical approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behavior.
+Our interpretation of our results leads to the conclusion that this canonical approach matches the limiting case of instantaneous diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behavior.
 
@@
 claimed that their implementation of diffusive homeostasis enables individual neurons to vary their firing rates more flexible compared to single-neuron homeostatic models, especially allowing for sustained encoding of different levels of external input.
-Interestingly, we could not confirm this, at least within the tests that we performed and the given set of standard parameters.
+Interestingly, we could not confirm this, at least by means of the tests that we performed and the given set of standard parameters.
 Overall, the resulting behavior of the excitatory population rather appeared to us as a form of single-neuron homeostasis whose individual targets are predetermined by the quenched random spatial structure of the respective cells.
@@
 Of course, this impression only applies to the case where the aforementioned mixture of influence between spatial and synaptic topology is dominated by the former.
-By analyzing network activity based on our analytic model we found that indeed only a single homeostatic fixed point exists for finite diffusion constants.
+By analyzing network activity based on our analytical model we found that indeed only a single homeostatic fixed point exists for finite diffusion constants.
 On a practical level though, the gradual decorrelation with this theoretical state of activity upon larger values of $\mathrm{D}$ was presumably caused by synaptic turnovers which change the synaptic input.
@@
 \subsubsection{Modifications of the Homeostatic Model}\label{Possible_Modifications_Section}
-Since these considerations evoked a rather skeptical view onto the biological plausibility of these results, we considered possible modifications of the homeostatic model.
+Since these elaborations elicited a quite skeptical view of the biological plausibility of our results, we considered possible modifications of the homeostatic model.
 One should note that these are to be evaluated in the context of providing a model of an actual physiological process.
-If the main goal was to simply provide a homeostatic method that retains an overall level of activity without tightly fixing individual rates, we would suggest to use the idealized model of instant diffusion, especially because of its computational simplicity.
-However, as already mentioned, the given experimentally based parameters do not allow to accept this simplification from the standpoint of biological and physical accuracy.
-
-Instead, we hypothesized that we might be able to uncouple activity from spatial structure without tweaking the diffusion process by spatially increasing the spread of NO-insertion.
+If the main goal was to simply provide a homeostatic method that retains an overall level of activity without tightly fixing individual rates, we would suggest to use the idealized model of instantaneous diffusion, especially because of its computational simplicity.
+However, as already mentioned, the given experimentally acquired parameters do not allow to accept this simplification with respect to biological and physical accuracy.
+
+Instead, we hypothesized that we might be able to uncouple activity from spatial structure without tweaking the diffusion process by spatially increasing the spread of NO insertion.
 The result presented in Section \ref{NO_source_spread_section} was positive.
@@
 From a more abstract point of view, it provides a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target.
-We therefore regard this idea as a potential modification for future use of diffusive homeostasis, gaining further control over the strictness of the homeostatic mechanism by adjusting the area of NO insertion.
+We therefore considered this idea as a potential modification for future use of diffusive homeostasis, gaining further control over the strictness of the homeostatic mechanism by adjusting the area of NO insertion.
 
@@
 Experimental studies have investigated the effect of NO onto the conductance of ionic channels \cite{Steinert_NO,Steinert_NO_2011}.
-Mapping these features onto a simple LIF-model is obviously not easy, and many consequences of NO-modulation onto neural dynamics can certainly not be represented in such a simple model.
+Mapping these features onto a simple LIF-model is obviously not easy, and many consequences of NO modulation onto neuronal dynamics can certainly not be represented in such a simple model.
 Our criticism is thus rather based on more general arguments.
@@
 Because of the limited amount of ion channels that exist in a cell and can be affected by nitric oxide, upper and lower bounds should however certainly be present.
-A simple approach to tackle this would be to implement hard bounds into our neuron model, not allowing the threshold to pass an upper and lower value.
+A simple approach to tackle this would be to implement hard bounds in our neuron model, not allowing the threshold to pass an upper and lower value.
 Another possibility is the implementation of these bounds by means of the differential equation itself.
-In either case, such a modification could break the ability of the network to tune thresholds in such a way that necessarily \emph{all} neurons eventually reach target concentration.
+In either case, such a modification could break the ability of the network to tune thresholds in such a way that necessarily \emph{all} neurons eventually reach the target concentration.
 As a consequence, the fixed point of firing rates under diffusive homeostasis would not be strictly determined by spatial structure, but by a combination of network structure and the neurons' positions.
@@
 The results of section \ref{Syn_Weight_Dist_Section} and \ref{Section_Syn_Lifetimes} have shown that both features, log-normal distribution of synaptic weights and a power-law distribution of synaptic lifetimes, can be reliably reproduced under our new homeostatic model.
-Relating this to the main result of Section \ref{Fir_Dist_Section}, it does not appear to be the case that a greater heterogeneity of firing activity has a significant influence onto the overall statistics of neural connectivity (though on a more detailed level, structural differences could be observed, as discussed in the next Section).
-
-The precise spiking activity of neurons does certainly influence weight dynamics due to STDP and learning processes in the brain depend on this relation between neural activity and synaptic structure.
-However, one might doubt that this non-randomness on a small scale is required to explain overall statistical features of neural connectivity.
+Relating this to the main result of Section \ref{Fir_Dist_Section}, it does not appear to be the case that a greater heterogeneity of firing activity has a significant influence onto the overall statistics of neuronal connectivity (though on a more detailed level, structural differences could be observed, as discussed in the next Section).
+
+The precise spiking activity of neurons does certainly influence weight dynamics due to STDP and learning processes in the brain depend on this relation between neuronal activity and synaptic structure.
+However, one might doubt that this non-randomness on a small scale is required to explain overall statistical features of neuronal connectivity.
 As mentioned in Section \ref{Syn_Weight_Dist_Section}, theoretical models based on stochastic processes were able to give an explanation for the presence of log-normal weight distributions \cite{Loewenstein_Spine_Sizes,Statman_Synapses_2014}.
@@
 \subsubsection{Strong Differences in Outgoing Weights}
-Even though our investigations on network topology were rather intended as a form of sanity check with respect to properties already found in earlier versions, we found a differences compared to non-diffusive homeostasis:
-The emergence of significantly above-average mean outgoing weights for a small subset of neurons, see section \ref{Section_Mean_outgoing_Weights}.
-By comparing the given mean values to statistics acquired by randomly shuffling recurrent excitatory weights and running a statistical test(see Figure \ref{Out_Weight_Mean_Quantile}), we found that this effect is indeed significant compared to chance.
-Thus, we identify the over-representation of strong outgoing weights as a non-random effect.
-However, we would like to emphasize that diffusive homeostasis is only indirectly responsible in the sense that it allows for a sustained heterogeneity among firing rates.
-
-Referring back to Figure \ref{Pop_Mean_Cross_Corr}, we can now relate the increment of correlation among the excitatory population in the case of diffusive homeostasis to the results discussed in this section: The emergence of very strong outgoing connections increases the probability of neurons being postynaptically connected to such highly influential neurons to fire shortly after the presynaptic neuron.
+Even though our investigations on network topology were rather intended as a form of sanity check with respect to properties already found in earlier versions, we found differences compared to non-diffusive homeostasis:
+the emergence of significantly above-average mean outgoing weights for a small subset of neurons, see section \ref{Section_Mean_outgoing_Weights}.
+By comparing the given mean values to statistics acquired by randomly shuffling recurrent excitatory weights and running a statistical test (see Figure \ref{Out_Weight_Mean_Quantile}), we found that this effect is indeed significant compared to chance.
+Therefore, we identify the over-representation of strong outgoing weights as a non-random effect.
+However, we would like to emphasize that diffusive homeostasis is only indirectly responsible, in the sense that it allows for a sustained heterogeneity among firing rates.
+
+Referring to Figure \ref{Pop_Mean_Cross_Corr}, we can now relate the increment of correlation among the excitatory population in the case of diffusive homeostasis to the results discussed in this section: The emergence of very strong outgoing connections increases the probability of neurons to be postynaptically connected to such highly influential neurons to fire shortly after the presynaptic neuron.
 In the light of the notion of ``rich get richer" or ``rich stay rich" weight dynamics that were reported for earlier versions of SORN and LIF-SORN, one can argue that this increment in correlation even further stabilizes these strong excitatory weights \cite{Pengsheng_2013,SORN_Paper}.
 
-Though theoretical and experimental studies have reported similarly about the presence of exceptionally ``ìnfluential" neurons \cite{Effenberger_2015,Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}, a lack of a clear concept of ``leader neurons" makes comparisons difficult and should be made with care.
-On the one hand, one could refer to the finding, that some neurons are more effective in terms of local spike initiation or bursting \cite{Eckmann_Leader_Neurons_2008}.
+Although theoretical and experimental studies have reported similarly about the presence of exceptionally ``ìnfluential" neurons \cite{Effenberger_2015,Yassin_Subnetworks_2010,Eckmann_Leader_Neurons_2008}, a lack of a clear concept of ``leader neurons" makes comparisons difficult and to be made with care.
+On the one hand, one could refer to the finding that some neurons are more effective in terms of local spike initiation or bursting \cite{Eckmann_Leader_Neurons_2008}.
 The presence of stronger outgoing weights for some excitatory neurons and an increment of pre-post spiketime correlations within the excitatory population generally support this finding.
-On the other hand, another aspect one could conceptually associate to ``driver neurons" is the presence of subnetworks of highly active neurons with stronger connectivity \cite{Yassin_Subnetworks_2010}.
+Another aspect one could conceptually associate to ``driver neurons" is the presence of subnetworks of highly active neurons with stronger connectivity \cite{Yassin_Subnetworks_2010}.
 Though we did find evidence that the connection fraction of a subpopulation of fast-spiking neurons was increased, the meaning and implication of this effect on a functional level needs more investigation.
-As mentioned in Section \ref{Section_Role_Fir_Rate_Het}, it has been argued that the combination of a large group of slowly firing neurons, which subject to stronger neuronal rewiring, and a small group of fast-firing neurons, forming more stable connections, is required to allow the brain to efficiently process and transmit information while being able to undergo longer lasting learning processes, which require plastic changes in the network structure \cite{Dragoi_2003,Buzsaki_2004,Buzsaki_Fir_Rates_2014}.
+As mentioned in Section \ref{Section_Role_Fir_Rate_Het}, it has been argued that the combination of a large group of slowly firing neurons, being subject to stronger neuronal rewiring, and a small group of fast-firing neurons, forming more stable connections, is required to allow the brain to efficiently process and transmit information while being able to undergo longer lasting learning processes, which require plastic changes in the network structure \cite{Dragoi_2003,Buzsaki_2004,Buzsaki_Fir_Rates_2014}.
 Thus, one might consider testing the performance of learning tasks that had previously been investigated using the SORN and LIF-SORN under diffusive homeostasis.
@@
 Our theoretical considerations regarding the steady state of firing activity allowed us to further clarify the actual determinants of the resulting firing rate statistics.
-It turned out that, depending on the choice of diffusion parameters, a weighted mixture between the distribution of neural inputs and the spatial configuration determines the resulting statistics of firing rates.
+It turned out that, depending on the choice of diffusion parameters, a weighted mixture between the distribution of neural inputs and the spatial configuration underlies the resulting statistics of firing rates.
 The former aspect is in line with common theoretical approaches of explaining firing rate distributions.
-The latter aspect can be subsumed by the hypothesis that local fluctuations of neural density can influence firing rates and shape their overall distribution.
+The latter aspect can be subsumed by the hypothesis that local fluctuations of neuronal density can influence firing rates and shape their overall distribution.
 This was a rather unconventional idea, and we had to leave the question of biological plausibility unanswered.
 
-The implementation of diffusive homeostasis led to an interesting observation regarding network structure: Due to the broad range of neural activity it allowed for the emergence of highly influential subgroups of excitatory neurons.
+The implementation of diffusive homeostasis led to an interesting observation regarding network structure: Due to the broad range of neuronal activity it allowed for the emergence of highly influential subgroups of excitatory neurons.
 This feature was not present in earlier versions of the LIF-SORN.
@@
 
-\section{Full Derivation of the Power Spectrum given in Equation \eqref{Pow_Spec_Theta_Final}}\label{Appendix_Power_Spectrum}
+\section{Full Derivation of the Power Spectrum Given in Equation \eqref{Pow_Spec_Theta_Final}}\label{Appendix_Power_Spectrum}
 Starting with the dynamic equations
@@
 i\omega f_n &= - \lambda f_n + \frac{\gamma \alpha N_{\rm exc.}}{L^2}f_\theta + \sigma_{NO} f_{\xi} \label{Appendix_Equation_3} \\
-i\omega f_\theta &= \frac{f_n}{NO_0\tau_{V_t}}\;. \label{Appendix_Equation_4}\\
+i\omega f_\theta &= \frac{f_n}{NO_0\tau_{V_t}}\;. \label{Appendix_Equation_4}
 \end{align}

### 2017-03-16 draft_duplex_version.tex
.

--- 2017-03-15 draft.tex
@@
 \usepackage{upgreek}
-\usepackage[titletoc]{appendix}
+\usepackage[titletoc,title]{appendix}
+\usepackage{afterpage}
+\usepackage[nottoc,notlot,notlof]{tocbibind}
+
 \captionsetup[table]{singlelinecheck=false}
 \captionsetup[figure]{singlelinecheck=false}
+
+\renewcommand{\floatpagefraction}{.8}
 
@@
 \clearpage
+
+\mbox{}
 \thispagestyle{empty}
+
+\newpage
+
+\pagenumbering{gobble}
 
@@
 \clearpage
+
+\mbox{}
 \thispagestyle{empty}
+
+\newpage
 
@@
 
+\pagenumbering{arabic}
+\setcounter{page}{1}
+
 \tableofcontents
@@
 \clearpage
-
-\setcounter{page}{1}
 
@@
 
+\mbox{}
+\thispagestyle{empty}
+
+\newpage
+
 \section{Introduction}
@@
 59-64]{Cybernetik_Systems_Cruse_2006}.
+
+\pagebreak
 
@@
 
+\pagebreak
+
 \subsection{Thesis Outline}
@@
 In the face of possible new features within the network's structure, we clarify the causal relation between diffusive spatial interaction and synaptic topology.
+
+\clearpage
 
@@
 
-\begin{table}
+\begin{table}[h]
 \caption{Parameters of synaptic connections.}
@@
 \end{align}
-By mean of the coordinate transformations
+By means of the coordinate transformations
 \begin{align}
@@
 Interspike intervals should be random on the level of single cells, approximately following the statistics of a Poisson process.
+
+Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficients of variation ($\mathrm{CV\equiv\sigma/\mu}$) taken over the set of excitatory and inhibitory neurons.
+However, we restricted the statistics of ISIs to neurons whose mean firing rate fell into a window of a width of $\rm 1\, Hz$ and a certain mean in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case (see legend in Figure \ref{ISI_CV_compare}).
+An approximately exponential distribution of ISIs was apparently preserved for diffusive homeostasis (represented by straight lines in a log-plot), which is characteristic for Poisson processes \cite[p.
+27]{Theor_Neur_Dayan}.
+For perfect Poisson spiking, the CV should give a value of 1.
+CVs that are smaller or larger, as seen in Figure \ref{ISI_CV_compare} B/D, indicate a tendency towards greater regularity or bunching, respectively.
+This observation is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons had an  under-representation of short ISIs, the opposite was the case for inhibitory neurons.
+These types of behavior of LIF-models have been shown to depend on the amount of fluctuations of the input the neuron receives: A larger CV of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals \cite{Ostojic2011}.
+By the CV of the \emph{input} we mean the ratio between standard deviation and mean of postsynaptic current due to presynaptic spiking events (under the assumption of a stationary mean and variance).
+This relation between fluctuating input and spiking statistics fitted nicely into our set of network parameters: Inhibitory neurons received stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
+This lowered the signal-to-noise ratio for the inputs of inhibitory neurons, leading to the aforementioned statistical differences.
+Still, we could observe a dominant exponential component for both excitatory and inhibitory neurons.
+
 \begin{figure}
@@
 \end{figure}
-Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficients of variation ($\mathrm{CV\equiv\sigma/\mu}$) taken over the set of excitatory and inhibitory neurons.
-However, we restricted the statistics of ISIs to neurons whose mean firing rate fell into a window of a width of $\rm 1\, Hz$ and a certain mean in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case (see legend in Figure \ref{ISI_CV_compare}).
-An approximately exponential distribution of ISIs is apparently preserved for diffusive homeostasis (represented by straight lines in a log-plot), which is characteristic for Poisson processes \cite[p.
-27]{Theor_Neur_Dayan}.
-For perfect Poisson spiking, the CV should give a value of 1.
-CVs that are smaller or larger, as seen in Figure \ref{ISI_CV_compare} B/D, indicate a tendency towards greater regularity or bunching, respectively.
-This observation is presumably due to the statistics of ISIs close to zero: Interestingly, while excitatory neurons have an  under-representation of short ISIs, the opposite is the case for inhibitory neurons.
-These types of behavior of LIF-models have been shown to depend on the amount of fluctuations of the input the neuron receives: A larger CV of neural input leads to a larger CV of ISIs for the output and an over-representation of small intervals \cite{Ostojic2011}.
-By the CV of the \emph{input} we mean the ratio between standard deviation and mean of postsynaptic current due to presynaptic spiking events (under the assumption of a stationary mean and variance).
-This relation between fluctuating input and spiking statistics fits nicely into our set of network parameters: Inhibitory neurons receive stronger recurrent inhibitory input ($\mathrm{-60\,mV}$ in total) compared to excitatory neurons ($\mathrm{-12\,mV}$).
-This lowers the signal-to-noise ratio for the inputs of inhibitory neurons, leading to the aforementioned statistical differences.
-Still, one can observe a dominant exponential component for both excitatory and inhibitory neurons.
 
@@
 
-\begin{table}
+\begin{table}[h]
 \caption{Diffusion constants and number of simulations used in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D}.}
@@
 %% density_vs_sum_out_weights.py
-\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights.png}
+\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_new.png}
 %% density_vs_sum_out_weights_points.py
-\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
+\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points_new.png}
 \caption[A/B: Scatter plot of reciprocal local neuron density and decadic logarithm of outgoing excitatory weights.
@@
 reported that NO is often synthesized in a more delocalized way by means of fine fibers originating from the soma \cite{Philippides_2005}.
-The diameter of these ``production areas" is on the order of $\mathrm{10-100 \upmu m}$.
+The diameter of these ``production areas" is on the order of $\mathrm{10-100\, \upmu m}$.
 
@@
 \begin{figure}
+\begin{center}
 %% spread_source_illustration.py
-\includegraphics[width=\textwidth]{../../plots/spread_source_illustration.png}
+\includegraphics[width=0.9\textwidth]{../../plots/spread_source_illustration.png}
 %% plot_external_input_switch_activity_spread_source.py
-\includegraphics[width=\textwidth]{../../plots/external_input_switch_spread_source.png}
+\includegraphics[width=0.855\textwidth]{../../plots/external_input_switch_spread_source.png}
 \caption[A/B: Illustration of circular kernels used for NO-insertion, overlay of all 400 neurons and a single example.
@@
 All settings were kept the same as for Figure \ref{Ext_Input_Switch}.}
+\end{center}
 \label{External_Input_Switch_Spread_Source}
@@
 Since this effect is directly linked to the low-density/high-firing-rate relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that synapses with above-average firing presynaptic neurons tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
+\clearpage
+\afterpage{\null\newpage}
+\clearpage
 
@@
 \clearpage
+\afterpage{\null\newpage}
+\clearpage
 
@@
 
-\section{Full Derivation of the Power Spectrum Given in Equation \eqref{Pow_Spec_Theta_Final}}\label{Appendix_Power_Spectrum}
+\section{Derivation of the Power Spectrum Given in Equation \eqref{Pow_Spec_Theta_Final}}\label{Appendix_Power_Spectrum}
 Starting with the dynamic equations
@@
 \dot{n} &= -\lambda n + \frac{\gamma \alpha N_{\rm exc.}}{L^2}\theta + \sigma_{NO} \xi(t) \label{Appendix_Equation_1}\\
-\dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \label{Appendix_Equation_2}
+\dot{\theta} &= \frac{1}{NO_0 \tau_{V_t}} n \; , \label{Appendix_Equation_2}
 \end{align}
@@
 \end{equation}
-Note that since we assumed the noise term $\xi$ to be approximately white and Gaussian noise with unit variance, its power spectrum is $|f_{\xi}|^2 = 1$
+Note that since we assumed the noise term $\xi$ to be approximately white and Gaussian noise with unit variance, its power spectrum is $|f_{\xi}|^2 = 1$.
 

### 2017-03-20 draft_duplex_shift_half_cm.tex
.

--- 2017-03-16 draft_duplex_version.tex
@@
 %\usepackage{layouts}
-\usepackage[a4paper,margin=1.5in]{geometry}
-%\usepackage{geometry}
-%\geometry{
-%a4paper,
-%left=2.0in,
-%right=1.0in}
+%\usepackage[a4paper,margin=1.5in]{geometry}
+\usepackage{geometry}
+\geometry{a4paper,lmargin=1.6969in,rmargin=1.3031in,tmargin=1.5in,bmargin=1.5in,twoside}
 \usepackage[utf8]{inputenc}
@@
 \pagenumbering{gobble}
+\setcounter{page}{1}
 
@@
 \pagenumbering{arabic}
-\setcounter{page}{1}
+\setcounter{page}{4}
 
@@
 Therefore, we actually found its minimal value for $x_{\rm max.} = \rm 750 \, s$ for both diffusive homeostasis and non-diffusive homeostasis ($d_{\rm max.,diff.}^{min.} = 0.30$, $d_{\rm max.,non-diff.}^{min.} = 0.34$).
-We thus accepted the values for $\alpha$ acquired by MLE for both entire datasets as valid, yielding $\mathrm{\alpha_{\rm diff.} = -1.455}$ and $\mathrm{\alpha_{\rm don-diff.} = -1.468}$.
+We thus accepted the values for $\alpha$ acquired by MLE for both entire datasets as valid, yielding $\mathrm{\alpha_{\rm diff.} = -1.455}$ and $\mathrm{\alpha_{\rm non-diff.} = -1.468}$.
 The resulting exponents are slightly smaller than previously reported values of $\mathrm{\approx - 5/3}$ \cite{SORN_Paper}.
@@
 \caption[Distribution of lifetimes of recurrent excitatory synaptic connections]{Distribution of lifetimes of recurrent excitatory synaptic connections.
-Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a power-law exponent of $\mathrm{\alpha_{\rm diff.} = -1.455}$ (standard error $\mathrm{\sigma_{\rm diff.} = 5.52 \cdot 10^{-4}}$) for diffusive homeostasis and $\mathrm{\alpha_{\rm don-diff.} = -1.468}$ (standard error $\mathrm{\sigma_{\rm don-diff.} = 5.70 \cdot 10^{-4}}$) for non-diffusive homeostasis.}
+Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a power-law exponent of $\mathrm{\alpha_{\rm diff.} = -1.455}$ (standard error $\mathrm{\sigma_{\rm diff.} = 5.52 \cdot 10^{-4}}$) for diffusive homeostasis and $\mathrm{\alpha_{\rm non-diff.} = -1.468}$ (standard error $\mathrm{\sigma_{\rm non-diff.} = 5.70 \cdot 10^{-4}}$) for non-diffusive homeostasis.}
 \label{Syn_Lifetimes}

### 2017-03-20 draft_duplex_shift_quarter_cm.tex
.

--- 2017-03-16 draft_duplex_version.tex
@@
 %\usepackage{layouts}
-\usepackage[a4paper,margin=1.5in]{geometry}
-%\usepackage{geometry}
-%\geometry{
-%a4paper,
-%left=2.0in,
-%right=1.0in}
+%\usepackage[a4paper,margin=1.5in]{geometry}
+\usepackage{geometry}
+\geometry{a4paper,lmargin=1.5984in,rmargin=1.4016in,tmargin=1.5in,bmargin=1.5in,twoside}
 \usepackage[utf8]{inputenc}
